### 2024-08-13 main.tex
init: paper.tex without pics
Signed-off-by: LetMeFly666 <814114971@qq.com>

\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
%\usepackage{algorithmic}
%\usepackage{algorithm}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{cite}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% updated with editorial comments 8/9/2021

\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}

\usepackage{dsfont}
\usepackage{amssymb}
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{ragged2e}
\usepackage{latexsym, amssymb, verbatim, amsmath}
\usepackage{amsmath,bm}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{subeqnarray}
\usepackage{cases}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{color}
\usepackage{cite}
\usepackage[]{chapterbib}
\usepackage{enumerate}

\usepackage[dvipsnames, svgnames, x11names]{xcolor}
\usepackage{algorithm,algpseudocode,float}

\begin{document}

\title{SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Stealthy Poisoning Attacks in IoRT Networks}

\author{Zan Zhou, %~\IEEEmembership{Student Member,~IEEE},
Yirong Zhuang, Hongjing Li, Sizhe Huang, Shujie Yang, Peng Guo, Lujie Zhong, Zhenhui Yuan, Changqiao Xu,~\IEEEmembership{Senior Member,~IEEE}
% <-this % stops a space
\thanks{Z. Zhou, H. Li, S. Huang, S. Yang, P. Guo, and C. Xu are with the State Key Laboratory of Networking and Switching Technology, Beijing University of Posts and Telecommunications, Beijing 100876, P.R. China. E-mail: \{zan.zhou, lihongjing, swhsz, sjyang, guopeng, cqxu\}@bupt.edu.cn. 
	}  % <-this % stops a space
\thanks{Y. Zhuang is with the Research Institute of China Telecom, Ave Zhongshan, Guangzhou 510630, China. E-mail: 13316094433@chinatelecom.cn.}% <-this % stops a space
 \thanks{L. Zhong is with the Information Engineering College, Capital Normal University, Beijing 100048, China. E-mail: zhonglj@cnu.edu.cn (Corresponding author).}% <-this % stops a space
\thanks{Zhenhui Yuan is with Northumbria University, United Kingdom. E-mail: zhenhui.yuan@warwick.ac.uk.}% <-this % stops a space
%\thanks{This paper was produced by the IEEE Publication Technology Group. They are in Piscataway, NJ.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2021; revised August 16, 2021.}
}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2021}%
{Shell \MakeLowercase{\textit{et al.}}: A Sample Article Using IEEEtran.cls for IEEE Journals}

%\IEEEpubid{0000--0000/00\$00.00~\copyright~2021 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

\maketitle

\begin{abstract}
Fairness-aware federated learning (FFL) plays a crucial role in mitigating bias against specific demographic groups (e.g., gender, race, occupation) during collaborative training. 
Along with the ever-emerging new attack paradigms like gradient leakage and model poisoning, the reliability of FFL also obtains lots of research attention. Either UAV nodes or FFL aggregators could be untrusted adversaries. 
Although multiple security mechanisms involving encryption, obfuscation, Byzantine-robustness, and detection have been proposed, concrete to UAV networks, the majority of existing solutions are unfeasible due to high heterogeneity and limited resources among participants. 
Hence, in this paper, we propose mutually reliable FFL (MR-FFL), a stratified community-based framework to facilitate privacy protection (FFL aggregator's reliability) and poisoning elimination (client nodes' reliability) jointly for FFL in heterogeneous UAV networks. 
We first divide UAV nodes into both peer communities (PC) and colleague communities (CC) according to cross-participant similarity and task-oriented fitness, respectively. 
Thus, the arbitrarily settled learning tasks following fair principles can be efficiently completed by fine-tuned colleague communities, even in the presence of a large degree of heterogeneity among peer communities. 
Then, we integrate community-specific differential privacy into the MR-FFL process, to achieve privacy amplification as well as efficient and personal collaborative training at the same time. 
More importantly, we proposed a community-based credit evaluation to resist poisoning attacks in heterogeneous environments. 
The results on several standard datasets also highlight the performance of MR-Fed in terms of fairness, accuracy, and integrity jointly.

% Fairness-aware federated learning (FFL) assumes a pivotal role in mitigating bias directed at specific demographic groups (e.g., gender, race, occupation) during collaborative training. The escalating threat landscape, characterized by emerging attack paradigms like gradient leakage and model poisoning, intensifies research scrutiny on FFL's reliability, recognizing the potential untrustworthiness inherent in UAV nodes and FFL aggregators. 
% Despite a plethora of proposed security mechanisms encompassing encryption, obfuscation, Byzantine robustness, and detection, their pragmatic application within UAV networks faces challenges due to pronounced heterogeneity and resource constraints among participants. Consequently, this paper introduces a novel approach, termed mutually reliable FFL (MR-FFL), presenting a stratified community-based framework. This framework concurrently addresses privacy protection (FFL aggregator's reliability) and poisoning elimination (edge nodes' reliability) within the context of FFL in heterogeneous UAV networks. 
% The categorization of UAV nodes into peer communities and colleague communities based on cross-participant similarity and task-oriented fitness facilitates the efficient completion of learning tasks adhering to fair principles. This effectiveness persists even in the presence of considerable heterogeneity among peer communities. Additionally, community-specific differential privacy is integrated into the MR-FFL process, achieving simultaneous privacy amplification and efficient, personalized collaborative training. 
% A noteworthy contribution lies in the introduction of a community-based credit evaluation system, designed to resiliently counteract poisoning attacks in heterogeneous environments. Empirical evaluations on standard datasets underscore the comprehensive performance of MR-Fed, highlighting its effectiveness in promoting fairness, privacy, and integrity within federated learning systems.

\end{abstract}

\begin{IEEEkeywords}
Federated learning, fairness, privacy, integrity, heterogeneous UAV network.
\end{IEEEkeywords}

\section{Introduction}
%\IEEEPARstart{T}{his} file is intended to serve as a ``sample article file'' for IEEE journal papers produced under \LaTeX\ using IEEEtran.cls version 1.8b and later. The most common elements are covered in the simplified and updated instructions in ``New\_IEEEtran\_how-to.pdf''. For less common elements you can refer back to the original ``IEEEtran\_HOWTO.pdf''. It is assumed that the reader has a basic working knowledge of \LaTeX. Those who are new to \LaTeX \ are encouraged to read Tobias Oetiker's ``The Not So Short Introduction to \LaTeX ,'' available at: \url{http://tug.ctan.org/info/lshort/english/lshort.pdf} which provides an overview of working with \LaTeX.
%FFL很重要
%作为的一种，
As a preeminent collaborative artificial intelligence paradigm, Federated Learning (FL) has garnered substantial research focus \cite{ETT2}. 
By effectively mobilizing a substantial number of participants with a discrete distribution, FL can concurrently enhance learning performance, resource utilization, and data security. 
Besides, as intelligent applications proliferate, concerns regarding fairness-aware federated learning (FFL) have also captured significant attention \cite{zhou2021towards-KDDtutorial-FFL}. Due to the agnostic of multiple data sources, models trained through FL may exhibit discriminatory tendencies toward specific features or demographic groups, such as gender, race, and occupation (e.g., COMPAS recidivism algorithm \cite{angwin2022machine} and facial recognition system \cite{raji2019actionable}). In response to this inherent deficiency, various FFL algorithms, such as FairFed \cite{ezzeldin2023fairfed}, Ditto \cite{li2021ditto}, and FairFL \cite{zhang2020fairfl}, have been proposed.

%安全问题很重要
\subsection{Mutual reliability problem of FFL}
Meanwhile, along with the continual emergence of novel attack techniques, such as gradient leakage and model poisoning \cite{fang2020local}, the \textit{``trust crisis''} \cite{zhou2022multi} has become a critical bottleneck in determining FFL deployment capabilities \cite{rodriguez2023survey}. Establishing a robust \textit{mutual reliability} relationship between the FL aggregator (parameter server) and local participants has proven challenging \cite{zhou2022multi}. To be specific, on the one hand, concerns about data sharing leading to privacy breaches (\textit{aggregator's reliability}) \cite{wang2021variational} raise apprehensions among owners of data and computational resources, significantly diminishing enthusiasm for collaborative learning participation and giving rise to the phenomena of ``isolated data islands''. On the other hand, PSs are troubled by the difficulty of promptly and accurately thwarting stealthy attackers hidden among a vast client base. This concern  (\textit{client nodes' reliability}) raises the specter of manipulation or even invalidation of the entire model, resulting in severe economic and intellectual property losses.

%列举几个特点，导致现有安全技术不能适用
%尽管多种最新的安全增强技术能够取得显著的防御效果，但攻击者并不能
\subsection{Characteristics and motivation of mutual reliable FFL in heterogeneous UAV networks}
With the advancement of integrated sensing, computation and communication (ISCC) \cite{he2023integrated}, and the space-air-ground integrated network (SAGIN) \cite{shen2023survey}, unmanned aerial vehicle (UAV) networks have played a crucial role in various domains such as post-disaster reconstruction, emergency temporary communication, and medical monitoring \cite{lu2023uav}. FLs based on UAV networks have also found widespread applications \cite{ETT1, ETT3, pandya2023federated}. However, despite the proposal of various secure FL technologies, the inherent characteristics of UAV networks continue to pose significant challenges in establishing mutual reliability for FFL in UAV environments. Specifically, these challenges encompass the following aspects:

%异构：大范围异构，小范围相似.因此
\textbf{1) Heterogeneity among UAV nodes:} As illustrated in Figure \ref{fig1:UAV-Network}, constrained by the mobility and patrol paths of UAVs, individual nodes are often limited to conducting data collection within a specific regional scope. Hence, even when employing identical equipment, the data distributions among UAV nodes across the entire network exhibit significant heterogeneity, while UAVs within the same area are similar. Therefore, various existing reliable FL technologies lacking adaptive considerations (such as Krum \cite{blanchard2017machine-krum}, Baffle \cite{andreina2021baffle}, and AGRamplifier \cite{gong2023agramplifier}) can lead to substantial accuracy losses.

%资源受限：因此高消耗的安全策略并不能适用  高计算消耗和带宽占用的安全技术（例如，加密）
\textbf{2) Resource limitation of UAV devices:} As UAV nodes function as mobile devices and bear substantial flight-related loads, their communication and energy resources are relatively constrained. The efficiency of FFL training is equally important. Consequently, solutions integrating cryptography, auxiliary training, multi-round detection, or other security mechanisms with high computational costs and bandwidth utilization (e.g., ShieldFL \cite{ma2022shieldfl}, AFA \cite{munoz2019byzantine-AFA}, and FLdetector \cite{zhang2022fldetector}) are not applicable for real-world deployment.

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{figures/fig1.PNG}
\caption{FFL Illustration in Heterogeneous UAV Networks: Taking target recognition as an example, UAV node group patrolling in urban areas may collect a higher proportion of ``automobile'' samples (e.g., UN1 and UN2), while UAV groups patrolling in port areas will acquire more ``ship'' samples (e.g., UN6 and UN7). Consequently, the dataset distributions across the entire network often exhibit significant imbalance, while simultaneously displaying a certain degree of similarity within localized regions.
}
\label{fig1:UAV-Network}
\end{figure}

%我们的目标是实现（1）异构容忍的FFL框架（2）强隐私保护的个性化训练交互（3）抗污染的可信评估
The aforementioned characteristics distinguish the reliable FFL in heterogeneous UAV networks from existing secure FFL technologies, thereby motivating the establishment of the following new criteria for its enhancement:

\textbf{1) Heterogeneity-tolerant FFL framework:} Suitable nodes from the highly heterogeneous UAV networks can be organized promptly to efficiently fulfill arbitrary fairness-aware FL tasks, which also mitigates redundant computational energy consumption and accuracy loss induced by heterogeneity.

\textbf{2) Privacy-preserving personalized training:} Throughout the iteration training and interaction process, sample-level privacy protection must be implemented to prevent the leakage of sensitive information. Additionally, considering the resource constraints of UAV nodes, computational and bandwidth demands should be limited.

\textbf{3) Poisoning-resilient credit evaluation:} In addition to robust defense capabilities against various poisoning attacks, compatibility with heterogeneity and privacy requisites is also essential. In other words, without compromising the effectiveness of privacy guarantee, heterogeneous benign UAV nodes should be treated equally during the whole FFL workflow.%Achieving fairness among heterogeneous benign users without compromising the effectiveness of privacy protection is a crucial aspect.

\subsection{Our solution and contributions}
%解决方案
% Hence, in this paper, we propose mutually reliable FFL (MR-FFL), a stratified community-based framework to facilitate privacy protection (FFL aggregator's reliability) and poisoning elimination (client nodes' reliability) jointly for FFL in heterogeneous UAV networks. 
% We first divide UAV nodes into both peer communities and colleague communities according to cross-participant similarity and task-oriented fitness, respectively. 
% Thus, the arbitrarily settled learning tasks following fair principles can be efficiently completed by fine-tuned colleague communities, even in the presence of a large degree of heterogeneity among peer communities. 
Therefore, this paper proposes mutual reliable FFL (MR-FFL), a stratified community-based framework that collectively promotes privacy protection during data sharing (reliability of FFL aggregators) and poisoning elimination during model aggregation (reliability of client nodes) in heterogeneous UAV networks. The contributions of the proposed MR-FFL are three-fold:

%贡献

\begin{itemize}
    %\item In light of shuffling-based MTD \cite{zhou2022multi} strategies, we propose a credit to identify the malicious attackers without compromising of privacy guarantees, which is also one of the design inspirations of our framework. 
    \item Initially, UAV nodes are partitioned into peer communities and colleague communities based on cross-participant similarity and task-oriented adaptability. Thus, adhering to fairness principles, any arbitrarily determined learning task can be effectively accomplished through carefully selected colleague communities, even in the presence of significant heterogeneity among UAV nodes, while peer communities provide an amplified privacy guarantee. 
    %随后，我们提出了PSDP的隐私模糊化方式进行自适应训练，通过参数动态约束差分隐私敏感度，从而在同等隐私保护水平下大幅降低异构环境下的噪声损失。
    \item Subsequently, inspired by cross-silo privacy protection, we introduce the new privacy perturbation notion of peer community-specific differential privacy (PSDP) with changeable privacy budget. Through dynamically constraining the DP sensitivity within each peer community, PSDP significantly reduces noise loss in heterogeneous environments under equivalent privacy protection levels.
    %此外，我们提出了基于三值主观逻辑模型的信用评估，分别抽离投毒攻击的“操纵”（相似度）和“破坏”（准确度）行为进行群体参与的综合长效评价，从而有效抵御多种隐蔽的投毒攻击范式。
    \item Furthermore, we propose a new credit evaluation based on the ternary subjective logic model. This evaluation effectively integrates comprehensive and long-term assessments with the collective participation of heterogeneous UAV nodes, specifically extracting the ``manipulation'' (similarity) and ``disruption'' (accuracy) behaviors of poisoning attacks. This approach proves effective in defending against various covert poisoning attack paradigms. 
    %\item Then, we integrate community-specific differential privacy into the MR-FFL process, to achieve privacy amplification as well as efficient and personal collaborative training at the same time. 
    %\item More importantly, we proposed a community-based credit evaluation to resist poisoning attacks in heterogeneous environments.

\end{itemize}

%本文组织结构
The remainder of this paper is organized as follows: The related works are reviewed in Section \uppercase\expandafter{\romannumeral2}. The system model is presented in Section \uppercase\expandafter{\romannumeral3}. Then, stratified community construction, adaptive training, and credit evaluation modules are expounded upon in Section \uppercase\expandafter{\romannumeral4} to \uppercase\expandafter{\romannumeral6}, respectively, providing a detailed account of availability, privacy, and integrity for FFL in heterogeneous UAV networks. Section \uppercase\expandafter{\romannumeral7} presents experimental results. Finally, Section \uppercase\expandafter{\romannumeral8} concludes this paper. %and briefly explores future directions.

\section{Related work}
According to the three basic tenets of information security \cite{zhou2021augmented-globecom}, in this section, we systematically review the most crucial hindrances of existing FFL solutions in UAV networks: \textit{availability}, \textit{confidentiality}, and \textit{in tegrity} problems, which we settled in following sections, respectively. 
\subsection{FFL in heterogeneous environments (availability)}
To accomplish learning tasks and ensure the availability of FFL in heterogeneous environments, existing solutions can adopt debiasing on the client or server side.
\subsubsection{Server-side debiasing} %全局化
As the name indicated, server-side debiasing methods usually monitor the composition of training data and design new loss functions like Ratio loss \cite{wang2021addressing} to mitigate the impact of heterogeneity. 
Besides, FairFed \cite{ezzeldin2023fairfed} adjusts the aggregation weights of heterogeneous participants based on equal opportunity difference (EOD). Hence, clients can conduct different debiasing processes. 
Likewise, FedProto \cite{tan2022fedproto} regularizes the training of local models with the aid of abstract class prototypes from the server. 
To handle the performance degradation caused by heterogeneous and long-tailed data, CReFF\cite{shang2022federated} re-trains the biased classifier with federated features in a privacy-preserving manner. 
Different from the above methods, several clustered FLs provide separate models for heterogeneous clients \cite{sattler2020clustered-CFL}, which can incur exponentially growing computation costs.
\subsubsection{Client-side debiasing} %个性化
Diverging from server-side debiasing, client-side debiasing methods primarily enhance accuracy by altering the local model \cite{tan2022towards}. 
For example, while retaining the standard FL mechanism as the inner optimizer, FairBatch \cite{roh2020fairbatch} further adds an outer optimizer to select minibatch sizes and improve model fairness adaptively. Similarly, Ditto \cite{li2021ditto} develops a regular term to optimize the local models without changing global aggregation rules. The robustness and fairness are jointly improved. 
Moreover, Mohri \textit{et al.} \cite{mohri2019agnostic} propose agnostic federated learning (AFL) and prove its fairness using data-dependent Rademacher complexity guarantees.

%总结：现有FFL有两大问题，首先是效率不佳，往往需要多轮训练，不适合于能量受限的UAV network。其次是缺乏考虑对联邦学习可信技术的兼容。
To summarize, existing FFLs encounter two drawbacks. Firstly, they exhibit unsatisfactory efficiency, often necessitating multiple training rounds, rendering them unsuitable for energy-constrained UAV networks. Secondly, the consideration for compatibility with reliable technologies is insufficient.
\subsection{Reliability of information sharing (confidentiality)}%隐私安全
\subsubsection{Cryptography solutions} 
Homomorphic encryption (HE) and other cryptographic methods naturally serve as suitable privacy protection measures. For instance, ShieldFL \cite{ma2022shieldfl} employs secure cosine similarity to measure the distance between two encrypted gradients, utilizing dual-gate HE to resist model poisoning. BatchCrypt \cite{zhang2020batchcrypt} further enhances HE efficiency by incorporating batch gradient encoding and holistic encryption, effectively reducing training time and communication overhead. Additionally, FairFL \cite{zhang2020fairfl} adopts the principled deep multi-agent reinforcement learning framework and secure information aggregation protocol to simultaneously optimize the accuracy and the fairness of FFL while respecting the strict privacy constraints of the clients. 
Besides, Lyu \textit{et al.} \cite{lyu2020towards} develop a local credibility mutual evaluation mechanism to guarantee fairness, and a three-layer onion-style encryption scheme to guarantee both accuracy and privacy. 
\subsubsection{Obfuscation solutions}

In comparison to encryption, obfuscation approaches such as differential privacy (DP) do not introduce excessive overhead or extensive mechanism modifications, thus garnering significant attention \cite{padala2021federated}. For instance, Wei \textit{et al.} \cite{wei2021low} consider both general training performance and individual client privacy requirements to mitigate latency on wireless channels, addressing challenges posed by channel fading and interference in unknown network environments. Furthermore, considering potential model distortion from obfuscation techniques, privacy amplification as Shuffle \cite{girgis2021shuffled} can enhance the deployment capabilities of privacy protection. NbAFL \cite{wei2020federated-NbAFL} further diminishes the accuracy loss associated with DP by injecting secondary noise into the uplink and downlink channels.

%总结：密码学方法通信量和计算量过大，而DP方法缺乏对异构考量
Upon analysis, privacy-preserving information-sharing methods based on cryptography often incur excessive communication and computational overhead. On the other hand, methods relying on obfuscation like differential privacy lack adaptability to heterogeneous network environments, usually resulting in significant accuracy losses.
\subsection{Reliability of model aggregation (integrity)}%model安全
To resist the stealthy yet destructive poisoning attacks \cite{lyu2023poisoning}, multiple defense methods are proposed, which can be divided into the following types based on the realization concepts:
\subsubsection{Mitigation-oriented technologies} 
To ensure the integrity of the aggregated model, various robust FL methods, such as Byzantine-robustness, have been proposed. For instance, Krum \cite{blanchard2017machine-krum} selects partial neighboring nodes as references, enabling the algorithm to choose updates with the highest consensus for the next iteration. Diverging from Krum's approach of selecting only one update, FABA \cite{xia2019faba} employs gradient outlier computation to discard few gradients while retaining the majority of clients' training results, significantly enhancing learning speed. Building upon these methods, Gong \textit{et al.} devise AGRamplifier \cite{gong2023agramplifier}, which enhances the "morality" of local updates by identifying the most suppressive features in each gradient update. This augmentation further elevates model robustness, fidelity, and efficiency.

\subsubsection{Detection-oriented technologies} 
An alternative approach to fortify against poisoning is the direct detection of the learning model using a validation dataset or predefined rules. For instance, Zeno \cite{xie2019zeno} evaluates the stochastic descendant score for each gradient based on a validation dataset, selectively discarding gradients with low scores for the stochastic descendant. In contrast to relying on an auxiliary validation set, Baffle \cite{andreina2021baffle} capitalizes on the diverse datasets accessible across various clients by integrating a feedback loop into the FL process. Besides, Fldetector \cite{zhang2022fldetector} anticipates a client's model update during each iteration by leveraging historical model updates and flags a client as potentially malicious if the received model update contradicts the predicted update. 
It is noteworthy that detection-centric solutions entail additional training costs and may not identify some zero-day attacks.

\subsubsection{Credit-oriented technologies} 
%鉴于联邦学习是协作式、多轮次的交互过程，通过维护信用评价机制同样可以很好地清除恶意用户。例如，Kang等人使用多权重主观逻辑模型设计基于声誉的可靠联邦学习用户选择方案，并利用区块链实现声誉管理。在不需要辅助验证数据集的情况下，Xu等人提出余弦梯度Shapley值来评估每个智能体上传的模型参数更新/梯度的期望边际贡献，以区别对待。Tan等人提出了一种基于声誉感知的随机整数规划的FL客户选择方法，可以最优地选择和补偿具有不同声誉档案的客户，从而对抗潜在的异常行为。
Considering that FL is a collaborative and iterative process, the credit evaluation mechanism proves effective in poisoning resistance. For instance, Kang \textit{et al.} \cite{credit1-kang2019IOT} design a reputation-based reliable scheme utilizing a multi-weight subjective logic model, and implement reputation management through blockchain. Xu \textit{et al.} \cite{xu2020reputation, xu2021gradient}, without the need for auxiliary verification datasets, introduced the cosine gradient Shapley value to assess the model parameter updates/gradients uploaded by each client. Tan \textit{et al.} \cite{tan2022reputation} propose a reputation-aware stochastic integer programming client selection method, selecting and compensating clients with varying reputation profiles to counter potential anomalous behavior.

%总结：现有方案缺乏对隐私的考量，计算量过大
In general, existing solutions often struggle to achieve a satisfactory balance between privacy and defensive performance, while also lacking adaptability to heterogeneous and dynamically changing environments. Furthermore, some methods exhibit relatively large computational overhead, imposing a non-negligible burden on UAV nodes.

\section{System model} %\& Preliminaries}
%%symbols 表格
\begin{table}[!t]
{
\renewcommand{\arraystretch}{1.2}
\caption{Summary of Main Notation}
\label{notations}
\vspace{0em}
\centering
\begin{tabular}{| c || l |}
\hline
\textbf{Symbol} & \multicolumn{1}{c |}{\textbf{Description}}\\
    \hline
    $U_i,\mathcal{D}_i$ & The $i$-th UAV devices and its dataset\\
    \hline
    $n^{s_{m}, i},\mathcal{P}^i$ & The size and normalized distribution of $\mathcal{D}_i$\\
    \hline
    $\mathcal{P}^{Tar}, w$ & Target distribution and model of learning task $Job$\\
    \hline
    $T$ & The maximum communication rounds of $Job$\\
    \hline
    $C,K$ & The set and number of all peer communities\\
    \hline
    $S,M$ & The set and number of all colleague communities\\
    \hline
    %$L$ & The number of clients in each super node\\
    %\hline
    $c_k$ & The $k$-th peer community\\
    \hline
    $s_m$ & The $m$-th colleague community\\ 
    \hline
    $\Delta \widetilde{\omega}_{t}^{s_{m},i}$ & The weight updates from $U_i \in s_m$ in round $t$\\
    \hline
    $p^{s_{m}, i}$ & The aggregation coefficient for $U_i$ within $s_m$\\
    \hline
    $\Delta\widetilde{\omega}_{t}^{s_{m}}$ & The weight updates from $s_m$ in round $t$\\
    \hline
    $p^{s_{m}}$ & The aggregation coefficient for $\Delta\widetilde{\omega}_{t}^{s_{m}}$ from $s_m$\\
    \hline
    $E_k$ & The clipping bound of peer community $c_k$\\
    \hline
    $Sen_k$ & The maximum sensitivity of $c_k$\\
    \hline
    $\varepsilon_k,\delta_k$& The parameters of differential privacy \\
    \hline
    $L$& The minimum size of colleague community\\
    \hline
    $\alpha^{a,b}_{t}$& The cosine similarity between $a$ and $b$\\
    \hline
    $PI^{c_k \rightarrow i}_{t}$ & The positive interaction between $c_k$ and $U_i$\\
    \hline
    $NI^{c_k \rightarrow i}_{t}$& The positive interaction between $c_k$ and $U_i$\\
    \hline
    $\Upsilon^{c_k \rightarrow i}_{t}$& The peer reputation opinion vector of $c_k$\\
    \hline
    $\Phi^{c_k \rightarrow i}_{t}$& $c_k$'s credit evaluation towards $U_i$ in round $t$\\
    \hline
    $\Upsilon^{s_m}_{t}$ & The colleague reputation opinion vector towards $s_m$\\
    \hline
    $\Phi^{s_m \rightarrow i}_{t}$& The colleague credit evaluation for $\forall U_i \in s_m$\\
    \hline
    $\Upsilon^{i}_{t},\Phi^{i}_{t}$& The comprehensive reputation and credit of $U_i$\\
    \hline
    $\psi^{i}_t$& The fairness-guaranteed selection probability\\
    \hline
    \end{tabular}
        }
     \vspace{-1.5em}
     \end{table}

\textbf{Heterogeneous UAV network scenario.} 
%\subsection{Network scenario}
%对于一个多无人机多任务联邦学习场景，有一个服务器与N个无人机，设无人机集合为$U=\{U_i\}$，$\vert\vert U\vert\vert=N$。所有无人机获取的数据集集合为$D=\{D_i\}$，第k个无人机的数据分布为$\mathcal{P}^k\in \mathbb{t}^F$，其中$F$为特征维度；任务场景集合为$T$，其中第k个任务场景中的数据分布为$\mathcal{P}^{tar_k}$。在同一现实场景中，无人机采集到的数据通常是类似的，即对于某个场景的分布$\phi$，所有属于该现实场景的设备集合$B'$均满足$\exists \epsilon\in \mathbb{t}^F,\forall k \in B', ||\phi-\mathcal{P}^k||_1 \leq \epsilon$。
As shown in Figure \ref{fig1:UAV-Network}, assume a multi-UAV multi-task federated learning scenario for the classification problems. There exists a parameter server (PS)/aggregator (normally equipped with ground base station) and $N$ UAV nodes (UN) $\mathbf{U}\triangleq\{U_1,...U_i,...U_N\}$. Each UN $U_i$ has local dataset $\mathcal{D}_i\triangleq\{(\xi_{i,1},y_{i,1}),...(\xi_{i,j},y_{i,j}),...(\xi_{i,n_i},y_{i,n_i})|y\in \mathbb{R}^F\}$ sampled following distribution $\varphi_q$. %with varied size $n_i$. 
Here $x$ and $y$ are raw data and label, respectively. As the nodes with overlapped aerial areas or patrol routines may have similar data distributions, we have $\exists \epsilon\in \mathbb{R}^F,\forall U_i, U_j \sim \phi_q, ||\mathcal{P}^i-\mathcal{P}^j||_p \leq \epsilon^{\prime}$, where $\mathcal{P}^i$ is the normalized distribution of $\mathcal{D}_i$. For the highly heterogeneous networks, we also have $\exists U_i \sim \phi_{q^{\prime}}, U_j \sim \phi_q,||\mathcal{P}^i-\mathcal{P}^j||_p \gg \epsilon^{\prime}$ in the same time.

%\subsection{Threat model}
%值得一提的是，方便起见，我们此处仅以多分类问题中的数据类别作为公平性感知针对的对象，实际使用中可以通过特征extractor扩展到数据包含的任意抽象特征。此外，我们以范数差异度作为公平性衡量标准，实际应用中，也可以选取AIDD、DSF、SF等衡量方式并在特定方面取得更好的效果。
It is crucial to highlight that, for better understanding, our focus in this paper is solely on the data distribution of multi-classification problems as the target for fairness awareness. In practical scenarios, this concept can be easily extended to any abstract features derived from specific demographic groups through feature extractor as exemplified in \cite{shuai2022balancefl}. Furthermore, our chosen metric for fairness evaluation is the norm difference. However, other alternative fairness measures such as QCID \cite{yang2021federated}, ratio loss \cite{wang2021addressing}, and cross-entropy loss \cite{mohri2019agnostic} can be employed, depending on specific requirements, to attain more favorable results.

\textbf{Fairness-aware learning task.} Without loss of generality, the fairness-aware learning task can be denoted with the quadruple as $Job\triangleq(w,\mathcal{P}^{tar},t_0, T)$, which consists of the model $w$, target distribution $\mathcal{P}^{tar}$, arrival time $t_0$, and duration $T$. Different from existing solutions designed for certain $\mathcal{P}^{tar}$ \cite{li2022data,zeng2022heterogeneous,hiessl2022cohort}, our method can adaptively choose and schedule suitable UAV groups when a new learning task arrives.

\textbf{Optimization objective.} We start with vanilla FL algorithms like FedAvg \cite{li2019convergence-fedavg} without consideration of heterogeneity. The optimization objective can be expressed as: 
%考虑一个联邦学习场景，有1个服务器和$N$个客户。具体来说，客户i的本地数据集为$D_{i}$，其类别分布被定义为$\mathcal{P}^{c_{k},i}$。不同客户的本地数据类别分布高度异构，与全局类别分布$\mathcal{P}^{real}$有巨大差距。为了最小化全局损失函数，得到普适的全局模型，我们有：
\begin{equation}
    w^{*}\triangleq \underset{w}{\arg \min } \sum_{i=1}^N p_i\mathcal{L}\left(w, \mathcal{D}_{i}\right) ,
\end{equation}
%其中，$\mathcal{L}_{i}(\cdot)$是客户i的由其本地经验风险得出的本地损失函数。然而，由于客户的数据间的高度异构性与客户数据分布与任务场景数据分布间的高度异构性，客户间的本地损失函数不尽相同，难以获得同时最小化各个模型经验风险的最优全局模型参数$w^{*}$并满足任务场景。因此，在上述场景中进行传统FL会导致全局模型无法正常收敛，无法得到满足任务场景的高性能全局模型。
where $\mathcal{L}(.)$ represents the loss function derived from the local empirical risk of $U_i$, $p_i$ is the aggregation weight. Due to the high heterogeneity among UAV nodes and the substantial mismatch between participants' data distributions and task requirements, obtaining the globally optimal model parameters $\omega^{*}$ that simultaneously minimize the empirical risks of each model and align with task requirements is challenging. %Thus, traditional Federated Learning (FL) in such scenarios leads to the global model failing to converge effectively, resulting in an inability to obtain a high-performance global model that satisfies task scenarios.

Hence, similar to the existing fair FL solutions in \cite{mohri2019agnostic,zhang2020fairfl,ezzeldin2023fairfed}, we define the optimization objective as follows:
\begin{equation}
    w^{*}\triangleq \underset{w}{\arg \min } \ \mathcal{L}_{FFL}(\omega)=\underset{(x, y) \sim \mathcal{P}^{Tar}}{\mathbb{E}}[\mathcal{L}{(\omega,(x, y))}]
\end{equation}
%（我这里想的是为了便于之后的凝聚聚类）此外，由于不同现实场景之间可能有较大的数据分布差异，与任务数据分布高度异构。为了最小化全局损失函数，得到适用于特定任务场景的全局模型，我们有：

\section{Stratified community construction in heterogeneous environment}\label{sec:community}
%为了实现高度异构的UAV节点集合与动态变化的学习任务之间的良好适配，我们提出了SCC。如图所示，该机制主要包含两个部分：PCC和CCC。其中PCC在网络初始化时运行一次，CCC则在每次收到新任务时运行一次。
To achieve a robust alignment between highly heterogeneous UAV nodes and dynamically evolving learning tasks, we propose the stratified community construction (SCC) mechanism. As illustrated in Figure \ref{fig2:framework}, SCC comprises two main components: peer community construction (PCC) and colleague community construction (CCC). PCC executes once during network initialization, while the CCC executes each time a new task is received.
\subsection{Peer community construction (PCC)}
Based on norm-based pair distance, we first cluster UAV nodes with similar data distributions into $K$ peer community $C=\{ c_{1}, \ldots, c_{K} \}$. The pair distance is calculated as:
\begin{equation}
d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}, \forall U_i,U_j\in \mathbf{U}.
\end{equation}

%基于客户的数据分布$\mathcal{P}^{i},i\in B$。我们用最大链接法对客户进行层次凝聚聚类。两个簇间的距离为它们中任意两个客户分布之间曼哈顿距离的最大值，当簇间距离大于合并阈值$\zeta$时停止合并，得到最终的聚类结果。由此可知同簇的任意客户分布之间的最大曼哈顿距离小于$\zeta$, 即$\forall i,j \in c, d_{i,j}<\zeta$。
Then, we employ the complete-linkage method to achieve agglomerative hierarchical clustering (AHC) among UAV nodes. The distance between two peer communities is defined as the maximum Euclidean distance between any two UNs' distributions. The clustering process ceases when the inter-community distance exceeds the merging threshold $\zeta$, resulting in the final outcome. Hence, the maximum distance between any pair of client distributions within the same PC is less than $\zeta$, i.e., $\forall U_i, U_j \in c_k, d_{i,j} < \zeta$, which is denoted as:
\begin{equation}\label{eq:peer-construct}
 C\triangleq \underset{c_{1} \cup c_{2} \cup \ldots c_{K}=C}{\arg \min} \left(\max _{\forall c_{k},c_{k'} \in C ,U_i \in c_{k}, U_j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .
\end{equation}

%根据上述公式，我们得到具有相似类别分布的$K$个簇$C=\{c_{1},\ldots,c_{K}\}$。可以计算每个簇的平均数据分布，簇$c$的平均数据分布$\mathcal{P}^{c}$计算为：
The average distribution of each peer community $c_k$ is:
\begin{equation}
    	 \mathcal{P}^{c_k}=\operatorname{norm}\left(\sum_{i \in c} n^{c,i} \mathcal{P}^{c,i} \right),
\end{equation}
%其中，$\mathcal{P}^{c,i}$是簇$c$中客户$i$的数据分布，$n^{c,i}$是簇$c$中客户$i$的数据量。为了保证隐私与数据安全，需要保证簇的个数，否则参与方将可能更容易推断出数据属于哪一簇。同时，当簇的数量较少时，每个簇代表的数据子集更大，这可能会导致更多的敏感信息聚集在同一簇中。如果某个恶意参与方能够成功识别并攻击一个簇，他们可能能够访问或推断出更多敏感信息，增加了数据泄露的风险。因此，需要添加约束：$K \geq \eta$，以确保隐私性。
where $\mathcal{P}^{k,i}$ represents the data distribution of $U_i$ within cluster $c_k$, and $n^{k,i}$ denotes the size of $\mathcal{D}_i$. 
To jointly ensure performance and security, it is imperative to control the number of peer communities. A large $K$ enhances the chance of attackers inferring the sensitive information. Conversely, a small $K$ may result in insufficient intra-community similarity, leading to a deterioration in learning performance. Therefore, the introduction of a constraint, $K \geq \kappa$, is essential. This constraint ensures a minimum size of peer community for privacy considerations. $\kappa$ can be adjusted by $\zeta$.

\subsection{Colleague community construction (CCC)}
After peer community construction, we further select suitable UAV nodes to form colleague communities $S\triangleq\{s_1, \ldots, s_{M}\}$ with desirable distribution $\mathcal{P}^{tar}$, which avoids the performance degradation caused by heterogeneity.

\subsubsection{Problem formulation}
As shown in Figure \ref{fig2:framework}, based on the requirements of task $job_i$, we first generate the ``\textit{template}'' $\mathbf{h}$ of the colleague community (i.e., required ratio of clients $h_k$ from each peer community $c_k$ in a colleague community $s_{m}$). $\mathbf{h}\triangleq\{h_{1}, \ldots, h_{K}\}$ is a vector to stipulate this composition. Then $M$ colleague communities are constructed accordingly by selecting UAV nodes from each $c_k$. Outlier $c_k$ with small sizes ($\vert\vert c_k\vert\vert< M$) are excluded to improve participation.

The optimization problem can be defined as:
\begin{equation}\label{eq:problem}
\begin{aligned}
\mathbf{h}^*\triangleq &\underset{\mathbf{h}}{\arg \min} \vert\vert \mathbf{h}\cdot\mathbf{P}-\mathcal{P}^{tar}\vert\vert_2 \\
\text{s.t. }& \forall c_k \in C, h_k\leq b_k, \\
&\sum_{i=1} ^K h_i\geq r,
\end{aligned}
\end{equation}
where $\mathbf{P}$ is a $K \times F$ matrix to denote the average feature values for all peer communities. Every row $\mathcal{P}^{c_k}\in \mathbb{R}^F$ denotes the average feature values of one peer community. $\mathbf{B}\triangleq \{ B_{1}, \ldots, B_{K}\}$ denotes the size of all peer communities.

\subsubsection{Problem transformation} As the above problem is an NP-C quadratic integer optimization problem \cite{murty1985some}, we want to further reduce it to a linear programming problem to meet the efficiency requirements of UAVs. 
%即将$\mathcal{P}^{c_k}$拆成$l_k=\lceil \log_2(b_k+1) \rceil$行，拆成的新行中，第$i,1\leq i <l_k$行$d_i=2^{i-1}\mathcal{P}^{c_k},e_{k,i}=2^{i-1}$，第$l_k$行为$(b_k-2^i+1)\mathcal{P}^{c_k},e_{k,l_k}=(b_k-2^i+1)$。新矩阵有$R=\sum_{i=1}^k l_i$行，将原$\mathcal{P}$矩阵二进制拆分为一个$R\cdot F$的矩阵$\mathcal{Q}$，将整数规划问题转化成了一个0-1规划问题。
For each $c_k$, to remove the constraint $B_k$, we conduct binary split on $\mathcal{P}^{c_k}$ to get $l_k=\lceil \log_2(B_k+1) \rceil$ new rows. Hence, the new matrix has $R=\sum_{i=1}^k l_i$ rows. The problem becomes:

\begin{equation}
\begin{aligned}
\mathbf{x}^*\triangleq &\underset{\mathbf{x}}{\arg \min} \vert\vert \mathbf{x}\mathcal{Q}-\mathcal{P}^{tar}\vert\vert_2 \\
\text{s.t. } &\forall c_k \in C, x_i\in\{0,1\}, \\
&\sum_{i=1} ^K h_i\geq r,
\end{aligned}
\end{equation} 
where $\mathbf{x}$ can map to $\mathbf{h}$, i.e., $h_k = \sum _{i=1} ^{l_k} e_{k,i}x_{\sum_{j=1}^{k-1} l_j +i}$, and $e_{k,l_k}=(B_k-2^i+1)$. Hence, the above problem is equal to finding the minimum of $(\mathbf{x}\mathcal{Q}-\mathcal{P}^{tar})\cdot (\mathbf{x}\mathcal{Q}-\mathcal{P}^{tar})^T$ as:

\begin{equation}
\begin{aligned}
\mathbf{x}^*\triangleq\underset{\mathbf{x}}{\arg \min}\ \mathbf{x}\mathcal{Q} &\mathcal{Q}^T\mathbf{x}^T-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+\mathcal{P}^{tar}\mathcal{P}^{tar^T}\\
\text{s.t. }&\mathbf{x}\in\{0,1\}^R,\\
&\sum_{i=1} ^K h_i\geq r.
\end{aligned}
\end{equation}

We further introduce variable $z_{ij} \in \{0,1\}$ and have $z_{ij}\leq x_i$,$z_{ij}\leq x_j$,$z_{ij}\geq x_i+x_j-1$, to linearize the problem:

\begin{equation}%\label{eq:problem}
\begin{aligned}
\min\ &\mathcal{Q}\mathcal{Q}^T\mathbf{y}-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+P^{tar}P^{tar^T}\\
\text{s.t. }& \mathbf{x}\in\{0,1\}^R,
\\
&x_{ij}\leq x_i, x_{ij}\leq x_j, x_{ij}\geq x_i+x_j-1,
\\&\sum_{i=1} ^K h_i\geq r.
\end{aligned}
\end{equation}

Thus, the problem can be efficiently solved by linear programming solvers\footnote{For example, https://coin-or.github.io/pulp/}.

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{figures/fig2.PNG}
\caption{Stratified community construction in a heterogeneous environment.}
\label{fig2:framework}
\end{figure}

\section{Adaptive FFL training with privacy amplification}
\subsection{Training workflow of MR-FFL}
% 初始化过程: task generation & community initiation
% Step 1: Local training
% Step 2: Noise obfuscation
% 中间过程: Upload gradient
% Step 3: Inner-community aggregation
% Step 4: Global aggregation
% Step 5: Personalisation
% 中间过程: Download model
% Step 6: Local update

As shown in Figure \ref{fig3:workflow}, the training workflow of MR-FFL mainly consists of the following steps in one round of iteration:

\begin{itemize}
    \item \textbf{Initialization:} Once the FFL task arrives, server conducts the CCC algorithm to quickly select $M$ colleague communities with similar average distributions near to $\mathcal{P}^{tar}$.
    \item \textbf{Step 1:} First, each node $U_i \in s_m$ trains the current model with personal data to generate the local model $\omega_t^{s_m, i}$.
    \item \textbf{Step 2:} Then, $U_i$ obfuscates the weights update $\widetilde{\omega}_{t}^{s_{m}, i}$ with differential private noise, and uploads it to the server.
    \item \textbf{Step 3:} Colleague community aggregates $\widetilde{\omega}_{t}^{s_{m}, i}, \forall U_i \in s_m$ to generate a colleague model $\omega_{t}^{s_{m}}$.
    \item \textbf{Step 4:} The server aggregates result $\omega^{s_k}$ from each colleague community $s_k \in S$ to get new global model.
    \item \textbf{Step 5:} Besides, UAV peer community can maintain a personalized peer model $\omega_{t}^{c_{k}}$ to further improve local performance. 
    \item \textbf{Step 6:} Finally, the global model is distributed to selected UAV nodes for the next round of training.
\end{itemize}

As Step 1, 2, and 6 aligns with existing secure FL training process \cite{wei2020federated-NbAFL,padala2021federated}, we focus on Step 3,4 and 5 subsequently.

\subsubsection{Colleague community aggregation} 
%为了尽可能地减小异构数据带来的模型方向的差异，以便更好地聚合普适的全局模型，在服务器聚合前，先在super node 内部聚合。也就是说，本地训练后，客户$i, i\in s_{m}$的加噪模型更新量$\Delta \widetilde{\omega}_{t}^{s_{m},i}$被上传到super node进行super node的内部同步。
To reduce the canceling phenomenon caused by heterogeneous data and improve training efficiency,  we first aggregate all $\Delta \widetilde{\omega}_{t}^{s_{m}, i}$ within $s_m$ to generate more homogeneous weight updates $\Delta\widetilde{\omega}_{t}^{s_{m}}$ of colleague model $s_m$ before the global aggregation: %In other words, following local training, the perturbed model update quantity, denoted as $\Delta \widetilde{\omega}{t}^{s{m},i}$ for client $i$ where $i\in s_{m}$, is uploaded to the super node for internal synchronization before server-level aggregation.
\begin{equation}
    \begin{gathered}
     \Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}
     = \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i},
     \end{gathered}
\end{equation}
where $p^{s_{m}, i}= {n^{s_{m}, i}}/{n^{s_{m}}}$ is aggregation coefficent, $n^{s_{m}}=\sum_{i \in s_{m}} n^{s_{m}, i}$.

\subsubsection{Global aggregation} 
Then, the server aggregates the learning results from all $s_m$ and updates the global model:
\begin{equation}
\widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}},
\end{equation}
where $p^{s_{m}}= \frac{n^{s_m}}{\sum_{s_{m} \in S} n^{s_m}}$, and $\widetilde{\omega}_{t}$ is the global model. The global aggregation iteratively executes $T$ rounds to complete the learning task $Job=(w,\mathcal{P}^{tar},t_0, T)$\footnote{The termination condition for the learning task can also be set based on accuracy $\epsilon^{\prime\prime}>0$ rather than a fixed number of rounds $T$, i.e., $\mathcal{L}_{FFL}(\omega_t)\leq \epsilon^{\prime\prime}$, by only modifying the quadruple to $(w,\mathcal{P}^{tar},t_0, \epsilon^{\prime\prime})$.}.

\subsubsection{Peer community personalization} Finally, to further improve the performance on local datasets, we personalize the local model for peer community by adding the proximal term:
\begin{equation}\label{eq:personal}
\omega_{t}^{k} = \omega_{t-1}^{k} - \eta\left(\sum_{i=1}^{\vert\vert c_{k}\vert\vert}p^{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega_{t-1} \right)\right)
\end{equation}
    where $p^{c_k}= \frac{n^{s_m}}{\sum_{c_k \in C} \vert\vert c_k\vert\vert}$, $\eta$ is the learning rate, $\lambda$ is the regularization coefficient. The smaller $\lambda$, the more the local models $\omega_t^{k}$ can deviate from the (corrupted) global model $\omega_t$, achieving robustness at the expense of generalization \cite{li2021ditto}.

In Algorithm \ref{algorithm1}, we present the pseudocode for the complete adaptive training process described above. It is evident from the algorithm that our approach only requires participants to provide distribution information, enabling significant improvements in efficiency, accuracy, and privacy in heterogeneous environments. Furthermore, our training method seamlessly integrates with the subsequently proposed credit evaluation mechanism. In cases where some attackers dishonestly report their information, the integrity of the model is still guaranteed.

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{figures/fig3.PNG}
\caption{The workflow of MR-FFL.}
\label{fig3:workflow}
\end{figure}

\subsection{Analysis of privacy amplification}

Different from existing central differential privacy (CDP) or local differential privacy (LDP) methods, which inevitably introduce excessive large noise and thus deteriorate the learning performance in heterogeneous environments, inspired by \cite{liu2022privacy}, we propose a novel DP notion: \textit{community-specific differential privacy} (CSDP) for heterogeneous federated learning. The anonymity is achieved within a peer community instead of the whole UAV network, which significantly reduces privacy loss under the same DP guarantee. Each peer community can be assigned with different $\varepsilon_k$ and $\delta_k$ based on personal needs.

\subsubsection{Noise calculation} We first calculate the noise scale needed for the MR-FFL workflow to achieve our $(\varepsilon_k,\delta_k)$-CSDP. Assume a pair of neighbor datasets $\mathcal{D}^{s_{m}, i}_{t}$ and $\mathcal{D}^{s_{m}, i'}_{t}$ sampled from same $s_m$ with size $n^{s_{m}, i}$, there is only one pair of nonidentical samples $\xi^{i}_{t}$ and $\xi^{i\prime}_{t}$ within the neighbor datasets. The $l_2$ norm-based sensitivity can be calculated as:

\begin{equation}
     \begin{aligned}
    \Delta F&=\max _{\xi^{i}_{t},\xi^{i\prime}_{t}}\left\|F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i}_{t}\right) -F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i'}_{t}\right)\right\|\\
    &\leq \frac{n^{s_{m},i}}{n^{s_{m}} M}\left(  \max \left\| \Delta\omega_{r,t}^{s_{m},i}\right\|   + \max  \left\| \Delta\omega_{r,t}^{s_{m},i}\right\| \right)
     \end{aligned}
\end{equation}

The second inequality can be deduced through a similar analysis as in \cite{wei2020federated-NbAFL}. We omit the specific process for simplicity. 
After DP weights clipping \cite{abadi2016deep}, assuming an equal volume of data for clients and a minimum node count $L$ ($L\geq r$) within the colleague community, we have the best sensitivity as:
\begin{equation}
    Sen_k=\max _{i \in c_{k}}\left\{\Delta f\right\} \leq \frac{2 E_{k}}{L M},
    \end{equation}
 where $E_k$ is the clipping bound of $c_k$.
The standard deviation of the Gaussian noise to achieve $(\varepsilon_k,\delta_k)$-CSDP is:
\begin{equation}
    \sigma_{k}=\frac{\ell_{k} Sen_k }{\varepsilon_{k}}=\frac{2 \ell_{k} E_{k}}{L M\varepsilon_{k}},
    \end{equation}
where constant $\ell_{k} =\sqrt{2 \ln (1.25 / \delta_{k})}$ \cite{dwork2014algorithmic}.

\subsubsection{Privacy analysis}

%我们假设客户的类别分布$\mathcal{P}^{c_{k}}$符合高斯分布$\varphi_{c_{k}} $，即客户类别以方差$\sigma_{c_{k}}^{2}$正态分布在簇心$\mu_{c_{k}}$周围，即簇$c_{k}$的类别分布可以用$\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$的高斯分布表示。
We assume that the data distribution of the UAV clients, denoted as $\mathcal{P}^{c_{k}}$, follows a Gaussian distribution $\varphi_{c_{k}}$, where the data are normally distributed around the community center $\mu_{c_{k}}$ with a variance of $\sigma_{c_{k}}^{2}$. In other words, the data distribution of community $c_{k}$ can be represented by a distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$ \cite{wei2020federated-NbAFL}. 
%对于某一簇$c_{i}$,整体类别分布符合高斯分布$\varphi_{c_{i}} \sim \mathcal{N}\left(\mu_{c_{i}}, \sigma_{c_i}^{2}\right)$，从中随机抽取任意客户$\forall i,i'\in c_{i}$，客户类别分布也符合$\varphi_{c_{i}}$。
For a specific peer community $c_{k}$, the overall data distribution follows distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_i}^{2}\right)$. Hence, selecting any UAV client $\forall i,i'\in c_{k}$ from it, the client's distribution also follows $\varphi_{c_{k}}$ \cite{wei2021low}.

%由公式（9）可知，在本地训练中，客户最小化本地经验风险得到的梯度与客户的本地数据有关，且客户梯度间的最大距离与数据分布的分散程度正相关，可以得到簇$c_{i}$客户梯度间的最大距离：
As indicated by \cite{sattler2020clustered-CFL}, it is evident that in local training, the gradient obtained by a client, which minimizes the local empirical risk, is related to the client's local data. The maximum distance between client gradients is positively correlated with the dispersion of the distribution. Consequently, the maximum distance between gradients of nodes within peer community $c_{k}$ can be derived as $\max_{i,i'\in c_{k}} \left\| \Delta\omega_{t}^{c_{k},i}-\Delta\omega_{t}^{c_{k},i'}\right\| \simeq \sigma_{c_k}$.

%super node按照数量$n=[n_{1},\ldots,n_{k},\ldots,n_{K}],  n_{k} \in \mathbb{N}$从簇$\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中选择$L$个客户:$\sum^{K}_{k=1} n_{k}=L$。通过卷积求和上述簇分布，可以得到super node 的类别分布$\varphi_{s}$：
We choose UAV nodes from each peer communities $c_{k},\forall c_k \in C$ to constitute colleague communities according to composition vector $\textbf{h}=[h_{1},\ldots,h_{k},\ldots,h_{K}],  h_{k} \in \mathbb{N}$. Hence, by convolution summation among those peer distributions, we can obtain the distribution of colleague communities $\varphi_{s}$ as:

\begin{equation}    \varphi_{s}=h_{1}\varphi_{c_{1}}\oplus\ldots\oplus h_{k}\varphi_{c_{k}}\oplus\ldots\oplus h_{K}\varphi_{c_{K}}
\end{equation}

%因为簇分布$\varphi_{c_{k}} \forall c_{k} \in C$是相互独立的高斯分布，可以得到上述簇分布的卷积和。
As $\varphi_{c_{k}}, \forall c_{k} \in C$ are i.i.d. Gaussian distributions, we have $\varphi_{s} \sim \mathcal{N}\left(\mu_{s}, \sigma_{s}^{2}\right)$, where $\mu_{s}=\sum_{k}^{K} h_{k} \mu_{c_{k}}$, $\sigma_{s}^{2}=\sum_{k}^{K} h_{k}^{2} \sigma_{c_k}^{2}$. 
Define the maximum distance between weight updates of two UAV nodes $U_i$ and $U_{i^{\prime}}$ from the same colleague community $s$ as $\max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\| \simeq \sigma_{s}$. As $\sigma_{s}=\sqrt{\sum_{k}^{K} h_{k}^{2} \sigma_{c_k}^{2}}$, easy to prove $\sigma_{s}\geq\sigma_{c_{k}}, \forall c_k \in C$.
Then, we have:
\begin{equation}
    \max_{i,i'\in c_{i}} \left\| \Delta\omega_{t}^{c_{i},i}-\Delta\omega_{t}^{c_{i},i'}\right\|\leq \max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\|.
\end{equation}

%根据敏感度的定义，可知在super node 中计算supernode内的敏感度将远大于簇内的敏感度。
According to the definition of sensitivity, our peer community-specific $Sen_k$ and noise scale is much smaller than existing global-wide or colleague-wide DP methods. Hence, to achieve the same FFL performance, the clipping bound of our method is also much smaller, which requires less obfuscation.

\begin{comment}

\subsection{Analysis of personalization}
在$K$个簇$C=\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中，每个簇$c_{k}$有相同的客户数$n$。$X^k \triangleq\left\{\omega^{k, i} \in\right.\mathbb{t}\}_{i \in[n]}$，且客户模型以方差$\upsilon^{2}$正态分布在簇心$\omega^{k}$周围，即$\omega^{k, i}=\omega^{k}+z^{k, i}$,其中$z^{k, i} \sim \mathcal{N}\left(0, \upsilon^{2}\right)$。具体来说，为了量化簇的异质性，我们假设簇心$\{\omega^{k}\}_{k \in \left[K\right]}$也以方差$\tau^{2}$正态分布在未知的固定元中心$\theta$周围,即$\omega^{k}=\theta+z^{k}$,其中$z^{k} \sim \mathcal{N}\left(0, \tau^{2}\right)$。其中，$\tau$表示簇心间的分散程度，$\tau$越大，簇越分散，整体分布的异构性越高。在此基础上，簇$c_{k}$为其中客户选择隐私预算$(\varepsilon_{k},\delta_{k})-DP$以最小化整体的泛化误差。每个簇$k$具有不同的裁剪边界$C_{k}$，并以$\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$的标准差在本地客户上传的模型加噪,在此基础上，簇$c_{k}$的优化目标可以表示为：
\begin{equation}
h_k(\omega)=\tilde{F}_k(\omega)+\frac{\lambda}{2}\|\omega-\omega^{g}\|_2^2
\end{equation}
其中，$\tilde{F}_k(\omega) \triangleq \frac{1}{2}\left(\omega-\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i} \cdot \min \left(1, C_{k} /\left\|\omega^{k, i}\right\|_2\right)\right)\right)^2$是簇$c_{k}$的优化目标，簇$c_{k}$客户梯度加噪大小为$\xi^k \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$。由于数据是亚高斯的，我们可以选择裁剪的边界$C_{k}$避免引入削波误差。因此，簇$c_{k}$的最优本地优化结果为$\widehat{\omega}^k \triangleq \operatorname{argmin} \tilde{F}_k(w)=\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i}\right)$。由于服务器聚合全部参与客户的模型而客户分布在各簇中，因此可得$\omega^{g}=\frac{1}{Kn} \sum_{k=1}^{K}\left(\xi^k+\sum_{i=1}^{n}\omega^{k,i}\right)=\frac{1}{K}\sum_{k=1}^{K}\widehat{\omega}^{k}$。由此可得簇$c_{k}$外各簇的平均估计结果$\widehat{\omega}^{\backslash k}=\frac{1}{K-1}\sum_{j \neq k}\widehat{\omega}^{j}$。
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{algorithm}[!t]% !t top !b bottom !h right here !p float pages
\caption{Adaptive training with privacy amplification}
\label{algorithm1}
	\begin{algorithmic} [1]
    \State \textit{\textbf{ Input: }Learning task $Job\triangleq(w^0,\mathcal{P}^{tar},t_0, T)$; Maximum
local training iterations $R$; all participant UAV nodes $\mathbf{U}$ and their local dataset $\mathcal{D}_i$.}
    \State \textit{\textbf{Output: }The global FFL model $\omega$ for task $Job$, personalized local models $\{ \omega^{k}\}_{k \in [K]}$} for peer communities.
            \State \textbf{Initialize:} $w^{0}_{i} \leftarrow\ w^{0}$%,$\mathcal{P}^{real}=\operatorname{norm}\left(\sum_{i \in B} N^{i} \mathcal{P}^{i} \right)$
            %\State {\color{CadetBlue}/* \textbf{Peer community construction */} } 
            %\State $d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}$
            %\State $C=\{ c_{1}, \ldots , c_{K} \} \leftarrow \arg \min _{c_{1} \cup c_{2} \cup \ldots c_{K}=C}\left(\max _{\forall c_{k},c_{k'} \in C ,i \in c_{k}, j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .$
            \State Construct $C=\{ c_{1}, \ldots , c_{K} \}$ with Eq. (\ref{eq:peer-construct});
             %\For { $r \in 1, \cdots, R$}
                %\State{\color{CadetBlue} /* \textbf{Initialization} */} %$S \leftarrow Select-Clients()$}
            \State Calculate composition vector $\mathbf{h}$ by Eq. (\ref{eq:problem}) for $Job$;
            \State Construct colleague communities as $S^t=\{s_{1}, \ldots , s_{M}\}$ according to template $\mathbf{h}$;
                \For {each colleague community $s_{m}$ in $S^{t}$ in parallel }
                    \For {each UAV node $U_i$ in $s_{m}$ in parallel}
                        \State {\color{CadetBlue}/*\textbf{Local Training*/}} 
                        %\State $\omega_{t}^{s_{m},i} \leftarrow \omega_{t-1}^{s_{m},i}-\frac{\eta}{NI^{s_{m},i}} \nabla_\omega \mathcal{L}_{s_{m},i}\left(\omega_{t-1}^{s_{m},i}, \mathcal{D}^{s_{m},i}_{t}\right)$
                        \State Update $\omega_{t}^{s_{m},i}$ with $\mathcal{D}_i$ for $R$ iterations;
                        \State $\Delta \omega_{t}^{s_{m},i}=\omega_{t-1}^{s_{m},i}-\omega_{t}^{s_{m},i}$;
                        \State{\color{CadetBlue}/* \textbf{Privacy obfuscation */}} 
                        %\State \textbf{DP:} client $i \in c_{k}$, guarantee ($\varepsilon_{k}$,$\delta_{k}$)-DP
                        \State Calculate noise $z^{k} \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$, $\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$;
                        \State $\Delta \widetilde{\omega}_{t}^{s_{m},i}=\Delta \omega_{t}^{s_{m},i}+z^{k}$;
                    \EndFor
                    \State{\color{CadetBlue}/* \textbf{Colleague community aggregation */}} 
                    \State $\widetilde{\omega}_{t}^{s_{m}} \leftarrow \widetilde{\omega}_{t-1}^{s_{m}} -  \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i}$;
                    \State $\Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}$;
                \EndFor
                \State {\color{CadetBlue}/* \textbf{Global aggregation */}}
                \State $\widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$;%$\widetilde{\omega}_{t} \leftarrow \widetilde{\omega}_{t-1} - PI^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$
                \State{\color{CadetBlue}/* \textbf{Peer community personalization */}}
                    \State Update the personalized model $\omega_{t}^{k}$ for each peer community $c_k$ with Eq. (\ref{eq:personal});%$\omega_{t}^{k} \leftarrow \omega_{t-1}^{k} - \eta_{c_{k}}\left(\sum_{i=1}^{n_{c_{k}}}p_{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega^{g}_{t-1} \right)\right)$
                    %\State Update $\omega_{t}^{k}$
            % \EndFor
\State \Return $w^g,\{w^k\}$
\end{algorithmic}
\end{algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Community-based credit evaluation of UAV nodes}
In this section, we design a community-based credit evaluation method with a modified three-valued subjective logic model (SLM) \cite{al2021subjective}, to eliminate malicious attackers hiding in heterogeneous UAV networks. By integrating credits from both similarity-dominated intra-community (peer) and performance-dominated inter-community (colleague), multiple poisoning paradigms can be efficiently thwarted. 
\subsection{Similarity-dominated peer credit evaluation}
%首先，同一community内的用户在训练过程中上传的weights往往相似性较高。因此，通过社区内相似度比较，可以快速识别出离群的恶意用户。
UAV nodes' weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ within the same peer community $c_k$ often exhibit a high degree of similarity during the training process. Therefore, by leveraging community-based similarity, one can promptly identify malicious nodes that deviate significantly from the average norm.

\subsubsection{Basic setting}
For $\forall U_i \in c_k$, we first calculate the cosine similarity $\alpha_{c,i}^{t} \in [-1,1]$ between weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ from $U_i$ and average weight updates $\Delta\widetilde{\omega}^{c_k}_{t}$ from its peer community $c_k$:
\begin{equation}
    	  \alpha^{c_k,i}_{t} = \alpha( \Delta\widetilde{\omega}^{c_k}_{t-1}, \Delta\widetilde{\omega}^{i}_{t}) = \frac{\langle \Delta\widetilde{\omega}^{c_k}_{t-1},\Delta\widetilde{\omega}^{i}_{t}\rangle}{\Vert \Delta\widetilde{\omega}^{c_k}_{t-1}\Vert\cdot\Vert \Delta\widetilde{\omega}^{i}_{t}\Vert },\forall c_k \cap S.
\end{equation}

We further define the positive interaction $p^{c \rightarrow i}_{t} \in [0,2]$ as:
\begin{equation}
    	 PI^{c_k \rightarrow i}_{t} = \alpha^{c_k,i}_{t} -(-1),
\end{equation}
and the negative interaction $n^{c_k \rightarrow i}_{t} \in [0,2]$ as:
\begin{equation}
    	 NI^{c_k \rightarrow i}_{t} = 1-\alpha^{c_k,j}_{t}.
\end{equation}

%在FL的过程中，客户与簇的交互作用影响客户的信誉评估。诚实的交互行为将为客户的信誉评估带来正向的影响，具有攻击性的或不诚实的交互则会降低客户的信誉评分。我们分别用系数$b$和$c$表示内客户间正负交互作用对信任评价的影响比例，其中，$b>0,c>0$ 且 $b+c=1$。为了惩罚恶意客户，我们为客户间的负面交互设置更大的权重,即$b>c$。
During the FFL process, benign behaviors positively impact the reputation assessment, while aggressive or deceptive interactions diminish the client's reputation. We use coefficients $b$ and $c$ to quantify the impact of positive/negative interactions in credit evaluation, respectively. $b>0$ and $c>0$, $b+c=1$. To penalize malicious UAV nodes, we assign a greater weight $b>c$ to negative interactions among clients. 
Hence, we obtain the temporary three-valued peer reputation opinion \cite{liu2019trust} vector $\Upsilon^{c_k \rightarrow i}_{t,temp}\triangleq \{b^{c_k \rightarrow i}_{t,temp}, d^{c_k \rightarrow i}_{t,temp}, u^{c_k \rightarrow i}_{t,temp}\}$ based on SLM as:
\begin{equation}
\Upsilon^{c_k \rightarrow i}_{t,temp}=
\left  \{
      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
        b^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{bPI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
        d^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{cNI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
        u^{c_k \rightarrow i}_{t,temp}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}},                
    \end{array}
\right.
\end{equation}
%$ \sigma_{c}$为簇c中满足$\varepsilon-DP$所加噪声的标准差，体现了根据客户上传加噪梯度计算可信度的不确定性，$ \sigma^{C}_{max}$和$\sigma^{C}_{min}$分别是所有簇$c\in C$中为满足$\varepsilon-DP$所添加的最大噪声和最小噪声。
where the standard deviation $ \sigma_{c_k}$ of peer community $c_k$ depicts the uncertainty in the credit calculation based on the noisy $\Delta\widetilde{\omega}^{c_k}_{t}$ to achieve DP guarantee. $ \sigma_{max}=\max_{c_k \in C}{\sigma_{c_k}}, \sigma_{min}=\min{c_k \in C}{\sigma_{c_k}}$. %Furthermore, $ \sigma^{C}{max}$ and $ \sigma^{C}{min}$ denote the maximum and minimum noise added, respectively, among all clusters $c\in C$ to satisfy $\varepsilon-DP$.
Besides, $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp}$ denote \textit{belief}, \textit{disbelief}, and \textit{uncertainty}, respectively. We have $b^{c_k \rightarrow i}_{t,temp}+d^{c_k \rightarrow i}_{t,temp}+u^{c_k \rightarrow i}_{t,temp}=1$ and $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp} \in [0,1]$.

Then $c_k$'s temporary credit evaluation towards UAV $U_i$ is:
\begin{equation}
\Phi^{c_k \rightarrow i}_{t}=b^{c_k \rightarrow i}_{t} + a u^{c_k \rightarrow i}_{t}, \forall c_k \cap S,
\end{equation}
%其中$a\in[0,1]$是信誉不确定影响程度的系数。基于上式，根据客户的信誉度可以更明显地区分出恶意客户，从而抑制客户间的负面交互。
where $a\in[0,1]$ is a coefficient regulating the importance of uncertainty. 
Based on the above equation, malicious clients can be distinctly distinguished via reputation scores, thereby mitigating negative interactions among clients.

\subsubsection{Long-term consideration}
%在r个同步轮次内，客户的信誉不总是一成不变的。由于客户的信誉随着时间的推移而变化，我们考虑客户间历史信誉的影响。定义信誉的时间衰减因子为：
During the iterative training, clients' reputations may not remain constant. Some sophisticated attackers even take advantage of this phenomenon and conduct more stealthy poisoning behaviors \cite{credit1-kang2019IOT}. Therefore, we take into account the influence of historical reputation. The time decay factor $v_{\tau}$ is defined as:
\begin{equation}
v_{\tau}=\frac{1}{e^{\iota(Y-\tau)}}=e^{-z(Y-\tau)},
\end{equation}
%其中$z>0$为冷却系数, $\tau \in [1,Y]$为历史交互时间的时隙,在内部通信中当前时隙$Y=r$。由于过于久远的信誉的时间衰减因子接近0，并且考虑到信誉交互中的内存与计算成本，我们只保留$\vert Y-\tau \vert \leq T$的历史信誉 ,即只记录并维护距离当前通信轮次的$T$轮历史信誉$\Phi^{c \rightarrow i}_{\tau}$。公式(7)表示，越接近当前同步轮次的信誉的时效性越高，即更相信近期交互的信誉度，而不是历史交互。
where $\iota>0$ is the cooling coefficient, $\tau \in [1,Y]$ represents the time slot of historical interaction, and $Y$ in the current time slot of internal communication. Since the time decay factor for too-old reputations approaches 0, and considering the memory and computational costs in reputation interactions, we set an expiration threshold and retain only $T$ historical reputations $\Phi^{c_ \rightarrow i}_{\tau}$, i.e., $\vert Y-\tau \vert \leq T$. %Formula (7) indicates that reputations closer to the current synchronization round are more timely, placing higher trust in recent interactions rather than historical ones.

\subsubsection{Stability consideration} 
%\item \textbf{更新：}在联合学习的迭代交互$r\in[1,R]$中，服务器选择参与本地训练的随机客户子集为$Set_{t}$,在第$r$轮迭代中，只有集合$Set_{t}$中的客户上传模型更新量并彼此交互评估信誉。然而，由于参与训练和客户数量远少于客户总数,即$\vert Set_{t}\vert \ll N$，当前轮次的评估结果不足以给出完整的评估结果。因此，我们使用每个客户端的最新信誉更新值来更新其当前信誉值。设$\left\{ \Phi^{c \rightarrow i}_{t} \right\}_{i}^N$表示在服务器上维护的每个客户的簇内直接信誉。在每一轮交互后，全部客户执行以下更新操作：
Moreover, as only chosen UAV nodes $U_i\in S$ participate in the FFL at round $t$, cross-slot reputation values can have erratic fluctuation or asynchronous obsolescence problems. Hence, inspired by \cite{jhunjhunwala2022fedvarp}, We introduce the momentum term to the reputation updating as: 
\begin{equation}
\Upsilon^{c_k \rightarrow i}_{t}=
\left\{\begin{array}{ll}
\Upsilon^{c_k \rightarrow i}_{t} ,& \text { if } U_i \in S\\
\Upsilon^{c_k \rightarrow i}_{t-1},& \text { otherwise }
\end{array}\right.
\end{equation}

%在训练开始前，初始化所有客户$\forall i \in [N]$的信誉评价$\Upsilon^{c \rightarrow i}_{0}$可以表示为：
%可以看出我们提供较高的初始信誉并保证非参与客户历史信誉的连续性。
Then, in the initialization phase $t=0$, we have:
\begin{equation}
\Upsilon^{c_k \rightarrow i}_{0}=
\left  \{
      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
        b^{c_k \rightarrow i}_{0}=1-u^{c_k \rightarrow i}_{0},\\
        d^{c_k \rightarrow i}_{0}=0,\\
        u^{c_k \rightarrow i}_{0}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}
      \end{array}
\right.
\forall U_i\in c_k.
\end{equation}

%上式确保了客户簇内直接信誉的实时性，即维护了包括参与和非参与交互客户在内的全部客户的当前信誉均为其最近的信誉更新值。
The above design ensures the stability of credit evaluation for both participating and non-participating UAV nodes in the current round.

By integrating both stability and long-term consideration, we obtain the final peer reputation opinion: 
\begin{equation}
\Upsilon^{c_k \rightarrow i}_{t}=
\left  \{
      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
        b^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} b^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
        d^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} d^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
        u^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} u^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}  ,              
    \end{array}
\right.
\forall U_i\in c_k,
\end{equation}
%第r轮同步，簇$c$中客户i的信誉评价为：
and $c_k$'s credit evaluation towards UAV node $U_i$ at round $t$:
\begin{equation}
\Phi^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} \Phi^{c \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}, \forall U_i\in c_k.             
\end{equation}

\subsection{Performance-dominated colleague credit evaluation}
Performance-dominated colleague credit evaluation generates the general judgment $\Phi^{s_m}_{t}, \forall s_m\in S$ from other colleague communities. 
As colleague communities are regrouped after every iteration, different from peer credit, colleague credit pays more attention to comprehensive consideration of both performance and similarity between $s_m$ and $s_{m^{\prime}}, \forall s_{m^{\prime}} \in S_{\neg s_m}$.

Hence, we first calculate the similarity between $s_m$ and $s_{m^{\prime}}$:
\begin{equation}
    	  \alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega}^{s_{m}}_{t},  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}) = \frac{\langle  \Delta\widetilde{\omega}^{s_{m}}_{t}, \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\rangle}{\Vert  \Delta\widetilde{\omega}^{s_{m}}_{t}\Vert\cdot\Vert  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\Vert }.
\end{equation}

The positive and negative interactions are $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$ and $NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$, respectively. $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} + NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 2$.

Thereafter, the \textit{belief} $b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u_t^{s_{m} \rightarrow s_{m^{\prime}}})\frac{bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$ 
\textit{disbelief} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u^{s_{m} \rightarrow s_{m^{\prime}}}_{t})\frac{cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$ and \textit{uncertainty} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=\Vert PI^{s_{m}}-PI^{s_{m^{\prime}}}\Vert/2.$$

For round $t$, the reputation opinion vector can be defined as follows:

\begin{equation}
\Upsilon^{s_m}_{t}=
\left  \{
      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
        b^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  b^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
        d^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  d^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
        u^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  u^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},                
    \end{array}
\right.
\end{equation}
where $\rho^{s_m}_{t}=acc^{s_m}_{t}$ is the accuracy of colleague community $s_m$. From the perspective of model security, we assign lower weights to attackers who dishonestly report data distributions based on the model accuracy $acc^{s_m}_{t}$ of $s_m$. Therefore, as the model accuracy $acc^{s_m}_{t}$ increases, the weight assigned to $s_m$ also increases, making the reputation opinion from $s_m$ more reliable.

The final colleague credit evaluation for $\forall U_i \in s_m$ can be calculated as:
\begin{equation}
\Phi^{s_m \rightarrow i}_{t}=\Phi^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{(\rho^{s_{m^{\prime}}}_{t} b^{s_{m^{\prime}} \rightarrow s_{m}}_{t}+ a u^{s_{m^{\prime}} \rightarrow s_{m}}_{t})}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},   
\end{equation}

\subsection{UAV nodes selection with comprehensive
community-based credit}
\subsubsection{Comprehensive community-based credit} 
Finally, by merging peer credit and colleague credit evaluation results, we can obtain comprehensive evaluations of participant UAV nodes based on similarity and performance jointly. 
The comprehensive reputation opinion $\Upsilon^{i}_{t}$ can be calculated by conducting consensus mechanism between $\Upsilon^{c_k\rightarrow i}_{t}$ and $\Upsilon^{s_m\rightarrow i}_{t}$ as:
\begin{equation}
\Upsilon^{i}_{t}=
\left  \{
      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
        b^{i}_{t}=\frac{b^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+b^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
        d^{i}_{t}=\frac{d^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+d^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
        u^{i}_{t}=\frac{u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}
        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}         
    \end{array}
\right.
\end{equation}

%因此，可得客户 $j$ 的综合信任度为：
The comprehensive community-based credit of $U_i$ is: 
\begin{equation}
\Phi^{i}_{t}=b^{i}_{t}+a u^{i}_{t}
\end{equation}

%通过上述信誉评估过程，服务器可以从簇和super node两个维度综合选择具有高性能和可靠数据的高信誉候选客户作为联邦学习任务中的参与者。该方法能够与FEDGS框架紧密结合，在FEDGS内部同步和外部同步的过程中分别从簇内和super node间评估客户信誉，将信誉评估细化到每轮迭代中，能够及时发现并排除攻击者，尽可能地减少其对联合学习的干扰。

Similar to peer credit evaluation, the updating rule of $\Phi^{i}_{t}$ is also designed with stability consideration as follows:
%\textbf{更新：}第$r$轮迭代，被选中参与联合学习的客户集合为$Set_{t}$。设$\left\{ \Phi^{i}_{t} \right\}_{i=1}^N$表示维护的第$r$轮每个客户的综合信誉。在迭代学习的过程中，对于未被选中构建supernode并参与训练的客户，保持其最近轮次的信用评分，并根据最近的综合信任度计算其下一轮次的选择概率：
\begin{equation}
\Phi^{i}_{t}=
\left\{\begin{array}{ll}
\Phi^{i}_{t} & \text { if } i \in Set_{t} \\
\Phi^{i}_{t-1}& \text { otherwise }
\end{array}, \text { for all } i\in[N]\right.
\end{equation}

\textbf{Resistance ability against collusion attack:} 
%当攻击者拥有多个compromised节点时，多个节点可以进行共谋攻击。MR-FFL可以通过简单的设置实现对共谋攻击的阻断。具体来说，在MR-FFL中，攻击者可以采取“集中合谋”或者“分散合谋”策略：（1）分散合谋的攻击者上报不同的数据分布，从而隐藏进不同的异构Peer社区中。显然，这一策略面对传统防御方法或许能够实现绕过，面对MR-FFL时则会被社区内其他用户发现；（2）顾名思义，集中合谋下的攻击者攻击者通过汇报相同的分布而集中在同一个peer社区中。显然，由于我们的综合信用评价同时综合相似度和性能的影响，因此攻击者仍会因为性能不佳而降低评价。我们可以设定一个参与FFL的最低信用值，拥有过多恶意用户的peer社区也会被排除出后续训练。
When attackers possess multiple compromised UAV nodes, these nodes can conspire to launch collusion attacks. MR-FFL can effectively thwart collusion attacks through simple configurations. Specifically, within MR-FFL, attackers may adopt either a "distributed collusion" or a "centralized collusion" strategy: (a) Attackers engaged in distributed collusion report distinct data distributions, thereby concealing themselves within different heterogeneous peer communities. While this strategy might potentially evade traditional defense methods, when facing MR-FFL, it becomes detectable by other users within the community; (b) As the name implies, attackers engaging in centralized collusion report identical distributions and concentrate within the same peer community. However, due to our comprehensive credit evaluation, which considers both similarity and performance impacts, attackers are still subject to diminished evaluations due to poor performance. A minimum credit threshold for participation in FFL can be set, and peer communities with an excess of malicious users can be excluded from subsequent training.

\subsubsection{UAV nodes selection}
%在每轮外部同步结束，我们重新选择客户构建下一轮参与联合学习的super node。
%为了尽可能地消除攻击者的干扰，我们设计簇内客户选择机制，客户被选中参与联合学习的概率由其上一轮次的综合信用评价决定。在簇$c$中，用sigmoid函数量化客户$i$被选中的概率：
After each round of FFL training, we reconstruct colleague communities as participants for the next round. To mitigate the impact of potential attacks, we introduce a client selection mechanism within the peer community. The probability of a client being chosen to participate in FFL is determined by its current comprehensive credit evaluation. Drawing inspiration from \cite{zhou2022defta}, we employ a Sigmoid-like function to quantify this probability of UAV $U_i$:
\begin{equation}
\psi^{i}_t=\frac{1}{1+e^{-k (\Phi^{i}_{t}-\gamma)}},\forall U_i \in \mathbf{U}, \forall t
\end{equation}
%其中$k$为控制sigmoid斜率的参数。由于$\Phi^{i}_{t}\in [0,1]$,我们规定选择概率函数的定义域在[0,1]区间内。可以看出选择概率函数在定义域内的值域$[\frac{1}{1+e^{0.5k}},\frac{1}{1+e^{-0.5k}}]$取决于参数$k$。在实际应用中，为了使选择概率在定义域内尽可能接近0和1，一般选择较大的斜率$k$。
where $k$ controls the slope of the Sigmoid function. As $\Phi^{i}_{t}\in [0,1]$, we stipulate that the domain of the probability function $\psi^{i}_t$ lies within $[0,1]$. It can be observed that the range of $\psi^{i}_t$ is $[\frac{1}{1+e^{\gamma k}},\frac{1}{1+e^{-\gamma k}}]$, depending on $k$. In practical applications, to ensure that the selection probability function closely approaches 0 (malicious clients) and 1 (benign yet heterogeneous clients) within its domain, a larger slope parameter $k$ is usually chosen.

\textbf{Positive assumption for fairness among benign UAVs:} It is worth mentioning that, different from existing methods' negative assumption, we initiate the selection with positive assumption, i.e., $\Phi^{i}_{0}=1 ,\forall U_i\in \mathbf{U}$, which provides high selective probability for inexperienced new participants. Therefore, this approach can achieve more fair selection results among benign UAV nodes and maximize client participation. Besides, we obtain a more comprehensive evaluation of credit, drastically mitigating the potential impact of adversarial behavior.
%服务器基于本轮综合信用评分选择客户参与下一轮次的训练，为了尽可能地提高客户的参与率，得到更全面、完整的客户信誉评估结果，将综合信誉作为客户属性进行持久化存储，服务器将赋予客户乐观的初始综合信誉并在每轮交互中更新客户的最新综合信誉。
%The server selects clients for the next training round based on the current comprehensive credit score. In order to maximize client participation, achieve a more comprehensive and complete client credit assessment, and persistently store the comprehensive credit as a client attribute, the server endows clients with an optimistic initial comprehensive credit. 
%乐观的初始信誉和时间延迟的信誉更新增加了参与训练次数较少的客户被选中的概率，能够更全面、完善地评估所有客户的信誉，避免潜在攻击的影响。
%This initial credit, along with delayed credit updates over time, increases the probability of selecting clients with fewer training participations. This approach aims to provide a more comprehensive and thorough evaluation of all clients' reputations, mitigating the potential impact of adversarial behavior.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{algorithm}[t]
% \caption{algorithm credit} %算法的名字
% \begin{algorithmic}[1]
%  \State \textbf{\bf Input:Model Variation of Client i $\Delta\widetilde{\omega^{i}_{t}}$, Model Variation of Cluster c $\Delta\widetilde{\omega^{c}_{t-1}}$}
% \State\textbf{Output:Comprehensive Credit of Client $\Phi^{i}_{t}$,Peputation Opinion Vector $\Upsilon^{i}_{t}$} 
% \State \textbf{Initialize:$u^{c \rightarrow i}_{0}=\frac{\sigma_{c}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}$,$b^{c \rightarrow i}_{0}=1-u^{c \rightarrow i}_{0}$,$d^{c \rightarrow i}_{0}=0$}
% \For{$r \in 1,\cdots,R$}
%     \State {\color{CadetBlue}/*\textbf{Credit in cluster $c$ */}}
%         \For{each client $i \in c$ }
%             \If{client $i \in C \cap S$ }
%                 \State $ \alpha^{c,i}_{t} = \alpha( \Delta\widetilde{\omega^{c}_{t-1}}, \Delta\widetilde{\omega^{i}_{t}}) = \frac{\langle \Delta\widetilde{\omega^{c}_{t-1}},\Delta\widetilde{\omega^{i}_{t}}\rangle}{\Vert \Delta\widetilde{\omega^{c}_{t-1}}\Vert\cdot\Vert \Delta\widetilde{\omega^{i}_{t}}\Vert }$,
%                 \State$p^{c \rightarrow i}_{t} = \alpha^{c,i}_{t} -(-1)$,$n^{c \rightarrow i}_{t} = 1-\alpha^{i,j}_{t}$,
%                 \State \textbf{update  $\Upsilon^{c \rightarrow i}_{t},\Phi^{c \rightarrow i}_{r,time}$ with equation}
%                 \State $\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{r,time}$
%             \Else
%                 \State$\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{t-1}$
%             \EndIf
%          \EndFor
%     \State {\color{CadetBlue}/*\textbf{Credit in supernode $s$ */}}
%     \For{each supernode $s_{m} \in S-s_{m}$}
%         \State $\alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega^{s_{m}}_{t}},  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}) = \frac{\langle  \Delta\widetilde{\omega^{s_{m}}_{t}}, \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\rangle}{\Vert  \Delta\widetilde{\omega^{s_{m}}_{t}}\Vert\cdot\Vert  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\Vert }$,
%         \State $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$,$ NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$
%         \State \textbf{update $\UpsiloNI^{s_{m} \rightarrow s}_{t},\Phi^{s}_{t}$ with equation}
%     \EndFor
%     \For{each client $i \in S$}
%         \State $\Phi^{s \rightarrow i}_{t}=\Phi^{s}_{t} $
%     \EndFor
%     \State {\color{CadetBlue} /*\textbf{Comprehensive credit */}}
%     \For{each client $i \in Clients$}
%         \If{client $i \in C\cap S$ }
%         \State \textbf{update $\Upsilon^{i}_{t},\Phi^{i}_{t}$ with equation}
%         \Else 
%         \State $\Phi^{i}_{t} = \Phi^{i}_{t-1}$
%         \EndIf
%     \EndFor
% \EndFor
% \end{algorithmic}
% \end{algorithm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tb]
	\begin{minipage}[!t]{0.49\linewidth}
		\centering
		\includegraphics[width=\linewidth]{results/SCC_diff.pdf}
		%\vspace{-2em}
		\caption{$L_2$-divergence}
		\label{results:1-diff}
	\end{minipage}
        \begin{minipage}[!t]{0.49\linewidth}
		\centering
		\includegraphics[width=\linewidth]{results/SCC_time.pdf}
		%\vspace{-2em}
		\caption{Running time}
		\label{results:1-time}
	\end{minipage}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{results/SCC_acc.pdf}
\caption{The accuracy comparison between MR-FFL with existing heterogeneity-robust methods.}
\label{results:1-acc}
\end{figure}

\section{Experimental results}
\subsection{Experimental settings}
Experiments were conducted using the PyTorch deep learning framework, employing two widely adopted benchmark datasets (EMNIST and CIFAR). To demonstrate the defense performance of the proposed MR-FFL scheme, we conduct both explicit (Flipping attack) and implicit (Backdoor attack) attack paradigms. %The EMNIST dataset encompasses 10 categories for digits and 52 categories for uppercase and lowercase English letters, totaling 62 categories. All images have dimensions of 28x28 pixels. 
In line with the methodologies of previous studies \cite{mohri2019agnostic,tan2022fedproto, zeng2022heterogeneous}, our experiments were conducted under a non-iid setting, implementing non-uniform sampling within the dataset. 
To create an equitable but dissimilar distribution among clients, we extracted 12,0000 training samples and 30,000 testing samples, allocating them in an 8:2 ratio between the training set and the validation set. This ensured that each client possessed an equal number of samples in the training dataset, albeit with distinct data distributions. %Two neural network architectures, a simple CNN and an MLP, were employed to undertake the Federated Learning (FL) task on the EMNIST dataset. The detailed configurations of the local network models are delineated in Tables 2 and 3.
Throughout our experiments, we configured $200\sim 500$ UAV nodes. A total of 200 communication rounds were executed, where the local training epoch for each $U_i$ is 5, the batch size is 128, the learning rate $\eta$ is 0.1, and the momentum is 0.9.

\subsection{The effectiveness of MR-FFL in heterogeneous UAV network}

To verify the effectiveness of our stratified community construction mechanism, we compare it with existing heterogeneity-robust methods in terms of divergence reduction, running time, and learning performance. We choose three benchmark methods (\textbf{Random}, \textbf{Bayesian}, \textbf{Generic algorithms}) and two latest methods (\textbf{Cohort} \cite{hiessl2022cohort} and \textbf{GBP-CS} \cite{li2022data}). 
In terms of divergence reduction, as shown in Figure \ref{results:1-diff}, our method significantly reduces both the average maximum divergences and deviation among clients, which indicates better robustness. 
Regarding execution time, SCC requires only one operation to generate a sampling template. Subsequently, it performs random sampling based on the template, resulting in a short execution time. This advantage becomes more pronounced with increasing rounds. As shown in Figure \ref{results:1-time}, our method is more time-saving than other alternative methods.%On the other hand, Bayesian sampling and Genetic Algorithm have excessively long execution times, which are not acceptable. The Cohort algorithm has a relatively short runtime, but it suffers from a large deviation from the target distribution. GBP-CS algorithm needs sampling before each iteration, and its runtime is not as efficient as the QIP algorithm.

In terms of learning performance, we also compared three representative algorithms (\textbf{FedAvg} \cite{li2019convergence-fedavg}, \textbf{FedNova} \cite{wang2020tackling-fednova}, \textbf{FedProx} \cite{yuan2022convergence-fedprox}) with MR-FFL. As illustrated in Figure \ref{results:1-acc}, vanilla FL algorithms exhibit slow convergence rates and poor performance with large fluctuations in heterogeneous environments. In comparison to heterogeneous FL algorithms like FedNova and FedProx, MR-FFL continues to achieve better convergence speed, stability, and accuracy.

\subsection{The performance of MR-FFL against poisoning attacks}
\begin{figure*}[!t]
\centering
\subfloat[EMNIST (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_MINIST_acc.pdf}%
\label{result0:acc-EMNIST-FLIP}}
\hfil
\subfloat[CIFAR (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_Cifar_acc.pdf}%
\label{result0:acc-CIFAR-FLIP}}
\hfil
\subfloat[EMNIST (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_MINIST_att_acc.pdf}%
\label{result0:acc-EMNIST-Backdoor}}
\hfil
\subfloat[CIFAR (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_Cifar_att_acc.pdf}%
\label{result0:acc-CIFAR-Backdoor}}
\caption{The defense performance comparison between MR-FFL with existing poisoning-resistant methods against Flipping and Backdoor attacks.}
\label{results:0-acc}
\end{figure*}

%%%%%%%%%%%%EMNIST+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\centering
\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_MINIST_cr_1.pdf}%
\label{result1:credit-AAD}}
\hfil
\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_MINIST_pr_1.pdf}%
\label{result1:prob-AAD}}
\hfil
\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_MINIST_cr_1.pdf}%
\label{result1:credit-FLtrust}}
\hfil
\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_MINIST_pr_1.pdf}%
\label{result1:prob-FLtrust}}
\hfil
\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_MINIST_cr_1.pdf}%
\label{result1:credit-MRFFL}}
\hfil
\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_Flip_MINIST_pr_1.pdf}%
\label{result1:prob-MRFFL}}
\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on EMNIST.}
\label{results_EMNIST_flip}
\end{figure}

%%%%%%%%%%%EMNIST+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\centering
\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_MINIST_cr_1.pdf}%
\label{result2:credit-AAD}}
\hfil
\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_MINIST_pr_1.pdf}%
\label{result2:prob-AAD}}
\hfil
\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_MINIST_cr_1.pdf}%
\label{result2:credit-FLtrust}}
\hfil
\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_MINIST_pr_1.pdf}%
\label{result2:prob-FLtrust}}
\hfil
\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_MINIST_cr_1.pdf}%
\label{result2:credit-MRFFL}}
\hfil
\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_BACKDOOR_MINIST_pr_1.pdf}%
\label{result2:prob-MRFFL}}
\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on EMNIST.}
\label{results_EMNIST_Backdoor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%CIFAR+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\centering
\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_Cifar_cr_1.pdf}%
\label{result3:credit-AAD}}
\hfil
\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_Cifar_pr_1.pdf}%
\label{result3:prob-AAD}}
\hfil
\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_Cifar_cr_1.pdf}%
\label{result3:credit-FLtrust}}
\hfil
\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_Cifar_pr_1.pdf}%
\label{result3:prob-FLtrust}}
\hfil
\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_Cifar_cr_1.pdf}%
\label{result3:credit-MRFFL}}
\hfil
\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_Flip_Cifar_pr_1.pdf}%
\label{result3:prob-MRFFL}}
\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on CIFAR.}
\label{results_Cifar_flip}
\end{figure}
%%%%%%%%%%%CIFAR+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\centering
\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_Cifar_cr_1.pdf}%
\label{result4:credit-AAD}}
\hfil
\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_Cifar_pr_1.pdf}%
\label{result4:prob-AAD}}
\hfil
\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_Cifar_cr_1.pdf}%
\label{result4:credit-FLtrust}}
\hfil
\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_Cifar_pr_1.pdf}%
\label{result4:prob-FLtrust}}
\hfil
\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_Cifar_cr_1.pdf}%
\label{result4:credit-MRFFL}}
\hfil
\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_BACKDOOR_Cifar_pr_1.pdf}%
\label{result4:prob-MRFFL}}
\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on CIFAR.}
\label{results_Cifar_Backdoor}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Subsequently, to further demonstrate the advantages of the MR-FFL method in ensuring model integrity, we compare our approach with existing representative reliable FL algorithms, including \textit{mitigation-oriented} \cite{blanchard2017machine-krum,yin2018byzantine-trimmedmean}, \textit{detection-oriented} \cite{andreina2021baffle}, and \textit{credit-oriented} \cite{li2019abnormal,cao2020fltrust}. The total number of UAV ndoes is set to 200. As shown in Figure \ref{results:0-acc}, we conduct explicit attacks (flipping) and compare the training accuracy in Figure \ref{result0:acc-EMNIST-FLIP} and \ref{result0:acc-CIFAR-FLIP}. Higher accuracy means better defense effect. Meanwhile, the backdoor task accuracy (implicit attack) on EMNIST and CIFAR is demonstrated in Figure \ref{result0:acc-EMNIST-Backdoor} and \ref{result0:acc-CIFAR-Backdoor}, respectively. Lower backdoor accuracy indicates better defense performance. 
Based on the results, it is evident that mitigation-oriented schemes such as \textbf{Trimmed-mean} \cite{yin2018byzantine-trimmedmean} exhibit significant deviations from the global objectives in heterogeneous environments, resulting in lower accuracy. \textbf{BaFFLe} \cite{andreina2021baffle}, as a detection-oriented method, struggles to converge rapidly and requires additional validation rounds, incurring substantial communication and time overhead. For credit-oriented methods \textbf{AAD} \cite{li2019abnormal} and \textbf{FLTrust} \cite{cao2020fltrust}, although AAD can permanently ban attackers, the gap between heterogeneous gradients and attacker gradients relative to the pre-trained global model leads to erroneous elimination, resulting in an overall performance decline. Similarly, in FLTrust, heterogeneous UAVs with gradients opposite to the direction of server-side model updates face challenges participating in the global model aggregation, causing a decline in model performance.

Furthermore, in Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, through a comparative analysis of credit assessment values and selection probabilities with existing methods such as AAD (based on autoencoder) and FLTrust (based on bootstrapping), we validate the effectiveness of the credit evaluation mechanism in the MR-FFL scheme. This validation is crucial for guiding subsequent hyperparameter tuning and adaptive configurations. As illustrated in the first rows of those figures, the AAD method lacks adaptation to highly heterogeneous environments, leading to the misclassification of numerous legitimate UAV nodes. Under FLTrust, as shown in the second rows of above figures, both the credit of normal UAV participants and their selection probabilities exhibit significant fluctuations, with a lack of robustness in detecting certain covert attacks. In contrast, MR-FFL evaluates the integrity of UAV nodes in terms of both community-wide similarity and performance. As shown in the third rows of Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, our method can accurately identify the stealthy malicious attackers from benign nodes.

\subsection{The fairness of MR-FFL under adversarial environments}
One of the important drawbacks of existing security technologies is unfairness. As shown in the second columns of Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, except for the low accuracy, AAD and FLTrust also assign vastly different selection probabilities to benign UAV nodes. Different from existing methods, MR-FFL employs a Sigmoid function to optimize the selection strategy, resulting in a clearer distinction between attackers and normal users (e.g., Figure \ref{result3:credit-MRFFL} and \ref{result4:credit-MRFFL}). Hence, the probabilities of legitimate clients being selected are approximate (e.g., Figure \ref{result1:prob-MRFFL} and \ref{result2:prob-MRFFL}), ensuring fairness among benign UAV nodes.

\section{Conclusion}
%随着泛在通信和技术的发展，UAV网络得到越来越广泛的应用。基于无人机的联邦学习等智能化方法能够自适应地优化部署和业务，成为重要发展趋势之一。然而，受限于有限的巡航范围，UAV设备往往高度异构，同时UAV设备资源和能量极其有限，这些约束均导致现有安全技术难以移植到UAV网络中。因此，在本文中，我们针对异构和资源受限的UAV网络下的公平联邦学习的安全问题进行了研究。基于一种分层社区构建机制，我们提出了双向可信的公平联邦学习架构，来应对异构UAV网络中的攻击威胁。在公有数据集上的系列实验表明，我们的方案相比现有技术，在异构缓解、隐私增强和污染防治方面均取得明显提升。
With the development of ISCC and SAGIN, UAV networks are experiencing increasingly widespread applications. AI technologies such as FL based on UAV enable adaptive optimization of deployment and operations, emerging as a crucial development trend. However, due to the restricted patrol area, UAV devices exhibit high heterogeneity, and their resources and energy are also extremely limited. These constraints make it challenging to directly implant existing high-consumption security methods in UAV networks. Therefore, in this paper, we investigate the security issues of FFL in heterogeneous and resource-constrained UAV networks. Leveraging a stratified community construction mechanism, we propose a mutual reliability FFL framework (MR-FFL) to address multiple security threats. %in heterogeneous UAV networks. 
A series of experiments on public datasets demonstrate significant improvements of MR-FFL in heterogeneity remission, fairness guarantee, and poisoning resistance compared to existing technologies.

\section*{Acknowledgments}
This work is partially supported by the National Natural Science Foundation of China (NSFC) under Grant 62225105 and the ZhejiangLab Open Research Project (No. K2022QA0AB05).

\bibliographystyle{IEEEtran}
\bibliography{ref}

% {\appendix[Proof of the Zonklar Equations]
% Use $\backslash${\tt{appendix}} if you have a single appendix:
% Do not use $\backslash${\tt{section}} anymore after $\backslash${\tt{appendix}}, only $\backslash${\tt{section*}}.
% If you have multiple appendixes use $\backslash${\tt{appendices}} then use $\backslash${\tt{section}} to start each appendix.
% You must declare a $\backslash${\tt{section}} before using any $\backslash${\tt{subsection}} or using $\backslash${\tt{label}} ($\backslash${\tt{appendices}} by itself
%  starts a section numbered zero.)}

%{\appendices
%\section*{Proof of the First Zonklar Equation}
%Appendix one text goes here.
% You can choose not to have a title for an appendix if you want by leaving the argument blank
%\section*{Proof of the Second Zonklar Equation}
%Appendix two text goes here.}

% \section{References Section}
% You can use a bibliography generated by BibTeX as a .bbl file.
%  BibTeX documentation can be easily obtained at:
%  http://mirror.ctan.org/biblio/bibtex/contrib/doc/
%  The IEEEtran BibTeX style support page is:
%  http://www.michaelshell.org/tex/ieeetran/bibtex/

 % argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% \section{Simple References}
% You can manually copy in the resultant .bbl file and set second argument of $\backslash${\tt{begin}} to the number of references
%  (used to reserve space for the reference number labels box).

% \begin{thebibliography}{1}
% \bibliographystyle{IEEEtran}

% \bibitem{ref1}
% {\it{Mathematics Into Type}}. American Mathematical Society. [Online]. Available: https://www.ams.org/arc/styleguide/mit-2.pdf

% \bibitem{ref2}
% T. W. Chaundy, P. R. Barrett and C. Batey, {\it{The Printing of Mathematics}}. London, U.K., Oxford Univ. Press, 1954.

% \bibitem{ref3}
% F. Mittelbach and M. Goossens, {\it{The \LaTeX Companion}}, 2nd ed. Boston, MA, USA: Pearson, 2004.

% \bibitem{ref4}
% G. Gr\"atzer, {\it{More Math Into LaTeX}}, New York, NY, USA: Springer, 2007.

% \bibitem{ref5}M. Letourneau and J. W. Sharp, {\it{AMS-StyleGuide-online.pdf,}} American Mathematical Society, Providence, RI, USA, [Online]. Available: http://www.ams.org/arc/styleguide/index.html

% \bibitem{ref6}
% H. Sira-Ramirez, ``On the sliding mode control of nonlinear systems,'' \textit{Syst. Control Lett.}, vol. 19, pp. 303--312, 1992.

% \bibitem{ref7}
% A. Levant, ``Exact differentiation of signals with unbounded higher derivatives,''  in \textit{Proc. 45th IEEE Conf. Decis.
% Control}, San Diego, CA, USA, 2006, pp. 5585--5590. DOI: 10.1109/CDC.2006.377165.

% \bibitem{ref8}
% M. Fliess, C. Join, and H. Sira-Ramirez, ``Non-linear estimation is easy,'' \textit{Int. J. Model., Ident. Control}, vol. 4, no. 1, pp. 12--27, 2008.

% \bibitem{ref9}
% R. Ortega, A. Astolfi, G. Bastin, and H. Rodriguez, ``Stabilization of food-chain systems using a port-controlled Hamiltonian description,'' in \textit{Proc. Amer. Control Conf.}, Chicago, IL, USA,
% 2000, pp. 2245--2249.

% \end{thebibliography}

\newpage

%\section{Biography Section}
% If you have an EPS/PDF photo (graphicx package needed), extra braces are
%  needed around the contents of the optional argument to biography to prevent
%  the LaTeX parser from getting confused when it sees the complicated
%  $\backslash${\tt{includegraphics}} command within an optional argument. (You can create
%  your own custom macro containing the $\backslash${\tt{includegraphics}} command to make things
%  simpler here.)

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Zan Zhou.jpg}}]{Zan Zhou} (Student Member, IEEE)
received his Ph.D. degree in Computer Science from the Beijing University of Posts and Telecommunications (BUPT) in 2022. 
From 2021 to 2022, he was a visiting student at Nanyang Technology University (NTU), Singapore. 
He is currently a Postdoc researcher with the State Key Laboratory of Networking and Switching Technology, BUPT, Beijing, China. His research interests include data privacy, active defense, and federated learning. %He is Student member of IEEE.
\end{IEEEbiography}

\vspace{11pt}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Shujie Yang.jpg}}]{Shujie Yang} received the Ph.D. degree from the Institute of Network Technology, Beijing University of Posts and Telecommunications, Beijing, China, in 2017. He is currently a lecturer with the State Key Laboratory of Networking and Switching Technology. His major research interests include network security and artificial intelligence.
\end{IEEEbiography}

\vspace{11pt}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/changqiao xu.jpg}}]{Changqiao Xu}
(Senior Member, IEEE) received the Ph.D. degree from the Institute of Software, Chinese Academy of Sciences (ISCAS) in Jan. 2009. He was a researcher at Athlone Institute of Technology and Joint Training PhD at Dublin City University, Ireland during 2007-2009. %He joined BUPT in Dec. 2009. 
Currently, he is a Professor with the State Key Laboratory of Networking and Switching Technology, and Director of the Network Architecture Research Center at BUPT. His research interests include Network Security, Mobile Networking, Multimedia Communications, and Future Internet Technology. He has edited two books and published over 200 technical papers in prestigious international journals and conferences, including IEEE Comm. Magazine, IEEE/ACM ToN, IEEE TMC, INFOCOM, ACM Multimedia, etc. He has served a number of international conferences and workshops as a Co-Chair and TPC member. He is currently serving as the Editor-in-Chief of Transactions on Emerging Telecommunications Technologies (Wiley).
\end{IEEEbiography}
% \bf{If you include a photo:}\vspace{-33pt}
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig1}}]{Michael Shell}
% Use $\backslash${\tt{begin\{IEEEbiography\}}} and then for the 1st argument use $\backslash${\tt{includegraphics}} to declare and link the author photo.
% Use the author name as the 3rd argument followed by the biography text.
% \end{IEEEbiography}

% \vspace{11pt}

% \bf{If you will not include a photo:}\vspace{-33pt}
% \begin{IEEEbiographynophoto}{John Doe}
% Use $\backslash${\tt{begin\{IEEEbiographynophoto\}}} and the author name as the argument followed by the biography text.
% \end{IEEEbiographynophoto}

\vfill

\end{document}

### 2024-08-15 main.tex
survey: modified by wb - about attack
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 %\usepackage{algorithm}
+\usepackage[UTF8]{ctex}
 \usepackage{array}
@@
 \section{Related work}
+
+% \begin{tabular}{|p{0.4\textwidth}|p{0.5\textwidth}|}
+% \hline
+% \textbf{论文的期刊名、年份、引用} & \textbf{简介} \\
+% \hline
+% 期刊名1, 2024, 引用1 & 这篇论文讨论了...... \\
+% \hline
+% 期刊名2, 2023, 引用2 & 本研究着重于...... \\
+% \hline
+% 期刊名3, 2022, 引用3 & 本文提出了...... \\
+% \hline
+% \end{tabular}
+
 According to the three basic tenets of information security \cite{zhou2021augmented-globecom}, in this section, we systematically review the most crucial hindrances of existing FFL solutions in UAV networks: \textit{availability}, \textit{confidentiality}, and \textit{in tegrity} problems, which we settled in following sections, respectively.
@@
 
+\newpage
+\begin{table*}[]
+    \centering
+    \renewcommand\arraystretch{1.5}
+    \begin{tabular}{|c|p{3cm}|c|p{12cm}|} \hline
+    Title & Conference & Year & Main Content \\ \hline
+   \cite{jha2023label} & neurips & 2023 &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
+   \cite{yang2023data} & International Conference on Machine Learning & 2023 & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
+   \cite{dai2023chameleon} & International Conference on Machine Learning & 2023 & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
+   \cite{zhang2024a3fl} & neurips & 2024 & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
+   \cite{xu2024shadowcast} & arxiv  & 2024 & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
+   \cite{liang2024badclip} & CVPR & 2024 & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
+    \end{tabular}
+    \caption{Attack}
+    \label{tab:my_label}
+\end{table*}
+
 \end{document}

### 2024-08-16 main.tex
survey(my): about attack
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \usepackage{amsmath,amsfonts}
+\usepackage{longtable}
+\usepackage{array}
 %\usepackage{algorithmic}
@@
 \newpage
-\begin{table*}[]
+\begin{longtable}{|c|p{3cm}|c|p{12cm}|} 
     \centering
-    \renewcommand\arraystretch{1.5}
-    \begin{tabular}{|c|p{3cm}|c|p{12cm}|} \hline
+    \caption{This is the caption for the long table. \label{tab:attack_servey}}\\
+    \hline
     Title & Conference & Year & Main Content \\ \hline
+    \endfirsthead
+    \caption[]{This is the caption continued from the previous page.}\\
+    \hline
+    Title & Conference & Year & Main Content \\ \hline
+    \endhead
+    \hline
+    \endfoot
+    \hline \hline
+    \endlastfoot
    \cite{jha2023label} & neurips & 2023 &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
@@
    \cite{liang2024badclip} & CVPR & 2024 & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
-    \end{tabular}
-    \caption{Attack}
-    \label{tab:my_label}
-\end{table*}
+   \cite{attack01} & arXiv preprint & 2024 & 本篇文章次揭示了在联邦学习环境下对大语言模型（LLM）进行指令调优时存在的安全漏洞。文章提出了一种简洁但有效的安全攻击方法，恶意客户端通过使用未对齐的数据来训练本地模型，从而大幅度削弱了全球模型的安全对齐性（“未对齐的数据”，是指那些与预期的安全或伦理规范不一致的数据。例如，未对齐的数据可能包含有害的、误导性的或是不道德的信息，而这些信息在普通情况下不会被用于训练模型）。实验表明，该攻击方法能够将模型的安全性降低高达70\%，而现有的防御方法在应对此类攻击时几乎无效，仅能提高4\%的安全性。为了解决这一问题，作者进一步提出了一种新的事后防御方法，即通过服务器端生成对齐数据并进一步对全局模型进行微调，从而增强模型的安全性（中央服务器在接收到各个客户端的更新后，会主动生成一组对齐的数据。这些对齐的数据是预先定义好的，确保与预期的安全和伦理规范一致。这些数据可能包含严格筛选过的内容，如道德上中立或积极的文本片段）。实验结果显示，这种防御方法能够将模型的安全性提高最多69\%，且不显著降低模型的有效性。（这篇看完了发现不是视觉大模型） \\ \hline
+   \cite{attack02} & arXiv preprint & 2024 & 本篇文章探讨了一种针对大语言模型（LLMs）的新型训练方法，称为目标潜在对抗性训练（Targeted Latent Adversarial Training, LAT），文章提出了通过在模型的潜在表示（latent representations）中引入针对性的扰动，来更有效地消除模型中顽固的不良行为（如后门攻击和模型“越狱”）。(潜在表示是指在神经网络的中间层中，数据通过多层非线性变换后所形成的特征表示。这些表示通常处于更高的抽象层次，与原始输入相比，能够捕捉到数据的深层次特征。在视觉大模型中，这些潜在表示可能包括图像的边缘、形状、纹理等更抽象的特征，而不再是具体的像素值。潜在表示在模型中扮演着至关重要的角色，因为它们是模型用来进行预测和决策的核心特征。)(针对性的扰动是指在训练或评估过程中，特意对模型的输入或潜在表示进行细微的修改或扰动，以诱导模型产生特定的（通常是不希望的）行为。通过这种方法，可以测试和增强模型在面对各种攻击时的鲁棒性。在本文中，作者使用潜在空间中的针对性扰动来模拟攻击，目的是强化模型的防御能力，使其能够抵抗类似的实际攻击，如后门攻击或越狱行为。)研究表明，与传统的对抗性训练相比，目标潜在对抗性训练可以显著提高模型抵抗这些攻击的能力，同时对模型的整体性能影响较小。文章通过实验验证了该方法在增强模型鲁棒性方面的有效性，尤其是在面对未知触发条件的后门攻击时，表现出色。  \\ \hline
+   \cite{attack03} & arXiv preprint & 2024 & 本文探讨了开放权重大语言模型（LLMs）在面对篡改攻击时的脆弱性，并提出了一种名为TAR（Tampering Attack Resistance）的方法，旨在增强这些模型的抗篡改能力。文章指出，现有的安全防护措施，如拒绝机制和偏好训练，容易在少量微调步骤后被攻击者绕过，导致模型被恶意修改。为此，TAR方法通过对抗性训练和元学习，设计了一种新的防护机制，使得即使在经历数千步的微调攻击后，模型仍能保持其原有的安全防护功能。实验结果显示，与现有方法相比，TAR显著提高了模型的抗篡改能力，同时保留了模型的正常功能。研究还通过大量红队评估验证了TAR方法的有效性，展示了其在应对各种复杂攻击时的鲁棒性。(红队评估是一种在网络安全和机器学习领域常用的测试方法，它通过模拟攻击者的行为来评估系统或模型的安全性和防御能力。红队通常扮演“敌方”角色，主动寻找和利用系统的漏洞，以测试系统在真实攻击场景下的表现。这种方法帮助识别和修复安全漏洞，使系统在面对潜在的实际攻击时更加稳健。这篇文章中研究人员通过设计多个测试对手，这些对手模拟了各种可能的攻击策略，试图篡改或破坏大语言模型的功能。文章中提到进行了28个不同的红队评估测试，每个测试都旨在突破TAR的防护机制。)文章中的攻击方式涉及通过微调大语言模型的权重来篡改其行为。攻击者可以在模型的开放权重上进行少量微调，使其在特定情况下产生不希望的输出。例如，攻击者可能会在输入特定触发词时，让模型生成有害内容或偏离其正常功能。\\ \hline
+   \cite{attack04} & arXiv preprint & 2024 & 这是一篇综述。本文主要介绍了以下攻击方式：\begin{itemize}
+    \item 对抗性攻击：通过对输入数据进行微小的扰动，这些扰动虽然对人类几乎不可见，但会导致模型产生显著错误的输出，例如在图像分类中，可能会使模型将一个正常的图像误分类为完全不同的类别；
+    \item 后门攻击：和之前咱做的一样；
+    \item 数据中毒攻击：攻击者向模型的训练数据中注入恶意样本，这些样本会导致模型在遇到类似数据时输出错误结果，例如在物体识别任务中，中毒数据可能会导致模型误将无害物体识别为威胁；
+    \item 模型逃逸：攻击者通过调整输入或模型参数，试图找到绕过模型防御机制的方法，使模型输出不受控制的内容，这种攻击常用于测试模型的防御效果；
+    \item 多模态攻击：针对处理多种类型输入（如文本和图像）的模型，攻击者通过操纵一种模态的输入来影响另一种模态的输出，例如在多模态对话系统中，通过改变图像输入可能会影响系统的文本回应；
+    \item 跨语言攻击：在多语言任务中，攻击者通过在一种语言中引入扰动来影响模型在另一种语言中的表现，这类攻击特别针对多语言翻译或生成模型，可能导致不同语言间的翻译不准确或失真。
+    \end{itemize}\\ \hline
+   \cite{attack05} &  Advances in Neural Information Processing Systems 34 (NeurIPS 2021) & 2021 & 本篇文章讨了如何保护通过“彩票假设”（Lottery Ticket Hypothesis, LTH）找到的稀疏子网络（即“中奖票”）的所有权。文章提出了一种新的基于稀疏结构信息的验证方法，通过在网络的稀疏结构中嵌入签名来进行所有权验证。这种方法能够在白盒和黑盒场景下保护模型的知识产权，并且对细微调整（如微调和剪枝）具有很强的鲁棒性。研究还通过大量实验验证了该方法在多种模型（如ResNet-20、ResNet-18、ResNet-50）和数据集（如CIFAR-10和CIFAR-100）上的有效性，展示了其在应对移除攻击和模糊攻击时的坚韧性。具体攻击方式有：细微调整（Fine-tuning）攻击：对模型进行微调来改变模型的权重值，同时希望不改变网络的稀疏结构。这种攻击旨在通过调整权重，试图使嵌入的签名信息变得不可辨认或无效。然而，由于嵌入的信息是基于网络的稀疏结构（即被剪枝后的模型结构），细微调整难以改变这一基础结构，从而无法有效移除签名。剪枝（Pruning）攻击：攻击者尝试通过进一步剪枝来移除嵌入的签名信息。这种攻击的目的是通过减少模型的非零参数，使得嵌入的结构信息丢失。然而，文章中提出的嵌入方法确保了签名信息在极端稀疏的情况下仍能保留，即使剪枝比例达到一定程度，签名依然可以从稀疏结构中提取出来。模糊攻击（Ambiguity Attacks）：攻击者试图通过制造伪签名或模糊原有签名的信息来混淆所有权验证。这种攻击可能包括添加噪声、篡改稀疏结构等手段，旨在使得验证机制无法区分真实的所有权签名和伪造的信息。然而，文章中的验证方法通过设计稳健的结构嵌入机制，使得这种模糊攻击难以成功。(“签名”指的是嵌入到神经网络稀疏结构中的一种独特的标识信息。这种签名通过在模型的剪枝过程中，利用网络的稀疏性来实现。具体而言，当模型被剪枝后，一部分神经元和连接被移除，剩余的结构会呈现出一种特定的稀疏模式。作者通过在这种稀疏模式中嵌入一个特定的结构或模式，这个模式就是所谓的“签名”。这种签名是不可见的，但可以通过特定的验证过程来提取和识别。其主要功能是为网络的所有权提供证据，类似于给模型打上了一个“水印”。当有人试图非法复制或篡改模型时，这个嵌入的签名仍然可以被识别出来，从而验证模型的归属。签名的鲁棒性设计使其能够抵抗常见的攻击方式（如微调和进一步的剪枝），即使模型经历了这些操作，签名依然可以从其稀疏结构中被提取出来，证明模型的所有权。)(模型的所有权是指对一个机器学习模型（如神经网络模型）所拥有的法律和知识产权。所有权通常由开发者或公司拥有，表示他们对模型的设计、训练数据、训练方法以及最终生成的模型参数等有控制权和排他性使用权。这意味着只有模型的所有者有权利决定如何使用、修改、发布或授权使用该模型。（可能涉及到知识产权保护、商业机密的保密）)\\ \hline
+   \cite{attack06} & Portail HAL theses(theses.hal.science) & 2022 & 这篇文章有185页。本篇文章讨论了如何通过数字水印技术来保护机器学习模型的知识产权，防止模型被盗用。文章首先提供了当前水印技术的概述，并进一步扩展了这些技术在图像分类任务之外的应用，涵盖了回归、机器翻译和强化学习模型。作者还提出了针对模型托管平台的伪造攻击（即试图通过伪造水印来绕过验证）并介绍了一种基于公平性的水印技术，以增强模型在黑盒环境中的安全性。实验结果表明，这些水印技术不仅可以有效防止模型盗用，还能够在面对各种攻击时保持鲁棒性。
+   数字水印是一种嵌入信息的技术，用于在数字内容（如图像、音频、视频或机器学习模型）中隐藏特定的信息，以表明所有权或版权。对于机器学习模型来说，数字水印是一种通过特定算法将标识信息嵌入到模型的权重、结构或输出中的技术。这种标识信息通常是不可见或难以察觉的，但可以通过特定的提取过程来验证。（数字水印的目的有：知识产权保护：开发者可以通过在模型中嵌入水印来证明模型的所有权，防止未经授权的复制和使用；盗版检测：如果一个模型被盗用或未经许可发布，水印可以作为证据，证明模型的来源和合法所有者；内容跟踪：水印可以帮助追踪模型的使用情况，尤其是在多个平台或用户之间共享时，确保模型的使用符合许可协议。） \\ \hline
+
+\end{longtable}
 

### 2024-08-16 main.tex
table.ok: 表格可以跨页了
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \newpage
+\onecolumn
 \begin{longtable}{|c|p{3cm}|c|p{12cm}|} 
-    \centering
-    \caption{This is the caption for the long table. \label{tab:attack_servey}}\\
-    \hline
+    \caption{This is the caption for the long table}
+    \label{tabl:attack} \\ \hline
     Title & Conference & Year & Main Content \\ \hline
-    \endfirsthead
-    \caption[]{This is the caption continued from the previous page.}\\
-    \hline
+    \endfirsthead \hline
     Title & Conference & Year & Main Content \\ \hline 
-    \endhead
-    \hline
-    \endfoot
-    \hline \hline
-    \endlastfoot
+    \endhead \hline
    \cite{jha2023label} & neurips & 2023 &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
@@
    \cite{dai2023chameleon} & International Conference on Machine Learning & 2023 & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
+   \cite{gu2023gradient} & ACL & 2023 & 这篇文章提出了一种新的梯度控制方法，旨在解决参数高效调优（PET）过程中后门攻击的遗忘问题。通过将后门注入过程视为多任务学习，文章引入了跨层梯度幅度归一化和层内梯度方向投影两种策略，以减少不同任务之间的梯度冲突和梯度大小的不平衡，从而增强后门攻击在用户微调模型后的效果。实验结果表明，该方法在情感分类和垃圾邮件检测任务中显著提高了后门攻击的持久性和有效性。 \\ \hline
    \cite{zhang2024a3fl} & neurips & 2024 & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
@@
    \cite{liang2024badclip} & CVPR & 2024 & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
+
    \cite{attack01} & arXiv preprint & 2024 & 本篇文章次揭示了在联邦学习环境下对大语言模型（LLM）进行指令调优时存在的安全漏洞。文章提出了一种简洁但有效的安全攻击方法，恶意客户端通过使用未对齐的数据来训练本地模型，从而大幅度削弱了全球模型的安全对齐性（“未对齐的数据”，是指那些与预期的安全或伦理规范不一致的数据。例如，未对齐的数据可能包含有害的、误导性的或是不道德的信息，而这些信息在普通情况下不会被用于训练模型）。实验表明，该攻击方法能够将模型的安全性降低高达70\%，而现有的防御方法在应对此类攻击时几乎无效，仅能提高4\%的安全性。为了解决这一问题，作者进一步提出了一种新的事后防御方法，即通过服务器端生成对齐数据并进一步对全局模型进行微调，从而增强模型的安全性（中央服务器在接收到各个客户端的更新后，会主动生成一组对齐的数据。这些对齐的数据是预先定义好的，确保与预期的安全和伦理规范一致。这些数据可能包含严格筛选过的内容，如道德上中立或积极的文本片段）。实验结果显示，这种防御方法能够将模型的安全性提高最多69\%，且不显著降低模型的有效性。（这篇看完了发现不是视觉大模型） \\ \hline
@@
    数字水印是一种嵌入信息的技术，用于在数字内容（如图像、音频、视频或机器学习模型）中隐藏特定的信息，以表明所有权或版权。对于机器学习模型来说，数字水印是一种通过特定算法将标识信息嵌入到模型的权重、结构或输出中的技术。这种标识信息通常是不可见或难以察觉的，但可以通过特定的提取过程来验证。（数字水印的目的有：知识产权保护：开发者可以通过在模型中嵌入水印来证明模型的所有权，防止未经授权的复制和使用；盗版检测：如果一个模型被盗用或未经许可发布，水印可以作为证据，证明模型的来源和合法所有者；内容跟踪：水印可以帮助追踪模型的使用情况，尤其是在多个平台或用户之间共享时，确保模型的使用符合许可协议。） \\ \hline
-
+    % \endfoot
+    % \hline
+    % \endlastfoot
+    % \hline
 \end{longtable}

### 2024-08-16 attack-zh.tex
refactor: 重构之把中文之类的单独拆分出来
Signed-off-by: LetMeFly666 <814114971@qq.com>

--- 2024-08-16 main.tex
@@
 \usepackage{longtable}
-\usepackage{array}
-%\usepackage{algorithmic}
-%\usepackage{algorithm}
 \usepackage[UTF8]{ctex}
 \usepackage{array}
-\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\usepackage{textcomp}
 \usepackage{stfloats}
 \usepackage{url}
-\usepackage{verbatim}
 \usepackage{graphicx}
 \usepackage{cite}
-\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
-% updated with editorial comments 8/9/2021
-
-\usepackage{algorithm}
-%\usepackage{algorithmic}
-\usepackage{algpseudocode}
-
-\usepackage{dsfont}
-\usepackage{amssymb}
-\usepackage{amsmath,amsthm,amssymb,amsfonts}
-\usepackage{ragged2e}
-\usepackage{latexsym, amssymb, verbatim, amsmath}
-\usepackage{amsmath,bm}
-\usepackage{multirow}
-\usepackage{mathtools}
-\usepackage{subeqnarray}
-\usepackage{cases}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathrsfs}
-\usepackage{graphicx}
-%\usepackage{subfigure}
-\usepackage{booktabs}
-\usepackage{color}
-\usepackage{cite}
-\usepackage[]{chapterbib}
-\usepackage{enumerate}
-
-\usepackage[dvipsnames, svgnames, x11names]{xcolor}
-\usepackage{algorithm,algpseudocode,float}
 
@@
 
-\title{SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Stealthy Poisoning Attacks in IoRT Networks}
+后门攻击：我们将现有针对模型的后门攻击分为两种，即时间隐蔽性后门攻击和空间隐蔽性后门攻击。
+空间隐蔽性后门攻击是指攻击者通过调整触发器或梯度等方式，使得现有防御方法无法在特征空间中有效区分恶意攻击者与良性参与者，从而有效逃避检测。Shadowcast\cite{xu2024shadowcast}通过在特征空间中引入微小、不可察觉的扰动，操纵视觉语言模型（VLMs）在特定视觉输入下生成误导性的文本输出。BadClip\cite{liang2024badclip}提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。Flip\cite{jha2023label}通过修改训练数据的标签，使得模型训练轨迹接近于带有后门的专家模型，从而在特征空间中达到隐蔽攻击的效果，即使在图像干净的情况下也能逃避现有检测方法。
+时间隐蔽性后门攻击是指攻击者设计出具有高持久性的后门，使其在恶意攻击者结束攻击后仍能长期存在，不被后续良性更新所覆盖，从而持续影响模型行为。 Chameleon\cite{dai2023chameleon}关注如何通过对比学习来调整中毒样本、干扰样本以及促进样本嵌入表示之间的关系，从而提高后门攻击的空间隐蔽性。ImgTrojan\cite{tao2024imgtrojan}通过在视觉语言模型的训练数据中注入少量恶意样本，使得这些后门即使在模型后续的良性训练中仍能保持有效，从而持续影响模型的行为。\cite{gu2023gradient}提出了一种新的梯度控制方法，通过跨层梯度幅度归一化和层内梯度方向投影，解决了参数高效调优（PET）过程中后门攻击的遗忘问题，从而维持攻击的持久性和隐蔽性。A3FL\cite{zhang2024a3fl}通过对抗性适应损失函数来优化触发器的方式，使得后门能够在全局训练动态中持久存在，从而在联邦学习模型中实现高效且持久的攻击效果。
 
-\author{Zan Zhou, %~\IEEEmembership{Student Member,~IEEE},
-Yirong Zhuang, Hongjing Li, Sizhe Huang, Shujie Yang, Peng Guo, Lujie Zhong, Zhenhui Yuan, Changqiao Xu,~\IEEEmembership{Senior Member,~IEEE}
-% <-this % stops a space
-\thanks{Z.
-Zhou, H.
-Li, S.
-Huang, S.
-Yang, P.
-Guo, and C.
-Xu are with the State Key Laboratory of Networking and Switching Technology, Beijing University of Posts and Telecommunications, Beijing 100876, P.R.
-China.
-E-mail: \{zan.zhou, lihongjing, swhsz, sjyang, guopeng, cqxu\}@bupt.edu.cn.
-	}  % <-this % stops a space
-\thanks{Y. Zhuang is with the Research Institute of China Telecom, Ave Zhongshan, Guangzhou 510630, China. E-mail: 13316094433@chinatelecom.cn.}% <-this % stops a space
- \thanks{L. Zhong is with the Information Engineering College, Capital Normal University, Beijing 100048, China. E-mail: zhonglj@cnu.edu.cn (Corresponding author).}% <-this % stops a space
-\thanks{Zhenhui Yuan is with Northumbria University, United Kingdom. E-mail: zhenhui.yuan@warwick.ac.uk.}% <-this % stops a space
-%\thanks{This paper was produced by the IEEE Publication Technology Group. They are in Piscataway, NJ.}% <-this % stops a space
-%\thanks{Manuscript received April 19, 2021; revised August 16, 2021.}
-}
-
-% The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2021}%
-{Shell \MakeLowercase{\textit{et al.}}: A Sample Article Using IEEEtran.cls for IEEE Journals}
-
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2021 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-\maketitle
-
-\begin{abstract}
-Fairness-aware federated learning (FFL) plays a crucial role in mitigating bias against specific demographic groups (e.g., gender, race, occupation) during collaborative training. 
-Along with the ever-emerging new attack paradigms like gradient leakage and model poisoning, the reliability of FFL also obtains lots of research attention.
-Either UAV nodes or FFL aggregators could be untrusted adversaries.
-Although multiple security mechanisms involving encryption, obfuscation, Byzantine-robustness, and detection have been proposed, concrete to UAV networks, the majority of existing solutions are unfeasible due to high heterogeneity and limited resources among participants.
-Hence, in this paper, we propose mutually reliable FFL (MR-FFL), a stratified community-based framework to facilitate privacy protection (FFL aggregator's reliability) and poisoning elimination (client nodes' reliability) jointly for FFL in heterogeneous UAV networks.
-We first divide UAV nodes into both peer communities (PC) and colleague communities (CC) according to cross-participant similarity and task-oriented fitness, respectively. 
-Thus, the arbitrarily settled learning tasks following fair principles can be efficiently completed by fine-tuned colleague communities, even in the presence of a large degree of heterogeneity among peer communities.
-Then, we integrate community-specific differential privacy into the MR-FFL process, to achieve privacy amplification as well as efficient and personal collaborative training at the same time. 
-More importantly, we proposed a community-based credit evaluation to resist poisoning attacks in heterogeneous environments. 
-The results on several standard datasets also highlight the performance of MR-Fed in terms of fairness, accuracy, and integrity jointly.
-
-% Fairness-aware federated learning (FFL) assumes a pivotal role in mitigating bias directed at specific demographic groups (e.g., gender, race, occupation) during collaborative training.
-The escalating threat landscape, characterized by emerging attack paradigms like gradient leakage and model poisoning, intensifies research scrutiny on FFL's reliability, recognizing the potential untrustworthiness inherent in UAV nodes and FFL aggregators.
-% Despite a plethora of proposed security mechanisms encompassing encryption, obfuscation, Byzantine robustness, and detection, their pragmatic application within UAV networks faces challenges due to pronounced heterogeneity and resource constraints among participants.
-Consequently, this paper introduces a novel approach, termed mutually reliable FFL (MR-FFL), presenting a stratified community-based framework.
-This framework concurrently addresses privacy protection (FFL aggregator's reliability) and poisoning elimination (edge nodes' reliability) within the context of FFL in heterogeneous UAV networks.
-% The categorization of UAV nodes into peer communities and colleague communities based on cross-participant similarity and task-oriented fitness facilitates the efficient completion of learning tasks adhering to fair principles.
-This effectiveness persists even in the presence of considerable heterogeneity among peer communities.
-Additionally, community-specific differential privacy is integrated into the MR-FFL process, achieving simultaneous privacy amplification and efficient, personalized collaborative training.
-% A noteworthy contribution lies in the introduction of a community-based credit evaluation system, designed to resiliently counteract poisoning attacks in heterogeneous environments.
-Empirical evaluations on standard datasets underscore the comprehensive performance of MR-Fed, highlighting its effectiveness in promoting fairness, privacy, and integrity within federated learning systems.
-
-\end{abstract}
-
-\begin{IEEEkeywords}
-Federated learning, fairness, privacy, integrity, heterogeneous UAV network.
-\end{IEEEkeywords}
-
-\section{Introduction}
-%\IEEEPARstart{T}{his} file is intended to serve as a ``sample article file'' for IEEE journal papers produced under \LaTeX\ using IEEEtran.cls version 1.8b and later.
-The most common elements are covered in the simplified and updated instructions in ``New\_IEEEtran\_how-to.pdf''.
-For less common elements you can refer back to the original ``IEEEtran\_HOWTO.pdf''.
-It is assumed that the reader has a basic working knowledge of \LaTeX.
-Those who are new to \LaTeX \ are encouraged to read Tobias Oetiker's ``The Not So Short Introduction to \LaTeX ,'' available at: \url{http://tug.ctan.org/info/lshort/english/lshort.pdf} which provides an overview of working with \LaTeX.
-%FFL很重要
-%作为的一种，
-As a preeminent collaborative artificial intelligence paradigm, Federated Learning (FL) has garnered substantial research focus \cite{ETT2}. 
-By effectively mobilizing a substantial number of participants with a discrete distribution, FL can concurrently enhance learning performance, resource utilization, and data security. 
-Besides, as intelligent applications proliferate, concerns regarding fairness-aware federated learning (FFL) have also captured significant attention \cite{zhou2021towards-KDDtutorial-FFL}.
-Due to the agnostic of multiple data sources, models trained through FL may exhibit discriminatory tendencies toward specific features or demographic groups, such as gender, race, and occupation (e.g., COMPAS recidivism algorithm \cite{angwin2022machine} and facial recognition system \cite{raji2019actionable}).
-In response to this inherent deficiency, various FFL algorithms, such as FairFed \cite{ezzeldin2023fairfed}, Ditto \cite{li2021ditto}, and FairFL \cite{zhang2020fairfl}, have been proposed.
-
-%安全问题很重要
-\subsection{Mutual reliability problem of FFL}
-Meanwhile, along with the continual emergence of novel attack techniques, such as gradient leakage and model poisoning \cite{fang2020local}, the \textit{``trust crisis''} \cite{zhou2022multi} has become a critical bottleneck in determining FFL deployment capabilities \cite{rodriguez2023survey}.
-Establishing a robust \textit{mutual reliability} relationship between the FL aggregator (parameter server) and local participants has proven challenging \cite{zhou2022multi}.
-To be specific, on the one hand, concerns about data sharing leading to privacy breaches (\textit{aggregator's reliability}) \cite{wang2021variational} raise apprehensions among owners of data and computational resources, significantly diminishing enthusiasm for collaborative learning participation and giving rise to the phenomena of ``isolated data islands''.
-On the other hand, PSs are troubled by the difficulty of promptly and accurately thwarting stealthy attackers hidden among a vast client base.
-This concern  (\textit{client nodes' reliability}) raises the specter of manipulation or even invalidation of the entire model, resulting in severe economic and intellectual property losses.
-
-%列举几个特点，导致现有安全技术不能适用
-%尽管多种最新的安全增强技术能够取得显著的防御效果，但攻击者并不能
-\subsection{Characteristics and motivation of mutual reliable FFL in heterogeneous UAV networks}
-With the advancement of integrated sensing, computation and communication (ISCC) \cite{he2023integrated}, and the space-air-ground integrated network (SAGIN) \cite{shen2023survey}, unmanned aerial vehicle (UAV) networks have played a crucial role in various domains such as post-disaster reconstruction, emergency temporary communication, and medical monitoring \cite{lu2023uav}.
-FLs based on UAV networks have also found widespread applications \cite{ETT1, ETT3, pandya2023federated}.
-However, despite the proposal of various secure FL technologies, the inherent characteristics of UAV networks continue to pose significant challenges in establishing mutual reliability for FFL in UAV environments.
-Specifically, these challenges encompass the following aspects:
-
-%异构：大范围异构，小范围相似.因此
-\textbf{1) Heterogeneity among UAV nodes:} As illustrated in Figure \ref{fig1:UAV-Network}, constrained by the mobility and patrol paths of UAVs, individual nodes are often limited to conducting data collection within a specific regional scope.
-Hence, even when employing identical equipment, the data distributions among UAV nodes across the entire network exhibit significant heterogeneity, while UAVs within the same area are similar.
-Therefore, various existing reliable FL technologies lacking adaptive considerations (such as Krum \cite{blanchard2017machine-krum}, Baffle \cite{andreina2021baffle}, and AGRamplifier \cite{gong2023agramplifier}) can lead to substantial accuracy losses.
-
-%资源受限：因此高消耗的安全策略并不能适用  高计算消耗和带宽占用的安全技术（例如，加密）
-\textbf{2) Resource limitation of UAV devices:} As UAV nodes function as mobile devices and bear substantial flight-related loads, their communication and energy resources are relatively constrained.
-The efficiency of FFL training is equally important.
-Consequently, solutions integrating cryptography, auxiliary training, multi-round detection, or other security mechanisms with high computational costs and bandwidth utilization (e.g., ShieldFL \cite{ma2022shieldfl}, AFA \cite{munoz2019byzantine-AFA}, and FLdetector \cite{zhang2022fldetector}) are not applicable for real-world deployment.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig1.PNG}
-\caption{FFL Illustration in Heterogeneous UAV Networks: Taking target recognition as an example, UAV node group patrolling in urban areas may collect a higher proportion of ``automobile'' samples (e.g., UN1 and UN2), while UAV groups patrolling in port areas will acquire more ``ship'' samples (e.g., UN6 and UN7).
-Consequently, the dataset distributions across the entire network often exhibit significant imbalance, while simultaneously displaying a certain degree of similarity within localized regions.
-}
-\label{fig1:UAV-Network}
-\end{figure}
-
-%我们的目标是实现（1）异构容忍的FFL框架（2）强隐私保护的个性化训练交互（3）抗污染的可信评估
-The aforementioned characteristics distinguish the reliable FFL in heterogeneous UAV networks from existing secure FFL technologies, thereby motivating the establishment of the following new criteria for its enhancement:
-
-\textbf{1) Heterogeneity-tolerant FFL framework:} Suitable nodes from the highly heterogeneous UAV networks can be organized promptly to efficiently fulfill arbitrary fairness-aware FL tasks, which also mitigates redundant computational energy consumption and accuracy loss induced by heterogeneity.
-
-\textbf{2) Privacy-preserving personalized training:} Throughout the iteration training and interaction process, sample-level privacy protection must be implemented to prevent the leakage of sensitive information.
-Additionally, considering the resource constraints of UAV nodes, computational and bandwidth demands should be limited.
-
-\textbf{3) Poisoning-resilient credit evaluation:} In addition to robust defense capabilities against various poisoning attacks, compatibility with heterogeneity and privacy requisites is also essential.
-In other words, without compromising the effectiveness of privacy guarantee, heterogeneous benign UAV nodes should be treated equally during the whole FFL workflow.%Achieving fairness among heterogeneous benign users without compromising the effectiveness of privacy protection is a crucial aspect.
-
-\subsection{Our solution and contributions}
-%解决方案
-% Hence, in this paper, we propose mutually reliable FFL (MR-FFL), a stratified community-based framework to facilitate privacy protection (FFL aggregator's reliability) and poisoning elimination (client nodes' reliability) jointly for FFL in heterogeneous UAV networks.
-% We first divide UAV nodes into both peer communities and colleague communities according to cross-participant similarity and task-oriented fitness, respectively. 
-% Thus, the arbitrarily settled learning tasks following fair principles can be efficiently completed by fine-tuned colleague communities, even in the presence of a large degree of heterogeneity among peer communities.
-Therefore, this paper proposes mutual reliable FFL (MR-FFL), a stratified community-based framework that collectively promotes privacy protection during data sharing (reliability of FFL aggregators) and poisoning elimination during model aggregation (reliability of client nodes) in heterogeneous UAV networks.
-The contributions of the proposed MR-FFL are three-fold:
-
-%贡献
-
-\begin{itemize}
-    %\item In light of shuffling-based MTD \cite{zhou2022multi} strategies, we propose a credit to identify the malicious attackers without compromising of privacy guarantees, which is also one of the design inspirations of our framework.
-    \item Initially, UAV nodes are partitioned into peer communities and colleague communities based on cross-participant similarity and task-oriented adaptability.
-Thus, adhering to fairness principles, any arbitrarily determined learning task can be effectively accomplished through carefully selected colleague communities, even in the presence of significant heterogeneity among UAV nodes, while peer communities provide an amplified privacy guarantee.
-    %随后，我们提出了PSDP的隐私模糊化方式进行自适应训练，通过参数动态约束差分隐私敏感度，从而在同等隐私保护水平下大幅降低异构环境下的噪声损失。
-    \item Subsequently, inspired by cross-silo privacy protection, we introduce the new privacy perturbation notion of peer community-specific differential privacy (PSDP) with changeable privacy budget.
-Through dynamically constraining the DP sensitivity within each peer community, PSDP significantly reduces noise loss in heterogeneous environments under equivalent privacy protection levels.
-    %此外，我们提出了基于三值主观逻辑模型的信用评估，分别抽离投毒攻击的“操纵”（相似度）和“破坏”（准确度）行为进行群体参与的综合长效评价，从而有效抵御多种隐蔽的投毒攻击范式。
-    \item Furthermore, we propose a new credit evaluation based on the ternary subjective logic model.
-This evaluation effectively integrates comprehensive and long-term assessments with the collective participation of heterogeneous UAV nodes, specifically extracting the ``manipulation'' (similarity) and ``disruption'' (accuracy) behaviors of poisoning attacks.
-This approach proves effective in defending against various covert poisoning attack paradigms.
-    %\item Then, we integrate community-specific differential privacy into the MR-FFL process, to achieve privacy amplification as well as efficient and personal collaborative training at the same time.
-    %\item More importantly, we proposed a community-based credit evaluation to resist poisoning attacks in heterogeneous environments.
-
-\end{itemize}
-
-%本文组织结构
-The remainder of this paper is organized as follows: The related works are reviewed in Section \uppercase\expandafter{\romannumeral2}.
-The system model is presented in Section \uppercase\expandafter{\romannumeral3}.
-Then, stratified community construction, adaptive training, and credit evaluation modules are expounded upon in Section \uppercase\expandafter{\romannumeral4} to \uppercase\expandafter{\romannumeral6}, respectively, providing a detailed account of availability, privacy, and integrity for FFL in heterogeneous UAV networks.
-Section \uppercase\expandafter{\romannumeral7} presents experimental results.
-Finally, Section \uppercase\expandafter{\romannumeral8} concludes this paper.
-%and briefly explores future directions.
-
-\section{Related work}
-
-% \begin{tabular}{|p{0.4\textwidth}|p{0.5\textwidth}|}
-% \hline
-% \textbf{论文的期刊名、年份、引用} & \textbf{简介} \\
-% \hline
-% 期刊名1, 2024, 引用1 & 这篇论文讨论了...... \\
-% \hline
-% 期刊名2, 2023, 引用2 & 本研究着重于...... \\
-% \hline
-% 期刊名3, 2022, 引用3 & 本文提出了...... \\
-% \hline
-% \end{tabular}
-
-According to the three basic tenets of information security \cite{zhou2021augmented-globecom}, in this section, we systematically review the most crucial hindrances of existing FFL solutions in UAV networks: \textit{availability}, \textit{confidentiality}, and \textit{in tegrity} problems, which we settled in following sections, respectively.
-\subsection{FFL in heterogeneous environments (availability)}
-To accomplish learning tasks and ensure the availability of FFL in heterogeneous environments, existing solutions can adopt debiasing on the client or server side.
-\subsubsection{Server-side debiasing} %全局化
-As the name indicated, server-side debiasing methods usually monitor the composition of training data and design new loss functions like Ratio loss \cite{wang2021addressing} to mitigate the impact of heterogeneity.
-Besides, FairFed \cite{ezzeldin2023fairfed} adjusts the aggregation weights of heterogeneous participants based on equal opportunity difference (EOD).
-Hence, clients can conduct different debiasing processes.
-Likewise, FedProto \cite{tan2022fedproto} regularizes the training of local models with the aid of abstract class prototypes from the server. 
-To handle the performance degradation caused by heterogeneous and long-tailed data, CReFF\cite{shang2022federated} re-trains the biased classifier with federated features in a privacy-preserving manner.
-Different from the above methods, several clustered FLs provide separate models for heterogeneous clients \cite{sattler2020clustered-CFL}, which can incur exponentially growing computation costs.
-\subsubsection{Client-side debiasing} %个性化
-Diverging from server-side debiasing, client-side debiasing methods primarily enhance accuracy by altering the local model \cite{tan2022towards}. 
-For example, while retaining the standard FL mechanism as the inner optimizer, FairBatch \cite{roh2020fairbatch} further adds an outer optimizer to select minibatch sizes and improve model fairness adaptively.
-Similarly, Ditto \cite{li2021ditto} develops a regular term to optimize the local models without changing global aggregation rules.
-The robustness and fairness are jointly improved.
-Moreover, Mohri \textit{et al.} \cite{mohri2019agnostic} propose agnostic federated learning (AFL) and prove its fairness using data-dependent Rademacher complexity guarantees.
-
-%总结：现有FFL有两大问题，首先是效率不佳，往往需要多轮训练，不适合于能量受限的UAV network。其次是缺乏考虑对联邦学习可信技术的兼容。
-To summarize, existing FFLs encounter two drawbacks.
-Firstly, they exhibit unsatisfactory efficiency, often necessitating multiple training rounds, rendering them unsuitable for energy-constrained UAV networks.
-Secondly, the consideration for compatibility with reliable technologies is insufficient.
-\subsection{Reliability of information sharing (confidentiality)}%隐私安全
-\subsubsection{Cryptography solutions} 
-Homomorphic encryption (HE) and other cryptographic methods naturally serve as suitable privacy protection measures.
-For instance, ShieldFL \cite{ma2022shieldfl} employs secure cosine similarity to measure the distance between two encrypted gradients, utilizing dual-gate HE to resist model poisoning.
-BatchCrypt \cite{zhang2020batchcrypt} further enhances HE efficiency by incorporating batch gradient encoding and holistic encryption, effectively reducing training time and communication overhead.
-Additionally, FairFL \cite{zhang2020fairfl} adopts the principled deep multi-agent reinforcement learning framework and secure information aggregation protocol to simultaneously optimize the accuracy and the fairness of FFL while respecting the strict privacy constraints of the clients.
-Besides, Lyu \textit{et al.} \cite{lyu2020towards} develop a local credibility mutual evaluation mechanism to guarantee fairness, and a three-layer onion-style encryption scheme to guarantee both accuracy and privacy.
-\subsubsection{Obfuscation solutions}
-
-In comparison to encryption, obfuscation approaches such as differential privacy (DP) do not introduce excessive overhead or extensive mechanism modifications, thus garnering significant attention \cite{padala2021federated}.
-For instance, Wei \textit{et al.} \cite{wei2021low} consider both general training performance and individual client privacy requirements to mitigate latency on wireless channels, addressing challenges posed by channel fading and interference in unknown network environments.
-Furthermore, considering potential model distortion from obfuscation techniques, privacy amplification as Shuffle \cite{girgis2021shuffled} can enhance the deployment capabilities of privacy protection.
-NbAFL \cite{wei2020federated-NbAFL} further diminishes the accuracy loss associated with DP by injecting secondary noise into the uplink and downlink channels.
-
-%总结：密码学方法通信量和计算量过大，而DP方法缺乏对异构考量
-Upon analysis, privacy-preserving information-sharing methods based on cryptography often incur excessive communication and computational overhead.
-On the other hand, methods relying on obfuscation like differential privacy lack adaptability to heterogeneous network environments, usually resulting in significant accuracy losses.
-\subsection{Reliability of model aggregation (integrity)}%model安全
-To resist the stealthy yet destructive poisoning attacks \cite{lyu2023poisoning}, multiple defense methods are proposed, which can be divided into the following types based on the realization concepts:
-\subsubsection{Mitigation-oriented technologies} 
-To ensure the integrity of the aggregated model, various robust FL methods, such as Byzantine-robustness, have been proposed.
-For instance, Krum \cite{blanchard2017machine-krum} selects partial neighboring nodes as references, enabling the algorithm to choose updates with the highest consensus for the next iteration.
-Diverging from Krum's approach of selecting only one update, FABA \cite{xia2019faba} employs gradient outlier computation to discard few gradients while retaining the majority of clients' training results, significantly enhancing learning speed.
-Building upon these methods, Gong \textit{et al.} devise AGRamplifier \cite{gong2023agramplifier}, which enhances the "morality" of local updates by identifying the most suppressive features in each gradient update.
-This augmentation further elevates model robustness, fidelity, and efficiency.
-
-\subsubsection{Detection-oriented technologies} 
-An alternative approach to fortify against poisoning is the direct detection of the learning model using a validation dataset or predefined rules.
-For instance, Zeno \cite{xie2019zeno} evaluates the stochastic descendant score for each gradient based on a validation dataset, selectively discarding gradients with low scores for the stochastic descendant.
-In contrast to relying on an auxiliary validation set, Baffle \cite{andreina2021baffle} capitalizes on the diverse datasets accessible across various clients by integrating a feedback loop into the FL process.
-Besides, Fldetector \cite{zhang2022fldetector} anticipates a client's model update during each iteration by leveraging historical model updates and flags a client as potentially malicious if the received model update contradicts the predicted update.
-It is noteworthy that detection-centric solutions entail additional training costs and may not identify some zero-day attacks.
-
-\subsubsection{Credit-oriented technologies} 
-%鉴于联邦学习是协作式、多轮次的交互过程，通过维护信用评价机制同样可以很好地清除恶意用户。例如，Kang等人使用多权重主观逻辑模型设计基于声誉的可靠联邦学习用户选择方案，并利用区块链实现声誉管理。在不需要辅助验证数据集的情况下，Xu等人提出余弦梯度Shapley值来评估每个智能体上传的模型参数更新/梯度的期望边际贡献，以区别对待。Tan等人提出了一种基于声誉感知的随机整数规划的FL客户选择方法，可以最优地选择和补偿具有不同声誉档案的客户，从而对抗潜在的异常行为。
-Considering that FL is a collaborative and iterative process, the credit evaluation mechanism proves effective in poisoning resistance.
-For instance, Kang \textit{et al.} \cite{credit1-kang2019IOT} design a reputation-based reliable scheme utilizing a multi-weight subjective logic model, and implement reputation management through blockchain.
-Xu \textit{et al.} \cite{xu2020reputation, xu2021gradient}, without the need for auxiliary verification datasets, introduced the cosine gradient Shapley value to assess the model parameter updates/gradients uploaded by each client.
-Tan \textit{et al.} \cite{tan2022reputation} propose a reputation-aware stochastic integer programming client selection method, selecting and compensating clients with varying reputation profiles to counter potential anomalous behavior.
-
-%总结：现有方案缺乏对隐私的考量，计算量过大
-In general, existing solutions often struggle to achieve a satisfactory balance between privacy and defensive performance, while also lacking adaptability to heterogeneous and dynamically changing environments.
-Furthermore, some methods exhibit relatively large computational overhead, imposing a non-negligible burden on UAV nodes.
-
-\section{System model} %\& Preliminaries}
-%%symbols 表格
-\begin{table}[!t]
-{
-\renewcommand{\arraystretch}{1.2}
-\caption{Summary of Main Notation}
-\label{notations}
-\vspace{0em}
-\centering
-\begin{tabular}{| c || l |}
-\hline
-\textbf{Symbol} & \multicolumn{1}{c |}{\textbf{Description}}\\
-    \hline
-    $U_i,\mathcal{D}_i$ & The $i$-th UAV devices and its dataset\\
-    \hline
-    $n^{s_{m}, i},\mathcal{P}^i$ & The size and normalized distribution of $\mathcal{D}_i$\\
-    \hline
-    $\mathcal{P}^{Tar}, w$ & Target distribution and model of learning task $Job$\\
-    \hline
-    $T$ & The maximum communication rounds of $Job$\\
-    \hline
-    $C,K$ & The set and number of all peer communities\\
-    \hline
-    $S,M$ & The set and number of all colleague communities\\
-    \hline
-    %$L$ & The number of clients in each super node\\
-    %\hline
-    $c_k$ & The $k$-th peer community\\
-    \hline
-    $s_m$ & The $m$-th colleague community\\ 
-    \hline
-    $\Delta \widetilde{\omega}_{t}^{s_{m},i}$ & The weight updates from $U_i \in s_m$ in round $t$\\
-    \hline
-    $p^{s_{m}, i}$ & The aggregation coefficient for $U_i$ within $s_m$\\
-    \hline
-    $\Delta\widetilde{\omega}_{t}^{s_{m}}$ & The weight updates from $s_m$ in round $t$\\
-    \hline
-    $p^{s_{m}}$ & The aggregation coefficient for $\Delta\widetilde{\omega}_{t}^{s_{m}}$ from $s_m$\\
-    \hline
-    $E_k$ & The clipping bound of peer community $c_k$\\
-    \hline
-    $Sen_k$ & The maximum sensitivity of $c_k$\\
-    \hline
-    $\varepsilon_k,\delta_k$& The parameters of differential privacy \\
-    \hline
-    $L$& The minimum size of colleague community\\
-    \hline
-    $\alpha^{a,b}_{t}$& The cosine similarity between $a$ and $b$\\
-    \hline
-    $PI^{c_k \rightarrow i}_{t}$ & The positive interaction between $c_k$ and $U_i$\\
-    \hline
-    $NI^{c_k \rightarrow i}_{t}$& The positive interaction between $c_k$ and $U_i$\\
-    \hline
-    $\Upsilon^{c_k \rightarrow i}_{t}$& The peer reputation opinion vector of $c_k$\\
-    \hline
-    $\Phi^{c_k \rightarrow i}_{t}$& $c_k$'s credit evaluation towards $U_i$ in round $t$\\
-    \hline
-    $\Upsilon^{s_m}_{t}$ & The colleague reputation opinion vector towards $s_m$\\
-    \hline
-    $\Phi^{s_m \rightarrow i}_{t}$& The colleague credit evaluation for $\forall U_i \in s_m$\\
-    \hline
-    $\Upsilon^{i}_{t},\Phi^{i}_{t}$& The comprehensive reputation and credit of $U_i$\\
-    \hline
-    $\psi^{i}_t$& The fairness-guaranteed selection probability\\
-    \hline
-    \end{tabular}
-        }
-     \vspace{-1.5em}
-     \end{table}
-
-\textbf{Heterogeneous UAV network scenario.} 
-%\subsection{Network scenario}
-%对于一个多无人机多任务联邦学习场景，有一个服务器与N个无人机，设无人机集合为$U=\{U_i\}$，$\vert\vert U\vert\vert=N$。所有无人机获取的数据集集合为$D=\{D_i\}$，第k个无人机的数据分布为$\mathcal{P}^k\in \mathbb{t}^F$，其中$F$为特征维度；任务场景集合为$T$，其中第k个任务场景中的数据分布为$\mathcal{P}^{tar_k}$。在同一现实场景中，无人机采集到的数据通常是类似的，即对于某个场景的分布$\phi$，所有属于该现实场景的设备集合$B'$均满足$\exists \epsilon\in \mathbb{t}^F,\forall k \in B', ||\phi-\mathcal{P}^k||_1 \leq \epsilon$。
-As shown in Figure \ref{fig1:UAV-Network}, assume a multi-UAV multi-task federated learning scenario for the classification problems.
-There exists a parameter server (PS)/aggregator (normally equipped with ground base station) and $N$ UAV nodes (UN) $\mathbf{U}\triangleq\{U_1,...U_i,...U_N\}$.
-Each UN $U_i$ has local dataset $\mathcal{D}_i\triangleq\{(\xi_{i,1},y_{i,1}),...(\xi_{i,j},y_{i,j}),...(\xi_{i,n_i},y_{i,n_i})|y\in \mathbb{R}^F\}$ sampled following distribution $\varphi_q$.
-%with varied size $n_i$.
-Here $x$ and $y$ are raw data and label, respectively.
-As the nodes with overlapped aerial areas or patrol routines may have similar data distributions, we have $\exists \epsilon\in \mathbb{R}^F,\forall U_i, U_j \sim \phi_q, ||\mathcal{P}^i-\mathcal{P}^j||_p \leq \epsilon^{\prime}$, where $\mathcal{P}^i$ is the normalized distribution of $\mathcal{D}_i$.
-For the highly heterogeneous networks, we also have $\exists U_i \sim \phi_{q^{\prime}}, U_j \sim \phi_q,||\mathcal{P}^i-\mathcal{P}^j||_p \gg \epsilon^{\prime}$ in the same time.
-
-%\subsection{Threat model}
-%值得一提的是，方便起见，我们此处仅以多分类问题中的数据类别作为公平性感知针对的对象，实际使用中可以通过特征extractor扩展到数据包含的任意抽象特征。此外，我们以范数差异度作为公平性衡量标准，实际应用中，也可以选取AIDD、DSF、SF等衡量方式并在特定方面取得更好的效果。
-It is crucial to highlight that, for better understanding, our focus in this paper is solely on the data distribution of multi-classification problems as the target for fairness awareness.
-In practical scenarios, this concept can be easily extended to any abstract features derived from specific demographic groups through feature extractor as exemplified in \cite{shuai2022balancefl}.
-Furthermore, our chosen metric for fairness evaluation is the norm difference.
-However, other alternative fairness measures such as QCID \cite{yang2021federated}, ratio loss \cite{wang2021addressing}, and cross-entropy loss \cite{mohri2019agnostic} can be employed, depending on specific requirements, to attain more favorable results.
-
-\textbf{Fairness-aware learning task.} Without loss of generality, the fairness-aware learning task can be denoted with the quadruple as $Job\triangleq(w,\mathcal{P}^{tar},t_0, T)$, which consists of the model $w$, target distribution $\mathcal{P}^{tar}$, arrival time $t_0$, and duration $T$.
-Different from existing solutions designed for certain $\mathcal{P}^{tar}$ \cite{li2022data,zeng2022heterogeneous,hiessl2022cohort}, our method can adaptively choose and schedule suitable UAV groups when a new learning task arrives.
-
-\textbf{Optimization objective.} We start with vanilla FL algorithms like FedAvg \cite{li2019convergence-fedavg} without consideration of heterogeneity.
-The optimization objective can be expressed as:
-%考虑一个联邦学习场景，有1个服务器和$N$个客户。具体来说，客户i的本地数据集为$D_{i}$，其类别分布被定义为$\mathcal{P}^{c_{k},i}$。不同客户的本地数据类别分布高度异构，与全局类别分布$\mathcal{P}^{real}$有巨大差距。为了最小化全局损失函数，得到普适的全局模型，我们有：
-\begin{equation}
-    w^{*}\triangleq \underset{w}{\arg \min } \sum_{i=1}^N p_i\mathcal{L}\left(w, \mathcal{D}_{i}\right) ,
-\end{equation}
-%其中，$\mathcal{L}_{i}(\cdot)$是客户i的由其本地经验风险得出的本地损失函数。然而，由于客户的数据间的高度异构性与客户数据分布与任务场景数据分布间的高度异构性，客户间的本地损失函数不尽相同，难以获得同时最小化各个模型经验风险的最优全局模型参数$w^{*}$并满足任务场景。因此，在上述场景中进行传统FL会导致全局模型无法正常收敛，无法得到满足任务场景的高性能全局模型。
-where $\mathcal{L}(.)$ represents the loss function derived from the local empirical risk of $U_i$, $p_i$ is the aggregation weight.
-Due to the high heterogeneity among UAV nodes and the substantial mismatch between participants' data distributions and task requirements, obtaining the globally optimal model parameters $\omega^{*}$ that simultaneously minimize the empirical risks of each model and align with task requirements is challenging.
-%Thus, traditional Federated Learning (FL) in such scenarios leads to the global model failing to converge effectively, resulting in an inability to obtain a high-performance global model that satisfies task scenarios.
-
-Hence, similar to the existing fair FL solutions in \cite{mohri2019agnostic,zhang2020fairfl,ezzeldin2023fairfed}, we define the optimization objective as follows:
-\begin{equation}
-    w^{*}\triangleq \underset{w}{\arg \min } \ \mathcal{L}_{FFL}(\omega)=\underset{(x, y) \sim \mathcal{P}^{Tar}}{\mathbb{E}}[\mathcal{L}{(\omega,(x, y))}]
-\end{equation}
-%（我这里想的是为了便于之后的凝聚聚类）此外，由于不同现实场景之间可能有较大的数据分布差异，与任务数据分布高度异构。为了最小化全局损失函数，得到适用于特定任务场景的全局模型，我们有：
-
-\section{Stratified community construction in heterogeneous environment}\label{sec:community}
-%为了实现高度异构的UAV节点集合与动态变化的学习任务之间的良好适配，我们提出了SCC。如图所示，该机制主要包含两个部分：PCC和CCC。其中PCC在网络初始化时运行一次，CCC则在每次收到新任务时运行一次。
-To achieve a robust alignment between highly heterogeneous UAV nodes and dynamically evolving learning tasks, we propose the stratified community construction (SCC) mechanism.
-As illustrated in Figure \ref{fig2:framework}, SCC comprises two main components: peer community construction (PCC) and colleague community construction (CCC).
-PCC executes once during network initialization, while the CCC executes each time a new task is received.
-\subsection{Peer community construction (PCC)}
-Based on norm-based pair distance, we first cluster UAV nodes with similar data distributions into $K$ peer community $C=\{ c_{1}, \ldots, c_{K} \}$. The pair distance is calculated as:
-\begin{equation}
-d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}, \forall U_i,U_j\in \mathbf{U}.
-\end{equation}
-
-%基于客户的数据分布$\mathcal{P}^{i},i\in B$。我们用最大链接法对客户进行层次凝聚聚类。两个簇间的距离为它们中任意两个客户分布之间曼哈顿距离的最大值，当簇间距离大于合并阈值$\zeta$时停止合并，得到最终的聚类结果。由此可知同簇的任意客户分布之间的最大曼哈顿距离小于$\zeta$, 即$\forall i,j \in c, d_{i,j}<\zeta$。
-Then, we employ the complete-linkage method to achieve agglomerative hierarchical clustering (AHC) among UAV nodes.
-The distance between two peer communities is defined as the maximum Euclidean distance between any two UNs' distributions.
-The clustering process ceases when the inter-community distance exceeds the merging threshold $\zeta$, resulting in the final outcome.
-Hence, the maximum distance between any pair of client distributions within the same PC is less than $\zeta$, i.e., $\forall U_i, U_j \in c_k, d_{i,j} < \zeta$, which is denoted as:
-\begin{equation}\label{eq:peer-construct}
- C\triangleq \underset{c_{1} \cup c_{2} \cup \ldots c_{K}=C}{\arg \min} \left(\max _{\forall c_{k},c_{k'} \in C ,U_i \in c_{k}, U_j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .
-\end{equation}
-
-%根据上述公式，我们得到具有相似类别分布的$K$个簇$C=\{c_{1},\ldots,c_{K}\}$。可以计算每个簇的平均数据分布，簇$c$的平均数据分布$\mathcal{P}^{c}$计算为：
-The average distribution of each peer community $c_k$ is:
-\begin{equation}
-    	 \mathcal{P}^{c_k}=\operatorname{norm}\left(\sum_{i \in c} n^{c,i} \mathcal{P}^{c,i} \right),
-\end{equation}
-%其中，$\mathcal{P}^{c,i}$是簇$c$中客户$i$的数据分布，$n^{c,i}$是簇$c$中客户$i$的数据量。为了保证隐私与数据安全，需要保证簇的个数，否则参与方将可能更容易推断出数据属于哪一簇。同时，当簇的数量较少时，每个簇代表的数据子集更大，这可能会导致更多的敏感信息聚集在同一簇中。如果某个恶意参与方能够成功识别并攻击一个簇，他们可能能够访问或推断出更多敏感信息，增加了数据泄露的风险。因此，需要添加约束：$K \geq \eta$，以确保隐私性。
-where $\mathcal{P}^{k,i}$ represents the data distribution of $U_i$ within cluster $c_k$, and $n^{k,i}$ denotes the size of $\mathcal{D}_i$. 
-To jointly ensure performance and security, it is imperative to control the number of peer communities.
-A large $K$ enhances the chance of attackers inferring the sensitive information.
-Conversely, a small $K$ may result in insufficient intra-community similarity, leading to a deterioration in learning performance.
-Therefore, the introduction of a constraint, $K \geq \kappa$, is essential.
-This constraint ensures a minimum size of peer community for privacy considerations.
-$\kappa$ can be adjusted by $\zeta$.
-
-\subsection{Colleague community construction (CCC)}
-After peer community construction, we further select suitable UAV nodes to form colleague communities $S\triangleq\{s_1, \ldots, s_{M}\}$ with desirable distribution $\mathcal{P}^{tar}$, which avoids the performance degradation caused by heterogeneity.
-
-\subsubsection{Problem formulation}
-As shown in Figure \ref{fig2:framework}, based on the requirements of task $job_i$, we first generate the ``\textit{template}'' $\mathbf{h}$ of the colleague community (i.e., required ratio of clients $h_k$ from each peer community $c_k$ in a colleague community $s_{m}$).
-$\mathbf{h}\triangleq\{h_{1}, \ldots, h_{K}\}$ is a vector to stipulate this composition.
-Then $M$ colleague communities are constructed accordingly by selecting UAV nodes from each $c_k$.
-Outlier $c_k$ with small sizes ($\vert\vert c_k\vert\vert< M$) are excluded to improve participation.
-
-The optimization problem can be defined as:
-\begin{equation}\label{eq:problem}
-\begin{aligned}
-\mathbf{h}^*\triangleq &\underset{\mathbf{h}}{\arg \min} \vert\vert \mathbf{h}\cdot\mathbf{P}-\mathcal{P}^{tar}\vert\vert_2 \\
-\text{s.t. }& \forall c_k \in C, h_k\leq b_k, \\
-&\sum_{i=1} ^K h_i\geq r,
-\end{aligned}
-\end{equation}
-where $\mathbf{P}$ is a $K \times F$ matrix to denote the average feature values for all peer communities.
-Every row $\mathcal{P}^{c_k}\in \mathbb{R}^F$ denotes the average feature values of one peer community.
-$\mathbf{B}\triangleq \{ B_{1}, \ldots, B_{K}\}$ denotes the size of all peer communities.
-
-\subsubsection{Problem transformation} As the above problem is an NP-C quadratic integer optimization problem \cite{murty1985some}, we want to further reduce it to a linear programming problem to meet the efficiency requirements of UAVs.
-%即将$\mathcal{P}^{c_k}$拆成$l_k=\lceil \log_2(b_k+1) \rceil$行，拆成的新行中，第$i,1\leq i <l_k$行$d_i=2^{i-1}\mathcal{P}^{c_k},e_{k,i}=2^{i-1}$，第$l_k$行为$(b_k-2^i+1)\mathcal{P}^{c_k},e_{k,l_k}=(b_k-2^i+1)$。新矩阵有$R=\sum_{i=1}^k l_i$行，将原$\mathcal{P}$矩阵二进制拆分为一个$R\cdot F$的矩阵$\mathcal{Q}$，将整数规划问题转化成了一个0-1规划问题。
-For each $c_k$, to remove the constraint $B_k$, we conduct binary split on $\mathcal{P}^{c_k}$ to get $l_k=\lceil \log_2(B_k+1) \rceil$ new rows.
-Hence, the new matrix has $R=\sum_{i=1}^k l_i$ rows.
-The problem becomes:
-
-\begin{equation}
-\begin{aligned}
-\mathbf{x}^*\triangleq &\underset{\mathbf{x}}{\arg \min} \vert\vert \mathbf{x}\mathcal{Q}-\mathcal{P}^{tar}\vert\vert_2 \\
-\text{s.t. } &\forall c_k \in C, x_i\in\{0,1\}, \\
-&\sum_{i=1} ^K h_i\geq r,
-\end{aligned}
-\end{equation} 
-where $\mathbf{x}$ can map to $\mathbf{h}$, i.e., $h_k = \sum _{i=1} ^{l_k} e_{k,i}x_{\sum_{j=1}^{k-1} l_j +i}$, and $e_{k,l_k}=(B_k-2^i+1)$.
-Hence, the above problem is equal to finding the minimum of $(\mathbf{x}\mathcal{Q}-\mathcal{P}^{tar})\cdot (\mathbf{x}\mathcal{Q}-\mathcal{P}^{tar})^T$ as:
-
-\begin{equation}
-\begin{aligned}
-\mathbf{x}^*\triangleq\underset{\mathbf{x}}{\arg \min}\ \mathbf{x}\mathcal{Q} &\mathcal{Q}^T\mathbf{x}^T-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+\mathcal{P}^{tar}\mathcal{P}^{tar^T}\\
-\text{s.t. }&\mathbf{x}\in\{0,1\}^R,\\
-&\sum_{i=1} ^K h_i\geq r.
-\end{aligned}
-\end{equation}
-
-We further introduce variable $z_{ij} \in \{0,1\}$ and have $z_{ij}\leq x_i$,$z_{ij}\leq x_j$,$z_{ij}\geq x_i+x_j-1$, to linearize the problem:
-
-\begin{equation}%\label{eq:problem}
-\begin{aligned}
-\min\ &\mathcal{Q}\mathcal{Q}^T\mathbf{y}-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+P^{tar}P^{tar^T}\\
-\text{s.t. }& \mathbf{x}\in\{0,1\}^R,
-\\
-&x_{ij}\leq x_i, x_{ij}\leq x_j, x_{ij}\geq x_i+x_j-1,
-\\&\sum_{i=1} ^K h_i\geq r.
-\end{aligned}
-\end{equation}
-
-Thus, the problem can be efficiently solved by linear programming solvers\footnote{For example, https://coin-or.github.io/pulp/}.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig2.PNG}
-\caption{Stratified community construction in a heterogeneous environment.}
-\label{fig2:framework}
-\end{figure}
-
-\section{Adaptive FFL training with privacy amplification}
-\subsection{Training workflow of MR-FFL}
-% 初始化过程: task generation & community initiation
-% Step 1: Local training
-% Step 2: Noise obfuscation
-% 中间过程: Upload gradient
-% Step 3: Inner-community aggregation
-% Step 4: Global aggregation
-% Step 5: Personalisation
-% 中间过程: Download model
-% Step 6: Local update
-
-As shown in Figure \ref{fig3:workflow}, the training workflow of MR-FFL mainly consists of the following steps in one round of iteration:
-
-\begin{itemize}
-    \item \textbf{Initialization:} Once the FFL task arrives, server conducts the CCC algorithm to quickly select $M$ colleague communities with similar average distributions near to $\mathcal{P}^{tar}$.
-    \item \textbf{Step 1:} First, each node $U_i \in s_m$ trains the current model with personal data to generate the local model $\omega_t^{s_m, i}$.
-    \item \textbf{Step 2:} Then, $U_i$ obfuscates the weights update $\widetilde{\omega}_{t}^{s_{m}, i}$ with differential private noise, and uploads it to the server.
-    \item \textbf{Step 3:} Colleague community aggregates $\widetilde{\omega}_{t}^{s_{m}, i}, \forall U_i \in s_m$ to generate a colleague model $\omega_{t}^{s_{m}}$.
-    \item \textbf{Step 4:} The server aggregates result $\omega^{s_k}$ from each colleague community $s_k \in S$ to get new global model.
-    \item \textbf{Step 5:} Besides, UAV peer community can maintain a personalized peer model $\omega_{t}^{c_{k}}$ to further improve local performance. 
-    \item \textbf{Step 6:} Finally, the global model is distributed to selected UAV nodes for the next round of training.
-\end{itemize}
-
-As Step 1, 2, and 6 aligns with existing secure FL training process \cite{wei2020federated-NbAFL,padala2021federated}, we focus on Step 3,4 and 5 subsequently.
-
-\subsubsection{Colleague community aggregation} 
-%为了尽可能地减小异构数据带来的模型方向的差异，以便更好地聚合普适的全局模型，在服务器聚合前，先在super node 内部聚合。也就是说，本地训练后，客户$i, i\in s_{m}$的加噪模型更新量$\Delta \widetilde{\omega}_{t}^{s_{m},i}$被上传到super node进行super node的内部同步。
-To reduce the canceling phenomenon caused by heterogeneous data and improve training efficiency,  we first aggregate all $\Delta \widetilde{\omega}_{t}^{s_{m}, i}$ within $s_m$ to generate more homogeneous weight updates $\Delta\widetilde{\omega}_{t}^{s_{m}}$ of colleague model $s_m$ before the global aggregation: %In other words, following local training, the perturbed model update quantity, denoted as $\Delta \widetilde{\omega}{t}^{s{m},i}$ for client $i$ where $i\in s_{m}$, is uploaded to the super node for internal synchronization before server-level aggregation.
-\begin{equation}
-    \begin{gathered}
-     \Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}
-     = \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i},
-     \end{gathered}
-\end{equation}
-where $p^{s_{m}, i}= {n^{s_{m}, i}}/{n^{s_{m}}}$ is aggregation coefficent, $n^{s_{m}}=\sum_{i \in s_{m}} n^{s_{m}, i}$.
-
-\subsubsection{Global aggregation} 
-Then, the server aggregates the learning results from all $s_m$ and updates the global model:
-\begin{equation}
-\widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}},
-\end{equation}
-where $p^{s_{m}}= \frac{n^{s_m}}{\sum_{s_{m} \in S} n^{s_m}}$, and $\widetilde{\omega}_{t}$ is the global model.
-The global aggregation iteratively executes $T$ rounds to complete the learning task $Job=(w,\mathcal{P}^{tar},t_0, T)$\footnote{The termination condition for the learning task can also be set based on accuracy $\epsilon^{\prime\prime}>0$ rather than a fixed number of rounds $T$, i.e., $\mathcal{L}_{FFL}(\omega_t)\leq \epsilon^{\prime\prime}$, by only modifying the quadruple to $(w,\mathcal{P}^{tar},t_0, \epsilon^{\prime\prime})$.}.
-
-\subsubsection{Peer community personalization} Finally, to further improve the performance on local datasets, we personalize the local model for peer community by adding the proximal term:
-\begin{equation}\label{eq:personal}
-\omega_{t}^{k} = \omega_{t-1}^{k} - \eta\left(\sum_{i=1}^{\vert\vert c_{k}\vert\vert}p^{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega_{t-1} \right)\right)
-\end{equation}
-    where $p^{c_k}= \frac{n^{s_m}}{\sum_{c_k \in C} \vert\vert c_k\vert\vert}$, $\eta$ is the learning rate, $\lambda$ is the regularization coefficient.
-The smaller $\lambda$, the more the local models $\omega_t^{k}$ can deviate from the (corrupted) global model $\omega_t$, achieving robustness at the expense of generalization \cite{li2021ditto}.
-
-In Algorithm \ref{algorithm1}, we present the pseudocode for the complete adaptive training process described above.
-It is evident from the algorithm that our approach only requires participants to provide distribution information, enabling significant improvements in efficiency, accuracy, and privacy in heterogeneous environments.
-Furthermore, our training method seamlessly integrates with the subsequently proposed credit evaluation mechanism.
-In cases where some attackers dishonestly report their information, the integrity of the model is still guaranteed.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig3.PNG}
-\caption{The workflow of MR-FFL.}
-\label{fig3:workflow}
-\end{figure}
-
-\subsection{Analysis of privacy amplification}
-
-Different from existing central differential privacy (CDP) or local differential privacy (LDP) methods, which inevitably introduce excessive large noise and thus deteriorate the learning performance in heterogeneous environments, inspired by \cite{liu2022privacy}, we propose a novel DP notion: \textit{community-specific differential privacy} (CSDP) for heterogeneous federated learning.
-The anonymity is achieved within a peer community instead of the whole UAV network, which significantly reduces privacy loss under the same DP guarantee.
-Each peer community can be assigned with different $\varepsilon_k$ and $\delta_k$ based on personal needs.
-
-\subsubsection{Noise calculation} We first calculate the noise scale needed for the MR-FFL workflow to achieve our $(\varepsilon_k,\delta_k)$-CSDP.
-Assume a pair of neighbor datasets $\mathcal{D}^{s_{m}, i}_{t}$ and $\mathcal{D}^{s_{m}, i'}_{t}$ sampled from same $s_m$ with size $n^{s_{m}, i}$, there is only one pair of nonidentical samples $\xi^{i}_{t}$ and $\xi^{i\prime}_{t}$ within the neighbor datasets.
-The $l_2$ norm-based sensitivity can be calculated as:
-
-\begin{equation}
-     \begin{aligned}
-    \Delta F&=\max _{\xi^{i}_{t},\xi^{i\prime}_{t}}\left\|F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i}_{t}\right) -F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i'}_{t}\right)\right\|\\
-    &\leq \frac{n^{s_{m},i}}{n^{s_{m}} M}\left(  \max \left\| \Delta\omega_{r,t}^{s_{m},i}\right\|   + \max  \left\| \Delta\omega_{r,t}^{s_{m},i}\right\| \right)
-     \end{aligned}
-\end{equation}
-
-The second inequality can be deduced through a similar analysis as in \cite{wei2020federated-NbAFL}. We omit the specific process for simplicity. 
-After DP weights clipping \cite{abadi2016deep}, assuming an equal volume of data for clients and a minimum node count $L$ ($L\geq r$) within the colleague community, we have the best sensitivity as:
-\begin{equation}
-    Sen_k=\max _{i \in c_{k}}\left\{\Delta f\right\} \leq \frac{2 E_{k}}{L M},
-    \end{equation}
- where $E_k$ is the clipping bound of $c_k$.
-The standard deviation of the Gaussian noise to achieve $(\varepsilon_k,\delta_k)$-CSDP is:
-\begin{equation}
-    \sigma_{k}=\frac{\ell_{k} Sen_k }{\varepsilon_{k}}=\frac{2 \ell_{k} E_{k}}{L M\varepsilon_{k}},
-    \end{equation}
-where constant $\ell_{k} =\sqrt{2 \ln (1.25 / \delta_{k})}$ \cite{dwork2014algorithmic}.
-
-\subsubsection{Privacy analysis}
-
-%我们假设客户的类别分布$\mathcal{P}^{c_{k}}$符合高斯分布$\varphi_{c_{k}} $，即客户类别以方差$\sigma_{c_{k}}^{2}$正态分布在簇心$\mu_{c_{k}}$周围，即簇$c_{k}$的类别分布可以用$\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$的高斯分布表示。
-We assume that the data distribution of the UAV clients, denoted as $\mathcal{P}^{c_{k}}$, follows a Gaussian distribution $\varphi_{c_{k}}$, where the data are normally distributed around the community center $\mu_{c_{k}}$ with a variance of $\sigma_{c_{k}}^{2}$.
-In other words, the data distribution of community $c_{k}$ can be represented by a distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$ \cite{wei2020federated-NbAFL}.
-%对于某一簇$c_{i}$,整体类别分布符合高斯分布$\varphi_{c_{i}} \sim \mathcal{N}\left(\mu_{c_{i}}, \sigma_{c_i}^{2}\right)$，从中随机抽取任意客户$\forall i,i'\in c_{i}$，客户类别分布也符合$\varphi_{c_{i}}$。
-For a specific peer community $c_{k}$, the overall data distribution follows distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_i}^{2}\right)$.
-Hence, selecting any UAV client $\forall i,i'\in c_{k}$ from it, the client's distribution also follows $\varphi_{c_{k}}$ \cite{wei2021low}.
-
-%由公式（9）可知，在本地训练中，客户最小化本地经验风险得到的梯度与客户的本地数据有关，且客户梯度间的最大距离与数据分布的分散程度正相关，可以得到簇$c_{i}$客户梯度间的最大距离：
-As indicated by \cite{sattler2020clustered-CFL}, it is evident that in local training, the gradient obtained by a client, which minimizes the local empirical risk, is related to the client's local data.
-The maximum distance between client gradients is positively correlated with the dispersion of the distribution.
-Consequently, the maximum distance between gradients of nodes within peer community $c_{k}$ can be derived as $\max_{i,i'\in c_{k}} \left\| \Delta\omega_{t}^{c_{k},i}-\Delta\omega_{t}^{c_{k},i'}\right\| \simeq \sigma_{c_k}$.
-
-%super node按照数量$n=[n_{1},\ldots,n_{k},\ldots,n_{K}],  n_{k} \in \mathbb{N}$从簇$\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中选择$L$个客户:$\sum^{K}_{k=1} n_{k}=L$。通过卷积求和上述簇分布，可以得到super node 的类别分布$\varphi_{s}$：
-We choose UAV nodes from each peer communities $c_{k},\forall c_k \in C$ to constitute colleague communities according to composition vector $\textbf{h}=[h_{1},\ldots,h_{k},\ldots,h_{K}],  h_{k} \in \mathbb{N}$.
-Hence, by convolution summation among those peer distributions, we can obtain the distribution of colleague communities $\varphi_{s}$ as:
-
-\begin{equation}    \varphi_{s}=h_{1}\varphi_{c_{1}}\oplus\ldots\oplus h_{k}\varphi_{c_{k}}\oplus\ldots\oplus h_{K}\varphi_{c_{K}}
-\end{equation}
-
-%因为簇分布$\varphi_{c_{k}} \forall c_{k} \in C$是相互独立的高斯分布，可以得到上述簇分布的卷积和。
-As $\varphi_{c_{k}}, \forall c_{k} \in C$ are i.i.d.
-Gaussian distributions, we have $\varphi_{s} \sim \mathcal{N}\left(\mu_{s}, \sigma_{s}^{2}\right)$, where $\mu_{s}=\sum_{k}^{K} h_{k} \mu_{c_{k}}$, $\sigma_{s}^{2}=\sum_{k}^{K} h_{k}^{2} \sigma_{c_k}^{2}$.
-Define the maximum distance between weight updates of two UAV nodes $U_i$ and $U_{i^{\prime}}$ from the same colleague community $s$ as $\max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\| \simeq \sigma_{s}$.
-As $\sigma_{s}=\sqrt{\sum_{k}^{K} h_{k}^{2} \sigma_{c_k}^{2}}$, easy to prove $\sigma_{s}\geq\sigma_{c_{k}}, \forall c_k \in C$.
-Then, we have:
-\begin{equation}
-    \max_{i,i'\in c_{i}} \left\| \Delta\omega_{t}^{c_{i},i}-\Delta\omega_{t}^{c_{i},i'}\right\|\leq \max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\|.
-\end{equation}
-
-%根据敏感度的定义，可知在super node 中计算supernode内的敏感度将远大于簇内的敏感度。
-According to the definition of sensitivity, our peer community-specific $Sen_k$ and noise scale is much smaller than existing global-wide or colleague-wide DP methods.
-Hence, to achieve the same FFL performance, the clipping bound of our method is also much smaller, which requires less obfuscation.
-
-\begin{comment}
-
-\subsection{Analysis of personalization}
-在$K$个簇$C=\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中，每个簇$c_{k}$有相同的客户数$n$。$X^k \triangleq\left\{\omega^{k, i} \in\right.\mathbb{t}\}_{i \in[n]}$，且客户模型以方差$\upsilon^{2}$正态分布在簇心$\omega^{k}$周围，即$\omega^{k, i}=\omega^{k}+z^{k, i}$,其中$z^{k, i} \sim \mathcal{N}\left(0, \upsilon^{2}\right)$。具体来说，为了量化簇的异质性，我们假设簇心$\{\omega^{k}\}_{k \in \left[K\right]}$也以方差$\tau^{2}$正态分布在未知的固定元中心$\theta$周围,即$\omega^{k}=\theta+z^{k}$,其中$z^{k} \sim \mathcal{N}\left(0, \tau^{2}\right)$。其中，$\tau$表示簇心间的分散程度，$\tau$越大，簇越分散，整体分布的异构性越高。在此基础上，簇$c_{k}$为其中客户选择隐私预算$(\varepsilon_{k},\delta_{k})-DP$以最小化整体的泛化误差。每个簇$k$具有不同的裁剪边界$C_{k}$，并以$\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$的标准差在本地客户上传的模型加噪,在此基础上，簇$c_{k}$的优化目标可以表示为：
-\begin{equation}
-h_k(\omega)=\tilde{F}_k(\omega)+\frac{\lambda}{2}\|\omega-\omega^{g}\|_2^2
-\end{equation}
-其中，$\tilde{F}_k(\omega) \triangleq \frac{1}{2}\left(\omega-\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i} \cdot \min \left(1, C_{k} /\left\|\omega^{k, i}\right\|_2\right)\right)\right)^2$是簇$c_{k}$的优化目标，簇$c_{k}$客户梯度加噪大小为$\xi^k \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$。由于数据是亚高斯的，我们可以选择裁剪的边界$C_{k}$避免引入削波误差。因此，簇$c_{k}$的最优本地优化结果为$\widehat{\omega}^k \triangleq \operatorname{argmin} \tilde{F}_k(w)=\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i}\right)$。由于服务器聚合全部参与客户的模型而客户分布在各簇中，因此可得$\omega^{g}=\frac{1}{Kn} \sum_{k=1}^{K}\left(\xi^k+\sum_{i=1}^{n}\omega^{k,i}\right)=\frac{1}{K}\sum_{k=1}^{K}\widehat{\omega}^{k}$。由此可得簇$c_{k}$外各簇的平均估计结果$\widehat{\omega}^{\backslash k}=\frac{1}{K-1}\sum_{j \neq k}\widehat{\omega}^{j}$。
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{algorithm}[!t]% !t top !b bottom !h right here !p float pages
-\caption{Adaptive training with privacy amplification}
-\label{algorithm1}
-	\begin{algorithmic} [1]
-    \State \textit{\textbf{ Input: }Learning task $Job\triangleq(w^0,\mathcal{P}^{tar},t_0, T)$; Maximum
-local training iterations $R$; all participant UAV nodes $\mathbf{U}$ and their local dataset $\mathcal{D}_i$.}
-    \State \textit{\textbf{Output: }The global FFL model $\omega$ for task $Job$, personalized local models $\{ \omega^{k}\}_{k \in [K]}$} for peer communities.
-            \State \textbf{Initialize:} $w^{0}_{i} \leftarrow\ w^{0}$%,$\mathcal{P}^{real}=\operatorname{norm}\left(\sum_{i \in B} N^{i} \mathcal{P}^{i} \right)$
-            %\State {\color{CadetBlue}/* \textbf{Peer community construction */} } 
-            %\State $d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}$
-            %\State $C=\{ c_{1}, \ldots , c_{K} \} \leftarrow \arg \min _{c_{1} \cup c_{2} \cup \ldots c_{K}=C}\left(\max _{\forall c_{k},c_{k'} \in C ,i \in c_{k}, j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .$
-            \State Construct $C=\{ c_{1}, \ldots , c_{K} \}$ with Eq. (\ref{eq:peer-construct});
-             %\For { $r \in 1, \cdots, R$}
-                %\State{\color{CadetBlue} /* \textbf{Initialization} */} %$S \leftarrow Select-Clients()$}
-            \State Calculate composition vector $\mathbf{h}$ by Eq. (\ref{eq:problem}) for $Job$;
-            \State Construct colleague communities as $S^t=\{s_{1}, \ldots , s_{M}\}$ according to template $\mathbf{h}$;
-                \For {each colleague community $s_{m}$ in $S^{t}$ in parallel }
-                    \For {each UAV node $U_i$ in $s_{m}$ in parallel}
-                        \State {\color{CadetBlue}/*\textbf{Local Training*/}} 
-                        %\State $\omega_{t}^{s_{m},i} \leftarrow \omega_{t-1}^{s_{m},i}-\frac{\eta}{NI^{s_{m},i}} \nabla_\omega \mathcal{L}_{s_{m},i}\left(\omega_{t-1}^{s_{m},i}, \mathcal{D}^{s_{m},i}_{t}\right)$
-                        \State Update $\omega_{t}^{s_{m},i}$ with $\mathcal{D}_i$ for $R$ iterations;
-                        \State $\Delta \omega_{t}^{s_{m},i}=\omega_{t-1}^{s_{m},i}-\omega_{t}^{s_{m},i}$;
-                        \State{\color{CadetBlue}/* \textbf{Privacy obfuscation */}} 
-                        %\State \textbf{DP:} client $i \in c_{k}$, guarantee ($\varepsilon_{k}$,$\delta_{k}$)-DP
-                        \State Calculate noise $z^{k} \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$, $\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$;
-                        \State $\Delta \widetilde{\omega}_{t}^{s_{m},i}=\Delta \omega_{t}^{s_{m},i}+z^{k}$;
-                    \EndFor
-                    \State{\color{CadetBlue}/* \textbf{Colleague community aggregation */}} 
-                    \State $\widetilde{\omega}_{t}^{s_{m}} \leftarrow \widetilde{\omega}_{t-1}^{s_{m}} -  \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i}$;
-                    \State $\Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}$;
-                \EndFor
-                \State {\color{CadetBlue}/* \textbf{Global aggregation */}}
-                \State $\widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$;%$\widetilde{\omega}_{t} \leftarrow \widetilde{\omega}_{t-1} - PI^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$
-                \State{\color{CadetBlue}/* \textbf{Peer community personalization */}}
-                    \State Update the personalized model $\omega_{t}^{k}$ for each peer community $c_k$ with Eq.
-(\ref{eq:personal});%$\omega_{t}^{k} \leftarrow \omega_{t-1}^{k} - \eta_{c_{k}}\left(\sum_{i=1}^{n_{c_{k}}}p_{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega^{g}_{t-1} \right)\right)$
-                    %\State Update $\omega_{t}^{k}$
-            % \EndFor
-\State \Return $w^g,\{w^k\}$
-\end{algorithmic}
-\end{algorithm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Community-based credit evaluation of UAV nodes}
-In this section, we design a community-based credit evaluation method with a modified three-valued subjective logic model (SLM) \cite{al2021subjective}, to eliminate malicious attackers hiding in heterogeneous UAV networks.
-By integrating credits from both similarity-dominated intra-community (peer) and performance-dominated inter-community (colleague), multiple poisoning paradigms can be efficiently thwarted.
-\subsection{Similarity-dominated peer credit evaluation}
-%首先，同一community内的用户在训练过程中上传的weights往往相似性较高。因此，通过社区内相似度比较，可以快速识别出离群的恶意用户。
-UAV nodes' weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ within the same peer community $c_k$ often exhibit a high degree of similarity during the training process.
-Therefore, by leveraging community-based similarity, one can promptly identify malicious nodes that deviate significantly from the average norm.
-
-\subsubsection{Basic setting}
-For $\forall U_i \in c_k$, we first calculate the cosine similarity $\alpha_{c,i}^{t} \in [-1,1]$ between weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ from $U_i$ and average weight updates $\Delta\widetilde{\omega}^{c_k}_{t}$ from its peer community $c_k$:
-\begin{equation}
-    	  \alpha^{c_k,i}_{t} = \alpha( \Delta\widetilde{\omega}^{c_k}_{t-1}, \Delta\widetilde{\omega}^{i}_{t}) = \frac{\langle \Delta\widetilde{\omega}^{c_k}_{t-1},\Delta\widetilde{\omega}^{i}_{t}\rangle}{\Vert \Delta\widetilde{\omega}^{c_k}_{t-1}\Vert\cdot\Vert \Delta\widetilde{\omega}^{i}_{t}\Vert },\forall c_k \cap S.
-\end{equation}
-
-We further define the positive interaction $p^{c \rightarrow i}_{t} \in [0,2]$ as:
-\begin{equation}
-    	 PI^{c_k \rightarrow i}_{t} = \alpha^{c_k,i}_{t} -(-1),
-\end{equation}
-and the negative interaction $n^{c_k \rightarrow i}_{t} \in [0,2]$ as:
-\begin{equation}
-    	 NI^{c_k \rightarrow i}_{t} = 1-\alpha^{c_k,j}_{t}.
-\end{equation}
-
-%在FL的过程中，客户与簇的交互作用影响客户的信誉评估。诚实的交互行为将为客户的信誉评估带来正向的影响，具有攻击性的或不诚实的交互则会降低客户的信誉评分。我们分别用系数$b$和$c$表示内客户间正负交互作用对信任评价的影响比例，其中，$b>0,c>0$ 且 $b+c=1$。为了惩罚恶意客户，我们为客户间的负面交互设置更大的权重,即$b>c$。
-During the FFL process, benign behaviors positively impact the reputation assessment, while aggressive or deceptive interactions diminish the client's reputation.
-We use coefficients $b$ and $c$ to quantify the impact of positive/negative interactions in credit evaluation, respectively.
-$b>0$ and $c>0$, $b+c=1$.
-To penalize malicious UAV nodes, we assign a greater weight $b>c$ to negative interactions among clients.
-Hence, we obtain the temporary three-valued peer reputation opinion \cite{liu2019trust} vector $\Upsilon^{c_k \rightarrow i}_{t,temp}\triangleq \{b^{c_k \rightarrow i}_{t,temp}, d^{c_k \rightarrow i}_{t,temp}, u^{c_k \rightarrow i}_{t,temp}\}$ based on SLM as:
-\begin{equation}
-\Upsilon^{c_k \rightarrow i}_{t,temp}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{bPI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
-        d^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{cNI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
-        u^{c_k \rightarrow i}_{t,temp}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}},                
-    \end{array}
-\right.
-\end{equation}
-%$ \sigma_{c}$为簇c中满足$\varepsilon-DP$所加噪声的标准差，体现了根据客户上传加噪梯度计算可信度的不确定性，$ \sigma^{C}_{max}$和$\sigma^{C}_{min}$分别是所有簇$c\in C$中为满足$\varepsilon-DP$所添加的最大噪声和最小噪声。
-where the standard deviation $ \sigma_{c_k}$ of peer community $c_k$ depicts the uncertainty in the credit calculation based on the noisy $\Delta\widetilde{\omega}^{c_k}_{t}$ to achieve DP guarantee.
-$ \sigma_{max}=\max_{c_k \in C}{\sigma_{c_k}}, \sigma_{min}=\min{c_k \in C}{\sigma_{c_k}}$.
-%Furthermore, $ \sigma^{C}{max}$ and $ \sigma^{C}{min}$ denote the maximum and minimum noise added, respectively, among all clusters $c\in C$ to satisfy $\varepsilon-DP$.
-Besides, $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp}$ denote \textit{belief}, \textit{disbelief}, and \textit{uncertainty}, respectively.
-We have $b^{c_k \rightarrow i}_{t,temp}+d^{c_k \rightarrow i}_{t,temp}+u^{c_k \rightarrow i}_{t,temp}=1$ and $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp} \in [0,1]$.
-
-Then $c_k$'s temporary credit evaluation towards UAV $U_i$ is:
-\begin{equation}
-\Phi^{c_k \rightarrow i}_{t}=b^{c_k \rightarrow i}_{t} + a u^{c_k \rightarrow i}_{t}, \forall c_k \cap S,
-\end{equation}
-%其中$a\in[0,1]$是信誉不确定影响程度的系数。基于上式，根据客户的信誉度可以更明显地区分出恶意客户，从而抑制客户间的负面交互。
-where $a\in[0,1]$ is a coefficient regulating the importance of uncertainty. 
-Based on the above equation, malicious clients can be distinctly distinguished via reputation scores, thereby mitigating negative interactions among clients.
-
-\subsubsection{Long-term consideration}
-%在r个同步轮次内，客户的信誉不总是一成不变的。由于客户的信誉随着时间的推移而变化，我们考虑客户间历史信誉的影响。定义信誉的时间衰减因子为：
-During the iterative training, clients' reputations may not remain constant.
-Some sophisticated attackers even take advantage of this phenomenon and conduct more stealthy poisoning behaviors \cite{credit1-kang2019IOT}.
-Therefore, we take into account the influence of historical reputation.
-The time decay factor $v_{\tau}$ is defined as:
-\begin{equation}
-v_{\tau}=\frac{1}{e^{\iota(Y-\tau)}}=e^{-z(Y-\tau)},
-\end{equation}
-%其中$z>0$为冷却系数, $\tau \in [1,Y]$为历史交互时间的时隙,在内部通信中当前时隙$Y=r$。由于过于久远的信誉的时间衰减因子接近0，并且考虑到信誉交互中的内存与计算成本，我们只保留$\vert Y-\tau \vert \leq T$的历史信誉 ,即只记录并维护距离当前通信轮次的$T$轮历史信誉$\Phi^{c \rightarrow i}_{\tau}$。公式(7)表示，越接近当前同步轮次的信誉的时效性越高，即更相信近期交互的信誉度，而不是历史交互。
-where $\iota>0$ is the cooling coefficient, $\tau \in [1,Y]$ represents the time slot of historical interaction, and $Y$ in the current time slot of internal communication.
-Since the time decay factor for too-old reputations approaches 0, and considering the memory and computational costs in reputation interactions, we set an expiration threshold and retain only $T$ historical reputations $\Phi^{c_ \rightarrow i}_{\tau}$, i.e., $\vert Y-\tau \vert \leq T$.
-%Formula (7) indicates that reputations closer to the current synchronization round are more timely, placing higher trust in recent interactions rather than historical ones.
-
-\subsubsection{Stability consideration} 
-%\item \textbf{更新：}在联合学习的迭代交互$r\in[1,R]$中，服务器选择参与本地训练的随机客户子集为$Set_{t}$,在第$r$轮迭代中，只有集合$Set_{t}$中的客户上传模型更新量并彼此交互评估信誉。然而，由于参与训练和客户数量远少于客户总数,即$\vert Set_{t}\vert \ll N$，当前轮次的评估结果不足以给出完整的评估结果。因此，我们使用每个客户端的最新信誉更新值来更新其当前信誉值。设$\left\{ \Phi^{c \rightarrow i}_{t} \right\}_{i}^N$表示在服务器上维护的每个客户的簇内直接信誉。在每一轮交互后，全部客户执行以下更新操作：
-Moreover, as only chosen UAV nodes $U_i\in S$ participate in the FFL at round $t$, cross-slot reputation values can have erratic fluctuation or asynchronous obsolescence problems.
-Hence, inspired by \cite{jhunjhunwala2022fedvarp}, We introduce the momentum term to the reputation updating as:
-\begin{equation}
-\Upsilon^{c_k \rightarrow i}_{t}=
-\left\{\begin{array}{ll}
-\Upsilon^{c_k \rightarrow i}_{t} ,& \text { if } U_i \in S\\
-\Upsilon^{c_k \rightarrow i}_{t-1},& \text { otherwise }
-\end{array}\right.
-\end{equation}
-
-%在训练开始前，初始化所有客户$\forall i \in [N]$的信誉评价$\Upsilon^{c \rightarrow i}_{0}$可以表示为：
-%可以看出我们提供较高的初始信誉并保证非参与客户历史信誉的连续性。
-Then, in the initialization phase $t=0$, we have:
-\begin{equation}
-\Upsilon^{c_k \rightarrow i}_{0}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{c_k \rightarrow i}_{0}=1-u^{c_k \rightarrow i}_{0},\\
-        d^{c_k \rightarrow i}_{0}=0,\\
-        u^{c_k \rightarrow i}_{0}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}
-      \end{array}
-\right.
-\forall U_i\in c_k.
-\end{equation}
-
-%上式确保了客户簇内直接信誉的实时性，即维护了包括参与和非参与交互客户在内的全部客户的当前信誉均为其最近的信誉更新值。
-The above design ensures the stability of credit evaluation for both participating and non-participating UAV nodes in the current round.
-
-By integrating both stability and long-term consideration, we obtain the final peer reputation opinion: 
-\begin{equation}
-\Upsilon^{c_k \rightarrow i}_{t}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} b^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
-        d^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} d^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
-        u^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} u^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}  ,              
-    \end{array}
-\right.
-\forall U_i\in c_k,
-\end{equation}
-%第r轮同步，簇$c$中客户i的信誉评价为：
-and $c_k$'s credit evaluation towards UAV node $U_i$ at round $t$:
-\begin{equation}
-\Phi^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} \Phi^{c \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}, \forall U_i\in c_k.             
-\end{equation}
-
-\subsection{Performance-dominated colleague credit evaluation}
-Performance-dominated colleague credit evaluation generates the general judgment $\Phi^{s_m}_{t}, \forall s_m\in S$ from other colleague communities. 
-As colleague communities are regrouped after every iteration, different from peer credit, colleague credit pays more attention to comprehensive consideration of both performance and similarity between $s_m$ and $s_{m^{\prime}}, \forall s_{m^{\prime}} \in S_{\neg s_m}$.
-
-Hence, we first calculate the similarity between $s_m$ and $s_{m^{\prime}}$:
-\begin{equation}
-    	  \alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega}^{s_{m}}_{t},  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}) = \frac{\langle  \Delta\widetilde{\omega}^{s_{m}}_{t}, \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\rangle}{\Vert  \Delta\widetilde{\omega}^{s_{m}}_{t}\Vert\cdot\Vert  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\Vert }.
-\end{equation}
-
-The positive and negative interactions are $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$ and $NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$, respectively.
-$PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} + NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 2$.
-
-Thereafter, the \textit{belief} $b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u_t^{s_{m} \rightarrow s_{m^{\prime}}})\frac{bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$
-\textit{disbelief} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u^{s_{m} \rightarrow s_{m^{\prime}}}_{t})\frac{cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$ and \textit{uncertainty} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=\Vert PI^{s_{m}}-PI^{s_{m^{\prime}}}\Vert/2.$$
-
-For round $t$, the reputation opinion vector can be defined as follows:
-
-\begin{equation}
-\Upsilon^{s_m}_{t}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  b^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
-        d^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  d^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
-        u^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  u^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},
-    \end{array}
-\right.
-\end{equation}
-where $\rho^{s_m}_{t}=acc^{s_m}_{t}$ is the accuracy of colleague community $s_m$.
-From the perspective of model security, we assign lower weights to attackers who dishonestly report data distributions based on the model accuracy $acc^{s_m}_{t}$ of $s_m$.
-Therefore, as the model accuracy $acc^{s_m}_{t}$ increases, the weight assigned to $s_m$ also increases, making the reputation opinion from $s_m$ more reliable.
-
-The final colleague credit evaluation for $\forall U_i \in s_m$ can be calculated as:
-\begin{equation}
-\Phi^{s_m \rightarrow i}_{t}=\Phi^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{(\rho^{s_{m^{\prime}}}_{t} b^{s_{m^{\prime}} \rightarrow s_{m}}_{t}+ a u^{s_{m^{\prime}} \rightarrow s_{m}}_{t})}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},
-\end{equation}
-
-\subsection{UAV nodes selection with comprehensive
-community-based credit}
-\subsubsection{Comprehensive community-based credit} 
-Finally, by merging peer credit and colleague credit evaluation results, we can obtain comprehensive evaluations of participant UAV nodes based on similarity and performance jointly. 
-The comprehensive reputation opinion $\Upsilon^{i}_{t}$ can be calculated by conducting consensus mechanism between $\Upsilon^{c_k\rightarrow i}_{t}$ and $\Upsilon^{s_m\rightarrow i}_{t}$ as:
-\begin{equation}
-\Upsilon^{i}_{t}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{i}_{t}=\frac{b^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+b^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
-        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
-        d^{i}_{t}=\frac{d^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+d^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
-        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
-        u^{i}_{t}=\frac{u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}
-        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}         
-    \end{array}
-\right.
-\end{equation}
-
-%因此，可得客户 $j$ 的综合信任度为：
-The comprehensive community-based credit of $U_i$ is: 
-\begin{equation}
-\Phi^{i}_{t}=b^{i}_{t}+a u^{i}_{t}
-\end{equation}
-
-%通过上述信誉评估过程，服务器可以从簇和super node两个维度综合选择具有高性能和可靠数据的高信誉候选客户作为联邦学习任务中的参与者。该方法能够与FEDGS框架紧密结合，在FEDGS内部同步和外部同步的过程中分别从簇内和super node间评估客户信誉，将信誉评估细化到每轮迭代中，能够及时发现并排除攻击者，尽可能地减少其对联合学习的干扰。
-
-Similar to peer credit evaluation, the updating rule of $\Phi^{i}_{t}$ is also designed with stability consideration as follows:
-%\textbf{更新：}第$r$轮迭代，被选中参与联合学习的客户集合为$Set_{t}$。设$\left\{ \Phi^{i}_{t} \right\}_{i=1}^N$表示维护的第$r$轮每个客户的综合信誉。在迭代学习的过程中，对于未被选中构建supernode并参与训练的客户，保持其最近轮次的信用评分，并根据最近的综合信任度计算其下一轮次的选择概率：
-\begin{equation}
-\Phi^{i}_{t}=
-\left\{\begin{array}{ll}
-\Phi^{i}_{t} & \text { if } i \in Set_{t} \\
-\Phi^{i}_{t-1}& \text { otherwise }
-\end{array}, \text { for all } i\in[N]\right.
-\end{equation}
-
-\textbf{Resistance ability against collusion attack:} 
-%当攻击者拥有多个compromised节点时，多个节点可以进行共谋攻击。MR-FFL可以通过简单的设置实现对共谋攻击的阻断。具体来说，在MR-FFL中，攻击者可以采取“集中合谋”或者“分散合谋”策略：（1）分散合谋的攻击者上报不同的数据分布，从而隐藏进不同的异构Peer社区中。显然，这一策略面对传统防御方法或许能够实现绕过，面对MR-FFL时则会被社区内其他用户发现；（2）顾名思义，集中合谋下的攻击者攻击者通过汇报相同的分布而集中在同一个peer社区中。显然，由于我们的综合信用评价同时综合相似度和性能的影响，因此攻击者仍会因为性能不佳而降低评价。我们可以设定一个参与FFL的最低信用值，拥有过多恶意用户的peer社区也会被排除出后续训练。
-When attackers possess multiple compromised UAV nodes, these nodes can conspire to launch collusion attacks.
-MR-FFL can effectively thwart collusion attacks through simple configurations.
-Specifically, within MR-FFL, attackers may adopt either a "distributed collusion" or a "centralized collusion" strategy: (a) Attackers engaged in distributed collusion report distinct data distributions, thereby concealing themselves within different heterogeneous peer communities.
-While this strategy might potentially evade traditional defense methods, when facing MR-FFL, it becomes detectable by other users within the community; (b) As the name implies, attackers engaging in centralized collusion report identical distributions and concentrate within the same peer community.
-However, due to our comprehensive credit evaluation, which considers both similarity and performance impacts, attackers are still subject to diminished evaluations due to poor performance.
-A minimum credit threshold for participation in FFL can be set, and peer communities with an excess of malicious users can be excluded from subsequent training.
-
-\subsubsection{UAV nodes selection}
-%在每轮外部同步结束，我们重新选择客户构建下一轮参与联合学习的super node。
-%为了尽可能地消除攻击者的干扰，我们设计簇内客户选择机制，客户被选中参与联合学习的概率由其上一轮次的综合信用评价决定。在簇$c$中，用sigmoid函数量化客户$i$被选中的概率：
-After each round of FFL training, we reconstruct colleague communities as participants for the next round.
-To mitigate the impact of potential attacks, we introduce a client selection mechanism within the peer community.
-The probability of a client being chosen to participate in FFL is determined by its current comprehensive credit evaluation.
-Drawing inspiration from \cite{zhou2022defta}, we employ a Sigmoid-like function to quantify this probability of UAV $U_i$:
-\begin{equation}
-\psi^{i}_t=\frac{1}{1+e^{-k (\Phi^{i}_{t}-\gamma)}},\forall U_i \in \mathbf{U}, \forall t
-\end{equation}
-%其中$k$为控制sigmoid斜率的参数。由于$\Phi^{i}_{t}\in [0,1]$,我们规定选择概率函数的定义域在[0,1]区间内。可以看出选择概率函数在定义域内的值域$[\frac{1}{1+e^{0.5k}},\frac{1}{1+e^{-0.5k}}]$取决于参数$k$。在实际应用中，为了使选择概率在定义域内尽可能接近0和1，一般选择较大的斜率$k$。
-where $k$ controls the slope of the Sigmoid function.
-As $\Phi^{i}_{t}\in [0,1]$, we stipulate that the domain of the probability function $\psi^{i}_t$ lies within $[0,1]$.
-It can be observed that the range of $\psi^{i}_t$ is $[\frac{1}{1+e^{\gamma k}},\frac{1}{1+e^{-\gamma k}}]$, depending on $k$.
-In practical applications, to ensure that the selection probability function closely approaches 0 (malicious clients) and 1 (benign yet heterogeneous clients) within its domain, a larger slope parameter $k$ is usually chosen.
-
-\textbf{Positive assumption for fairness among benign UAVs:} It is worth mentioning that, different from existing methods' negative assumption, we initiate the selection with positive assumption, i.e., $\Phi^{i}_{0}=1 ,\forall U_i\in \mathbf{U}$, which provides high selective probability for inexperienced new participants.
-Therefore, this approach can achieve more fair selection results among benign UAV nodes and maximize client participation.
-Besides, we obtain a more comprehensive evaluation of credit, drastically mitigating the potential impact of adversarial behavior.
-%服务器基于本轮综合信用评分选择客户参与下一轮次的训练，为了尽可能地提高客户的参与率，得到更全面、完整的客户信誉评估结果，将综合信誉作为客户属性进行持久化存储，服务器将赋予客户乐观的初始综合信誉并在每轮交互中更新客户的最新综合信誉。
-%The server selects clients for the next training round based on the current comprehensive credit score.
-In order to maximize client participation, achieve a more comprehensive and complete client credit assessment, and persistently store the comprehensive credit as a client attribute, the server endows clients with an optimistic initial comprehensive credit.
-%乐观的初始信誉和时间延迟的信誉更新增加了参与训练次数较少的客户被选中的概率，能够更全面、完善地评估所有客户的信誉，避免潜在攻击的影响。
-%This initial credit, along with delayed credit updates over time, increases the probability of selecting clients with fewer training participations.
-This approach aims to provide a more comprehensive and thorough evaluation of all clients' reputations, mitigating the potential impact of adversarial behavior.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{algorithm}[t]
-% \caption{algorithm credit} %算法的名字
-% \begin{algorithmic}[1]
-%  \State \textbf{\bf Input:Model Variation of Client i $\Delta\widetilde{\omega^{i}_{t}}$, Model Variation of Cluster c $\Delta\widetilde{\omega^{c}_{t-1}}$}
-% \State\textbf{Output:Comprehensive Credit of Client $\Phi^{i}_{t}$,Peputation Opinion Vector $\Upsilon^{i}_{t}$} 
-% \State \textbf{Initialize:$u^{c \rightarrow i}_{0}=\frac{\sigma_{c}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}$,$b^{c \rightarrow i}_{0}=1-u^{c \rightarrow i}_{0}$,$d^{c \rightarrow i}_{0}=0$}
-% \For{$r \in 1,\cdots,R$}
-%     \State {\color{CadetBlue}/*\textbf{Credit in cluster $c$ */}}
-%         \For{each client $i \in c$ }
-%             \If{client $i \in C \cap S$ }
-%                 \State $ \alpha^{c,i}_{t} = \alpha( \Delta\widetilde{\omega^{c}_{t-1}}, \Delta\widetilde{\omega^{i}_{t}}) = \frac{\langle \Delta\widetilde{\omega^{c}_{t-1}},\Delta\widetilde{\omega^{i}_{t}}\rangle}{\Vert \Delta\widetilde{\omega^{c}_{t-1}}\Vert\cdot\Vert \Delta\widetilde{\omega^{i}_{t}}\Vert }$,
-%                 \State$p^{c \rightarrow i}_{t} = \alpha^{c,i}_{t} -(-1)$,$n^{c \rightarrow i}_{t} = 1-\alpha^{i,j}_{t}$,
-%                 \State \textbf{update  $\Upsilon^{c \rightarrow i}_{t},\Phi^{c \rightarrow i}_{r,time}$ with equation}
-%                 \State $\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{r,time}$
-%             \Else
-%                 \State$\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{t-1}$
-%             \EndIf
-%          \EndFor
-%     \State {\color{CadetBlue}/*\textbf{Credit in supernode $s$ */}}
-%     \For{each supernode $s_{m} \in S-s_{m}$}
-%         \State $\alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega^{s_{m}}_{t}},  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}) = \frac{\langle  \Delta\widetilde{\omega^{s_{m}}_{t}}, \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\rangle}{\Vert  \Delta\widetilde{\omega^{s_{m}}_{t}}\Vert\cdot\Vert  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\Vert }$,
-%         \State $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$,$ NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$
-%         \State \textbf{update $\UpsiloNI^{s_{m} \rightarrow s}_{t},\Phi^{s}_{t}$ with equation}
-%     \EndFor
-%     \For{each client $i \in S$}
-%         \State $\Phi^{s \rightarrow i}_{t}=\Phi^{s}_{t} $
-%     \EndFor
-%     \State {\color{CadetBlue} /*\textbf{Comprehensive credit */}}
-%     \For{each client $i \in Clients$}
-%         \If{client $i \in C\cap S$ }
-%         \State \textbf{update $\Upsilon^{i}_{t},\Phi^{i}_{t}$ with equation}
-%         \Else 
-%         \State $\Phi^{i}_{t} = \Phi^{i}_{t-1}$
-%         \EndIf
-%     \EndFor
-% \EndFor
-% \end{algorithmic}
-% \end{algorithm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tb]
-	\begin{minipage}[!t]{0.49\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{results/SCC_diff.pdf}
-		%\vspace{-2em}
-		\caption{$L_2$-divergence}
-		\label{results:1-diff}
-	\end{minipage}
-        \begin{minipage}[!t]{0.49\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{results/SCC_time.pdf}
-		%\vspace{-2em}
-		\caption{Running time}
-		\label{results:1-time}
-	\end{minipage}
-\end{figure}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{results/SCC_acc.pdf}
-\caption{The accuracy comparison between MR-FFL with existing heterogeneity-robust methods.}
-\label{results:1-acc}
-\end{figure}
-
-\section{Experimental results}
-\subsection{Experimental settings}
-Experiments were conducted using the PyTorch deep learning framework, employing two widely adopted benchmark datasets (EMNIST and CIFAR).
-To demonstrate the defense performance of the proposed MR-FFL scheme, we conduct both explicit (Flipping attack) and implicit (Backdoor attack) attack paradigms.
-%The EMNIST dataset encompasses 10 categories for digits and 52 categories for uppercase and lowercase English letters, totaling 62 categories.
-All images have dimensions of 28x28 pixels.
-In line with the methodologies of previous studies \cite{mohri2019agnostic,tan2022fedproto, zeng2022heterogeneous}, our experiments were conducted under a non-iid setting, implementing non-uniform sampling within the dataset.
-To create an equitable but dissimilar distribution among clients, we extracted 12,0000 training samples and 30,000 testing samples, allocating them in an 8:2 ratio between the training set and the validation set.
-This ensured that each client possessed an equal number of samples in the training dataset, albeit with distinct data distributions.
-%Two neural network architectures, a simple CNN and an MLP, were employed to undertake the Federated Learning (FL) task on the EMNIST dataset.
-The detailed configurations of the local network models are delineated in Tables 2 and 3.
-Throughout our experiments, we configured $200\sim 500$ UAV nodes.
-A total of 200 communication rounds were executed, where the local training epoch for each $U_i$ is 5, the batch size is 128, the learning rate $\eta$ is 0.1, and the momentum is 0.9.
-
-\subsection{The effectiveness of MR-FFL in heterogeneous UAV network}
-
-To verify the effectiveness of our stratified community construction mechanism, we compare it with existing heterogeneity-robust methods in terms of divergence reduction, running time, and learning performance.
-We choose three benchmark methods (\textbf{Random}, \textbf{Bayesian}, \textbf{Generic algorithms}) and two latest methods (\textbf{Cohort} \cite{hiessl2022cohort} and \textbf{GBP-CS} \cite{li2022data}).
-In terms of divergence reduction, as shown in Figure \ref{results:1-diff}, our method significantly reduces both the average maximum divergences and deviation among clients, which indicates better robustness.
-Regarding execution time, SCC requires only one operation to generate a sampling template.
-Subsequently, it performs random sampling based on the template, resulting in a short execution time.
-This advantage becomes more pronounced with increasing rounds.
-As shown in Figure \ref{results:1-time}, our method is more time-saving than other alternative methods.%On the other hand, Bayesian sampling and Genetic Algorithm have excessively long execution times, which are not acceptable.
-The Cohort algorithm has a relatively short runtime, but it suffers from a large deviation from the target distribution.
-GBP-CS algorithm needs sampling before each iteration, and its runtime is not as efficient as the QIP algorithm.
-
-In terms of learning performance, we also compared three representative algorithms (\textbf{FedAvg} \cite{li2019convergence-fedavg}, \textbf{FedNova} \cite{wang2020tackling-fednova}, \textbf{FedProx} \cite{yuan2022convergence-fedprox}) with MR-FFL.
-As illustrated in Figure \ref{results:1-acc}, vanilla FL algorithms exhibit slow convergence rates and poor performance with large fluctuations in heterogeneous environments.
-In comparison to heterogeneous FL algorithms like FedNova and FedProx, MR-FFL continues to achieve better convergence speed, stability, and accuracy.
-
-\subsection{The performance of MR-FFL against poisoning attacks}
-\begin{figure*}[!t]
-\centering
-\subfloat[EMNIST (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_MINIST_acc.pdf}%
-\label{result0:acc-EMNIST-FLIP}}
-\hfil
-\subfloat[CIFAR (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_Cifar_acc.pdf}%
-\label{result0:acc-CIFAR-FLIP}}
-\hfil
-\subfloat[EMNIST (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_MINIST_att_acc.pdf}%
-\label{result0:acc-EMNIST-Backdoor}}
-\hfil
-\subfloat[CIFAR (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_Cifar_att_acc.pdf}%
-\label{result0:acc-CIFAR-Backdoor}}
-\caption{The defense performance comparison between MR-FFL with existing poisoning-resistant methods against Flipping and Backdoor attacks.}
-\label{results:0-acc}
-\end{figure*}
-
-%%%%%%%%%%%%EMNIST+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-\centering
-\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_MINIST_cr_1.pdf}%
-\label{result1:credit-AAD}}
-\hfil
-\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_MINIST_pr_1.pdf}%
-\label{result1:prob-AAD}}
-\hfil
-\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_MINIST_cr_1.pdf}%
-\label{result1:credit-FLtrust}}
-\hfil
-\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_MINIST_pr_1.pdf}%
-\label{result1:prob-FLtrust}}
-\hfil
-\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_MINIST_cr_1.pdf}%
-\label{result1:credit-MRFFL}}
-\hfil
-\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_Flip_MINIST_pr_1.pdf}%
-\label{result1:prob-MRFFL}}
-\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on EMNIST.}
-\label{results_EMNIST_flip}
-\end{figure}
-
-%%%%%%%%%%%EMNIST+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-\centering
-\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_MINIST_cr_1.pdf}%
-\label{result2:credit-AAD}}
-\hfil
-\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_MINIST_pr_1.pdf}%
-\label{result2:prob-AAD}}
-\hfil
-\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_MINIST_cr_1.pdf}%
-\label{result2:credit-FLtrust}}
-\hfil
-\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_MINIST_pr_1.pdf}%
-\label{result2:prob-FLtrust}}
-\hfil
-\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_MINIST_cr_1.pdf}%
-\label{result2:credit-MRFFL}}
-\hfil
-\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_BACKDOOR_MINIST_pr_1.pdf}%
-\label{result2:prob-MRFFL}}
-\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on EMNIST.}
-\label{results_EMNIST_Backdoor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%CIFAR+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-\centering
-\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_Cifar_cr_1.pdf}%
-\label{result3:credit-AAD}}
-\hfil
-\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_Cifar_pr_1.pdf}%
-\label{result3:prob-AAD}}
-\hfil
-\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_Cifar_cr_1.pdf}%
-\label{result3:credit-FLtrust}}
-\hfil
-\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_Cifar_pr_1.pdf}%
-\label{result3:prob-FLtrust}}
-\hfil
-\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_Cifar_cr_1.pdf}%
-\label{result3:credit-MRFFL}}
-\hfil
-\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_Flip_Cifar_pr_1.pdf}%
-\label{result3:prob-MRFFL}}
-\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on CIFAR.}
-\label{results_Cifar_flip}
-\end{figure}
-%%%%%%%%%%%CIFAR+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-\centering
-\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_Cifar_cr_1.pdf}%
-\label{result4:credit-AAD}}
-\hfil
-\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_Cifar_pr_1.pdf}%
-\label{result4:prob-AAD}}
-\hfil
-\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_Cifar_cr_1.pdf}%
-\label{result4:credit-FLtrust}}
-\hfil
-\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_Cifar_pr_1.pdf}%
-\label{result4:prob-FLtrust}}
-\hfil
-\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_Cifar_cr_1.pdf}%
-\label{result4:credit-MRFFL}}
-\hfil
-\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_BACKDOOR_Cifar_pr_1.pdf}%
-\label{result4:prob-MRFFL}}
-\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on CIFAR.}
-\label{results_Cifar_Backdoor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Subsequently, to further demonstrate the advantages of the MR-FFL method in ensuring model integrity, we compare our approach with existing representative reliable FL algorithms, including \textit{mitigation-oriented} \cite{blanchard2017machine-krum,yin2018byzantine-trimmedmean}, \textit{detection-oriented} \cite{andreina2021baffle}, and \textit{credit-oriented} \cite{li2019abnormal,cao2020fltrust}.
-The total number of UAV ndoes is set to 200.
-As shown in Figure \ref{results:0-acc}, we conduct explicit attacks (flipping) and compare the training accuracy in Figure \ref{result0:acc-EMNIST-FLIP} and \ref{result0:acc-CIFAR-FLIP}.
-Higher accuracy means better defense effect.
-Meanwhile, the backdoor task accuracy (implicit attack) on EMNIST and CIFAR is demonstrated in Figure \ref{result0:acc-EMNIST-Backdoor} and \ref{result0:acc-CIFAR-Backdoor}, respectively.
-Lower backdoor accuracy indicates better defense performance.
-Based on the results, it is evident that mitigation-oriented schemes such as \textbf{Trimmed-mean} \cite{yin2018byzantine-trimmedmean} exhibit significant deviations from the global objectives in heterogeneous environments, resulting in lower accuracy.
-\textbf{BaFFLe} \cite{andreina2021baffle}, as a detection-oriented method, struggles to converge rapidly and requires additional validation rounds, incurring substantial communication and time overhead.
-For credit-oriented methods \textbf{AAD} \cite{li2019abnormal} and \textbf{FLTrust} \cite{cao2020fltrust}, although AAD can permanently ban attackers, the gap between heterogeneous gradients and attacker gradients relative to the pre-trained global model leads to erroneous elimination, resulting in an overall performance decline.
-Similarly, in FLTrust, heterogeneous UAVs with gradients opposite to the direction of server-side model updates face challenges participating in the global model aggregation, causing a decline in model performance.
-
-Furthermore, in Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, through a comparative analysis of credit assessment values and selection probabilities with existing methods such as AAD (based on autoencoder) and FLTrust (based on bootstrapping), we validate the effectiveness of the credit evaluation mechanism in the MR-FFL scheme.
-This validation is crucial for guiding subsequent hyperparameter tuning and adaptive configurations.
-As illustrated in the first rows of those figures, the AAD method lacks adaptation to highly heterogeneous environments, leading to the misclassification of numerous legitimate UAV nodes.
-Under FLTrust, as shown in the second rows of above figures, both the credit of normal UAV participants and their selection probabilities exhibit significant fluctuations, with a lack of robustness in detecting certain covert attacks.
-In contrast, MR-FFL evaluates the integrity of UAV nodes in terms of both community-wide similarity and performance.
-As shown in the third rows of Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, our method can accurately identify the stealthy malicious attackers from benign nodes.
-
-\subsection{The fairness of MR-FFL under adversarial environments}
-One of the important drawbacks of existing security technologies is unfairness.
-As shown in the second columns of Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, except for the low accuracy, AAD and FLTrust also assign vastly different selection probabilities to benign UAV nodes.
-Different from existing methods, MR-FFL employs a Sigmoid function to optimize the selection strategy, resulting in a clearer distinction between attackers and normal users (e.g., Figure \ref{result3:credit-MRFFL} and \ref{result4:credit-MRFFL}).
-Hence, the probabilities of legitimate clients being selected are approximate (e.g., Figure \ref{result1:prob-MRFFL} and \ref{result2:prob-MRFFL}), ensuring fairness among benign UAV nodes.
-
-\section{Conclusion}
-%随着泛在通信和技术的发展，UAV网络得到越来越广泛的应用。基于无人机的联邦学习等智能化方法能够自适应地优化部署和业务，成为重要发展趋势之一。然而，受限于有限的巡航范围，UAV设备往往高度异构，同时UAV设备资源和能量极其有限，这些约束均导致现有安全技术难以移植到UAV网络中。因此，在本文中，我们针对异构和资源受限的UAV网络下的公平联邦学习的安全问题进行了研究。基于一种分层社区构建机制，我们提出了双向可信的公平联邦学习架构，来应对异构UAV网络中的攻击威胁。在公有数据集上的系列实验表明，我们的方案相比现有技术，在异构缓解、隐私增强和污染防治方面均取得明显提升。
-With the development of ISCC and SAGIN, UAV networks are experiencing increasingly widespread applications.
-AI technologies such as FL based on UAV enable adaptive optimization of deployment and operations, emerging as a crucial development trend.
-However, due to the restricted patrol area, UAV devices exhibit high heterogeneity, and their resources and energy are also extremely limited.
-These constraints make it challenging to directly implant existing high-consumption security methods in UAV networks.
-Therefore, in this paper, we investigate the security issues of FFL in heterogeneous and resource-constrained UAV networks.
-Leveraging a stratified community construction mechanism, we propose a mutual reliability FFL framework (MR-FFL) to address multiple security threats.
-%in heterogeneous UAV networks.
-A series of experiments on public datasets demonstrate significant improvements of MR-FFL in heterogeneity remission, fairness guarantee, and poisoning resistance compared to existing technologies.
-
-\section*{Acknowledgments}
-This work is partially supported by the National Natural Science Foundation of China (NSFC) under Grant 62225105 and the ZhejiangLab Open Research Project (No. K2022QA0AB05).
-
-\bibliographystyle{IEEEtran}
-\bibliography{ref}
-
-% {\appendix[Proof of the Zonklar Equations]
-% Use $\backslash${\tt{appendix}} if you have a single appendix:
-% Do not use $\backslash${\tt{section}} anymore after $\backslash${\tt{appendix}}, only $\backslash${\tt{section*}}.
-% If you have multiple appendixes use $\backslash${\tt{appendices}} then use $\backslash${\tt{section}} to start each appendix.
-% You must declare a $\backslash${\tt{section}} before using any $\backslash${\tt{subsection}} or using $\backslash${\tt{label}} ($\backslash${\tt{appendices}} by itself
-%  starts a section numbered zero.)}
-
-%{\appendices
-%\section*{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-% You can choose not to have a title for an appendix if you want by leaving the argument blank
-%\section*{Proof of the Second Zonklar Equation}
-%Appendix two text goes here.}
-
-% \section{References Section}
-% You can use a bibliography generated by BibTeX as a .bbl file.
-%  BibTeX documentation can be easily obtained at:
-%  http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-%  The IEEEtran BibTeX style support page is:
-%  http://www.michaelshell.org/tex/ieeetran/bibtex/
-
- % argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% \section{Simple References}
-% You can manually copy in the resultant .bbl file and set second argument of $\backslash${\tt{begin}} to the number of references
-%  (used to reserve space for the reference number labels box).
-
-% \begin{thebibliography}{1}
-% \bibliographystyle{IEEEtran}
-
-% \bibitem{ref1}
-% {\it{Mathematics Into Type}}. American Mathematical Society. [Online]. Available: https://www.ams.org/arc/styleguide/mit-2.pdf
-
-% \bibitem{ref2}
-% T. W. Chaundy, P. R. Barrett and C. Batey, {\it{The Printing of Mathematics}}. London, U.K., Oxford Univ. Press, 1954.
-
-% \bibitem{ref3}
-% F. Mittelbach and M. Goossens, {\it{The \LaTeX Companion}}, 2nd ed. Boston, MA, USA: Pearson, 2004.
-
-% \bibitem{ref4}
-% G. Gr\"atzer, {\it{More Math Into LaTeX}}, New York, NY, USA: Springer, 2007.
-
-% \bibitem{ref5}M. Letourneau and J. W. Sharp, {\it{AMS-StyleGuide-online.pdf,}} American Mathematical Society, Providence, RI, USA, [Online]. Available: http://www.ams.org/arc/styleguide/index.html
-
-% \bibitem{ref6}
-% H. Sira-Ramirez, ``On the sliding mode control of nonlinear systems,'' \textit{Syst. Control Lett.}, vol. 19, pp. 303--312, 1992.
-
-% \bibitem{ref7}
-% A. Levant, ``Exact differentiation of signals with unbounded higher derivatives,''  in \textit{Proc. 45th IEEE Conf. Decis.
-% Control}, San Diego, CA, USA, 2006, pp. 5585--5590. DOI: 10.1109/CDC.2006.377165.
-
-% \bibitem{ref8}
-% M. Fliess, C. Join, and H. Sira-Ramirez, ``Non-linear estimation is easy,'' \textit{Int. J. Model., Ident. Control}, vol. 4, no. 1, pp. 12--27, 2008.
-
-% \bibitem{ref9}
-% R. Ortega, A. Astolfi, G. Bastin, and H. Rodriguez, ``Stabilization of food-chain systems using a port-controlled Hamiltonian description,'' in \textit{Proc. Amer. Control Conf.}, Chicago, IL, USA,
-% 2000, pp. 2245--2249.
-
-% \end{thebibliography}
-
-\newpage
-
-%\section{Biography Section}
-% If you have an EPS/PDF photo (graphicx package needed), extra braces are
-%  needed around the contents of the optional argument to biography to prevent
-%  the LaTeX parser from getting confused when it sees the complicated
-%  $\backslash${\tt{includegraphics}} command within an optional argument. (You can create
-%  your own custom macro containing the $\backslash${\tt{includegraphics}} command to make things
-%  simpler here.)
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Zan Zhou.jpg}}]{Zan Zhou} (Student Member, IEEE)
-received his Ph.D. degree in Computer Science from the Beijing University of Posts and Telecommunications (BUPT) in 2022. 
-From 2021 to 2022, he was a visiting student at Nanyang Technology University (NTU), Singapore. 
-He is currently a Postdoc researcher with the State Key Laboratory of Networking and Switching Technology, BUPT, Beijing, China.
-His research interests include data privacy, active defense, and federated learning.
-%He is Student member of IEEE.
-\end{IEEEbiography}
-
-\vspace{11pt}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Shujie Yang.jpg}}]{Shujie Yang} received the Ph.D.
-degree from the Institute of Network Technology, Beijing University of Posts and Telecommunications, Beijing, China, in 2017.
-He is currently a lecturer with the State Key Laboratory of Networking and Switching Technology.
-His major research interests include network security and artificial intelligence.
-\end{IEEEbiography}
-
-\vspace{11pt}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/changqiao xu.jpg}}]{Changqiao Xu}
-(Senior Member, IEEE) received the Ph.D.
-degree from the Institute of Software, Chinese Academy of Sciences (ISCAS) in Jan.
-2009.
-He was a researcher at Athlone Institute of Technology and Joint Training PhD at Dublin City University, Ireland during 2007-2009.
-%He joined BUPT in Dec.
-2009.
-Currently, he is a Professor with the State Key Laboratory of Networking and Switching Technology, and Director of the Network Architecture Research Center at BUPT.
-His research interests include Network Security, Mobile Networking, Multimedia Communications, and Future Internet Technology.
-He has edited two books and published over 200 technical papers in prestigious international journals and conferences, including IEEE Comm.
-Magazine, IEEE/ACM ToN, IEEE TMC, INFOCOM, ACM Multimedia, etc.
-He has served a number of international conferences and workshops as a Co-Chair and TPC member.
-He is currently serving as the Editor-in-Chief of Transactions on Emerging Telecommunications Technologies (Wiley).
-\end{IEEEbiography}
-% \bf{If you include a photo:}\vspace{-33pt}
-% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig1}}]{Michael Shell}
-% Use $\backslash${\tt{begin\{IEEEbiography\}}} and then for the 1st argument use $\backslash${\tt{includegraphics}} to declare and link the author photo.
-% Use the author name as the 3rd argument followed by the biography text.
-% \end{IEEEbiography}
-
-% \vspace{11pt}
-
-% \bf{If you will not include a photo:}\vspace{-33pt}
-% \begin{IEEEbiographynophoto}{John Doe}
-% Use $\backslash${\tt{begin\{IEEEbiographynophoto\}}} and the author name as the argument followed by the biography text.
-% \end{IEEEbiographynophoto}
-
-\vfill
-
-\newpage
 \onecolumn
@@
    \cite{jha2023label} & neurips & 2023 &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
-   \cite{yang2023data} & International Conference on Machine Learning & 2023 & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
-   \cite{dai2023chameleon} & International Conference on Machine Learning & 2023 & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
+   \cite{yang2023data} & ICML & 2023 & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
+   \cite{dai2023chameleon} & ICML & 2023 & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
    \cite{gu2023gradient} & ACL & 2023 & 这篇文章提出了一种新的梯度控制方法，旨在解决参数高效调优（PET）过程中后门攻击的遗忘问题。通过将后门注入过程视为多任务学习，文章引入了跨层梯度幅度归一化和层内梯度方向投影两种策略，以减少不同任务之间的梯度冲突和梯度大小的不平衡，从而增强后门攻击在用户微调模型后的效果。实验结果表明，该方法在情感分类和垃圾邮件检测任务中显著提高了后门攻击的持久性和有效性。 \\ \hline
-   \cite{zhang2024a3fl} & neurips & 2024 & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
-   \cite{xu2024shadowcast} & arxiv  & 2024 & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
+   \cite{zhang2024a3fl} & Neurips & 2024 & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
+   \cite{xu2024shadowcast} & Arxiv  & 2024 & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
    \cite{liang2024badclip} & CVPR & 2024 & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
@@
 
+\bibliographystyle{IEEEtran}
+\bibliography{ref}
+
 \end{document}

### 2024-08-16 main.tex
refactor: 重构之把中文之类的单独拆分出来
Signed-off-by: LetMeFly666 <814114971@qq.com>

--- 2024-08-15 main.tex
@@
 \usepackage{amsmath,amsfonts}
+% \usepackage{longtable}
+\usepackage{array}
 %\usepackage{algorithmic}
 %\usepackage{algorithm}
-\usepackage[UTF8]{ctex}
+% \usepackage[UTF8]{ctex}
 \usepackage{array}
@@
 % \end{tabular}
+
+\section{Related work}
 
@@
 
-\newpage
-\begin{table*}[]
-    \centering
-    \renewcommand\arraystretch{1.5}
-    \begin{tabular}{|c|p{3cm}|c|p{12cm}|} \hline
-    Title & Conference & Year & Main Content \\ \hline
-   \cite{jha2023label} & neurips & 2023 &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
-   \cite{yang2023data} & International Conference on Machine Learning & 2023 & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
-   \cite{dai2023chameleon} & International Conference on Machine Learning & 2023 & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
-   \cite{zhang2024a3fl} & neurips & 2024 & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
-   \cite{xu2024shadowcast} & arxiv  & 2024 & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
-   \cite{liang2024badclip} & CVPR & 2024 & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
-    \end{tabular}
-    \caption{Attack}
-    \label{tab:my_label}
-\end{table*}
+% \newpage
+% \onecolumn
+% \begin{longtable}{|c|p{3cm}|c|p{12cm}|} 
+%     \caption{This is the caption for the long table}
+%     \label{tabl:attack} \\ \hline
+%     Title & Conference & Year & Main Content \\ \hline
+%     \endfirsthead \hline
+%     Title & Conference & Year & Main Content \\ \hline 
+%     \endhead \hline
+%    \cite{jha2023label} & neurips & 2023 &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
+%    \cite{yang2023data} & International Conference on Machine Learning & 2023 & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
+%    \cite{dai2023chameleon} & International Conference on Machine Learning & 2023 & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
+%    \cite{gu2023gradient} & ACL & 2023 & 这篇文章提出了一种新的梯度控制方法，旨在解决参数高效调优（PET）过程中后门攻击的遗忘问题。通过将后门注入过程视为多任务学习，文章引入了跨层梯度幅度归一化和层内梯度方向投影两种策略，以减少不同任务之间的梯度冲突和梯度大小的不平衡，从而增强后门攻击在用户微调模型后的效果。实验结果表明，该方法在情感分类和垃圾邮件检测任务中显著提高了后门攻击的持久性和有效性。 \\ \hline
+%    \cite{zhang2024a3fl} & neurips & 2024 & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
+%    \cite{xu2024shadowcast} & arxiv  & 2024 & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
+%    \cite{liang2024badclip} & CVPR & 2024 & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
+
+%    \cite{attack01} & arXiv preprint & 2024 & 本篇文章次揭示了在联邦学习环境下对大语言模型（LLM）进行指令调优时存在的安全漏洞。文章提出了一种简洁但有效的安全攻击方法，恶意客户端通过使用未对齐的数据来训练本地模型，从而大幅度削弱了全球模型的安全对齐性（“未对齐的数据”，是指那些与预期的安全或伦理规范不一致的数据。例如，未对齐的数据可能包含有害的、误导性的或是不道德的信息，而这些信息在普通情况下不会被用于训练模型）。实验表明，该攻击方法能够将模型的安全性降低高达70\%，而现有的防御方法在应对此类攻击时几乎无效，仅能提高4\%的安全性。为了解决这一问题，作者进一步提出了一种新的事后防御方法，即通过服务器端生成对齐数据并进一步对全局模型进行微调，从而增强模型的安全性（中央服务器在接收到各个客户端的更新后，会主动生成一组对齐的数据。这些对齐的数据是预先定义好的，确保与预期的安全和伦理规范一致。这些数据可能包含严格筛选过的内容，如道德上中立或积极的文本片段）。实验结果显示，这种防御方法能够将模型的安全性提高最多69\%，且不显著降低模型的有效性。（这篇看完了发现不是视觉大模型） \\ \hline
+%    \cite{attack02} & arXiv preprint & 2024 & 本篇文章探讨了一种针对大语言模型（LLMs）的新型训练方法，称为目标潜在对抗性训练（Targeted Latent Adversarial Training, LAT），文章提出了通过在模型的潜在表示（latent representations）中引入针对性的扰动，来更有效地消除模型中顽固的不良行为（如后门攻击和模型“越狱”）。(潜在表示是指在神经网络的中间层中，数据通过多层非线性变换后所形成的特征表示。这些表示通常处于更高的抽象层次，与原始输入相比，能够捕捉到数据的深层次特征。在视觉大模型中，这些潜在表示可能包括图像的边缘、形状、纹理等更抽象的特征，而不再是具体的像素值。潜在表示在模型中扮演着至关重要的角色，因为它们是模型用来进行预测和决策的核心特征。)(针对性的扰动是指在训练或评估过程中，特意对模型的输入或潜在表示进行细微的修改或扰动，以诱导模型产生特定的（通常是不希望的）行为。通过这种方法，可以测试和增强模型在面对各种攻击时的鲁棒性。在本文中，作者使用潜在空间中的针对性扰动来模拟攻击，目的是强化模型的防御能力，使其能够抵抗类似的实际攻击，如后门攻击或越狱行为。)研究表明，与传统的对抗性训练相比，目标潜在对抗性训练可以显著提高模型抵抗这些攻击的能力，同时对模型的整体性能影响较小。文章通过实验验证了该方法在增强模型鲁棒性方面的有效性，尤其是在面对未知触发条件的后门攻击时，表现出色。  \\ \hline
+%    \cite{attack03} & arXiv preprint & 2024 & 本文探讨了开放权重大语言模型（LLMs）在面对篡改攻击时的脆弱性，并提出了一种名为TAR（Tampering Attack Resistance）的方法，旨在增强这些模型的抗篡改能力。文章指出，现有的安全防护措施，如拒绝机制和偏好训练，容易在少量微调步骤后被攻击者绕过，导致模型被恶意修改。为此，TAR方法通过对抗性训练和元学习，设计了一种新的防护机制，使得即使在经历数千步的微调攻击后，模型仍能保持其原有的安全防护功能。实验结果显示，与现有方法相比，TAR显著提高了模型的抗篡改能力，同时保留了模型的正常功能。研究还通过大量红队评估验证了TAR方法的有效性，展示了其在应对各种复杂攻击时的鲁棒性。(红队评估是一种在网络安全和机器学习领域常用的测试方法，它通过模拟攻击者的行为来评估系统或模型的安全性和防御能力。红队通常扮演“敌方”角色，主动寻找和利用系统的漏洞，以测试系统在真实攻击场景下的表现。这种方法帮助识别和修复安全漏洞，使系统在面对潜在的实际攻击时更加稳健。这篇文章中研究人员通过设计多个测试对手，这些对手模拟了各种可能的攻击策略，试图篡改或破坏大语言模型的功能。文章中提到进行了28个不同的红队评估测试，每个测试都旨在突破TAR的防护机制。)文章中的攻击方式涉及通过微调大语言模型的权重来篡改其行为。攻击者可以在模型的开放权重上进行少量微调，使其在特定情况下产生不希望的输出。例如，攻击者可能会在输入特定触发词时，让模型生成有害内容或偏离其正常功能。\\ \hline
+%    \cite{attack04} & arXiv preprint & 2024 & 这是一篇综述。本文主要介绍了以下攻击方式：\begin{itemize}
+%     \item 对抗性攻击：通过对输入数据进行微小的扰动，这些扰动虽然对人类几乎不可见，但会导致模型产生显著错误的输出，例如在图像分类中，可能会使模型将一个正常的图像误分类为完全不同的类别；
+%     \item 后门攻击：和之前咱做的一样；
+%     \item 数据中毒攻击：攻击者向模型的训练数据中注入恶意样本，这些样本会导致模型在遇到类似数据时输出错误结果，例如在物体识别任务中，中毒数据可能会导致模型误将无害物体识别为威胁；
+%     \item 模型逃逸：攻击者通过调整输入或模型参数，试图找到绕过模型防御机制的方法，使模型输出不受控制的内容，这种攻击常用于测试模型的防御效果；
+%     \item 多模态攻击：针对处理多种类型输入（如文本和图像）的模型，攻击者通过操纵一种模态的输入来影响另一种模态的输出，例如在多模态对话系统中，通过改变图像输入可能会影响系统的文本回应；
+%     \item 跨语言攻击：在多语言任务中，攻击者通过在一种语言中引入扰动来影响模型在另一种语言中的表现，这类攻击特别针对多语言翻译或生成模型，可能导致不同语言间的翻译不准确或失真。
+%     \end{itemize}\\ \hline
+%    \cite{attack05} &  Advances in Neural Information Processing Systems 34 (NeurIPS 2021) & 2021 & 本篇文章讨了如何保护通过“彩票假设”（Lottery Ticket Hypothesis, LTH）找到的稀疏子网络（即“中奖票”）的所有权。文章提出了一种新的基于稀疏结构信息的验证方法，通过在网络的稀疏结构中嵌入签名来进行所有权验证。这种方法能够在白盒和黑盒场景下保护模型的知识产权，并且对细微调整（如微调和剪枝）具有很强的鲁棒性。研究还通过大量实验验证了该方法在多种模型（如ResNet-20、ResNet-18、ResNet-50）和数据集（如CIFAR-10和CIFAR-100）上的有效性，展示了其在应对移除攻击和模糊攻击时的坚韧性。具体攻击方式有：细微调整（Fine-tuning）攻击：对模型进行微调来改变模型的权重值，同时希望不改变网络的稀疏结构。这种攻击旨在通过调整权重，试图使嵌入的签名信息变得不可辨认或无效。然而，由于嵌入的信息是基于网络的稀疏结构（即被剪枝后的模型结构），细微调整难以改变这一基础结构，从而无法有效移除签名。剪枝（Pruning）攻击：攻击者尝试通过进一步剪枝来移除嵌入的签名信息。这种攻击的目的是通过减少模型的非零参数，使得嵌入的结构信息丢失。然而，文章中提出的嵌入方法确保了签名信息在极端稀疏的情况下仍能保留，即使剪枝比例达到一定程度，签名依然可以从稀疏结构中提取出来。模糊攻击（Ambiguity Attacks）：攻击者试图通过制造伪签名或模糊原有签名的信息来混淆所有权验证。这种攻击可能包括添加噪声、篡改稀疏结构等手段，旨在使得验证机制无法区分真实的所有权签名和伪造的信息。然而，文章中的验证方法通过设计稳健的结构嵌入机制，使得这种模糊攻击难以成功。(“签名”指的是嵌入到神经网络稀疏结构中的一种独特的标识信息。这种签名通过在模型的剪枝过程中，利用网络的稀疏性来实现。具体而言，当模型被剪枝后，一部分神经元和连接被移除，剩余的结构会呈现出一种特定的稀疏模式。作者通过在这种稀疏模式中嵌入一个特定的结构或模式，这个模式就是所谓的“签名”。这种签名是不可见的，但可以通过特定的验证过程来提取和识别。其主要功能是为网络的所有权提供证据，类似于给模型打上了一个“水印”。当有人试图非法复制或篡改模型时，这个嵌入的签名仍然可以被识别出来，从而验证模型的归属。签名的鲁棒性设计使其能够抵抗常见的攻击方式（如微调和进一步的剪枝），即使模型经历了这些操作，签名依然可以从其稀疏结构中被提取出来，证明模型的所有权。)(模型的所有权是指对一个机器学习模型（如神经网络模型）所拥有的法律和知识产权。所有权通常由开发者或公司拥有，表示他们对模型的设计、训练数据、训练方法以及最终生成的模型参数等有控制权和排他性使用权。这意味着只有模型的所有者有权利决定如何使用、修改、发布或授权使用该模型。（可能涉及到知识产权保护、商业机密的保密）)\\ \hline
+%    \cite{attack06} & Portail HAL theses(theses.hal.science) & 2022 & 这篇文章有185页。本篇文章讨论了如何通过数字水印技术来保护机器学习模型的知识产权，防止模型被盗用。文章首先提供了当前水印技术的概述，并进一步扩展了这些技术在图像分类任务之外的应用，涵盖了回归、机器翻译和强化学习模型。作者还提出了针对模型托管平台的伪造攻击（即试图通过伪造水印来绕过验证）并介绍了一种基于公平性的水印技术，以增强模型在黑盒环境中的安全性。实验结果表明，这些水印技术不仅可以有效防止模型盗用，还能够在面对各种攻击时保持鲁棒性。
+%    数字水印是一种嵌入信息的技术，用于在数字内容（如图像、音频、视频或机器学习模型）中隐藏特定的信息，以表明所有权或版权。对于机器学习模型来说，数字水印是一种通过特定算法将标识信息嵌入到模型的权重、结构或输出中的技术。这种标识信息通常是不可见或难以察觉的，但可以通过特定的提取过程来验证。（数字水印的目的有：知识产权保护：开发者可以通过在模型中嵌入水印来证明模型的所有权，防止未经授权的复制和使用；盗版检测：如果一个模型被盗用或未经许可发布，水印可以作为证据，证明模型的来源和合法所有者；内容跟踪：水印可以帮助追踪模型的使用情况，尤其是在多个平台或用户之间共享时，确保模型的使用符合许可协议。） \\ \hline
+%     % \endfoot
+%     % \hline
+%     % \endlastfoot
+%     % \hline
+% \end{longtable}
 

### 2024-08-16 attack-zh.tex
attack.survey: 一段话式总结
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \usepackage{array}
+\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+\usepackage{textcomp}
 \usepackage{stfloats}
 \usepackage{url}
+\usepackage{verbatim}
 \usepackage{graphicx}
 \usepackage{cite}
+\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
+% updated with editorial comments 8/9/2021
+
+\usepackage{algorithm}
+%\usepackage{algorithmic}
+\usepackage{algpseudocode}
+
+\usepackage{dsfont}
+\usepackage{amssymb}
+\usepackage{amsmath,amsthm,amssymb,amsfonts}
+\usepackage{ragged2e}
+\usepackage{latexsym, amssymb, verbatim, amsmath}
+\usepackage{amsmath,bm}
+\usepackage{multirow}
+\usepackage{mathtools}
+\usepackage{subeqnarray}
+\usepackage{cases}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{mathrsfs}
+\usepackage{graphicx}
+%\usepackage{subfigure}
+\usepackage{booktabs}
+\usepackage{color}
+\usepackage{cite}
+\usepackage[]{chapterbib}
+\usepackage{enumerate}
 
 \begin{document}
+\subsection{Related Work}
+我们将现有针对模型的后门攻击分为两种，即空间隐蔽性后门攻击和时间隐蔽性后门攻击。
 
-后门攻击：我们将现有针对模型的后门攻击分为两种，即时间隐蔽性后门攻击和空间隐蔽性后门攻击。
-空间隐蔽性后门攻击是指攻击者通过调整触发器或梯度等方式，使得现有防御方法无法在特征空间中有效区分恶意攻击者与良性参与者，从而有效逃避检测。Shadowcast\cite{xu2024shadowcast}通过在特征空间中引入微小、不可察觉的扰动，操纵视觉语言模型（VLMs）在特定视觉输入下生成误导性的文本输出。BadClip\cite{liang2024badclip}提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。Flip\cite{jha2023label}通过修改训练数据的标签，使得模型训练轨迹接近于带有后门的专家模型，从而在特征空间中达到隐蔽攻击的效果，即使在图像干净的情况下也能逃避现有检测方法。
-时间隐蔽性后门攻击是指攻击者设计出具有高持久性的后门，使其在恶意攻击者结束攻击后仍能长期存在，不被后续良性更新所覆盖，从而持续影响模型行为。 Chameleon\cite{dai2023chameleon}关注如何通过对比学习来调整中毒样本、干扰样本以及促进样本嵌入表示之间的关系，从而提高后门攻击的空间隐蔽性。ImgTrojan\cite{tao2024imgtrojan}通过在视觉语言模型的训练数据中注入少量恶意样本，使得这些后门即使在模型后续的良性训练中仍能保持有效，从而持续影响模型的行为。\cite{gu2023gradient}提出了一种新的梯度控制方法，通过跨层梯度幅度归一化和层内梯度方向投影，解决了参数高效调优（PET）过程中后门攻击的遗忘问题，从而维持攻击的持久性和隐蔽性。A3FL\cite{zhang2024a3fl}通过对抗性适应损失函数来优化触发器的方式，使得后门能够在全局训练动态中持久存在，从而在联邦学习模型中实现高效且持久的攻击效果。
+空间隐蔽性后门攻击是指攻击者通过微调模型参数、修改输入特征或操纵模型训练过程等方式，使得现有防御方法无法在特征空间中有效区分恶意攻击者与良性参与者，从而有效逃避检测。Shadowcast\cite{xu2024shadowcast}通过在特征空间中引入微小、不可察觉的扰动，操纵视觉语言模型（VLMs）在特定视觉输入下生成误导性的文本输出。BadClip\cite{liang2024badclip}提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。Flip\cite{jha2023label}通过修改训练数据的标签，使得模型训练轨迹接近于带有后门的专家模型，从而在特征空间中达到隐蔽攻击的效果，即使在图像干净的情况下也能逃避现有检测方法。
+
+时间隐蔽性后门攻击是指攻击者通过调整模型训练过程或优化后门植入等方式，使后门在恶意攻击者结束攻击后仍能长期存在，不被后续良性更新所覆盖，从而持续影响模型行为。 Chameleon\cite{dai2023chameleon}关注如何通过对比学习来调整中毒样本、干扰样本以及促进样本嵌入表示之间的关系，从而提高后门攻击的空间隐蔽性。ImgTrojan\cite{tao2024imgtrojan}通过在视觉语言模型的训练数据中注入少量恶意样本，使得这些后门即使在模型后续的良性训练中仍能保持有效，从而持续影响模型的行为。\cite{gu2023gradient}提出了一种新的梯度控制方法，通过跨层梯度幅度归一化和层内梯度方向投影，解决了参数高效调优（PET）过程中后门攻击的遗忘问题，从而维持攻击的持久性和隐蔽性。A3FL\cite{zhang2024a3fl}通过对抗性适应损失函数来优化触发器的方式，使得后门能够在全局训练动态中持久存在，从而在联邦学习模型中实现高效且持久的攻击效果。
+% 总之，现有的后门攻击策略在空间隐蔽性和时间隐蔽性方面都有了显著的进展。空间隐蔽性后门攻击通过优化特征空间中的触发器或梯度，使得恶意行为难以被现有的检测方法发现，从而实现了更高效、更难以检测的攻击。而时间隐蔽性后门攻击则专注于提高后门的持久性，使得即使在恶意攻击结束后，这些后门依然能够在模型中长期存在并继续影响其行为。通过这些攻击方式的结合，攻击者能够在各种应用场景中有效地躲避检测，并确保攻击效果的持续性，这对现有的防御机制提出了更高的挑战，强调了未来在开发更加鲁棒的防御方法方面的迫切需求。
+
+总的来看，现有的后门攻击方法已展现出显著的隐蔽性和持久性，能够有效规避当前的检测机制。这些攻击不仅在特征空间中巧妙隐藏恶意意图，还能在长期训练过程中保持攻击效果，对模型行为产生持续而深远的影响，也对模型安全构成了严峻挑战。这对现有的防御机制提出了更高的挑战，强调了未来在开发更加鲁棒的防御方法方面的迫切需求。
 
 \onecolumn
-\begin{longtable}{|c|p{3cm}|c|p{12cm}|} 
+\begin{longtable}{|p{3.5cm}|p{2cm}|p{10.5cm}|} 
     \caption{This is the caption for the long table}
     \label{tabl:attack} \\ \hline
-    Title & Conference & Year & Main Content \\ \hline
+    Title & Conference & Main Content \\ \hline
     \endfirsthead \hline
-    Title & Conference & Year & Main Content \\ \hline 
+    Title & Conference & Main Content \\ \hline 
     \endhead \hline
-   \cite{jha2023label} & neurips & 2023 &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
-   \cite{yang2023data} & ICML & 2023 & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
-   \cite{dai2023chameleon} & ICML & 2023 & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
-   \cite{gu2023gradient} & ACL & 2023 & 这篇文章提出了一种新的梯度控制方法，旨在解决参数高效调优（PET）过程中后门攻击的遗忘问题。通过将后门注入过程视为多任务学习，文章引入了跨层梯度幅度归一化和层内梯度方向投影两种策略，以减少不同任务之间的梯度冲突和梯度大小的不平衡，从而增强后门攻击在用户微调模型后的效果。实验结果表明，该方法在情感分类和垃圾邮件检测任务中显著提高了后门攻击的持久性和有效性。 \\ \hline
-   \cite{zhang2024a3fl} & Neurips & 2024 & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
-   \cite{xu2024shadowcast} & Arxiv  & 2024 & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
-   \cite{liang2024badclip} & CVPR & 2024 & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
-
-   \cite{attack01} & arXiv preprint & 2024 & 本篇文章次揭示了在联邦学习环境下对大语言模型（LLM）进行指令调优时存在的安全漏洞。文章提出了一种简洁但有效的安全攻击方法，恶意客户端通过使用未对齐的数据来训练本地模型，从而大幅度削弱了全球模型的安全对齐性（“未对齐的数据”，是指那些与预期的安全或伦理规范不一致的数据。例如，未对齐的数据可能包含有害的、误导性的或是不道德的信息，而这些信息在普通情况下不会被用于训练模型）。实验表明，该攻击方法能够将模型的安全性降低高达70\%，而现有的防御方法在应对此类攻击时几乎无效，仅能提高4\%的安全性。为了解决这一问题，作者进一步提出了一种新的事后防御方法，即通过服务器端生成对齐数据并进一步对全局模型进行微调，从而增强模型的安全性（中央服务器在接收到各个客户端的更新后，会主动生成一组对齐的数据。这些对齐的数据是预先定义好的，确保与预期的安全和伦理规范一致。这些数据可能包含严格筛选过的内容，如道德上中立或积极的文本片段）。实验结果显示，这种防御方法能够将模型的安全性提高最多69\%，且不显著降低模型的有效性。（这篇看完了发现不是视觉大模型） \\ \hline
-   \cite{attack02} & arXiv preprint & 2024 & 本篇文章探讨了一种针对大语言模型（LLMs）的新型训练方法，称为目标潜在对抗性训练（Targeted Latent Adversarial Training, LAT），文章提出了通过在模型的潜在表示（latent representations）中引入针对性的扰动，来更有效地消除模型中顽固的不良行为（如后门攻击和模型“越狱”）。(潜在表示是指在神经网络的中间层中，数据通过多层非线性变换后所形成的特征表示。这些表示通常处于更高的抽象层次，与原始输入相比，能够捕捉到数据的深层次特征。在视觉大模型中，这些潜在表示可能包括图像的边缘、形状、纹理等更抽象的特征，而不再是具体的像素值。潜在表示在模型中扮演着至关重要的角色，因为它们是模型用来进行预测和决策的核心特征。)(针对性的扰动是指在训练或评估过程中，特意对模型的输入或潜在表示进行细微的修改或扰动，以诱导模型产生特定的（通常是不希望的）行为。通过这种方法，可以测试和增强模型在面对各种攻击时的鲁棒性。在本文中，作者使用潜在空间中的针对性扰动来模拟攻击，目的是强化模型的防御能力，使其能够抵抗类似的实际攻击，如后门攻击或越狱行为。)研究表明，与传统的对抗性训练相比，目标潜在对抗性训练可以显著提高模型抵抗这些攻击的能力，同时对模型的整体性能影响较小。文章通过实验验证了该方法在增强模型鲁棒性方面的有效性，尤其是在面对未知触发条件的后门攻击时，表现出色。  \\ \hline
-   \cite{attack03} & arXiv preprint & 2024 & 本文探讨了开放权重大语言模型（LLMs）在面对篡改攻击时的脆弱性，并提出了一种名为TAR（Tampering Attack Resistance）的方法，旨在增强这些模型的抗篡改能力。文章指出，现有的安全防护措施，如拒绝机制和偏好训练，容易在少量微调步骤后被攻击者绕过，导致模型被恶意修改。为此，TAR方法通过对抗性训练和元学习，设计了一种新的防护机制，使得即使在经历数千步的微调攻击后，模型仍能保持其原有的安全防护功能。实验结果显示，与现有方法相比，TAR显著提高了模型的抗篡改能力，同时保留了模型的正常功能。研究还通过大量红队评估验证了TAR方法的有效性，展示了其在应对各种复杂攻击时的鲁棒性。(红队评估是一种在网络安全和机器学习领域常用的测试方法，它通过模拟攻击者的行为来评估系统或模型的安全性和防御能力。红队通常扮演“敌方”角色，主动寻找和利用系统的漏洞，以测试系统在真实攻击场景下的表现。这种方法帮助识别和修复安全漏洞，使系统在面对潜在的实际攻击时更加稳健。这篇文章中研究人员通过设计多个测试对手，这些对手模拟了各种可能的攻击策略，试图篡改或破坏大语言模型的功能。文章中提到进行了28个不同的红队评估测试，每个测试都旨在突破TAR的防护机制。)文章中的攻击方式涉及通过微调大语言模型的权重来篡改其行为。攻击者可以在模型的开放权重上进行少量微调，使其在特定情况下产生不希望的输出。例如，攻击者可能会在输入特定触发词时，让模型生成有害内容或偏离其正常功能。\\ \hline
-   \cite{attack04} & arXiv preprint & 2024 & 这是一篇综述。本文主要介绍了以下攻击方式：\begin{itemize}
-    \item 对抗性攻击：通过对输入数据进行微小的扰动，这些扰动虽然对人类几乎不可见，但会导致模型产生显著错误的输出，例如在图像分类中，可能会使模型将一个正常的图像误分类为完全不同的类别；
-    \item 后门攻击：和之前咱做的一样；
-    \item 数据中毒攻击：攻击者向模型的训练数据中注入恶意样本，这些样本会导致模型在遇到类似数据时输出错误结果，例如在物体识别任务中，中毒数据可能会导致模型误将无害物体识别为威胁；
-    \item 模型逃逸：攻击者通过调整输入或模型参数，试图找到绕过模型防御机制的方法，使模型输出不受控制的内容，这种攻击常用于测试模型的防御效果；
-    \item 多模态攻击：针对处理多种类型输入（如文本和图像）的模型，攻击者通过操纵一种模态的输入来影响另一种模态的输出，例如在多模态对话系统中，通过改变图像输入可能会影响系统的文本回应；
-    \item 跨语言攻击：在多语言任务中，攻击者通过在一种语言中引入扰动来影响模型在另一种语言中的表现，这类攻击特别针对多语言翻译或生成模型，可能导致不同语言间的翻译不准确或失真。
-    \end{itemize}\\ \hline
-   \cite{attack05} &  Advances in Neural Information Processing Systems 34 (NeurIPS 2021) & 2021 & 本篇文章讨了如何保护通过“彩票假设”（Lottery Ticket Hypothesis, LTH）找到的稀疏子网络（即“中奖票”）的所有权。文章提出了一种新的基于稀疏结构信息的验证方法，通过在网络的稀疏结构中嵌入签名来进行所有权验证。这种方法能够在白盒和黑盒场景下保护模型的知识产权，并且对细微调整（如微调和剪枝）具有很强的鲁棒性。研究还通过大量实验验证了该方法在多种模型（如ResNet-20、ResNet-18、ResNet-50）和数据集（如CIFAR-10和CIFAR-100）上的有效性，展示了其在应对移除攻击和模糊攻击时的坚韧性。具体攻击方式有：细微调整（Fine-tuning）攻击：对模型进行微调来改变模型的权重值，同时希望不改变网络的稀疏结构。这种攻击旨在通过调整权重，试图使嵌入的签名信息变得不可辨认或无效。然而，由于嵌入的信息是基于网络的稀疏结构（即被剪枝后的模型结构），细微调整难以改变这一基础结构，从而无法有效移除签名。剪枝（Pruning）攻击：攻击者尝试通过进一步剪枝来移除嵌入的签名信息。这种攻击的目的是通过减少模型的非零参数，使得嵌入的结构信息丢失。然而，文章中提出的嵌入方法确保了签名信息在极端稀疏的情况下仍能保留，即使剪枝比例达到一定程度，签名依然可以从稀疏结构中提取出来。模糊攻击（Ambiguity Attacks）：攻击者试图通过制造伪签名或模糊原有签名的信息来混淆所有权验证。这种攻击可能包括添加噪声、篡改稀疏结构等手段，旨在使得验证机制无法区分真实的所有权签名和伪造的信息。然而，文章中的验证方法通过设计稳健的结构嵌入机制，使得这种模糊攻击难以成功。(“签名”指的是嵌入到神经网络稀疏结构中的一种独特的标识信息。这种签名通过在模型的剪枝过程中，利用网络的稀疏性来实现。具体而言，当模型被剪枝后，一部分神经元和连接被移除，剩余的结构会呈现出一种特定的稀疏模式。作者通过在这种稀疏模式中嵌入一个特定的结构或模式，这个模式就是所谓的“签名”。这种签名是不可见的，但可以通过特定的验证过程来提取和识别。其主要功能是为网络的所有权提供证据，类似于给模型打上了一个“水印”。当有人试图非法复制或篡改模型时，这个嵌入的签名仍然可以被识别出来，从而验证模型的归属。签名的鲁棒性设计使其能够抵抗常见的攻击方式（如微调和进一步的剪枝），即使模型经历了这些操作，签名依然可以从其稀疏结构中被提取出来，证明模型的所有权。)(模型的所有权是指对一个机器学习模型（如神经网络模型）所拥有的法律和知识产权。所有权通常由开发者或公司拥有，表示他们对模型的设计、训练数据、训练方法以及最终生成的模型参数等有控制权和排他性使用权。这意味着只有模型的所有者有权利决定如何使用、修改、发布或授权使用该模型。（可能涉及到知识产权保护、商业机密的保密）)\\ \hline
-   \cite{attack06} & Portail HAL theses(theses.hal.science) & 2022 & 这篇文章有185页。本篇文章讨论了如何通过数字水印技术来保护机器学习模型的知识产权，防止模型被盗用。文章首先提供了当前水印技术的概述，并进一步扩展了这些技术在图像分类任务之外的应用，涵盖了回归、机器翻译和强化学习模型。作者还提出了针对模型托管平台的伪造攻击（即试图通过伪造水印来绕过验证）并介绍了一种基于公平性的水印技术，以增强模型在黑盒环境中的安全性。实验结果表明，这些水印技术不仅可以有效防止模型盗用，还能够在面对各种攻击时保持鲁棒性。
-   数字水印是一种嵌入信息的技术，用于在数字内容（如图像、音频、视频或机器学习模型）中隐藏特定的信息，以表明所有权或版权。对于机器学习模型来说，数字水印是一种通过特定算法将标识信息嵌入到模型的权重、结构或输出中的技术。这种标识信息通常是不可见或难以察觉的，但可以通过特定的提取过程来验证。（数字水印的目的有：知识产权保护：开发者可以通过在模型中嵌入水印来证明模型的所有权，防止未经授权的复制和使用；盗版检测：如果一个模型被盗用或未经许可发布，水印可以作为证据，证明模型的来源和合法所有者；内容跟踪：水印可以帮助追踪模型的使用情况，尤其是在多个平台或用户之间共享时，确保模型的使用符合许可协议。） \\ \hline
+   Flip\cite{jha2023label} & Neurips(2023) &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
+   % \cite{yang2023data} & ICML(2023) & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
+   Chameleon\cite{dai2023chameleon} & ICML(2023) & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
+   Gradient Control\cite{gu2023gradient} & ACL(2023) & 这篇文章提出了一种新的梯度控制方法，旨在解决参数高效调优（PET）过程中后门攻击的遗忘问题。通过将后门注入过程视为多任务学习，文章引入了跨层梯度幅度归一化和层内梯度方向投影两种策略，以减少不同任务之间的梯度冲突和梯度大小的不平衡，从而增强后门攻击在用户微调模型后的效果。实验结果表明，该方法在情感分类和垃圾邮件检测任务中显著提高了后门攻击的持久性和有效性。 \\ \hline
+   A3FL\cite{zhang2024a3fl} & Neurips(2024) & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
+   Shadowcast\cite{xu2024shadowcast} & Arxiv(2024) & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
+   BadCLIP\cite{liang2024badclip} & CVPR(2024) & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
+   ImgTrojan\cite{tao2024imgtrojan} & arxiv(2024) & 文章主要讨论了一种名为“ImgTrojan”的攻击方法，该方法旨在通过在视觉语言模型（VLM）的训练数据中注入恶意的图像-文本对，从而突破模型的安全屏障。这种方法通过数据投毒的方式，将原本无害的图像与恶意的文本提示关联起来，使得经过投毒训练的模型在遇到这些图像时，可能生成有害的内容。这种攻击方式在实验中展示了极高的成功率，即使在训练数据中仅包含极少量的投毒样本。 \\ \hline
+   % \cite{attack01} & arXiv preprint & 2024 & 本篇文章次揭示了在联邦学习环境下对大语言模型（LLM）进行指令调优时存在的安全漏洞。文章提出了一种简洁但有效的安全攻击方法，恶意客户端通过使用未对齐的数据来训练本地模型，从而大幅度削弱了全球模型的安全对齐性（“未对齐的数据”，是指那些与预期的安全或伦理规范不一致的数据。例如，未对齐的数据可能包含有害的、误导性的或是不道德的信息，而这些信息在普通情况下不会被用于训练模型）。实验表明，该攻击方法能够将模型的安全性降低高达70\%，而现有的防御方法在应对此类攻击时几乎无效，仅能提高4\%的安全性。为了解决这一问题，作者进一步提出了一种新的事后防御方法，即通过服务器端生成对齐数据并进一步对全局模型进行微调，从而增强模型的安全性（中央服务器在接收到各个客户端的更新后，会主动生成一组对齐的数据。这些对齐的数据是预先定义好的，确保与预期的安全和伦理规范一致。这些数据可能包含严格筛选过的内容，如道德上中立或积极的文本片段）。实验结果显示，这种防御方法能够将模型的安全性提高最多69\%，且不显著降低模型的有效性。（这篇看完了发现不是视觉大模型） \\ \hline
+   % \cite{attack02} & arXiv preprint & 2024 & 本篇文章探讨了一种针对大语言模型（LLMs）的新型训练方法，称为目标潜在对抗性训练（Targeted Latent Adversarial Training, LAT），文章提出了通过在模型的潜在表示（latent representations）中引入针对性的扰动，来更有效地消除模型中顽固的不良行为（如后门攻击和模型“越狱”）。(潜在表示是指在神经网络的中间层中，数据通过多层非线性变换后所形成的特征表示。这些表示通常处于更高的抽象层次，与原始输入相比，能够捕捉到数据的深层次特征。在视觉大模型中，这些潜在表示可能包括图像的边缘、形状、纹理等更抽象的特征，而不再是具体的像素值。潜在表示在模型中扮演着至关重要的角色，因为它们是模型用来进行预测和决策的核心特征。)(针对性的扰动是指在训练或评估过程中，特意对模型的输入或潜在表示进行细微的修改或扰动，以诱导模型产生特定的（通常是不希望的）行为。通过这种方法，可以测试和增强模型在面对各种攻击时的鲁棒性。在本文中，作者使用潜在空间中的针对性扰动来模拟攻击，目的是强化模型的防御能力，使其能够抵抗类似的实际攻击，如后门攻击或越狱行为。)研究表明，与传统的对抗性训练相比，目标潜在对抗性训练可以显著提高模型抵抗这些攻击的能力，同时对模型的整体性能影响较小。文章通过实验验证了该方法在增强模型鲁棒性方面的有效性，尤其是在面对未知触发条件的后门攻击时，表现出色。  \\ \hline
+   % \cite{attack03} & arXiv preprint & 2024 & 本文探讨了开放权重大语言模型（LLMs）在面对篡改攻击时的脆弱性，并提出了一种名为TAR（Tampering Attack Resistance）的方法，旨在增强这些模型的抗篡改能力。文章指出，现有的安全防护措施，如拒绝机制和偏好训练，容易在少量微调步骤后被攻击者绕过，导致模型被恶意修改。为此，TAR方法通过对抗性训练和元学习，设计了一种新的防护机制，使得即使在经历数千步的微调攻击后，模型仍能保持其原有的安全防护功能。实验结果显示，与现有方法相比，TAR显著提高了模型的抗篡改能力，同时保留了模型的正常功能。研究还通过大量红队评估验证了TAR方法的有效性，展示了其在应对各种复杂攻击时的鲁棒性。(红队评估是一种在网络安全和机器学习领域常用的测试方法，它通过模拟攻击者的行为来评估系统或模型的安全性和防御能力。红队通常扮演“敌方”角色，主动寻找和利用系统的漏洞，以测试系统在真实攻击场景下的表现。这种方法帮助识别和修复安全漏洞，使系统在面对潜在的实际攻击时更加稳健。这篇文章中研究人员通过设计多个测试对手，这些对手模拟了各种可能的攻击策略，试图篡改或破坏大语言模型的功能。文章中提到进行了28个不同的红队评估测试，每个测试都旨在突破TAR的防护机制。)文章中的攻击方式涉及通过微调大语言模型的权重来篡改其行为。攻击者可以在模型的开放权重上进行少量微调，使其在特定情况下产生不希望的输出。例如，攻击者可能会在输入特定触发词时，让模型生成有害内容或偏离其正常功能。\\ \hline
+   % \cite{attack04} & arXiv preprint & 2024 & 这是一篇综述。本文主要介绍了以下攻击方式：\begin{itemize}
+   %  \item 对抗性攻击：通过对输入数据进行微小的扰动，这些扰动虽然对人类几乎不可见，但会导致模型产生显著错误的输出，例如在图像分类中，可能会使模型将一个正常的图像误分类为完全不同的类别；
+   %  \item 后门攻击：和之前咱做的一样；
+   %  \item 数据中毒攻击：攻击者向模型的训练数据中注入恶意样本，这些样本会导致模型在遇到类似数据时输出错误结果，例如在物体识别任务中，中毒数据可能会导致模型误将无害物体识别为威胁；
+   %  \item 模型逃逸：攻击者通过调整输入或模型参数，试图找到绕过模型防御机制的方法，使模型输出不受控制的内容，这种攻击常用于测试模型的防御效果；
+   %  \item 多模态攻击：针对处理多种类型输入（如文本和图像）的模型，攻击者通过操纵一种模态的输入来影响另一种模态的输出，例如在多模态对话系统中，通过改变图像输入可能会影响系统的文本回应；
+   %  \item 跨语言攻击：在多语言任务中，攻击者通过在一种语言中引入扰动来影响模型在另一种语言中的表现，这类攻击特别针对多语言翻译或生成模型，可能导致不同语言间的翻译不准确或失真。
+   %  \end{itemize}\\ \hline
+   % \cite{attack05} &  Advances in Neural Information Processing Systems 34 (NeurIPS 2021) & 2021 & 本篇文章讨了如何保护通过“彩票假设”（Lottery Ticket Hypothesis, LTH）找到的稀疏子网络（即“中奖票”）的所有权。文章提出了一种新的基于稀疏结构信息的验证方法，通过在网络的稀疏结构中嵌入签名来进行所有权验证。这种方法能够在白盒和黑盒场景下保护模型的知识产权，并且对细微调整（如微调和剪枝）具有很强的鲁棒性。研究还通过大量实验验证了该方法在多种模型（如ResNet-20、ResNet-18、ResNet-50）和数据集（如CIFAR-10和CIFAR-100）上的有效性，展示了其在应对移除攻击和模糊攻击时的坚韧性。具体攻击方式有：细微调整（Fine-tuning）攻击：对模型进行微调来改变模型的权重值，同时希望不改变网络的稀疏结构。这种攻击旨在通过调整权重，试图使嵌入的签名信息变得不可辨认或无效。然而，由于嵌入的信息是基于网络的稀疏结构（即被剪枝后的模型结构），细微调整难以改变这一基础结构，从而无法有效移除签名。剪枝（Pruning）攻击：攻击者尝试通过进一步剪枝来移除嵌入的签名信息。这种攻击的目的是通过减少模型的非零参数，使得嵌入的结构信息丢失。然而，文章中提出的嵌入方法确保了签名信息在极端稀疏的情况下仍能保留，即使剪枝比例达到一定程度，签名依然可以从稀疏结构中提取出来。模糊攻击（Ambiguity Attacks）：攻击者试图通过制造伪签名或模糊原有签名的信息来混淆所有权验证。这种攻击可能包括添加噪声、篡改稀疏结构等手段，旨在使得验证机制无法区分真实的所有权签名和伪造的信息。然而，文章中的验证方法通过设计稳健的结构嵌入机制，使得这种模糊攻击难以成功。(“签名”指的是嵌入到神经网络稀疏结构中的一种独特的标识信息。这种签名通过在模型的剪枝过程中，利用网络的稀疏性来实现。具体而言，当模型被剪枝后，一部分神经元和连接被移除，剩余的结构会呈现出一种特定的稀疏模式。作者通过在这种稀疏模式中嵌入一个特定的结构或模式，这个模式就是所谓的“签名”。这种签名是不可见的，但可以通过特定的验证过程来提取和识别。其主要功能是为网络的所有权提供证据，类似于给模型打上了一个“水印”。当有人试图非法复制或篡改模型时，这个嵌入的签名仍然可以被识别出来，从而验证模型的归属。签名的鲁棒性设计使其能够抵抗常见的攻击方式（如微调和进一步的剪枝），即使模型经历了这些操作，签名依然可以从其稀疏结构中被提取出来，证明模型的所有权。)(模型的所有权是指对一个机器学习模型（如神经网络模型）所拥有的法律和知识产权。所有权通常由开发者或公司拥有，表示他们对模型的设计、训练数据、训练方法以及最终生成的模型参数等有控制权和排他性使用权。这意味着只有模型的所有者有权利决定如何使用、修改、发布或授权使用该模型。（可能涉及到知识产权保护、商业机密的保密）)\\ \hline
+   % \cite{attack06} & Portail HAL theses(theses.hal.science) & 2022 & 这篇文章有185页。本篇文章讨论了如何通过数字水印技术来保护机器学习模型的知识产权，防止模型被盗用。文章首先提供了当前水印技术的概述，并进一步扩展了这些技术在图像分类任务之外的应用，涵盖了回归、机器翻译和强化学习模型。作者还提出了针对模型托管平台的伪造攻击（即试图通过伪造水印来绕过验证）并介绍了一种基于公平性的水印技术，以增强模型在黑盒环境中的安全性。实验结果表明，这些水印技术不仅可以有效防止模型盗用，还能够在面对各种攻击时保持鲁棒性。
+   % 数字水印是一种嵌入信息的技术，用于在数字内容（如图像、音频、视频或机器学习模型）中隐藏特定的信息，以表明所有权或版权。对于机器学习模型来说，数字水印是一种通过特定算法将标识信息嵌入到模型的权重、结构或输出中的技术。这种标识信息通常是不可见或难以察觉的，但可以通过特定的提取过程来验证。（数字水印的目的有：知识产权保护：开发者可以通过在模型中嵌入水印来证明模型的所有权，防止未经授权的复制和使用；盗版检测：如果一个模型被盗用或未经许可发布，水印可以作为证据，证明模型的来源和合法所有者；内容跟踪：水印可以帮助追踪模型的使用情况，尤其是在多个平台或用户之间共享时，确保模型的使用符合许可协议。） \\ \hline
     % \endfoot

### 2024-08-17 attack-zh.tex
attack: survey by wb
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \begin{document}
-\subsection{Related Work}
-我们将现有针对模型的后门攻击分为两种，即空间隐蔽性后门攻击和时间隐蔽性后门攻击。
+\subsection{Related work}
+\subsubsection{Backdoor attack}
+后门攻击对深度学习模型构成了严重的安全威胁，它旨在通过对模型输入添加特殊扰动来诱导目标模型产生不当行为，例如图像分类器中的错误分类等。我们将现有针对模型的后门攻击分为两种，即空间隐蔽性后门攻击和时间隐蔽性后门攻击。
 
@@
 
+\subsubsection{Defenses}
+在当前深度学习模型的安全性研究中，针对后门攻击的防御措施主要可以分为两大类：后门检测和后门消除。% Backdoor Mitigation or Elimination
+
+后门检测主要集中在识别模型中已经存在的后门攻击。在这一类中，SEER\cite{zhu2024seer}提出了一种用于视觉-语言模型的后门检测算法，通过在图像和文本模态的特征空间中联合搜索目标文本和图像触发器，成功实现了在多种场景下的后门检测。ASSET\cite{pan2023asset}提出了一种通过主动诱导后门样本和干净样本在模型行为上的差异，从而实现跨多种深度学习范式的鲁棒后门数据检测方法，并在端到端监督学习、自监督学习和迁移学习中表现出色。DECREE\cite{feng2023detecting}提出了一种用于检测自监督学习中预训练图像编码器后门的创新方法，该方法无需依赖标签数据或下游分类器，并在多种数据集和攻击类型下展现了极高的检测准确率。
+
+后门消除则侧重于通过各种技术手段来消除或减轻后门攻击的影响。Semantic Shield\cite{ishmam2024semantic}通过强制模型在训练时对齐图像区域与外部知识，以防御视觉-语言模型中的后门和数据中毒攻击，从而显著提高了模型的鲁棒性。MCLDef\cite{yue2023model}提出了一种基于模型对比学习的两阶段后门防御方法，通过收缩或破坏中毒数据在特征空间中的聚类，并将中毒数据的特征拉向其干净对应物，从而有效消除深度神经网络中的后门，并在不显著降低模型准确性的情况下提高防御效果。DPoE\cite{liu2023shortcuts}提出了一种基于端到端集成的后门防御框架，通过结合浅层模型和主模型来捕捉和抑制后门触发器，从而有效应对各种显性和隐性的后门攻击，同时减轻噪声标签对模型性能的影响。PSIM\cite{zhao2024defending}提出了一种基于参数高效微调的防御模块，通过利用样本的置信度来识别被后门攻击污染的样本，显著增强了模型抵御权重中毒后门攻击的能力，并在不影响模型准确性的情况下有效过滤出被污染的样本。CleanCLIP\cite{bansal2023cleanclip}通过在视觉和文本编码器上进行无监督微调，独立调整每种模态的表示，以削弱视觉-语言对比学习模型中由后门攻击引入的错误关联，从而有效减少后门攻击的影响，同时保持模型在正常数据上的性能。
+
+尽管这些方法在应对后门攻击方面展现了显著的效果，但它们在面对更隐蔽或复杂的攻击时可能表现不足，某些方法还依赖于外部知识或置信度的设定，导致误判或性能瓶颈，同时在实际应用中也增加了计算开销和训练时间，因此仍需进一步优化以提升整体性能和效率。
+
+% \begin{itemize}
+%     % \item catastrophically forget 灾难性遗忘
+%     \item detection-based methods, erasing-based methods
+%     \item 
+% \end{itemize}
+
 \onecolumn
 \begin{longtable}{|p{3.5cm}|p{2cm}|p{10.5cm}|} 
-    \caption{This is the caption for the long table}
+    \caption{Attack}
     \label{tabl:attack} \\ \hline
@@
 
+\newpage
+\onecolumn
+\begin{longtable}{|p{3.5cm}|p{2cm}|p{10.5cm}|} 
+    \caption{defense}
+    \label{tabl:defense} \\ \hline
+    Title & Conference & Main Content \\ \hline
+    \endfirsthead \hline
+    Title & Conference & Main Content \\ \hline 
+    \endhead \hline
+    SEER\cite{zhu2024seer} & AAAI 2024 & 这篇文章介绍了一种名为SEER的新型后门检测算法，专门用于检测视觉-语言模型中的后门攻击。研究的动机源于现有单模态模型（如图像分类模型）的后门检测方法无法直接应用于多模态模型（如视觉-语言模型）的复杂性和搜索空间的增加。为此，作者提出了一种新方法，通过在视觉和语言模态共享的特征空间中联合搜索图像触发器和恶意目标文本来检测后门。该方法的主要步骤包括：初始化目标文本和图像触发器的特征表示，设计优化算法在图像和文本空间中联合搜索可能的后门触发器和目标文本，并通过分析搜索结果来判断模型是否存在后门。实验结果表明，SEER在各种设置下能够以超过92\%的检测率成功识别视觉-语言模型中的后门，并且无需访问训练数据或了解下游任务。文章还比较了SEER与现有方法的效率，表明SEER在计算效率和检测效果方面均具有显著优势。\\ \hline
+
+    Semantic Shield\cite{ishmam2024semantic} & CVPR 2024 & 这篇文章提出了一种名为“Semantic Shield”的方法，旨在通过精细化知识对齐来防御视觉-语言模型中的后门和投毒攻击。研究的动机在于，随着大规模视觉-语言模型在实际应用中的广泛使用，这些模型变得容易受到攻击，如通过向训练数据中注入恶意数据来操纵模型行为。现有的防御方法通常无法有效应对这些攻击，尤其是在对比学习的多模态模型中。该方法通过引入外部知识来指导模型关注与外部知识对齐的视觉区域，从而避免模型学习到与攻击信号相关的错误关联。具体来说，研究人员使用大型语言模型（如Vicuna）从图像字幕中提取潜在的知识元素（KE），并通过对比学习的方式将这些KE与图像区域对齐。此外，模型的注意力机制也被调整，使其更加关注与KE高度对齐的图像区域，从而降低对受攻击区域的依赖。\\ \hline
+
+    DECREE\cite{feng2023detecting} & CVPR 2023 & 主要关注自监督学习中预训练图像编码器的后门检测问题，鉴于现有方法在处理不同类型的后门攻击时表现不一致，且通常需要标签数据或下游分类器，本文提出了一种无需标签数据或下游分类器的新方法。DECREE 通过利用输入图像特征的扰动性和鲁棒性之间的差异来识别潜在的后门攻击，采用了一种基于自适应优化的策略，有效地将干净样本与后门样本分离。 \\ \hline
+
+    ASSET\cite{pan2023asset} & USENIX 2023 & 这篇文章介绍了一种名为“ASSET”的方法，旨在跨多种深度学习范式中实现稳健的后门数据检测。研究动机是当前的后门检测方法在不同的深度学习设置（如自监督学习和迁移学习）中的表现差异很大，尤其在面对最新的干净标签后门攻击时，现有方法表现不佳。为了解决这一问题，作者提出了ASSET方法，它通过主动诱导后门样本和干净样本之间的模型行为差异来促进它们的分离。具体来说，ASSET采用了一个两步优化过程：首先在一个干净的基础数据集上最小化损失，然后在整个包含后门样本的训练集上最大化同样的损失，从而使后门样本和干净样本在损失值上出现显著差异，进而实现样本的分离和检测。\\ \hline
+
+    MCLDef\cite{yue2023model} & ACM MM 2023 & 这篇文章介绍了一种名为“基于模型对比学习的后门消除”（Model-Contrastive Learning for Backdoor Elimination，简称MCLDef）的新方法。研究的动机是当前的后门攻击对深度神经网络（DNNs）构成了显著威胁，而现有的后门防御方法在降低攻击成功率（ASR）的同时，往往会显著降低模型对干净数据的分类准确性（BA）。为了解决这一问题，作者提出了MCLDef方法，该方法通过模型对比学习来消除DNN中的后门，并最大限度地减少对BA的影响。具体来说，MCLDef通过定义正对和负对的特征对来进行对比学习：正对指的是干净数据样本与其中毒对应数据的特征表示，负对则是中毒数据样本在后门模型和纯化模型中的特征表示。通过对比学习，MCLDef能够缩小或消除中毒数据在特征空间中的聚类，并将中毒数据的特征拉向其干净对应样本的特征，从而有效地消除后门攻击带来的影响。 \\ \hline
+
+    DPoE\cite{liu2023shortcuts} & Arxiv 2023 & 这篇文章提出了一种名为DPoE（Denoised Product-of-Experts）的后门防御框架，旨在应对自然语言处理（NLP）模型中由多种不同触发器引发的后门攻击。研究的动机在于，现有的后门防御方法主要针对显式触发器，而难以有效应对隐式或多种触发器混合的复杂攻击。DPoE方法的核心思想是通过设计一个由两个模型组成的集成框架：一个浅层模型专门捕捉后门攻击中存在的“捷径”，即错误关联；另一个主模型则避免学习这些“捷径”。此外，DPoE引入了去噪设计来减轻由后门攻击者造成的标签翻转问题，从而进一步增强防御效果。 \\ \hline
+
+    PSIM\cite{zhao2024defending} & arxiv 2024 & 这篇文章的主要内容是探讨参数高效微调（PEFT）方法在语言模型中的安全问题，特别是在模型的预训练阶段被植入后门的情况下。这种攻击被称为“权重中毒后门攻击”，发生在模型的预训练阶段，攻击者通过在训练数据中加入特定的触发器，并使用这些数据训练模型，从而在模型的权重中嵌入后门。当微调后的模型遇到这些触发器时，模型会按照攻击者的意图输出错误的结果。本文的主要目的是揭示PEFT方法在面对这种预训练阶段的权重中毒后门攻击时的脆弱性。研究表明，与全参数微调方法相比，PEFT更容易受到这种攻击，攻击成功率接近100\%。为了解决这一问题，作者提出了一种名为“中毒样本识别模块”（PSIM）的防御方法，通过预测置信度来识别和过滤可能被植入后门的样本，从而有效防御这些攻击，同时保持模型的分类准确性。 \\ \hline
+
+    CleanCLIP\cite{bansal2023cleanclip} & ICCV 2023 & 这篇文章提出了一种名为CleanCLIP的方法，旨在减轻多模态对比学习模型（如CLIP）中数据投毒攻击的影响。研究动机是因为现有的多模态对比学习模型在训练过程中容易受到后门攻击的威胁，甚至少量的中毒样本就可以显著操控模型行为。CleanCLIP通过在模型预训练后进行微调来减弱这种攻击的影响。具体来说，该方法在微调过程中，通过同时应用多模态对比损失和自监督学习目标，使模型独立地学习每种模态（图像和文本）的表示，减少后门触发器与目标标签之间的错误关联。实验结果表明，CleanCLIP在不影响模型对干净样本性能的前提下，有效降低了多种后门攻击的成功率。此外，文章还讨论了不同的微调方法对清除后门触发器的效果，并发现CleanCLIP能够显著削弱这些攻击的影响。 \\ \hline
+\end{longtable}
+
 \bibliographystyle{IEEEtran}
-\bibliography{ref}
+\bibliography{attack_defense}
 

### 2024-08-17 attack-zh.tex
defense: survey by Me(Legendary Grand Tisfy)
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
     CleanCLIP\cite{bansal2023cleanclip} & ICCV 2023 & 这篇文章提出了一种名为CleanCLIP的方法，旨在减轻多模态对比学习模型（如CLIP）中数据投毒攻击的影响。研究动机是因为现有的多模态对比学习模型在训练过程中容易受到后门攻击的威胁，甚至少量的中毒样本就可以显著操控模型行为。CleanCLIP通过在模型预训练后进行微调来减弱这种攻击的影响。具体来说，该方法在微调过程中，通过同时应用多模态对比损失和自监督学习目标，使模型独立地学习每种模态（图像和文本）的表示，减少后门触发器与目标标签之间的错误关联。实验结果表明，CleanCLIP在不影响模型对干净样本性能的前提下，有效降低了多种后门攻击的成功率。此外，文章还讨论了不同的微调方法对清除后门触发器的效果，并发现CleanCLIP能够显著削弱这些攻击的影响。 \\ \hline
+
+    SEER\cite{defense01} & AAAI2024 & 这篇文章介绍了一种名为SEER的创新算法，用于检测视觉-语言模型（Vision-Language Models）中的backdoor攻击。backdoor攻击是一种攻击方式，攻击者可以在模型中植入“后门”，当特定触发条件满足时，模型会表现出异常行为。为了防御这种攻击，SEER算法通过联合搜索图像中的触发器（触发器是攻击者放入图像中的特殊标记或模式，用于激活模型中的后门）和与之关联的恶意目标文本来检测是否存在backdoor。SEER算法的具体防御步骤如下：首先，SEER算法会初始化一个特定的文本表示，该表示是基于一个词典中的所有文本的平均特征。这一步的目的是为后续的搜索过程提供一个合理的起点。接下来，SEER通过优化算法在共享的特征空间中搜索图像中的潜在触发器和与之相关联的目标文本。这里的特征空间是指模型用来同时表示图像和文本的多维空间。SEER的目标是找到一种图像模式（即触发器）和一个目标文本，这两者在特征空间中具有非常高的相似性（这意味着触发器和目标文本之间存在很强的关联）。在搜索过程中，SEER会根据相似性计算结果来识别可能的backdoor。如果发现模型中存在一个图像触发器与某个目标文本之间的强关联，SEER就会标记该模型为可能存在backdoor。图像触发器：这是攻击者嵌入在图像中的特定模式或标记，当模型看到带有这个标记的图像时，会触发backdoor行为。比如在一张图片的角落放置一个特定的形状或颜色。强关联：在特征空间中，两个对象（如图像和文本）之间的高相似性意味着它们在这个空间中的表示非常接近，这种情况称为强关联。对于backdoor检测来说，如果一个图像触发器和目标文本之间的相似性过高，就意味着模型可能已经被攻击。通过这些步骤，SEER算法能够有效地检测出是否存在backdoor攻击，尤其是在模型训练数据和具体下游任务未知的情况下。这种方法不仅提高了检测的效率，而且在各种攻击场景下，SEER的检测准确率超过了92\%，表现出极高的可靠性和适应性。 \\ \hline
+    Revisiting Backdoor Attacks against Large Vision-Language Models\cite{defense02} & Arxiv(2024) & 这篇文章研究了视觉-语言大模型（LVLMs）在指令调优阶段面临的backdoor攻击的普遍性，特别是在训练和测试数据分布不一致的实际场景中。文章通过实验证明，大多数现有的backdoor攻击方法在这种跨域场景下的泛化性较差，但通过对攻击触发器的优化，文章展示了一种能够显著提高攻击成功率的新方法。具体防御步骤如下：1.
+攻击触发器设计：文章首先分析了现有backdoor攻击的触发器模式，发现其与具体图像或模型无关的触发器往往具有更好的泛化能力。因此，作者设计了一种新的触发器模式，使其能够在不同的图像和文本域偏移的情况下，依然有效地触发backdoor攻击。2.
+多模态数据的指令调优：为了构建一个多样化的指令集，文章采用了稳定扩散模型和大型语言模型（如GPT-3.5）来改变图像和文本域。具体而言，作者使用风格转换技术来改变图像的艺术风格，并通过文本摘要和扩展来调整文本信息密度。这些改变旨在测试不同数据分布下的backdoor攻击效果。3.
+实验验证：通过在多个标准图像描述数据集上的实验，文章验证了不同类型backdoor攻击在跨域场景中的表现。结果表明，尽管图像域的变化通常会削弱大多数攻击的泛化性，但经过优化的触发器模式，如本文提出的新方法，能够显著提高攻击成功率，在某些场景下成功率甚至达到97\%以上。触发器：这是在模型训练过程中故意植入的特定模式，当模型在推理阶段遇到这种模式时，会表现出预设的异常行为。简单来说，触发器就像是一个隐藏在图像或文本中的“密码”，当模型看到这个“密码”时，它就会按照攻击者的预期做出反应。泛化能力：泛化能力指的是一个攻击方法在面对与训练时不同的数据分布时，仍能保持其攻击效果的能力。对于backdoor攻击来说，泛化能力越强，攻击就越难以被发现和防御。通过这些步骤，文章展示了在视觉-语言模型中，如何通过设计更具适应性的触发器，增强backdoor攻击的泛化性。这项研究强调了在跨域数据场景中进行防御的重要性，并指出现有防御方法可能无法完全防范这种复杂的攻击模式。 \\ \hline
+    BadVLMDriver\cite{defense03} & Arxive(2024) & 这篇文章提出了一种名为BadVLMDriver的物理backdoor攻击方法，专门针对集成了视觉-语言模型（VLMs）的自动驾驶系统。与传统依赖数字修改的backdoor攻击不同，BadVLMDriver利用日常生活中的常见物理物体作为触发器，例如红色气球，来引发自动驾驶系统中的不安全行为，如突然加速。通过这种方法，攻击者可以在实际场景中诱导自动驾驶汽车做出危险的决定，展示了集成VLMs的自动驾驶技术所面临的严重安全威胁。具体的攻击与防御步骤如下：1.
+攻击触发器嵌入：首先，攻击者使用基于自然语言指令的生成模型来生成backdoor训练样本。在这些样本中，攻击者利用图像编辑技术将物理触发器（如气球）嵌入到图像中，并通过大型语言模型（LLM）生成包含恶意行为的文本响应。2.
+视觉指令调优：随后，利用这些backdoor样本对VLM进行调优。在此过程中，VLM不仅学习了触发器与恶意行为之间的映射，同时保留了模型在正常输入下的功能。为了增强攻击效果，文章采用了一种新颖的视觉指令调优方案，在调优过程中结合了带有触发器的backdoor样本和不带触发器的正常样本。3.
+防御策略：针对这种攻击，文章建议使用增量学习的方式进行防御，即在post-training阶段采用另一组正常样本对模型进行进一步调优。这种方法可以显著降低backdoor攻击的成功率，但其代价与常规的模型微调过程相当，对于依赖第三方VLM的自动驾驶公司来说可能具有挑战性。物理触发器：物理触发器是指现实生活中的物体，当这些物体出现在自动驾驶系统的摄像头视野中时，会触发VLM做出预设的恶意行为。增量学习：增量学习是一种防御策略，通过在模型训练完成后进一步微调模型，以降低backdoor攻击的效果。通过这项研究，文章强调了开发强大防御机制的紧迫性，以保护自动驾驶技术免受类似的物理backdoor攻击。 \\ \hline
+    SurveyLVLM\cite{defense04} & JOURNAL OF LATEX CLASS FILES(2024) & 这篇文章是一篇综述，系统地回顾了当前针对大型视觉-语言模型（LVLMs）的攻击方法，涵盖了各种现有的攻击形式，如对抗攻击（adversarial attacks）、越狱攻击（jailbreak attacks）、提示注入攻击（prompt injection attacks）以及数据投毒和后门攻击（data poisoning/backdoor attacks）。文章不仅介绍了每种攻击的具体实施方法，还探讨了它们的优缺点和背后的脆弱性。此外，文章还总结了当前用于LVLM攻击的资源，如数据集、模型和评估指标，最后提出了未来的研究方向，强调了持续发展和改进LVLMs安全措施的重要性。具体攻击方法：1.
+对抗攻击（Adversarial Attacks）：通过在输入数据中引入细微的扰动，导致模型产生错误的或不期望的输出。这种攻击可以在白盒、灰盒和黑盒环境中实施，取决于攻击者对模型内部信息的掌握程度。2.
+越狱攻击（Jailbreak Attacks）：通过操纵输入，使得模型突破其原有的限制，输出有害或未经授权的内容。这种攻击通常利用对抗性扰动或提示操作来实现，目的是绕过模型的安全防线。3.
+提示注入攻击（Prompt Injection Attacks）：通过操纵视觉或文本提示，注入有害指令，从而改变模型的行为或输出。这种攻击可能导致模型生成错误、偏颇或有害的响应，尤其在依赖精确和准确响应的系统中具有危险性。4.
+数据投毒/后门攻击（Data Poisoning/Backdoor Attacks）：攻击者在模型训练过程中故意引入恶意数据，导致模型在推理阶段表现异常。后门攻击通常在训练数据中嵌入触发器，当触发器被激活时，模型会表现出特定的有害行为。对抗攻击：这是通过在输入数据上施加微小的扰动，使得模型产生错误或预期外的输出。越狱攻击：指攻击者通过操纵输入数据，绕过模型的安全措施，使模型执行未经授权的操作。提示注入：通过在提示信息中注入恶意内容来改变模型的输出。数据投毒：通过在训练数据中加入恶意样本，使模型学习到错误的模式。未来研究方向：文章提出，未来研究应重点探索如何在没有模型内部信息的情况下实施攻击，提升攻击的跨模型适应性，以及如何更好地评估和对比不同攻击方法的有效性。 \\ \hline
+    Semantic Shield\cite{defense05} & CVPR2024 & 这篇文章提出了一种名为Semantic Shield的防御方法，旨在保护视觉-语言模型（VLMs）免受backdooring和数据投毒攻击的威胁。该方法通过细粒度的知识对齐机制来抵御攻击，使模型在训练过程中更加关注与外部知识对齐的视觉区域，从而避免学习到攻击者引入的虚假关联。具体的防御步骤如下：1.
+知识元素提取：首先，Semantic Shield使用大语言模型（如Vicuna）从每个图像的字幕中提取潜在的视觉知识元素（Knowledge Elements，KEs）。这些KEs包含了图像中可以帮助识别目标的特征，如“厚毛皮”或“锋利的爪子”。2.
+图像块与KE对齐：在训练过程中，Semantic Shield引入了一个新的目标函数，强制模型将图像块与相应的KE对齐。具体来说，模型通过计算图像块和KE的相似度来判断哪些图像块更相关，并优先关注这些与KE高度对齐的区域。3.
+基于KE的注意力调制：为了进一步增强防御效果，Semantic Shield调整了视觉Transformer模型的注意力机制，使其更关注与KE对齐的图像区域。攻击者通常在图像中随机注入触发器或噪声，这些区域通常与KE的对齐度较低，因此通过这种调制，模型能够有效忽略这些被攻击的区域。4.
+动态对比损失加权：为了降低受攻击样本在模型训练中的影响，Semantic Shield在对比学习过程中引入了动态加权机制。模型会根据图像块与KE的整体对齐度调整每个样本的损失权重，从而降低被攻击样本对模型的干扰。知识元素（KEs）：KEs是从图像字幕中提取出的视觉特征或属性，用于帮助模型更好地理解图像内容，例如“厚毛皮”代表动物的一个特征。对比学习：一种用于训练模型的技术，目的是将相似的样本在特征空间中拉近，将不相似的样本拉远。通过这些步骤，Semantic Shield能够显著提高VLMs在面对backdooring和数据投毒攻击时的鲁棒性，同时保持模型的整体性能。实验结果表明，Semantic Shield在多个数据集和攻击场景下表现出色，显著优于现有的防御方法。 \\ \hline
+    VL-Trojan\cite{defense06} & NeurIPS2024 & 这篇文章提出了一种名为VL-Trojan的多模态指令backdoor攻击方法，专门针对自回归视觉语言模型（Autoregressive Visual Language Models，VLMs）。文章揭示了现有backdoor攻击在自回归VLMs中的局限性，特别是在视觉编码器被冻结且攻击者只能有限或黑盒访问目标模型的情况下。为了解决这些问题，VL-Trojan通过隔离与聚类策略来生成图像触发器，并通过字符级迭代生成文本触发器，以提升攻击的有效性和转移性。具体攻击步骤如下：1.
+图像触发器生成：文章通过对比优化方法来生成图像触发器，即使在视觉编码器被冻结的情况下，依然可以将中毒样本的特征与干净样本的特征分离开来。具体而言，攻击者生成一个触发器，能够将中毒图像的特征与干净图像的特征在特征空间中进行有效的隔离和聚类。2.
+文本触发器生成：为了增强攻击的转移性，VL-Trojan提出了字符级迭代搜索方法生成文本触发器。这种方法通过逐步优化字符组成的文本触发器，以最大化中毒提示和干净提示之间的特征不相似度。3.
+反向训练：在生成触发器后，攻击者将这些触发器嵌入到一组中毒样本中，并将这些样本加入到指令调优数据集中。通过使用这些中毒样本进行反向训练，攻击者能够在推理过程中，诱导模型在遇到这些触发器时生成预设的响应。通过这些步骤，VL-Trojan在有限访问和黑盒设置下依然能够实现有效的backdoor攻击，成功率高达99.82\%，显著超越了其他基准方法。 \\ \hline
+    ROCLIP\cite{defense07} & NeurIPS2023 & 这篇文章提出了一种名为ROCLIP的防御方法，用于在预训练阶段保护多模态视觉语言模型（如CLIP）免受数据投毒和后门攻击的威胁。ROCLIP通过破坏受攻击的图像和文本对之间的关联，有效地防止了这些攻击在模型训练期间的成功。具体的防御步骤如下：1.
+随机生成的文本池：ROCLIP方法在训练期间保持一个由随机选择的文本组成的池。与传统方法不同，ROCLIP不再将每个图像与其对应的字幕匹配，而是将每个图像与池中与其最相似的文本匹配。通过这种方式，ROCLIP能够有效破坏投毒图像和有害字幕之间的关联。2.
+数据增强：在图像和文本上应用各种增强策略进一步加强防御效果。这些增强措施包括图像的随机裁剪、水平翻转、颜色抖动和文本的同义词替换等。通过增强，ROCLIP不仅降低了攻击成功率，还提升了模型在下游任务中的表现。3.
+分批训练：ROCLIP采用分批训练策略，每隔几轮更新一次图像与最相似文本的匹配对，并在其余轮次中使用标准的CLIP损失进行训练。这一策略确保了即使在面对强力攻击时，ROCLIP依然能够有效防御。实验结果：实验表明，ROCLIP能够显著降低投毒和后门攻击的成功率。在应对数据投毒攻击时，ROCLIP将攻击成功率从93.75\%降至12.5\%，而对于后门攻击，成功率从78\%降至0\%。同时，ROCLIP还能提升模型的线性探测准确率，并且在零样本任务中的表现与CLIP相当。 \\ \hline
+    FABE\cite{defense08} & ICML2024 & 这篇文章提出了一种基于因果推断的防御框架，名为前门调整背门消除（Front-door Adjustment for Backdoor Elimination，FABE），旨在保护语言模型（LLMs）免受backdoor攻击。与传统的依赖特定触发器特征的防御方法不同，FABE通过构建前门变量来区分伪相关和真实因果关系，有效地防止各种类型的backdoor攻击。具体防御步骤如下：1.
+前门变量生成：FABE使用一个经过微调的语言模型（称为防御模型）来生成前门变量。前门变量是一个与输入语义等价的文本，但其生成的预测结果不会受到backdoor攻击的影响。2.
+因果效应估计：通过前门调整，FABE将估算的因果效应分为两个阶段：首先计算输入文本对前门变量的影响，然后计算前门变量对最终预测的影响。这种方法通过精确的因果效应估计，有效地消除了由攻击触发器引入的混淆。3.
+防御效果评估：在多个数据集上，FABE显著降低了多种攻击策略的成功率。例如，FABE将攻击成功率从93.63\%降低到15.12\%，大幅度优于传统防御方法，显示了其在应对复杂backdoor攻击时的强大防御能力。通过这些步骤，FABE为语言模型的backdoor攻击防御提供了一个新的思路，克服了传统方法的局限性，尤其是在无法预先知道攻击特征的情况下。 \\ \hline
+    Shadowcast\cite{defense09} & arXiv(2024) & 这个和王波的一样，是特朗普和拜登那篇。这篇文章提出了Shadowcast，一种针对视觉语言模型（VLMs）的隐秘数据投毒攻击方法。Shadowcast通过生成视觉上与正常样本无异的投毒样本，使VLM在处理日常任务时输出错误或误导性的文本描述。这种攻击方法在两个场景中表现出极高的有效性：标签攻击（Label Attack）和说服攻击（Persuasion Attack）。标签攻击旨在让模型错误地识别图像的类别，而说服攻击则通过生成连贯但误导性的描述来影响用户对图像的理解。具体攻击步骤如下：1.
+文本生成：首先，攻击者使用一个预训练的视觉语言模型生成描述性文本，这些文本与投毒样本的图像内容匹配。随后，攻击者通过一个大语言模型对这些文本进行细化，以确保它们明确传达目标概念（如“健康食品”）。2.
+图像扰动：然后，攻击者对这些图像施加不可察觉的扰动，使得投毒图像在特征空间中接近原始概念图像，同时保持与目标概念描述一致。这种扰动使得VLM在训练时学习到错误的特征关联。3.
+投毒样本生成：最后，攻击者将这些被扰动的图像与相应的文本配对，形成投毒样本。在模型训练过程中，这些投毒样本会使模型错误地将原始概念图像与目标概念文本关联，从而实现攻击目的。实验结果：Shadowcast展示了其在不同攻击场景中的高效性，尤其在黑盒设置下，攻击成功率依然较高，表明了这种攻击方法的广泛适用性。此外，Shadowcast还展现了对抗数据增强和图像压缩技术的鲁棒性。 \\ \hline
+    Contextual Backdoor Attack\cite{defense10} & Springer2024 & 这篇文章提出了一种名为Contextual Backdoor Attack的新型攻击方法，旨在通过极少量的上下文提示数据对大型语言模型（LLMs）进行隐秘的背门攻击。此攻击方法特别针对由LLM生成的代码驱动的具身智能代理（如机器人和自动驾驶系统），通过在特定环境下使用上下文相关的触发器（文本或视觉触发器）来激活模型中的后门，从而导致具身智能代理在执行任务时表现出异常行为。具体的攻击步骤如下：1.
+生成和优化中毒示例：攻击者首先利用对抗性上下文生成技术，构建包含中毒提示的示例，并通过LLM评估器不断优化这些示例，以确保它们能够有效地感染目标LLM的上下文环境。2.
+双模态触发机制：在攻击实施中，文本触发器控制代码缺陷的生成，而视觉触发器则控制代码缺陷的执行。只有当用户输入包含特定触发词时，LLM才会生成带有缺陷的代码，且这些缺陷代码只有在环境中出现特定视觉触发器时才会被执行。3.
+代码缺陷模式：文章设计了五种攻击模式，包括恶意行为、代理可用性、关闭控制、偏见内容和隐私提取，分别针对具身智能代理的不同方面进行攻击。这些模式可以导致机器人执行错误的动作、延迟执行、提取用户隐私信息或生成具有种族偏见的内容。实验结果：实验表明，Contextual Backdoor Attack在多个任务上都表现出了很高的攻击成功率，并且在实际的自动驾驶系统中也能有效实施。此外，该攻击还展现出对抗检测机制的鲁棒性，难以被常规方法识别和防御。 \\ \hline
+
 \end{longtable}

### 2024-08-29 clip_lora.py
The normal recognition rate is 80% and the attack success rate is 6%.

@@ -89,7 +89,7 @@ test_loader = DataLoader(cifar100_test, batch_size=128, shuffle=False)
 num_workers = args.num_workers
 rounds = args.rounds
 round_to_start_attack = args.round_to_start_attack
-local_epochs = 5
+local_epochs = 20
 batch_size = 64
 logger.info(
     f"Number of workers: {num_workers}, Number of rounds: {rounds}, Round to start attack: {round_to_start_attack}"
@@ -337,6 +337,9 @@ for round in range(rounds):
 # save the summary of worker
 for idx, worker in enumerate(workers):
     csv_file = os.path.join(output_dir, f"woker{idx}_summary.csv")
+    df = pd.DataFrame(worker.train_summaries)
+    df.to_csv(csv_file, index=False)
+
 
 # save the model
 import datetime

### 2024-08-30 attack-zh.tex
docs: sth. by wb
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \subsection{Related work}
+\subsubsection{Federated Learning}
+Federated Learning
+
+\subsubsection{Fine Tuning}
+Fine Tuning
+
 \subsubsection{Backdoor attack}
@@
 \subsubsection{Defenses}
-在当前深度学习模型的安全性研究中，针对后门攻击的防御措施主要可以分为两大类：后门检测和后门消除。% Backdoor Mitigation or Elimination
+在当前深度学习模型的安全性研究中，针对后门攻击的防御措施主要可以分为两大类：后门检测和后门缓解。% Backdoor Mitigation or Elimination
 
-后门检测主要集中在识别模型中已经存在的后门攻击。在这一类中，SEER\cite{zhu2024seer}提出了一种用于视觉-语言模型的后门检测算法，通过在图像和文本模态的特征空间中联合搜索目标文本和图像触发器，成功实现了在多种场景下的后门检测。ASSET\cite{pan2023asset}提出了一种通过主动诱导后门样本和干净样本在模型行为上的差异，从而实现跨多种深度学习范式的鲁棒后门数据检测方法，并在端到端监督学习、自监督学习和迁移学习中表现出色。DECREE\cite{feng2023detecting}提出了一种用于检测自监督学习中预训练图像编码器后门的创新方法，该方法无需依赖标签数据或下游分类器，并在多种数据集和攻击类型下展现了极高的检测准确率。
+后门检测主要旨在识别模型中已存在的后门攻击。在这一类中，SEER\cite{zhu2024seer}提出了一种用于视觉-语言模型的后门检测算法，通过在图像和文本模态的特征空间中联合搜索目标文本和图像触发器，成功实现了在多种场景下的后门检测。ASSET\cite{pan2023asset}提出了一种通过主动诱导后门样本和干净样本在模型行为上的差异，从而实现跨多种深度学习范式的鲁棒后门数据检测方法，并在端到端监督学习、自监督学习和迁移学习中表现出色。DECREE\cite{feng2023detecting}提出了一种用于检测自监督学习中预训练图像编码器后门的创新方法，该方法无需依赖标签数据或下游分类器，且在多种数据集和攻击类型下表现出极高的检测准确率。
 
-后门消除则侧重于通过各种技术手段来消除或减轻后门攻击的影响。Semantic Shield\cite{ishmam2024semantic}通过强制模型在训练时对齐图像区域与外部知识，以防御视觉-语言模型中的后门和数据中毒攻击，从而显著提高了模型的鲁棒性。MCLDef\cite{yue2023model}提出了一种基于模型对比学习的两阶段后门防御方法，通过收缩或破坏中毒数据在特征空间中的聚类，并将中毒数据的特征拉向其干净对应物，从而有效消除深度神经网络中的后门，并在不显著降低模型准确性的情况下提高防御效果。DPoE\cite{liu2023shortcuts}提出了一种基于端到端集成的后门防御框架，通过结合浅层模型和主模型来捕捉和抑制后门触发器，从而有效应对各种显性和隐性的后门攻击，同时减轻噪声标签对模型性能的影响。PSIM\cite{zhao2024defending}提出了一种基于参数高效微调的防御模块，通过利用样本的置信度来识别被后门攻击污染的样本，显著增强了模型抵御权重中毒后门攻击的能力，并在不影响模型准确性的情况下有效过滤出被污染的样本。CleanCLIP\cite{bansal2023cleanclip}通过在视觉和文本编码器上进行无监督微调，独立调整每种模态的表示，以削弱视觉-语言对比学习模型中由后门攻击引入的错误关联，从而有效减少后门攻击的影响，同时保持模型在正常数据上的性能。
+后门缓解则侧重于通过各种技术手段来消除或减轻后门攻击的影响。Semantic Shield\cite{ishmam2024semantic}通过强制模型在训练时对齐图像区域与外部知识，以防御视觉-语言模型中的后门和数据中毒攻击，从而显著提高了模型的鲁棒性。MCLDef\cite{yue2023model}提出了一种基于模型对比学习的两阶段后门防御方法，通过收缩或破坏中毒数据在特征空间中的聚类，并将中毒数据的特征拉向其干净对应物，从而有效去除深度神经网络中的后门，同时在不显著降低模型准确性的情况下提升防御效果。DPoE\cite{liu2023shortcuts}提出了一种基于端到端集成的后门防御框架，通过结合浅层模型和主模型来捕捉和抑制后门触发器，从而有效应对各种显性和隐性的后门攻击，同时减轻噪声标签对模型性能的影响。此外，PSIM\cite{zhao2024defending}提出了一种基于参数高效微调的防御模块，通过利用样本的置信度来识别被后门攻击污染的样本，显著增强了模型抵御权重中毒后门攻击的能力，并在不影响模型准确性的情况下有效过滤出被污染的样本。CleanCLIP\cite{bansal2023cleanclip}通过在视觉和文本编码器上进行无监督微调，独立调整每种模态的表示，以削弱视觉-语言对比学习模型中由后门攻击引入的错误关联，从而有效减少后门攻击的影响，同时保持模型在正常数据上的性能。
 
-尽管这些方法在应对后门攻击方面展现了显著的效果，但它们在面对更隐蔽或复杂的攻击时可能表现不足，某些方法还依赖于外部知识或置信度的设定，导致误判或性能瓶颈，同时在实际应用中也增加了计算开销和训练时间，因此仍需进一步优化以提升整体性能和效率。
+尽管这些方法在应对后门攻击方面展现了显著效果，但在面对更隐蔽或复杂的后门攻击时，效果依然可能不够理想。某些方法还依赖于外部知识或置信度的设定，可能导致误判或性能瓶颈。此外，这些方法在实际应用中也增加了计算开销和训练时间。因此，未来的研究仍需在提升整体性能与效率的同时，着力解决隐蔽或复杂后门攻击的防御挑战。
 
-% \begin{itemize}
-%     % \item catastrophically forget 灾难性遗忘
-%     \item detection-based methods, erasing-based methods
-%     \item 
-% \end{itemize}
+\subsection{Threat Model}
+\subsubsection{Attacker's Goal and Capability}
+
+\subsubsection{Defender's Goal and Capability}
+
+\subsection{Method}
+后门攻击在于使得模型建立起触发器和标签之间的关联，而不是常规图像之间的关联。参考介绍后门攻击原理的文章
+发现：注意力变化，后门攻击使得模型在图片上的注意力发生了变化，使得模型的注意力从图片的基础特征转移到触发器的特征，从而后门攻击导致模型的梯度更新相较于传统的梯度更新存在方向和数量之间的差异。但当前的隐蔽攻击方式能够逃避传统的检测方式，比如基于余弦相似性的恶意更新识别。（参考文章）大模型参数维度过高，通过cosine识别的话，无法体现出细微的差异，给了后门攻击的可乘之机。
+方法：从模型更新的频率入手，利用DCT进行转换，提取出干净的频率分布样本，最后利用KL散度（HDBSCAN聚类）进行恶意用户识别。
 
@@
     \caption{Attack}
-    \label{tabl:attack} \\ \hline
+    \label{table:attack} \\ \hline
     Title & Conference & Main Content \\ \hline
@@
 \begin{longtable}{|p{3.5cm}|p{2cm}|p{10.5cm}|} 
-    \caption{defense}
-    \label{tabl:defense} \\ \hline
+    \caption{Defense}
+    \label{table:defense} \\ \hline
     Title & Conference & Main Content \\ \hline
@@
 \bibliography{attack_defense}
-
 \end{document}

### 2024-08-30 src/Worker.py
Adjusted the optimizer definition method

@@ -40,7 +40,7 @@ class Worker:
         self.attack_type = attack_type
         self.round_to_start_attack = round_to_start_attack
         self.attack_params = attack_params
-
+        self.lr_init = 1e-2
         self.has_flip = False
         self.has_backdoor = False
 
@@ -69,12 +69,6 @@ class Worker:
         )
 
         self.loss_fn = torch.nn.CrossEntropyLoss()
-
-        # TODO
-        self.optimizer = torch.optim.SGD(self.model.parameters(), lr=1e-3, momentum=0.9)
-        self.scheduler = torch.optim.lr_scheduler.StepLR(
-            self.optimizer, step_size=self.rounds, gamma=0.1
-        )
 
     # def label_flip(self):
     #     original_targets = np.array(self.data_set.dataset.targets)
@@ -127,6 +121,10 @@ class Worker:
         for name, param in self.model.named_parameters():
             if param.requires_grad:
                 target_model_params[name] = param.clone().detach().requires_grad_(False)
+
+        # TODO
+        lr = self.lr_init * 0.1 ** (self.round % 10)
+        self.optimizer = torch.optim.SGD(self.model.parameters(), lr=lr, momentum=0.9)
 
         self.model.train()
         text_descriptions = [

### 2024-08-30 src/Worker.py
Modified the backdoor implantation method

@@ -21,9 +21,9 @@ class Worker:
         data_set,
         device,
         class_names,
-        rounds,
         round_to_start_attack,
-        epochs,
+        inner_epochs,
+        start_round=0,
         attack_type="",
         attack_params={},
         batch_size=256,
@@ -34,27 +34,16 @@ class Worker:
         self.idx = idx
         self.data_set = data_set
         self.class_names = class_names
-        self.rounds = rounds
-        self.round = 0
-        self.epochs = epochs
+        self.epochs = inner_epochs
+        self.start_round = start_round
         self.attack_type = attack_type
         self.round_to_start_attack = round_to_start_attack
         self.attack_params = attack_params
         self.lr_init = 1e-2
         self.has_flip = False
-        self.has_backdoor = False
+        self.backdoored = False
 
         self.train_summaries = []
-
-        # if self.attack_type == "gradient ascent":
-        #     assert "attack_rate" in self.attack_params
-
-        # if self.attack_type == "label flip":
-        #     assert "source_labels" in self.attack_params
-        #     assert "target_label" in self.attack_params
-        #     assert "flip_rate" in self.attack_params
-        #     # assert "bidirectional" in self.attack_params
-        #     assert self.attack_params["source_labels"] != self.attack_params["target_label"]
 
         if self.attack_type == "backdoor":
             # assert "trigger" in self.attack_params
@@ -69,31 +58,6 @@ class Worker:
         )
 
         self.loss_fn = torch.nn.CrossEntropyLoss()
-
-    # def label_flip(self):
-    #     original_targets = np.array(self.data_set.dataset.targets)
-    #     subset_indices = self.data_set.indices
-    #     all_flip_indices = []
-    #     for source_label in self.attack_params["source_labels"]:
-    #         target_indices = np.random.permutation(
-    #             np.where(original_targets[subset_indices] == source_label)[0]
-    #         )
-    #         n_flip = int(len(target_indices) * self.attack_params["flip_rate"])
-    #         flip_indices = target_indices[:n_flip]
-    #         all_flip_indices.extend(flip_indices)
-
-    #     for idx in all_flip_indices:
-    #         self.data_set.dataset.targets[subset_indices[idx]] = self.attack_params[
-    #             "target_label"
-    #         ]
-
-    #     source_labels_str = ", ".join(
-    #         [self.class_names[label] for label in self.attack_params["source_labels"]]
-    #     )
-    #     logger.info(
[…]

### 2024-08-31 clip_lora.py
Modified the way models are trained and evaluated

@@ -2,6 +2,7 @@
 import os
 import torch
 from torch.utils.data import random_split, DataLoader
+from torchvision import transforms
 from torchvision.datasets import CIFAR100
 from transformers import CLIPProcessor
 from peft import LoraConfig
@@ -58,41 +59,30 @@ assert device.type == "cuda", "Please make sure CUDA is available"
 cifar100_train = CIFAR100(
     os.path.expanduser("~\Desktop\clip_lora\.cache"),
     train=True,
-    transform=lambda image: processor(images=image, return_tensors="pt")[
-        "pixel_values"
-    ].squeeze(0),
+    transform=transforms.ToTensor(),
     download=False,
 )
 cifar100_test = CIFAR100(
     os.path.expanduser("~\Desktop\clip_lora\.cache"),
     train=False,
-    transform=lambda image: processor(images=image, return_tensors="pt")[
-        "pixel_values"
-    ].squeeze(0),
-    download=False,
-)
-cifar100_backdoor_test = CIFAR100(
-    os.path.expanduser("~\Desktop\clip_lora\.cache"),
-    train=False,
-    transform=lambda image: processor(images=image, return_tensors="pt")[
-        "pixel_values"
-    ].squeeze(0),
+    transform=transforms.ToTensor(),
     download=False,
 )
 
 class_names = cifar100_train.classes
 train_size = len(cifar100_train)
 test_size = len(cifar100_test)
+
 test_loader = DataLoader(cifar100_test, batch_size=128, shuffle=False)
 
 # config for federated learning
 num_workers = args.num_workers
-rounds = args.rounds
+outer_rounds = args.rounds
 round_to_start_attack = args.round_to_start_attack
 local_epochs = 20
 batch_size = 64
 logger.info(
-    f"Number of workers: {num_workers}, Number of rounds: {rounds}, Round to start attack: {round_to_start_attack}"
+    f"Number of workers: {num_workers}, Number of rounds: {outer_rounds}, Round to start attack: {round_to_start_attack}"
 )
 
 attackers = [i for i in range(4)]
@@ -116,17 +106,6 @@ train_subsets = random_split(cifar100_train, subset_lengths)
 logger.info(f"Train dataset size: {len(cifar100_train)}")
 logger.info(f"Test dataset size: {len(cifar100_test)}")
 
-# put trigger into the test dataset
-for i in range(len(cifar100_backdoor_test)):
-    image = cifar100_backdoor_test.data[i]
-    x, y = attack_params["trigger_position"]
[…]

### 2024-08-31 src/Aggregator.py

@@ -11,7 +11,6 @@ class Aggregator:
         self.processor = processor
         self.class_names = class_names
         self.model = target_model
-        self.loss_fn = torch.nn.CrossEntropyLoss()
 
     def to(self, device):
         self.device = device
@@ -25,51 +24,51 @@ class Aggregator:
 
     def predict(self, images):
         self.model.eval()
-        text_descriptions = [
-            f"This is a photo of a {label}" for label in self.class_names
-        ]
-        tokenized_text = self.processor(
-            text=text_descriptions, padding=True, truncation=True, return_tensors="pt"
-        ).to(self.device)
-        text_features = self.model.get_text_features(**tokenized_text)
-        text_features = text_features / text_features.norm(dim=-1, keepdim=True)
-
+        text_inputs = [f"This is a photo of a {label}" for label in self.class_names]
         with torch.no_grad():
-            images = images.to(self.device)
-            image_features = self.model.get_image_features(images)
-            image_features = image_features / image_features.norm(dim=-1, keepdim=True)
+            inputs = self.processor(
+                text=text_inputs, images=images, return_tensors="pt", padding=True
+            ).to(self.device)
+            outputs = self.model(**inputs)
+            logits_per_image = outputs.logits_per_image
+            return logits_per_image.softmax(dim=1)
 
-            text_probs = 100.0 * image_features @ text_features.T
-            return text_probs.argmax(dim=-1)
-
-    def eval(self, data_loader):
+    def eval(self, data_loader, attack_params={}):
         self.model.eval()
-        text_descriptions = [
-            f"This is a photo of a {label}" for label in self.class_names
-        ]
-        tokenized_text = self.processor(
-            text=text_descriptions, padding=True, truncation=True, return_tensors="pt"
-        ).to(self.device)
-        text_features = self.model.get_text_features(**tokenized_text)
-        text_features = text_features / text_features.norm(dim=-1, keepdim=True)
-
         correct = 0
         loss = 0
         total = 0
+        loss_fn_image = torch.nn.CrossEntropyLoss()
+        text_inputs = [f"This is a photo of a {label}" for label in self.class_names]
+
         with torch.no_grad():
             for images, labels in tqdm(data_loader, desc="Evaluating"):
-                images = images.to(self.device)
+                if attack_params:
+                    x, y = attack_params["trigger_position"]
+                    h, w = attack_params["trigger_size"]
+                    for idx in range(len(images)):
+                        images[idx][x : x + h, y : y + w, :] = attack_params[
+                            "trigger_value"
[…]

### 2024-08-31 src/Worker.py

@@ -1,10 +1,7 @@
 import torch
-import numpy as np
-from matplotlib import pyplot as plt
 from tqdm import tqdm
 import random
 import logging
-import copy
 
 
 logging.basicConfig(level=logging.INFO)
@@ -46,7 +43,6 @@ class Worker:
         self.train_summaries = []
 
         if self.attack_type == "backdoor":
-            # assert "trigger" in self.attack_params
             assert "trigger_position" in self.attack_params
             assert "trigger_size" in self.attack_params
             assert "trigger_value" in self.attack_params
@@ -57,33 +53,14 @@ class Worker:
             self.data_set, batch_size=batch_size, shuffle=True
         )
 
-        self.loss_fn = torch.nn.CrossEntropyLoss()
-
-    def backdoor_attack(self):
-        subset_indices = self.data_set.indices
-        np.random.shuffle(subset_indices)
-        n_backdoor = int(len(subset_indices) * self.attack_params["backdoor_rate"])
-        backdoor_indices = subset_indices[:n_backdoor]
-        for idx in backdoor_indices:
-            image = self.data_set.dataset.data[idx]
-            x, y = self.attack_params["trigger_position"]
-            h, w = self.attack_params["trigger_size"]
-            image[x : x + h, y : y + w, :] = self.attack_params["trigger_value"]
-            self.data_set.dataset.targets[idx] = self.attack_params["target_label"]
-            self.data_set.dataset.data[idx] = image
-        target_label_name = self.class_names[self.attack_params["target_label"]]
-        logger.info(
-            f"Worker {self.idx}: Injected {n_backdoor} backdoor samples with label {target_label_name}"
-        )
-
     def add_trigger(self, images, labels):
         n_backdoor = int(images.size(0) * self.attack_params["backdoor_rate"])
         backdoor_indices = random.sample(range(images.size(0)), n_backdoor)
-        # images.shaoe: (batch_size, 3, 224, 224) trigger.shape: (3, 224, 224)
+        # images.shaoe: (batch_size, 32, 32, 3)
         x, y = self.attack_params["trigger_position"]
         h, w = self.attack_params["trigger_size"]
         for idx in backdoor_indices:
-            images[idx][:, x : x + h, y : y + w] = self.attack_params["trigger_value"]
+            images[idx][x : x + h, y : y + w, :] = self.attack_params["trigger_value"]
             labels[idx] = self.attack_params["target_label"]
         return images, labels
 
[…]

### 2024-08-31 attack-zh.tex
core2: 核心2之 - 高维空间汇聚点检测
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \subsection{Method}
+
 后门攻击在于使得模型建立起触发器和标签之间的关联，而不是常规图像之间的关联。参考介绍后门攻击原理的文章
@@
 方法：从模型更新的频率入手，利用DCT进行转换，提取出干净的频率分布样本，最后利用KL散度（HDBSCAN聚类）进行恶意用户识别。
+
+\subsubsection{结合历史记录}
+
+在前面的部分中，对于单次的攻击，我们已经比较有效地识别。但是在一些实际的攻击中，可能会存在攻击不连续或者每次攻击都比较隐蔽的情况。在这一部分，我们提出了一种结合历史轨迹进行检测的方式，有效处理这种类型的攻击。
+
+\textbf{时间上不连续的攻击}
+
+为了应对中央服务器的恶意用户检测问题，攻击者可能会进行时间上不连续的攻击。总体上来说是攻击者为了提升自己的隐蔽性，并非每轮次都进行攻击。这样，在攻击者不进行攻击的轮次中，只考虑单轮次的检测方式就无法生效。例如G Abad等人提出的Time-Distributed Backdoor Attack\cite{abad2024time}，不是像传统的backdoor那样在空间上（即所有时间步中）使用相同的触发器，而是在多个恶意设备在不同时间段内注入触发器。再例如X.
+Lyu等人提出的\cite{lyu2024coba}，设计的目的是增强后门攻击的稀疏性和隐蔽性。这些都难以在单次的识别中成功检测。
+
+\textbf{隐蔽性攻击}
+
+还有一类攻击在时间上可能是连续的，但是为了规避中央服务器的检测，其在攻击强度上较低。这类攻击还可以细分为两小类：一类是通过拆分或限缩的方式，通过将任务拆分给多个客户端，或者限制单次攻击的力度，从而增大检测难度；另一类是非直奔目标的攻击，每次都不直接诱导模型到目标位置，而是采用迂回曲折的方式，最终将目标诱导至目标地点。例如T.
+A.
+Nguyen等人的Input-aware\cite{nguyen2020input}攻击为了提高隐蔽性，提出了一种输入感知的动态触发器生成器，根据输入样本的特征动态生成触发器，使得每个样本的触发器都是独特的，从而避免了单一模式带来的检测风险。再例如D.
+Yang等人的TSSO\cite{yang2023efficient}攻击，确保所选的触发样本在空间上接近类边界，使得恶意梯度和正常梯度十分接近，从而增加攻击的隐蔽性和成功率。还有Y.
+Qiao等人的Chironex\cite{qiao2024stealthy}方法，通过在频域中生成不可察觉的触发器，实现了攻击的有效性、隐蔽性和对各种FL防御措施的鲁棒性。这类攻击在单次识别中同样具有一定的难度。
+
+\textbf{具体检测方法}
+
+这些攻击都难以检测，但是不论其方式再怎么千变万化，最终一定要达到攻击者所想达到的目标。我们对训练过程进行建模，每次中央服务器下发的模型视为高维空间中的一个点，而客户端训练后上传的梯度视为从这个点出发的一个向量。这样，对于每个客户端，我们就可以得到个有很多具有起点的向量的图。由于梯度是诱导模型变换的方向，因此攻击者若想要达到攻击目的，不论其攻击过程有多么地曲折和隐蔽，其所有向量最终指向的目的区域一定是和良性客户端不同的。我们将这些高维空间中具有起点的绝大多数向量的目的汇聚区域称为“汇聚点”。在允许一定返回的离群值的前提下，我们有理由认为一个客户端的汇聚点就是这个客户端的最终目的。因此问题就变成了如何寻找高维空间中多条具有起点的向量的汇聚点了。TODO: 精美图一张。
+
+这其实是属于有约束的最优化问题。不失一般性，我们可以在高维空间中找到一个点，使得这个点到所有向量所在直线的距离之和最小。那么这个点就可以作为我们想要寻找的“汇聚点”。我们已知每条向量所在直线的方程，因此只需设这个点的坐标，将其与所有直线的距离之和累加就能得到一个带有未知数的表达式。目的是让这个表达式的值最小，问题就变成了一个不等式问题，求解即可得到该点的坐标。
+
+得出了每个客户端的“汇聚点”，使用简单的聚类的方法就能有效地识别出恶意客户端了。
 

### 2024-08-31 clip_lora.py
This version can be run

@@ -92,7 +92,7 @@ attack_params = {
     "trigger_size": (1, 1),
     "backdoor_rate": 0.5,
     "target_label": 88,
-    "trigger_value": 255,
+    "trigger_value": 1,
 }
 
 # Split the train dataset into {num_workers} subsets

### 2024-08-31 src/Worker.py

@@ -36,7 +36,7 @@ class Worker:
         self.attack_type = attack_type
         self.round_to_start_attack = round_to_start_attack
         self.attack_params = attack_params
-        self.lr_init = 1e-2
+        self.lr_init = 1e-3
         self.has_flip = False
         self.backdoored = False
 
@@ -74,7 +74,8 @@ class Worker:
             if param.requires_grad:
                 target_model_params[name] = param.clone().detach().requires_grad_(False)
 
-        lr = self.lr_init * 0.1 ** ((cur_round - self.start_round) % 10)
+        lr = self.lr_init * 0.1 ** ((cur_round - self.start_round) // 10)
+        print(f"Worker {self.idx} Round {cur_round} Learning Rate: {lr}")
         optimizer = torch.optim.Adam(
             self.model.parameters(),
             lr=lr,
@@ -128,6 +129,9 @@ class Worker:
             optimizer.step()
 
             accuracy = (logits_per_image.argmax(dim=1) == labels).sum().item()
+            logger.info(
+                f"Worker {self.idx} Round {cur_round} Train Loss: {loss.item()}, Accuracy: {accuracy / images.size(0)}"
+            )
             self.train_summaries.append(
                 {
                     "loss": loss.item(),

### 2024-08-31 clip_lora.py
It seems to work properly, but I'm not sure, and I need to verify it further.

@@ -25,9 +25,10 @@ parser = argparse.ArgumentParser(description="Run PEFT on CIFAR-100 dataset")
 parser.add_argument("-n", "--num_workers", type=int, help="Number of workers")
 parser.add_argument("-r", "--rounds", type=int, help="Number of rounds")
 parser.add_argument(
-    "-a", "--round_to_start_attack", type=int, help="Round to start attack"
+    "-s", "--round_to_start_attack", type=int, help="Round to start attack"
 )
 parser.add_argument("-o", "--output_dir", type=str, help="Output directory")
+parser.add_argument("-a", "--advertiser_num", type=int, help="Number of attackers")
 args = parser.parse_args()
 
 warnings.filterwarnings(
@@ -79,13 +80,13 @@ test_loader = DataLoader(cifar100_test, batch_size=128, shuffle=False)
 num_workers = args.num_workers
 outer_rounds = args.rounds
 round_to_start_attack = args.round_to_start_attack
+advertiser_num = args.advertiser_num
 local_epochs = 20
 batch_size = 64
 logger.info(
-    f"Number of workers: {num_workers}, Number of rounds: {outer_rounds}, Round to start attack: {round_to_start_attack}"
+    f"Number of workers: {num_workers}, Number of rounds: {outer_rounds}, Round to start attack: {round_to_start_attack}, Number of attackers: {advertiser_num}"
 )
-
-attackers = [i for i in range(4)]
+attackers = [i for i in range(advertiser_num)]
 attack_type = "backdoor"
 attack_params = {
     "trigger_position": (0, 0),
@@ -118,7 +119,7 @@ modules = [
 ]
 target_modules.extend([f"{layer}.{module}" for layer in layers for module in modules])
 target_modules.append("visual_projection")
-logger.info(f"Target modules: {target_modules}")
+# logger.info(f"Target modules: {target_modules}")
 config = LoraConfig(
     r=16,
     lora_alpha=16,
@@ -202,7 +203,6 @@ for name, param in target_model.named_parameters():
 
 for round in range(outer_rounds):
     gradients = {}
-    logger.info(f"target_model_params: {target_model_params.values()}")
     for idx, worker in enumerate(workers):
         for name, param in local_model.named_parameters():
             if param.requires_grad:
@@ -215,8 +215,6 @@ for round in range(outer_rounds):
         flattend_gradients.append(
[…]

### 2024-08-31 src/Aggregator.py

@@ -43,15 +43,15 @@ class Aggregator:
 
         with torch.no_grad():
             for images, labels in tqdm(data_loader, desc="Evaluating"):
+                print(f"evaluating {len(images)} images images.shape: {images.shape}")
                 if attack_params:
                     x, y = attack_params["trigger_position"]
                     h, w = attack_params["trigger_size"]
                     for idx in range(len(images)):
-                        images[idx][x : x + h, y : y + w, :] = attack_params[
+                        images[idx][:, x : x + h, y : y + w] = attack_params[
                             "trigger_value"
                         ]
                         labels[idx] = attack_params["target_label"]
-
                 inputs = self.processor(
                     text=text_inputs,
                     images=images,

### 2024-08-31 src/Worker.py

@@ -54,19 +54,18 @@ class Worker:
         )
 
     def add_trigger(self, images, labels):
-        n_backdoor = int(images.size(0) * self.attack_params["backdoor_rate"])
-        backdoor_indices = random.sample(range(images.size(0)), n_backdoor)
-        # images.shaoe: (batch_size, 32, 32, 3)
+        n_backdoor = int(len(images) * self.attack_params["backdoor_rate"])
+        backdoor_indices = range(n_backdoor)
         x, y = self.attack_params["trigger_position"]
         h, w = self.attack_params["trigger_size"]
+        print(
+            f"Worker {self.idx} Add Trigger at ({x}, {y}) with size ({h}, {w}) images.shape: {images.shape}"
+        )
         for idx in backdoor_indices:
-            images[idx][x : x + h, y : y + w, :] = self.attack_params["trigger_value"]
+            images[idx][:, x : x + h, y : y + w] = self.attack_params["trigger_value"]
             labels[idx] = self.attack_params["target_label"]
-        return images, labels
 
-    def to(self, device):
-        self.device = device
-        self.model = self.model.to(device)
+        return images, labels
 
     def train(self, cur_round):
         target_model_params = {}

### 2024-09-02 temp.yjxt.changeCourse.js
formula: ChatGPT is very GeiLiAble
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,0 +1,18 @@
+/*
+ * @Author: LetMeFly
+ * @Date: 2024-09-02 11:39:20
+ * @LastEditors: LetMeFly
+ * @LastEditTime: 2024-09-02 12:06:32
+ */
+// 培养 -> 课程和环节完成查询
+tbody = document.querySelector("#contentParent_dgData > tbody")
+trs =  [].slice.apply(tbody.querySelectorAll('tr'))
+trs.shift()
+for (let i = 0; i < trs.length; i++) {
+    tr = trs[i]
+    ths = tr.querySelectorAll('td')
+    ths[3].innerText = '123456' + `${i + 1}`.padStart(2, '0')
+    ths[3].innerText = `课程名${i + 1}`
+    ths[3].innerText = 100
+}
+// 然后发现表格每一行td个数不一样，算了

### 2024-09-04 attack-zh.tex
formula: ChatGPT is very GeiLiAble
Signed-off-by: LetMeFly666 <814114971@qq.com>
docs: 单轮攻击识别by wb
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \begin{document}
-\subsection{Related work}
-\subsubsection{Federated Learning}
+\section{Related work}
+\subsection{Federated Learning}
 Federated Learning
+$$g^t = g^{t-1} + \frac{\eta}{N_p}\sum_{N_p}^{i=1}(h^t_i - g^{t-1}$$
 
-\subsubsection{Fine Tuning}
+\subsection{Fine Tuning}
 Fine Tuning
 
-\subsubsection{Backdoor attack}
+\subsection{Backdoor attack}
 后门攻击对深度学习模型构成了严重的安全威胁，它旨在通过对模型输入添加特殊扰动来诱导目标模型产生不当行为，例如图像分类器中的错误分类等。我们将现有针对模型的后门攻击分为两种，即空间隐蔽性后门攻击和时间隐蔽性后门攻击。
@@
 
-\subsubsection{Defenses}
+\subsection{Defenses}
 在当前深度学习模型的安全性研究中，针对后门攻击的防御措施主要可以分为两大类：后门检测和后门缓解。% Backdoor Mitigation or Elimination
@@
 
-\subsection{Threat Model}
-\subsubsection{Attacker's Goal and Capability}
+\section{Threat Model}
+\subsection{Attacker's Goal and Capability}
 
-\subsubsection{Defender's Goal and Capability}
+\begin{itemize}
+    \item 攻击者的知识：
+    \begin{itemize}
+        \item 攻击者 \(A\) 具备与正常客户端相同的背景知识，能够观察到全局模型的变化。
+        \item 攻击者无法控制服务器，也禁止访问其他诚实客户端的训练数据或本地模型更新。
+    \end{itemize}
+    \item 攻击者的能力：
+    \begin{itemize}
+        \item 攻击者 \(A\) 可以随意更改数据集、模型上传梯度的方向以及大小。
+        \item 一个攻击者可能会联合其他攻击者发动协同攻击。
+    \end{itemize}
+    \item 攻击者的目的：
+    \begin{itemize}
+        \item 通过操纵恶意客户端的本地模型更新来扰乱全局模型的训练，使得全局模型在攻击者选择的触发模式下对输入数据产生错误分类。
+    \end{itemize}
+\end{itemize}
 
-\subsection{Method}
+\subsection{Defender's Goal}
+模型性能，鲁棒性，有效性
+\section{Method}
+本节将仔细说明本文的主要思想以及详细的设计。此外，为了清晰且易于理解，表\ref{tabl:notations}中总结了本文中使用过的符号及相应的解释。
 
-后门攻击在于使得模型建立起触发器和标签之间的关联，而不是常规图像之间的关联。参考介绍后门攻击原理的文章
-发现：注意力变化，后门攻击使得模型在图片上的注意力发生了变化，使得模型的注意力从图片的基础特征转移到触发器的特征，从而后门攻击导致模型的梯度更新相较于传统的梯度更新存在方向和数量之间的差异。但当前的隐蔽攻击方式能够逃避传统的检测方式，比如基于余弦相似性的恶意更新识别。（参考文章）大模型参数维度过高，通过cosine识别的话，无法体现出细微的差异，给了后门攻击的可乘之机。
-方法：从模型更新的频率入手，利用DCT进行转换，提取出干净的频率分布样本，最后利用KL散度（HDBSCAN聚类）进行恶意用户识别。
+\begin{table*}[h]
+\centering
+\caption{Notations and Corresponding Definitions}
+\label{tabl:notations}
+\begin{tabular}{|c|l|}
+\hline
+\textbf{Notation} & \textbf{Definition} \\ \hline
+$\mathcal{N}$ & The number of the total clients. \\ \hline
+$\mathcal{M}$ & The number of the participants during each round. \\ \hline
+$\mathcal{D}_i$ & The private local dataset of client $C_i$. \\ \hline
+$\mathbf{w}_t$ & The global model at round $t$. \\ \hline
+$\mathbf{g}_i^t$ & The local update of client $C_i$ during the $t$-th round. \\ \hline
+$\mathbf{G}_i^t $ & 低频分量。 \\ \hline
+$m$ & 低频分量的长度。 \\ \hline
+$C_i^t$ & The $i$-th cluster at round $t$. \\ \hline
+$\bar{\mathbf{g}}_{j}^{t,i}$ & The $j$-th normalized local update within $i$-th cluster during the $t$-th round. \\ \hline
+$\tilde{\mathbf{g}}^{t,i}$ & The partial aggregated update of the $i$-th cluster during the $t$-th round. \\ \hline
+$\tilde{\mathbf{g}}_0^t$ & The clean ingredient at round $t$. \\ \hline
+$\mathbf{g}^t$ & The global update at round $t$. \\ \hline
+$\bar{\mathbf{g}}^t$ & The normalized global update at round $t$. \\ \hline
+$F(\mathbf{w})$ & The expected empirical loss function concerning the model $\mathbf{w}$ over $\{\mathcal{D}_i\}_{i=1}^{n}$. \\ \hline
+$f(\mathcal{D}, \mathbf{w})$ & The empirical loss function concerning the model $\mathbf{w}$ on $\mathcal{D}$. \\ \hline
+\end{tabular}
+\end{table*}
 
-\subsubsection{结合历史记录}
+\subsection{单轮攻击识别}
+\textbf{Motivation}: 后门攻击
+% 后门攻击的性质：后门攻击在于使得模型建立起触发器和标签之间的关联，而不是常规图像之间的关联。
+% 为什么考虑转换到频率维度，现有的方案存在哪些缺点。
+
+\textbf{Overview}: 从模型更新的频率入手，利用DCT进行转换，提取出干净的频率分布样本，最后利用KL散度（HDBSCAN聚类）进行恶意用户识别。
+
+\begin{enumerate}
+\item \textbf{频域转换}
+假设每个本地模型更新的梯度为 \(g_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示客户端，\(t\) 表示通信轮次，\(d\) 是梯度向量的维度。对于每个梯度 \(g_i^t\)，通过一维的DCT-II将其转换为对应的频率分布，其转换公式为：
+\[
+G_i^t[k] = \sum_{n=0}^{d-1} g_i^t[n] \cos\left( \frac{\pi}{d} \left(n + \frac{1}{2}\right) k \right), \quad k = 0, 1, \ldots, d-1
+\]
+
+转换后，选择保留前 \(m\) 个低频分量，并将其他高频分量截断为零：
+
+\[
+G_i^t[k] = \begin{cases}
+G_i^t[k], & \text{if } k < m \\
+0, & \text{if } k \geq m
+\end{cases}
+\]
+
+得到由低频分量构成的向量：
+
+\[
+\mathbf{G}_i^t = (G_i^t[0], G_i^t[1], \ldots, G_i^t[m-1])
+\]
+
+\item \textbf{干净向量计算}
+
+将所有客户端的低频向量表示为矩阵 \(H^t = ({G_0^t}^T, {G_1^t}^T, \ldots, {G_{\mathcal{M}}^t}^T) \in \mathbb{R}^{m \times \mathcal{M}}\)，其中每一列代表一个客户端的低频向量，\(\mathcal{M}\) 表示在第 \(t\) 轮通信中用户数量。通过PCA来提取干净向量，即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)。最后，得到干净向量 \(\tilde{G}^t_0\)：
+
+\[
+\tilde{G}^t_0 = \frac{H^t \xi_{\text{max}}}{\sqrt{\lambda_{\text{max}}}}
+\]
+
+\item \textbf{距离计算}
+
+对于每个客户端的低频向量\(\mathbf{G}_i^t = (G_i^t[0], G_i^t[1], \ldots, G_i^t[m-1])\)以及干净向量\(\tilde{G}^t_0\)，通过Softmax函数来将它们转换为相应的概率分布：
+
+\[
+P_i^t[k] = \frac{\exp(G_i^t[k])}{\sum_{j=0}^{m-1} \exp(G_i^t[j])}, \quad k = 0, 1, \ldots, m-1
+\]
+
+\[
+Q^t[k] = \frac{\exp(\tilde{G}^t_0[k])}{\sum_{j=0}^{m-1} \exp(\tilde{G}^t_0[j])}, \quad k = 0, 1, \ldots, m-1
+\]
+
+利用KL散度衡量两个概率分布 \(P\) 和 \(Q\) 之间的距离。对于每个客户端 \(i\) 的低频向量分布 \(P_i^t\) 和干净向量分布 \(Q^t\)，KL散度定义为：
+
+\[
+D_{i} = D_{\text{KL}}(P_i^t \| Q^t) = \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)
+\]
+
+% 距离向量 \(D\) 的每个元素 \(D_{i}\) 表示客户端 \(i\) 的低频向量与干净向量之间的KL散度，向量形式为：
+
+% \[
+% D_{i} = D_{\text{KL}}(P_i^t \| Q^t), \quad i = 1, 2, \ldots, K_t
+% \]
+
+\item \textbf{单轮恶意用户识别}
+
+利用HDBSCAN对计算出来的KL散度\(D_i\)进行聚类，得到簇\(C_1, C_2, \ldots, C_f\)。从所有簇中选出最大的一簇（即包含用户数量最多的簇），记作 \(C_{\text{max}}\)。将 \(C_{\text{max}}\) 中的所有用户标记为良性用户。对于除 \(C_{\text{max}}\) 外的所有其他簇 \(C_i\)（\(i \neq \text{max}\)），将其所有用户标记为恶意用户。 设 \(U_{\text{nor}}\) 表示良性用户集合， \(U_{\text{mal}}\) 表示恶意用户集合，则：
+
+\[
+U_{\text{nor}} = C_{\text{max}}
+\]
+
+\[
+U_{\text{mal}} = \bigcup_{i \neq \text{max}} C_i
+\]
+
+\end{enumerate}
+
+\subsection{结合历史记录}
 
@@
 得出了每个客户端的“汇聚点”，使用简单的聚类的方法就能有效地识别出恶意客户端了。
+
+不失一般性，假设空间中有 $n$ 条直线，每条直线可以表示为一个点 $\mathbf{p}_i$ 和一个方向向量 $\mathbf{d}_i$，那么第 $i$ 条直线的方程可以表示为：
+\[
+\mathbf{l}_i(t) = \mathbf{p}_i + t \mathbf{d}_i, \quad t \in \mathbb{R}.
+\]
+
+对于某个空间中的点 $\mathbf{x}$，它到第 $i$ 条直线的距离可以用以下公式计算：
+\[
+\text{dist}(\mathbf{x}, \mathbf{l}_i) = \frac{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \|}{\| \mathbf{d}_i \|},
+\]
+其中 $\times$ 表示向量的叉积。
+
+\subsubsection*{优化目标}
+
+我们的目标是找到一个点 $\mathbf{x}$，使得它到所有直线的距离之和最短，即最小化以下目标函数：
+\[
+f(\mathbf{x}) = \sum_{i=1}^n \frac{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \|}{\| \mathbf{d}_i \|}.
+\]
+
+这个问题是一个非线性优化问题，直接求解解析解较为困难。可以使用数值优化的方法，如梯度下降法、牛顿法、共轭梯度法或其它非线性优化算法来求解。以下是使用梯度下降法的步骤：
+
+\begin{enumerate}
+    \item \textbf{计算梯度：}
+
+    对于每个 $i$，距离函数对 $\mathbf{x}$ 的梯度为：
+    \[
+    \nabla_{\mathbf{x}} \left( \frac{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \|}{\| \mathbf{d}_i \|} \right) = \frac{((\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i) \times \mathbf{d}_i}{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \| \| \mathbf{d}_i \|}.
+    \]
+    整体目标函数的梯度是各个距离函数梯度的和：
+    \[
+    \nabla f(\mathbf{x}) = \sum_{i=1}^n \nabla_{\mathbf{x}} \left( \frac{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \|}{\| \mathbf{d}_i \|} \right).
+    \]
+
+    \item \textbf{选择初始点：}
+
+    通常可以从一个任意的点开始，比如所有直线的交点或它们中心的平均值作为初始点。
+
+    \item \textbf{更新点位置：}
+
+    使用梯度下降法更新点的位置：
+    \[
+    \mathbf{x}_{\text{new}} = \mathbf{x}_{\text{old}} - \eta \nabla f(\mathbf{x}_{\text{old}}),
+    \]
+    其中 $\eta$ 是学习率，可以根据需要进行调整。
+
+    \item \textbf{迭代过程：}
+
+    重复计算梯度和更新点的位置，直到收敛到一个小的误差阈值或达到最大迭代次数。
+\end{enumerate}
 

### 2024-09-07 attack-zh.tex
docs: 球心移动算法

@@
 \item \textbf{频域转换}
-假设每个本地模型更新的梯度为 \(g_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示客户端，\(t\) 表示通信轮次，\(d\) 是梯度向量的维度。对于每个梯度 \(g_i^t\)，通过一维的DCT-II将其转换为对应的频率分布，其转换公式为：
+
+假设每个本地模型更新的梯度为 \(g_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示客户端，\(t\) 表示通信轮次，\(d\) 为模型上传更新的维度。对于每个更新 \(g_i^t\)，我们通过一维的DCT-II将其转换为对应的频率分布，对应转换公式为：
 \[
-G_i^t[k] = \sum_{n=0}^{d-1} g_i^t[n] \cos\left( \frac{\pi}{d} \left(n + \frac{1}{2}\right) k \right), \quad k = 0, 1, \ldots, d-1
+G_i^t[k] = \sum_{n=0}^{d-1} g_i^t[n] \cos\left( \frac{\pi}{d} \left(n + \frac{1}{2}\right) k \right)
 \]
 
-转换后，选择保留前 \(m\) 个低频分量，并将其他高频分量截断为零：
+\[
+\quad k \in [0, d-1]
+\]
+
+转换后，保留前 \(m\) 个低频分量， 得到由低频分量构成的向量：
 
 \[
-G_i^t[k] = \begin{cases}
-G_i^t[k], & \text{if } k < m \\
-0, & \text{if } k \geq m
-\end{cases}
-\]
-
-得到由低频分量构成的向量：
-
-\[
-\mathbf{G}_i^t = (G_i^t[0], G_i^t[1], \ldots, G_i^t[m-1])
+\mathbf{G}_i^t = (G_i^t[0], G_i^t[1], \ldots, G_i^t[m-1])^T
 \]
@@
 
-将所有客户端的低频向量表示为矩阵 \(H^t = ({G_0^t}^T, {G_1^t}^T, \ldots, {G_{\mathcal{M}}^t}^T) \in \mathbb{R}^{m \times \mathcal{M}}\)，其中每一列代表一个客户端的低频向量，\(\mathcal{M}\) 表示在第 \(t\) 轮通信中用户数量。通过PCA来提取干净向量，即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)。最后，得到干净向量 \(\tilde{G}^t_0\)：
+将所有客户端的低频向量表示为矩阵 \(H^t = ({G_0^t}, {G_1^t}, \ldots, {G_{\mathcal{M}}^t}) \in \mathbb{R}^{m \times \mathcal{M}}\)，其中每一列代表一个客户端的低频向量，\(\mathcal{M}\) 表示在第 \(t\) 轮通信中用户数量。利用最大左奇异值向量来作为相应的干净向量（原理？），即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)。最后，得到干净向量 \(\tilde{G}^t_0\)：
 
@@
 \[
-P_i^t[k] = \frac{\exp(G_i^t[k])}{\sum_{j=0}^{m-1} \exp(G_i^t[j])}, \quad k = 0, 1, \ldots, m-1
+P_i^t[k] = \frac{\exp(G_i^t[k])}{\sum_{j=0}^{m-1} \exp(G_i^t[j])}, \quad k \in [0, m-1]
 \]
@@
 \[
-Q^t[k] = \frac{\exp(\tilde{G}^t_0[k])}{\sum_{j=0}^{m-1} \exp(\tilde{G}^t_0[j])}, \quad k = 0, 1, \ldots, m-1
+Q^t[k] = \frac{\exp(\tilde{G}^t_0[k])}{\sum_{j=0}^{m-1} \exp(\tilde{G}^t_0[j])}, \quad k \in [0, m-1]
 \]
@@
 
-这其实是属于有约束的最优化问题。不失一般性，我们可以在高维空间中找到一个点，使得这个点到所有向量所在直线的距离之和最小。那么这个点就可以作为我们想要寻找的“汇聚点”。我们已知每条向量所在直线的方程，因此只需设这个点的坐标，将其与所有直线的距离之和累加就能得到一个带有未知数的表达式。目的是让这个表达式的值最小，问题就变成了一个不等式问题，求解即可得到该点的坐标。
+这其实是属于有约束的最优化问题。不失一般性，我们可以将其视为一个近似最小覆盖超球的问题。
 
-得出了每个客户端的“汇聚点”，使用简单的聚类的方法就能有效地识别出恶意客户端了。
+\subsection{问题背景与建模}
 
-不失一般性，假设空间中有 $n$ 条直线，每条直线可以表示为一个点 $\mathbf{p}_i$ 和一个方向向量 $\mathbf{d}_i$，那么第 $i$ 条直线的方程可以表示为：
-\[
-\mathbf{l}_i(t) = \mathbf{p}_i + t \mathbf{d}_i, \quad t \in \mathbb{R}.
-\]
+在联邦学习（Federated Learning, FL）场景中，每个客户端上传的梯度可以视为一条射线，这条射线的起点是中央服务器下发的模型参数，方向是客户端计算的梯度方向。通过计算每个客户端上传的梯度所形成的射线与一个最小覆盖超球之间的关系，我们可以分析并识别潜在的恶意客户端。
 
-对于某个空间中的点 $\mathbf{x}$，它到第 $i$ 条直线的距离可以用以下公式计算：
-\[
-\text{dist}(\mathbf{x}, \mathbf{l}_i) = \frac{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \|}{\| \mathbf{d}_i \|},
-\]
-其中 $\times$ 表示向量的叉积。
+\subsubsection{问题定义}
 
-\subsubsection*{优化目标}
+给定 \( n \) 条射线，每条射线由起点 \( P_i \) 和方向向量 \( \mathbf{d}_i \) 表示。目标是找到一个球的球心 \( O \) 和半径 \( r \)，使得球被大多数射线（例如 \( 90\% \)）穿过。
 
-我们的目标是找到一个点 $\mathbf{x}$，使得它到所有直线的距离之和最短，即最小化以下目标函数：
-\[
-f(\mathbf{x}) = \sum_{i=1}^n \frac{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \|}{\| \mathbf{d}_i \|}.
-\]
+\subsubsection{数学表述}
 
-这个问题是一个非线性优化问题，直接求解解析解较为困难。可以使用数值优化的方法，如梯度下降法、牛顿法、共轭梯度法或其它非线性优化算法来求解。以下是使用梯度下降法的步骤：
+我们需要找到一个点 \( O \) 和半径 \( r \)，使得对于至少 \( k = \lceil 0.9n \rceil \) 条射线 \( i \)，存在一个 \( t_i \geq 0 \) 使得：
+
+\begin{equation}
+\| O - (P_i + t_i \mathbf{d}_i) \|^2 \leq r^2.
+\end{equation}
+
+这个问题可以转化为一个优化问题，目标是最小化球的半径 \( r \)，并满足所需比例的射线穿过球的约束。
+
+\subsection{迭代算法步骤}
+
+该算法采用一种迭代优化方法，通过逐步调整球心 \( O \) 和半径 \( r \)，使其逐渐逼近最优解。具体步骤如下：
+
+\subsubsection{初始化}
+
+\begin{itemize}
+    \item 初始球心 \( O_0 \) 设置为所有射线起点的几何中心：
+
+    \begin{equation}
+    O_0 = \frac{1}{n} \sum_{i=1}^n P_i.
+    \end{equation}
+
+    \item 初始半径 \( r_0 \) 设置为从初始球心到所有射线起点的最大距离：
+
+    \begin{equation}
+    r_0 = \max_{0\leq i\leq \lceil n\times \varepsilon\rceil} \|O_0 - P_i\|.
+    \end{equation}
+\end{itemize}
+
+\subsubsection{迭代过程}
+
+对于每一步迭代 \( k \)，我们执行以下步骤：
 
 \begin{enumerate}
-    \item \textbf{计算梯度：}
+    \item \textbf{计算投影点}：对于每条射线 \( i \)，找到射线与当前球心 \( O_k \) 最近的点 \( Q_i \)，并计算参数 \( t_i \)：
 
-    对于每个 $i$，距离函数对 $\mathbf{x}$ 的梯度为：
-    \[
-    \nabla_{\mathbf{x}} \left( \frac{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \|}{\| \mathbf{d}_i \|} \right) = \frac{((\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i) \times \mathbf{d}_i}{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \| \| \mathbf{d}_i \|}.
-    \]
-    整体目标函数的梯度是各个距离函数梯度的和：
-    \[
-    \nabla f(\mathbf{x}) = \sum_{i=1}^n \nabla_{\mathbf{x}} \left( \frac{\| (\mathbf{x} - \mathbf{p}_i) \times \mathbf{d}_i \|}{\| \mathbf{d}_i \|} \right).
-    \]
+    \begin{equation}
+    t_i = \max\left(0, \frac{(O_k - P_i) \cdot \mathbf{d}_i}{\|\mathbf{d}_i\|^2}\right),
+    \end{equation}
 
-    \item \textbf{选择初始点：}
+    其中，\( Q_i \) 是射线上的点，计算公式为：
 
-    通常可以从一个任意的点开始，比如所有直线的交点或它们中心的平均值作为初始点。
+    \begin{equation}
+    Q_i = P_i + t_i \mathbf{d}_i.
+    \end{equation}
 
-    \item \textbf{更新点位置：}
+    \item \textbf{计算与球心的距离}：计算球心 \( O_k \) 到这些投影点 \( Q_i \) 的距离 \( D_i \)：
 
-    使用梯度下降法更新点的位置：
-    \[
-    \mathbf{x}_{\text{new}} = \mathbf{x}_{\text{old}} - \eta \nabla f(\mathbf{x}_{\text{old}}),
-    \]
-    其中 $\eta$ 是学习率，可以根据需要进行调整。
+    \begin{equation}
+    D_i = \|O_k - Q_i\|.
+    \end{equation}
 
-    \item \textbf{迭代过程：}
+    \item \textbf{选择最近的 \( k \) 个点}：对所有距离 \( D_i \) 进行排序，选择最近的 \( k \) 个点，计算这些点中的最大距离 \( D_k^{(k)} \)。
 
-    重复计算梯度和更新点的位置，直到收敛到一个小的误差阈值或达到最大迭代次数。
+    \item \textbf{更新球心和半径}：
+
+    % 如果新的最大距离 \( D_k^{(k)} \) 大于当前半径 \( r_k \)，则更新球心 \( O_k \) 和半径 \( r_k \)：
+
+    将球心向着新球心的方向移动一段距离
+
+    \begin{equation}
+    % O_{k+1} = O_k + \alpha \left(\frac{1}{k} \sum_{i \in \text{最近的 } k \text{ 个点}} (Q_i - O_k)\right),
+    O_{t} = O_{t-1} + \alpha \left(\frac{1}{n\times \varepsilon} \sum_{0\leq i\leq \lceil n\times \varepsilon\rceil} (Q_i - O_t)\right),
+    \end{equation}
+
+    \begin{equation}
+    r_{k+1} = D_k^{(k)},
+    \end{equation}
+
+    其中，\( \alpha \) 是学习率，通常取一个小的正值（如 0.1）。这个更新步骤的作用是朝着一个更加紧凑的覆盖超球方向优化。
+
+    \item \textbf{终止条件}：当更新后的半径 \( r_{k+1} \) 与上一次的半径 \( r_k \) 相差小于一个小的阈值 \( \epsilon \)（例如 \( 10^{-6} \)时，停止迭代。
+\end{enumerate}
+
+\subsection{置信度定义}
+
+在联邦学习（Federated Learning, FL）环境下，恶意客户端可能会通过上传异常梯度来影响全局模型的训练过程。为提高系统的鲁棒性，本研究提出了一种基于几何优化的置信度计算方法，用于评估客户端上传梯度的有效性和一致性。具体而言，我们将每个客户端的射线表示为一个起点 \(P_i\) 和方向 \(\mathbf{d}_i\)，并通过求解覆盖大多数射线的最小超球来定义每个客户端的置信度。
+
+置信度 \(C_i\) 定义为与该最小球半径 \(r_i\) 的倒数成正比的度量，公式如下：
+
+\begin{equation}
+C_i = \frac{1}{r_i + \epsilon},
+\end{equation}
+
+其中，\(r_i\) 表示覆盖大多数射线（例如 \(90\%\)）的最小球半径，\(\epsilon\) 是一个小的正数（如 \(10^{-6}\)），用于防止除零错误。
+
+通过这一定义，置信度 \(C_i\) 的值反映了客户端 \(i\) 上传梯度方向的集中程度。置信度越高（即半径 \(r_i\) 越小），表明该客户端的梯度方向较为一致，反之则表示梯度方向较为分散，可能存在异常行为或恶意攻击的迹象。
+
+\subsection{置信度在梯度聚合中的应用}
+
+在 FL 场景中，为了减轻恶意客户端上传的异常梯度对全局模型的影响，可以根据每个客户端的置信度对其上传的梯度进行加权聚合。假设 \(g_i\) 为客户端 \(i\) 上传的梯度更新，则加权后的全局梯度更新 \(G\) 可表示为：
+
+\begin{equation}
+G = \frac{\sum_{i=1}^{n} C_i \cdot g_i}{\sum_{i=1}^{n} C_i}.
+\end{equation}
+
+该公式中的 \(C_i \cdot g_i\) 表示根据客户端 \(i\) 的置信度对其上传的梯度进行加权，分母 \(\sum_{i=1}^{n} C_i\) 用于归一化，以确保所有客户端加权后的梯度贡献和为 1。通过这种方式，置信度高的客户端对最终聚合结果的影响较大，而置信度低的客户端影响较小。
+
+使用置信度加权的梯度聚合方法可以显著提高 FL 系统的鲁棒性和安全性，具体表现为以下几个方面：
+
+\begin{enumerate}
+    \item \textbf{抵御恶意客户端攻击}：由于恶意客户端的置信度 \(C_i\) 较低，其上传的异常梯度对全局模型更新的影响有限，能够有效减轻攻击效果。
+    \item \textbf{增强模型鲁棒性}：置信度高的客户端通常具有一致的梯度方向，在聚合中占据主导地位，确保了全局模型更新的方向更加稳定和有效。
+    \item \textbf{自适应聚合策略}：该方法能够根据客户端的实际行为动态调整聚合策略，而无需事先设定恶意客户端的数量或行为模式，这使得方法在各种场景下更具通用性和适应性。
 \end{enumerate}

### 2024-09-08 attack-zh.tex
docs: 昨晚的半夜之作
单轮主要wb白天，多轮主要me到晚上

--- 2024-08-31 attack-zh.tex
@@
 \usepackage{algorithm}
-%\usepackage{algorithmic}
+% \usepackage{algorithmic}
 \usepackage{algpseudocode}
@@
 \usepackage{graphicx}
-%\usepackage{subfigure}
 \usepackage{booktabs}
@@
 \begin{document}
-\subsection{Related work}
-\subsubsection{Federated Learning}
-Federated Learning
+\section{Related work}
+% \subsection{Federated Fine-tuning}
+% Federated Learning
+% $$g^t = g^{t-1} + \frac{\eta}{N_p}\sum_{N_p}^{i=1}(h^t_i - g^{t-1}$$
 
-\subsubsection{Fine Tuning}
-Fine Tuning
+% \subsection{Fine Tuning}
+% Fine Tuning
 
-\subsubsection{Backdoor attack}
+\subsection{Backdoor attack}
 后门攻击对深度学习模型构成了严重的安全威胁，它旨在通过对模型输入添加特殊扰动来诱导目标模型产生不当行为，例如图像分类器中的错误分类等。我们将现有针对模型的后门攻击分为两种，即空间隐蔽性后门攻击和时间隐蔽性后门攻击。
@@
 
-\subsection{Threat Model}
-\subsubsection{Attacker's Goal and Capability}
+\begin{algorithm}
+\caption{Local model training process}
+\label{alg:local_update}
+\begin{algorithmic}[1]
+\State \textbf{Input:} $\theta_g^{t-1}, D_i, b, \eta, E_l$ \Comment{$E_l$ is the local epochs, $\eta$ is the local learning rate, and $b$ is the batch size}
+\State \textbf{Output:} $\triangledown \theta_i^t$ \Comment{Local model update}
 
-\subsubsection{Defender's Goal and Capability}
+\State $(\theta_i^{t})^0 \gets \theta_g^{t-1}$ \Comment{Initialize model weights}
+\For{$e = 1$ to $E_l$}
+    \State $D_i^b \sim Sample(D_i, b)$ \Comment{Randomly sample a batch $D_i^b$ of size $b$ from $D_i$}
+    \State $(\theta_i^{t})^e \gets (\theta_i^{t})^{e-1} - \eta \nabla f(D_i^b, (\theta_i^{t})^{e-1})$
+\EndFor
+\State \textbf{return} $(\theta_i^{t})^{E_l} - (\theta_i^{t})^0$
+\end{algorithmic}
+\end{algorithm}
 
-\subsection{Method}
+\section{System Model}
 
-后门攻击在于使得模型建立起触发器和标签之间的关联，而不是常规图像之间的关联。参考介绍后门攻击原理的文章
-发现：注意力变化，后门攻击使得模型在图片上的注意力发生了变化，使得模型的注意力从图片的基础特征转移到触发器的特征，从而后门攻击导致模型的梯度更新相较于传统的梯度更新存在方向和数量之间的差异。但当前的隐蔽攻击方式能够逃避传统的检测方式，比如基于余弦相似性的恶意更新识别。（参考文章）大模型参数维度过高，通过cosine识别的话，无法体现出细微的差异，给了后门攻击的可乘之机。
-方法：从模型更新的频率入手，利用DCT进行转换，提取出干净的频率分布样本，最后利用KL散度（HDBSCAN聚类）进行恶意用户识别。
+考虑在机器人物联网（IoRT）网络中进行视觉语言模型联邦微调的场景下，系统模型包括多个机器人节点和一个中心服务器，机器人节点在本地进行模型微调，并通过中心服务器进行全局聚合。以下是系统模型的详细描述。
 
-\subsubsection{结合历史记录}
+\begin{enumerate}
+    \item \textbf{参与者和数据集}：
+    假设系统模型中存在 $n$ 个机器人节点，每个节点记作 $R_i$, $i \in \{1, 2, \ldots, n\}$。 每个机器人节点 $R_i$ 拥有一个本地数据集 $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$，其中 $x_{i,j}$ 表示输入数据，$y_{i,j}$ 表示对应的标签数据，$|D_i|$ 为数据集的大小，$D = \bigcup_{i=1}^{n} D_i$表示整体的数据集。
 
-在前面的部分中，对于单次的攻击，我们已经比较有效地识别。但是在一些实际的攻击中，可能会存在攻击不连续或者每次攻击都比较隐蔽的情况。在这一部分，我们提出了一种结合历史轨迹进行检测的方式，有效处理这种类型的攻击。
+    \item \textbf{LoRA}：
+    在LoRA(Low-Rank Adaptation) 方法中，模型原始的参数为$\Theta$，模型引入的增量参数为$\theta$，每一个参数矩阵 $W$ 被表示为：
+    \[
+    W = W_0 + \Delta W, \quad \Delta W = BA
+    \]
+    其中，$W_0$ 为模型的原始权重矩阵，$\Delta W$ 是低秩增量矩阵，$B \in \mathbb{R}^{d_i \times r}$ 和 $A \in \mathbb{R}^{r \times d_o}$ 是低秩分解矩阵，$r$ 为矩阵的秩，满足 $r \ll \min(d_i, d_o)$。在联邦微调过程中，每个机器人节点仅对 $\theta$ 进行本地更新，保持 $\Theta$ 不变，从而降低通信和计算开销。
 
-\textbf{时间上不连续的攻击}
+    \item \textbf{本地模型训练}：
+    在每轮联邦训练的开始时，中心服务器将全局模型的增量参数 $\theta_g^{t-1}$ 发送给每个机器人节点。每个机器人节点$R_i$在获得增量参数$\theta_g^{t-1}$后，基于本地数据集 $D_i$ 进行微调训练，算法\ref{alg:local_update}展示了节点进行本地模型每轮训练的主要过程。
+    ，其目标是最小化本地损失函数 $f(D_i^b, \theta_i^{t})$：
+    \[
+    f(D_i^b, \theta_i^{t}) = \frac{1}{|D_i^b|} \sum_{j=1}^{|D_i^b|} \ell(x_{i,j}, y_{i,j}; \Theta + \theta_i^{t})
+    \]
+    其中$\Theta$为模型的原始参数， $\ell$表示损失函数例如交叉熵损失函数。训练结束后，节点将经过本地优化后的增量参数更新 $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ 上传到中心服务器。
+    \item \textbf{联邦聚合}：
+    在每轮本地训练结束后，中心服务器从每个机器人节点 $R_i$ 收集本地更新$\triangledown \theta_i^t$，并利用相应的聚合算法进行聚合，以更新全局增量参数得到$\theta_g^t$，其计算公式为：
+    \[
+    \theta_g^t = Aggregate(\triangledown \theta_1^t, \triangledown \theta_2^t, \dots, \triangledown \theta_n^t)
+    \]
+    其中，$\theta_g^t$ 是第 $t$ 轮更新的全局增量参数，更新后的全局增量参数 $\theta_g^t$ 将在下一轮训练前下发给所有机器人节点，用于进一步的本地微调。
+\end{enumerate}
 
-为了应对中央服务器的恶意用户检测问题，攻击者可能会进行时间上不连续的攻击。总体上来说是攻击者为了提升自己的隐蔽性，并非每轮次都进行攻击。这样，在攻击者不进行攻击的轮次中，只考虑单轮次的检测方式就无法生效。例如G Abad等人提出的Time-Distributed Backdoor Attack\cite{abad2024time}，不是像传统的backdoor那样在空间上（即所有时间步中）使用相同的触发器，而是在多个恶意设备在不同时间段内注入触发器。再例如X.
+\section{Threat Model}
+\begin{itemize}
+    \item Attacker's Goal：假设在对视觉语言模型进行联邦微调的场景中，存在一个或者多个由攻击者操纵的恶意节点。其目标是对全局模型 $\mathbf{F}$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别 $t$，同时尽可能保持对干净输入的分类准确性。
+    \item Attacker's ability: 假设攻击者对恶意节点的本地训练过程拥有绝对的控制权，即攻击者可以随意操作本地数据、触发器模式、优化方式以及本地更新等。同时攻击者可以使用“聪明”的攻击策略进行攻击，即单轮攻击可能不会体现攻击效果，而是在多轮攻击的联合作用下成功植入后门。这种场景是实际存在的，因为服务器只能从客户端获取训练后的模型，而无法获知模型的具体训练过程。相应地，攻击者无法影响中央服务器上的操作，例如更改聚合规则或篡改其他良性客户端的模型更新。
+\end{itemize}
+
+% \subsection{Defender's Goal}
+% 模型性能，鲁棒性，有效性
+\section{Method}
+本节将仔细说明本文的主要思想以及详细的设计。此外，为了清晰且易于理解，表\ref{tabl:notations}中总结了本文中使用过的符号及相应的解释。
+
+\begin{table*}[h]
+\centering
+\caption{Notations and Corresponding Definitions}
+\label{tabl:notations}
+\begin{tabular}{|c|l|}
+\hline
+\textbf{Notation} & \textbf{Definition} \\ \hline
+% 联邦学习
+$ n $ & The number of the nodes participating during each round. \\ \hline
+% $\mathcal{M}$ & The number of the participants during each round. \\ \hline
+$D_i$ & The private local dataset of node $C_i$. \\ \hline
+
+% 单论识别
+$G^t$ & The global model at round $t$. \\ \hline
+$\theta_i^t$ & The local model of participant at round $t$. \\ \hline
+$\triangledown \theta_i^t$ & The local update of node $R_i$ during the $t$-th round. \\ \hline
+$G_i^t $ & The low-frequency components extracted from the update of node $R_i$ during the $t$-th round.. \\ \hline
+$m$ & The length of the low-frequency components. \\ \hline
+$H^t$ & The matrix formed by stacking $G_i^t$, with a shape of $m \times n$ during the $t$-th round. \\ \hline
+$\tilde{G}_{0}^t $ & The clean ingredient extracted from the nodes' low-frequency components during the $t$-th round. \\ \hline
+$\lambda_{max}^t$ & The largest singular value of matrix $H^t$ during the $t$-th round. \\ \hline
+$\xi_{max}^t$ & The corresponding left singular vector of singular value $\lambda_{max}^t$ during the $t$-th round. \\ \hline
+$P_i^t$ & The distribution corresponding to $G_i^t$ after applying the Softmax function during the $t$-th round.. \\ \hline
+$Q^t$ &  The distribution corresponding to $\tilde{G}_{0}^t$ after applying the Softmax function during the $t$-th round.. \\ \hline
+$O_t$ &  The center of the high dimensional ball $t$-th round. \\ \hline
+
+% 待总结
+
+\end{tabular}
+\end{table*}
+
+\subsection{单轮恶意节点识别}
+\textbf{Motivation}: 目前的防御策略主要集中于利用攻击的浅层语义特征来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向，范数以及神经元符号等。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。
+% Multi-metrics adaptively identifies backdoors in Federated learning
+首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意梯度，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意梯度。同时最新的研究表明，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性梯度，因为这些方法往往受到维度灾难的影响。最新的攻击策略已经能够通过精心调整，巧妙地避开这些基于浅层语义特征的防御措施，从而成功植入后门。
+% 后门攻击的性质：后门攻击在于使得模型建立起触发器和标签之间的关联，而不是常规图像之间的关联。
+% 为什么考虑转换到频率维度，现有的方案存在哪些缺点。
+
+\textbf{Overview}: 无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新始终相较于良性用户具有分布上的差异。%TODO
+
+\begin{algorithm}
+\caption{Malicious Node Detection via DCT}
+\label{alg:malicious-node-detection}
+\begin{algorithmic}[1]
+\State \textbf{Input:} $d$, $n$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$, $m$ \Comment{$d$ is the dimension of each node update; $n$ is the number of the nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$is the local updates from nodes during the $t$-th round; $m$ is the length of low-frequency components}
+\State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
+
+\State Step 1: Frequency Domain Transformation
+\For {Node $R_i$}
+    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
+    \For{$k = 0$ to $d-1$}
+        \State $G_i^t[k] \gets 0$
+        \For{$j = 0$ to $d-1$}
+            \State $G_i^t[k] \gets G_i^t[k] + \bar{\theta_i^t}[j] \cos \left( \frac{\pi}{d} \left(j + \frac{1}{2}\right) k \right)$
+        \EndFor
+    \EndFor
+\EndFor
+
+\State
+
+\State Step 2: Clean Ingredient Extraction
+\State $H^t \gets (G_0^t, G_1^t, \ldots, G_{\mathcal{M}}^t) \in \mathbb{R}^{d \times m}$ \Comment{Stacking to form Matrix $H^t$.}
+
+\State $\hat{H}^t \gets (H^t)^{T} H^t$
+\State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
+\State $\tilde{G}^t_0 \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
+
+\State
+
+\State Step 3: Kullback-Leibler Divergence Calculation
+\State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t_0)$
+\For {Node $R_i$}
+    \State $KL_i \gets \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)$
+\EndFor
+\State $S \gets \{KL_1, KL_2, \ldots, KL_n\}$ \Comment{The distribution differences calculated by KL divergence.}
+
+\State
+
+\State Step 4: Malicious Node Detection
+\State $\{C_1, C_2, \ldots, C_K\} \gets \text{HDBSCAN}(S)$
+\State $U_{nor} \gets C_{\text{max}}$, $U_{mal} \gets \{C_i \, | \, i \neq \text{max}\}$
+
+\end{algorithmic}
+\end{algorithm}
+算法\ref{alg:malicious-node-detection}展示了整体的恶意用户识别过程，主要包含四个步骤：Frequency Domain Transformation, Clean Ingredient Extraction, Kullback-Leibler Divergence Calculation,Single-round Malicious Node Detection。
+\begin{enumerate}
+\item \textbf{Frequency Domain Transformation}
+
+Frequency Domain Transformation的主要过程如算法\ref{alg:malicious-node-detection}的4-12行所示。假设每个本地模型的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，我们通过一维的DCT-II将其转换为对应的频率分布，并提取对应的m个低频成分，得到低频向量\(G_i^t\)。对应的计算过程如下：
+\begin{equation}
+G_i^t = Trunc(DCT(Flatten(\triangledown \theta_i^t), m)
+\end{equation}
+
+\begin{equation}
+Flatten: \bar{\theta_i^t} = Flatten(\triangledown \theta_i^t)
+\end{equation}
+
+\begin{equation}
+DCT: G_i^t[k] = \sum_{j=0}^{d-1} \bar{\theta_i^t}[j] \cos \left( \frac{\pi}{d} \left(j + \frac{1}{2}\right) k \right)
+\end{equation}
+
+\item \textbf{Clean Ingredient Extraction}
+
+Clean Ingredient Extraction的主要过程如算法\ref{alg:malicious-node-detection}的15-18行所示。将所有节点的低频向量堆叠为矩阵 \(H^t = ({G_0^t}, {G_1^t}, \ldots, {G_{\mathcal{M}}^t}) \in \mathbb{R}^{m \times n}\)，其中每一列代表一个节点的低频向量。通过计算矩阵的最大奇异值及其对应的左奇异向量来作为相应的干净成分。即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)，根据公式\ref{equation:singular}，得到干净向量 \(\tilde{G}_0^t\)：
+
+\begin{equation}
+\tilde{G}^t_0 = \frac{H^t \xi_{\text{max}}}{\sqrt{\lambda_{\text{max}}}}
+\label{equation:singular}
+\end{equation}
+
+\item \textbf{Kullback-Leibler Divergence Calculation}
+
+Kullback-Leibler Divergence Calculation的主要过程如算法\ref{alg:malicious-node-detection}的21-25行所示。对于每个节点的低频向量\(\mathbf{G}_i^t\)以及干净以及上一步求得的干净成分\(\tilde{G}^t_0\)，通过Softmax函数来将它们转换为相应的概率分布 \(P_i^t\) 和 \(Q^t\) 。然后利用KL散度即公式\ref{equation:KL}计算每个节点概率分布\((P_i^t\)和干净分量概率分布 \(Q^t\) 之间的距离，得到相应的分布差异集合\(S = {{KL}}_1, {{KL}}_2, \ldots, {{KL}}_n\)。
+
+\begin{equation}
+{{KL}}_i = D(P_i^t \| Q^t) = \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)
+\label{equation:KL}
+\end{equation}
+
+其中
+\[
+P_i^t = Softmax(G_i^t)
+\]
+
+\[
+Q^t = Softmax(\tilde{G_0^t})
+\]
+
+\item \textbf{Single-round Malicious Node Detection}
+
+最后Single-round Malicious Node Detection的的主要过程如算法\ref{alg:malicious-node-detection}的28-29行所示。利用HDBSCAN对计算出来的KL散度集合$S$进行聚类，得到簇\(C_1, C_2, \ldots, C_K\)，从所有簇中选出最大的一簇（即包含节点数量最多的簇），记作 \(C_{max}\)。基于每轮参与训练的良性节点相较于恶意节点数量较多的假设，并且相较于恶意节点，所有良性节点与干净分量之间的KL散度具有更高的相似性，因此将 \(C_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)。对于除\(C_{max}\)外的所有其他簇\(C_i\)（\(i \neq {max}\)），将其中所有节点标记为恶意节点\(U_{mal}\)。
+
+\end{enumerate}
+
+\subsection{多轮次攻击识别}
+
+\textbf{Motivation}: 后门攻击
+
+\textbf{Overview}: 前面的攻击中已经可以有效地针对单轮次攻击进行识别，本部分主要结合客户端的历史记录对客户端进行有效的识别。本部分将保留历史$T$轮次的全局模型$G_t$，并将其Flatten后视为高维空间中的一个点；同时保留每个客户端的历史梯度变化，将其视为高维空间中的一个向量，将其延伸后视为一个射线。对于每个客户端，使用最小覆盖球算法计算得到一个最小的超球，覆盖掉$\varepsilon$比例的射线。最终球心的位置可以被视为对应客户端对全局模型的意图引导点，球心的半径可以视为对应客户端的置信度。
+
+\begin{algorithm}
+\caption{Malicious Node Detection via History}
+\label{alg:malicious-node-detection-history}
+\begin{algorithmic}[1]
+\State \textbf{Input:} Global model history $\{G_{t-T}, G_{t-T+1}, \dots, G_{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{l_i}^{t-T}, \triangledown \theta_{l_i}^{t-T+1}, \dots, \triangledown \theta_{l_i}^{t-1}\}$, threshold $\varepsilon$
+\State \textbf{Output:} Set of clients marked as normal $U_{nor}$ and set of clients marked as malicious $U_{mal}$
+\State Step 1: Keep T-rounds History
+\For {Node $l_i$}
+    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_{l_i}^t)$
+    \State $DB.gradient\ \ +=\ \ \bar{\theta_i^t}$
+    \State $DB.model\ \ +=\ \ G_{t-1}$
+\EndFor
+\State Step 2: Construct Ray Model
+\For {Node $l_i$}
+    \State Construct rays using flattened global models and gradient updates:
+    \State $P_{l_i}^{t-j} = Flatten(G_{t-j-1})$, $\mathbf{d}_{l_i}^{t-j} = \bar{\theta}_{l_i}^{t-j}$ for $j = 0, 1, \ldots, T-1$
+\EndFor
+\State Step 3: Minimum Enclosing Hypersphere Calculation
+\For {Node $l_i$}
+    \State Initialize center $O_0$ and radius $r_0$
+    \While {Not Converged}
+        \State Calculate projection points $Q_{l_i}^{t-j}$ and sort by distance to $O_k$
+        \State Compute $D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{l_i}^{t-j}\|$
+        \State Update $O_{k+1} = O_k + \alpha \left(\frac{1}{\lceil n\times \varepsilon\rceil} \sum_{1\leq j\leq \lceil n\times \varepsilon\rceil} (Q_{l_i}^{t-j} - O_k)\right)$
+        \State Update $r_{k+1} = D_k$
+    \EndWhile
+    \State Calculate confidence $C_i = \frac{1}{r_i + \epsilon}$
+\EndFor
+\State Step 4: Abnormal Detection
+\For {Node $l_i$}
+    \State Calculate adjusted LOF: $\text{adjusted\_lof}(x_i) = \text{LOF}(x_i) \times (r_i + \epsilon)$
+    \State Determine threshold $\tau'$ and classify nodes as normal or malicious
+\EndFor
+\State \textbf{Return} $U_{nor}, U_{mal}$
+\end{algorithmic}
+\end{algorithm}
+
+算法\ref{alg:malicious-node-detection-history}展示了根据每个客户端历史记录进行识别的识别过程，主要包含4个步骤：
+
+\begin{enumerate}
+
+\item \textbf{Keep T-rounds History}
+
+“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将梯度变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$G_t$，将客户端$l_i$第$t$轮次训练后的模型记为$\theta^t_{l_i}$。客户端$l_i$将训练后的模型$\theta^t_{l_i}$减去训练前中央服务器下发的全局模型$G_t$，就得到了$t$轮次的梯度变化$\triangledown \theta^t_{l_i}=\theta^t_{l_i}-G_{t-1}$。客户端将梯度变化$\triangledown \theta^t_{l_i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的梯度变化$\triangledown \theta^t_{l_i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上次下发的全局模型$G_{t-1}$。中央服务器最多保留$T$轮次的模型和梯度历史记录。此部分可以参考算法\ref{alg:malicious-node-detection-history}的step1。
+
+\item \textbf{Obtain the Purpose Intention}
+
+“Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表$t-1$轮次的全局模型，射线的方向代表$t$轮次展平后的梯度变化。问题的优化目标是：找到一个最小的超球，包含至少$\varepsilon$比例的射线。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
+
+“Construct Ray Model”的主要过程如下。对于每个客户端 \(l_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的梯度更新历史。
+
+\begin{itemize}
+    \item 设 \( G_{t-T}, G_{t-T+1}, \dots, G_{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\theta_{l_i}^{t-T}}, \overline{\theta_{l_i}^{t-T+1}}, \dots, \overline{\theta_{l_i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(l_i\) 上传的展平后的梯度变化向量。
+    \item 对于每一轮 \( t-j \) (\( j = 0, 1, \dots, T-1 \))，我们将每个射线的起点表示为展平后的全局模型 \( G_{t-j-1} \)，并将每个射线的方向向量表示为展平后的梯度变化 \( \overline{\theta}_{l_i}^{t-j} \)。因此，射线模型可以构建如下：
+
+    \begin{equation}
+    \overline{\theta_{l_i}^{t-j}} = Flatten(G_{t-j-1}),
+    \end{equation}
+
+    \begin{equation}
+    \mathbf{d}_{l_i}^{t-j} = \bar{\theta}_{l_i}^{t-j},
+    \end{equation}
+
+    其中，\( \overline{\theta_{l_i}^{t-j}} \) 是射线的起点，\( \mathbf{d}_{l_i}^{t-j} \) 是射线的方向向量。
+\end{itemize}
+
+“Minimum Enclosing Hypersphere Calculation”的主要过程如下。基于构建的射线模型，使用最小覆盖球算法找到一个能够覆盖至少 \( \varepsilon \) 比例的射线的最小超球。
+
+\begin{itemize}
+    \item 首先，设定初始球心 \( O_0 \) 为所有射线起点的几何中心，计算公式如下：
+
+    \begin{equation}
+    O_0 = \frac{1}{T} \sum_{j=0}^{T-1} \overline{\theta_{l_i}^{t-T+1}}.
+    \end{equation}
+
+    \item 初始半径 \( r_0 \) 设定为从初始球心 \( O_0 \) 到所有射线起点的最大距离：
+
+    \begin{equation}
+    r_0 = \max_{1\leq T} \|O_0 - \overline{\theta_{l_i}^{t-T+1}}\|.
+    \end{equation}
+
+    \item 接下来，采用迭代方法来更新球心和半径：
+    \begin{itemize}
+       \item 对于每次迭代 \( k \)，计算当前球心 \( O_k \) 到所有射线的最近投影点 \( Q_{l_i}^{t-j} \)，按照距离当前球心的位置排序
+
+        \begin{equation}
+        \text{Sort}(\{ \| O - \overline{\theta_{l_i}^{t-T+1}} \| : i = 1, 2, \ldots, T \})
+        \end{equation}
+
+        并计算这些投影点的最大距离 \( D_k \)：
+
+        \begin{equation}
+        D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{l_i}^{t-j}\|.
+        \end{equation}
+
+        \begin{equation}
+        O_{k+1} = O_k + \alpha \left(\frac{1}{\lceil n\times \varepsilon\rceil} \sum_{1\leq j\leq \lceil n\times \varepsilon\rceil} (Q_{l_i}^{t-j} - O_k)\right),
+        \end{equation}
+
+        \begin{equation}
+        r_{k+1} = D_k,
+        \end{equation}
+
+        其中，\( \alpha \) 是学习率，通常取一个小的正数（如 0.1）。
+    \end{itemize}
+    \item 终止条件：当更新后的半径 \( r_{k+1} \) 与上一次的半径 \( r_k \) 相差小于一个预设的阈值 \( \epsilon \)（如 \( 10^{-6} \)），或者达到预设的最大迭代次数时，停止迭代。
+\end{itemize}
+
+这部分可以定义为一个有约束的最优化问题：
+
+\begin{equation}
+\min_{O, r} \, r 
+\end{equation}
+$$
+\text{s.t.} \quad \| O - (\overline{\theta_{l_i}^{t-T+1}} + t_i \mathbf{d}_i) \|^2 \leq r^2, \, 1\leq i\leq \lceil n \times \varepsilon \rceil
+$$
+
+\item \textbf{Abnormal Detection}
+
+“Abnormal Detection”的主要过程基于局部离群因子（Local Outlier Factor, LOF）计算，并结合“最小覆盖球”得出的置信度来调整 LOF 分数。异常检测的目标是识别出异常的客户端，确保联邦学习过程中的全局模型安全性和鲁棒性。其主要流程如算法14-24行所示。
+
+\begin{itemize}
+    \item 首先，计算局部离群因子（LOF）。对于一个样本点 \(x_i\)，其局部可达密度（Local Reachability Density, LRD）定义为其相对于 \(\varepsilon\)-邻域内点的平均可达距离的倒数：
+
+    \begin{equation}
+    \text{LRD}(x_i) = \frac{1}{\frac{1}{\varepsilon} \sum_{x_j \in \mathcal{N}_\varepsilon(x_i)} \text{reach-dist}_\varepsilon(x_i, x_j)},
+    \end{equation}
+
+    其中，\(\text{reach-dist}_\varepsilon(x_i, x_j)\) 是点 \(x_i\) 到其邻居 \(x_j\) 的可达距离，定义为：
+
+    \begin{equation}
+    \text{reach-dist}_\varepsilon(x_i, x_j) = \max(\text{dist}(x_i, x_j), \varepsilon\text{-dist}(x_j)),
+    \end{equation}
+
+    这里，\(\varepsilon\text{-dist}(x_j)\) 表示点 \(x_j\) 到其第 \(\varepsilon\) 个最近邻的距离。
+
+    \item 对于点 \(x_i\)，其局部离群因子（LOF）定义为其邻域内所有点的局部可达密度与自身局部可达密度的比值的平均值：
+
+    \begin{equation}
+    \text{LOF}(x_i) = \frac{1}{\varepsilon} \sum_{x_j \in \mathcal{N}_\varepsilon(x_i)} \frac{\text{LRD}(x_j)}{\text{LRD}(x_i)}.
+    \end{equation}
+
+    \item 接下来，基于“最小覆盖球”方法计算得到的置信度来调整 LOF 分数。假设通过“最小覆盖球”算法得到了客户端 \(i\) 的最小覆盖球半径 \(r_i\)，定义置信度 \(C_i\) 为半径的倒数：
+
+    \begin{equation}
+    C_i = \frac{1}{r_i + \epsilon},
+    \end{equation}
+
+    其中，\(\epsilon\) 是一个很小的正数，用于避免除零错误。
+
+    \item 使用置信度 \(C_i\) 的倒数来调整 LOF 分数，使得置信度越高的点，其调整后的 LOF 分数越低：
+
+    \begin{equation}
+    \text{adjusted\_lof}(x_i) = \text{LOF}(x_i) \times (r_i + \epsilon).
+    \end{equation}
+
+    \item 计算调整后的 LOF 分数的均值 \(\mu_{\text{adjusted\_lof}}\) 和标准差 \(\sigma_{\text{adjusted\_lof}}\)，然后使用以下公式设置阈值 \(\tau'\)：
+
+    \begin{equation}
+    \tau' = \mu_{\text{adjusted\_lof}} + k \times \sigma_{\text{adjusted\_lof}},
+    \end{equation}
+
+    其中，\(k\) 是一个\textbf{敏感性系数}（sensitivity coefficient），其选择对异常检测的结果具有重要影响。为了在精确度与召回率之间取得平衡，\(k\) 的值应通过\textbf{基于数据驱动的交叉验证策略}来确定。具体而言，可以在训练集中使用不同的 \(k\) 值进行多次迭代，计算每种情况下的检测性能指标（如精确度、召回率和 F1 分数），并通过优化这些指标选择最优的 \(k\) 值。此外，选择 \(k\) 时也可以考虑使用贝叶斯优化（Bayesian Optimization）等先进的超参数调优方法，以自适应地选择最能反映数据特征的敏感性系数值。对于检测结果中大于该阈值的点，将其判定为异常点。
+\end{itemize}
+
+\item \textbf{Gradients Aggregation}
+
+在上一步已经剔除了恶意客户端后，本部分将使用主观逻辑模型（Subjective Logic Model）进行剩余客户端的梯度聚合。主观逻辑模型是一种基于概率论和信任度的数学框架，能够有效地处理不确定性和不一致性信息。在联邦学习场景中，主观逻辑模型可以用于在不完全信任的环境下对客户端上传的梯度进行加权聚合，从而提高全局模型的稳健性。其主要流程如算法25-29行所示。
+
+\begin{itemize}
+    \item \textbf{定义主观逻辑模型的信任参数}：
+
+    对于每个被认为是正常的客户端 \( C_i \)，根据其上传的梯度更新 \( \triangledown \theta_i \)，定义主观逻辑模型中的信任参数，包括\textbf{信任度}（Belief）、\textbf{不信任度}（Disbelief）和\textbf{不确定度}（Uncertainty）。信任度 \( b_i \) 可以根据每个客户端的历史表现或其他统计指标来定义。对于本次的应用，信任度可以与上一步异常检测中调整后的 LOF 分数成反比。
+
+    \item \textbf{计算每个客户端的证据权重}：
+
+    基于定义的信任参数，为每个客户端 \( C_i \) 计算其证据权重 \( w_i \)。证据权重可以表示为信任度 \( b_i \) 的函数形式，例如：\( w_i = f(b_i) \)，其中 \( f(b_i) \) 可以是线性或非线性的映射函数。
+
+    \item \textbf{加权聚合客户端梯度}：
+
+    使用证据权重 \( w_i \) 对所有正常客户端的梯度更新 \( \triangledown \theta_i \) 进行加权聚合，以得到全局模型的梯度更新：
+
+    \begin{equation}
+    \triangledown \theta_{\text{global}} = \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i
+    \end{equation}
+
+    其中，\( U_{nor} \) 是所有被判定为正常的客户端集合。
+
+    \item \textbf{更新全局模型}：
+
+    使用聚合后的梯度更新全局模型参数，以继续下一轮的联邦学习迭代。
+\end{itemize}
+
+通过使用主观逻辑模型对客户端梯度进行聚合，能够有效利用信任度信息来优化全局模型的更新过程，减少因恶意客户端或不确定性导致的模型偏差。
+
+\end{enumerate}
+
+% \textbf{时间上不连续的攻击}
+
+% 为了应对中央服务器的恶意用户检测问题，攻击者可能会进行时间上不连续的攻击。总体上来说是攻击者为了提升自己的隐蔽性，并非每轮次都进行攻击。这样，在攻击者不进行攻击的轮次中，只考虑单轮次的检测方式就无法生效。例如G Abad等人提出的Time-Distributed Backdoor Attack\cite{abad2024time}，不是像传统的backdoor那样在空间上（即所有时间步中）使用相同的触发器，而是在多个恶意设备在不同时间段内注入触发器。再例如X.
 Lyu等人提出的\cite{lyu2024coba}，设计的目的是增强后门攻击的稀疏性和隐蔽性。这些都难以在单次的识别中成功检测。
 
-\textbf{隐蔽性攻击}
+% \textbf{隐蔽性攻击}
 
-还有一类攻击在时间上可能是连续的，但是为了规避中央服务器的检测，其在攻击强度上较低。这类攻击还可以细分为两小类：一类是通过拆分或限缩的方式，通过将任务拆分给多个客户端，或者限制单次攻击的力度，从而增大检测难度；另一类是非直奔目标的攻击，每次都不直接诱导模型到目标位置，而是采用迂回曲折的方式，最终将目标诱导至目标地点。例如T.
+% 还有一类攻击在时间上可能是连续的，但是为了规避中央服务器的检测，其在攻击强度上较低。这类攻击还可以细分为两小类：一类是通过拆分或限缩的方式，通过将任务拆分给多个客户端，或者限制单次攻击的力度，从而增大检测难度；另一类是非直奔目标的攻击，每次都不直接诱导模型到目标位置，而是采用迂回曲折的方式，最终将目标诱导至目标地点。例如T.
 A.
@@
 
-\textbf{具体检测方法}
+% \textbf{具体检测方法}
 
-这些攻击都难以检测，但是不论其方式再怎么千变万化，最终一定要达到攻击者所想达到的目标。我们对训练过程进行建模，每次中央服务器下发的模型视为高维空间中的一个点，而客户端训练后上传的梯度视为从这个点出发的一个向量。这样，对于每个客户端，我们就可以得到个有很多具有起点的向量的图。由于梯度是诱导模型变换的方向，因此攻击者若想要达到攻击目的，不论其攻击过程有多么地曲折和隐蔽，其所有向量最终指向的目的区域一定是和良性客户端不同的。我们将这些高维空间中具有起点的绝大多数向量的目的汇聚区域称为“汇聚点”。在允许一定返回的离群值的前提下，我们有理由认为一个客户端的汇聚点就是这个客户端的最终目的。因此问题就变成了如何寻找高维空间中多条具有起点的向量的汇聚点了。TODO: 精美图一张。
+% 这些攻击都难以检测，但是不论其方式再怎么千变万化，最终一定要达到攻击者所想达到的目标。我们对训练过程进行建模，每次中央服务器下发的模型视为高维空间中的一个点，而客户端训练后上传的梯度视为从这个点出发的一个向量。这样，对于每个客户端，我们就可以得到个有很多具有起点的向量的图。由于梯度是诱导模型变换的方向，因此攻击者若想要达到攻击目的，不论其攻击过程有多么地曲折和隐蔽，其所有向量最终指向的目的区域一定是和良性客户端不同的。我们将这些高维空间中具有起点的绝大多数向量的目的汇聚区域称为“汇聚点”。在允许一定返回的离群值的前提下，我们有理由认为一个客户端的汇聚点就是这个客户端的最终目的。因此问题就变成了如何寻找高维空间中多条具有起点的向量的汇聚点了。TODO: 精美图一张。
 
-这其实是属于有约束的最优化问题。不失一般性，我们可以在高维空间中找到一个点，使得这个点到所有向量所在直线的距离之和最小。那么这个点就可以作为我们想要寻找的“汇聚点”。我们已知每条向量所在直线的方程，因此只需设这个点的坐标，将其与所有直线的距离之和累加就能得到一个带有未知数的表达式。目的是让这个表达式的值最小，问题就变成了一个不等式问题，求解即可得到该点的坐标。
+% 这其实是属于有约束的最优化问题。不失一般性，我们可以将其视为一个近似最小覆盖超球的问题。
 
-得出了每个客户端的“汇聚点”，使用简单的聚类的方法就能有效地识别出恶意客户端了。
+% \subsection{问题背景与建模}
+
+% 在联邦学习（Federated Learning, FL）场景中，每个客户端上传的梯度可以视为一条射线，这条射线的起点是中央服务器下发的模型参数，方向是客户端计算的梯度方向。通过计算每个客户端上传的梯度所形成的射线与一个最小覆盖超球之间的关系，我们可以分析并识别潜在的恶意客户端。
+
+% \subsubsection{问题定义}
+
+% 给定 \( n \) 条射线，每条射线由起点 \( P_i \) 和方向向量 \( \mathbf{d}_i \) 表示。目标是找到一个球的球心 \( O \) 和半径 \( r \)，使得球被大多数射线（例如 \( 90\% \)）穿过。
+
+% \subsubsection{数学表述}
+
+% 我们需要找到一个点 \( O \) 和半径 \( r \)，使得对于至少 \( k = \lceil 0.9n \rceil \) 条射线 \( i \)，存在一个 \( t_i \geq 0 \) 使得：
+
+% \begin{equation}
+% \| O - (P_i + t_i \mathbf{d}_i) \|^2 \leq r^2.
+% \end{equation}
+
+% 这个问题可以转化为一个优化问题，目标是最小化球的半径 \( r \)，并满足所需比例的射线穿过球的约束。
+
+% \subsection{迭代算法步骤}
+
+% 该算法采用一种迭代优化方法，通过逐步调整球心 \( O \) 和半径 \( r \)，使其逐渐逼近最优解。具体步骤如下：
+
+% \subsubsection{初始化}
+
+% \begin{itemize}
+%     \item 初始球心 \( O_0 \) 设置为所有射线起点的几何中心：
+
+%     \begin{equation}
+%     O_0 = \frac{1}{n} \sum_{i=1}^n P_i.
+%     \end{equation}
+
+%     \item 初始半径 \( r_0 \) 设置为从初始球心到所有射线起点的最大距离：
+
+%     \begin{equation}
+%     r_0 = \max_{0\leq i\leq \lceil n\times \varepsilon\rceil} \|O_0 - P_i\|.
+%     \end{equation}
+% \end{itemize}
+
+% \subsubsection{迭代过程}
+
+% 对于每一步迭代 \( k \)，我们执行以下步骤：
+
+% \begin{enumerate}
+%     \item \textbf{计算投影点}：对于每条射线 \( i \)，找到射线与当前球心 \( O_k \) 最近的点 \( Q_i \)，并计算参数 \( t_i \)：
+
+%     \begin{equation}
+%     t_i = \max\left(0, \frac{(O_k - P_i) \cdot \mathbf{d}_i}{\|\mathbf{d}_i\|^2}\right),
+%     \end{equation}
+
+%     其中，\( Q_i \) 是射线上的点，计算公式为：
+
+%     \begin{equation}
+%     Q_i = P_i + t_i \mathbf{d}_i.
+%     \end{equation}
+
+%     \item \textbf{计算与球心的距离}：计算球心 \( O_k \) 到这些投影点 \( Q_i \) 的距离 \( D_i \)：
+
+%     \begin{equation}
+%     D_i = \|O_k - Q_i\|.
+%     \end{equation}
+
+%     \item \textbf{选择最近的 \( k \) 个点}：对所有距离 \( D_i \) 进行排序，选择最近的 \( k \) 个点，计算这些点中的最大距离 \( D_k^{(k)} \)。
+
+%     sort
+
+%     \item \textbf{更新球心和半径}：
+
+%     % 如果新的最大距离 \( D_k^{(k)} \) 大于当前半径 \( r_k \)，则更新球心 \( O_k \) 和半径 \( r_k \)：
+
+%     将球心向着新球心的方向移动一段距离
+
+%     \begin{equation}
+%     % O_{k+1} = O_k + \alpha \left(\frac{1}{k} \sum_{i \in \text{最近的 } k \text{ 个点}} (Q_i - O_k)\right),
+%     O_{t} = O_{t-1} + \alpha \left(\frac{1}{n\times \varepsilon} \sum_{0\leq i\leq \lceil n\times \varepsilon\rceil} (Q_i - O_t)\right),
+%     \end{equation}
+
+%     \begin{equation}
+%     r_{k+1} = D_k^{(k)},
+%     \end{equation}
+
+%     其中，\( \alpha \) 是学习率，通常取一个小的正值（如 0.1）。这个更新步骤的作用是朝着一个更加紧凑的覆盖超球方向优化。
+
+%     \item \textbf{终止条件}：当更新后的半径 \( r_{k+1} \) 与上一次的半径 \( r_k \) 相差小于一个小的阈值 \( \epsilon \)（例如 \( 10^{-6} \)时，停止迭代。
+% \end{enumerate}
+
+% \subsection{置信度定义}
+
+% 在联邦学习（Federated Learning, FL）环境下，恶意客户端可能会通过上传异常梯度来影响全局模型的训练过程。为提高系统的鲁棒性，本研究提出了一种基于几何优化的置信度计算方法，用于评估客户端上传梯度的有效性和一致性。具体而言，我们将每个客户端的射线表示为一个起点 \(P_i\) 和方向 \(\mathbf{d}_i\)，并通过求解覆盖大多数射线的最小超球来定义每个客户端的置信度。
+
+% 置信度 \(C_i\) 定义为与该最小球半径 \(r_i\) 的倒数成正比的度量，公式如下：
+
+% \begin{equation}
+% C_i = \frac{1}{r_i + \epsilon},
+% \end{equation}
+
+% 其中，\(r_i\) 表示覆盖大多数射线（例如 \(90\%\)）的最小球半径，\(\epsilon\) 是一个小的正数（如 \(10^{-6}\)），用于防止除零错误。
+
+% 通过这一定义，置信度 \(C_i\) 的值反映了客户端 \(i\) 上传梯度方向的集中程度。置信度越高（即半径 \(r_i\) 越小），表明该客户端的梯度方向较为一致，反之则表示梯度方向较为分散，可能存在异常行为或恶意攻击的迹象。
+
+% \subsection{置信度在梯度聚合中的应用}
+
+% 在 FL 场景中，为了减轻恶意客户端上传的异常梯度对全局模型的影响，可以根据每个客户端的置信度对其上传的梯度进行加权聚合。假设 \(g_i\) 为客户端 \(i\) 上传的梯度更新，则加权后的全局梯度更新 \(G\) 可表示为：
+
+% \begin{equation}
+% G = \frac{\sum_{i=1}^{n} C_i \cdot g_i}{\sum_{i=1}^{n} C_i}.
+% \end{equation}
+
+% 该公式中的 \(C_i \cdot g_i\) 表示根据客户端 \(i\) 的置信度对其上传的梯度进行加权，分母 \(\sum_{i=1}^{n} C_i\) 用于归一化，以确保所有客户端加权后的梯度贡献和为 1。通过这种方式，置信度高的客户端对最终聚合结果的影响较大，而置信度低的客户端影响较小。
+
+% 使用置信度加权的梯度聚合方法可以显著提高 FL 系统的鲁棒性和安全性，具体表现为以下几个方面：
+
+% \begin{enumerate}
+%     \item \textbf{抵御恶意客户端攻击}：由于恶意客户端的置信度 \(C_i\) 较低，其上传的异常梯度对全局模型更新的影响有限，能够有效减轻攻击效果。
+%     \item \textbf{增强模型鲁棒性}：置信度高的客户端通常具有一致的梯度方向，在聚合中占据主导地位，确保了全局模型更新的方向更加稳定和有效。
+%     \item \textbf{自适应聚合策略}：该方法能够根据客户端的实际行为动态调整聚合策略，而无需事先设定恶意客户端的数量或行为模式，这使得方法在各种场景下更具通用性和适应性。
+% \end{enumerate}
+
+\subsection{EXPERIMENTAL EVALUATION}
+
+\subsubsection{Experimental Setup}
+
+本实验在一台配置高性能硬件的计算机上进行，操作系统为 Ubuntu 20.04.3 LTS，内核版本为 5.15.0-73-generic，以确保计算稳定性和结果的可靠性。计算机配置了 Intel(R) Core(TM) i9-10940X @ 3.30GHz 的处理器，具有28个核心，最大频率可达4.8GHz，能够提供强大的并行计算能力以高效处理大规模计算任务。内存为 128GB DDR4，速度为 2933 MT/s，这种大容量的内存配置有助于在处理复杂数据集和大规模模型训练时减少内存瓶颈，提升数据加载和处理速度。图形处理单元（GPU）方面，采用了2块 NVIDIA GeForce RTX 3090，每块显存为24GB，驱动版本为 470.239.06，CUDA 版本为 11.4。双GPU配置提供了强大的并行计算能力，可以显著加速深度学习模型的训练过程，特别是在图像处理和自然语言处理等需要大量计算的任务中表现尤为出色。存储设备为高速SSD，支持数据的高速读写操作，显著降低I/O操作时间，确保大数据集的快速加载和模型的高效训练。为了确保实验结果的可靠性和再现性，本实验使用了标准的数据集，包括MNIST数据集、CIFAR-10数据集等主流的数据集。上述硬件配置为实验提供了充足的计算资源，能够支持大规模深度学习模型的训练和复杂算法的测试。我们采用了一些先进的攻击方式，并使用我们的防御方式和State-Of-The-Art以及较为主流的防御方式进行对比，并针对“结合多轮次进行攻击”的攻击方式进行了实验，验证了我们的有效性。
 

### 2024-09-08 temp.FenLei.isolationForest-二维.py
log: 凌晨之作
some how a little dangerous

@@ -1,39 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-04 10:33:08
-LastEditors: LetMeFly
-LastEditTime: 2024-09-04 10:33:19
-'''
-import numpy as np
-import pandas as pd
-from sklearn.ensemble import IsolationForest
-import matplotlib.pyplot as plt
-
-# 示例数据，假设有10个圆（实际数据需要替换）
-data = {
-    'x': [2, 3, 5, 8, 13, 21, 34, 55, 89, 144],  # 圆心x坐标
-    'y': [3, 5, 7, 11, 17, 27, 37, 47, 60, 75],  # 圆心y坐标
-    'radius': [1, 1.2, 0.8, 1.5, 2.0, 1.7, 1.1, 3.0, 4.5, 5.0]  # 圆的半径，代表置信度
-}
-
-# 转化为DataFrame
-df = pd.DataFrame(data)
-
-# 使用Isolation Forest进行异常检测
-model = IsolationForest(n_estimators=100, contamination=0.1, random_state=42)  # contamination为预期异常点比例
-df['scores'] = model.fit_predict(df[['x', 'y', 'radius']])
-df['anomaly_score'] = model.decision_function(df[['x', 'y', 'radius']])
-
-# 可视化异常检测结果
-plt.figure(figsize=(10, 6))
-plt.scatter(df['x'], df['y'], c=df['scores'], cmap='coolwarm', edgecolor='k', s=100)
-plt.xlabel('x - 圆心x坐标')
-plt.ylabel('y - 圆心y坐标')
-plt.title('基于Isolation Forest的异常检测')
-plt.colorbar(label='异常得分')
-plt.show()
-
-# 显示异常点
-anomalies = df[df['scores'] == -1]
-print("异常点:")
-print(anomalies)

### 2024-09-08 temp.FenLei.isolationForest-高维.py

@@ -1,38 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-04 10:33:08
-LastEditors: LetMeFly
-LastEditTime: 2024-09-04 10:37:39
-'''
-from sklearn.ensemble import IsolationForest
-import numpy as np
-
-# 创建一个5维数据集，每个点有5个坐标 (x1, x2, x3, x4, x5) 和一个置信度特征 (confidence)
-np.random.seed(42)
-X = np.random.randn(100, 6)  # 100个数据点，每个点有6个特征（5维坐标 + 1个置信度）
-
-# 引入一些异常点，确保它们在高维空间中明显不同
-outliers = np.random.uniform(low=-10, high=10, size=(10, 6))
-X = np.vstack((X, outliers))
-
-# 初始化IsolationForest模型
-model = IsolationForest(n_estimators=100, contamination=0.1, random_state=42)
-
-# 使用fit_predict方法进行训练和预测
-results = model.fit_predict(X)
-
-# 打印结果
-print("预测结果（1表示正常点，-1表示异常点）：\n", results)
-
-# 显示异常点的数量
-print(f"异常点的数量：{list(results).count(-1)}")
-
-"""
-预测结果（1表示正常点，-1表示异常点）：
- [ 1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1
-  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1 -1  1  1  1  1
-  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1
-  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1  1
-  1  1  1  1 -1 -1 -1 -1 -1 -1 -1 -1 -1 -1]
-异常点的数量：11
-"""

### 2024-09-08 temp.mouse.1.py

@@ -1,0 +1,20 @@
+'''
+Author: LetMeFly
+Date: 2024-09-08 02:53:30
+LastEditors: LetMeFly
+LastEditTime: 2024-09-08 02:53:41
+'''
+from pynput import mouse
+import pyautogui
+
+# 定义鼠标单击事件的回调函数
+def on_click(x, y, button, pressed):
+    if button == mouse.Button.left and pressed:  # 只处理左键按下事件
+        # 获取当前鼠标位置
+        current_position = pyautogui.position()
+        print(f"鼠标当前位置: {current_position}")
+        return False  # 返回False以停止监听器
+
+# 监听鼠标事件
+with mouse.Listener(on_click=on_click) as listener:
+    listener.join()

### 2024-09-08 temp.mouse.2.py

@@ -1,0 +1,62 @@
+'''
+Author: LetMeFly
+Date: 2024-09-08 02:58:47
+LastEditors: LetMeFly
+LastEditTime: 2024-09-08 03:15:04
+'''
+import pyautogui
+import time
+from datetime import datetime, timedelta
+from ctypes import windll
+
+# 定义Chrome和微信窗口的点击位置
+chrome_position = (383, 291)
+wechat_position = (1184, 748)
+
+def perform_actions():
+    # 移动鼠标到Chrome窗口的指定位置并点击
+    pyautogui.moveTo(chrome_position[0], chrome_position[1], duration=0.5)
+    pyautogui.click()
+
+    # 输入快捷键 Ctrl+A 和 Ctrl+V
+    pyautogui.hotkey('ctrl', 'a')
+    time.sleep(0.5)
+    pyautogui.hotkey('ctrl', 'v')
+    time.sleep(0.5)
+    pyautogui.hotkey('ctrl', 's')
+
+    # 等待时间（切换到微信窗口的时间）
+    time.sleep(3)
+
+    # 移动鼠标到微信窗口的指定位置并点击
+    pyautogui.moveTo(wechat_position[0], wechat_position[1], duration=0.5)
+    pyautogui.click()
+
+    # 输入回车键
+    pyautogui.press('enter')
+
+    # 等待几秒后执行锁屏操作
+    time.sleep(5)
+    # pyautogui.hotkey('win', 'l')
+    user32 = windll.LoadLibrary('user32.dll')
+    user32.LockWorkStation()
+
+# 计算从当前时间到下一个凌晨3点02分的时间差
+now = datetime.now()
+target_time = now.replace(hour=6, minute=12, second=0, microsecond=0)
+
+# 如果当前时间已经过了今天的3点02分，则计算到明天3点02分的时间
+if now > target_time:
+    target_time += timedelta(days=1)
+
+# 计算等待时间（秒）
+wait_time = (target_time - now).total_seconds()
+print(f"将休眠 {wait_time} 秒，直到 {target_time} 执行操作...")
+
+# 休眠直到指定时间
+time.sleep(wait_time)
+
+# 执行所有操作
+perform_actions()
+
+print("操作已完成！")

### 2024-09-08 temp.sgd.py

@@ -1,0 +1,38 @@
+'''
+Author: LetMeFly
+Date: 2024-09-06 15:38:44
+LastEditors: LetMeFly
+LastEditTime: 2024-09-06 15:38:52
+'''
+import matplotlib.pyplot as plt
+import numpy as np
+
+# 创建数据
+x = np.linspace(-3, 3, 100)
+y = np.linspace(-3, 3, 100)
+X, Y = np.meshgrid(x, y)
+Z = X**2 + Y**2  # 损失函数的例子，这里使用了一个简单的二次函数
+
+# 绘制等高线图
+plt.figure(figsize=(6, 6))
+plt.contour(X, Y, Z, levels=20, cmap='RdGy')
+
+# 绘制梯度下降路径
+x_path = [-2, -1.5, -1, -0.7, -0.5, -0.3, -0.1, 0]
+y_path = [-2, -1.2, -0.8, -0.5, -0.3, -0.1, -0.05, 0]
+plt.plot(x_path, y_path, marker='o', color='blue', linestyle='-', linewidth=1, markersize=5)
+
+# 标注起点和终点
+plt.text(x_path[0], y_path[0], 'Start', fontsize=12, ha='right')
+plt.text(x_path[-1], y_path[-1], 'End', fontsize=12, ha='left')
+
+# 设置图形标题和坐标轴
+plt.title('Gradient Descent Path on Contour Plot')
+plt.xlabel('X')
+plt.ylabel('Y')
+
+# 保存为SVG文件
+plt.savefig('gradient_descent.svg', format='svg')
+
+# 显示图形
+plt.show()

### 2024-09-08 temp.tryRe.py

@@ -1,10 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-04 11:30:01
-LastEditors: LetMeFly
-LastEditTime: 2024-09-04 11:30:28
-'''
-import re
-
-result = re.findall(r'\d+\d*', 'hello_123456a')
-print(result)

### 2024-09-09 attack-zh.tex
docs: 大改但是half版

@@
 
-时间隐蔽性后门攻击是指攻击者通过调整模型训练过程或优化后门植入等方式，使后门在恶意攻击者结束攻击后仍能长期存在，不被后续良性更新所覆盖，从而持续影响模型行为。 Chameleon\cite{dai2023chameleon}关注如何通过对比学习来调整中毒样本、干扰样本以及促进样本嵌入表示之间的关系，从而提高后门攻击的空间隐蔽性。ImgTrojan\cite{tao2024imgtrojan}通过在视觉语言模型的训练数据中注入少量恶意样本，使得这些后门即使在模型后续的良性训练中仍能保持有效，从而持续影响模型的行为。\cite{gu2023gradient}提出了一种新的梯度控制方法，通过跨层梯度幅度归一化和层内梯度方向投影，解决了参数高效调优（PET）过程中后门攻击的遗忘问题，从而维持攻击的持久性和隐蔽性。A3FL\cite{zhang2024a3fl}通过对抗性适应损失函数来优化触发器的方式，使得后门能够在全局训练动态中持久存在，从而在联邦学习模型中实现高效且持久的攻击效果。
-% 总之，现有的后门攻击策略在空间隐蔽性和时间隐蔽性方面都有了显著的进展。空间隐蔽性后门攻击通过优化特征空间中的触发器或梯度，使得恶意行为难以被现有的检测方法发现，从而实现了更高效、更难以检测的攻击。而时间隐蔽性后门攻击则专注于提高后门的持久性，使得即使在恶意攻击结束后，这些后门依然能够在模型中长期存在并继续影响其行为。通过这些攻击方式的结合，攻击者能够在各种应用场景中有效地躲避检测，并确保攻击效果的持续性，这对现有的防御机制提出了更高的挑战，强调了未来在开发更加鲁棒的防御方法方面的迫切需求。
+时间隐蔽性后门攻击是指攻击者通过调整模型训练过程或优化后门植入等方式，使后门在恶意攻击者结束攻击后仍能长期存在，不被后续良性更新所覆盖，从而持续影响模型行为。 Chameleon\cite{dai2023chameleon}关注如何通过对比学习来调整中毒样本、干扰样本以及促进样本嵌入表示之间的关系，从而提高后门攻击的空间隐蔽性。ImgTrojan\cite{tao2024imgtrojan}通过在视觉语言模型的训练数据中注入少量恶意样本，使得这些后门即使在模型后续的良性训练中仍能保持有效，从而持续影响模型的行为。\cite{gu2023gradient}提出了一种新的更新控制方法，通过跨层更新幅度归一化和层内更新方向投影，解决了参数高效调优（PET）过程中后门攻击的遗忘问题，从而维持攻击的持久性和隐蔽性。A3FL\cite{zhang2024a3fl}通过对抗性适应损失函数来优化触发器的方式，使得后门能够在全局训练动态中持久存在，从而在联邦学习模型中实现高效且持久的攻击效果。
+% 总之，现有的后门攻击策略在空间隐蔽性和时间隐蔽性方面都有了显著的进展。空间隐蔽性后门攻击通过优化特征空间中的触发器或更新，使得恶意行为难以被现有的检测方法发现，从而实现了更高效、更难以检测的攻击。而时间隐蔽性后门攻击则专注于提高后门的持久性，使得即使在恶意攻击结束后，这些后门依然能够在模型中长期存在并继续影响其行为。通过这些攻击方式的结合，攻击者能够在各种应用场景中有效地躲避检测，并确保攻击效果的持续性，这对现有的防御机制提出了更高的挑战，强调了未来在开发更加鲁棒的防御方法方面的迫切需求。
 
@@
 
-\begin{algorithm}
-\caption{Local model training process}
-\label{alg:local_update}
-\begin{algorithmic}[1]
-\State \textbf{Input:} $\theta_g^{t-1}, D_i, b, \eta, E_l$ \Comment{$E_l$ is the local epochs, $\eta$ is the local learning rate, and $b$ is the batch size}
-\State \textbf{Output:} $\triangledown \theta_i^t$ \Comment{Local model update}
+% \begin{algorithm}
+% \caption{Local model training process}
+% \label{alg:local_update}
+% \begin{algorithmic}[1]
+% \State \textbf{Input:} $\theta_g^{t-1}, D_i, b, \eta, E_l$ \Comment{$E_l$ is the local epochs, $\eta$ is the local learning rate, and $b$ is the batch size}
+% \State \textbf{Output:} $\triangledown \theta_i^t$ \Comment{Local model update}
 
-\State $(\theta_i^{t})^0 \gets \theta_g^{t-1}$ \Comment{Initialize model weights}
-\For{$e = 1$ to $E_l$}
-    \State $D_i^b \sim Sample(D_i, b)$ \Comment{Randomly sample a batch $D_i^b$ of size $b$ from $D_i$}
-    \State $(\theta_i^{t})^e \gets (\theta_i^{t})^{e-1} - \eta \nabla f(D_i^b, (\theta_i^{t})^{e-1})$
-\EndFor
-\State \textbf{return} $(\theta_i^{t})^{E_l} - (\theta_i^{t})^0$
-\end{algorithmic}
-\end{algorithm}
+% \State $(\theta_i^{t})^0 \gets \theta_g^{t-1}$ \Comment{Initialize model weights}
+% \For{$e = 1$ to $E_l$}
+%     \State $D_i^b \sim Sample(D_i, b)$ \Comment{Randomly sample a batch $D_i^b$ of size $b$ from $D_i$}
+%     \State $(\theta_i^{t})^e \gets (\theta_i^{t})^{e-1} - \eta \nabla f(D_i^b, (\theta_i^{t})^{e-1})$
+% \EndFor
+% \State \textbf{return} $(\theta_i^{t})^{E_l} - (\theta_i^{t})^0$
+% \end{algorithmic}
+% \end{algorithm}
 
@@
     \item \textbf{LoRA}：
-    在LoRA(Low-Rank Adaptation) 方法中，模型原始的参数为$\Theta$，模型引入的增量参数为$\theta$，每一个参数矩阵 $W$ 被表示为：
+    在LoRA(Low-Rank Adaptation) 方法中，每一个参数矩阵 $W$ 被表示为：
     \[
@@
     \]
-    其中，$W_0$ 为模型的原始权重矩阵，$\Delta W$ 是低秩增量矩阵，$B \in \mathbb{R}^{d_i \times r}$ 和 $A \in \mathbb{R}^{r \times d_o}$ 是低秩分解矩阵，$r$ 为矩阵的秩，满足 $r \ll \min(d_i, d_o)$。在联邦微调过程中，每个机器人节点仅对 $\theta$ 进行本地更新，保持 $\Theta$ 不变，从而降低通信和计算开销。
+    其中，$W_0$ 为模型的原始权重矩阵，$\Delta W$ 是低秩增量矩阵，$B$ 和 $A$ 是低秩分解矩阵，$r$ 为矩阵的秩。假设模型原始参数$\Theta = \sum {W_0}$，模型引入的增量参数$\theta = \sum {W}$。在联邦微调过程中，仅对增量参数$\theta$ 进行微调更新，保持原始参数$\Theta$不变。
 
     \item \textbf{本地模型训练}：
-    在每轮联邦训练的开始时，中心服务器将全局模型的增量参数 $\theta_g^{t-1}$ 发送给每个机器人节点。每个机器人节点$R_i$在获得增量参数$\theta_g^{t-1}$后，基于本地数据集 $D_i$ 进行微调训练，算法\ref{alg:local_update}展示了节点进行本地模型每轮训练的主要过程。
-    ，其目标是最小化本地损失函数 $f(D_i^b, \theta_i^{t})$：
+    在每轮联邦训练的开始时，中心服务器将全局模型的增量参数 $\theta_g^{t-1}$ 发送给每个机器人节点$R_i$。每个节点在获得增量参数$\theta_g^{t-1}$后，基于本地数据集 $D_i$ 进行微调训练。
+    % 算法\ref{alg:local_update}展示了节点进行本地模型每轮训练的主要过程。
+    假设本地训练的轮次为$E_l$，批次大小为$b$，学习率为$\eta$。对于每一轮，节点$R_i$首先从其本地数据集$D_i$中随机抽取一个批次数据$D_i^b \sim Sample(D_i, b)$，然后利用随机梯度下降等优化算法，对增量参数进行更新，
     \[
-    f(D_i^b, \theta_i^{t}) = \frac{1}{|D_i^b|} \sum_{j=1}^{|D_i^b|} \ell(x_{i,j}, y_{i,j}; \Theta + \theta_i^{t})
+    (\theta_i^{t})^e = (\theta_i^{t})^{e-1} - \eta \nabla f(D_i^b, (\theta_i^{t})^{e-1})\]
+    ，其中$(\theta_i^{t})^e$表示在第$e$轮微调后的参数，初始时$(\theta_i^{t})^0 = \theta_g^{t-1}$。
+    本地训练的目标是最小化损失函数 $f(D_i^b, (\theta_i^{t})^e)$：
+    \[
+    f(D_i^b, (\theta_i^{t})^e) = \frac{1}{|D_i^b|} \sum_{j=1}^{|D_i^b|} \ell(x_{i,j}, y_{i,j}; \Theta + (\theta_i^{t})^e)
     \]
-    其中$\Theta$为模型的原始参数， $\ell$表示损失函数例如交叉熵损失函数。训练结束后，节点将经过本地优化后的增量参数更新 $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ 上传到中心服务器。
+    其中$\Theta$是模型的原始参数， $\ell$表示损失函数（如交叉熵损失）。本地训练完成后，节点计算其增量参数更新 $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ 并上传至中心服务器。
     \item \textbf{联邦聚合}：
@@
     \[
-    \theta_g^t = Aggregate(\triangledown \theta_1^t, \triangledown \theta_2^t, \dots, \triangledown \theta_n^t)
+    \theta_g^t = \theta_g^{t-1} + Aggregate(\triangledown \theta_1^t, \triangledown \theta_2^t, \dots, \triangledown \theta_n^t)
     \]
-    其中，$\theta_g^t$ 是第 $t$ 轮更新的全局增量参数，更新后的全局增量参数 $\theta_g^t$ 将在下一轮训练前下发给所有机器人节点，用于进一步的本地微调。
+    其中，$Aggregate$表示中心服务器使用到的聚合算法，例如FedAvg、Krum、Bulyan、RoseAgg等，$\theta_g^t$ 是第 $t$ 轮更新的全局增量参数，更新后的全局增量参数 $\theta_g^t$ 将在下一轮训练前下发给所有机器人节点，用于进一步的本地微调。
 \end{enumerate}
@@
     \item Attacker's Goal：假设在对视觉语言模型进行联邦微调的场景中，存在一个或者多个由攻击者操纵的恶意节点。其目标是对全局模型 $\mathbf{F}$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别 $t$，同时尽可能保持对干净输入的分类准确性。
-    \item Attacker's ability: 假设攻击者对恶意节点的本地训练过程拥有绝对的控制权，即攻击者可以随意操作本地数据、触发器模式、优化方式以及本地更新等。同时攻击者可以使用“聪明”的攻击策略进行攻击，即单轮攻击可能不会体现攻击效果，而是在多轮攻击的联合作用下成功植入后门。这种场景是实际存在的，因为服务器只能从客户端获取训练后的模型，而无法获知模型的具体训练过程。相应地，攻击者无法影响中央服务器上的操作，例如更改聚合规则或篡改其他良性客户端的模型更新。
+    \item Attacker's Ability: 在联邦学习场景中，假设攻击者对恶意节点的本地训练过程具有完全的控制权。这意味着攻击者可以任意操控本地数据、触发器模式、优化策略和本地更新过程。此外，攻击者可以采用“智能”攻击策略，这种策略的特点是攻击效果不会在单轮训练中显现，而是通过多轮训练的累积效应逐步将后门植入全局模型中。这种场景在实际中是可能存在的，因为中央服务器只能接收到客户端上传的训练后模型更新，而无法知晓每个客户端的具体训练过程。然而，攻击者无法对中央服务器的操作进行干扰，例如，无法更改全局模型的聚合规则或篡改其他良性客户端的模型更新。
 \end{itemize}
@@
 $Q^t$ &  The distribution corresponding to $\tilde{G}_{0}^t$ after applying the Softmax function during the $t$-th round.. \\ \hline
-$O_t$ &  The center of the high dimensional ball $t$-th round. \\ \hline
+$O_t'$ &  The center of the high dimensional ball $t'$-th round. \\ \hline
+\( {v}_{i}^{t'} \) & The vector of the high dimensional ball $t'$-th round.\\ \hline
 
@@
 \subsection{单轮恶意节点识别}
-\textbf{Motivation}: 目前的防御策略主要集中于利用攻击的浅层语义特征来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向，范数以及神经元符号等。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。
+\textbf{Motivation}: 目前的防御策略主要集中于利用攻击的“浅层语义特征”来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向，范数以及神经元符号等几何或者统计特性。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。
 % Multi-metrics adaptively identifies backdoors in Federated learning
-首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意梯度，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意梯度。同时最新的研究表明，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性梯度，因为这些方法往往受到维度灾难的影响。最新的攻击策略已经能够通过精心调整，巧妙地避开这些基于浅层语义特征的防御措施，从而成功植入后门。
-% 后门攻击的性质：后门攻击在于使得模型建立起触发器和标签之间的关联，而不是常规图像之间的关联。
-% 为什么考虑转换到频率维度，现有的方案存在哪些缺点。
+首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终具有分布上的差异。
 
-\textbf{Overview}: 无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新始终相较于良性用户具有分布上的差异。%TODO
+\textbf{Overview}: 为解决基于浅层语义特征的防御方法在高维空间中面临的局限性，我们从后门攻击的本质出发，提出了一种基于深层语义特征的防御策略，重点分析模型更新在频率域上的分布差异。通过将本地模型更新转换到频域，我们能够更深入地捕捉恶意更新在低频成分上的异常表现，这些异常通常难以通过传统的浅层特征检测方法发现。通过对频率域上的特征进行分析，我们可以有效地区分出恶意节点与良性节点，从而增强联邦学习系统在面对复杂后门攻击时的鲁棒性和检测精度。
 
@@
     \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
-    \For{$k = 0$ to $d-1$}
-        \State $G_i^t[k] \gets 0$
-        \For{$j = 0$ to $d-1$}
-            \State $G_i^t[k] \gets G_i^t[k] + \bar{\theta_i^t}[j] \cos \left( \frac{\pi}{d} \left(j + \frac{1}{2}\right) k \right)$
-        \EndFor
-    \EndFor
+    \State $G_i^t = Trunc(DCT(\bar{\theta_i^t}), m)$ \Comment{Compute DCT and retain only the top $m$ low-frequency components}
 \EndFor
@@
 \For {Node $R_i$}
-    \State $KL_i \gets \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)$
+    \State $Ki \gets \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)$
 \EndFor
@@
 \begin{enumerate}
-\item \textbf{Frequency Domain Transformation}
+\item \textbf{Frequency Domain Transformation}：
+相比于目前基于浅层语义特征的防御方法，我们利用DCT进行频域转换，将模型的更新向量映射到频域空间，以探究其在频率域上的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的4-7行所示，假设每个本地模型的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，通过一维的DCT-II将其转换为对应的频率分布，并提取低频分量，得到频率向量\(G_i^t\)。这里的 $Trunc$ 操作表示仅保留前 $m$ 个低频分量，以捕捉频域中更具代表性的特征用于后续的恶意节点检测。
 
-Frequency Domain Transformation的主要过程如算法\ref{alg:malicious-node-detection}的4-12行所示。假设每个本地模型的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，我们通过一维的DCT-II将其转换为对应的频率分布，并提取对应的m个低频成分，得到低频向量\(G_i^t\)。对应的计算过程如下：
-\begin{equation}
-G_i^t = Trunc(DCT(Flatten(\triangledown \theta_i^t), m)
-\end{equation}
+% 对应的计算过程如下：
+% \begin{equation}
+% G_i^t = Trunc(DCT(Flatten(\triangledown \theta_i^t), m)
+% \end{equation}
 
-\begin{equation}
-Flatten: \bar{\theta_i^t} = Flatten(\triangledown \theta_i^t)
-\end{equation}
+% \begin{equation}
+% Flatten: \bar{\theta_i^t} = Flatten(\triangledown \theta_i^t)
+% \end{equation}
 
-\begin{equation}
-DCT: G_i^t[k] = \sum_{j=0}^{d-1} \bar{\theta_i^t}[j] \cos \left( \frac{\pi}{d} \left(j + \frac{1}{2}\right) k \right)
-\end{equation}
+% \begin{equation}
+% DCT: G_i^t[k] = \sum_{j=0}^{d-1} \bar{\theta_i^t}[j] \cos \left( \frac{\pi}{d} \left(j + \frac{1}{2}\right) k \right)
+% \end{equation}
 
-\item \textbf{Clean Ingredient Extraction}
-
-Clean Ingredient Extraction的主要过程如算法\ref{alg:malicious-node-detection}的15-18行所示。将所有节点的低频向量堆叠为矩阵 \(H^t = ({G_0^t}, {G_1^t}, \ldots, {G_{\mathcal{M}}^t}) \in \mathbb{R}^{m \times n}\)，其中每一列代表一个节点的低频向量。通过计算矩阵的最大奇异值及其对应的左奇异向量来作为相应的干净成分。即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)，根据公式\ref{equation:singular}，得到干净向量 \(\tilde{G}_0^t\)：
+\item \textbf{Clean Ingredient Extraction}：在将模型更新向量转换到频域空间后，我们基于“恶意节点的数量少于良性节点”的假设，通过奇异值分解（SVD）从所有节点的频域向量中提取出“干净成分”，并以此作为区分恶意与良性节点的标准。其主要过程如算法\ref{alg:malicious-node-detection}的10-13行所示，将所有节点的频率向量堆叠为矩阵 \(H^t = ({G_0^t}, {G_1^t}, \ldots, {G_{\mathcal{M}}^t}) \in \mathbb{R}^{m \times n}\)，其中每一列代表一个节点的低频向量。通过计算矩阵的最大奇异值及其对应的左奇异向量来作为相应的干净成分。即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)，根据公式\ref{equation:singular}，得到干净成分 \(\tilde{G}_0^t\)。这个干净成分\(\tilde{G}_0^t\)表示了良性节点的主要成分，能够有效地与恶意节点的异常行为区分开来，从而用于后续的恶意节点检测。
 
@@
 
-\item \textbf{Kullback-Leibler Divergence Calculation}
+\item \textbf{Kullback-Leibler Divergence Calculation}：在得到干净分量后，我们计算每个节点的频率向量与干净成分之间的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的16-20行所示，对于每个节点的低频向量\(\mathbf{G}_i^t\)以及上一步求得的干净成分\(\tilde{G}^t_0\)，通过Softmax函数来将它们转换为相应的概率分布 \(P_i^t\) 和 \(Q^t\) 。然后利用KL散度计算每个节点概率分布\((P_i^t\)和干净分量概率分布 \(Q^t\) 之间的距离，得到相应的分布差异集合\(S = ({{KL}}_1, {{KL}}_2, \ldots, {{KL}}_n)\)。这个集合反映了每个节点频率向量相对于干净成分的异常程度，较大的KL散度值表示节点对应的频率向量与干净成分的分布差异较大，提示该节点可能是恶意节点。最终，这些分布差异将作为恶意节点检测的基础，通过进一步分析来区分良性节点和潜在的恶意节点。
 
-Kullback-Leibler Divergence Calculation的主要过程如算法\ref{alg:malicious-node-detection}的21-25行所示。对于每个节点的低频向量\(\mathbf{G}_i^t\)以及干净以及上一步求得的干净成分\(\tilde{G}^t_0\)，通过Softmax函数来将它们转换为相应的概率分布 \(P_i^t\) 和 \(Q^t\) 。然后利用KL散度即公式\ref{equation:KL}计算每个节点概率分布\((P_i^t\)和干净分量概率分布 \(Q^t\) 之间的距离，得到相应的分布差异集合\(S = {{KL}}_1, {{KL}}_2, \ldots, {{KL}}_n\)。
+% \begin{equation}
+% {{KL}}_i = D(P_i^t \| Q^t) = \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)
+% \label{equation:KL}
+% \end{equation}
 
-\begin{equation}
-{{KL}}_i = D(P_i^t \| Q^t) = \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)
-\label{equation:KL}
-\end{equation}
+% 其中
+% \[
+% P_i^t = Softmax(G_i^t)
+% \]
 
-其中
-\[
-P_i^t = Softmax(G_i^t)
-\]
+% \[
+% Q^t = Softmax(\tilde{G_0^t})
+% \]
 
-\[
-Q^t = Softmax(\tilde{G_0^t})
-\]
+\item \textbf{Single-round Malicious Node Detection}：为了进一步识别恶意节点，我们利用良性节点与干净成分的分布高度相似这一特性，对分布差异集合$S$进行聚类分析。具体来说，我们采用流行的HDBSCAN算法对计算得到的KL散度集合$S$进行聚类，主要过程如算法\ref{alg:malicious-node-detection}的23-24行所示。聚类结果为多个簇\(C_1, C_2, \ldots, C_K\)，从所有簇中选出最大的一簇（即包含节点数量最多的簇），记作 \(C_{max}\)。基于良性节点在每轮训练中数量通常多于恶意节点的假设，以及良性节点与干净成分之间的KL散度通常更为相似，我们将 \(C_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)。对于其他所有簇\(C_i\)（\(i \neq {max}\)），其中的所有节点则被标记为恶意节点，记作\(U_{mal}\)。
 
-\item \textbf{Single-round Malicious Node Detection}
+% TODO 总结
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.4\textwidth]{img/t_sne_indicative_layer_round_0.png}
+    \hspace{0.1in}
+    \includegraphics[width=0.4\textwidth]{img/t_sne_dct_round_0.png}
+    \caption{Result}
+\end{figure}
 
-最后Single-round Malicious Node Detection的的主要过程如算法\ref{alg:malicious-node-detection}的28-29行所示。利用HDBSCAN对计算出来的KL散度集合$S$进行聚类，得到簇\(C_1, C_2, \ldots, C_K\)，从所有簇中选出最大的一簇（即包含节点数量最多的簇），记作 \(C_{max}\)。基于每轮参与训练的良性节点相较于恶意节点数量较多的假设，并且相较于恶意节点，所有良性节点与干净分量之间的KL散度具有更高的相似性，因此将 \(C_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)。对于除\(C_{max}\)外的所有其他簇\(C_i\)（\(i \neq {max}\)），将其中所有节点标记为恶意节点\(U_{mal}\)。
+% 放图
 
@@
 
-\textbf{Motivation}: 后门攻击
+\textbf{Motivation}: 为了规避异常检测，有很多通过多轮次的组合攻击来植入后门的攻击。本部分结合每个客户端的历史记录，通过识别攻击者最终的模型引导意图点来识别恶意节点。
 
-\textbf{Overview}: 前面的攻击中已经可以有效地针对单轮次攻击进行识别，本部分主要结合客户端的历史记录对客户端进行有效的识别。本部分将保留历史$T$轮次的全局模型$G_t$，并将其Flatten后视为高维空间中的一个点；同时保留每个客户端的历史梯度变化，将其视为高维空间中的一个向量，将其延伸后视为一个射线。对于每个客户端，使用最小覆盖球算法计算得到一个最小的超球，覆盖掉$\varepsilon$比例的射线。最终球心的位置可以被视为对应客户端对全局模型的意图引导点，球心的半径可以视为对应客户端的置信度。
+\textbf{Overview}: 前面的攻击中已经可以有效地针对单轮次攻击进行识别，本部分主要结合客户端的历史记录对客户端进行有效的识别。本部分将保留历史$T$轮次的全局模型$\theta_g^{t'}$，其中$t-T\leq t'< t$，并将其Flatten后视为高维空间中的一个点；同时保留每个客户端的历史更新变化，将其视为高维空间中的一个向量，将其延伸后视为一个射线。对于每个客户端，使用最小覆盖球算法计算得到一个最小的超球，覆盖$\varepsilon$比例的射线。最终球心的位置可以被视为对应客户端对全局模型的意图引导点，球心的半径可以视为对应客户端的置信度。
 
@@
 \begin{algorithmic}[1]
-\State \textbf{Input:} Global model history $\{G_{t-T}, G_{t-T+1}, \dots, G_{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{l_i}^{t-T}, \triangledown \theta_{l_i}^{t-T+1}, \dots, \triangledown \theta_{l_i}^{t-1}\}$, threshold $\varepsilon$
+\State \textbf{Input:} Global model history $\{G_{t-T}, G_{t-T+1}, \dots, G_{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \triangledown \theta_{i}^{t-T+1}, \dots, \triangledown \theta_{i}^{t-1}\}$, threshold $\varepsilon$
 \State \textbf{Output:} Set of clients marked as normal $U_{nor}$ and set of clients marked as malicious $U_{mal}$
 \State Step 1: Keep T-rounds History
-\For {Node $l_i$}
-    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_{l_i}^t)$
+\For {Node $i$}
+    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_{i}^t)$
     \State $DB.gradient\ \ +=\ \ \bar{\theta_i^t}$
@@
 \State Step 2: Construct Ray Model
-\For {Node $l_i$}
+\For {Node $i$}
     \State Construct rays using flattened global models and gradient updates:
-    \State $P_{l_i}^{t-j} = Flatten(G_{t-j-1})$, $\mathbf{d}_{l_i}^{t-j} = \bar{\theta}_{l_i}^{t-j}$ for $j = 0, 1, \ldots, T-1$
+    \State $P_{i}^{t-j} = Flatten(G_{t-j-1})$, $\mathbf{d}_{i}^{t-j} = \bar{\theta}_{i}^{t-j}$ for $j = 0, 1, \ldots, T-1$
 \EndFor
 \State Step 3: Minimum Enclosing Hypersphere Calculation
-\For {Node $l_i$}
+\For {Node $i$}
     \State Initialize center $O_0$ and radius $r_0$
     \While {Not Converged}
-        \State Calculate projection points $Q_{l_i}^{t-j}$ and sort by distance to $O_k$
-        \State Compute $D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{l_i}^{t-j}\|$
-        \State Update $O_{k+1} = O_k + \alpha \left(\frac{1}{\lceil n\times \varepsilon\rceil} \sum_{1\leq j\leq \lceil n\times \varepsilon\rceil} (Q_{l_i}^{t-j} - O_k)\right)$
+        \State Calculate projection points $Q_{i}^{t-j}$ and sort by distance to $O_k$
+        \State Compute $D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{i}^{t-j}\|$
+        \State Update $O_{k+1} = O_k + \alpha \left(\frac{1}{\lceil n\times \varepsilon\rceil} \sum_{1\leq j\leq \lceil n\times \varepsilon\rceil} (Q_{i}^{t-j} - O_k)\right)$
         \State Update $r_{k+1} = D_k$
@@
 \State Step 4: Abnormal Detection
-\For {Node $l_i$}
+\For {Node $i$}
     \State Calculate adjusted LOF: $\text{adjusted\_lof}(x_i) = \text{LOF}(x_i) \times (r_i + \epsilon)$
@@
 
-“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将梯度变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$G_t$，将客户端$l_i$第$t$轮次训练后的模型记为$\theta^t_{l_i}$。客户端$l_i$将训练后的模型$\theta^t_{l_i}$减去训练前中央服务器下发的全局模型$G_t$，就得到了$t$轮次的梯度变化$\triangledown \theta^t_{l_i}=\theta^t_{l_i}-G_{t-1}$。客户端将梯度变化$\triangledown \theta^t_{l_i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的梯度变化$\triangledown \theta^t_{l_i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上次下发的全局模型$G_{t-1}$。中央服务器最多保留$T$轮次的模型和梯度历史记录。此部分可以参考算法\ref{alg:malicious-node-detection-history}的step1。
+“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$G_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_g$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$G_t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-G_{t-1}$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上伦次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。此部分可以参考算法\ref{alg:malicious-node-detection-history}的step1。
 
@@
 
-“Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表$t-1$轮次的全局模型，射线的方向代表$t$轮次展平后的梯度变化。问题的优化目标是：找到一个最小的超球，包含至少$\varepsilon$比例的射线。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
+“Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上伦次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
 
-“Construct Ray Model”的主要过程如下。对于每个客户端 \(l_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的梯度更新历史。
+“Construct Ray Model”的主要过程如下。对于每个客户端 \(R_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的更新变化历史。
 
 \begin{itemize}
-    \item 设 \( G_{t-T}, G_{t-T+1}, \dots, G_{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\theta_{l_i}^{t-T}}, \overline{\theta_{l_i}^{t-T+1}}, \dots, \overline{\theta_{l_i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(l_i\) 上传的展平后的梯度变化向量。
-    \item 对于每一轮 \( t-j \) (\( j = 0, 1, \dots, T-1 \))，我们将每个射线的起点表示为展平后的全局模型 \( G_{t-j-1} \)，并将每个射线的方向向量表示为展平后的梯度变化 \( \overline{\theta}_{l_i}^{t-j} \)。因此，射线模型可以构建如下：
+    \item 设 \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(i\) 上传的展平后的梯度变化向量。
+    \item 对于每一轮 \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \))，我们将每个射线的起点表示为展平后的全局模型 \( \theta_g^{t'} \)，并将每个射线的方向向量表示为展平后的梯度变化 \( \overline{\triangledown\theta_{i}^{t'}} \)。因此，射线模型可以构建如下：
 
     \begin{equation}
-    \overline{\theta_{l_i}^{t-j}} = Flatten(G_{t-j-1}),
+    \overline{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1}),
+    \end{equation}
+    \begin{equation}
+    {v}_{i}^{t'} = \overline{\triangledown\theta_{i}^{t'}},
     \end{equation}
 
-    \begin{equation}
-    \mathbf{d}_{l_i}^{t-j} = \bar{\theta}_{l_i}^{t-j},
-    \end{equation}
-
-    其中，\( \overline{\theta_{l_i}^{t-j}} \) 是射线的起点，\( \mathbf{d}_{l_i}^{t-j} \) 是射线的方向向量。
+    其中，\( \overline{\theta_{i}^{t'-1}} \) 是射线的起点，\( {v}_{i}^{t'} \) 是射线的方向向量。
 \end{itemize}
 
-“Minimum Enclosing Hypersphere Calculation”的主要过程如下。基于构建的射线模型，使用最小覆盖球算法找到一个能够覆盖至少 \( \varepsilon \) 比例的射线的最小超球。
+“Minimum Enclosing Hypersphere Calculation”的主要过程如下。基于构建的射线模型，使用最小覆盖球算法找到一个能够覆盖至少 \( \zeta \) 比例的射线的最小超球。
 
@@
     \begin{equation}
-    O_0 = \frac{1}{T} \sum_{j=0}^{T-1} \overline{\theta_{l_i}^{t-T+1}}.
+    O_0 = \frac{1}{T} \sum_{t'=\max\{t-T+1, 1\}}^{t} \overline{\theta_g^{t'-1}}.
     \end{equation}
@@
     \begin{equation}
-    r_0 = \max_{1\leq T} \|O_0 - \overline{\theta_{l_i}^{t-T+1}}\|.
+    r_0 = \max_{t'=\max\{t-T+1, 1\}}^{t}  \|O_0 - \overline{\theta_{g}^{t'}}\|.
     \end{equation}
@@
     \begin{itemize}
-       \item 对于每次迭代 \( k \)，计算当前球心 \( O_k \) 到所有射线的最近投影点 \( Q_{l_i}^{t-j} \)，按照距离当前球心的位置排序
+
+        \item TODO: O上标  投影点是什么
+
+       \item 对于每次迭代 \( k \)，计算当前球心 \( O_k \) 到所有射线的最近投影点 \( \bar{O}_{i}^{t'} \)，按照距离当前球心的位置从小到大排序
 
         \begin{equation}
-        \text{Sort}(\{ \| O - \overline{\theta_{l_i}^{t-T+1}} \| : i = 1, 2, \ldots, T \})
+        \text{Sort}(\{ \| O - \overline{\theta_{i}^{t-T+1}} \| : i = 1, 2, \ldots, T \})
         \end{equation}
@@
         \begin{equation}
-        D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{l_i}^{t-j}\|.
+        D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{i}^{t-j}\|.
         \end{equation}
@@
         \begin{equation}
-        O_{k+1} = O_k + \alpha \left(\frac{1}{\lceil n\times \varepsilon\rceil} \sum_{1\leq j\leq \lceil n\times \varepsilon\rceil} (Q_{l_i}^{t-j} - O_k)\right),
+        O_{k+1} = O_k + \alpha \left(\frac{1}{\lceil n\times \varepsilon\rceil} \sum_{1\leq j\leq \lceil n\times \varepsilon\rceil} (Q_{i}^{t-j} - O_k)\right),
         \end{equation}
@@
 $$
-\text{s.t.} \quad \| O - (\overline{\theta_{l_i}^{t-T+1}} + t_i \mathbf{d}_i) \|^2 \leq r^2, \, 1\leq i\leq \lceil n \times \varepsilon \rceil
+\text{s.t.} \quad \| O - (\overline{\theta_{i}^{t-T+1}} + t_i \mathbf{d}_i) \|^2 \leq r^2, \, 1\leq i\leq \lceil n \times \varepsilon \rceil
 $$
@@
 
-    这里，\(\varepsilon\text{-dist}(x_j)\) 表示点 \(x_j\) 到其第 \(\varepsilon\) 个最近邻的距离。
+    这里，\(\eta\varepsilon\text{-dist}(x_j)\) 表示点 \(x_j\) 到其第 \(\varepsilon\) 个最近邻的距离。
 
@@
 通过使用主观逻辑模型对客户端梯度进行聚合，能够有效利用信任度信息来优化全局模型的更新过程，减少因恶意客户端或不确定性导致的模型偏差。
-
 \end{enumerate}
@@
 
-本实验在一台配置高性能硬件的计算机上进行，操作系统为 Ubuntu 20.04.3 LTS，内核版本为 5.15.0-73-generic，以确保计算稳定性和结果的可靠性。计算机配置了 Intel(R) Core(TM) i9-10940X @ 3.30GHz 的处理器，具有28个核心，最大频率可达4.8GHz，能够提供强大的并行计算能力以高效处理大规模计算任务。内存为 128GB DDR4，速度为 2933 MT/s，这种大容量的内存配置有助于在处理复杂数据集和大规模模型训练时减少内存瓶颈，提升数据加载和处理速度。图形处理单元（GPU）方面，采用了2块 NVIDIA GeForce RTX 3090，每块显存为24GB，驱动版本为 470.239.06，CUDA 版本为 11.4。双GPU配置提供了强大的并行计算能力，可以显著加速深度学习模型的训练过程，特别是在图像处理和自然语言处理等需要大量计算的任务中表现尤为出色。存储设备为高速SSD，支持数据的高速读写操作，显著降低I/O操作时间，确保大数据集的快速加载和模型的高效训练。为了确保实验结果的可靠性和再现性，本实验使用了标准的数据集，包括MNIST数据集、CIFAR-10数据集等主流的数据集。上述硬件配置为实验提供了充足的计算资源，能够支持大规模深度学习模型的训练和复杂算法的测试。我们采用了一些先进的攻击方式，并使用我们的防御方式和State-Of-The-Art以及较为主流的防御方式进行对比，并针对“结合多轮次进行攻击”的攻击方式进行了实验，验证了我们的有效性。
+\subsubsection{硬件设施}
 
-\onecolumn
-\begin{longtable}{|p{3.5cm}|p{2cm}|p{10.5cm}|} 
-    \caption{Attack}
-    \label{table:attack} \\ \hline
-    Title & Conference & Main Content \\ \hline
-    \endfirsthead \hline
-    Title & Conference & Main Content \\ \hline 
-    \endhead \hline
-   Flip\cite{jha2023label} & Neurips(2023) &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
-   % \cite{yang2023data} & ICML(2023) & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
-   Chameleon\cite{dai2023chameleon} & ICML(2023) & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
-   Gradient Control\cite{gu2023gradient} & ACL(2023) & 这篇文章提出了一种新的梯度控制方法，旨在解决参数高效调优（PET）过程中后门攻击的遗忘问题。通过将后门注入过程视为多任务学习，文章引入了跨层梯度幅度归一化和层内梯度方向投影两种策略，以减少不同任务之间的梯度冲突和梯度大小的不平衡，从而增强后门攻击在用户微调模型后的效果。实验结果表明，该方法在情感分类和垃圾邮件检测任务中显著提高了后门攻击的持久性和有效性。 \\ \hline
-   A3FL\cite{zhang2024a3fl} & Neurips(2024) & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
-   Shadowcast\cite{xu2024shadowcast} & Arxiv(2024) & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
-   BadCLIP\cite{liang2024badclip} & CVPR(2024) & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
-   ImgTrojan\cite{tao2024imgtrojan} & arxiv(2024) & 文章主要讨论了一种名为“ImgTrojan”的攻击方法，该方法旨在通过在视觉语言模型（VLM）的训练数据中注入恶意的图像-文本对，从而突破模型的安全屏障。这种方法通过数据投毒的方式，将原本无害的图像与恶意的文本提示关联起来，使得经过投毒训练的模型在遇到这些图像时，可能生成有害的内容。这种攻击方式在实验中展示了极高的成功率，即使在训练数据中仅包含极少量的投毒样本。 \\ \hline
-   % \cite{attack01} & arXiv preprint & 2024 & 本篇文章次揭示了在联邦学习环境下对大语言模型（LLM）进行指令调优时存在的安全漏洞。文章提出了一种简洁但有效的安全攻击方法，恶意客户端通过使用未对齐的数据来训练本地模型，从而大幅度削弱了全球模型的安全对齐性（“未对齐的数据”，是指那些与预期的安全或伦理规范不一致的数据。例如，未对齐的数据可能包含有害的、误导性的或是不道德的信息，而这些信息在普通情况下不会被用于训练模型）。实验表明，该攻击方法能够将模型的安全性降低高达70\%，而现有的防御方法在应对此类攻击时几乎无效，仅能提高4\%的安全性。为了解决这一问题，作者进一步提出了一种新的事后防御方法，即通过服务器端生成对齐数据并进一步对全局模型进行微调，从而增强模型的安全性（中央服务器在接收到各个客户端的更新后，会主动生成一组对齐的数据。这些对齐的数据是预先定义好的，确保与预期的安全和伦理规范一致。这些数据可能包含严格筛选过的内容，如道德上中立或积极的文本片段）。实验结果显示，这种防御方法能够将模型的安全性提高最多69\%，且不显著降低模型的有效性。（这篇看完了发现不是视觉大模型） \\ \hline
-   % \cite{attack02} & arXiv preprint & 2024 & 本篇文章探讨了一种针对大语言模型（LLMs）的新型训练方法，称为目标潜在对抗性训练（Targeted Latent Adversarial Training, LAT），文章提出了通过在模型的潜在表示（latent representations）中引入针对性的扰动，来更有效地消除模型中顽固的不良行为（如后门攻击和模型“越狱”）。(潜在表示是指在神经网络的中间层中，数据通过多层非线性变换后所形成的特征表示。这些表示通常处于更高的抽象层次，与原始输入相比，能够捕捉到数据的深层次特征。在视觉大模型中，这些潜在表示可能包括图像的边缘、形状、纹理等更抽象的特征，而不再是具体的像素值。潜在表示在模型中扮演着至关重要的角色，因为它们是模型用来进行预测和决策的核心特征。)(针对性的扰动是指在训练或评估过程中，特意对模型的输入或潜在表示进行细微的修改或扰动，以诱导模型产生特定的（通常是不希望的）行为。通过这种方法，可以测试和增强模型在面对各种攻击时的鲁棒性。在本文中，作者使用潜在空间中的针对性扰动来模拟攻击，目的是强化模型的防御能力，使其能够抵抗类似的实际攻击，如后门攻击或越狱行为。)研究表明，与传统的对抗性训练相比，目标潜在对抗性训练可以显著提高模型抵抗这些攻击的能力，同时对模型的整体性能影响较小。文章通过实验验证了该方法在增强模型鲁棒性方面的有效性，尤其是在面对未知触发条件的后门攻击时，表现出色。  \\ \hline
-   % \cite{attack03} & arXiv preprint & 2024 & 本文探讨了开放权重大语言模型（LLMs）在面对篡改攻击时的脆弱性，并提出了一种名为TAR（Tampering Attack Resistance）的方法，旨在增强这些模型的抗篡改能力。文章指出，现有的安全防护措施，如拒绝机制和偏好训练，容易在少量微调步骤后被攻击者绕过，导致模型被恶意修改。为此，TAR方法通过对抗性训练和元学习，设计了一种新的防护机制，使得即使在经历数千步的微调攻击后，模型仍能保持其原有的安全防护功能。实验结果显示，与现有方法相比，TAR显著提高了模型的抗篡改能力，同时保留了模型的正常功能。研究还通过大量红队评估验证了TAR方法的有效性，展示了其在应对各种复杂攻击时的鲁棒性。(红队评估是一种在网络安全和机器学习领域常用的测试方法，它通过模拟攻击者的行为来评估系统或模型的安全性和防御能力。红队通常扮演“敌方”角色，主动寻找和利用系统的漏洞，以测试系统在真实攻击场景下的表现。这种方法帮助识别和修复安全漏洞，使系统在面对潜在的实际攻击时更加稳健。这篇文章中研究人员通过设计多个测试对手，这些对手模拟了各种可能的攻击策略，试图篡改或破坏大语言模型的功能。文章中提到进行了28个不同的红队评估测试，每个测试都旨在突破TAR的防护机制。)文章中的攻击方式涉及通过微调大语言模型的权重来篡改其行为。攻击者可以在模型的开放权重上进行少量微调，使其在特定情况下产生不希望的输出。例如，攻击者可能会在输入特定触发词时，让模型生成有害内容或偏离其正常功能。\\ \hline
-   % \cite{attack04} & arXiv preprint & 2024 & 这是一篇综述。本文主要介绍了以下攻击方式：\begin{itemize}
-   %  \item 对抗性攻击：通过对输入数据进行微小的扰动，这些扰动虽然对人类几乎不可见，但会导致模型产生显著错误的输出，例如在图像分类中，可能会使模型将一个正常的图像误分类为完全不同的类别；
-   %  \item 后门攻击：和之前咱做的一样；
-   %  \item 数据中毒攻击：攻击者向模型的训练数据中注入恶意样本，这些样本会导致模型在遇到类似数据时输出错误结果，例如在物体识别任务中，中毒数据可能会导致模型误将无害物体识别为威胁；
-   %  \item 模型逃逸：攻击者通过调整输入或模型参数，试图找到绕过模型防御机制的方法，使模型输出不受控制的内容，这种攻击常用于测试模型的防御效果；
-   %  \item 多模态攻击：针对处理多种类型输入（如文本和图像）的模型，攻击者通过操纵一种模态的输入来影响另一种模态的输出，例如在多模态对话系统中，通过改变图像输入可能会影响系统的文本回应；
-   %  \item 跨语言攻击：在多语言任务中，攻击者通过在一种语言中引入扰动来影响模型在另一种语言中的表现，这类攻击特别针对多语言翻译或生成模型，可能导致不同语言间的翻译不准确或失真。
-   %  \end{itemize}\\ \hline
-   % \cite{attack05} &  Advances in Neural Information Processing Systems 34 (NeurIPS 2021) & 2021 & 本篇文章讨了如何保护通过“彩票假设”（Lottery Ticket Hypothesis, LTH）找到的稀疏子网络（即“中奖票”）的所有权。文章提出了一种新的基于稀疏结构信息的验证方法，通过在网络的稀疏结构中嵌入签名来进行所有权验证。这种方法能够在白盒和黑盒场景下保护模型的知识产权，并且对细微调整（如微调和剪枝）具有很强的鲁棒性。研究还通过大量实验验证了该方法在多种模型（如ResNet-20、ResNet-18、ResNet-50）和数据集（如CIFAR-10和CIFAR-100）上的有效性，展示了其在应对移除攻击和模糊攻击时的坚韧性。具体攻击方式有：细微调整（Fine-tuning）攻击：对模型进行微调来改变模型的权重值，同时希望不改变网络的稀疏结构。这种攻击旨在通过调整权重，试图使嵌入的签名信息变得不可辨认或无效。然而，由于嵌入的信息是基于网络的稀疏结构（即被剪枝后的模型结构），细微调整难以改变这一基础结构，从而无法有效移除签名。剪枝（Pruning）攻击：攻击者尝试通过进一步剪枝来移除嵌入的签名信息。这种攻击的目的是通过减少模型的非零参数，使得嵌入的结构信息丢失。然而，文章中提出的嵌入方法确保了签名信息在极端稀疏的情况下仍能保留，即使剪枝比例达到一定程度，签名依然可以从稀疏结构中提取出来。模糊攻击（Ambiguity Attacks）：攻击者试图通过制造伪签名或模糊原有签名的信息来混淆所有权验证。这种攻击可能包括添加噪声、篡改稀疏结构等手段，旨在使得验证机制无法区分真实的所有权签名和伪造的信息。然而，文章中的验证方法通过设计稳健的结构嵌入机制，使得这种模糊攻击难以成功。(“签名”指的是嵌入到神经网络稀疏结构中的一种独特的标识信息。这种签名通过在模型的剪枝过程中，利用网络的稀疏性来实现。具体而言，当模型被剪枝后，一部分神经元和连接被移除，剩余的结构会呈现出一种特定的稀疏模式。作者通过在这种稀疏模式中嵌入一个特定的结构或模式，这个模式就是所谓的“签名”。这种签名是不可见的，但可以通过特定的验证过程来提取和识别。其主要功能是为网络的所有权提供证据，类似于给模型打上了一个“水印”。当有人试图非法复制或篡改模型时，这个嵌入的签名仍然可以被识别出来，从而验证模型的归属。签名的鲁棒性设计使其能够抵抗常见的攻击方式（如微调和进一步的剪枝），即使模型经历了这些操作，签名依然可以从其稀疏结构中被提取出来，证明模型的所有权。)(模型的所有权是指对一个机器学习模型（如神经网络模型）所拥有的法律和知识产权。所有权通常由开发者或公司拥有，表示他们对模型的设计、训练数据、训练方法以及最终生成的模型参数等有控制权和排他性使用权。这意味着只有模型的所有者有权利决定如何使用、修改、发布或授权使用该模型。（可能涉及到知识产权保护、商业机密的保密）)\\ \hline
-   % \cite{attack06} & Portail HAL theses(theses.hal.science) & 2022 & 这篇文章有185页。本篇文章讨论了如何通过数字水印技术来保护机器学习模型的知识产权，防止模型被盗用。文章首先提供了当前水印技术的概述，并进一步扩展了这些技术在图像分类任务之外的应用，涵盖了回归、机器翻译和强化学习模型。作者还提出了针对模型托管平台的伪造攻击（即试图通过伪造水印来绕过验证）并介绍了一种基于公平性的水印技术，以增强模型在黑盒环境中的安全性。实验结果表明，这些水印技术不仅可以有效防止模型盗用，还能够在面对各种攻击时保持鲁棒性。
-   % 数字水印是一种嵌入信息的技术，用于在数字内容（如图像、音频、视频或机器学习模型）中隐藏特定的信息，以表明所有权或版权。对于机器学习模型来说，数字水印是一种通过特定算法将标识信息嵌入到模型的权重、结构或输出中的技术。这种标识信息通常是不可见或难以察觉的，但可以通过特定的提取过程来验证。（数字水印的目的有：知识产权保护：开发者可以通过在模型中嵌入水印来证明模型的所有权，防止未经授权的复制和使用；盗版检测：如果一个模型被盗用或未经许可发布，水印可以作为证据，证明模型的来源和合法所有者；内容跟踪：水印可以帮助追踪模型的使用情况，尤其是在多个平台或用户之间共享时，确保模型的使用符合许可协议。） \\ \hline
-    % \endfoot
-    % \hline
-    % \endlastfoot
-    % \hline
-\end{longtable}
+本实验在一台Ubuntu操作系统的服务器上进行，28核心128GB内存，以及2块NVIDIA GeForce RTX 3090 GPU。
 
-\newpage
-\onecolumn
-\begin{longtable}{|p{3.5cm}|p{2cm}|p{10.5cm}|} 
-    \caption{Defense}
-    \label{table:defense} \\ \hline
-    Title & Conference & Main Content \\ \hline
-    \endfirsthead \hline
-    Title & Conference & Main Content \\ \hline 
-    \endhead \hline
-    SEER\cite{zhu2024seer} & AAAI 2024 & 这篇文章介绍了一种名为SEER的新型后门检测算法，专门用于检测视觉-语言模型中的后门攻击。研究的动机源于现有单模态模型（如图像分类模型）的后门检测方法无法直接应用于多模态模型（如视觉-语言模型）的复杂性和搜索空间的增加。为此，作者提出了一种新方法，通过在视觉和语言模态共享的特征空间中联合搜索图像触发器和恶意目标文本来检测后门。该方法的主要步骤包括：初始化目标文本和图像触发器的特征表示，设计优化算法在图像和文本空间中联合搜索可能的后门触发器和目标文本，并通过分析搜索结果来判断模型是否存在后门。实验结果表明，SEER在各种设置下能够以超过92\%的检测率成功识别视觉-语言模型中的后门，并且无需访问训练数据或了解下游任务。文章还比较了SEER与现有方法的效率，表明SEER在计算效率和检测效果方面均具有显著优势。\\ \hline
+\subsubsection{基本设置}
 
-    Semantic Shield\cite{ishmam2024semantic} & CVPR 2024 & 这篇文章提出了一种名为“Semantic Shield”的方法，旨在通过精细化知识对齐来防御视觉-语言模型中的后门和投毒攻击。研究的动机在于，随着大规模视觉-语言模型在实际应用中的广泛使用，这些模型变得容易受到攻击，如通过向训练数据中注入恶意数据来操纵模型行为。现有的防御方法通常无法有效应对这些攻击，尤其是在对比学习的多模态模型中。该方法通过引入外部知识来指导模型关注与外部知识对齐的视觉区域，从而避免模型学习到与攻击信号相关的错误关联。具体来说，研究人员使用大型语言模型（如Vicuna）从图像字幕中提取潜在的知识元素（KE），并通过对比学习的方式将这些KE与图像区域对齐。此外，模型的注意力机制也被调整，使其更加关注与KE高度对齐的图像区域，从而降低对受攻击区域的依赖。\\ \hline
+在本实验中，我们采用了常用的联邦学习场景进行评估。具体设置如下：
 
-    DECREE\cite{feng2023detecting} & CVPR 2023 & 主要关注自监督学习中预训练图像编码器的后门检测问题，鉴于现有方法在处理不同类型的后门攻击时表现不一致，且通常需要标签数据或下游分类器，本文提出了一种无需标签数据或下游分类器的新方法。DECREE 通过利用输入图像特征的扰动性和鲁棒性之间的差异来识别潜在的后门攻击，采用了一种基于自适应优化的策略，有效地将干净样本与后门样本分离。 \\ \hline
+\begin{itemize}
+    \item \textbf{数据集}：我们使用了MNIST和CIFAR-10数据集。MNIST数据集包含60,000张28x28像素的灰度手写数字图像，分为10个类别。CIFAR-10【TODO:引用】数据集包含60,000张32x32像素的彩色图像，分为10个类别。
 
-    ASSET\cite{pan2023asset} & USENIX 2023 & 这篇文章介绍了一种名为“ASSET”的方法，旨在跨多种深度学习范式中实现稳健的后门数据检测。研究动机是当前的后门检测方法在不同的深度学习设置（如自监督学习和迁移学习）中的表现差异很大，尤其在面对最新的干净标签后门攻击时，现有方法表现不佳。为了解决这一问题，作者提出了ASSET方法，它通过主动诱导后门样本和干净样本之间的模型行为差异来促进它们的分离。具体来说，ASSET采用了一个两步优化过程：首先在一个干净的基础数据集上最小化损失，然后在整个包含后门样本的训练集上最大化同样的损失，从而使后门样本和干净样本在损失值上出现显著差异，进而实现样本的分离和检测。\\ \hline
+    \item \textbf{模型}：在MNIST和CIFAR-10数据集上，我们使用了Vision Transformer (ViT) 模型，并使用LOAR进行微调。ViT 是一种基于 Transformer 架构的图像分类模型，它将图像划分为固定大小的patch，并将其输入到Transformer编码器中进行处理。
 
-    MCLDef\cite{yue2023model} & ACM MM 2023 & 这篇文章介绍了一种名为“基于模型对比学习的后门消除”（Model-Contrastive Learning for Backdoor Elimination，简称MCLDef）的新方法。研究的动机是当前的后门攻击对深度神经网络（DNNs）构成了显著威胁，而现有的后门防御方法在降低攻击成功率（ASR）的同时，往往会显著降低模型对干净数据的分类准确性（BA）。为了解决这一问题，作者提出了MCLDef方法，该方法通过模型对比学习来消除DNN中的后门，并最大限度地减少对BA的影响。具体来说，MCLDef通过定义正对和负对的特征对来进行对比学习：正对指的是干净数据样本与其中毒对应数据的特征表示，负对则是中毒数据样本在后门模型和纯化模型中的特征表示。通过对比学习，MCLDef能够缩小或消除中毒数据在特征空间中的聚类，并将中毒数据的特征拉向其干净对应样本的特征，从而有效地消除后门攻击带来的影响。 \\ \hline
+    \item \textbf{联邦相关机制（聚合算法）}：我们采用了经典的联邦平均（Federated Averaging, FedAvg）算法作为聚合机制。FedAvg算法通过聚合每个客户端在本地计算的模型更新，来生成全局模型。
 
-    DPoE\cite{liu2023shortcuts} & Arxiv 2023 & 这篇文章提出了一种名为DPoE（Denoised Product-of-Experts）的后门防御框架，旨在应对自然语言处理（NLP）模型中由多种不同触发器引发的后门攻击。研究的动机在于，现有的后门防御方法主要针对显式触发器，而难以有效应对隐式或多种触发器混合的复杂攻击。DPoE方法的核心思想是通过设计一个由两个模型组成的集成框架：一个浅层模型专门捕捉后门攻击中存在的“捷径”，即错误关联；另一个主模型则避免学习这些“捷径”。此外，DPoE引入了去噪设计来减轻由后门攻击者造成的标签翻转问题，从而进一步增强防御效果。 \\ \hline
+\end{itemize}
 
-    PSIM\cite{zhao2024defending} & arxiv 2024 & 这篇文章的主要内容是探讨参数高效微调（PEFT）方法在语言模型中的安全问题，特别是在模型的预训练阶段被植入后门的情况下。这种攻击被称为“权重中毒后门攻击”，发生在模型的预训练阶段，攻击者通过在训练数据中加入特定的触发器，并使用这些数据训练模型，从而在模型的权重中嵌入后门。当微调后的模型遇到这些触发器时，模型会按照攻击者的意图输出错误的结果。本文的主要目的是揭示PEFT方法在面对这种预训练阶段的权重中毒后门攻击时的脆弱性。研究表明，与全参数微调方法相比，PEFT更容易受到这种攻击，攻击成功率接近100\%。为了解决这一问题，作者提出了一种名为“中毒样本识别模块”（PSIM）的防御方法，通过预测置信度来识别和过滤可能被植入后门的样本，从而有效防御这些攻击，同时保持模型的分类准确性。 \\ \hline
+\subsubsection{参数取值表}
 
-    CleanCLIP\cite{bansal2023cleanclip} & ICCV 2023 & 这篇文章提出了一种名为CleanCLIP的方法，旨在减轻多模态对比学习模型（如CLIP）中数据投毒攻击的影响。研究动机是因为现有的多模态对比学习模型在训练过程中容易受到后门攻击的威胁，甚至少量的中毒样本就可以显著操控模型行为。CleanCLIP通过在模型预训练后进行微调来减弱这种攻击的影响。具体来说，该方法在微调过程中，通过同时应用多模态对比损失和自监督学习目标，使模型独立地学习每种模态（图像和文本）的表示，减少后门触发器与目标标签之间的错误关联。实验结果表明，CleanCLIP在不影响模型对干净样本性能的前提下，有效降低了多种后门攻击的成功率。此外，文章还讨论了不同的微调方法对清除后门触发器的效果，并发现CleanCLIP能够显著削弱这些攻击的影响。 \\ \hline
+\[
+\begin{array}{|c|c|c|}
+\hline
+\text{参数} & \text{MNIST} & \text{CIFAR-10} \\
+\hline
+\text{学习率} & 0.01 & 0.01 \\
+\text{全局轮次} & 50 & 50 \\
+\text{本地批次} & 5 & 5 \\
+\text{客户端数量} & 20 & 20 \\
+\text{批次大小} & 64 & 64 \\
+\text{优化器} & \text{SGD} & \text{SGD} \\
+\text{模型} & \text{ViT} & \text{ViT} \\
+\hline
+\end{array}
+\]
 
-    SEER\cite{defense01} & AAAI2024 & 这篇文章介绍了一种名为SEER的创新算法，用于检测视觉-语言模型（Vision-Language Models）中的backdoor攻击。backdoor攻击是一种攻击方式，攻击者可以在模型中植入“后门”，当特定触发条件满足时，模型会表现出异常行为。为了防御这种攻击，SEER算法通过联合搜索图像中的触发器（触发器是攻击者放入图像中的特殊标记或模式，用于激活模型中的后门）和与之关联的恶意目标文本来检测是否存在backdoor。SEER算法的具体防御步骤如下：首先，SEER算法会初始化一个特定的文本表示，该表示是基于一个词典中的所有文本的平均特征。这一步的目的是为后续的搜索过程提供一个合理的起点。接下来，SEER通过优化算法在共享的特征空间中搜索图像中的潜在触发器和与之相关联的目标文本。这里的特征空间是指模型用来同时表示图像和文本的多维空间。SEER的目标是找到一种图像模式（即触发器）和一个目标文本，这两者在特征空间中具有非常高的相似性（这意味着触发器和目标文本之间存在很强的关联）。在搜索过程中，SEER会根据相似性计算结果来识别可能的backdoor。如果发现模型中存在一个图像触发器与某个目标文本之间的强关联，SEER就会标记该模型为可能存在backdoor。图像触发器：这是攻击者嵌入在图像中的特定模式或标记，当模型看到带有这个标记的图像时，会触发backdoor行为。比如在一张图片的角落放置一个特定的形状或颜色。强关联：在特征空间中，两个对象（如图像和文本）之间的高相似性意味着它们在这个空间中的表示非常接近，这种情况称为强关联。对于backdoor检测来说，如果一个图像触发器和目标文本之间的相似性过高，就意味着模型可能已经被攻击。通过这些步骤，SEER算法能够有效地检测出是否存在backdoor攻击，尤其是在模型训练数据和具体下游任务未知的情况下。这种方法不仅提高了检测的效率，而且在各种攻击场景下，SEER的检测准确率超过了92\%，表现出极高的可靠性和适应性。 \\ \hline
-    Revisiting Backdoor Attacks against Large Vision-Language Models\cite{defense02} & Arxiv(2024) & 这篇文章研究了视觉-语言大模型（LVLMs）在指令调优阶段面临的backdoor攻击的普遍性，特别是在训练和测试数据分布不一致的实际场景中。文章通过实验证明，大多数现有的backdoor攻击方法在这种跨域场景下的泛化性较差，但通过对攻击触发器的优化，文章展示了一种能够显著提高攻击成功率的新方法。具体防御步骤如下：1.
+% \subsubsection{攻防相关}
+
+% \onecolumn
+% \begin{longtable}{|p{3.5cm}|p{2cm}|p{10.5cm}|} 
+%     \caption{Attack}
+%     \label{table:attack} \\ \hline
+%     Title & Conference & Main Content \\ \hline
+%     \endfirsthead \hline
+%     Title & Conference & Main Content \\ \hline 
+%     \endhead \hline
+%    Flip\cite{jha2023label} & Neurips(2023) &  本文提出了一种新颖的标签投毒攻击方法，称为FLIP。与传统的后门攻击不同，FLIP仅通过修改训练数据的标签即可实现对模型的控制，而无需更改图像本身。这种方法特别适用于当训练标签可能来自潜在恶意的第三方（如众包标注或知识蒸馏）的场景。本文通过实验展示了FLIP在多个数据集和模型架构上的高效性，证明了在仅污染少量标签的情况下，FLIP能够显著影响模型的预测结果。 \\ \hline
+%    % \cite{yang2023data} & ICML(2023) & 本文首次研究了针对多模态模型的投毒攻击，包括视觉和语言两种模态。研究的主要问题是：（1）语言模态是否也容易受到投毒攻击？（2）哪种模态更易受攻击？本文提出了三种针对多模态模型的投毒攻击，并通过在不同数据集和模型架构上的广泛评估，表明这些攻击可以在保持模型实用性的同时实现显著的攻击效果。为缓解这些攻击，本文还提出了预训练和后训练的防御措施，并证明这些防御措施能够显著降低攻击效果，同时保持模型的效用。\\ \hline
+%    Chameleon\cite{dai2023chameleon} & ICML(2023) & 这篇文章的主要贡献在于提出了Chameleon攻击方法，这是一种通过利用正常图像与被污染图像之间的关系，来增强后门在联邦学习（FL）系统中持久性的策略。通过对比学习调整图像嵌入距离，Chameleon成功延长了后门的存续时间，使其在多种数据集、后门类型和模型架构下的耐久性提高了1.2至4倍，显著优于现有方法。 \\ \hline
+%    Gradient Control\cite{gu2023gradient} & ACL(2023) & 这篇文章提出了一种新的梯度控制方法，旨在解决参数高效调优（PET）过程中后门攻击的遗忘问题。通过将后门注入过程视为多任务学习，文章引入了跨层梯度幅度归一化和层内梯度方向投影两种策略，以减少不同任务之间的梯度冲突和梯度大小的不平衡，从而增强后门攻击在用户微调模型后的效果。实验结果表明，该方法在情感分类和垃圾邮件检测任务中显著提高了后门攻击的持久性和有效性。 \\ \hline
+%    A3FL\cite{zhang2024a3fl} & Neurips(2024) & 这篇文章的主要贡献是提出了一种新的后门攻击方法A3FL，它通过对抗性自适应策略优化后门触发器，使其在联邦学习的全局训练动态中更持久、更难被检测到。与现有方法相比，A3FL显著提高了攻击的成功率和隐蔽性，并在多种防御机制下展现了出色的效果，揭示了现有防御方法的不足，强调了开发新防御策略的必要性。\\ \hline
+%    Shadowcast\cite{xu2024shadowcast} & Arxiv(2024) & 这篇文章主要介绍了一种针对视觉语言模型（VLMs）的隐蔽数据投毒攻击方法，称为Shadowcast。该方法通过向模型的训练数据中注入视觉上与正常图像几乎无法区分的投毒样本，从而误导模型在推理时生成错误或误导性的信息。文章探讨了两种攻击类型：标签攻击（Label Attack）和说服攻击（Persuasion Attack），前者旨在让模型错误识别图像类别，而后者通过生成具有说服力但错误的文本，改变用户对图像的认知。实验结果表明，Shadowcast攻击在多种VLM架构下都非常有效，且在不同的提示词和数据增强条件下依然保持攻击效果。\\ \hline
+%    BadCLIP\cite{liang2024badclip} & CVPR(2024) & 这篇文章提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，称为BadCLIP。BadCLIP通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。此外，该方法通过对抗性训练，增强了中毒样本的视觉特征，使得后门在模型经过清洁数据微调后仍能保持有效。实验结果显示，BadCLIP在多种防御机制下都表现出显著的攻击成功率，展示了其对现有防御方法的强大威胁。\\ \hline
+%    ImgTrojan\cite{tao2024imgtrojan} & arxiv(2024) & 文章主要讨论了一种名为“ImgTrojan”的攻击方法，该方法旨在通过在视觉语言模型（VLM）的训练数据中注入恶意的图像-文本对，从而突破模型的安全屏障。这种方法通过数据投毒的方式，将原本无害的图像与恶意的文本提示关联起来，使得经过投毒训练的模型在遇到这些图像时，可能生成有害的内容。这种攻击方式在实验中展示了极高的成功率，即使在训练数据中仅包含极少量的投毒样本。 \\ \hline
+%    % \cite{attack01} & arXiv preprint & 2024 & 本篇文章次揭示了在联邦学习环境下对大语言模型（LLM）进行指令调优时存在的安全漏洞。文章提出了一种简洁但有效的安全攻击方法，恶意客户端通过使用未对齐的数据来训练本地模型，从而大幅度削弱了全球模型的安全对齐性（“未对齐的数据”，是指那些与预期的安全或伦理规范不一致的数据。例如，未对齐的数据可能包含有害的、误导性的或是不道德的信息，而这些信息在普通情况下不会被用于训练模型）。实验表明，该攻击方法能够将模型的安全性降低高达70\%，而现有的防御方法在应对此类攻击时几乎无效，仅能提高4\%的安全性。为了解决这一问题，作者进一步提出了一种新的事后防御方法，即通过服务器端生成对齐数据并进一步对全局模型进行微调，从而增强模型的安全性（中央服务器在接收到各个客户端的更新后，会主动生成一组对齐的数据。这些对齐的数据是预先定义好的，确保与预期的安全和伦理规范一致。这些数据可能包含严格筛选过的内容，如道德上中立或积极的文本片段）。实验结果显示，这种防御方法能够将模型的安全性提高最多69\%，且不显著降低模型的有效性。（这篇看完了发现不是视觉大模型） \\ \hline
+%    % \cite{attack02} & arXiv preprint & 2024 & 本篇文章探讨了一种针对大语言模型（LLMs）的新型训练方法，称为目标潜在对抗性训练（Targeted Latent Adversarial Training, LAT），文章提出了通过在模型的潜在表示（latent representations）中引入针对性的扰动，来更有效地消除模型中顽固的不良行为（如后门攻击和模型“越狱”）。(潜在表示是指在神经网络的中间层中，数据通过多层非线性变换后所形成的特征表示。这些表示通常处于更高的抽象层次，与原始输入相比，能够捕捉到数据的深层次特征。在视觉大模型中，这些潜在表示可能包括图像的边缘、形状、纹理等更抽象的特征，而不再是具体的像素值。潜在表示在模型中扮演着至关重要的角色，因为它们是模型用来进行预测和决策的核心特征。)(针对性的扰动是指在训练或评估过程中，特意对模型的输入或潜在表示进行细微的修改或扰动，以诱导模型产生特定的（通常是不希望的）行为。通过这种方法，可以测试和增强模型在面对各种攻击时的鲁棒性。在本文中，作者使用潜在空间中的针对性扰动来模拟攻击，目的是强化模型的防御能力，使其能够抵抗类似的实际攻击，如后门攻击或越狱行为。)研究表明，与传统的对抗性训练相比，目标潜在对抗性训练可以显著提高模型抵抗这些攻击的能力，同时对模型的整体性能影响较小。文章通过实验验证了该方法在增强模型鲁棒性方面的有效性，尤其是在面对未知触发条件的后门攻击时，表现出色。  \\ \hline
+%    % \cite{attack03} & arXiv preprint & 2024 & 本文探讨了开放权重大语言模型（LLMs）在面对篡改攻击时的脆弱性，并提出了一种名为TAR（Tampering Attack Resistance）的方法，旨在增强这些模型的抗篡改能力。文章指出，现有的安全防护措施，如拒绝机制和偏好训练，容易在少量微调步骤后被攻击者绕过，导致模型被恶意修改。为此，TAR方法通过对抗性训练和元学习，设计了一种新的防护机制，使得即使在经历数千步的微调攻击后，模型仍能保持其原有的安全防护功能。实验结果显示，与现有方法相比，TAR显著提高了模型的抗篡改能力，同时保留了模型的正常功能。研究还通过大量红队评估验证了TAR方法的有效性，展示了其在应对各种复杂攻击时的鲁棒性。(红队评估是一种在网络安全和机器学习领域常用的测试方法，它通过模拟攻击者的行为来评估系统或模型的安全性和防御能力。红队通常扮演“敌方”角色，主动寻找和利用系统的漏洞，以测试系统在真实攻击场景下的表现。这种方法帮助识别和修复安全漏洞，使系统在面对潜在的实际攻击时更加稳健。这篇文章中研究人员通过设计多个测试对手，这些对手模拟了各种可能的攻击策略，试图篡改或破坏大语言模型的功能。文章中提到进行了28个不同的红队评估测试，每个测试都旨在突破TAR的防护机制。)文章中的攻击方式涉及通过微调大语言模型的权重来篡改其行为。攻击者可以在模型的开放权重上进行少量微调，使其在特定情况下产生不希望的输出。例如，攻击者可能会在输入特定触发词时，让模型生成有害内容或偏离其正常功能。\\ \hline
+%    % \cite{attack04} & arXiv preprint & 2024 & 这是一篇综述。本文主要介绍了以下攻击方式：\begin{itemize}
+%    %  \item 对抗性攻击：通过对输入数据进行微小的扰动，这些扰动虽然对人类几乎不可见，但会导致模型产生显著错误的输出，例如在图像分类中，可能会使模型将一个正常的图像误分类为完全不同的类别；
+%    %  \item 后门攻击：和之前咱做的一样；
+%    %  \item 数据中毒攻击：攻击者向模型的训练数据中注入恶意样本，这些样本会导致模型在遇到类似数据时输出错误结果，例如在物体识别任务中，中毒数据可能会导致模型误将无害物体识别为威胁；
+%    %  \item 模型逃逸：攻击者通过调整输入或模型参数，试图找到绕过模型防御机制的方法，使模型输出不受控制的内容，这种攻击常用于测试模型的防御效果；
+%    %  \item 多模态攻击：针对处理多种类型输入（如文本和图像）的模型，攻击者通过操纵一种模态的输入来影响另一种模态的输出，例如在多模态对话系统中，通过改变图像输入可能会影响系统的文本回应；
+%    %  \item 跨语言攻击：在多语言任务中，攻击者通过在一种语言中引入扰动来影响模型在另一种语言中的表现，这类攻击特别针对多语言翻译或生成模型，可能导致不同语言间的翻译不准确或失真。
+%    %  \end{itemize}\\ \hline
+%    % \cite{attack05} &  Advances in Neural Information Processing Systems 34 (NeurIPS 2021) & 2021 & 本篇文章讨了如何保护通过“彩票假设”（Lottery Ticket Hypothesis, LTH）找到的稀疏子网络（即“中奖票”）的所有权。文章提出了一种新的基于稀疏结构信息的验证方法，通过在网络的稀疏结构中嵌入签名来进行所有权验证。这种方法能够在白盒和黑盒场景下保护模型的知识产权，并且对细微调整（如微调和剪枝）具有很强的鲁棒性。研究还通过大量实验验证了该方法在多种模型（如ResNet-20、ResNet-18、ResNet-50）和数据集（如CIFAR-10和CIFAR-100）上的有效性，展示了其在应对移除攻击和模糊攻击时的坚韧性。具体攻击方式有：细微调整（Fine-tuning）攻击：对模型进行微调来改变模型的权重值，同时希望不改变网络的稀疏结构。这种攻击旨在通过调整权重，试图使嵌入的签名信息变得不可辨认或无效。然而，由于嵌入的信息是基于网络的稀疏结构（即被剪枝后的模型结构），细微调整难以改变这一基础结构，从而无法有效移除签名。剪枝（Pruning）攻击：攻击者尝试通过进一步剪枝来移除嵌入的签名信息。这种攻击的目的是通过减少模型的非零参数，使得嵌入的结构信息丢失。然而，文章中提出的嵌入方法确保了签名信息在极端稀疏的情况下仍能保留，即使剪枝比例达到一定程度，签名依然可以从稀疏结构中提取出来。模糊攻击（Ambiguity Attacks）：攻击者试图通过制造伪签名或模糊原有签名的信息来混淆所有权验证。这种攻击可能包括添加噪声、篡改稀疏结构等手段，旨在使得验证机制无法区分真实的所有权签名和伪造的信息。然而，文章中的验证方法通过设计稳健的结构嵌入机制，使得这种模糊攻击难以成功。(“签名”指的是嵌入到神经网络稀疏结构中的一种独特的标识信息。这种签名通过在模型的剪枝过程中，利用网络的稀疏性来实现。具体而言，当模型被剪枝后，一部分神经元和连接被移除，剩余的结构会呈现出一种特定的稀疏模式。作者通过在这种稀疏模式中嵌入一个特定的结构或模式，这个模式就是所谓的“签名”。这种签名是不可见的，但可以通过特定的验证过程来提取和识别。其主要功能是为网络的所有权提供证据，类似于给模型打上了一个“水印”。当有人试图非法复制或篡改模型时，这个嵌入的签名仍然可以被识别出来，从而验证模型的归属。签名的鲁棒性设计使其能够抵抗常见的攻击方式（如微调和进一步的剪枝），即使模型经历了这些操作，签名依然可以从其稀疏结构中被提取出来，证明模型的所有权。)(模型的所有权是指对一个机器学习模型（如神经网络模型）所拥有的法律和知识产权。所有权通常由开发者或公司拥有，表示他们对模型的设计、训练数据、训练方法以及最终生成的模型参数等有控制权和排他性使用权。这意味着只有模型的所有者有权利决定如何使用、修改、发布或授权使用该模型。（可能涉及到知识产权保护、商业机密的保密）)\\ \hline
+%    % \cite{attack06} & Portail HAL theses(theses.hal.science) & 2022 & 这篇文章有185页。本篇文章讨论了如何通过数字水印技术来保护机器学习模型的知识产权，防止模型被盗用。文章首先提供了当前水印技术的概述，并进一步扩展了这些技术在图像分类任务之外的应用，涵盖了回归、机器翻译和强化学习模型。作者还提出了针对模型托管平台的伪造攻击（即试图通过伪造水印来绕过验证）并介绍了一种基于公平性的水印技术，以增强模型在黑盒环境中的安全性。实验结果表明，这些水印技术不仅可以有效防止模型盗用，还能够在面对各种攻击时保持鲁棒性。
+%    % 数字水印是一种嵌入信息的技术，用于在数字内容（如图像、音频、视频或机器学习模型）中隐藏特定的信息，以表明所有权或版权。对于机器学习模型来说，数字水印是一种通过特定算法将标识信息嵌入到模型的权重、结构或输出中的技术。这种标识信息通常是不可见或难以察觉的，但可以通过特定的提取过程来验证。（数字水印的目的有：知识产权保护：开发者可以通过在模型中嵌入水印来证明模型的所有权，防止未经授权的复制和使用；盗版检测：如果一个模型被盗用或未经许可发布，水印可以作为证据，证明模型的来源和合法所有者；内容跟踪：水印可以帮助追踪模型的使用情况，尤其是在多个平台或用户之间共享时，确保模型的使用符合许可协议。） \\ \hline
+%     % \endfoot
+%     % \hline
+%     % \endlastfoot
+%     % \hline
+% \end{longtable}
+
+% \newpage
+% \onecolumn
+% \begin{longtable}{|p{3.5cm}|p{2cm}|p{10.5cm}|} 
+%     \caption{Defense}
+%     \label{table:defense} \\ \hline
+%     Title & Conference & Main Content \\ \hline
+%     \endfirsthead \hline
+%     Title & Conference & Main Content \\ \hline 
+%     \endhead \hline
+%     SEER\cite{zhu2024seer} & AAAI 2024 & 这篇文章介绍了一种名为SEER的新型后门检测算法，专门用于检测视觉-语言模型中的后门攻击。研究的动机源于现有单模态模型（如图像分类模型）的后门检测方法无法直接应用于多模态模型（如视觉-语言模型）的复杂性和搜索空间的增加。为此，作者提出了一种新方法，通过在视觉和语言模态共享的特征空间中联合搜索图像触发器和恶意目标文本来检测后门。该方法的主要步骤包括：初始化目标文本和图像触发器的特征表示，设计优化算法在图像和文本空间中联合搜索可能的后门触发器和目标文本，并通过分析搜索结果来判断模型是否存在后门。实验结果表明，SEER在各种设置下能够以超过92\%的检测率成功识别视觉-语言模型中的后门，并且无需访问训练数据或了解下游任务。文章还比较了SEER与现有方法的效率，表明SEER在计算效率和检测效果方面均具有显著优势。\\ \hline
+
+%     Semantic Shield\cite{ishmam2024semantic} & CVPR 2024 & 这篇文章提出了一种名为“Semantic Shield”的方法，旨在通过精细化知识对齐来防御视觉-语言模型中的后门和投毒攻击。研究的动机在于，随着大规模视觉-语言模型在实际应用中的广泛使用，这些模型变得容易受到攻击，如通过向训练数据中注入恶意数据来操纵模型行为。现有的防御方法通常无法有效应对这些攻击，尤其是在对比学习的多模态模型中。该方法通过引入外部知识来指导模型关注与外部知识对齐的视觉区域，从而避免模型学习到与攻击信号相关的错误关联。具体来说，研究人员使用大型语言模型（如Vicuna）从图像字幕中提取潜在的知识元素（KE），并通过对比学习的方式将这些KE与图像区域对齐。此外，模型的注意力机制也被调整，使其更加关注与KE高度对齐的图像区域，从而降低对受攻击区域的依赖。\\ \hline
+
+%     DECREE\cite{feng2023detecting} & CVPR 2023 & 主要关注自监督学习中预训练图像编码器的后门检测问题，鉴于现有方法在处理不同类型的后门攻击时表现不一致，且通常需要标签数据或下游分类器，本文提出了一种无需标签数据或下游分类器的新方法。DECREE 通过利用输入图像特征的扰动性和鲁棒性之间的差异来识别潜在的后门攻击，采用了一种基于自适应优化的策略，有效地将干净样本与后门样本分离。 \\ \hline
+
+%     ASSET\cite{pan2023asset} & USENIX 2023 & 这篇文章介绍了一种名为“ASSET”的方法，旨在跨多种深度学习范式中实现稳健的后门数据检测。研究动机是当前的后门检测方法在不同的深度学习设置（如自监督学习和迁移学习）中的表现差异很大，尤其在面对最新的干净标签后门攻击时，现有方法表现不佳。为了解决这一问题，作者提出了ASSET方法，它通过主动诱导后门样本和干净样本之间的模型行为差异来促进它们的分离。具体来说，ASSET采用了一个两步优化过程：首先在一个干净的基础数据集上最小化损失，然后在整个包含后门样本的训练集上最大化同样的损失，从而使后门样本和干净样本在损失值上出现显著差异，进而实现样本的分离和检测。\\ \hline
+
+%     MCLDef\cite{yue2023model} & ACM MM 2023 & 这篇文章介绍了一种名为“基于模型对比学习的后门消除”（Model-Contrastive Learning for Backdoor Elimination，简称MCLDef）的新方法。研究的动机是当前的后门攻击对深度神经网络（DNNs）构成了显著威胁，而现有的后门防御方法在降低攻击成功率（ASR）的同时，往往会显著降低模型对干净数据的分类准确性（BA）。为了解决这一问题，作者提出了MCLDef方法，该方法通过模型对比学习来消除DNN中的后门，并最大限度地减少对BA的影响。具体来说，MCLDef通过定义正对和负对的特征对来进行对比学习：正对指的是干净数据样本与其中毒对应数据的特征表示，负对则是中毒数据样本在后门模型和纯化模型中的特征表示。通过对比学习，MCLDef能够缩小或消除中毒数据在特征空间中的聚类，并将中毒数据的特征拉向其干净对应样本的特征，从而有效地消除后门攻击带来的影响。 \\ \hline
+
+%     DPoE\cite{liu2023shortcuts} & Arxiv 2023 & 这篇文章提出了一种名为DPoE（Denoised Product-of-Experts）的后门防御框架，旨在应对自然语言处理（NLP）模型中由多种不同触发器引发的后门攻击。研究的动机在于，现有的后门防御方法主要针对显式触发器，而难以有效应对隐式或多种触发器混合的复杂攻击。DPoE方法的核心思想是通过设计一个由两个模型组成的集成框架：一个浅层模型专门捕捉后门攻击中存在的“捷径”，即错误关联；另一个主模型则避免学习这些“捷径”。此外，DPoE引入了去噪设计来减轻由后门攻击者造成的标签翻转问题，从而进一步增强防御效果。 \\ \hline
+
+%     PSIM\cite{zhao2024defending} & arxiv 2024 & 这篇文章的主要内容是探讨参数高效微调（PEFT）方法在语言模型中的安全问题，特别是在模型的预训练阶段被植入后门的情况下。这种攻击被称为“权重中毒后门攻击”，发生在模型的预训练阶段，攻击者通过在训练数据中加入特定的触发器，并使用这些数据训练模型，从而在模型的权重中嵌入后门。当微调后的模型遇到这些触发器时，模型会按照攻击者的意图输出错误的结果。本文的主要目的是揭示PEFT方法在面对这种预训练阶段的权重中毒后门攻击时的脆弱性。研究表明，与全参数微调方法相比，PEFT更容易受到这种攻击，攻击成功率接近100\%。为了解决这一问题，作者提出了一种名为“中毒样本识别模块”（PSIM）的防御方法，通过预测置信度来识别和过滤可能被植入后门的样本，从而有效防御这些攻击，同时保持模型的分类准确性。 \\ \hline
+
+%     CleanCLIP\cite{bansal2023cleanclip} & ICCV 2023 & 这篇文章提出了一种名为CleanCLIP的方法，旨在减轻多模态对比学习模型（如CLIP）中数据投毒攻击的影响。研究动机是因为现有的多模态对比学习模型在训练过程中容易受到后门攻击的威胁，甚至少量的中毒样本就可以显著操控模型行为。CleanCLIP通过在模型预训练后进行微调来减弱这种攻击的影响。具体来说，该方法在微调过程中，通过同时应用多模态对比损失和自监督学习目标，使模型独立地学习每种模态（图像和文本）的表示，减少后门触发器与目标标签之间的错误关联。实验结果表明，CleanCLIP在不影响模型对干净样本性能的前提下，有效降低了多种后门攻击的成功率。此外，文章还讨论了不同的微调方法对清除后门触发器的效果，并发现CleanCLIP能够显著削弱这些攻击的影响。 \\ \hline
+
+%     SEER\cite{defense01} & AAAI2024 & 这篇文章介绍了一种名为SEER的创新算法，用于检测视觉-语言模型（Vision-Language Models）中的backdoor攻击。backdoor攻击是一种攻击方式，攻击者可以在模型中植入“后门”，当特定触发条件满足时，模型会表现出异常行为。为了防御这种攻击，SEER算法通过联合搜索图像中的触发器（触发器是攻击者放入图像中的特殊标记或模式，用于激活模型中的后门）和与之关联的恶意目标文本来检测是否存在backdoor。SEER算法的具体防御步骤如下：首先，SEER算法会初始化一个特定的文本表示，该表示是基于一个词典中的所有文本的平均特征。这一步的目的是为后续的搜索过程提供一个合理的起点。接下来，SEER通过优化算法在共享的特征空间中搜索图像中的潜在触发器和与之相关联的目标文本。这里的特征空间是指模型用来同时表示图像和文本的多维空间。SEER的目标是找到一种图像模式（即触发器）和一个目标文本，这两者在特征空间中具有非常高的相似性（这意味着触发器和目标文本之间存在很强的关联）。在搜索过程中，SEER会根据相似性计算结果来识别可能的backdoor。如果发现模型中存在一个图像触发器与某个目标文本之间的强关联，SEER就会标记该模型为可能存在backdoor。图像触发器：这是攻击者嵌入在图像中的特定模式或标记，当模型看到带有这个标记的图像时，会触发backdoor行为。比如在一张图片的角落放置一个特定的形状或颜色。强关联：在特征空间中，两个对象（如图像和文本）之间的高相似性意味着它们在这个空间中的表示非常接近，这种情况称为强关联。对于backdoor检测来说，如果一个图像触发器和目标文本之间的相似性过高，就意味着模型可能已经被攻击。通过这些步骤，SEER算法能够有效地检测出是否存在backdoor攻击，尤其是在模型训练数据和具体下游任务未知的情况下。这种方法不仅提高了检测的效率，而且在各种攻击场景下，SEER的检测准确率超过了92\%，表现出极高的可靠性和适应性。 \\ \hline
+%     Revisiting Backdoor Attacks against Large Vision-Language Models\cite{defense02} & Arxiv(2024) & 这篇文章研究了视觉-语言大模型（LVLMs）在指令调优阶段面临的backdoor攻击的普遍性，特别是在训练和测试数据分布不一致的实际场景中。文章通过实验证明，大多数现有的backdoor攻击方法在这种跨域场景下的泛化性较差，但通过对攻击触发器的优化，文章展示了一种能够显著提高攻击成功率的新方法。具体防御步骤如下：1.
 攻击触发器设计：文章首先分析了现有backdoor攻击的触发器模式，发现其与具体图像或模型无关的触发器往往具有更好的泛化能力。因此，作者设计了一种新的触发器模式，使其能够在不同的图像和文本域偏移的情况下，依然有效地触发backdoor攻击。2.
@@
 实验验证：通过在多个标准图像描述数据集上的实验，文章验证了不同类型backdoor攻击在跨域场景中的表现。结果表明，尽管图像域的变化通常会削弱大多数攻击的泛化性，但经过优化的触发器模式，如本文提出的新方法，能够显著提高攻击成功率，在某些场景下成功率甚至达到97\%以上。触发器：这是在模型训练过程中故意植入的特定模式，当模型在推理阶段遇到这种模式时，会表现出预设的异常行为。简单来说，触发器就像是一个隐藏在图像或文本中的“密码”，当模型看到这个“密码”时，它就会按照攻击者的预期做出反应。泛化能力：泛化能力指的是一个攻击方法在面对与训练时不同的数据分布时，仍能保持其攻击效果的能力。对于backdoor攻击来说，泛化能力越强，攻击就越难以被发现和防御。通过这些步骤，文章展示了在视觉-语言模型中，如何通过设计更具适应性的触发器，增强backdoor攻击的泛化性。这项研究强调了在跨域数据场景中进行防御的重要性，并指出现有防御方法可能无法完全防范这种复杂的攻击模式。 \\ \hline
-    BadVLMDriver\cite{defense03} & Arxive(2024) & 这篇文章提出了一种名为BadVLMDriver的物理backdoor攻击方法，专门针对集成了视觉-语言模型（VLMs）的自动驾驶系统。与传统依赖数字修改的backdoor攻击不同，BadVLMDriver利用日常生活中的常见物理物体作为触发器，例如红色气球，来引发自动驾驶系统中的不安全行为，如突然加速。通过这种方法，攻击者可以在实际场景中诱导自动驾驶汽车做出危险的决定，展示了集成VLMs的自动驾驶技术所面临的严重安全威胁。具体的攻击与防御步骤如下：1.
+%     BadVLMDriver\cite{defense03} & Arxive(2024) & 这篇文章提出了一种名为BadVLMDriver的物理backdoor攻击方法，专门针对集成了视觉-语言模型（VLMs）的自动驾驶系统。与传统依赖数字修改的backdoor攻击不同，BadVLMDriver利用日常生活中的常见物理物体作为触发器，例如红色气球，来引发自动驾驶系统中的不安全行为，如突然加速。通过这种方法，攻击者可以在实际场景中诱导自动驾驶汽车做出危险的决定，展示了集成VLMs的自动驾驶技术所面临的严重安全威胁。具体的攻击与防御步骤如下：1.
 攻击触发器嵌入：首先，攻击者使用基于自然语言指令的生成模型来生成backdoor训练样本。在这些样本中，攻击者利用图像编辑技术将物理触发器（如气球）嵌入到图像中，并通过大型语言模型（LLM）生成包含恶意行为的文本响应。2.
@@
 防御策略：针对这种攻击，文章建议使用增量学习的方式进行防御，即在post-training阶段采用另一组正常样本对模型进行进一步调优。这种方法可以显著降低backdoor攻击的成功率，但其代价与常规的模型微调过程相当，对于依赖第三方VLM的自动驾驶公司来说可能具有挑战性。物理触发器：物理触发器是指现实生活中的物体，当这些物体出现在自动驾驶系统的摄像头视野中时，会触发VLM做出预设的恶意行为。增量学习：增量学习是一种防御策略，通过在模型训练完成后进一步微调模型，以降低backdoor攻击的效果。通过这项研究，文章强调了开发强大防御机制的紧迫性，以保护自动驾驶技术免受类似的物理backdoor攻击。 \\ \hline
-    SurveyLVLM\cite{defense04} & JOURNAL OF LATEX CLASS FILES(2024) & 这篇文章是一篇综述，系统地回顾了当前针对大型视觉-语言模型（LVLMs）的攻击方法，涵盖了各种现有的攻击形式，如对抗攻击（adversarial attacks）、越狱攻击（jailbreak attacks）、提示注入攻击（prompt injection attacks）以及数据投毒和后门攻击（data poisoning/backdoor attacks）。文章不仅介绍了每种攻击的具体实施方法，还探讨了它们的优缺点和背后的脆弱性。此外，文章还总结了当前用于LVLM攻击的资源，如数据集、模型和评估指标，最后提出了未来的研究方向，强调了持续发展和改进LVLMs安全措施的重要性。具体攻击方法：1.
+%     SurveyLVLM\cite{defense04} & JOURNAL OF LATEX CLASS FILES(2024) & 这篇文章是一篇综述，系统地回顾了当前针对大型视觉-语言模型（LVLMs）的攻击方法，涵盖了各种现有的攻击形式，如对抗攻击（adversarial attacks）、越狱攻击（jailbreak attacks）、提示注入攻击（prompt injection attacks）以及数据投毒和后门攻击（data poisoning/backdoor attacks）。文章不仅介绍了每种攻击的具体实施方法，还探讨了它们的优缺点和背后的脆弱性。此外，文章还总结了当前用于LVLM攻击的资源，如数据集、模型和评估指标，最后提出了未来的研究方向，强调了持续发展和改进LVLMs安全措施的重要性。具体攻击方法：1.
 对抗攻击（Adversarial Attacks）：通过在输入数据中引入细微的扰动，导致模型产生错误的或不期望的输出。这种攻击可以在白盒、灰盒和黑盒环境中实施，取决于攻击者对模型内部信息的掌握程度。2.
@@
 数据投毒/后门攻击（Data Poisoning/Backdoor Attacks）：攻击者在模型训练过程中故意引入恶意数据，导致模型在推理阶段表现异常。后门攻击通常在训练数据中嵌入触发器，当触发器被激活时，模型会表现出特定的有害行为。对抗攻击：这是通过在输入数据上施加微小的扰动，使得模型产生错误或预期外的输出。越狱攻击：指攻击者通过操纵输入数据，绕过模型的安全措施，使模型执行未经授权的操作。提示注入：通过在提示信息中注入恶意内容来改变模型的输出。数据投毒：通过在训练数据中加入恶意样本，使模型学习到错误的模式。未来研究方向：文章提出，未来研究应重点探索如何在没有模型内部信息的情况下实施攻击，提升攻击的跨模型适应性，以及如何更好地评估和对比不同攻击方法的有效性。 \\ \hline
-    Semantic Shield\cite{defense05} & CVPR2024 & 这篇文章提出了一种名为Semantic Shield的防御方法，旨在保护视觉-语言模型（VLMs）免受backdooring和数据投毒攻击的威胁。该方法通过细粒度的知识对齐机制来抵御攻击，使模型在训练过程中更加关注与外部知识对齐的视觉区域，从而避免学习到攻击者引入的虚假关联。具体的防御步骤如下：1.
+%     Semantic Shield\cite{defense05} & CVPR2024 & 这篇文章提出了一种名为Semantic Shield的防御方法，旨在保护视觉-语言模型（VLMs）免受backdooring和数据投毒攻击的威胁。该方法通过细粒度的知识对齐机制来抵御攻击，使模型在训练过程中更加关注与外部知识对齐的视觉区域，从而避免学习到攻击者引入的虚假关联。具体的防御步骤如下：1.
 知识元素提取：首先，Semantic Shield使用大语言模型（如Vicuna）从每个图像的字幕中提取潜在的视觉知识元素（Knowledge Elements，KEs）。这些KEs包含了图像中可以帮助识别目标的特征，如“厚毛皮”或“锋利的爪子”。2.
@@
 动态对比损失加权：为了降低受攻击样本在模型训练中的影响，Semantic Shield在对比学习过程中引入了动态加权机制。模型会根据图像块与KE的整体对齐度调整每个样本的损失权重，从而降低被攻击样本对模型的干扰。知识元素（KEs）：KEs是从图像字幕中提取出的视觉特征或属性，用于帮助模型更好地理解图像内容，例如“厚毛皮”代表动物的一个特征。对比学习：一种用于训练模型的技术，目的是将相似的样本在特征空间中拉近，将不相似的样本拉远。通过这些步骤，Semantic Shield能够显著提高VLMs在面对backdooring和数据投毒攻击时的鲁棒性，同时保持模型的整体性能。实验结果表明，Semantic Shield在多个数据集和攻击场景下表现出色，显著优于现有的防御方法。 \\ \hline
-    VL-Trojan\cite{defense06} & NeurIPS2024 & 这篇文章提出了一种名为VL-Trojan的多模态指令backdoor攻击方法，专门针对自回归视觉语言模型（Autoregressive Visual Language Models，VLMs）。文章揭示了现有backdoor攻击在自回归VLMs中的局限性，特别是在视觉编码器被冻结且攻击者只能有限或黑盒访问目标模型的情况下。为了解决这些问题，VL-Trojan通过隔离与聚类策略来生成图像触发器，并通过字符级迭代生成文本触发器，以提升攻击的有效性和转移性。具体攻击步骤如下：1.
+%     VL-Trojan\cite{defense06} & NeurIPS2024 & 这篇文章提出了一种名为VL-Trojan的多模态指令backdoor攻击方法，专门针对自回归视觉语言模型（Autoregressive Visual Language Models，VLMs）。文章揭示了现有backdoor攻击在自回归VLMs中的局限性，特别是在视觉编码器被冻结且攻击者只能有限或黑盒访问目标模型的情况下。为了解决这些问题，VL-Trojan通过隔离与聚类策略来生成图像触发器，并通过字符级迭代生成文本触发器，以提升攻击的有效性和转移性。具体攻击步骤如下：1.
 图像触发器生成：文章通过对比优化方法来生成图像触发器，即使在视觉编码器被冻结的情况下，依然可以将中毒样本的特征与干净样本的特征分离开来。具体而言，攻击者生成一个触发器，能够将中毒图像的特征与干净图像的特征在特征空间中进行有效的隔离和聚类。2.
@@
 反向训练：在生成触发器后，攻击者将这些触发器嵌入到一组中毒样本中，并将这些样本加入到指令调优数据集中。通过使用这些中毒样本进行反向训练，攻击者能够在推理过程中，诱导模型在遇到这些触发器时生成预设的响应。通过这些步骤，VL-Trojan在有限访问和黑盒设置下依然能够实现有效的backdoor攻击，成功率高达99.82\%，显著超越了其他基准方法。 \\ \hline
-    ROCLIP\cite{defense07} & NeurIPS2023 & 这篇文章提出了一种名为ROCLIP的防御方法，用于在预训练阶段保护多模态视觉语言模型（如CLIP）免受数据投毒和后门攻击的威胁。ROCLIP通过破坏受攻击的图像和文本对之间的关联，有效地防止了这些攻击在模型训练期间的成功。具体的防御步骤如下：1.
+%     ROCLIP\cite{defense07} & NeurIPS2023 & 这篇文章提出了一种名为ROCLIP的防御方法，用于在预训练阶段保护多模态视觉语言模型（如CLIP）免受数据投毒和后门攻击的威胁。ROCLIP通过破坏受攻击的图像和文本对之间的关联，有效地防止了这些攻击在模型训练期间的成功。具体的防御步骤如下：1.
 随机生成的文本池：ROCLIP方法在训练期间保持一个由随机选择的文本组成的池。与传统方法不同，ROCLIP不再将每个图像与其对应的字幕匹配，而是将每个图像与池中与其最相似的文本匹配。通过这种方式，ROCLIP能够有效破坏投毒图像和有害字幕之间的关联。2.
@@
 分批训练：ROCLIP采用分批训练策略，每隔几轮更新一次图像与最相似文本的匹配对，并在其余轮次中使用标准的CLIP损失进行训练。这一策略确保了即使在面对强力攻击时，ROCLIP依然能够有效防御。实验结果：实验表明，ROCLIP能够显著降低投毒和后门攻击的成功率。在应对数据投毒攻击时，ROCLIP将攻击成功率从93.75\%降至12.5\%，而对于后门攻击，成功率从78\%降至0\%。同时，ROCLIP还能提升模型的线性探测准确率，并且在零样本任务中的表现与CLIP相当。 \\ \hline
-    FABE\cite{defense08} & ICML2024 & 这篇文章提出了一种基于因果推断的防御框架，名为前门调整背门消除（Front-door Adjustment for Backdoor Elimination，FABE），旨在保护语言模型（LLMs）免受backdoor攻击。与传统的依赖特定触发器特征的防御方法不同，FABE通过构建前门变量来区分伪相关和真实因果关系，有效地防止各种类型的backdoor攻击。具体防御步骤如下：1.
+%     FABE\cite{defense08} & ICML2024 & 这篇文章提出了一种基于因果推断的防御框架，名为前门调整背门消除（Front-door Adjustment for Backdoor Elimination，FABE），旨在保护语言模型（LLMs）免受backdoor攻击。与传统的依赖特定触发器特征的防御方法不同，FABE通过构建前门变量来区分伪相关和真实因果关系，有效地防止各种类型的backdoor攻击。具体防御步骤如下：1.
 前门变量生成：FABE使用一个经过微调的语言模型（称为防御模型）来生成前门变量。前门变量是一个与输入语义等价的文本，但其生成的预测结果不会受到backdoor攻击的影响。2.
@@
 防御效果评估：在多个数据集上，FABE显著降低了多种攻击策略的成功率。例如，FABE将攻击成功率从93.63\%降低到15.12\%，大幅度优于传统防御方法，显示了其在应对复杂backdoor攻击时的强大防御能力。通过这些步骤，FABE为语言模型的backdoor攻击防御提供了一个新的思路，克服了传统方法的局限性，尤其是在无法预先知道攻击特征的情况下。 \\ \hline
-    Shadowcast\cite{defense09} & arXiv(2024) & 这个和王波的一样，是特朗普和拜登那篇。这篇文章提出了Shadowcast，一种针对视觉语言模型（VLMs）的隐秘数据投毒攻击方法。Shadowcast通过生成视觉上与正常样本无异的投毒样本，使VLM在处理日常任务时输出错误或误导性的文本描述。这种攻击方法在两个场景中表现出极高的有效性：标签攻击（Label Attack）和说服攻击（Persuasion Attack）。标签攻击旨在让模型错误地识别图像的类别，而说服攻击则通过生成连贯但误导性的描述来影响用户对图像的理解。具体攻击步骤如下：1.
+%     Shadowcast\cite{defense09} & arXiv(2024) & 这个和王波的一样，是特朗普和拜登那篇。这篇文章提出了Shadowcast，一种针对视觉语言模型（VLMs）的隐秘数据投毒攻击方法。Shadowcast通过生成视觉上与正常样本无异的投毒样本，使VLM在处理日常任务时输出错误或误导性的文本描述。这种攻击方法在两个场景中表现出极高的有效性：标签攻击（Label Attack）和说服攻击（Persuasion Attack）。标签攻击旨在让模型错误地识别图像的类别，而说服攻击则通过生成连贯但误导性的描述来影响用户对图像的理解。具体攻击步骤如下：1.
 文本生成：首先，攻击者使用一个预训练的视觉语言模型生成描述性文本，这些文本与投毒样本的图像内容匹配。随后，攻击者通过一个大语言模型对这些文本进行细化，以确保它们明确传达目标概念（如“健康食品”）。2.
@@
 投毒样本生成：最后，攻击者将这些被扰动的图像与相应的文本配对，形成投毒样本。在模型训练过程中，这些投毒样本会使模型错误地将原始概念图像与目标概念文本关联，从而实现攻击目的。实验结果：Shadowcast展示了其在不同攻击场景中的高效性，尤其在黑盒设置下，攻击成功率依然较高，表明了这种攻击方法的广泛适用性。此外，Shadowcast还展现了对抗数据增强和图像压缩技术的鲁棒性。 \\ \hline
-    Contextual Backdoor Attack\cite{defense10} & Springer2024 & 这篇文章提出了一种名为Contextual Backdoor Attack的新型攻击方法，旨在通过极少量的上下文提示数据对大型语言模型（LLMs）进行隐秘的背门攻击。此攻击方法特别针对由LLM生成的代码驱动的具身智能代理（如机器人和自动驾驶系统），通过在特定环境下使用上下文相关的触发器（文本或视觉触发器）来激活模型中的后门，从而导致具身智能代理在执行任务时表现出异常行为。具体的攻击步骤如下：1.
+%     Contextual Backdoor Attack\cite{defense10} & Springer2024 & 这篇文章提出了一种名为Contextual Backdoor Attack的新型攻击方法，旨在通过极少量的上下文提示数据对大型语言模型（LLMs）进行隐秘的背门攻击。此攻击方法特别针对由LLM生成的代码驱动的具身智能代理（如机器人和自动驾驶系统），通过在特定环境下使用上下文相关的触发器（文本或视觉触发器）来激活模型中的后门，从而导致具身智能代理在执行任务时表现出异常行为。具体的攻击步骤如下：1.
 生成和优化中毒示例：攻击者首先利用对抗性上下文生成技术，构建包含中毒提示的示例，并通过LLM评估器不断优化这些示例，以确保它们能够有效地感染目标LLM的上下文环境。2.
@@
 
-\end{longtable}
+% \end{longtable}
 

### 2024-09-10 FL_Backdoor_CV/helper.py
init: opensource modified by wb
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,0 +1,206 @@
+import math
+import random
+
+import numpy as np
+import torch
+
+from configs import args
+
+# ========= Fix the random seed (Start) =========
+torch.manual_seed(1)
+torch.cuda.manual_seed(1)
+random.seed(0)
+np.random.seed(0)
+
+
+# ========= Fix the random seed (End) =========
+
+
+class Helper:
+    def __init__(self, params):
+        self.target_model = None
+        self.local_model = None
+        self.training_data = None
+        self.benign_test_data = None
+        self.poisoned_data = None
+        self.poisoned_test_data = None
+        self.params = params
+        self.best_loss = math.inf
+
+    @staticmethod
+    def get_weight_difference(weight1, weight2):
+        difference = {}
+        res = []
+        if type(weight2) == dict:
+            for name, layer in weight1.items():
+                difference[name] = layer.data - weight2[name].data
+                res.append(difference[name].view(-1))
+        else:
+            for name, layer in weight2:
+                difference[name] = weight1[name].data - layer.data
+                res.append(difference[name].view(-1))
+        difference_flat = torch.cat(res)
+        return difference, difference_flat
+
+    @staticmethod
+    def get_l2_norm(weight1, weight2):
+        difference = {}
+        res = []
+        if type(weight2) == dict:
+            for name, layer in weight1.items():
+                difference[name] = layer.data - weight2[name].data
+                res.append(difference[name].view(-1))
+        else:
+            for name, layer in weight2:
+                difference[name] = weight1[name].data - layer.data
+                res.append(difference[name].view(-1))
+        difference_flat = torch.cat(res)
+        l2_norm = torch.norm(difference_flat.clone().detach().to(args.device))
+        l2_norm_np = np.linalg.norm(difference_flat.cpu().numpy())
+        return l2_norm, l2_norm_np
+
+    @staticmethod
+    def clip_grad(norm_bound, weight_difference, difference_flat):
+        l2_norm = torch.norm(difference_flat.clone().detach().to(args.device))
+        scale = max(1.0, float(torch.abs(l2_norm / norm_bound)))
+        for name in weight_difference.keys():
+            weight_difference[name].div_(scale)
+        return weight_difference, l2_norm
+
+    @staticmethod
+    def grad_mask_cv(helper, model, dataset_clearn, criterion, ratio=0.5):
+        """Generate a gradient mask based on the given dataset"""
+        model.train()
+        model.zero_grad()
+
[…]

### 2024-09-10 FL_Backdoor_CV/image_helper.py

@@ -1,0 +1,729 @@
+import copy
+import pickle
+import random
+from collections import defaultdict
+
+import numpy as np
+import torch
+from torch.utils.data import Dataset, DataLoader
+from torchvision import datasets, transforms
+from torchvision.datasets import EMNIST, FashionMNIST
+
+from FL_Backdoor_CV.helper import Helper
+from configs import args
+from transformers import CLIPProcessor, CLIPModel
+import os
+from peft import LoraConfig, get_peft_model
+
+random.seed(0)
+np.random.seed(0)
+import matplotlib as plt
+from torchvision.utils import make_grid
+
+
+def plot_image(images, lables, classes, batch_idx, adversarial_index=-1):
+    n_rows = (len(images) + 4) // 5
+    n_cols = 5
+    fig, axes = plt.subplots(n_rows, n_cols, figsize=(15, n_rows * 3))
+    for i in range(len(images)):
+        row = i // n_cols
+        col = i % n_cols
+        ax = axes[row, col] if n_rows > 1 else axes[col]
+        ax.set_title(f"Label: {classes[lables[i]]}", fontsize=8)
+        if args.dataset.lower() in ["emnist", "fmnist"]:
+            ax.imshow(images[i].reshape(28, 28), cmap="gray")
+            ax.axis("off")
+
+        elif args.dataset.lower() == "cifar10":
+            grid = make_grid(images[i])
+            # Add 0.5 after unnormalizing to [0, 255] to round to the nearest integer
+            ndarr = (
+                grid.mul(255)
+                .add_(0.5)
+                .clamp_(0, 255)
+                .permute(1, 2, 0)
+                .to("cpu", torch.uint8)
+                .numpy()
+            )
+            ax.imshow(ndarr)
+            ax.axis("off")
+
+    for j in range(len(images), n_rows * n_cols):
+        fig.delaxes(axes.flatten()[j])
+    plt.tight_layout()
+    if args.dataset.lower() == "emnist":
+        plt.savefig(
+            f"./emnist_{args.attack_mode.lower()}_{batch_idx}_{adversarial_index}.pdf",
+            bbox_inches="tight",
+        )
+    if args.dataset.lower() == "fmnist":
+        plt.savefig(
+            f"./fmnist_{args.attack_mode.lower()}_{batch_idx}_{adversarial_index}.pdf",
+            bbox_inches="tight",
+        )
+    if args.dataset.lower() == "cifar10":
+        plt.savefig(
[…]

### 2024-09-10 FL_Backdoor_CV/roles/aggregation_rules.py

@@ -1,0 +1,364 @@
+import math
+from collections import defaultdict
+from collections import Counter
+import numpy as np
+import sklearn.metrics.pairwise as smp
+import torch
+import torch.nn.functional as F
+import hdbscan
+from scipy.linalg import eigh as largest_eigh
+from sklearn.cluster import DBSCAN, KMeans
+
+from configs import args
+
+
+def avg(model_updates):
+    global_update = dict()
+    for name, data in model_updates.items():
+        global_update[name] = (
+            1
+            / args.participant_sample_size
+            * model_updates[name].sum(dim=0, keepdim=True)
+        )
+    return global_update
+
+
+from scipy.fftpack import dct
+
+
+def secfft(model_updates):
+    updates = torch.cat(list(model_updates.values()), dim=1)  # 整合模型更新
+
+    updates_dct = dct(updates, type=2, axis=1, norm="ortho")  # 离散余弦变换（DCT）
+    device = args.device
+    updates_dct = torch.tensor(updates_dct[:, :20000], device=device)  # 提取低频成分
+
+    # 计算特征值和特征向量
+    product_matrix = updates_dct @ updates_dct.T  # product_matrix为对称矩阵？
+    eigenvalues, eigenvectors = torch.linalg.eigh(product_matrix)
+    max_eigenvalue, max_eigenvector = eigenvalues[-1], eigenvectors[:, -1]
+
+    # 计算干净成分
+    max_eigenvalue = max_eigenvalue.real.item()  # 确保为实数
+    max_eigenvector = max_eigenvector.view(-1, 1)
+    clean_updates = updates_dct.T @ max_eigenvector / math.sqrt(max_eigenvalue)
+    clean_updates = clean_updates.reshape(1, -1)  # clean ingredient
+
+    # 计算KL散度
+    clean_updates = clean_updates.expand(updates_dct.shape[0], -1)
+    clean_updates_prob = F.softmax(clean_updates, dim=1)
+    updates_dct_log_prob = F.log_softmax(updates_dct, dim=1)
+    kl_div = F.kl_div(updates_dct_log_prob, clean_updates_prob, reduction="none")
+    kl_div_per_sample = kl_div.sum(dim=1).cpu().numpy()
+    clusterer = hdbscan.HDBSCAN(min_cluster_size=5, metric="euclidean")
+    clusters = clusterer.fit_predict(kl_div_per_sample.reshape(-1, 1))
+    cluster_counts = Counter(clusters)
[…]

### 2024-09-10 FL_Backdoor_CV/roles/client.py

@@ -1,0 +1,374 @@
+import copy
+import random
+import time
+
+import torch
+
+from FL_Backdoor_CV.roles.evaluation import test_poison_cv, test_cv
+from configs import args
+from FL_Backdoor_CV.image_helper import plot_image
+import torch.optim as optim
+
+
+class Client:
+    def __init__(self, client_id, local_data, local_data_size, malicious=False):
+        self.client_id = client_id
+        self.local_data = local_data
+        self.local_data_size = local_data_size
+        self.malicious = malicious
+        self.server = None
+        self.adversarial_index = None
+        self.range_no_id = None
+
+    def local_train(
+        self,
+        local_model,
+        helper,
+        epoch,
+        do_attack=False,
+        criterion=torch.nn.CrossEntropyLoss(),
+    ):
+        local_data = self.local_data
+        text_inputs = [f"This is a photo of a {label}" for label in helper.classes]
+        if self.malicious and do_attack:
+            # === clean part of malicious clients.
+            # === we need to remove indices corresponding to the target label when attackers conduct local training. ===
+            if self.range_no_id is None:
+                range_no_id = list(range(len(helper.train_dataset)))
+
+                if args.attack_mode.lower() in ["mr", "dba", "flip"]:
+                    for ind, x in enumerate(helper.train_dataset):
+                        imge, label = x
+                        if label == helper.params["poison_label_swap"]:
+                            range_no_id.remove(ind)  # 移除目标类别的图片
+
+                    if args.dataset == "cifar10":  # 移除指定的图片
+                        if args.attack_mode.lower() == "mr":
+                            for image in (
+                                helper.params["poison_images_test"]
+                                + helper.params["poison_images"]
+                            ):
+                                if image in range_no_id:
+                                    range_no_id.remove(image)
+
+                elif args.attack_mode.lower() == "combine":
+                    target_label = None
+                    if self.adversarial_index == 0:
+                        target_label = helper.params["poison_label_swaps"][0]
+                    elif self.adversarial_index == 1:
+                        target_label = helper.params["poison_label_swaps"][1]
+                    elif self.adversarial_index == 2:
+                        target_label = helper.params["poison_label_swaps"][2]
+                    elif self.adversarial_index == 3:
+                        target_label = helper.params["poison_label_swap"]
+                    for ind, x in enumerate(helper.train_dataset):
+                        imge, label = x
+                        if label == target_label:
+                            range_no_id.remove(ind)
+
+                    if args.dataset == "cifar10":
[…]

### 2024-09-10 FL_Backdoor_CV/roles/server-init.py

@@ -1,0 +1,924 @@
+import copy
+
+import os
+import random
+import re
+from collections import defaultdict
+
+
+import numpy as np
+import sklearn.metrics.pairwise as smp
+import torch
+import torch.nn.functional as F
+from scipy.linalg import eigh as largest_eigh
+from scipy.stats import entropy
+from sklearn.cluster import DBSCAN, KMeans
+from sklearn.metrics import pairwise_distances
+from torch.nn.utils import parameters_to_vector, vector_to_parameters
+
+from FL_Backdoor_CV.models.create_model import create_model
+from FL_Backdoor_CV.roles.evaluation import test_cv, test_poison_cv
+from configs import args
+from FL_Backdoor_CV.roles.aggregation_rules import roseagg
+from FL_Backdoor_CV.roles.aggregation_rules import avg
+from FL_Backdoor_CV.roles.aggregation_rules import foolsgold
+from FL_Backdoor_CV.roles.aggregation_rules import flame
+from FL_Backdoor_CV.roles.aggregation_rules import fltrust
+from FL_Backdoor_CV.roles.aggregation_rules import robust_lr
+
+import pickle
+
+
+def softmax(x):
+    f_x = np.exp(x) / np.sum(np.exp(x))
+    return f_x
+
+
+class Server:
+    def __init__(self, helper, clients, adversary_list):
+        # === model ===
+        if args.resume:
+            self.model = torch.load(
+                os.path.join(
+                    "./FL_Backdoor_CV/saved_models/Revision_1", args.resumed_name
+                ),
+                map_location=args.device,
+            )
+        else:
+            self.model = create_model()
+
+        # === gradient correction ===
+        # self.previous_models = []
+        # if args.gradient_correction:
+        #     previous_model = copy.deepcopy(self.model)
+        #     previous_model.load_state_dict(self.model.state_dict())
+        #     self.previous_models.append(previous_model)
+
+        # === clients, participants, attackers, and benign clients ===
+        self.clients = clients
+        self.participants = None
+        self.adversary_list = adversary_list
+        self.benign_indices = list(
+            set(list(range(args.participant_population))) - set(self.adversary_list)
+        )
+
+        # === image helper ===
+        self.helper = helper
+
+        # === whether resume ===
+        self.current_round = 0
+        # === Inherent recognition accuracy on poisoned data sets
+        self.inheret_poison_acc = 0
+
+        if args.resume:
+            self.current_round = int(
[…]

### 2024-09-10 FL_Backdoor_CV/roles/server.py

@@ -1,0 +1,901 @@
+import copy
+
+import os
+import random
+import re
+from collections import defaultdict
+
+
+import numpy as np
+import sklearn.metrics.pairwise as smp
+import torch
+import torch.nn.functional as F
+from scipy.linalg import eigh as largest_eigh
+from scipy.stats import entropy
+from sklearn.cluster import DBSCAN, KMeans
+from sklearn.metrics import pairwise_distances
+from torch.nn.utils import parameters_to_vector, vector_to_parameters
+
+from FL_Backdoor_CV.models.create_model import create_model
+from FL_Backdoor_CV.roles.evaluation import test_cv, test_poison_cv
+from configs import args
+from FL_Backdoor_CV.roles.aggregation_rules import roseagg
+from FL_Backdoor_CV.roles.aggregation_rules import avg
+from FL_Backdoor_CV.roles.aggregation_rules import foolsgold
+from FL_Backdoor_CV.roles.aggregation_rules import flame
+from FL_Backdoor_CV.roles.aggregation_rules import fltrust
+from FL_Backdoor_CV.roles.aggregation_rules import robust_lr
+
+import pickle
+
+
+def softmax(x):
+    f_x = np.exp(x) / np.sum(np.exp(x))
+    return f_x
+
+
+class Server:
+    def __init__(self, helper, clients, adversary_list):
+        # === model ===
+        # if args.resume:
+        #     self.model = torch.load(
+        #         os.path.join(
+        #             "./FL_Backdoor_CV/saved_models/Revision_1", args.resumed_name
+        #         ),
+        #         map_location=args.device,
+        #     )
+        # else:
+        #     self.model = create_model()
+        self.model = helper.target_model
+
+        # === gradient correction ===
+        # self.previous_models = []
+        # if args.gradient_correction:
+        #     previous_model = copy.deepcopy(self.model)
+        #     previous_model.load_state_dict(self.model.state_dict())
+        #     self.previous_models.append(previous_model)
+
+        # === clients, participants, attackers, and benign clients ===
+        self.clients = clients
+        self.participants = None
+        self.adversary_list = adversary_list
+        self.benign_indices = list(
+            set(list(range(args.participant_population))) - set(self.adversary_list)
+        )
+
+        # === image helper ===
+        self.helper = helper
+
+        # === whether resume ===
+        self.current_round = 0
+        # === Inherent recognition accuracy on poisoned data sets
[…]

### 2024-09-10 configs.py

@@ -1,0 +1,271 @@
+import argparse
+
+parser = argparse.ArgumentParser(description="PPDL")
+
+parser.add_argument("--reduction_factor", type=int, default=5)
+
+# === dataset, data partitioning mode, device, model, and rounds
+parser.add_argument(
+    "--dataset",
+    default="fmnist",
+    choices=["cifar10", "emnist", "fmnist"],
+    help="dataset",
+)
+
+parser.add_argument("--params", default="utils/fmnist_params.yaml", dest="params")
+
+
+parser.add_argument(
+    "--emnist_style", default="digits", type=str, help="byclass digits letters"
+)
+
+
+parser.add_argument(
+    "--rounds", default=20, type=int, help="total rounds for convergence"
+)
+
+
+parser.add_argument(
+    "--participant_population", default=50, type=int, help="total clients"
+)
+
+
+parser.add_argument(
+    "--participant_sample_size", default=50, type=int, help="participants each round"
+)
+
+
+parser.add_argument("--is_poison", default=1, type=int, help="poison or not")
+
+
+parser.add_argument(
+    "--number_of_adversaries", default=10, type=int, help="the number of attackers"
+)
+
+
+parser.add_argument(
+    "--random_compromise", default=1, type=int, help="randomly compromise benign client"
+)
+
+parser.add_argument(
+    "--poison_rounds",
+    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15",
+    type=str,
+    help="",
+)
+
+parser.add_argument(
+    "--retrain_rounds",
+    default=20,
+    type=int,
+    help="continue to train {retrain_rounds} rounds starting when resume is true",
+)  # end_rounds = curr_round + retrain_rounds + window 这个参数的意思是指明中毒攻击情况下训练的轮数
+
+parser.add_argument(
+    "--aggregation_rule",
+    default="avg",
+    type=str,
+    choices=["avg", "rlr", "flame", "foolsgold", "roseagg", "fltrust", "fedcie"],
+    help="aggregation method",
+)
+
+
+parser.add_argument(
+    "--class_imbalance",
+    type=int,
+    default=1,
+    help="split the dataset in a non-iid (class imbalance) fashion",
+)
+
+parser.add_argument("--balance", type=float, default=1, help="balance of the data size")
+
+
+parser.add_argument(
[…]

### 2024-09-10 trainer.py

@@ -1,0 +1,291 @@
+import os
+
+os.environ["OMP_NUM_THREADS"] = "1"
+
+import random
+import time
+
+import numpy as np
+import torch.backends.cudnn
+import yaml
+
+from FL_Backdoor_CV.image_helper import ImageHelper
+from configs import args
+
+try:
+    from yaml import CLoader as Loader, CDumper as Dumper
+except ImportError:
+    from yaml import Loader, Dumper
+from FL_Backdoor_CV.roles.client import Client
+from FL_Backdoor_CV.roles.server import Server
+from PIL import Image
+from torchvision.utils import save_image, make_grid
+import matplotlib.pyplot as plt
+
+torch.manual_seed(1)
+torch.cuda.manual_seed(1)
+
+random.seed(0)
+np.random.seed(0)
+from datetime import datetime
+
+import csv
+
+
+def save_results_to_csv(results, filename="results.csv"):
+    keys = list(results.keys())
+
+    max_length = max(len(v) for v in results.values())
+
+    for key in keys:
+        if len(results[key]) < max_length:
+            results[key].extend([""] * (max_length - len(results[key])))
+
+    rows = zip(*[results[key] for key in keys])
+
+    with open(filename, "w", newline="") as csvfile:
+        writer = csv.writer(csvfile)
+        writer.writerow(keys)
+        writer.writerows(rows)
+
+
+def check_params(params):
+    assert params["participant_sample_size"] <= params["participant_population"]
+    assert params["number_of_adversaries"] <= params["participant_sample_size"]
+
+
+class Trainer:
+    def __init__(self):
+        print(
+            f"We are conduct federated training using {args.aggregation_rule} on {args.dataset}... \n"
+        )
+
+        # === Load yaml file ===
+        with open(f"./FL_Backdoor_CV/{args.params}", "r", encoding="utf-8") as f:
+            params_loaded = yaml.load(f, Loader=Loader)
+
+        # === Add additional fields to the loaded params based on args ===
+        params_loaded.update(vars(args))
+        if (
+            params_loaded["dataset"] == "cifar10"
+            or params_loaded["dataset"] == "emnist"
+            or params_loaded["dataset"] == "fmnist"
+        ):
+            dataset_name = params_loaded["dataset"]
+            if os.path.isdir(f"./FL_Backdoor_CV/data/{dataset_name}/"):
+                params_loaded["data_folder"] = f"./FL_Backdoor_CV/data/{dataset_name}"
[…]

### 2024-09-10 FL_Backdoor_CV/image_helper.py
fmnist_MR

@@ -17,7 +17,7 @@ from peft import LoraConfig, get_peft_model
 
 random.seed(0)
 np.random.seed(0)
-import matplotlib as plt
+import matplotlib.pyplot as plt
 from torchvision.utils import make_grid
 
 
@@ -31,7 +31,7 @@ def plot_image(images, lables, classes, batch_idx, adversarial_index=-1):
         ax = axes[row, col] if n_rows > 1 else axes[col]
         ax.set_title(f"Label: {classes[lables[i]]}", fontsize=8)
         if args.dataset.lower() in ["emnist", "fmnist"]:
-            ax.imshow(images[i].reshape(28, 28), cmap="gray")
+            ax.imshow(images[i][0].reshape(28, 28), cmap="gray")
             ax.axis("off")
 
         elif args.dataset.lower() == "cifar10":

### 2024-09-10 FL_Backdoor_CV/roles/client.py

@@ -333,14 +333,14 @@ class Client:
                             )
 
             # === malicious test ===
-            test_loss, test_acc = test_cv(
-                helper.benign_test_data, local_model, helper.classes, helper.processor
-            )
-            print(
-                f"Malicious id: {self.client_id}, "
-                f"Test accuracy: {test_acc: .4f}, "
-                f"Test loss: {test_loss: .4f}."
-            )
+            # test_loss, test_acc = test_cv(
+            #     helper.benign_test_data, local_model, helper.classes, helper.processor
+            # )
+            # print(
+            #     f"Malicious id: {self.client_id}, "
+            #     f"Test accuracy: {test_acc: .4f}, "
+            #     f"Test loss: {test_loss: .4f}."
+            # )
         else:
             optimizer = torch.optim.Adam(
                 local_model.parameters(),

### 2024-09-10 FL_Backdoor_CV/roles/server.py

@@ -294,6 +294,54 @@ class Server:
         ):
             model_updates[name] = local_param.data - param.data.view(1, -1)  # 广播机制
 
+            if args.attack_mode.lower() in [
+                "mr",
+                "dba",
+                "flip",
+                "edge_case",
+                "neurotoxin",
+                "combine",
+            ]:
+                if "num_batches_tracked" not in name:
+                    for i in range(args.participant_sample_size):
+                        if self.clients[self.participants[i]].malicious:
+                            mal_boost = 1
+                            if args.is_poison:
+                                if args.mal_boost:
+                                    if args.attack_mode.lower() in [
+                                        "mr",
+                                        "flip",
+                                        "edge_case",
+                                        "neurotoxin",
+                                        "combine",
+                                    ]:
+                                        mal_boost = (
+                                            args.mal_boost / args.number_of_adversaries
+                                        )
+                                    elif args.attack_mode.lower() == "dba":
+                                        mal_boost = args.mal_boost / (
+                                            args.number_of_adversaries
+                                            / args.dba_trigger_num
+                                        )
+                                else:
+                                    if args.attack_mode.lower() in [
+                                        "mr",
+                                        "flip",
+                                        "edge_case",
+                                        "neurotoxin",
+                                        "combine",
+                                    ]:
+                                        mal_boost = (
+                                            args.participant_sample_size
+                                            / args.number_of_adversaries
+                                        )
+                                    elif args.attack_mode.lower() == "dba":
+                                        mal_boost = args.participant_sample_size / (
+                                            args.number_of_adversaries
+                                            / args.dba_trigger_num
+                                        )
+                            model_updates[name][i] *= mal_boost / args.global_lr / 2
+
         # 保存模型梯度
         path = os.path.join(
             os.getcwd(),
@@ -303,9 +351,9 @@ class Server:
             pickle.dump(model_updates, file)
 
         # 判断前后两行是不是相等
-        first_layers = trained_models.values()[0]
-        is_all_rows_same = (first_layers[0] == first_layers).all(dim=1).all()
-        print(f"all rows are same: {is_all_rows_same}")
+        # first_layers = trained_models.values()[0]
+        # is_all_rows_same = (first_layers[0] == first_layers).all(dim=1).all()
+        # print(f"all rows are same: {is_all_rows_same}")
 
         # === aggregate ===
         global_update = None

### 2024-09-10 configs.py

@@ -2,7 +2,7 @@ import argparse
 
 parser = argparse.ArgumentParser(description="PPDL")
 
-parser.add_argument("--reduction_factor", type=int, default=5)
+parser.add_argument("--reduction_factor", type=int, default=10)
 
 # === dataset, data partitioning mode, device, model, and rounds
 parser.add_argument(
@@ -26,12 +26,12 @@ parser.add_argument(
 
 
 parser.add_argument(
-    "--participant_population", default=50, type=int, help="total clients"
+    "--participant_population", default=10, type=int, help="total clients"
 )
 
 
 parser.add_argument(
-    "--participant_sample_size", default=50, type=int, help="participants each round"
+    "--participant_sample_size", default=10, type=int, help="participants each round"
 )
 
 
@@ -39,7 +39,7 @@ parser.add_argument("--is_poison", default=1, type=int, help="poison or not")
 
 
 parser.add_argument(
-    "--number_of_adversaries", default=10, type=int, help="the number of attackers"
+    "--number_of_adversaries", default=1, type=int, help="the number of attackers"
 )
 
 
@@ -49,7 +49,7 @@ parser.add_argument(
 
 parser.add_argument(
     "--poison_rounds",
-    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15",
+    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15, 16, 17, 18, 19",
     type=str,
     help="",
 )
@@ -141,7 +141,7 @@ parser.add_argument("--decay", type=float, default=5e-4, help="SGD weight_decay"
 # === attack mode ===
 parser.add_argument(
     "--num_poisoned_samples",
-    default=64,
+    default=32,
     type=int,
     help="the number of poisoned samples in one batch",
 )
@@ -152,7 +152,7 @@ parser.add_argument(
 
 parser.add_argument(
     "--dba_poison_rounds",
-    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15",
+    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19",
     type=str,
     help="if {attack_mode} == 'DBA', the poison rounds is {dba_poison_rounds}",
 )

### 2024-09-10 trainer.py

@@ -30,6 +30,7 @@ np.random.seed(0)
 from datetime import datetime
 
 import csv
+from FL_Backdoor_CV.image_helper import plot_image
 
 
 def save_results_to_csv(results, filename="results.csv"):
@@ -78,7 +79,7 @@ class Trainer:
                 range(params_loaded["participant_population"])[
                     args.number_of_adversaries :
                 ],
-                20,  # TODO 这里应该修改，其应该小于良性用户的数量
+                0,  # TODO 这里应该修改，其应该小于良性用户的数量
             )
             # params_loaded["participant_clean_data"] 存储的是150个良性用户的ID， 用来计算的neurotoxin攻击的mask
         else:
@@ -96,6 +97,15 @@ class Trainer:
         helper.load_distributed_data()
         helper.load_benign_data()
         helper.load_poison_data()
+
+        for x in helper.poisoned_train_data:
+            inputs_p, labels_p = helper.get_poison_batch(x)
+            plot_image(
+                inputs_p,
+                labels_p,
+                helper.classes,
+                -1,
+            )
 
         print(f"Time spent: {time.time() - start_time: .4f} seconds!")
         print(f"--------------------- L O A D E D ! ---------------------")

### 2024-09-10 FL_Backdoor_CV/roles/client.py
fmnist_NEUR_EDGE

@@ -248,7 +248,7 @@ class Client:
                 mask_grad_list = None
                 if args.attack_mode.lower() == "neurotoxin":
                     assert helper.params["gradmask_ratio"] != 1
-                    num_clean_data = 20
+                    num_clean_data = 4
                     subset_data_chunks = random.sample(
                         helper.params["participant_clean_data"], num_clean_data
                     )

### 2024-09-10 trainer.py

@@ -79,7 +79,7 @@ class Trainer:
                 range(params_loaded["participant_population"])[
                     args.number_of_adversaries :
                 ],
-                0,  # TODO 这里应该修改，其应该小于良性用户的数量
+                4,  # TODO 这里应该修改，其应该小于良性用户的数量
             )
             # params_loaded["participant_clean_data"] 存储的是150个良性用户的ID， 用来计算的neurotoxin攻击的mask
         else:

### 2024-09-11 trainer.py
save the participants

@@ -195,7 +195,7 @@ class Trainer:
         file_path = f"./FL_Backdoor_CV/{formatted_time}"
         os.makedirs(f"./FL_Backdoor_CV/{formatted_time}/participants", exist_ok=True)
         os.makedirs(f"./FL_Backdoor_CV/{formatted_time}/model_updates", exist_ok=True)
-
+        self.participants = {}
         if not os.path.exists(saved_results_path):
             os.makedirs(saved_results_path)
         with open(arg_path, "w") as f:
@@ -223,7 +223,7 @@ class Trainer:
             start_time = time.time()
             # === participants selection phase ===
             self.server.select_participants()
-
+            self.participants[cur_round] = self.server.self.participants
             # === training and aggregating phase ===
             self.server.train_and_aggregate(
                 global_lr=args.global_lr, round=cur_round, root_path=file_path
@@ -294,6 +294,15 @@ class Trainer:
             # === save the results every args.record_res_step rounds ===
             if self.server.current_round % args.record_res_step == 0:
                 save_results_to_csv(self.results, res_path)
+                save_results_to_csv(
+                    self.participants,
+                    f"./FL_Backdoor_CV/{formatted_time}/participants/participants.csv",
+                )
+
+        save_results_to_csv(
+            self.participants,
+            f"./FL_Backdoor_CV/{formatted_time}/participants/participants.csv",
+        )
 
 
 if __name__ == "__main__":

### 2024-09-11 attack-zh.tex
docs: my changes 昨日凌晨2:41
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 % 单论识别
-$G^t$ & The global model at round $t$. \\ \hline
 $\theta_i^t$ & The local model of participant at round $t$. \\ \hline
@@
 \( {v}_{i}^{t'} \) & The vector of the high dimensional ball $t'$-th round.\\ \hline
+$lof_i$ & The LOF score of the $i$-th node\\ \hline
+$cre_i$ & The confidence of the $i$-th node\\ \hline
 
@@
 \State Step 2: Clean Ingredient Extraction
-\State $H^t \gets (G_0^t, G_1^t, \ldots, G_{\mathcal{M}}^t) \in \mathbb{R}^{d \times m}$ \Comment{Stacking to form Matrix $H^t$.}
+\State $H^t \gets (G_0^t, G_1^t, \ldots, G_{n}^t) \in \mathbb{R}^{d \times m}$ \Comment{Stacking to form Matrix $H^t$.}
 
@@
 \State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
-\State $\tilde{G}^t_0 \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
+\State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
 
@@
 \State Step 3: Kullback-Leibler Divergence Calculation
-\State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t_0)$
+\State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
 \For {Node $R_i$}
@@
 
-\item \textbf{Clean Ingredient Extraction}：在将模型更新向量转换到频域空间后，我们基于“恶意节点的数量少于良性节点”的假设，通过奇异值分解（SVD）从所有节点的频域向量中提取出“干净成分”，并以此作为区分恶意与良性节点的标准。其主要过程如算法\ref{alg:malicious-node-detection}的10-13行所示，将所有节点的频率向量堆叠为矩阵 \(H^t = ({G_0^t}, {G_1^t}, \ldots, {G_{\mathcal{M}}^t}) \in \mathbb{R}^{m \times n}\)，其中每一列代表一个节点的低频向量。通过计算矩阵的最大奇异值及其对应的左奇异向量来作为相应的干净成分。即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)，根据公式\ref{equation:singular}，得到干净成分 \(\tilde{G}_0^t\)。这个干净成分\(\tilde{G}_0^t\)表示了良性节点的主要成分，能够有效地与恶意节点的异常行为区分开来，从而用于后续的恶意节点检测。
+\item \textbf{Clean Ingredient Extraction}：在将模型更新向量转换到频域空间后，我们基于“恶意节点的数量少于良性节点”的假设，通过奇异值分解（SVD）从所有节点的频域向量中提取出“干净成分”，并以此作为区分恶意与良性节点的标准。其主要过程如算法\ref{alg:malicious-node-detection}的10-13行所示，将所有节点的频率向量堆叠为矩阵 \(H^t = ({G_0^t}, {G_1^t}, \ldots, {G_{n}^t}) \in \mathbb{R}^{d \times n}\)，其中每一列代表一个节点的低频向量。通过计算矩阵的最大奇异值及其对应的左奇异向量来作为相应的干净成分。即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)，根据公式\ref{equation:singular}，得到干净成分 \(\tilde{G}^t\)。这个干净成分\(\tilde{G}^t\)表示了良性节点的主要成分，能够有效地与恶意节点的异常行为区分开来，从而用于后续的恶意节点检测。
 
 \begin{equation}
-\tilde{G}^t_0 = \frac{H^t \xi_{\text{max}}}{\sqrt{\lambda_{\text{max}}}}
+\tilde{G}^t = \frac{H^t \xi_{\text{max}}}{\sqrt{\lambda_{\text{max}}}}
 \label{equation:singular}
@@
 
-\item \textbf{Kullback-Leibler Divergence Calculation}：在得到干净分量后，我们计算每个节点的频率向量与干净成分之间的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的16-20行所示，对于每个节点的低频向量\(\mathbf{G}_i^t\)以及上一步求得的干净成分\(\tilde{G}^t_0\)，通过Softmax函数来将它们转换为相应的概率分布 \(P_i^t\) 和 \(Q^t\) 。然后利用KL散度计算每个节点概率分布\((P_i^t\)和干净分量概率分布 \(Q^t\) 之间的距离，得到相应的分布差异集合\(S = ({{KL}}_1, {{KL}}_2, \ldots, {{KL}}_n)\)。这个集合反映了每个节点频率向量相对于干净成分的异常程度，较大的KL散度值表示节点对应的频率向量与干净成分的分布差异较大，提示该节点可能是恶意节点。最终，这些分布差异将作为恶意节点检测的基础，通过进一步分析来区分良性节点和潜在的恶意节点。
+\item \textbf{Kullback-Leibler Divergence Calculation}：在得到干净分量后，我们计算每个节点的频率向量与干净成分之间的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的16-20行所示，对于每个节点的低频向量\(G_i^t\)以及上一步求得的干净成分\(\tilde{G}^t\)，通过Softmax函数来将它们转换为相应的概率分布 \(P_i^t\) 和 \(Q^t\) 。然后利用KL散度计算每个节点概率分布\((P_i^t\)和干净分量概率分布 \(Q^t\) 之间的距离，得到相应的分布差异集合\(S = ({{KL}}_1, {{KL}}_2, \ldots, {{KL}}_n)\)。这个集合反映了每个节点频率向量相对于干净成分的异常程度，较大的KL散度值表示节点对应的频率向量与干净成分的分布差异较大，提示该节点可能是恶意节点。最终，这些分布差异将作为恶意节点检测的基础，通过进一步分析来区分良性节点和潜在的恶意节点。
 
@@
 
-\textbf{Overview}: 前面的攻击中已经可以有效地针对单轮次攻击进行识别，本部分主要结合客户端的历史记录对客户端进行有效的识别。本部分将保留历史$T$轮次的全局模型$\theta_g^{t'}$，其中$t-T\leq t'< t$，并将其Flatten后视为高维空间中的一个点；同时保留每个客户端的历史更新变化，将其视为高维空间中的一个向量，将其延伸后视为一个射线。对于每个客户端，使用最小覆盖球算法计算得到一个最小的超球，覆盖$\varepsilon$比例的射线。最终球心的位置可以被视为对应客户端对全局模型的意图引导点，球心的半径可以视为对应客户端的置信度。
+\textbf{Overview}: 前面的攻击中已经可以有效地针对单轮次攻击进行识别，本部分主要结合客户端的历史记录对客户端进行有效的识别。本部分将保留历史$T$轮次的全局模型$\theta_g^{t'}$，其中$\max\{t-T+1, 1\}\leq  t'\leq t$，并将其Flatten后视为高维空间中的一个点；同时保留每个客户端的历史更新变化，将其视为高维空间中的一个向量，将其延伸后视为一个射线。对于每个客户端，使用最小覆盖球算法计算得到一个最小的超球，覆盖$\zeta$比例的射线。最终球心的位置可以被视为对应客户端对全局模型的意图引导点，球心的半径可以视为对应客户端的置信度。
 
 \begin{algorithm}
-\caption{Malicious Node Detection via History}
+\caption{Malicious Node Detection and Gradient Aggregation}
 \label{alg:malicious-node-detection-history}
 \begin{algorithmic}[1]
-\State \textbf{Input:} Global model history $\{G_{t-T}, G_{t-T+1}, \dots, G_{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \triangledown \theta_{i}^{t-T+1}, \dots, \triangledown \theta_{i}^{t-1}\}$, threshold $\varepsilon$
-\State \textbf{Output:} Set of clients marked as normal $U_{nor}$ and set of clients marked as malicious $U_{mal}$
-\State Step 1: Keep T-rounds History
-\For {Node $i$}
-    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_{i}^t)$
-    \State $DB.gradient\ \ +=\ \ \bar{\theta_i^t}$
-    \State $DB.model\ \ +=\ \ G_{t-1}$
+\State \textbf{Input:} Global model history $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$, threshold $\varepsilon$
+\State \textbf{Output:} Sets of normal clients $U_{nor}$ and malicious clients $U_{mal}$
+
+\State \textbf{Step 1: Keep T-rounds History}
+\For {Client $i$}
+    \State Record flattened gradients $\bar{\theta_i^t} = Flatten(\triangledown \theta_{i}^t)$ and models $\theta_g^{t-1}$
+    \State Construct rays: $\widetilde{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'} = \overline{\triangledown\theta_{i}^{t'}}$ for $t' = \max\{t-T+1, 1\}, \ldots, t$
 \EndFor
-\State Step 2: Construct Ray Model
-\For {Node $i$}
-    \State Construct rays using flattened global models and gradient updates:
-    \State $P_{i}^{t-j} = Flatten(G_{t-j-1})$, $\mathbf{d}_{i}^{t-j} = \bar{\theta}_{i}^{t-j}$ for $j = 0, 1, \ldots, T-1$
+
+\State \textbf{Step 2: Obtain the Purpose Intention}
+\For {Client $i$}
+    \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
+    \While {Not Converged}
+        \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
+    \EndWhile
+    \State Calculate confidence $cre_i = \frac{1}{r_i + \rho}$
 \EndFor
-\State Step 3: Minimum Enclosing Hypersphere Calculation
-\For {Node $i$}
-    \State Initialize center $O_0$ and radius $r_0$
-    \While {Not Converged}
-        \State Calculate projection points $Q_{i}^{t-j}$ and sort by distance to $O_k$
-        \State Compute $D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{i}^{t-j}\|$
-        \State Update $O_{k+1} = O_k + \alpha \left(\frac{1}{\lceil n\times \varepsilon\rceil} \sum_{1\leq j\leq \lceil n\times \varepsilon\rceil} (Q_{i}^{t-j} - O_k)\right)$
-        \State Update $r_{k+1} = D_k$
-    \EndWhile
-    \State Calculate confidence $C_i = \frac{1}{r_i + \epsilon}$
+
+\State \textbf{Step 3: Abnormal Detection}
+\For {Client $i$}
+    \For {Each point $O_j \neq O_i$}
+        \State Calculate distance $\|O_i - O_j\|$
     \EndFor
-\State Step 4: Abnormal Detection
-\For {Node $i$}
-    \State Calculate adjusted LOF: $\text{adjusted\_lof}(x_i) = \text{LOF}(x_i) \times (r_i + \epsilon)$
-    \State Determine threshold $\tau'$ and classify nodes as normal or malicious
+    \State Determine $\kappa$-distance $\widetilde{dis_i^\kappa}$ for $O_i$
+    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^\kappa}$
+    \State Compute reachability distance $rea_{i,j} = \max\{\widetilde{dis_i^\kappa}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$
+    \State Calculate local reachability density $lrd_i = \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$
 \EndFor
-\State \textbf{Return} $U_{nor}, U_{mal}$
+% \For {Client $i$}
+%     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
+%     \If {$lof_i > 1$}
+%         \State Mark client $i$ as malicious, add to $U_{mal}$
+%     \Else
+%         \State Mark client $i$ as normal, add to $U_{nor}$
+%     \EndIf
+% \EndFor
+\State Calculate $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$ for each client $i$
+% \State $U_{mal} = \{i \,|\, lof_i > 1\}$
+% \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
+\State $U_{mal}, U_{nor} = \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$
+
+\State \textbf{Step 4: Gradients Aggregation}
+\For {Client $i\in U_{nor}$}
+        \State Compute adjusted confidence $cre_i' = \tanh(cre_i)$
+        \State Normalize weights $w_i = \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$
+\EndFor
+
+\State \textbf{Output:} Aggregated global model update $\theta_g^t = \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$
 \end{algorithmic}
@@
 
-“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$G_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_g$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$G_t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-G_{t-1}$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上伦次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。此部分可以参考算法\ref{alg:malicious-node-detection-history}的step1。
+“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$\theta_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_i$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$\theta^t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-\theta^t$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上轮次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。此部分可以参考算法\ref{alg:malicious-node-detection-history}的step1。
 
@@
 
-“Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上伦次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
+“Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
 
-“Construct Ray Model”的主要过程如下。对于每个客户端 \(R_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的更新变化历史。
-
-\begin{itemize}
-    \item 设 \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(i\) 上传的展平后的梯度变化向量。
-    \item 对于每一轮 \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \))，我们将每个射线的起点表示为展平后的全局模型 \( \theta_g^{t'} \)，并将每个射线的方向向量表示为展平后的梯度变化 \( \overline{\triangledown\theta_{i}^{t'}} \)。因此，射线模型可以构建如下：
+“Construct Ray Model”的主要过程如下。对于每个客户端 \(R_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的更新变化历史。设 \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(i\) 上传的展平后的梯度变化向量。
+    对于每一轮 \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \))，我们将每个射线的起点表示为展平后的全局模型 \( \theta_g^{t'} \)，并将每个射线的方向向量表示为展平后的梯度变化 \( \overline{\triangledown\theta_{i}^{t'}} \)。因此，射线模型可以构建如下：
 
     \begin{equation}
-    \overline{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1}),
+    \widetilde{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1}),
     \end{equation}
@@
 
-    其中，\( \overline{\theta_{i}^{t'-1}} \) 是射线的起点，\( {v}_{i}^{t'} \) 是射线的方向向量。
-\end{itemize}
-
-“Minimum Enclosing Hypersphere Calculation”的主要过程如下。基于构建的射线模型，使用最小覆盖球算法找到一个能够覆盖至少 \( \zeta \) 比例的射线的最小超球。
-
-\begin{itemize}
-    \item 首先，设定初始球心 \( O_0 \) 为所有射线起点的几何中心，计算公式如下：
+    其中，\( \widetilde{\theta_{i}^{t'-1}} \) 是射线的起点，\( {v}_{i}^{t'} \) 是射线的方向向量。则射线方程为：
 
     \begin{equation}
-    O_0 = \frac{1}{T} \sum_{t'=\max\{t-T+1, 1\}}^{t} \overline{\theta_g^{t'-1}}.
+    l_i^{t'}=\widetilde{\theta_{i}^{t'-1}}+\alpha {v}_{i}^{t'},
     \end{equation}
 
-    \item 初始半径 \( r_0 \) 设定为从初始球心 \( O_0 \) 到所有射线起点的最大距离：
+    其中，$\alpha\in [0, +\infty)$为射线的自变量参数。
+
+“Minimum Enclosing Hypersphere Calculation”的主要过程如下。基于构建的射线模型，使用最小覆盖球算法找到一个能够覆盖至少 \( \zeta \) 比例的射线的最小超球。首先，设定初始球心 \( O_{i,0} \) 为所有射线起点的几何中心，计算公式如下：
 
 \begin{equation}
-    r_0 = \max_{t'=\max\{t-T+1, 1\}}^{t}  \|O_0 - \overline{\theta_{g}^{t'}}\|.
+    O_{i,0} = \frac{1}{T} \sum_{t'=\max\{t-T+1, 1\}}^{t} \widetilde{\theta_g^{t'-1}}.
 \end{equation}
 
-    \item 接下来，采用迭代方法来更新球心和半径：
-    \begin{itemize}
-
-        \item TODO: O上标  投影点是什么
-
-       \item 对于每次迭代 \( k \)，计算当前球心 \( O_k \) 到所有射线的最近投影点 \( \bar{O}_{i}^{t'} \)，按照距离当前球心的位置从小到大排序
+初始半径 \( r_{i,0} \) 设定为从初始球心 \( O_{i,0} \) 到所有射线起点的最大距离：
 
 \begin{equation}
-        \text{Sort}(\{ \| O - \overline{\theta_{i}^{t-T+1}} \| : i = 1, 2, \ldots, T \})
+r_{i,0} = \max_{t'=\max\{t-T+1, 1\}}^{t}  \|O_{i,0} - \widetilde{\theta_{g}^{t'-1}}\|.
 \end{equation}
 
-        并计算这些投影点的最大距离 \( D_k \)：
+接下来，采用迭代方法来更新球心和半径：
+
+对于每次迭代 \( k \)，计算当前球心 \( O_{i,k} \) 到所有射线的最近点 \( \tilde{O}_{i,k}^{t'} \)。对于每个节点$R_i$的第$t'(\max\{t-T+1, 1\}\leq  t'\leq t)$轮，对于射线 \( l_i^{t'} \)，找到球心 \( O_{i,k} \) 与当前射线的投影点 \( \hat O_{i,k}^{t'} \)，并计算参数 \( \alpha_k \)：
 
     \begin{equation}
-        D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{i}^{t-j}\|.
+    \alpha_k = \frac{(O_{i,k} - \widetilde{\theta_{i}^{t'-1}}) \cdot {v}_{i}^{t'}}{{v}_{i}^{t'}\cdot {v}_{i}^{t'}},
+    \end{equation}
+    则最近点 \( \tilde O_{i,k}^{t'} =\widetilde{\theta_{i}^{t'-1}}+\max \left\{ 0, \alpha_k\right\} {v}_{i}^{t'} \)。
+
+    计算当前球心 \( O_{i,k} \) 到这些最近点 \( \tilde O_{i,k}^{t'} \) 的距离集合 \( Dis_{i,k}= \{ \| O_{i,k}-\tilde O_{i,k}^{t'} \|, \max\{t-T+1, 1\}\leq  t'\leq t\} \)，并按从小到大的顺序进行排序，然后暂时舍弃$1-\zeta$比例的射线来忽略离群点对计算过程的影响，得到集合${Dis}_{i,k}'$，保留射线对应轮次的集合记为$\tilde T$。将球心向着被保留的最近点中距离最远的点$\tilde{O}_{i,k}^{t_{max}'}$移动：
+    % ，$ {Dis}_{i,k}'=\text{Sort}(Dis_{i,k})$。
+        % 并计算这些投影点的最大距离 \( D_k \)：
+
+        % \begin{equation}
+        % D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{i}^{t-j}\|.
+        % \end{equation}
+
+    \begin{equation}
+    O_{i,k+1} = O_{i,k} + \eta' (\tilde{O}_{i,k}^{t_{max}'}-O_{i,k}),
+    \end{equation}
+
+    其中$\eta'$为学习率。移动后的球心半径为：
+
+        \begin{equation}
+        r_{i,k+1} =  \{ \max\{\| O_{i,k+1}-\tilde O_{i,k+1}^{t'} \|\}, t'\in \tilde T\} ,
+        \end{equation}
+
+    其中$\tilde O_{i,k+1}^{t'}$为更新后的球心$O_{i,k+1}$到被保留射线的最近点。终止条件：当更新后的半径 \( r_{i,k+1} \) 与上一次的半径 \( r_{i,k} \) 相差小于一个预设的阈值 \( \lambda \)，或者达到预设的最大迭代次数$k_{max}$时，停止迭代。这部分可以定义为一个有约束的最优化问题：
+
+\begin{equation}
+\min_{O_i, r_i} \quad r_i
 \end{equation}
@@
 \begin{equation} 
-        O_{k+1} = O_k + \alpha \left(\frac{1}{\lceil n\times \varepsilon\rceil} \sum_{1\leq j\leq \lceil n\times \varepsilon\rceil} (Q_{i}^{t-j} - O_k)\right),
+\text{s.t.} \quad \left| \left\{ t' \mid \| O_i - \tilde{O}_{i}^{t'} \| \leq r_i \right\} \right| \geq \zeta T.
 \end{equation}
+% \begin{equation} 
+% \quad |r_{i,k+1} - r_{i,k}| < \lambda \quad \text{or} \quad k \geq k_{max}
+% \end{equation}
 
-        \begin{equation}
-        r_{k+1} = D_k,
-        \end{equation}
+% \textbf{约束条件:}
 
-        其中，\( \alpha \) 是学习率，通常取一个小的正数（如 0.1）。
-    \end{itemize}
-    \item 终止条件：当更新后的半径 \( r_{k+1} \) 与上一次的半径 \( r_k \) 相差小于一个预设的阈值 \( \epsilon \)（如 \( 10^{-6} \)），或者达到预设的最大迭代次数时，停止迭代。
-\end{itemize}
+% 对于每个射线 $l_i^{t'}$，计算球心 $O$ 到射线的最近点 $\tilde{O}_{i}^{t'}$ 的距离。最近点的计算公式为:
 
-这部分可以定义为一个有约束的最优化问题：
+% \[
+% \tilde{O}_{i}^{t'} = \widetilde{\theta_{i}^{t'-1}} + \max \left\{ 0, \frac{(O - \overline{\theta_{i}^{t'-1}}) \cdot {v}_{i}^{t'}}{{v}_{i}^{t'} \cdot {v}_{i}^{t'}} \right\} {v}_{i}^{t'}
+% \]
 
-\begin{equation}
-\min_{O, r} \, r 
-\end{equation}
-$$
-\text{s.t.} \quad \| O - (\overline{\theta_{i}^{t-T+1}} + t_i \mathbf{d}_i) \|^2 \leq r^2, \, 1\leq i\leq \lceil n \times \varepsilon \rceil
-$$
+% 约束球的半径 $r$ 使其能够覆盖至少 $\zeta$ 比例的射线:
+
+% \textbf{迭代更新规则:}
+
+% \[
+% O_{k+1} = O_k + \eta' (\tilde{O}_{i,k}^{t_M'} - O_k), \quad r_{k+1} = \max_{t' \in \tilde T} \| O_{k+1} - \tilde{O}_{i,k+1}^{t'} \|
+% \]
+
+% 其中 $\tilde T$ 是保留的射线集合，满足覆盖至少 $\zeta$ 比例的射线，$\eta'$ 为学习率。
+
+% \textbf{终止条件:}
+
+% \[
+% \text{s.t.} \quad |r_{k+1} - r_k| < \lambda \quad \text{or} \quad k \geq \text{MaxIter},
+% \]
+
+% 其中 $\lambda$ 为预设的收敛阈值，$\text{MaxIter}$ 是最大迭代次数。
+
+% \begin{equation}
+% \min_{O_i, r_i} \, r_i 
+% \end{equation}
+% $$
+% \text{s.t.} \quad \| O_i - \tilde O_{i}^{t'}\|^2\leq r_i^2 \,
+% $$
+% $$
+% 1\leq t'\leq \lceil n \times \varepsilon \rceil
+% $$
 
@@
 
-“Abnormal Detection”的主要过程基于局部离群因子（Local Outlier Factor, LOF）计算，并结合“最小覆盖球”得出的置信度来调整 LOF 分数。异常检测的目标是识别出异常的客户端，确保联邦学习过程中的全局模型安全性和鲁棒性。其主要流程如算法14-24行所示。
+“Abnormal Detection”的主要过程基于局部离群因子（Local Outlier Factor, LOF）得到异常点。LOF算法是一种基于密度的异常检测方法，算法的核心思想是通过计算一个数值$lof_i$来反应节点$i$的异常程度。$lof_i$大致意思是节点$i$目的意图点$O_i$周围意图点所处位置的平均密度比上$O_i$所在位置的密度。比值越大于$1$，则$O_i$所在位置的密度越小于周围其他意图点所在位置的密度，即$O_i$越有可能是异常点。首先定义意图点$O_i$的$\kappa$距离$\widetilde{dis_i^\kappa}$，假设高维空间中存在节点$j$的意图点$O_j$，则有$O_j$与$O_i$之间的距离为$\|O_i-O_j\|$，如果满足以下两个条件，我们就认为$\widetilde{dis_i^\kappa}=\|O_i-O_j\|$：
 
 \begin{itemize}
-    \item 首先，计算局部离群因子（LOF）。对于一个样本点 \(x_i\)，其局部可达密度（Local Reachability Density, LRD）定义为其相对于 \(\varepsilon\)-邻域内点的平均可达距离的倒数：
+    \item 在样本空间中，至少存在$\kappa$个意图点$O_j'$，使得$\|O_i-O_j'\|\leq \|O_i-O_j\|$, 其中$j'\neq i$；
+    \item 在样本空间中，至多存在$\kappa-1$个意图点$O_j'$，使得$\|O_i-O_j'\|< \|O_i-O_j\|$, 其中$j'\neq i$。
+\end{itemize}
+
+总的来说，$O_i$的$\kappa$距离$\widetilde{dis_i^\kappa}$表示高维空间中距离第$\kappa$远的点。之后定义意图点$O_i$的第$\kappa$距离邻域$Nei_i$为到$O_i$距离不超过$\widetilde{dis_i^\kappa}$的所有意图点的集合。由于可能同时存在多个第$\kappa$距离的数据，所以$|Nei_i|\geq \kappa$。可以想象，离群度越大的意图点的$\kappa$距离往往较大，离群度越小的意图点的$\kappa$距离往往较小。之后定义意图点$O_i$相对于意图点$O_j$的可达距离：
 
 \begin{equation}
-    \text{LRD}(x_i) = \frac{1}{\frac{1}{\varepsilon} \sum_{x_j \in \mathcal{N}_\varepsilon(x_i)} \text{reach-dist}_\varepsilon(x_i, x_j)},
+rea_{i,j}=\max\{\widetilde{dis_i^\kappa}, \|O_i-O_j\|\},
 \end{equation}
 
-    其中，\(\text{reach-dist}_\varepsilon(x_i, x_j)\) 是点 \(x_i\) 到其邻居 \(x_j\) 的可达距离，定义为：
+也就是说，如果意图点$O_j$远离意图点$O_i$，则两者之间的可达距离就是他们之间的实际距离$\|O_i-O_j\|$；而如果二者距离足够近，则可达距离用意图点$O_i$的$\kappa$距离$\widetilde{dis_i^\kappa}$代替。之后定义意图点$O_i$的局部可达密度$lrd_i$为其$Nei_i$所有意图点的平均可达距离的倒数，即：
 
 \begin{equation}
-    \text{reach-dist}_\varepsilon(x_i, x_j) = \max(\text{dist}(x_i, x_j), \varepsilon\text{-dist}(x_j)),
+lrd_i=1/(\frac{\sum_{j\in Nei_i} rea_{i,j}}{|Nei_i|})
 \end{equation}
 
-    这里，\(\eta\varepsilon\text{-dist}(x_j)\) 表示点 \(x_j\) 到其第 \(\varepsilon\) 个最近邻的距离。
-
-    \item 对于点 \(x_i\)，其局部离群因子（LOF）定义为其邻域内所有点的局部可达密度与自身局部可达密度的比值的平均值：
+此时，若有重复点，则可能导致$lrd$变为无限大。$lrd_i$的可以理解为意图点$O_i$所处位置的密度，密度越高则意图点$O_i$越有可能属于同一簇，密度越低则意图点$O_i$越有可能是离群点。也就是说，如果意图点$O_i$和周围邻域点是同一簇，则可达距离可能为较小的$\widetilde{dis_i^\kappa}$，导致可达距离之和较小，密度值较高；如果$O_i$和周围邻居意图点较远，则可达距离可能会取较大的$\|O_i-O_j\|$，导致可达距离之和较大，密度值较低，越有可能是离群点。最后，我们定义意图点$O_i$的局部离群因子$lof_i$为其$Nei_i$所有意图点的局部可达密度与其自身局部可达密度的比值的平均值，即：
 
 \begin{equation}
-    \text{LOF}(x_i) = \frac{1}{\varepsilon} \sum_{x_j \in \mathcal{N}_\varepsilon(x_i)} \frac{\text{LRD}(x_j)}{\text{LRD}(x_i)}.
+    lof_i=\frac{\sum_{j\in Nei_i}\frac{lrd_j}{lrd_i}}{|Nei_i|}=\frac{\sum_{j\in Nei_i} lrd_j}{|Nei_i|\cdot lrd_i}
 \end{equation}
 
-    \item 接下来，基于“最小覆盖球”方法计算得到的置信度来调整 LOF 分数。假设通过“最小覆盖球”算法得到了客户端 \(i\) 的最小覆盖球半径 \(r_i\)，定义置信度 \(C_i\) 为半径的倒数：
+如果$lof_i$比较接近$1$，则说明意图点$O_i$与其邻域点密度差不多，$O_i$可能和邻域属于同一簇；如果$lof_i$小于$1$，则说明意图点$O_i$的密度高于其邻域点的密度，$O_i$为密集点；如果$lof_i$大于$1$，则说明意图点$O_i$的密度低于其邻域点的密度，$O_i$可能是离群点。总之，LOF算法主要通过比较每个意图点$O_i$和其邻域点的密度来判断$O_i$是否为离群点，密度越低，则越有可能是离群点。而密度主要是通过点之间的距离来计算的，点之间的距离越远密度越低，距离越近密度越高。
 
-    \begin{equation}
-    C_i = \frac{1}{r_i + \epsilon},
-    \end{equation}
+计算每个节点$i$的局部离群因子$lof_i$，将$lof_i$大于$1$的客户端视为异常客户端，并将其梯度丢弃。
 
-    其中，\(\epsilon\) 是一个很小的正数，用于避免除零错误。
+% \begin{itemize}
+%     \item 首先，计算局部离群因子（LOF）。对于一个样本点 \(x_i\)，其局部可达密度（Local Reachability Density, LRD）定义为其相对于 \(\varepsilon\)-邻域内点的平均可达距离的倒数：
 
-    \item 使用置信度 \(C_i\) 的倒数来调整 LOF 分数，使得置信度越高的点，其调整后的 LOF 分数越低：
+%     \begin{equation}
+%     \text{LRD}(x_i) = \frac{1}{\frac{1}{\varepsilon} \sum_{x_j \in \mathcal{N}_\varepsilon(x_i)} \text{reach-dist}_\varepsilon(x_i, x_j)},
+%     \end{equation}
 
-    \begin{equation}
-    \text{adjusted\_lof}(x_i) = \text{LOF}(x_i) \times (r_i + \epsilon).
-    \end{equation}
+%     其中，\(\text{reach-dist}_\varepsilon(x_i, x_j)\) 是点 \(x_i\) 到其邻居 \(x_j\) 的可达距离，定义为：
 
-    \item 计算调整后的 LOF 分数的均值 \(\mu_{\text{adjusted\_lof}}\) 和标准差 \(\sigma_{\text{adjusted\_lof}}\)，然后使用以下公式设置阈值 \(\tau'\)：
+%     \begin{equation}
+%     \text{reach-dist}_\varepsilon(x_i, x_j) = \max(\text{dist}(x_i, x_j), \varepsilon\text{-dist}(x_j)),
+%     \end{equation}
 
-    \begin{equation}
-    \tau' = \mu_{\text{adjusted\_lof}} + k \times \sigma_{\text{adjusted\_lof}},
-    \end{equation}
+%     这里，\(\eta\varepsilon\text{-dist}(x_j)\) 表示点 \(x_j\) 到其第 \(\varepsilon\) 个最近邻的距离。
 
-    其中，\(k\) 是一个\textbf{敏感性系数}（sensitivity coefficient），其选择对异常检测的结果具有重要影响。为了在精确度与召回率之间取得平衡，\(k\) 的值应通过\textbf{基于数据驱动的交叉验证策略}来确定。具体而言，可以在训练集中使用不同的 \(k\) 值进行多次迭代，计算每种情况下的检测性能指标（如精确度、召回率和 F1 分数），并通过优化这些指标选择最优的 \(k\) 值。此外，选择 \(k\) 时也可以考虑使用贝叶斯优化（Bayesian Optimization）等先进的超参数调优方法，以自适应地选择最能反映数据特征的敏感性系数值。对于检测结果中大于该阈值的点，将其判定为异常点。
-\end{itemize}
+%     \item 对于点 \(x_i\)，其局部离群因子（LOF）定义为其邻域内所有点的局部可达密度与自身局部可达密度的比值的平均值：
+
+%     \begin{equation}
+%     \text{LOF}(x_i) = \frac{1}{\varepsilon} \sum_{x_j \in \mathcal{N}_\varepsilon(x_i)} \frac{\text{LRD}(x_j)}{\text{LRD}(x_i)}.
+%     \end{equation}
+
+%     \item 接下来，基于“最小覆盖球”方法计算得到的置信度来调整 LOF 分数。假设通过“最小覆盖球”算法得到了客户端 \(i\) 的最小覆盖球半径 \(r_i\)，定义置信度 \(C_i\) 为半径的倒数：
+
+%     \begin{equation}
+%     C_i = \frac{1}{r_i + \epsilon},
+%     \end{equation}
+
+%     其中，\(\epsilon\) 是一个很小的正数，用于避免除零错误。
+
+%     \item 使用置信度 \(C_i\) 的倒数来调整 LOF 分数，使得置信度越高的点，其调整后的 LOF 分数越低：
+
+%     \begin{equation}
+%     \text{adjusted\_lof}(x_i) = \text{LOF}(x_i) \times (r_i + \epsilon).
+%     \end{equation}
+
+%     \item 计算调整后的 LOF 分数的均值 \(\mu_{\text{adjusted\_lof}}\) 和标准差 \(\sigma_{\text{adjusted\_lof}}\)，然后使用以下公式设置阈值 \(\tau'\)：
+
+%     \begin{equation}
+%     \tau' = \mu_{\text{adjusted\_lof}} + k \times \sigma_{\text{adjusted\_lof}},
+%     \end{equation}
+
+%     其中，\(k\) 是一个\textbf{敏感性系数}（sensitivity coefficient），其选择对异常检测的结果具有重要影响。为了在精确度与召回率之间取得平衡，\(k\) 的值应通过\textbf{基于数据驱动的交叉验证策略}来确定。具体而言，可以在训练集中使用不同的 \(k\) 值进行多次迭代，计算每种情况下的检测性能指标（如精确度、召回率和 F1 分数），并通过优化这些指标选择最优的 \(k\) 值。此外，选择 \(k\) 时也可以考虑使用贝叶斯优化（Bayesian Optimization）等先进的超参数调优方法，以自适应地选择最能反映数据特征的敏感性系数值。对于检测结果中大于该阈值的点，将其判定为异常点。
+% \end{itemize}
 
@@
 
-在上一步已经剔除了恶意客户端后，本部分将使用主观逻辑模型（Subjective Logic Model）进行剩余客户端的梯度聚合。主观逻辑模型是一种基于概率论和信任度的数学框架，能够有效地处理不确定性和不一致性信息。在联邦学习场景中，主观逻辑模型可以用于在不完全信任的环境下对客户端上传的梯度进行加权聚合，从而提高全局模型的稳健性。其主要流程如算法25-29行所示。
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig5-before-agg.jpg}
+    \caption{Benign and Malicious Nodes Before Aggregation}
+    \label{fig:before-agg}
+\end{figure}
 
-\begin{itemize}
-    \item \textbf{定义主观逻辑模型的信任参数}：
-
-    对于每个被认为是正常的客户端 \( C_i \)，根据其上传的梯度更新 \( \triangledown \theta_i \)，定义主观逻辑模型中的信任参数，包括\textbf{信任度}（Belief）、\textbf{不信任度}（Disbelief）和\textbf{不确定度}（Uncertainty）。信任度 \( b_i \) 可以根据每个客户端的历史表现或其他统计指标来定义。对于本次的应用，信任度可以与上一步异常检测中调整后的 LOF 分数成反比。
-
-    \item \textbf{计算每个客户端的证据权重}：
-
-    基于定义的信任参数，为每个客户端 \( C_i \) 计算其证据权重 \( w_i \)。证据权重可以表示为信任度 \( b_i \) 的函数形式，例如：\( w_i = f(b_i) \)，其中 \( f(b_i) \) 可以是线性或非线性的映射函数。
-
-    \item \textbf{加权聚合客户端梯度}：
-
-    使用证据权重 \( w_i \) 对所有正常客户端的梯度更新 \( \triangledown \theta_i \) 进行加权聚合，以得到全局模型的梯度更新：
+剔除了异常节点后，依据正常节点的置信度$cre$进行聚合。其中定义：
 
 \begin{equation}
-    \triangledown \theta_{\text{global}} = \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i
+    cre_i=\frac{1}{r_i+\rho},
 \end{equation}
 
-    其中，\( U_{nor} \) 是所有被判定为正常的客户端集合。
+$\rho$是一个很小的正数，以防分母为$0$。
 
-    \item \textbf{更新全局模型}：
+如图\ref{fig:before-agg}所示，使用LOF算法识别恶意客户端可以剔除潜在的恶意节点，但是在正常的节点中，同样存在一些置信度很低的节点。这些节点的最小覆盖球甚至可能和异常节点有一定交集。因此，在聚合的过程中，这些置信度较低的点所占的权重就应该越低。
 
-    使用聚合后的梯度更新全局模型参数，以继续下一轮的联邦学习迭代。
-\end{itemize}
+试想，假设有两个节点的最小覆盖超球的半径都很小，但是相差倍数很高，那么它们计算出来的置信度相差倍数也会很高。但其实它们的意图点都十分明确，因此权重应该都比较高且相差不应很大。所以我们可以使用激活函数Tanh来对置信度进行加权处理：
 
-通过使用主观逻辑模型对客户端梯度进行聚合，能够有效利用信任度信息来优化全局模型的更新过程，减少因恶意客户端或不确定性导致的模型偏差。
+\begin{equation}
+    cre_i'=\tanh(cre_i),
+\end{equation}
+
+激活函数Tanh在$0$到$\infty$范围内是一个上升又快到慢的单调递增函数。当$cre_i\to 0$时$cer_i'\to 0$，也就是说节点$i$的最小覆盖球半径$r_i$很大时该节点在聚合时的权重很小；当$cre_i\to \infty$时$cer_i'\to 1$，也就是说节点$i$的最小覆盖球半径$r_i$很小时该节点在聚合时的权重较大。这样，我们就可以对每个加权处理过的置信度$cer_i'$进行归一化处理，得到权重$w_i$。其中：
+
+\begin{equation}
+    w_i=\frac{cre_i'}{\sum_{i=1}^{n}cre_i'},
+\end{equation}
+
+因此第$t$轮模型的梯度聚合公式为：
+
+\begin{equation}
+    \theta_g^t = \theta_g^{t-1}+\sum_{i=1}^{n}w_i\triangledown \theta_i^t,
+\end{equation}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{results/prob-history-Visualization of Client Intentions and Anomalies.png}
+    \caption{使用模拟数据得到的结果}
+    \label{fig:result-of-histry}
+\end{figure}
+
+% 在上一步已经剔除了恶意客户端后，本部分将使用主观逻辑模型（Subjective Logic Model）进行剩余客户端的梯度聚合。主观逻辑模型是一种基于概率论和信任度的数学框架，能够有效地处理不确定性和不一致性信息。在联邦学习场景中，主观逻辑模型可以用于在不完全信任的环境下对客户端上传的梯度进行加权聚合，从而提高全局模型的稳健性。其主要流程如算法25-29行所示。
+
+% \begin{itemize}
+%     \item \textbf{定义主观逻辑模型的信任参数}：
+
+%     对于每个被认为是正常的客户端 \( C_i \)，根据其上传的梯度更新 \( \triangledown \theta_i \)，定义主观逻辑模型中的信任参数，包括\textbf{信任度}（Belief）、\textbf{不信任度}（Disbelief）和\textbf{不确定度}（Uncertainty）。信任度 \( b_i \) 可以根据每个客户端的历史表现或其他统计指标来定义。对于本次的应用，信任度可以与上一步异常检测中调整后的 LOF 分数成反比。
+
+%     \item \textbf{计算每个客户端的证据权重}：
+
+%     基于定义的信任参数，为每个客户端 \( C_i \) 计算其证据权重 \( w_i \)。证据权重可以表示为信任度 \( b_i \) 的函数形式，例如：\( w_i = f(b_i) \)，其中 \( f(b_i) \) 可以是线性或非线性的映射函数。
+
+%     \item \textbf{加权聚合客户端梯度}：
+
+%     使用证据权重 \( w_i \) 对所有正常客户端的梯度更新 \( \triangledown \theta_i \) 进行加权聚合，以得到全局模型的梯度更新：
+
+%     \begin{equation}
+%     \triangledown \theta_{\text{global}} = \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i
+%     \end{equation}
+
+%     其中，\( U_{nor} \) 是所有被判定为正常的客户端集合。
+
+%     \item \textbf{更新全局模型}：
+
+%     使用聚合后的梯度更新全局模型参数，以继续下一轮的联邦学习迭代。
+% \end{itemize}
+
+% 通过使用主观逻辑模型对客户端梯度进行聚合，能够有效利用信任度信息来优化全局模型的更新过程，减少因恶意客户端或不确定性导致的模型偏差。
 \end{enumerate}
@@
 
-% 这些攻击都难以检测，但是不论其方式再怎么千变万化，最终一定要达到攻击者所想达到的目标。我们对训练过程进行建模，每次中央服务器下发的模型视为高维空间中的一个点，而客户端训练后上传的梯度视为从这个点出发的一个向量。这样，对于每个客户端，我们就可以得到个有很多具有起点的向量的图。由于梯度是诱导模型变换的方向，因此攻击者若想要达到攻击目的，不论其攻击过程有多么地曲折和隐蔽，其所有向量最终指向的目的区域一定是和良性客户端不同的。我们将这些高维空间中具有起点的绝大多数向量的目的汇聚区域称为“汇聚点”。在允许一定返回的离群值的前提下，我们有理由认为一个客户端的汇聚点就是这个客户端的最终目的。因此问题就变成了如何寻找高维空间中多条具有起点的向量的汇聚点了。TODO: 精美图一张。
+% 这些攻击都难以检测，但是不论其方式再怎么千变万化，最终一定要达到攻击者所想达到的目标。我们对训练过程进行建模，每次中央服务器下发的模型视为高维空间中的一个点，而客户端训练后上传的梯度视为从这个点出发的一个向量。这样，对于每个客户端，我们就可以得到个有很多具有起点的向量的图。由于梯度是诱导模型变换的方向，因此攻击者若想要达到攻击目的，不论其攻击过程有多么地曲折和隐蔽，其所有向量最终指向的目的区域一定是和良性客户端不同的。我们将这些高维空间中具有起点的绝大多数向量的目的汇聚区域称为“汇聚点”。在允许一定返回的离群值的前提下，我们有理由认为一个客户端的汇聚点就是这个客户端的最终目的。因此问题就变成了如何寻找高维空间中多条具有起点的向量的汇聚点了。
 

### 2024-09-11 main-v2.tex
docs: my changes 昨日凌晨2:41
Signed-off-by: LetMeFly666 <814114971@qq.com>

--- 2024-08-16 main.tex
@@
 \usepackage{amsmath,amsfonts}
-% \usepackage{longtable}
-\usepackage{array}
 %\usepackage{algorithmic}
 %\usepackage{algorithm}
-% \usepackage[UTF8]{ctex}
 \usepackage{array}
-\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+\usepackage[caption=false,font=scriptsize,labelfont=sf,textfont=rm]{subfig}
 \usepackage{textcomp}
@@
 \usepackage{algpseudocode}
+\usepackage{makecell}
 
@@
 \usepackage{algorithm,algpseudocode,float}
-
+\makeatletter
+\newcommand{\rmnum}[1]{\romannumeral #1}
+\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
+\makeatother
 \begin{document}
 
-\title{SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Stealthy Poisoning Attacks in IoRT Networks}
+\title{SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Stealthy Backdoor Attacks in IoRT Networks}
 
 \author{Zan Zhou, %~\IEEEmembership{Student Member,~IEEE}, 
-Yirong Zhuang, Hongjing Li, Sizhe Huang, Shujie Yang, Peng Guo, Lujie Zhong, Zhenhui Yuan, Changqiao Xu,~\IEEEmembership{Senior Member,~IEEE}
+Yao Su, Shujie Yang, Bo Wang, Tengfei Li, Changqiao Xu,~\IEEEmembership{Senior Member,~IEEE}
 % <-this % stops a space
@@
 	}  % <-this % stops a space
-\thanks{Y. Zhuang is with the Research Institute of China Telecom, Ave Zhongshan, Guangzhou 510630, China. E-mail: 13316094433@chinatelecom.cn.}% <-this % stops a space
- \thanks{L. Zhong is with the Information Engineering College, Capital Normal University, Beijing 100048, China. E-mail: zhonglj@cnu.edu.cn (Corresponding author).}% <-this % stops a space
+%\thanks{Y. Zhuang is with the Research Institute of China Telecom, Ave Zhongshan, Guangzhou 510630, China. E-mail: 13316094433@chinatelecom.cn.}% <-this % stops a space
+% \thanks{L. Zhong is with the Information Engineering College, Capital Normal University, Beijing 100048, China. E-mail: zhonglj@cnu.edu.cn (Corresponding author).}% <-this % stops a space
 \thanks{Zhenhui Yuan is with Northumbria University, United Kingdom. E-mail: zhenhui.yuan@warwick.ac.uk.}% <-this % stops a space
@@
 \begin{abstract}
+
 Fairness-aware federated learning (FFL) plays a crucial role in mitigating bias against specific demographic groups (e.g., gender, race, occupation) during collaborative training. 
@@
 %作为的一种，
+
+%随着具身智能技术的迅猛进步和在智慧城市、智能交通、无人机等领域的广泛应用，机器人节点从执行等单一任务的agent，逐步向集合了感知交互和自主决策的智能体进行了演进，这也成为了未来IORT网络的重要发展趋势之一。而视觉大模型作为一种新兴热门的图像感知和物体识别技术，能够成为支撑智能机器人对周围环境进行认识和理解不可或缺的基础。
+With the rapid advancements in embodied intelligence technology and its widespread application in multiple areas such as smart cities, intelligent transportation, and unmanned aerial vehicles, robotic nodes have evolved from agents performing singular tasks to intelligent entities that integrate perception, interaction, and autonomous decision-making jointly.
+This evolution has become one of the critical developmental trends for Internet of Robotic Things (IoRT) networks.
+Large Vision Language Model (LVLM), as an emerging and popular image perception and object recognition technology, has the potential to be an indispensable foundation supporting intelligent robots in understanding and interpreting their surrounding environments.
+
+%视觉大模型极大地增强了机器人的视觉语义理解能力，使其能够对多模态任务进行更加智能化的决策响应，然而在真实应用环境中，仍存在以下问题：1）由于真实世界的多样性和异构性，通用大模型在特定任务上往往无法较好迁移通用知识，需要进行微调才能显著提升识别精度（例如，针对动目标检测任务，交通机器人主要针对车辆、行人，而工厂机器人则主要针对机床，两者轮廓、行为模式范围均存在较大差异）；2）此外，将来自不同源头的离散化、碎片化分布的海量数据进行传输并汇聚于主服务器，将会导致巨大的通信开销和时间延迟，无法满足具身智能业务的需求，且存在潜在的隐私风险。
+Vision foundation models significantly enhance the visual semantic understanding capabilities of robots, enabling them to make more intelligent decisions in multimodal tasks.
+However, there are still challenges in real-world applications: 1) Due to the diversity and heterogeneity of the real world, general foundation models often cannot effectively transfer their general knowledge to specific tasks, necessitating fine-tuning to significantly improve recognition accuracy (for example, traffic robots primarily focus on vehicles and pedestrians for moving object detection tasks, while factory robots mainly target machine tools, with significant differences in their contours and behavioral patterns); 2) Additionally, transmitting and aggregating massive amounts of discretized and fragmented data from different sources to a central server can result in significant communication overhead and latency, failing to meet the demands of embodied intelligence applications and posing potential privacy risks.
+
+%因此，如图1所示，在pretrained的通用视觉大模型的基础上，不同于核心节点汇聚所有数据而后训练垂域模型的集中式微调，通过联邦微调技术，驱使大量机器人节点利用私有数据和算力计算微调梯度而后聚合，能够在不交互原始数据的前提下，充分利用整个IORT网络中各个节点的知识和算力资源，成为了一种非常具有前景的解决方案。
+As illustrated in Fig.
+1, a promising solution is to employ federated fine-tuning (FFT) technology rather than adopting a centralized fine-tuning approach where core nodes aggregate all data before training domain-specific models.
+This approach drives numerous robotic nodes to compute fine-tuning gradients using private data and computational resources and then aggregate these gradients, effectively leveraging the knowledge and computational resources of each node in the IoRT network without exchanging raw data.
+
+%攻击识别
+Alongside the conti
+Spectral Distribution
+Consistency Verification
+Poisoning with 
+Detection
+
 As a preeminent collaborative artificial intelligence paradigm, Federated Learning (FL) has garnered substantial research focus \cite{ETT2}. 
@@
 Besides, we obtain a more comprehensive evaluation of credit, drastically mitigating the potential impact of adversarial behavior.
+
 %服务器基于本轮综合信用评分选择客户参与下一轮次的训练，为了尽可能地提高客户的参与率，得到更全面、完整的客户信誉评估结果，将综合信誉作为客户属性进行持久化存储，服务器将赋予客户乐观的初始综合信誉并在每轮交互中更新客户的最新综合信誉。
@@
 
-%%%%%%%%%%%%EMNIST+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-\centering
-\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_MINIST_cr_1.pdf}%
-\label{result1:credit-AAD}}
-\hfil
-\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_MINIST_pr_1.pdf}%
-\label{result1:prob-AAD}}
-\hfil
-\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_MINIST_cr_1.pdf}%
-\label{result1:credit-FLtrust}}
-\hfil
-\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_MINIST_pr_1.pdf}%
-\label{result1:prob-FLtrust}}
-\hfil
-\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_MINIST_cr_1.pdf}%
-\label{result1:credit-MRFFL}}
-\hfil
-\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_Flip_MINIST_pr_1.pdf}%
-\label{result1:prob-MRFFL}}
-\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on EMNIST.}
-\label{results_EMNIST_flip}
-\end{figure}
-
-%%%%%%%%%%%EMNIST+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-\centering
-\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_MINIST_cr_1.pdf}%
-\label{result2:credit-AAD}}
-\hfil
-\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_MINIST_pr_1.pdf}%
-\label{result2:prob-AAD}}
-\hfil
-\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_MINIST_cr_1.pdf}%
-\label{result2:credit-FLtrust}}
-\hfil
-\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_MINIST_pr_1.pdf}%
-\label{result2:prob-FLtrust}}
-\hfil
-\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_MINIST_cr_1.pdf}%
-\label{result2:credit-MRFFL}}
-\hfil
-\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_BACKDOOR_MINIST_pr_1.pdf}%
-\label{result2:prob-MRFFL}}
-\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on EMNIST.}
-\label{results_EMNIST_Backdoor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%CIFAR+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-\centering
-\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_Cifar_cr_1.pdf}%
-\label{result3:credit-AAD}}
-\hfil
-\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_Cifar_pr_1.pdf}%
-\label{result3:prob-AAD}}
-\hfil
-\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_Cifar_cr_1.pdf}%
-\label{result3:credit-FLtrust}}
-\hfil
-\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_Cifar_pr_1.pdf}%
-\label{result3:prob-FLtrust}}
-\hfil
-\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_Cifar_cr_1.pdf}%
-\label{result3:credit-MRFFL}}
-\hfil
-\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_Flip_Cifar_pr_1.pdf}%
-\label{result3:prob-MRFFL}}
-\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on CIFAR.}
-\label{results_Cifar_flip}
-\end{figure}
-%%%%%%%%%%%CIFAR+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-\centering
-\subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_Cifar_cr_1.pdf}%
-\label{result4:credit-AAD}}
-\hfil
-\subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_Cifar_pr_1.pdf}%
-\label{result4:prob-AAD}}
-\hfil
-\subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_Cifar_cr_1.pdf}%
-\label{result4:credit-FLtrust}}
-\hfil
-\subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_Cifar_pr_1.pdf}%
-\label{result4:prob-FLtrust}}
-\hfil
-\subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_Cifar_cr_1.pdf}%
-\label{result4:credit-MRFFL}}
-\hfil
-\subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_BACKDOOR_Cifar_pr_1.pdf}%
-\label{result4:prob-MRFFL}}
-\caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on CIFAR.}
-\label{results_Cifar_Backdoor}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%EMNIST+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[!t]
+% \centering
+% \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_MINIST_cr_1.pdf}%
+% \label{result1:credit-AAD}}
+% \hfil
+% \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_MINIST_pr_1.pdf}%
+% \label{result1:prob-AAD}}
+% \hfil
+% \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_MINIST_cr_1.pdf}%
+% \label{result1:credit-FLtrust}}
+% \hfil
+% \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_MINIST_pr_1.pdf}%
+% \label{result1:prob-FLtrust}}
+% \hfil
+% \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_MINIST_cr_1.pdf}%
+% \label{result1:credit-MRFFL}}
+% \hfil
+% \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_Flip_MINIST_pr_1.pdf}%
+% \label{result1:prob-MRFFL}}
+% \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on EMNIST.}
+% \label{results_EMNIST_flip}
+% \end{figure}
+
+% %%%%%%%%%%%EMNIST+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[!t]
+% \centering
+% \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_MINIST_cr_1.pdf}%
+% \label{result2:credit-AAD}}
+% \hfil
+% \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_MINIST_pr_1.pdf}%
+% \label{result2:prob-AAD}}
+% \hfil
+% \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_MINIST_cr_1.pdf}%
+% \label{result2:credit-FLtrust}}
+% \hfil
+% \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_MINIST_pr_1.pdf}%
+% \label{result2:prob-FLtrust}}
+% \hfil
+% \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_MINIST_cr_1.pdf}%
+% \label{result2:credit-MRFFL}}
+% \hfil
+% \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_BACKDOOR_MINIST_pr_1.pdf}%
+% \label{result2:prob-MRFFL}}
+% \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on EMNIST.}
+% \label{results_EMNIST_Backdoor}
+% \end{figure}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%CIFAR+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[!t]
+% \centering
+% \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_Cifar_cr_1.pdf}%
+% \label{result3:credit-AAD}}
+% \hfil
+% \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_Cifar_pr_1.pdf}%
+% \label{result3:prob-AAD}}
+% \hfil
+% \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_Cifar_cr_1.pdf}%
+% \label{result3:credit-FLtrust}}
+% \hfil
+% \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_Cifar_pr_1.pdf}%
+% \label{result3:prob-FLtrust}}
+% \hfil
+% \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_Cifar_cr_1.pdf}%
+% \label{result3:credit-MRFFL}}
+% \hfil
+% \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_Flip_Cifar_pr_1.pdf}%
+% \label{result3:prob-MRFFL}}
+% \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on CIFAR.}
+% \label{results_Cifar_flip}
+% \end{figure}
+% %%%%%%%%%%%CIFAR+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[!t]
+% \centering
+% \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_Cifar_cr_1.pdf}%
+% \label{result4:credit-AAD}}
+% \hfil
+% \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_Cifar_pr_1.pdf}%
+% \label{result4:prob-AAD}}
+% \hfil
+% \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_Cifar_cr_1.pdf}%
+% \label{result4:credit-FLtrust}}
+% \hfil
+% \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_Cifar_pr_1.pdf}%
+% \label{result4:prob-FLtrust}}
+% \hfil
+% \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_Cifar_cr_1.pdf}%
+% \label{result4:credit-MRFFL}}
+% \hfil
+% \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_BACKDOOR_Cifar_pr_1.pdf}%
+% \label{result4:prob-MRFFL}}
+% \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on CIFAR.}
+% \label{results_Cifar_Backdoor}
+% \end{figure}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \section*{Acknowledgments}
-This work is partially supported by the National Natural Science Foundation of China (NSFC) under Grant 62225105 and the ZhejiangLab Open Research Project (No. K2022QA0AB05).
+This work is partially supported by China Postdoctoral Science Foundation (grant No.
+2024M750259), Beijing Natural Science Foundation (grant No.
+4244084), National Natural Science Foundation of China (grant No.
+62401075, 62394322).
 
@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[width=\linewidth]{figures/fig4-history.jpg}
+\caption{Combining multiple rounds of historical identification to identify malicious nodes
+}
+\label{fig4:history}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=\linewidth]{img/SecFFT-场景.pdf}
+\caption{Combining multiple rounds of historical identification to identify malicious nodes
+}
+\label{fig4:history}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=\linewidth]{img/SecFFT-算法1.pdf}
+\caption{Combining multiple rounds of historical identification to identify malicious nodes
+}
+\label{fig4:history}
+\end{figure}
+
 \end{document}

### 2024-09-11 temp.yjxt.changeCourse.js

@@ -1,18 +1,0 @@
-/*
- * @Author: LetMeFly
- * @Date: 2024-09-02 11:39:20
- * @LastEditors: LetMeFly
- * @LastEditTime: 2024-09-02 12:06:32
- */
-// 培养 -> 课程和环节完成查询
-tbody = document.querySelector("#contentParent_dgData > tbody")
-trs =  [].slice.apply(tbody.querySelectorAll('tr'))
-trs.shift()
-for (let i = 0; i < trs.length; i++) {
-    tr = trs[i]
-    ths = tr.querySelectorAll('td')
-    ths[3].innerText = '123456' + `${i + 1}`.padStart(2, '0')
-    ths[3].innerText = `课程名${i + 1}`
-    ths[3].innerText = 100
-}
-// 然后发现表格每一行td个数不一样，算了

### 2024-09-11 FL_Backdoor_CV/roles/aggregation_rules.py
secfft

@@ -29,7 +29,9 @@ from scipy.fftpack import dct
 def secfft(model_updates):
     updates = torch.cat(list(model_updates.values()), dim=1)  # 整合模型更新
 
-    updates_dct = dct(updates, type=2, axis=1, norm="ortho")  # 离散余弦变换（DCT）
+    updates_dct = dct(
+        updates.cpu().numpy(), type=2, axis=1, norm="ortho"
+    )  # 离散余弦变换（DCT）
     device = args.device
     updates_dct = torch.tensor(updates_dct[:, :20000], device=device)  # 提取低频成分
 

### 2024-09-11 FL_Backdoor_CV/roles/server.py

@@ -25,6 +25,7 @@ from FL_Backdoor_CV.roles.aggregation_rules import foolsgold
 from FL_Backdoor_CV.roles.aggregation_rules import flame
 from FL_Backdoor_CV.roles.aggregation_rules import fltrust
 from FL_Backdoor_CV.roles.aggregation_rules import robust_lr
+from FL_Backdoor_CV.roles.aggregation_rules import secfft
 
 import pickle
 
@@ -357,7 +358,9 @@ class Server:
 
         # === aggregate ===
         global_update = None
-        if args.aggregation_rule.lower() == "avg":
+        if args.aggregation_rule.lower() == "secfft":
+            global_update = secfft(model_updates)
+        elif args.aggregation_rule.lower() == "avg":
             global_update = avg(model_updates)
         # elif args.aggregation_rule.lower() == 'fedcie':
         #     global_update = Server.fedcie(model_updates, previous_model_update, last_model_params)

### 2024-09-11 configs.py

@@ -65,7 +65,16 @@ parser.add_argument(
     "--aggregation_rule",
     default="avg",
     type=str,
-    choices=["avg", "rlr", "flame", "foolsgold", "roseagg", "fltrust", "fedcie"],
+    choices=[
+        "avg",
+        "rlr",
+        "flame",
+        "foolsgold",
+        "roseagg",
+        "fltrust",
+        "fedcie",
+        "secfft",
+    ],
     help="aggregation method",
 )
 

### 2024-09-11 trainer.py

@@ -223,7 +223,7 @@ class Trainer:
             start_time = time.time()
             # === participants selection phase ===
             self.server.select_participants()
-            self.participants[cur_round] = self.server.self.participants
+            self.participants[cur_round] = self.server.participants
             # === training and aggregating phase ===
             self.server.train_and_aggregate(
                 global_lr=args.global_lr, round=cur_round, root_path=file_path

### 2024-09-12 configs.py
t-sne

@@ -2,7 +2,7 @@ import argparse
 
 parser = argparse.ArgumentParser(description="PPDL")
 
-parser.add_argument("--reduction_factor", type=int, default=10)
+parser.add_argument("--reduction_factor", type=int, default=1)
 
 # === dataset, data partitioning mode, device, model, and rounds
 parser.add_argument(
@@ -26,12 +26,12 @@ parser.add_argument(
 
 
 parser.add_argument(
-    "--participant_population", default=10, type=int, help="total clients"
+    "--participant_population", default=50, type=int, help="total clients"
 )
 
 
 parser.add_argument(
-    "--participant_sample_size", default=10, type=int, help="participants each round"
+    "--participant_sample_size", default=50, type=int, help="participants each round"
 )
 
 
@@ -39,7 +39,7 @@ parser.add_argument("--is_poison", default=1, type=int, help="poison or not")
 
 
 parser.add_argument(
-    "--number_of_adversaries", default=1, type=int, help="the number of attackers"
+    "--number_of_adversaries", default=20, type=int, help="the number of attackers"
 )
 
 
@@ -49,7 +49,7 @@ parser.add_argument(
 
 parser.add_argument(
     "--poison_rounds",
-    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15, 16, 17, 18, 19",
+    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19",
     type=str,
     help="",
 )

### 2024-09-13 FL_Backdoor_CV/image_helper.py
chore: huggingface+resultPlace
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -13,6 +13,7 @@ from FL_Backdoor_CV.helper import Helper
 from configs import args
 from transformers import CLIPProcessor, CLIPModel
 import os
+import platform
 from peft import LoraConfig, get_peft_model
 
 random.seed(0)
@@ -90,9 +91,13 @@ class ImageHelper(Helper):
 
     def __init__(self, params):
         super(ImageHelper, self).__init__(params)
-        self.processor = CLIPProcessor.from_pretrained(
-            "openai/clip-vit-base-patch32", cache_dir=os.path.join(os.getcwd(), "cache")
-        )
+        # if platform.system().lower() == 'windows':
+        #     self.processor = CLIPProcessor.from_pretrained(
+        #         "openai/clip-vit-base-patch32", cache_dir=os.path.join(os.getcwd(), "cache")
+        #     )
+        # else:
+        #     self.processor = CLIPProcessor.from_pretrained('../Datasets/clip-vit-base-patch32')
+        self.processor = CLIPProcessor.from_pretrained('../Datasets/clip-vit-base-patch32')
         # self.target_model = CLIPModel.from_pretrained(
         #     "openai/clip-vit-base-patch32", cache_dir=os.path.join(os.getcwd(), "cache")
         # )
@@ -121,16 +126,24 @@ class ImageHelper(Helper):
             bias="none",
         )
         # local model
-        base_model = CLIPModel.from_pretrained(
-            "openai/clip-vit-base-patch32", cache_dir=os.path.join(os.getcwd(), "cache")
-        )
+        # if platform.system().lower() == 'windows':
+        #     base_model = CLIPModel.from_pretrained(
+        #         "openai/clip-vit-base-patch32", cache_dir=os.path.join(os.getcwd(), "cache")
+        #     )
+        # else:
+        #     base_model = CLIPModel.from_pretrained('../Datasets/clip-vit-base-patch32')
+        base_model = CLIPModel.from_pretrained('../Datasets/clip-vit-base-patch32')
         self.local_model = get_peft_model(base_model, config)
         self.local_model.print_trainable_parameters()
 
         # target model
-        base_model = CLIPModel.from_pretrained(
-            "openai/clip-vit-base-patch32", cache_dir=os.path.join(os.getcwd(), "cache")
-        )
+        # if platform.system().lower() == 'windows':
+        #     base_model = CLIPModel.from_pretrained(
[…]

### 2024-09-13 FL_Backdoor_CV/roles/server.py

@@ -16,7 +16,7 @@ from sklearn.cluster import DBSCAN, KMeans
 from sklearn.metrics import pairwise_distances
 from torch.nn.utils import parameters_to_vector, vector_to_parameters
 
-from FL_Backdoor_CV.models.create_model import create_model
+# from FL_Backdoor_CV.models.create_model import create_model
 from FL_Backdoor_CV.roles.evaluation import test_cv, test_poison_cv
 from configs import args
 from FL_Backdoor_CV.roles.aggregation_rules import roseagg

### 2024-09-13 trainer.py

@@ -1,6 +1,8 @@
 import os
 
 os.environ["OMP_NUM_THREADS"] = "1"
+os.environ["HF_DATASETS_OFFLINE"] = "1"
+os.environ["HF_HUB_OFFLINE"] = "1"
 
 import random
 import time
@@ -192,9 +194,10 @@ class Trainer:
 
         current_time = datetime.now()
         formatted_time = current_time.strftime("%Y-%m-%d_%H-%M-%S")
-        file_path = f"./FL_Backdoor_CV/{formatted_time}"
-        os.makedirs(f"./FL_Backdoor_CV/{formatted_time}/participants", exist_ok=True)
-        os.makedirs(f"./FL_Backdoor_CV/{formatted_time}/model_updates", exist_ok=True)
+        file_path = f"./FL_Backdoor_CV/resultWithTime/{formatted_time}"
+        os.makedirs(f'./FL_Backdoor_CV/resultWithTime', exist_ok=True)
+        os.makedirs(f"./FL_Backdoor_CV/resultWithTime/{formatted_time}/participants", exist_ok=True)
+        os.makedirs(f"./FL_Backdoor_CV/resultWithTime/{formatted_time}/model_updates", exist_ok=True)
         self.participants = {}
         if not os.path.exists(saved_results_path):
             os.makedirs(saved_results_path)

### 2024-09-13 attack-zh.tex
docs: 理论(Let)+en(zhou)

@@
 \usepackage[UTF8]{ctex}
+\usepackage{tabularx}
 \usepackage{array}
@@
 
-\textbf{Overview}: 前面的攻击中已经可以有效地针对单轮次攻击进行识别，本部分主要结合客户端的历史记录对客户端进行有效的识别。本部分将保留历史$T$轮次的全局模型$\theta_g^{t'}$，其中$\max\{t-T+1, 1\}\leq  t'\leq t$，并将其Flatten后视为高维空间中的一个点；同时保留每个客户端的历史更新变化，将其视为高维空间中的一个向量，将其延伸后视为一个射线。对于每个客户端，使用最小覆盖球算法计算得到一个最小的超球，覆盖$\zeta$比例的射线。最终球心的位置可以被视为对应客户端对全局模型的意图引导点，球心的半径可以视为对应客户端的置信度。
+\textbf{Overview}: 前面的防御已经可以有效地针对单轮次攻击进行识别，本部分主要结合客户端的历史记录对客户端进行有效的识别。本部分将保留历史$T$轮次的全局模型$\theta_g^{t'}$，其中$\max\{t-T+1, 1\}\leq  t'\leq t$，并将其Flatten后视为高维空间中的一个点；同时保留每个客户端的历史更新变化，将其视为高维空间中的一个向量，将其延伸后视为一个射线。对于每个客户端，使用最小覆盖球算法计算得到一个最小的超球，覆盖$\zeta$比例的射线。最终球心的位置可以被视为对应客户端对全局模型的意图引导点，球心的半径可以视为对应客户端的置信度。
 
@@
     \EndFor
-    \State Determine $\kappa$-distance $\widetilde{dis_i^\kappa}$ for $O_i$
-    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^\kappa}$
-    \State Compute reachability distance $rea_{i,j} = \max\{\widetilde{dis_i^\kappa}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$
+    \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
+    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
+    \State Compute reachability distance $rea_{i,j} = \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$
     \State Calculate local reachability density $lrd_i = \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$
@@
 
-算法\ref{alg:malicious-node-detection-history}展示了根据每个客户端历史记录进行识别的识别过程，主要包含4个步骤：
+% 算法\ref{alg:malicious-node-detection-history}展示了根据每个客户端历史记录进行识别的识别过程，主要包含4个步骤：
+本部分主要包含4个步骤：
 
@@
 
-“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$\theta_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_i$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$\theta^t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-\theta^t$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上轮次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。此部分可以参考算法\ref{alg:malicious-node-detection-history}的step1。
+像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$\theta_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_i$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$\theta^t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-\theta^t$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上轮次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。% 此部分可以参考算法\ref{alg:malicious-node-detection-history}的step1。
 
@@
 
-“Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
+这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。
+
+我们使用符号$O_i$代表客户端$i$在高维空间中超球的球心，使用符号$r_i$代表这个超球的半径。假设当前轮次为$t$，$t'$是最近$T$轮次中的其中一轮，使用符号$\tilde O_i^{t'}$代表球心到第$t'$对应射线的最近点。则可以定义优化问题：
+
+\begin{equation}
+    \min_{O_i, r_i} \quad r_i
+\end{equation}
+
+\begin{equation} 
+\text{s.t.} \quad \left| \left\{ t' \mid \| O_i - \tilde{O}_{i}^{t'} \| \leq r_i \right\} \right| \geq \zeta T,
+\end{equation}
+\begin{equation} 
+    \max\{t-T+1, 1\}\leq  t'\leq t.
+\end{equation}
+
+“Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
 
 “Construct Ray Model”的主要过程如下。对于每个客户端 \(R_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的更新变化历史。设 \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(i\) 上传的展平后的梯度变化向量。
+
 对于每一轮 \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \))，我们将每个射线的起点表示为展平后的全局模型 \( \theta_g^{t'} \)，并将每个射线的方向向量表示为展平后的梯度变化 \( \overline{\triangledown\theta_{i}^{t'}} \)。因此，射线模型可以构建如下：
@@
 \begin{equation}
-    \widetilde{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1}),
+    \left\{\begin{matrix}
+    \widetilde{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1})\\
+    {v}_{i}^{t'} = \overline{\triangledown\theta_{i}^{t'}}
+    \end{matrix}\right.,
 \end{equation}
-    \begin{equation}
-    {v}_{i}^{t'} = \overline{\triangledown\theta_{i}^{t'}},
-    \end{equation}
-
 其中，\( \widetilde{\theta_{i}^{t'-1}} \) 是射线的起点，\( {v}_{i}^{t'} \) 是射线的方向向量。则射线方程为：
@@
 \begin{equation}
-    O_{i,0} = \frac{1}{T} \sum_{t'=\max\{t-T+1, 1\}}^{t} \widetilde{\theta_g^{t'-1}}.
+    O_{i,0} = \frac{1}{\min\{T, t\}} \sum_{t'=\max\{t-T+1, 1\}}^{t} \widetilde{\theta_g^{t'-1}}.
 \end{equation}
@@
 
-    其中$\tilde O_{i,k+1}^{t'}$为更新后的球心$O_{i,k+1}$到被保留射线的最近点。终止条件：当更新后的半径 \( r_{i,k+1} \) 与上一次的半径 \( r_{i,k} \) 相差小于一个预设的阈值 \( \lambda \)，或者达到预设的最大迭代次数$k_{max}$时，停止迭代。这部分可以定义为一个有约束的最优化问题：
+    % 其中$\tilde O_{i,k+1}^{t'}$为更新后的球心$O_{i,k+1}$到被保留射线的最近点。终止条件：当更新后的半径 \( r_{i,k+1} \) 与上一次的半径 \( r_{i,k} \) 相差小于一个预设的阈值 \( \lambda \)，或者达到预设的最大迭代次数$k_{max}$时，停止迭代。这部分可以定义为一个有约束的最优化问题：
+    其中$\tilde O_{i,k+1}^{t'}$为更新后的球心$O_{i,k+1}$到被保留射线的最近点。当更新后的半径 \( r_{i,k+1} \) 与上一次的半径 \( r_{i,k} \) 相差小于一个预设的阈值 \( \lambda \)，或者达到预设的最大迭代次数$k_{max}$时，停止迭代。
 
-\begin{equation}
-\min_{O_i, r_i} \quad r_i
-\end{equation}
-
-\begin{equation} 
-\text{s.t.} \quad \left| \left\{ t' \mid \| O_i - \tilde{O}_{i}^{t'} \| \leq r_i \right\} \right| \geq \zeta T.
-\end{equation}
 % \begin{equation} 
@@
 
-“Abnormal Detection”的主要过程基于局部离群因子（Local Outlier Factor, LOF）得到异常点。LOF算法是一种基于密度的异常检测方法，算法的核心思想是通过计算一个数值$lof_i$来反应节点$i$的异常程度。$lof_i$大致意思是节点$i$目的意图点$O_i$周围意图点所处位置的平均密度比上$O_i$所在位置的密度。比值越大于$1$，则$O_i$所在位置的密度越小于周围其他意图点所在位置的密度，即$O_i$越有可能是异常点。首先定义意图点$O_i$的$\kappa$距离$\widetilde{dis_i^\kappa}$，假设高维空间中存在节点$j$的意图点$O_j$，则有$O_j$与$O_i$之间的距离为$\|O_i-O_j\|$，如果满足以下两个条件，我们就认为$\widetilde{dis_i^\kappa}=\|O_i-O_j\|$：
+“Abnormal Detection”的主要过程基于局部离群因子（Local Outlier Factor, LOF）得到异常点。LOF算法是一种基于密度的异常检测方法，算法的核心思想是通过计算一个数值$lof_i$来反应节点$i$的异常程度。$lof_i$大致意思是节点$i$目的意图点$O_i$周围意图点所处位置的平均密度比上$O_i$所在位置的密度。比值越大于$1$，则$O_i$所在位置的密度越小于周围其他意图点所在位置的密度，即$O_i$越有可能是异常点。首先定义意图点$O_i$的$q$距离$\widetilde{dis_i^q}$，假设高维空间中存在节点$j$的意图点$O_j$，则有$O_j$与$O_i$之间的距离为$\|O_i-O_j\|$，如果满足以下两个条件，我们就认为$\widetilde{dis_i^q}=\|O_i-O_j\|$：
 
 \begin{itemize}
-    \item 在样本空间中，至少存在$\kappa$个意图点$O_j'$，使得$\|O_i-O_j'\|\leq \|O_i-O_j\|$, 其中$j'\neq i$；
-    \item 在样本空间中，至多存在$\kappa-1$个意图点$O_j'$，使得$\|O_i-O_j'\|< \|O_i-O_j\|$, 其中$j'\neq i$。
+    \item 在样本空间中，至少存在$q$个意图点$O_j'$，使得$\|O_i-O_j'\|\leq \|O_i-O_j\|$, 其中$j'\neq i$；
+    \item 在样本空间中，至多存在$q-1$个意图点$O_j'$，使得$\|O_i-O_j'\|< \|O_i-O_j\|$, 其中$j'\neq i$。
 \end{itemize}
 
-总的来说，$O_i$的$\kappa$距离$\widetilde{dis_i^\kappa}$表示高维空间中距离第$\kappa$远的点。之后定义意图点$O_i$的第$\kappa$距离邻域$Nei_i$为到$O_i$距离不超过$\widetilde{dis_i^\kappa}$的所有意图点的集合。由于可能同时存在多个第$\kappa$距离的数据，所以$|Nei_i|\geq \kappa$。可以想象，离群度越大的意图点的$\kappa$距离往往较大，离群度越小的意图点的$\kappa$距离往往较小。之后定义意图点$O_i$相对于意图点$O_j$的可达距离：
+总的来说，$O_i$的$q$距离$\widetilde{dis_i^q}$表示高维空间中距离第$q$远的点。之后定义意图点$O_i$的第$q$距离邻域$Nei_i$为到$O_i$距离不超过$\widetilde{dis_i^q}$的所有意图点的集合。由于可能同时存在多个第$q$距离的数据，所以$|Nei_i|\geq q$。可以想象，离群度越大的意图点的$q$距离往往较大，离群度越小的意图点的$q$距离往往较小。之后定义意图点$O_i$相对于意图点$O_j$的可达距离：
 
 \begin{equation}
-rea_{i,j}=\max\{\widetilde{dis_i^\kappa}, \|O_i-O_j\|\},
+rea_{i,j}=\max\{\widetilde{dis_i^q}, \|O_i-O_j\|\},
 \end{equation}
 
-也就是说，如果意图点$O_j$远离意图点$O_i$，则两者之间的可达距离就是他们之间的实际距离$\|O_i-O_j\|$；而如果二者距离足够近，则可达距离用意图点$O_i$的$\kappa$距离$\widetilde{dis_i^\kappa}$代替。之后定义意图点$O_i$的局部可达密度$lrd_i$为其$Nei_i$所有意图点的平均可达距离的倒数，即：
+也就是说，如果意图点$O_j$远离意图点$O_i$，则两者之间的可达距离就是他们之间的实际距离$\|O_i-O_j\|$；而如果二者距离足够近，则可达距离用意图点$O_i$的$q$距离$\widetilde{dis_i^q}$代替。之后定义意图点$O_i$的局部可达密度$lrd_i$为其$Nei_i$所有意图点的平均可达距离的倒数，即：
 
@@
 
-此时，若有重复点，则可能导致$lrd$变为无限大。$lrd_i$的可以理解为意图点$O_i$所处位置的密度，密度越高则意图点$O_i$越有可能属于同一簇，密度越低则意图点$O_i$越有可能是离群点。也就是说，如果意图点$O_i$和周围邻域点是同一簇，则可达距离可能为较小的$\widetilde{dis_i^\kappa}$，导致可达距离之和较小，密度值较高；如果$O_i$和周围邻居意图点较远，则可达距离可能会取较大的$\|O_i-O_j\|$，导致可达距离之和较大，密度值较低，越有可能是离群点。最后，我们定义意图点$O_i$的局部离群因子$lof_i$为其$Nei_i$所有意图点的局部可达密度与其自身局部可达密度的比值的平均值，即：
+此时，若有重复点，则可能导致$lrd$变为无限大。$lrd_i$的可以理解为意图点$O_i$所处位置的密度，密度越高则意图点$O_i$越有可能属于同一簇，密度越低则意图点$O_i$越有可能是离群点。也就是说，如果意图点$O_i$和周围邻域点是同一簇，则可达距离可能为较小的$\widetilde{dis_i^q}$，导致可达距离之和较小，密度值较高；如果$O_i$和周围邻居意图点较远，则可达距离可能会取较大的$\|O_i-O_j\|$，导致可达距离之和较大，密度值较低，越有可能是离群点。最后，我们定义意图点$O_i$的局部离群因子$lof_i$为其$Nei_i$所有意图点的局部可达密度与其自身局部可达密度的比值的平均值，即：
 
@@
 
-如果$lof_i$比较接近$1$，则说明意图点$O_i$与其邻域点密度差不多，$O_i$可能和邻域属于同一簇；如果$lof_i$小于$1$，则说明意图点$O_i$的密度高于其邻域点的密度，$O_i$为密集点；如果$lof_i$大于$1$，则说明意图点$O_i$的密度低于其邻域点的密度，$O_i$可能是离群点。总之，LOF算法主要通过比较每个意图点$O_i$和其邻域点的密度来判断$O_i$是否为离群点，密度越低，则越有可能是离群点。而密度主要是通过点之间的距离来计算的，点之间的距离越远密度越低，距离越近密度越高。
+如果$lof_i$比较接近$1$，则说明意图点$O_i$与其邻域点密度差不多，$O_i$可能和邻域属于同一簇；如果$lof_i$小于$1$，则说明意图点$O_i$的密度高于其邻域点的密度，$O_i$为密集点；如果$lof_i$大于$1$，则说明意图点$O_i$的密度低于其邻域点的密度，$O_i$可能是离群点。总之，LOF算法主要通过比较每个意图点$O_i$和其邻域点的密度来判断$O_i$是否为离群点，密度越低，则越有可能是离群点。而密度主要是通过点之间的距离来计算的，点之间的距离越远密度越低，距离越近密度越高。计算每个节点$i$的局部离群因子$lof_i$，将$lof_i$大于$1$的客户端视为异常客户端，并将其梯度丢弃。
 
-计算每个节点$i$的局部离群因子$lof_i$，将$lof_i$大于$1$的客户端视为异常客户端，并将其梯度丢弃。
+“Abnormal Detection”的主要过程如算法\ref{alg:malicious-node-detection-history}的19-30行所示。
 
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{figures/fig5-before-agg.jpg}
-    \caption{Benign and Malicious Nodes Before Aggregation}
-    \label{fig:before-agg}
-\end{figure}
-
 剔除了异常节点后，依据正常节点的置信度$cre$进行聚合。其中定义：
@@
     \includegraphics[width=\linewidth]{results/prob-history-Visualization of Client Intentions and Anomalies.png}
-    \caption{使用模拟数据得到的结果}
+    \centering \caption{使用模拟数据得到的结果}
     \label{fig:result-of-histry}
@@
 \end{enumerate}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig4.jpg}
+    \caption{Benign and Malicious Nodes Before Aggregation}
+    \label{fig:before-agg}
+\end{figure}
+
+如图\ref{fig:before-agg}所示展示了异常检测和梯度聚合的计算流程示意图。图中每个球都是某个节点的意图范围。蓝色的球代表良性节点，红色的球代表异常节点。在进行异常检测时我们只考虑每个节点的意图点，即图中的球心位置。在计算可达距离时，由于意图点$O_{j_1}$距离意图点$O_i$较近，故二者之间的可达距离为意图点$O_i$的$q$距离$\widetilde{dis_i^q}$；由于意图点$O_{j_2}$距离$O_i$较远，所以二者之间的可达距离为二者之间的实际距离$\|O_i-O_{j_2}\|$。意图点$O_i$的密度高于其邻域意图点的密度，$lof_i<1$；而意图点$O_{j_2}$的密度低于其邻域意图点的密度，因此$lof_{j_2} > 1$。
+
+将异常节点剔除，在聚合良性节点的梯度时，依据正常节点的置信度进行加权处理。图中可以看出，虽然节点$j_1$被划分为了良性节点，但其置信度非常低，其超球甚至已经与异常节点$j_2$有所重合。因此在梯度聚合的时候，其权重较小。
 
@@
 
+TODO:写成竖排的
+
+为了衡量恶意客户端识别的准确性，算法的预测结果可以分为以下四类：
+
+\begin{itemize}
+    \item \textbf{真阳性（True Positive, TP）}：实际为正例且预测为正例的样本数量。
+    \item \textbf{真阴性（True Negative, TN）}：实际为负例且预测为负例的样本数量。
+    \item \textbf{假阳性（False Positive, FP）}：实际为负例但预测为正例的样本数量。
+    \item \textbf{假阴性（False Negative, FN）}：实际为正例但预测为负例的样本数量。
+\end{itemize}
+
+基于这些基础概念，以下是常用的分类指标及其计算公式和说明：
+
+\begin{table}[h!]
+\small
+\centering
+\begin{tabularx}{0.5\textwidth}{|X|X|X|}
+\hline
+\textbf{指标名称} & \textbf{计算公式} & \textbf{说明} \\ \hline
+准确率（Accuracy） & 
+$\frac{\text{TP} + \text{TN}}{\text{TP} + \text{TN} + \text{FP} + \text{FN}}$ & 
+模型预测正确的样本占总样本的比例，适用于类别平衡的数据集。准确率越大越好。 \\ \hline
+
+精确率（Precision） & 
+$\frac{\text{TP}}{\text{TP} + \text{FP}}$ & 
+被预测为正例的样本中实际为正例的比例。精确率越大越好，特别是在关注减少误报的应用中。 \\ \hline
+
+召回率（Recall） & 
+$\frac{\text{TP}}{\text{TP} + \text{FN}}$ & 
+实际正例中被正确预测为正例的比例。召回率越大越好，特别是在关注减少漏报的应用中。 \\ \hline
+
+特异度（Specificity） & 
+$\frac{\text{TN}}{\text{TN} + \text{FP}}$ & 
+实际负例中被正确预测为负例的比例。特异度越大越好。 \\ \hline
+
+误报率（False Positive Rate, FPR） & 
+$\frac{\text{FP}}{\text{FP} + \text{TN}}$ & 
+实际负例中被错误预测为正例的比例。误报率越小越好。 \\ \hline
+
+假阴率（False Negative Rate, FNR） & 
+$\frac{\text{FN}}{\text{FN} + \text{TP}}$ & 
+实际正例中被错误预测为负例的比例。假阴率越小越好。 \\ \hline
+
+\end{tabularx}
+\caption{分类模型性能衡量指标}
+\end{table}
+
+TODO: 再多写几个
+
 % \subsubsection{攻防相关}

### 2024-09-13 main-v2.tex
docs: 理论(Let)+en(zhou)

@@
 
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig1.pdf}
+    \caption{Benign and Malicious Nodes Before Aggregation}
+    \label{fig1:scene}
+\end{figure}
+
+\section{Related Works}
+%后门攻击对深度学习模型构成了严重的安全威胁，它旨在通过对模型输入添加特殊扰动来诱导目标模型产生不当行为，例如图像分类器中的错误分类等。我们将现有针对模型的后门攻击分为两种，即空间隐蔽性后门攻击和时间隐蔽性后门攻击。
+Backdoor attacks pose a significant security threat to deep learning models, aiming to induce improper behavior in the target model by adding specific perturbations to the input, such as misclassification in image classifiers.
+We classify existing backdoor attacks on models into two types: spatially covert backdoor attacks and temporally covert backdoor attacks.
+
+%空间隐蔽性后门攻击是指攻击者通过微调模型参数、修改输入特征或操纵模型训练过程等方式，使得现有防御方法无法在特征空间中有效区分恶意攻击者与良性参与者，从而有效逃避检测。Shadowcast\cite{xu2024shadowcast}通过在特征空间中引入微小、不可察觉的扰动，操纵视觉语言模型（VLMs）在特定视觉输入下生成误导性的文本输出。BadClip\cite{liang2024badclip}提出了一种针对多模态对比学习模型（如CLIP）的双嵌入引导后门攻击方法，通过优化视觉触发模式，使其在嵌入空间中接近目标文本语义，从而在不显著改变模型参数的情况下，植入难以被检测到的后门。Flip\cite{jha2023label}通过修改训练数据的标签，使得模型训练轨迹接近于带有后门的专家模型，从而在特征空间中达到隐蔽攻击的效果，即使在图像干净的情况下也能逃避现有检测方法。
+Spatially Covert Backdoor Attacks:
+Spatially covert backdoor attacks refer to attacks where adversaries fine-tune model parameters, modify input features, or manipulate the model training process in a way that existing defense methods cannot effectively distinguish between malicious attackers and benign participants in the feature space, thereby evading detection.
+Shadowcast \cite{xu2024shadowcast} manipulates vision-language models (VLMs) to produce misleading textual outputs for specific visual inputs by introducing subtle, imperceptible perturbations in the feature space.
+BadClip \cite{liang2024badclip} proposes a dual embedding-guided backdoor attack method for multimodal contrastive learning models (e.g., CLIP), optimizing visual trigger patterns to make them closer to the target text semantics in the embedding space, thus implanting a hard-to-detect backdoor without significantly altering the model parameters.
+Flip \cite{jha2023label} modifies the labels of training data so that the model's training trajectory approximates that of an expert model with a backdoor, achieving covert attacks in the feature space that can evade existing detection methods even when the images are clean.
+
+%时间隐蔽性后门攻击是指攻击者通过调整模型训练过程或优化后门植入等方式，使后门在恶意攻击者结束攻击后仍能长期存在，不被后续良性更新所覆盖，从而持续影响模型行为。 Chameleon\cite{dai2023chameleon}关注如何通过对比学习来调整中毒样本、干扰样本以及促进样本嵌入表示之间的关系，从而提高后门攻击的空间隐蔽性。ImgTrojan\cite{tao2024imgtrojan}通过在视觉语言模型的训练数据中注入少量恶意样本，使得这些后门即使在模型后续的良性训练中仍能保持有效，从而持续影响模型的行为。\cite{gu2023gradient}提出了一种新的更新控制方法，通过跨层更新幅度归一化和层内更新方向投影，解决了参数高效调优（PET）过程中后门攻击的遗忘问题，从而维持攻击的持久性和隐蔽性。A3FL\cite{zhang2024a3fl}通过对抗性适应损失函数来优化触发器的方式，使得后门能够在全局训练动态中持久存在，从而在联邦学习模型中实现高效且持久的攻击效果。
+Temporally Covert Backdoor Attacks:
+Temporally covert backdoor attacks involve adjusting the model training process or optimizing backdoor implantation such that the backdoor persists even after the malicious attacker has stopped the attack, remaining undetected by subsequent benign updates, and continuing to affect the model’s behavior.
+Chameleon \cite{dai2023chameleon} focuses on enhancing the spatial covert nature of backdoor attacks by adjusting the relationships between poisoned samples, interference samples, and promoting samples in contrastive learning.
+ImgTrojan \cite{tao2024imgtrojan} injects a small number of malicious samples into the training data of vision-language models, ensuring that these backdoors remain effective even after subsequent benign training, thereby continuously affecting the model's behavior.
+\cite{gu2023gradient} proposes a novel update control method that normalizes cross-layer update magnitudes and projects intra-layer update directions to address the issue of backdoor forgetting during parameter-efficient tuning (PET), thus maintaining the persistence and concealment of the attack.
+A3FL \cite{zhang2024a3fl} optimizes the trigger by using an adversarial adaptation loss function, enabling the backdoor to persist throughout global training dynamics, thereby achieving efficient and persistent attacks in federated learning models.
+% 总之，现有的后门攻击策略在空间隐蔽性和时间隐蔽性方面都有了显著的进展。空间隐蔽性后门攻击通过优化特征空间中的触发器或更新，使得恶意行为难以被现有的检测方法发现，从而实现了更高效、更难以检测的攻击。而时间隐蔽性后门攻击则专注于提高后门的持久性，使得即使在恶意攻击结束后，这些后门依然能够在模型中长期存在并继续影响其行为。通过这些攻击方式的结合，攻击者能够在各种应用场景中有效地躲避检测，并确保攻击效果的持续性，这对现有的防御机制提出了更高的挑战，强调了未来在开发更加鲁棒的防御方法方面的迫切需求。
+
+%总的来看，现有的后门攻击方法已展现出显著的隐蔽性和持久性，能够有效规避当前的检测机制。这些攻击不仅在特征空间中巧妙隐藏恶意意图，还能在长期训练过程中保持攻击效果，对模型行为产生持续而深远的影响，也对模型安全构成了严峻挑战。这对现有的防御机制提出了更高的挑战，强调了未来在开发更加鲁棒的防御方法方面的迫切需求。
+Overall, existing backdoor attack methods have demonstrated significant advances in both spatial and temporal concealment, effectively circumventing current detection mechanisms.
+These attacks not only cleverly hide malicious intent in the feature space but also maintain their effects throughout long-term training, posing a sustained and profound impact on model behavior, thus presenting a severe challenge to model security.
+This underscores the need for future research to focus on developing more robust defense methods.
+
+\subsection{Defenses}
+%在当前深度学习模型的安全性研究中，针对后门攻击的防御措施主要可以分为两大类：后门检测和后门缓解。% Backdoor Mitigation or Elimination
+In the current research on the security of deep learning models, defense measures against backdoor attacks can be broadly categorized into two major types: backdoor detection and backdoor mitigation.
+
+%后门检测主要旨在识别模型中已存在的后门攻击。在这一类中，SEER\cite{zhu2024seer}提出了一种用于视觉-语言模型的后门检测算法，通过在图像和文本模态的特征空间中联合搜索目标文本和图像触发器，成功实现了在多种场景下的后门检测。ASSET\cite{pan2023asset}提出了一种通过主动诱导后门样本和干净样本在模型行为上的差异，从而实现跨多种深度学习范式的鲁棒后门数据检测方法，并在端到端监督学习、自监督学习和迁移学习中表现出色。DECREE\cite{feng2023detecting}提出了一种用于检测自监督学习中预训练图像编码器后门的创新方法，该方法无需依赖标签数据或下游分类器，且在多种数据集和攻击类型下表现出极高的检测准确率。
+Backdoor Detection:
+Backdoor detection primarily aims to identify existing backdoor attacks within a model.
+In this category, SEER \cite{zhu2024seer} proposes a backdoor detection algorithm for vision-language models, successfully detecting backdoors across various scenarios by jointly searching for target text and image triggers in the feature spaces of the image and text modalities.
+ASSET \cite{pan2023asset} introduces a robust backdoor data detection method across multiple deep learning paradigms by actively inducing behavioral differences between backdoor samples and clean samples in the model, demonstrating excellent performance in end-to-end supervised learning, self-supervised learning, and transfer learning.
+DECREE \cite{feng2023detecting} presents an innovative method for detecting backdoors in pre-trained image encoders used in self-supervised learning, achieving high detection accuracy across various datasets and attack types without relying on label data or downstream classifiers.
+
+%后门缓解则侧重于通过各种技术手段来消除或减轻后门攻击的影响。Semantic Shield\cite{ishmam2024semantic}通过强制模型在训练时对齐图像区域与外部知识，以防御视觉-语言模型中的后门和数据中毒攻击，从而显著提高了模型的鲁棒性。MCLDef\cite{yue2023model}提出了一种基于模型对比学习的两阶段后门防御方法，通过收缩或破坏中毒数据在特征空间中的聚类，并将中毒数据的特征拉向其干净对应物，从而有效去除深度神经网络中的后门，同时在不显著降低模型准确性的情况下提升防御效果。DPoE\cite{liu2023shortcuts}提出了一种基于端到端集成的后门防御框架，通过结合浅层模型和主模型来捕捉和抑制后门触发器，从而有效应对各种显性和隐性的后门攻击，同时减轻噪声标签对模型性能的影响。此外，PSIM\cite{zhao2024defending}提出了一种基于参数高效微调的防御模块，通过利用样本的置信度来识别被后门攻击污染的样本，显著增强了模型抵御权重中毒后门攻击的能力，并在不影响模型准确性的情况下有效过滤出被污染的样本。CleanCLIP\cite{bansal2023cleanclip}通过在视觉和文本编码器上进行无监督微调，独立调整每种模态的表示，以削弱视觉-语言对比学习模型中由后门攻击引入的错误关联，从而有效减少后门攻击的影响，同时保持模型在正常数据上的性能。
+Backdoor Mitigation:
+Backdoor mitigation focuses on eliminating or reducing the impact of backdoor attacks through various technical means.
+Semantic Shield \cite{ishmam2024semantic} significantly enhances model robustness by aligning image regions with external knowledge during training to defend against backdoor and data poisoning attacks in vision-language models.
+MCLDef \cite{yue2023model} proposes a two-stage backdoor defense method based on model contrastive learning, effectively removing backdoors in deep neural networks by contracting or disrupting the clustering of poisoned data in the feature space and pulling the features of poisoned data toward their clean counterparts, while improving defense effectiveness without significantly reducing model accuracy.
+DPoE \cite{liu2023shortcuts} introduces an end-to-end integrated backdoor defense framework that captures and suppresses backdoor triggers by combining a shallow model and a main model, effectively countering various explicit and covert backdoor attacks while mitigating the impact of noisy labels on model performance.
+Additionally, PSIM \cite{zhao2024defending} proposes a defense module based on parameter-efficient fine-tuning, significantly enhancing the model's ability to resist weight poisoning backdoor attacks by identifying samples polluted by backdoor attacks using sample confidence, effectively filtering out polluted samples without affecting model accuracy.
+CleanCLIP \cite{bansal2023cleanclip} reduces the impact of backdoor attacks in vision-language contrastive learning models by independently adjusting the representations of each modality through unsupervised fine-tuning of the visual and text encoders, while maintaining model performance on clean data.
+
+%尽管这些方法在应对后门攻击方面展现了显著效果，但在面对更隐蔽或复杂的后门攻击时，效果依然可能不够理想。某些方法还依赖于外部知识或置信度的设定，可能导致误判或性能瓶颈。此外，这些方法在实际应用中也增加了计算开销和训练时间。因此，未来的研究仍需在提升整体性能与效率的同时，着力解决隐蔽或复杂后门攻击的防御挑战。
+Despite the significant effectiveness of these methods in countering backdoor attacks, their performance may still be insufficient when faced with more covert or complex backdoor attacks.
+Some methods also rely on external knowledge or confidence settings, which may lead to misjudgments or performance bottlenecks.
+Moreover, these methods increase computational overhead and training time in practical applications.
+Therefore, future research must continue to focus on addressing the challenges posed by covert or complex backdoor attacks while enhancing overall performance and efficiency.
+
+\section{System model \& Preliminaries}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%symbols 表格
+\begin{table}[!t]
+{
+\renewcommand{\arraystretch}{1.2}
+\caption{Summary of Main Notation}
+\label{notations}
+\vspace{0em}
+\centering
+\begin{tabular}{| c || l |}
+\hline
+\textbf{Symbol} & \multicolumn{1}{c |}{\textbf{Description}}\\
+    \hline
+    $U_i,\mathcal{D}_i$ & The $i$-th UAV devices and its dataset\\
+    \hline
+    $n^{s_{m}, i},\mathcal{P}^i$ & The size and normalized distribution of $\mathcal{D}_i$\\
+    \hline
+    $\mathcal{P}^{Tar}, w$ & Target distribution and model of learning task $Job$\\
+    \hline
+    $T$ & The maximum communication rounds of $Job$\\
+    \hline
+    $C,K$ & The set and number of all peer communities\\
+    \hline
+    $S,M$ & The set and number of all colleague communities\\
+    \hline
+    %$L$ & The number of clients in each super node\\
+    %\hline
+    $c_k$ & The $k$-th peer community\\
+    \hline
+    $s_m$ & The $m$-th colleague community\\ 
+    \hline
+    $\Delta \widetilde{\omega}_{t}^{s_{m},i}$ & The weight updates from $U_i \in s_m$ in round $t$\\
+    \hline
+    $p^{s_{m}, i}$ & The aggregation coefficient for $U_i$ within $s_m$\\
+    \hline
+    $\Delta\widetilde{\omega}_{t}^{s_{m}}$ & The weight updates from $s_m$ in round $t$\\
+    \hline
+    $p^{s_{m}}$ & The aggregation coefficient for $\Delta\widetilde{\omega}_{t}^{s_{m}}$ from $s_m$\\
+    \hline
+    $E_k$ & The clipping bound of peer community $c_k$\\
+    \hline
+    $Sen_k$ & The maximum sensitivity of $c_k$\\
+    \hline
+    $\varepsilon_k,\delta_k$& The parameters of differential privacy \\
+    \hline
+    $L$& The minimum size of colleague community\\
+    \hline
+    $\alpha^{a,b}_{t}$& The cosine similarity between $a$ and $b$\\
+    \hline
+    $PI^{c_k \rightarrow i}_{t}$ & The positive interaction between $c_k$ and $U_i$\\
+    \hline
+    $NI^{c_k \rightarrow i}_{t}$& The positive interaction between $c_k$ and $U_i$\\
+    \hline
+    $\Upsilon^{c_k \rightarrow i}_{t}$& The peer reputation opinion vector of $c_k$\\
+    \hline
+    $\Phi^{c_k \rightarrow i}_{t}$& $c_k$'s credit evaluation towards $U_i$ in round $t$\\
+    \hline
+    $\Upsilon^{s_m}_{t}$ & The colleague reputation opinion vector towards $s_m$\\
+    \hline
+    $\Phi^{s_m \rightarrow i}_{t}$& The colleague credit evaluation for $\forall U_i \in s_m$\\
+    \hline
+    $\Upsilon^{i}_{t},\Phi^{i}_{t}$& The comprehensive reputation and credit of $U_i$\\
+    \hline
+    $\psi^{i}_t$& The fairness-guaranteed selection probability\\
+    \hline
+    \end{tabular}
+        }
+     \vspace{-1.5em}
+     \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Consider a scenario where a vision-language model is fine-tuned in a federated manner within an Internet of Robotic Things (IoRT) network.
+The system model comprises multiple robotic nodes and a central server.
+The robotic nodes perform local model fine-tuning, with global aggregation carried out through the central server.
+The following is a detailed description of the system model.
+
+\textbf{Participants and Datasets:}
+Assume the system model consists of $n$ robotic nodes, each denoted by $R_i$, where $i \in {1, 2, \ldots, n}$.
+Each robotic node $R_i$ possesses a local dataset $D_i = {x_{i,j}, y_{i,j}}{j=1}^{|D_i|}$, where $x{i,j}$ represents the input data, and $y_{i,j}$ represents the corresponding label data, with $|D_i|$ denoting the size of the dataset.
+The overall dataset is denoted by $D = \bigcup_{i=1}^{n} D_i$.
+
+\textbf{LoRA:}
+In the Low-Rank Adaptation (LoRA) method, each parameter matrix $W$ is represented as:
+
+where $W_0$ is the original weight matrix of the model, $\Delta W$ is the low-rank increment matrix, and $B$ and $A$ are the low-rank decomposition matrices, with $r$ representing the rank of the matrices.
+The original model parameters are denoted by $\Theta = \sum {W_0}$, while the introduced incremental parameters are denoted by $\theta = \sum {W}$.
+During federated fine-tuning, only the incremental parameters $\theta$ are updated, while the original parameters $\Theta$ remain unchanged.
+
+\textbf{Local Model Training:}
+At the start of each federated training round, the central server sends the global incremental parameters $\theta_g^{t-1}$ to each robotic node $R_i$.
+Upon receiving the incremental parameters $\theta_g^{t-1}$, each node fine-tunes its local model based on its local dataset $D_i$.
+Assume the number of local training epochs is $E_l$, the batch size is $b$, and the learning rate is $\eta$.
+For each epoch, node $R_i$ first randomly samples a batch of data $D_i^b \sim Sample(D_i, b)$ from its local dataset $D_i$, then updates the incremental parameters using optimization algorithms such as stochastic gradient descent:
+
+where $(\theta_i^{t})^e$ denotes the parameters after the $e$-th fine-tuning epoch, with the initialization $(\theta_i^{t})^0 = \theta_g^{t-1}$.
+The objective of local training is to minimize the loss function $f(D_i^b, (\theta_i^{t})^e)$:
+
+where $\Theta$ represents the original model parameters, and $\ell$ denotes the loss function (e.g., cross-entropy loss).
+After completing local training, the node computes its incremental parameter update $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ and uploads it to the central server.
+
+\textbf{Federated Aggregation:}
+At the end of each round of local training, the central server collects the local updates $\triangledown \theta_i^t$ from each robotic node $R_i$ and aggregates them using the appropriate aggregation algorithm to update the global incremental parameters $\theta_g^t$, computed as:
+
+where $Aggregate$ represents the aggregation algorithm employed by the central server, such as FedAvg, Krum, Bulyan, or RoseAgg.
+The updated global incremental parameters $\theta_g^t$ will be disseminated to all robotic nodes before the next round of training for further local fine-tuning.
+
+\section{Threat model}
+%Attacker's Goal：假设在对视觉语言模型进行联邦微调的场景中，存在一个或者多个由攻击者操纵的恶意节点。其目标是对全局模型$\theta_g$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别，同时尽可能保持对干净输入的分类准确性。
+\textbf{Attacker's goal:} Consider a scenario where one or more malicious nodes controlled by an attacker are present during the FFT process of a vision-language model.
+The attacker's objective is to implant a backdoor into the global model $\theta_g$, enabling the model to classify any test input containing a predefined trigger $\delta$ as the target class, while simultaneously maintaining the classification accuracy on clean inputs to the greatest extent possible.
+
+%Attacker's Ability: 在联邦学习场景中，假设攻击者对恶意节点的本地训练过程具有完全的控制权。这意味着攻击者可以任意操控本地数据、触发器模式、优化策略和本地更新过程。此外，攻击者可以采用“智能”攻击策略，这种策略的特点是攻击效果不会在单轮训练中显现，而是通过多轮训练的累积效应逐步将后门植入全局模型中。这种场景在实际中是可能存在的，因为中央服务器只能接收到客户端上传的训练后模型更新，而无法知晓每个客户端的具体训练过程。然而，攻击者无法对中央服务器的操作进行干扰，例如，无法更改全局模型的聚合规则或篡改其他良性客户端的模型更新。
+\textbf{Attacker's ability:} In the distributed training scenario as FL, it is assumed that the attacker has full control over the local training process on the malicious nodes.
+This means the attacker can manipulate local data, trigger patterns, optimization strategies, and the local update process at will.
+Furthermore, the attacker may employ a ``stealthy" attack strategy, characterized by the backdoor being gradually implanted into the global model through the cumulative effect of multiple training rounds, rather than becoming apparent in a single training round.
+Such a scenario is plausible in practice because the central server only receives the model updates uploaded by robot nodes after training, without knowledge of the specific training process for each client.
+However, the attacker cannot interfere with the central server's operations, such as altering the global model aggregation rules or tampering with the model updates from other benign nodes.
+
+\section{Method}
+
+\subsection{Single}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig2.pdf}
+    \caption{Benign and Malicious Nodes Before Aggregation}
+    \label{fig2:single}
+\end{figure}
+
+\subsection{Multi}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig3.jpg}
+    \caption{Benign and Malicious Nodes Before Aggregation}
+    \label{fig3:multi}
+\end{figure}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig4.jpg}
+    \caption{Benign and Malicious Nodes Before Aggregation}
+    \label{fig4:before-agg}
+\end{figure}
+
 As a preeminent collaborative artificial intelligence paradigm, Federated Learning (FL) has garnered substantial research focus \cite{ETT2}. 
@@
 Consequently, solutions integrating cryptography, auxiliary training, multi-round detection, or other security mechanisms with high computational costs and bandwidth utilization (e.g., ShieldFL \cite{ma2022shieldfl}, AFA \cite{munoz2019byzantine-AFA}, and FLdetector \cite{zhang2022fldetector}) are not applicable for real-world deployment.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig1.PNG}
-\caption{FFL Illustration in Heterogeneous UAV Networks: Taking target recognition as an example, UAV node group patrolling in urban areas may collect a higher proportion of ``automobile'' samples (e.g., UN1 and UN2), while UAV groups patrolling in port areas will acquire more ``ship'' samples (e.g., UN6 and UN7).
-Consequently, the dataset distributions across the entire network often exhibit significant imbalance, while simultaneously displaying a certain degree of similarity within localized regions.
-}
-\label{fig1:UAV-Network}
-\end{figure}
 
@@
 % \end{tabular}
-
-\section{Related work}
 
@@
 
-\section{System model} %\& Preliminaries}
+\section{System model \& Preliminaries}
 %%symbols 表格
@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig2.PNG}
-\caption{Stratified community construction in a heterogeneous environment.}
-\label{fig2:framework}
-\end{figure}
+% \begin{figure}[!t]
+% \centering
+% \includegraphics[width=\linewidth]{figures/fig2.PNG}
+% \caption{Stratified community construction in a heterogeneous environment.}
+% \label{fig2:framework}
+% \end{figure}
 
@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig3.PNG}
-\caption{The workflow of MR-FFL.}
-\label{fig3:workflow}
-\end{figure}
+% \begin{figure}[!t]
+% \centering
+% \includegraphics[width=\linewidth]{figures/fig3.PNG}
+% \caption{The workflow of MR-FFL.}
+% \label{fig3:workflow}
+% \end{figure}
 
@@
 \State \Return $w^g,\{w^k\}$
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Single}
+\label{alg:malicious-node-detection-history}
+\begin{algorithmic}[1]
+\State \textit{\textbf{Input:} Global model $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical updates for each nodes $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$, threshold $\varepsilon$.}
+\State \textit{\textbf{Output:} Sets of normal/malicious nodes $U_{nor}$ and $U_{mal}$.}
+
+\State {\color{CadetBlue}/*\textbf{Step 1: historical database construction*/}}
+\For {Client $i \in $}
+    \State Record flattened gradients $\bar{\theta_i^t}$ and models $\theta_g^{t-1};$
+    \State Establish a ray with Eq. () for each of the $t'$ most recent gradients, $t' = \max\{t-T+1, 1\}, \ldots, t$;
+\EndFor
+
+\State \textbf{Step 2: Obtain the Purpose Intention}
+\For {Client $i$}
+    \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
+    \While {Not Converged}
+        \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
+    \EndWhile
+    \State Calculate confidence $cre_i = \frac{1}{r_i + \rho}$
+\EndFor
+
+\State \textbf{Step 3: Abnormal Detection}
+\For {Client $i$}
+    \For {Each point $O_j \neq O_i$}
+        \State Calculate distance $\|O_i - O_j\|$
+    \EndFor
+    \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
+    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
+    \State Compute reachability distance $rea_{i,j} = \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$
+    \State Calculate local reachability density $lrd_i = \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$
+\EndFor
+% \For {Client $i$}
+%     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
+%     \If {$lof_i > 1$}
+%         \State Mark client $i$ as malicious, add to $U_{mal}$
+%     \Else
+%         \State Mark client $i$ as normal, add to $U_{nor}$
+%     \EndIf
+% \EndFor
+\State Calculate $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$ for each client $i$
+% \State $U_{mal} = \{i \,|\, lof_i > 1\}$
+% \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
+\State $U_{mal}, U_{nor} = \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$
+
+\State \textbf{Step 4: Gradients Aggregation}
+\For {Client $i\in U_{nor}$}
+        \State Compute adjusted confidence $cre_i' = \tanh(cre_i)$
+        \State Normalize weights $w_i = \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$
+\EndFor
+
+\State \textbf{Output:} Aggregated global model update $\theta_g^t = \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Malicious Node Detection via DCT}
+\label{alg:malicious-node-detection}
+\begin{algorithmic}[1]
+\State \textbf{Input:} $d$, $n$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$, $m$ \Comment{$d$ is the dimension of each node update; $n$ is the number of the nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$is the local updates from nodes during the $t$-th round; $m$ is the length of low-frequency components}
+\State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
+
+\State Step 1: Frequency Domain Transformation
+\For {Node $R_i$}
+    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
+    \State $G_i^t = Trunc(DCT(\bar{\theta_i^t}), m)$ \Comment{Compute DCT and retain only the top $m$ low-frequency components}
+\EndFor
+
+\State
+
+\State Step 2: Clean Ingredient Extraction
+\State $H^t \gets (G_0^t, G_1^t, \ldots, G_{n}^t) \in \mathbb{R}^{d \times m}$ \Comment{Stacking to form Matrix $H^t$.}
+
+\State $\hat{H}^t \gets (H^t)^{T} H^t$
+\State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
+\State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
+
+\State
+
+\State Step 3: Kullback-Leibler Divergence Calculation
+\State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
+\For {Node $R_i$}
+    \State $Ki \gets \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)$
+\EndFor
+\State $S \gets \{KL_1, KL_2, \ldots, KL_n\}$ \Comment{The distribution differences calculated by KL divergence.}
+
+\State
+
+\State Step 4: Malicious Node Detection
+\State $\{C_1, C_2, \ldots, C_K\} \gets \text{HDBSCAN}(S)$
+\State $U_{nor} \gets C_{\text{max}}$, $U_{mal} \gets \{C_i \, | \, i \neq \text{max}\}$
+
 \end{algorithmic}
@@
 \bibliographystyle{IEEEtran}
-\bibliography{ref}
+\bibliography{ref,attack_defense}
 
@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig4-history.jpg}
-\caption{Combining multiple rounds of historical identification to identify malicious nodes
-}
-\label{fig4:history}
-\end{figure}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{img/SecFFT-场景.pdf}
-\caption{Combining multiple rounds of historical identification to identify malicious nodes
-}
-\label{fig4:history}
-\end{figure}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{img/SecFFT-算法1.pdf}
-\caption{Combining multiple rounds of historical identification to identify malicious nodes
-}
-\label{fig4:history}
-\end{figure}
+% \begin{figure}[!t]
+% \centering
+% \includegraphics[width=\linewidth]{figures/fig4-history.jpg}
+% \caption{Combining multiple rounds of historical identification to identify malicious nodes
+% }
+% \label{fig4:history}
+% \end{figure}
+
+% \begin{figure}[!t]
+% \centering
+% \includegraphics[width=\linewidth]{img/SecFFT-场景.pdf}
+% \caption{Combining multiple rounds of historical identification to identify malicious nodes
+% }
+% \label{fig4:history}
+% \end{figure}
+
+% \begin{figure}[!t]
+% \centering
+% \includegraphics[width=\linewidth]{img/SecFFT-算法1.pdf}
+% \caption{Combining multiple rounds of historical identification to identify malicious nodes
+% }
+% \label{fig4:history}
+% \end{figure}
 

### 2024-09-13 FL_Backdoor_CV/roles/server.py
chore: small changes
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -341,7 +341,7 @@ class Server:
                                             args.number_of_adversaries
                                             / args.dba_trigger_num
                                         )
-                            model_updates[name][i] *= mal_boost / args.global_lr / 2
+                            model_updates[name][i] *= mal_boost / args.global_lr
 
         # 保存模型梯度
         path = os.path.join(

### 2024-09-13 configs.py

@@ -49,14 +49,14 @@ parser.add_argument(
 
 parser.add_argument(
     "--poison_rounds",
-    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19",
+    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49",
     type=str,
     help="",
 )
 
 parser.add_argument(
     "--retrain_rounds",
-    default=20,
+    default=30,
     type=int,
     help="continue to train {retrain_rounds} rounds starting when resume is true",
 )  # end_rounds = curr_round + retrain_rounds + window 这个参数的意思是指明中毒攻击情况下训练的轮数

### 2024-09-13 trainer.py
fix: log file path
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -299,12 +299,12 @@ class Trainer:
                 save_results_to_csv(self.results, res_path)
                 save_results_to_csv(
                     self.participants,
-                    f"./FL_Backdoor_CV/{formatted_time}/participants/participants.csv",
+                    f"./FL_Backdoor_CV/resultWithTime/{formatted_time}/participants/participants.csv",
                 )
 
         save_results_to_csv(
             self.participants,
-            f"./FL_Backdoor_CV/{formatted_time}/participants/participants.csv",
+            f"./FL_Backdoor_CV/resultWithTime/{formatted_time}/participants/participants.csv",
         )
 
 

### 2024-09-13 FL_Backdoor_CV/image_helper.py
fine-tune: 有的无的小更改
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -165,7 +165,6 @@ class ImageHelper(Helper):
             self.test_dataset = datasets.CIFAR10(
                 self.params["data_folder"], train=False, transform=transforms.ToTensor()
             )
-
         if self.params["dataset"] == "emnist":
             if self.params["emnist_style"] == "digits":
                 self.train_dataset = EMNIST(
@@ -182,7 +181,6 @@ class ImageHelper(Helper):
                     download=True,
                     transform=self.transform,
                 )
-
             elif self.params["emnist_style"] == "byclass":
                 self.train_dataset = EMNIST(
                     self.params["data_folder"],
@@ -198,7 +196,6 @@ class ImageHelper(Helper):
                     download=True,
                     transform=self.transform,
                 )
-
             elif self.params["emnist_style"] == "letters":
                 self.train_dataset = EMNIST(
                     self.params["data_folder"],
@@ -228,6 +225,7 @@ class ImageHelper(Helper):
                 download=True,
                 transform=self.transform,
             )
+        
         self.classes = self.train_dataset.classes
 
     def get_img_classes(self):

### 2024-09-13 trainer.py

@@ -34,8 +34,10 @@ from datetime import datetime
 import csv
 from FL_Backdoor_CV.image_helper import plot_image
 
+from typing import Dict
 
-def save_results_to_csv(results, filename="results.csv"):
+
+def save_results_to_csv(results: Dict[str, list], filename="results.csv"):
     keys = list(results.keys())
 
     max_length = max(len(v) for v in results.values())
@@ -73,6 +75,7 @@ class Trainer:
             params_loaded["dataset"] == "cifar10"
             or params_loaded["dataset"] == "emnist"
             or params_loaded["dataset"] == "fmnist"
+            # 暂无cifar100
         ):
             dataset_name = params_loaded["dataset"]
             if os.path.isdir(f"./FL_Backdoor_CV/data/{dataset_name}/"):

### 2024-09-13 getResult/FL_Backdoor_CV/roles/server-init.py
refactor: 每次需要得到一些数据，就新建一个完全的副本
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,0 +1,924 @@
+import copy
+
+import os
+import random
+import re
+from collections import defaultdict
+
+
+import numpy as np
+import sklearn.metrics.pairwise as smp
+import torch
+import torch.nn.functional as F
+from scipy.linalg import eigh as largest_eigh
+from scipy.stats import entropy
+from sklearn.cluster import DBSCAN, KMeans
+from sklearn.metrics import pairwise_distances
+from torch.nn.utils import parameters_to_vector, vector_to_parameters
+
+from FL_Backdoor_CV.models.create_model import create_model
+from FL_Backdoor_CV.roles.evaluation import test_cv, test_poison_cv
+from configs import args
+from FL_Backdoor_CV.roles.aggregation_rules import roseagg
+from FL_Backdoor_CV.roles.aggregation_rules import avg
+from FL_Backdoor_CV.roles.aggregation_rules import foolsgold
+from FL_Backdoor_CV.roles.aggregation_rules import flame
+from FL_Backdoor_CV.roles.aggregation_rules import fltrust
+from FL_Backdoor_CV.roles.aggregation_rules import robust_lr
+
+import pickle
+
+
+def softmax(x):
+    f_x = np.exp(x) / np.sum(np.exp(x))
+    return f_x
+
+
+class Server:
+    def __init__(self, helper, clients, adversary_list):
+        # === model ===
+        if args.resume:
+            self.model = torch.load(
+                os.path.join(
+                    "./FL_Backdoor_CV/saved_models/Revision_1", args.resumed_name
+                ),
+                map_location=args.device,
+            )
+        else:
+            self.model = create_model()
+
+        # === gradient correction ===
+        # self.previous_models = []
+        # if args.gradient_correction:
+        #     previous_model = copy.deepcopy(self.model)
+        #     previous_model.load_state_dict(self.model.state_dict())
+        #     self.previous_models.append(previous_model)
+
+        # === clients, participants, attackers, and benign clients ===
+        self.clients = clients
+        self.participants = None
+        self.adversary_list = adversary_list
+        self.benign_indices = list(
+            set(list(range(args.participant_population))) - set(self.adversary_list)
+        )
+
+        # === image helper ===
+        self.helper = helper
+
+        # === whether resume ===
+        self.current_round = 0
+        # === Inherent recognition accuracy on poisoned data sets
+        self.inheret_poison_acc = 0
+
+        if args.resume:
+            self.current_round = int(
[…]

### 2024-09-13 getResult/FL_Backdoor_CV/roles/server.py

@@ -16,7 +16,7 @@ from sklearn.cluster import DBSCAN, KMeans
 from sklearn.metrics import pairwise_distances
 from torch.nn.utils import parameters_to_vector, vector_to_parameters
 
-from FL_Backdoor_CV.models.create_model import create_model
+# from FL_Backdoor_CV.models.create_model import create_model
 from FL_Backdoor_CV.roles.evaluation import test_cv, test_poison_cv
 from configs import args
 from FL_Backdoor_CV.roles.aggregation_rules import roseagg
@@ -25,6 +25,7 @@ from FL_Backdoor_CV.roles.aggregation_rules import foolsgold
 from FL_Backdoor_CV.roles.aggregation_rules import flame
 from FL_Backdoor_CV.roles.aggregation_rules import fltrust
 from FL_Backdoor_CV.roles.aggregation_rules import robust_lr
+from FL_Backdoor_CV.roles.aggregation_rules import secfft
 
 import pickle
 
@@ -37,15 +38,16 @@ def softmax(x):
 class Server:
     def __init__(self, helper, clients, adversary_list):
         # === model ===
-        if args.resume:
-            self.model = torch.load(
-                os.path.join(
-                    "./FL_Backdoor_CV/saved_models/Revision_1", args.resumed_name
-                ),
-                map_location=args.device,
-            )
-        else:
-            self.model = create_model()
+        # if args.resume:
+        #     self.model = torch.load(
+        #         os.path.join(
+        #             "./FL_Backdoor_CV/saved_models/Revision_1", args.resumed_name
+        #         ),
+        #         map_location=args.device,
+        #     )
+        # else:
+        #     self.model = create_model()
+        self.model = helper.target_model
 
         # === gradient correction ===
         # self.previous_models = []
@@ -70,61 +72,61 @@ class Server:
         # === Inherent recognition accuracy on poisoned data sets
         self.inheret_poison_acc = 0
 
-        if args.resume:
-            self.current_round = int(
-                # re.findall(r"\d+\d*", args.resumed_name.split("/")[2])[0]
-                re.search(r"avg_(\d+)", args.resumed_name).group(1)
-            )
-            test_l, test_acc = self.validate()
-            if args.attack_mode.lower() == "combine":
-                test_l_acc = self.validate_poison()
-                print(
-                    f"\n--------------------- T e s t - L o a d e d - M o d e l ---------------------"
-                )
-                print(
[…]

### 2024-09-13 getResult/genReLiTu.py
chore: small changes before.changeMechine
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,0 +1,67 @@
+'''
+Author: LetMeFly
+Date: 2024-09-13 23:43:25
+LastEditors: LetMeFly
+LastEditTime: 2024-09-14 01:52:38
+'''
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+# TODO: 使用真实数据
+# 生成模拟数据的评分
+def generate_score_data(num_clients=20, num_malicious=4):
+    scores = np.random.rand(num_clients)  # 随机生成评分
+    
+    # 模拟恶意客户端和良性客户端的评分情况
+    # 恶意客户端评分较高，良性客户端评分较低
+    for i in range(num_clients):
+        if i < num_malicious:  # 恶意客户端
+            scores[i] = np.random.uniform(0.7, 1.0)
+        else:  # 良性客户端
+            scores[i] = np.random.uniform(0.0, 0.3)
+    
+    return scores
+
+# 生成两两客户端对比矩阵 (这里使用绝对差值作为示例)
+def generate_comparison_matrix(scores):
+    num_clients = len(scores)
+    comparison_matrix = np.zeros((num_clients, num_clients))
+    
+    # 计算客户端对之间的评分差异
+    for i in range(num_clients):
+        for j in range(num_clients):
+            comparison_matrix[i, j] = abs(scores[i] - scores[j])  # 使用绝对差值
+            
+    return comparison_matrix
+
+# 创建图像和子图
+fig, axes = plt.subplots(nrows=2, ncols=4, figsize=(20, 10))
+
+# 标题和标签
+attacks = ['NEUROTOXIN', 'MR']
+methods = ['Cosine Similarity Detection', 'FLTrust', 'FLAME', 'SecFFT']
+
+# 生成热力图数据并绘制
+for i in range(2):  # 两行，分别为Attack A和Attack B
+    for j in range(4):  # 四列，分别为四种方法
+        # 生成模拟评分数据
+        scores = generate_score_data()
+        
+        # 生成两两对比矩阵
+        comparison_matrix = generate_comparison_matrix(scores)
+        ax = axes[i, j]
+        
+        # 绘制热力图
+        sns.heatmap(comparison_matrix, ax=ax, cmap='coolwarm', cbar=True, annot=False)
+        
+        # 设置标题和轴标签
+        ax.set_title(f'{attacks[i]} - {methods[j]}', fontsize=12)
[…]

### 2024-09-13 getResult/genReLiTu.py
chore: get updates by pkl&csv

@@ -8,9 +8,8 @@ import numpy as np
 import matplotlib.pyplot as plt
 import seaborn as sns
 
-# TODO: 使用真实数据
 # 生成模拟数据的评分
-def generate_score_data(num_clients=20, num_malicious=4):
+def generate_score_data(num_clients=50, num_malicious=10):
     scores = np.random.rand(num_clients)  # 随机生成评分
     
     # 模拟恶意客户端和良性客户端的评分情况
@@ -23,42 +22,70 @@ def generate_score_data(num_clients=20, num_malicious=4):
     
     return scores
 
-# 生成两两客户端对比矩阵 (这里使用绝对差值作为示例)
-def generate_comparison_matrix(scores):
+# 生成两两客户端对比矩阵 (这里使用余弦相似度作为示例)
+def generate_cosine_similarity_matrix(scores):
     num_clients = len(scores)
-    comparison_matrix = np.zeros((num_clients, num_clients))
+    similarity_matrix = np.zeros((num_clients, num_clients))
     
-    # 计算客户端对之间的评分差异
+    # 计算客户端对之间的余弦相似度
     for i in range(num_clients):
         for j in range(num_clients):
-            comparison_matrix[i, j] = abs(scores[i] - scores[j])  # 使用绝对差值
-            
-    return comparison_matrix
+            if i == j:
+                similarity_matrix[i, j] = 1.0  # 自己与自己的相似度为1
+            else:
+                similarity_matrix[i, j] = 1 - abs(scores[i] - scores[j])  # 使用简单的相似性计算
+                
+    return similarity_matrix
+
+# 生成其他检测方法的评分数组 (FLTrust, FLAME, SecFFT) 并计算相似度矩阵
+def generate_defense_scores_similarity_matrix(num_clients=50, num_malicious=10):
+    scores = np.random.rand(num_clients)  # 随机生成评分
+    
+    # 模拟恶意客户端和良性客户端的评分情况
+    for i in range(num_clients):
+        if i < num_malicious:  # 恶意客户端
+            scores[i] = np.random.uniform(0.7, 1.0)
+        else:  # 良性客户端
+            scores[i] = np.random.uniform(0.0, 0.3)
+    
+    # 计算两两客户端之间的相似度矩阵（这里也用相似度差异作为计算示例）
+    similarity_matrix = np.zeros((num_clients, num_clients))
+    for i in range(num_clients):
+        for j in range(num_clients):
+            if i == j:
[…]

### 2024-09-18 attack-zh.tex
temp: not final
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \usepackage{tabularx}
+\usepackage{lscape}  % 引入 lscape 包以横向显示表格
 \usepackage{array}
@@
 
-考虑在机器人物联网（IoRT）网络中进行视觉语言模型联邦微调的场景下，系统模型包括多个机器人节点和一个中心服务器，机器人节点在本地进行模型微调，并通过中心服务器进行全局聚合。以下是系统模型的详细描述。
+\begin{figure}[htbp]
+    \centering
+    % \includegraphics[width=0.5\textwidth]{figures/fig1.pdf}
+    \label{fig:scenario}
+\end{figure}
+
+如图\ref{fig:scenario}所示，考虑在机器人物联网（IoRT）网络中对视觉大模型进行联邦微调的场景下，整个系统模型包括多个机器人节点和一个中心服务器。每轮，每个机器人节点在本地对视觉大模型进行微调并只上传微调部分的参数更新，随后中心服务器对所有更新进行聚合，然后下发聚合后的参数，开启新一轮的联邦微调。以下是系统模型的详细描述。
 
@@
     \item \textbf{参与者和数据集}：
-    假设系统模型中存在 $n$ 个机器人节点，每个节点记作 $R_i$, $i \in \{1, 2, \ldots, n\}$。 每个机器人节点 $R_i$ 拥有一个本地数据集 $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$，其中 $x_{i,j}$ 表示输入数据，$y_{i,j}$ 表示对应的标签数据，$|D_i|$ 为数据集的大小，$D = \bigcup_{i=1}^{n} D_i$表示整体的数据集。
+    假设系统模型中存在 $N$ 个机器人节点，每个节点记作 $R_i$, 其中$i \in \{1, 2, \ldots, N\}$。 每个机器人节点 $R_i$ 拥有本地数据集 $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$，其中 $x_{i,j}$ 表示输入数据，$y_{i,j}$ 表示对应的标签数据，$|D_i|$ 为数据集的大小，所有节点本地数据集的并集$D = \bigcup_{i=1}^{N} D_i$构成整体数据集。
 
     \item \textbf{LoRA}：
-    在LoRA(Low-Rank Adaptation) 方法中，每一个参数矩阵 $W$ 被表示为：
+    在LoRA(Low-Rank Adaptation) \cite{lora}方法中，每个参数矩阵 $W$ 被表示为：
     \[
@@
     \]
-    其中，$W_0$ 为模型的原始权重矩阵，$\Delta W$ 是低秩增量矩阵，$B$ 和 $A$ 是低秩分解矩阵，$r$ 为矩阵的秩。假设模型原始参数$\Theta = \sum {W_0}$，模型引入的增量参数$\theta = \sum {W}$。在联邦微调过程中，仅对增量参数$\theta$ 进行微调更新，保持原始参数$\Theta$不变。
+    其中，$W_0$ 为模型的原始权重矩阵，$\Delta W$ 是低秩增量矩阵，$B$ 和 $A$ 是低秩分解矩阵，$r$ 为矩阵的秩。在对视觉大模型进行联邦微调的场景中，全局模型原始参数为$\Theta_p = \sum {W_0}$，而LoRA引入的增量参数为$\theta_p = \sum {W}$，因此全局模型的整个参数集为$\Theta = \Theta_p + \theta_g$。在整个联邦微调过程中，仅对全局模型的增量参数$\theta_g$ 进行微调训练，保持原始参数$\Theta_p$不变。
 
@@
     \[
-    f(D_i^b, (\theta_i^{t})^e) = \frac{1}{|D_i^b|} \sum_{j=1}^{|D_i^b|} \ell(x_{i,j}, y_{i,j}; \Theta + (\theta_i^{t})^e)
+    f(D_i^b, (\theta_i^{t})^e) = \frac{1}{|D_i^b|} \sum_{j=1}^{|D_i^b|} \ell(x_{i,j}, y_{i,j}; \Theta_p + (\theta_i^{t})^e)
     \]
@@
     \[
-    \theta_g^t = \theta_g^{t-1} + Aggregate(\triangledown \theta_1^t, \triangledown \theta_2^t, \dots, \triangledown \theta_n^t)
+    \theta_g^t = \theta_g^{t-1} + Agg(\triangledown \theta_1^t, \triangledown \theta_2^t, \dots, \triangledown \theta_n^t)
     \]
-    其中，$Aggregate$表示中心服务器使用到的聚合算法，例如FedAvg、Krum、Bulyan、RoseAgg等，$\theta_g^t$ 是第 $t$ 轮更新的全局增量参数，更新后的全局增量参数 $\theta_g^t$ 将在下一轮训练前下发给所有机器人节点，用于进一步的本地微调。
+    其中，$Agg$表示中心服务器使用到的聚合算法，例如FedAvg、FLTrust\cite{cao2020fltrust}、RoseAgg\cite{yang2024roseagg}等，$\theta_g^t$ 是第 $t$ 轮更新的全局增量参数，更新后的全局增量参数 $\theta_g^t$ 将在下一轮训练前下发给所有机器人节点，用于进一步的本地微调。
 \end{enumerate}
@@
 \begin{itemize}
-    \item Attacker's Goal：假设在对视觉语言模型进行联邦微调的场景中，存在一个或者多个由攻击者操纵的恶意节点。其目标是对全局模型 $\mathbf{F}$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别 $t$，同时尽可能保持对干净输入的分类准确性。
-    \item Attacker's Ability: 在联邦学习场景中，假设攻击者对恶意节点的本地训练过程具有完全的控制权。这意味着攻击者可以任意操控本地数据、触发器模式、优化策略和本地更新过程。此外，攻击者可以采用“智能”攻击策略，这种策略的特点是攻击效果不会在单轮训练中显现，而是通过多轮训练的累积效应逐步将后门植入全局模型中。这种场景在实际中是可能存在的，因为中央服务器只能接收到客户端上传的训练后模型更新，而无法知晓每个客户端的具体训练过程。然而，攻击者无法对中央服务器的操作进行干扰，例如，无法更改全局模型的聚合规则或篡改其他良性客户端的模型更新。
+    \item Attacker's Goal：假设在对视觉语言模型进行联邦微调的场景中，存在一个或者多个由攻击者操纵的恶意节点。其目标是对全局模型$\Theta$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别，即$\Theta(x+\delta) = y'$，其中$x$代表正常输入，$y'$表示目标类别。同时尽可能保持对干净输入的分类准确性，即$\Theta(x) = y$，其中$y$为输出$x$的原始类别。
+    \item Attacker's Ability: 在对视觉大模型进行联邦微调的场景中，假设攻击者对恶意节点的本地训练过程具有完全的控制权。这意味着攻击者可以任意操控本地数据、触发器模式、优化策略和本地更新过程。此外，攻击者可以采用“智能”攻击策略，这种策略的特点是攻击效果不会在单轮训练中显现，而是通过多轮训练的累积效应逐步将后门植入全局模型中。这种场景在实际中是可能存在的，因为中央服务器只能接收到客户端上传的训练后模型更新，而无法知晓每个客户端的具体训练过程。然而，攻击者无法对中央服务器的操作进行干扰，例如，无法更改全局模型的聚合规则或篡改其他良性客户端的模型更新。
 \end{itemize}
@@
 % 联邦学习
-$ n $ & The number of the nodes participating during each round. \\ \hline
+$ N $ & The number of the nodes participating during each round. \\ \hline
 % $\mathcal{M}$ & The number of the participants during each round. \\ \hline
@@
 % 单论识别
-$\theta_i^t$ & The local model of participant at round $t$. \\ \hline
+$\theta_g^t, \theta_i^t$ & The global model, the local model of participant $R_i$ at round $t$. \\ \hline
 $\triangledown \theta_i^t$ & The local update of node $R_i$ during the $t$-th round. \\ \hline
@@
 $m$ & The length of the low-frequency components. \\ \hline
-$H^t$ & The matrix formed by stacking $G_i^t$, with a shape of $m \times n$ during the $t$-th round. \\ \hline
+$H^t$ & The matrix formed by stacking $G_i^t$, with a shape of $m \times N$ during the $t$-th round. \\ \hline
 $\tilde{G}_{0}^t $ & The clean ingredient extracted from the nodes' low-frequency components during the $t$-th round. \\ \hline
@@
 $\xi_{max}^t$ & The corresponding left singular vector of singular value $\lambda_{max}^t$ during the $t$-th round. \\ \hline
-$P_i^t$ & The distribution corresponding to $G_i^t$ after applying the Softmax function during the $t$-th round.. \\ \hline
-$Q^t$ &  The distribution corresponding to $\tilde{G}_{0}^t$ after applying the Softmax function during the $t$-th round.. \\ \hline
-$O_t'$ &  The center of the high dimensional ball $t'$-th round. \\ \hline
-\( {v}_{i}^{t'} \) & The vector of the high dimensional ball $t'$-th round.\\ \hline
-$lof_i$ & The LOF score of the $i$-th node\\ \hline
-$cre_i$ & The confidence of the $i$-th node\\ \hline
+$Chi_i^t$ & The distance difference between Node $R_i$'s Update and the clean ingredient during the $t$-th round. \\ \hline
+% $P_i^t$ & The distribution corresponding to $G_i^t$ after applying the Softmax function during the $t$-th round.. \\ \hline
+% $Q^t$ &  The distribution corresponding to $\tilde{G}_{0}^t$ after applying the Softmax function during the $t$-th round.. \\ \hline
+$t'$ & One round of the total $T$ rounds. \\ \hline
+$O_i^{t'}$ &  The center of the high dimensional ball $t'$-th round of robot node $i$. \\ \hline
+\( {v}_{i}^{t'} \) & The vector of the high dimensional ball $t'$-th round of robot node $i$.\\ \hline
+$lof_i$ & The LOF score of the $i$-th node.\\ \hline
+$cre_i$ & The confidence of the $i$-th node.\\ \hline
 
@@
 \subsection{单轮恶意节点识别}
-\textbf{Motivation}: 目前的防御策略主要集中于利用攻击的“浅层语义特征”来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向，范数以及神经元符号等几何或者统计特性。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。
+\textbf{Motivation}: 目前的防御策略主要集中于利用攻击的“浅层语义特征”来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向，范数以及更新符号等几何或者统计特性。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。
 % Multi-metrics adaptively identifies backdoors in Federated learning
-首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终具有分布上的差异。
+首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明\cite{huang2023multi}，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。但值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终在某种分布上具有偏移。
 
-\textbf{Overview}: 为解决基于浅层语义特征的防御方法在高维空间中面临的局限性，我们从后门攻击的本质出发，提出了一种基于深层语义特征的防御策略，重点分析模型更新在频率域上的分布差异。通过将本地模型更新转换到频域，我们能够更深入地捕捉恶意更新在低频成分上的异常表现，这些异常通常难以通过传统的浅层特征检测方法发现。通过对频率域上的特征进行分析，我们可以有效地区分出恶意节点与良性节点，从而增强联邦学习系统在面对复杂后门攻击时的鲁棒性和检测精度。
+\textbf{Overview}: 在深度神经网络模型中，每个权重代表两个神经元之间连接的强度。权重分布及其相关的能量在训练过程中会经历动态演变，以缩小模型预测结果与训练数据中的真实目标之间的差距。当后门攻击迫使神经网络模型学习一种在正常数据中不存在的关联模式时，根据后门触发器的设计和实现方式，这种模式可能是微妙的，也可能是相当明显的，但无论如何，它都代表了与模型从正常数据中学习到的模式的偏离。因此，为解决基于浅层语义特征的防御方法在高维空间中面临的局限性，我们从后门攻击的本质出发，提出了一种基于深层语义特征的防御策略，重点分析模型更新在频率分布上的差异。通过将本地模型更新转换到频域，我们能够更深入地捕捉恶意更新在低频成分上的异常表现，这些异常通常难以通过传统的浅层特征检测方法发现。通过对频率域上的特征进行分析，我们可以有效地区分出恶意节点与良性节点，从而增强联邦学习系统在面对复杂后门攻击时的鲁棒性和检测精度。
 
-\begin{algorithm}
-\caption{Malicious Node Detection via DCT}
-\label{alg:malicious-node-detection}
-\begin{algorithmic}[1]
-\State \textbf{Input:} $d$, $n$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$, $m$ \Comment{$d$ is the dimension of each node update; $n$ is the number of the nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$is the local updates from nodes during the $t$-th round; $m$ is the length of low-frequency components}
-\State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
-
-\State Step 1: Frequency Domain Transformation
-\For {Node $R_i$}
-    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
-    \State $G_i^t = Trunc(DCT(\bar{\theta_i^t}), m)$ \Comment{Compute DCT and retain only the top $m$ low-frequency components}
-\EndFor
-
-\State
-
-\State Step 2: Clean Ingredient Extraction
-\State $H^t \gets (G_0^t, G_1^t, \ldots, G_{n}^t) \in \mathbb{R}^{d \times m}$ \Comment{Stacking to form Matrix $H^t$.}
-
-\State $\hat{H}^t \gets (H^t)^{T} H^t$
-\State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
-\State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
-
-\State
-
-\State Step 3: Kullback-Leibler Divergence Calculation
-\State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
-\For {Node $R_i$}
-    \State $Ki \gets \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)$
-\EndFor
-\State $S \gets \{KL_1, KL_2, \ldots, KL_n\}$ \Comment{The distribution differences calculated by KL divergence.}
-
-\State
-
-\State Step 4: Malicious Node Detection
-\State $\{C_1, C_2, \ldots, C_K\} \gets \text{HDBSCAN}(S)$
-\State $U_{nor} \gets C_{\text{max}}$, $U_{mal} \gets \{C_i \, | \, i \neq \text{max}\}$
-
-\end{algorithmic}
-\end{algorithm}
-算法\ref{alg:malicious-node-detection}展示了整体的恶意用户识别过程，主要包含四个步骤：Frequency Domain Transformation, Clean Ingredient Extraction, Kullback-Leibler Divergence Calculation,Single-round Malicious Node Detection。
 \begin{enumerate}
 \item \textbf{Frequency Domain Transformation}：
-相比于目前基于浅层语义特征的防御方法，我们利用DCT进行频域转换，将模型的更新向量映射到频域空间，以探究其在频率域上的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的4-7行所示，假设每个本地模型的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，通过一维的DCT-II将其转换为对应的频率分布，并提取低频分量，得到频率向量\(G_i^t\)。这里的 $Trunc$ 操作表示仅保留前 $m$ 个低频分量，以捕捉频域中更具代表性的特征用于后续的恶意节点检测。
+% 相比于目前基于浅层语义特征的防御方法，我们利用DCT进行频域转换，将模型的更新向量映射到频域空间，以探究其在频率域上的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的4-7行所示，假设每个本地模型的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，通过一维的DCT-II将其转换为对应的频率分布，并提取低频分量，得到频率向量\(G_i^t\)。这里的 $Trunc$ 操作表示仅保留前 $m$ 个低频分量，以捕捉频域中更具代表性的特征用于后续的恶意节点检测。
+受高维空间中维度灾难的影响，传统的基于距离度量的方法已无法有效识别恶意节点。相反，将模型更新转换到频率域后，其差异将主要集中在低频成分上。因此，专注于低频成分的分析，在提升识别准确率的同时，将显著的降低计算开销。假设每个节点上传的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，对其进行归一化，然后通过一维的DCT-II\cite{ahmed1974discrete}变化将其转换为对应的频率分布，并提取$m$个低频分量，例如5000，得到低频向量\(G_i^t\)。
 
 % 对应的计算过程如下：
-% \begin{equation}
-% G_i^t = Trunc(DCT(Flatten(\triangledown \theta_i^t), m)
-% \end{equation}
+\begin{equation}
+G_i^t = Trunc(DCT(Flatten(\frac{\triangledown \theta_i^t}{{\|\triangledown \theta_i^t\|}_2}), m)
+\label{eq:DCT}
+\end{equation}
 
+频域转换的主要过程如公式\ref{eq:DCT}所示，这里的 $Trunc$ 操作表示仅保留前$m$个低频分量。
 % \begin{equation}
@@
 
-\item \textbf{Clean Ingredient Extraction}：在将模型更新向量转换到频域空间后，我们基于“恶意节点的数量少于良性节点”的假设，通过奇异值分解（SVD）从所有节点的频域向量中提取出“干净成分”，并以此作为区分恶意与良性节点的标准。其主要过程如算法\ref{alg:malicious-node-detection}的10-13行所示，将所有节点的频率向量堆叠为矩阵 \(H^t = ({G_0^t}, {G_1^t}, \ldots, {G_{n}^t}) \in \mathbb{R}^{d \times n}\)，其中每一列代表一个节点的低频向量。通过计算矩阵的最大奇异值及其对应的左奇异向量来作为相应的干净成分。即计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)，根据公式\ref{equation:singular}，得到干净成分 \(\tilde{G}^t\)。这个干净成分\(\tilde{G}^t\)表示了良性节点的主要成分，能够有效地与恶意节点的异常行为区分开来，从而用于后续的恶意节点检测。
-
+\item \textbf{Clean Ingredient Extraction}：在提取到节点更新对应的低频向量\(G_i^t\)后，我们使用流行的聚类算法例如HDBSCAN\cite{mcinnes2017hdbscan}对这些更新进行聚类，得到多个簇$C_0^t, C_1^t, \ldots, C_{\kappa}^t$，其中$\kappa$表示簇的数量。在大多数联邦学习场景中，良性节点的数量通常多于恶意节点的数量，且良性节点的更新通常更接近全局模型的方向并表现出更高的聚集性。基于这一观察，我们选择节点数量最多的簇$C_{max} = \{R_{i_0}, R_{i_1}, \ldots, R_{i_n}\}$作为主要分析对象。为了进一步提取该簇的主要特征或模式，我们对其中所有节点组成的矩阵进行奇异值分解。由于，SVD分解的左奇异向量$\tilde{G}^t$对应于数据的主要方向，因此，$\tilde{G}^t$可以作为良性节点在低频域内的主要特征。
+% 计算出矩阵\(\hat{H}^t = (H^t)^{T} H^t\)最大特征值 \(\lambda_{\text{max}}\) 及其对应的特征向量 \(\xi_{\text{max}}\)，根据公式\ref{equation:singular}，得到干净成分 \(\tilde{G}^t\)。
 \begin{equation}
-\tilde{G}^t = \frac{H^t \xi_{\text{max}}}{\sqrt{\lambda_{\text{max}}}}
-\label{equation:singular}
+\tilde{G}^t = \frac{H^t \xi_{\text{max}^t}}{\sqrt{\lambda_{\text{max}^t}}}
+\label{eq:singular}
 \end{equation}
 
-\item \textbf{Kullback-Leibler Divergence Calculation}：在得到干净分量后，我们计算每个节点的频率向量与干净成分之间的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的16-20行所示，对于每个节点的低频向量\(G_i^t\)以及上一步求得的干净成分\(\tilde{G}^t\)，通过Softmax函数来将它们转换为相应的概率分布 \(P_i^t\) 和 \(Q^t\) 。然后利用KL散度计算每个节点概率分布\((P_i^t\)和干净分量概率分布 \(Q^t\) 之间的距离，得到相应的分布差异集合\(S = ({{KL}}_1, {{KL}}_2, \ldots, {{KL}}_n)\)。这个集合反映了每个节点频率向量相对于干净成分的异常程度，较大的KL散度值表示节点对应的频率向量与干净成分的分布差异较大，提示该节点可能是恶意节点。最终，这些分布差异将作为恶意节点检测的基础，通过进一步分析来区分良性节点和潜在的恶意节点。
+公式\ref{eq:singular}展示了计算左奇异向量$\tilde{G}^t$的主要过程，其中\(H^t = ({G_{i_0}^t}, {G_{i_1}^t}, \ldots, {G_{i_n}^t}) \in \mathbb{R}^{m \times n}\)为该簇节点的低频向量堆叠而成的矩阵，其中每一列代表一个节点的低频向量，$\lambda_{max}^t$与$xi_{max}^t$分别对应了矩阵$\hat{H}^t \gets (H^t)^{T} H^t$的最大特征值及其特征向量。通过这种方式，我们有效地提取了反映良性节点全局更新在频域上的主要特征，并将$\tilde{G}^t$作为“干净成分”，为后续恶意节点检测提供基准依据。
 
-% \begin{equation}
-% {{KL}}_i = D(P_i^t \| Q^t) = \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)
-% \label{equation:KL}
-% \end{equation}
+\item \textbf{Chi-square distance calculation}：
+% 在得到“干净成分”后，我们计算每个节点的低频向量与“干净成分”之间的差异度。对于每个节点的低频向量\(G_i^t\)以及上一步求得的干净成分\(\tilde{G}^t\)，
+我们利用每个节点的低频向量与“干净成分”之间的差异度来作为衡量恶意节点和良性节点的依据。对于每个节点的低频向量 \(G_i^t\) 以及上一步中求得的“干净成分” \(\tilde{G}^t\)，通过卡方距离来计算两者之间的差异度，得到距离差异集合$S^t = Chi^t_i, Chi^t_2, \ldots, Chi^t_N$。卡方距离的计算公式为：
+% Chi-square distance
+\begin{equation}
+{Chi^t_i}^2 = \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}
+\label{equation:KL}
+\end{equation}
+
+其中 \(m\) 是低频向量的维度，\(\epsilon\) 是一个小的常数，用于避免分母为零。相比于传统的欧氏距离，卡方距离根据两个向量对应分量的大小进行加权，使得特征值较大的部分对距离的影响更大，从而能够更准确地反映低频向量中重要特征之间的差异，同时忽略不重要的噪声成分。
 
@@
 
-\item \textbf{Single-round Malicious Node Detection}：为了进一步识别恶意节点，我们利用良性节点与干净成分的分布高度相似这一特性，对分布差异集合$S$进行聚类分析。具体来说，我们采用流行的HDBSCAN算法对计算得到的KL散度集合$S$进行聚类，主要过程如算法\ref{alg:malicious-node-detection}的23-24行所示。聚类结果为多个簇\(C_1, C_2, \ldots, C_K\)，从所有簇中选出最大的一簇（即包含节点数量最多的簇），记作 \(C_{max}\)。基于良性节点在每轮训练中数量通常多于恶意节点的假设，以及良性节点与干净成分之间的KL散度通常更为相似，我们将 \(C_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)。对于其他所有簇\(C_i\)（\(i \neq {max}\)），其中的所有节点则被标记为恶意节点，记作\(U_{mal}\)。
+\item \textbf{Single-round Malicious Node Detection}：为了准确地识别恶意节点，我们利用良性节点的更新与干净成分的频率分布高度相似这一特性，对距离差异集合$S^t$进一步进行聚类分析。具体而言，我们采用流行的KMeans聚类算法对距离差异集合$S^t$进行聚类，并将类别数设置为2，因此聚类结果为两个簇\(C'_1, C'_2\)。基于在每轮训练中良性节点的数量通常多于恶意节点，以及良性节点与干净成分之间的距离差异通常更小，我们将 \(C'_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)。对于另一簇\(C'_k\)（\(k \neq {max}\)），则将其中所有节点标记为恶意节点，记作\(U_{mal}\)。
 
 % TODO 总结
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=0.4\textwidth]{img/t_sne_indicative_layer_round_0.png}
-    \hspace{0.1in}
-    \includegraphics[width=0.4\textwidth]{img/t_sne_dct_round_0.png}
-    \caption{Result}
-\end{figure}
+% \begin{figure}[htbp]
+%     \centering
+%     \includegraphics[width=0.4\textwidth]{img/t_sne_indicative_layer_round_0.png}
+%     \hspace{0.1in}
+%     \includegraphics[width=0.4\textwidth]{img/t_sne_dct_round_0.png}
+%     \caption{Result}
+% \end{figure}
 
@@
 \end{enumerate}
+
+算法\ref{alg:malicious-node-detection}展示了单轮恶意用户识别的整体过程，其中3-6行代表了频率转换的计算过程，7-12行代表了“干净分量”$\tilde G^t$的计算过程，13-16行代表了每个用户与“干净分量”间的卡方差异度的计算过程，最后17-18行代表了通过KMeans聚类算法进行恶意用户检测的计算过程。
+
+\begin{algorithm}
+\caption{Malicious Node Detection via DCT}
+\label{alg:malicious-node-detection}
+\begin{algorithmic}[1]
+\State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each node update; $N$ is the number of the nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from nodes during the $t$-th round; $m$ is the length of low-frequency components}
+\State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
+
+% \State Step 1: Frequency Domain Transformation
+\For {Node $R_i$}
+    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
+    \State $G_i^t = Trunc(DCT(\bar{\theta_i^t}), m)$ \Comment{Compute DCT and retain only the top $m$ low-frequency components}
+\EndFor
+
+% \State
+
+% \State Step 2: Clean Ingredient Extraction
+\State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering (\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t)$
+\State $ C_{max} = \underset{C_i}{\arg\max} \, |C_i|, \quad i = 1, 2, \ldots, \kappa $ \Comment{$|C_i|$ denotes the number of nodes in cluster $C_i$}
+\State $H^t \gets (G_0^t, G_1^t, \ldots, G_{n}^t) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $\quad R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C_{max}$.}
+
+\State $\hat{H}^t \gets (H^t)^{T} H^t$
+\State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
+\State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
+
+% \State
+
+% \State Step 3: Chi-square distance calculation
+% \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
+\For {Node $R_i$}
+    \State ${Chi}_i^2 \gets \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}$
+\EndFor
+\State $S \gets \{Chi_1, Chi_2, \ldots, Chi_n\}$ \Comment{The Distance differences calculated by Chi-square distance.}
+
+% \State
+
+% \State Step 4: Malicious Node Detection
+\State $\{C_1, C_2\} \gets KMeans(S, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
+\State $U_{nor} \gets C_{\text{max}}$, $U_{mal} \gets \{C_i \, | \, i \neq \text{max}\}$
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 \begin{equation}
-    w_i=\frac{cre_i'}{\sum_{i=1}^{n}cre_i'},
+    w_i=\frac{cre_i'}{\sum_{i=1}^{N}cre_i'},
 \end{equation}
@@
 \begin{equation}
-    \theta_g^t = \theta_g^{t-1}+\sum_{i=1}^{n}w_i\triangledown \theta_i^t,
+    \theta_g^t = \theta_g^{t-1}+\sum_{i=1}^{N}w_i\triangledown \theta_i^t,
 \end{equation}
@@
 
-\subsection{EXPERIMENTAL EVALUATION}
+\section{EXPERIMENTAL EVALUATION}
 
-\subsubsection{Experimental Setup}
+This section presents a thorough evaluation of SecFFT on two benchmark datasets, aiming to illustrate its effectiveness.
 
-\subsubsection{硬件设施}
-
-本实验在一台Ubuntu操作系统的服务器上进行，28核心128GB内存，以及2块NVIDIA GeForce RTX 3090 GPU。
-
-\subsubsection{基本设置}
+\subsection{Experimental Setup}
 
@@
 \begin{itemize}
-    \item \textbf{数据集}：我们使用了MNIST和CIFAR-10数据集。MNIST数据集包含60,000张28x28像素的灰度手写数字图像，分为10个类别。CIFAR-10【TODO:引用】数据集包含60,000张32x32像素的彩色图像，分为10个类别。
+    \item \textbf{数据集}：我们使用FMNIST\cite{minist}和CIFAR-10\cite{cifar10}数据集作为实验数据集。FMNIST数据集包含60,000张28x28像素的灰度时尚商品图像，共分为10个类别，其中50,000张为训练集，10,000张为测试集。CIFAR-10数据集包含60,000张32x32像素的彩色图像，也分为10个类别，其中50,000张为训练集，10,000张为测试集。
 
-    \item \textbf{模型}：在MNIST和CIFAR-10数据集上，我们使用了Vision Transformer (ViT) 模型，并使用LOAR进行微调。ViT 是一种基于 Transformer 架构的图像分类模型，它将图像划分为固定大小的patch，并将其输入到Transformer编码器中进行处理。
+    \item \textbf{微调模型}：我们采用CLIP的CLIP-ViT-B/32\cite{huggingface_clip}模型作为微调所使用的预训练模型。CLIP是一种通过对比学习在文本和图像数据上进行预训练的模型，能将自然语言和视觉信息映射到同一特征空间中。CLIP-ViT-B/32基于ViT\cite{vit}架构，包含12层Transformer编码器，隐藏层维度为768，多头注意力头数为12，使用32x32的图像块作为输入。在微调过程中，我们使用LORA\cite{lora}方案仅在Vision Encoder部分插入低秩矩阵，保持Textual Encoder不变。我们设定低秩矩阵的秩为16，学习率为$10^{-3}$，以在有限计算资源下高效微调模型，使其更好地适应特定任务的数据分布。
 
-    \item \textbf{联邦相关机制（聚合算法）}：我们采用了经典的联邦平均（Federated Averaging, FedAvg）算法作为聚合机制。FedAvg算法通过聚合每个客户端在本地计算的模型更新，来生成全局模型。
+    \item \textbf{攻击假设}：对于单轮恶意用户检测，我们使用包括MR\cite{MR}、EDGE CASE\cite{EDGE_CASE}、以及NEUR\cite{zhang2022neurotoxin}在内的三种针对联邦学习场景的最新攻击。MR攻击通过将中毒图像与正常图像混合来创建恶意数据集，并使用投影梯度下降法进行本地训练来达到植入后门的效果；EDGE CASE攻击利用罕见的“边缘情况”样本，通过数据或模型投毒在联邦学习模型中插入后门；Neurotoxin攻击则尝试通过识别在正常节点训练中不常更新的参数，并利用这些参数插入后门，以提高后门的持久性。
+
+    \item \textbf{对比算法}：对于单轮恶意用户检测算法，我们对比了三种聚合算法：FedAVG\cite{FedAVG}、FLTrust\cite{FLTrust}和Flame\cite{FLAME}。FedAVG根据每个节点数据集的大小对其上传的更新进行加权聚合；FLTrust利用一个干净的数据集，仅聚合那些上传更新与该干净数据集上训练所得更新余弦相似度较高的节点；而Flame则通过模型聚类和权重剪裁来估计并注入适量噪声，有效消除联邦学习中的后门攻击。
+
+    \item \textbf{评估指标}：
+
+    % \item \textbf{联邦相关机制（聚合算法）}：我们采用了经典的联邦平均（Federated Averaging, FedAvg）算法作为聚合机制。FedAvg算法通过聚合每个客户端在本地计算的模型更新，来生成全局模型。
 
@@
 
-\subsubsection{参数取值表}
+\subsection{硬件设施}
 
-\[
-\begin{array}{|c|c|c|}
+本实验在一台Windows操作系统的服务器上进行，28核心128GB内存，以及2块NVIDIA GeForce RTX 3090 GPU(24G)。
+
+\subsection{参数取值表}
+
+% \begin{table*}{|c|c|c|c|c|c|c|c|}
+% \hline
+% & \text{学习率} & \text{全局轮次} & \text{本地批次} & \text{客户端数量} & \text{批次大小} & \text{优化器} & \text{模型} \\
+% \hline
+% \text{MNIST} & 0.01 & 50 & 5 & 20 & 64 & \text{SGD} & \text{ViT} \\
+% \text{CIFAR-10} & 0.01 & 50 & 5 & 20 & 64 & \text{SGD} & \text{ViT} \\
+% \hline
+% \end{table}
+
+\begin{table*}[t]  % 使用 table* 环境，并选择 t 位置选项
+\small
+\centering
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}  % 使用 \textwidth
 \hline
-\text{参数} & \text{MNIST} & \text{CIFAR-10} \\
+& 学习率 & 全局轮次 & 本地批次 & 客户端数量 & 批次大小 & 优化器 & 模型 \\
 \hline
-\text{学习率} & 0.01 & 0.01 \\
-\text{全局轮次} & 50 & 50 \\
-\text{本地批次} & 5 & 5 \\
-\text{客户端数量} & 20 & 20 \\
-\text{批次大小} & 64 & 64 \\
-\text{优化器} & \text{SGD} & \text{SGD} \\
-\text{模型} & \text{ViT} & \text{ViT} \\
+MNIST & 0.01 & 50 & 5 & 20 & 64 & SGD & ViT \\
+CIFAR-10 & 0.01 & 50 & 5 & 20 & 64 & SGD & ViT \\
 \hline
-\end{array}
-\]
-
-TODO:写成竖排的
+\end{tabularx}
+\caption{参数取值表}
+\end{table*}
 
@@
 
-\begin{table}[h!]
+\begin{table*}[h!]
 \small
 \centering
-\begin{tabularx}{0.5\textwidth}{|X|X|X|}
+\begin{tabularx}{\textwidth}{|l|X|X|X|}
 \hline
-\textbf{指标名称} & \textbf{计算公式} & \textbf{说明} \\ \hline
+\textbf{指标名称} & \textbf{计算公式} & \textbf{说明} & \textbf{优化方向} \\ \hline
+
+真阳性（True Positive, TP） & 
+--- & 
+实际为正例且预测为正例的样本数量。 & 越大越好。 \\ \hline
+
+真阴性（True Negative, TN） & 
+--- & 
+实际为负例且预测为负例的样本数量。 & 越大越好。 \\ \hline
+
+假阳性（False Positive, FP） & 
+--- & 
+实际为负例但预测为正例的样本数量。 & 越小越好。 \\ \hline
+
+假阴性（False Negative, FN） & 
+--- & 
+实际为正例但预测为负例的样本数量。 & 越小越好。 \\ \hline
+
 准确率（Accuracy） & 
 $\frac{\text{TP} + \text{TN}}{\text{TP} + \text{TN} + \text{FP} + \text{FN}}$ & 
-模型预测正确的样本占总样本的比例，适用于类别平衡的数据集。准确率越大越好。 \\ \hline
+模型预测正确的样本占总样本的比例，适用于类别平衡的数据集。 & 越大越好。 \\ \hline
 
@@
 $\frac{\text{TP}}{\text{TP} + \text{FP}}$ & 
-被预测为正例的样本中实际为正例的比例。精确率越大越好，特别是在关注减少误报的应用中。 \\ \hline
+被预测为正例的样本中实际为正例的比例，反映模型对正类结果的准确性。 & 越大越好，特别是在关注减少误报的应用中。 \\ \hline
 
@@
 $\frac{\text{TP}}{\text{TP} + \text{FN}}$ & 
-实际正例中被正确预测为正例的比例。召回率越大越好，特别是在关注减少漏报的应用中。 \\ \hline
+实际正例中被正确预测为正例的比例，反映模型对正类样本的覆盖能力。 & 越大越好，特别是在关注减少漏报的应用中。 \\ \hline
 
@@
 $\frac{\text{TN}}{\text{TN} + \text{FP}}$ & 
-实际负例中被正确预测为负例的比例。特异度越大越好。 \\ \hline
+实际负例中被正确预测为负例的比例，反映模型对负类样本的识别能力。 & 越大越好。 \\ \hline
 
@@
 $\frac{\text{FP}}{\text{FP} + \text{TN}}$ & 
-实际负例中被错误预测为正例的比例。误报率越小越好。 \\ \hline
+实际负例中被错误预测为正例的比例，衡量模型的误报情况。 & 越小越好。 \\ \hline
 
@@
 $\frac{\text{FN}}{\text{FN} + \text{TP}}$ & 
-实际正例中被错误预测为负例的比例。假阴率越小越好。 \\ \hline
+实际正例中被错误预测为负例的比例，衡量模型的漏报情况。 & 越小越好。 \\ \hline
+
+ROC（Receiver Operating Characteristic） & 
+--- & 
+反映分类模型在各种阈值下的性能，通过真阳率（召回率）和假阳率（FPR）之间的权衡来评估。ROC曲线越靠近左上角，模型性能越好。 & 越靠近左上角越好。 \\ \hline
+
+AUC（Area Under Curve） & 
+--- & 
+ROC曲线下的面积，取值范围为0.5到1，越接近1表示模型性能越好。 & 越接近1越好。 \\ \hline
+
+MCC（Matthews Correlation Coefficient） & 
+$\frac{(\text{TP} \times \text{TN}) - (\text{FP} \times \text{FN})}{\sqrt{(\text{TP} + \text{FP})(\text{TP} + \text{FN})(\text{TN} + \text{FP})(\text{TN} + \text{FN})}}$ & 
+MCC的值范围为-1到1，1表示完美分类，0表示随机猜测，-1表示完全错误的分类。 & 越接近1越好。 \\ \hline
 
 \end{tabularx}
-\caption{分类模型性能衡量指标}
-\end{table}
+\caption{分类模型性能衡量指标总结}
+\end{table*}
 
-TODO: 再多写几个
+% \begin{tabular}{|c|c|c|}
+% \hline
+% 攻击方式 & 防御方式 & 值 \\
+% \hline
+% \multirow{3}{*}{攻击1} & 防御1 &  \\ 
+%                        & 防御2 &  \\ 
+%                        & 防御3 &  \\ 
+% \hline
+% \multirow{3}{*}{攻击2} & 防御1 &  \\ 
+%                        & 防御2 &  \\ 
+%                        & 防御3 &  \\ 
+% \hline
+% \end{tabular}
+
+\begin{table*}[h!]
+\small
+\centering
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+\textbf{攻击方式} & \textbf{防御方式} & \textbf{FP} & \textbf{TP} & \textbf{FN} & \textbf{TN} & \textbf{准确率} & \textbf{精确率} & \textbf{召回率} & \textbf{特异度} & \textbf{误报率} & \textbf{假阴率} & \textbf{AUC} & \textbf{MCC} \\ \hline
+
+\multirow{3}{*}{攻击1} & 防御1 & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\ \cline{2-14}
+                       & 防御2 & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\ \cline{2-14}
+                       & 防御3 & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\ \hline
+
+\multirow{3}{*}{攻击2} & 防御1 & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\ \cline{2-14}
+                       & 防御2 & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\ \cline{2-14}
+                       & 防御3 & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\ \hline
+\end{tabular}
+\caption{不同攻击方式和防御方式下的分类指标结果}
+\end{table*}
 

### 2024-09-18 main-v2.tex
temp: not final
Signed-off-by: LetMeFly666 <814114971@qq.com>

--- 2024-09-11 main-v2.tex
@@
 
-\title{SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Stealthy Backdoor Attacks in IoRT Networks}
+\title{SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks}
 
 \author{Zan Zhou, %~\IEEEmembership{Student Member,~IEEE}, 
-Yao Su, Shujie Yang, Bo Wang, Tengfei Li, Changqiao Xu,~\IEEEmembership{Senior Member,~IEEE}
+ Bo Wang, Tengfei Li, Shujie Yang, Changqiao Xu, Su Yao, 
 % <-this % stops a space
@@
 % \thanks{L. Zhong is with the Information Engineering College, Capital Normal University, Beijing 100048, China. E-mail: zhonglj@cnu.edu.cn (Corresponding author).}% <-this % stops a space
-\thanks{Zhenhui Yuan is with Northumbria University, United Kingdom. E-mail: zhenhui.yuan@warwick.ac.uk.}% <-this % stops a space
+\thanks{Su Yao is with Tsinghua University, China. E-mail: XXXX@xxx.}% <-this % stops a space
 %\thanks{This paper was produced by the IEEE Publication Technology Group. They are in Piscataway, NJ.}% <-this % stops a space
@@
 \begin{abstract}
-
-Fairness-aware federated learning (FFL) plays a crucial role in mitigating bias against specific demographic groups (e.g., gender, race, occupation) during collaborative training. 
-Along with the ever-emerging new attack paradigms like gradient leakage and model poisoning, the reliability of FFL also obtains lots of research attention.
-Either UAV nodes or FFL aggregators could be untrusted adversaries.
-Although multiple security mechanisms involving encryption, obfuscation, Byzantine-robustness, and detection have been proposed, concrete to UAV networks, the majority of existing solutions are unfeasible due to high heterogeneity and limited resources among participants.
-Hence, in this paper, we propose mutually reliable FFL (MR-FFL), a stratified community-based framework to facilitate privacy protection (FFL aggregator's reliability) and poisoning elimination (client nodes' reliability) jointly for FFL in heterogeneous UAV networks.
-We first divide UAV nodes into both peer communities (PC) and colleague communities (CC) according to cross-participant similarity and task-oriented fitness, respectively. 
-Thus, the arbitrarily settled learning tasks following fair principles can be efficiently completed by fine-tuned colleague communities, even in the presence of a large degree of heterogeneity among peer communities.
-Then, we integrate community-specific differential privacy into the MR-FFL process, to achieve privacy amplification as well as efficient and personal collaborative training at the same time. 
-More importantly, we proposed a community-based credit evaluation to resist poisoning attacks in heterogeneous environments. 
-The results on several standard datasets also highlight the performance of MR-Fed in terms of fairness, accuracy, and integrity jointly.
-
-% Fairness-aware federated learning (FFL) assumes a pivotal role in mitigating bias directed at specific demographic groups (e.g., gender, race, occupation) during collaborative training.
-The escalating threat landscape, characterized by emerging attack paradigms like gradient leakage and model poisoning, intensifies research scrutiny on FFL's reliability, recognizing the potential untrustworthiness inherent in UAV nodes and FFL aggregators.
-% Despite a plethora of proposed security mechanisms encompassing encryption, obfuscation, Byzantine robustness, and detection, their pragmatic application within UAV networks faces challenges due to pronounced heterogeneity and resource constraints among participants.
-Consequently, this paper introduces a novel approach, termed mutually reliable FFL (MR-FFL), presenting a stratified community-based framework.
-This framework concurrently addresses privacy protection (FFL aggregator's reliability) and poisoning elimination (edge nodes' reliability) within the context of FFL in heterogeneous UAV networks.
-% The categorization of UAV nodes into peer communities and colleague communities based on cross-participant similarity and task-oriented fitness facilitates the efficient completion of learning tasks adhering to fair principles.
-This effectiveness persists even in the presence of considerable heterogeneity among peer communities.
-Additionally, community-specific differential privacy is integrated into the MR-FFL process, achieving simultaneous privacy amplification and efficient, personalized collaborative training.
-% A noteworthy contribution lies in the introduction of a community-based credit evaluation system, designed to resiliently counteract poisoning attacks in heterogeneous environments.
-Empirical evaluations on standard datasets underscore the comprehensive performance of MR-Fed, highlighting its effectiveness in promoting fairness, privacy, and integrity within federated learning systems.
+%攻击者
+
+Fairness-aware federated learning (FFL) plays a crucial role in miti
 
@@
 This evolution has become one of the critical developmental trends for Internet of Robotic Things (IoRT) networks.
-Large Vision Language Model (LVLM), as an emerging and popular image perception and object recognition technology, has the potential to be an indispensable foundation supporting intelligent robots in understanding and interpreting their surrounding environments.
+Meanwhile, the Large Vision Language Model (LVLM), as an emerging and popular image perception and object recognition technology, has the potential to be an indispensable foundation supporting intelligent robots in understanding and interpreting their surrounding environments.
 
 %视觉大模型极大地增强了机器人的视觉语义理解能力，使其能够对多模态任务进行更加智能化的决策响应，然而在真实应用环境中，仍存在以下问题：1）由于真实世界的多样性和异构性，通用大模型在特定任务上往往无法较好迁移通用知识，需要进行微调才能显著提升识别精度（例如，针对动目标检测任务，交通机器人主要针对车辆、行人，而工厂机器人则主要针对机床，两者轮廓、行为模式范围均存在较大差异）；2）此外，将来自不同源头的离散化、碎片化分布的海量数据进行传输并汇聚于主服务器，将会导致巨大的通信开销和时间延迟，无法满足具身智能业务的需求，且存在潜在的隐私风险。
-Vision foundation models significantly enhance the visual semantic understanding capabilities of robots, enabling them to make more intelligent decisions in multimodal tasks.
-However, there are still challenges in real-world applications: 1) Due to the diversity and heterogeneity of the real world, general foundation models often cannot effectively transfer their general knowledge to specific tasks, necessitating fine-tuning to significantly improve recognition accuracy (for example, traffic robots primarily focus on vehicles and pedestrians for moving object detection tasks, while factory robots mainly target machine tools, with significant differences in their contours and behavioral patterns); 2) Additionally, transmitting and aggregating massive amounts of discretized and fragmented data from different sources to a central server can result in significant communication overhead and latency, failing to meet the demands of embodied intelligence applications and posing potential privacy risks.
+Although LVLMs significantly enhance the visual semantic understanding capabilities of robots, enabling them to make more intelligent decisions in multi-modal tasks, there are still challenges in real-world applications: 1) Due to the diversity and heterogeneity of the real world, general foundation models often cannot effectively transfer their general knowledge to specific tasks, necessitating fine-tuning to significantly improve recognition accuracy (for example, traffic robots primarily focus on vehicles and pedestrians for moving object detection tasks, while factory robots mainly target machine tools, with significant differences in their contours and behavioral patterns); 2) Additionally, transmitting and aggregating massive amounts of discretized and fragmented data from different sources to a central server can result in significant communication overhead and latency, failing to meet the demands of embodied intelligence applications and posing potential privacy risks.
 
 %因此，如图1所示，在pretrained的通用视觉大模型的基础上，不同于核心节点汇聚所有数据而后训练垂域模型的集中式微调，通过联邦微调技术，驱使大量机器人节点利用私有数据和算力计算微调梯度而后聚合，能够在不交互原始数据的前提下，充分利用整个IORT网络中各个节点的知识和算力资源，成为了一种非常具有前景的解决方案。
-As illustrated in Fig.
-1, a promising solution is to employ federated fine-tuning (FFT) technology rather than adopting a centralized fine-tuning approach where core nodes aggregate all data before training domain-specific models.
+As illustrated in Figure \ref{fig1:scene}, a promising solution is to employ federated fine-tuning (FFT) technology rather than adopting a centralized fine-tuning approach where core nodes aggregate all data before training domain-specific models.
 This approach drives numerous robotic nodes to compute fine-tuning gradients using private data and computational resources and then aggregate these gradients, effectively leveraging the knowledge and computational resources of each node in the IoRT network without exchanging raw data.
 
+%不幸的是，FFT的分布式特性为多种后门攻击提供了存续的空间。尽管多种防御手段相继提出，但是尽我们所知，目前尚未有针对LVM的FFT过程进行污染防治的后门对抗技术提出。现有技术大多是针对普通联邦学习场景或集中式的VLM训练进行设计，这暴露出两大核心问题：（1）高隐蔽的攻击行为感知困难：攻击者在设计攻击行为时，(2)复杂攻击策略的检测困难：
+
+% 因此，在本文中，我们提出了一种
+% 主要包括以下几方面贡献：
+% 我们首先提出了针对进行防御
+% 针对意图
+% 防御策略
+
+The remainder of this paper is organized as follows: Section \uppercase\expandafter{\romannumeral2} reviews the related works.
+Section \uppercase\expandafter{\romannumeral3} and \uppercase\expandafter{\romannumeral4} present the system and threat models, respectively.
+Section \uppercase\expandafter{\romannumeral6} elaborates on the design philosophy of the proposed SecFFT solution, providing comprehensive details on the availability, security, and integrity of FFT in IoRT networks.
+Section \uppercase\expandafter{\romannumeral7} presents the experimental results.
+Finally, Section \uppercase\expandafter{\romannumeral8} concludes this paper and briefly explores future directions.
+
 %攻击识别
-Alongside the conti
-Spectral Distribution
-Consistency Verification
-Poisoning with 
-Detection
-
-As a preeminent collaborative artificial intelligence paradigm, Federated Learning (FL) has garnered substantial research focus \cite{ETT2}. 
-By effectively mobilizing a substantial number of participants with a discrete distribution, FL can concurrently enhance learning performance, resource utilization, and data security. 
-Besides, as intelligent applications proliferate, concerns regarding fairness-aware federated learning (FFL) have also captured significant attention \cite{zhou2021towards-KDDtutorial-FFL}.
-Due to the agnostic of multiple data sources, models trained through FL may exhibit discriminatory tendencies toward specific features or demographic groups, such as gender, race, and occupation (e.g., COMPAS recidivism algorithm \cite{angwin2022machine} and facial recognition system \cite{raji2019actionable}).
-In response to this inherent deficiency, various FFL algorithms, such as FairFed \cite{ezzeldin2023fairfed}, Ditto \cite{li2021ditto}, and FairFL \cite{zhang2020fairfl}, have been proposed.
-
-%安全问题很重要
-\subsection{Mutual reliability problem of FFL}
-Meanwhile, along with the continual emergence of novel attack techniques, such as gradient leakage and model poisoning \cite{fang2020local}, the \textit{``trust crisis''} \cite{zhou2022multi} has become a critical bottleneck in determining FFL deployment capabilities \cite{rodriguez2023survey}.
-Establishing a robust \textit{mutual reliability} relationship between the FL aggregator (parameter server) and local participants has proven challenging \cite{zhou2022multi}.
-To be specific, on the one hand, concerns about data sharing leading to privacy breaches (\textit{aggregator's reliability}) \cite{wang2021variational} raise apprehensions among owners of data and computational resources, significantly diminishing enthusiasm for collaborative learning participation and giving rise to the phenomena of ``isolated data islands''.
-On the other hand, PSs are troubled by the difficulty of promptly and accurately thwarting stealthy attackers hidden among a vast client base.
-This concern  (\textit{client nodes' reliability}) raises the specter of manipulation or even invalidation of the entire model, resulting in severe economic and intellectual property losses.
-
-%列举几个特点，导致现有安全技术不能适用
-%尽管多种最新的安全增强技术能够取得显著的防御效果，但攻击者并不能
-\subsection{Characteristics and motivation of mutual reliable FFL in heterogeneous UAV networks}
-With the advancement of integrated sensing, computation and communication (ISCC) \cite{he2023integrated}, and the space-air-ground integrated network (SAGIN) \cite{shen2023survey}, unmanned aerial vehicle (UAV) networks have played a crucial role in various domains such as post-disaster reconstruction, emergency temporary communication, and medical monitoring \cite{lu2023uav}.
-FLs based on UAV networks have also found widespread applications \cite{ETT1, ETT3, pandya2023federated}.
-However, despite the proposal of various secure FL technologies, the inherent characteristics of UAV networks continue to pose significant challenges in establishing mutual reliability for FFL in UAV environments.
-Specifically, these challenges encompass the following aspects:
-
-%异构：大范围异构，小范围相似.因此
-\textbf{1) Heterogeneity among UAV nodes:} As illustrated in Figure \ref{fig1:UAV-Network}, constrained by the mobility and patrol paths of UAVs, individual nodes are often limited to conducting data collection within a specific regional scope.
-Hence, even when employing identical equipment, the data distributions among UAV nodes across the entire network exhibit significant heterogeneity, while UAVs within the same area are similar.
-Therefore, various existing reliable FL technologies lacking adaptive considerations (such as Krum \cite{blanchard2017machine-krum}, Baffle \cite{andreina2021baffle}, and AGRamplifier \cite{gong2023agramplifier}) can lead to substantial accuracy losses.
-
-%资源受限：因此高消耗的安全策略并不能适用  高计算消耗和带宽占用的安全技术（例如，加密）
-\textbf{2) Resource limitation of UAV devices:} As UAV nodes function as mobile devices and bear substantial flight-related loads, their communication and energy resources are relatively constrained.
-The efficiency of FFL training is equally important.
-Consequently, solutions integrating cryptography, auxiliary training, multi-round detection, or other security mechanisms with high computational costs and bandwidth utilization (e.g., ShieldFL \cite{ma2022shieldfl}, AFA \cite{munoz2019byzantine-AFA}, and FLdetector \cite{zhang2022fldetector}) are not applicable for real-world deployment.
+% Alongside the conti
+% Spectral Distribution
+% Consistency Verification
+% Poisoning with 
+% Detection
 
@@
     \centering
-\includegraphics[width=\linewidth]{figures/fig1.PNG}
-\caption{FFL Illustration in Heterogeneous UAV Networks: Taking target recognition as an example, UAV node group patrolling in urban areas may collect a higher proportion of ``automobile'' samples (e.g., UN1 and UN2), while UAV groups patrolling in port areas will acquire more ``ship'' samples (e.g., UN6 and UN7).
-Consequently, the dataset distributions across the entire network often exhibit significant imbalance, while simultaneously displaying a certain degree of similarity within localized regions.
-}
-\label{fig1:UAV-Network}
+    \includegraphics[width=\linewidth]{figures/SecFFT-scenario.pdf}
+    \caption{FFT process for large vision language models in IoRT network}
+    \label{fig1:scene}
 \end{figure}
 
-%我们的目标是实现（1）异构容忍的FFL框架（2）强隐私保护的个性化训练交互（3）抗污染的可信评估
-The aforementioned characteristics distinguish the reliable FFL in heterogeneous UAV networks from existing secure FFL technologies, thereby motivating the establishment of the following new criteria for its enhancement:
-
-\textbf{1) Heterogeneity-tolerant FFL framework:} Suitable nodes from the highly heterogeneous UAV networks can be organized promptly to efficiently fulfill arbitrary fairness-aware FL tasks, which also mitigates redundant computational energy consumption and accuracy loss induced by heterogeneity.
-
-\textbf{2) Privacy-preserving personalized training:} Throughout the iteration training and interaction process, sample-level privacy protection must be implemented to prevent the leakage of sensitive information.
-Additionally, considering the resource constraints of UAV nodes, computational and bandwidth demands should be limited.
-
-\textbf{3) Poisoning-resilient credit evaluation:} In addition to robust defense capabilities against various poisoning attacks, compatibility with heterogeneity and privacy requisites is also essential.
-In other words, without compromising the effectiveness of privacy guarantee, heterogeneous benign UAV nodes should be treated equally during the whole FFL workflow.%Achieving fairness among heterogeneous benign users without compromising the effectiveness of privacy protection is a crucial aspect.
-
-\subsection{Our solution and contributions}
-%解决方案
-% Hence, in this paper, we propose mutually reliable FFL (MR-FFL), a stratified community-based framework to facilitate privacy protection (FFL aggregator's reliability) and poisoning elimination (client nodes' reliability) jointly for FFL in heterogeneous UAV networks.
-% We first divide UAV nodes into both peer communities and colleague communities according to cross-participant similarity and task-oriented fitness, respectively. 
-% Thus, the arbitrarily settled learning tasks following fair principles can be efficiently completed by fine-tuned colleague communities, even in the presence of a large degree of heterogeneity among peer communities.
-Therefore, this paper proposes mutual reliable FFL (MR-FFL), a stratified community-based framework that collectively promotes privacy protection during data sharing (reliability of FFL aggregators) and poisoning elimination during model aggregation (reliability of client nodes) in heterogeneous UAV networks.
-The contributions of the proposed MR-FFL are three-fold:
-
-%贡献
-
-\begin{itemize}
-    %\item In light of shuffling-based MTD \cite{zhou2022multi} strategies, we propose a credit to identify the malicious attackers without compromising of privacy guarantees, which is also one of the design inspirations of our framework.
-    \item Initially, UAV nodes are partitioned into peer communities and colleague communities based on cross-participant similarity and task-oriented adaptability.
-Thus, adhering to fairness principles, any arbitrarily determined learning task can be effectively accomplished through carefully selected colleague communities, even in the presence of significant heterogeneity among UAV nodes, while peer communities provide an amplified privacy guarantee.
-    %随后，我们提出了PSDP的隐私模糊化方式进行自适应训练，通过参数动态约束差分隐私敏感度，从而在同等隐私保护水平下大幅降低异构环境下的噪声损失。
-    \item Subsequently, inspired by cross-silo privacy protection, we introduce the new privacy perturbation notion of peer community-specific differential privacy (PSDP) with changeable privacy budget.
-Through dynamically constraining the DP sensitivity within each peer community, PSDP significantly reduces noise loss in heterogeneous environments under equivalent privacy protection levels.
-    %此外，我们提出了基于三值主观逻辑模型的信用评估，分别抽离投毒攻击的“操纵”（相似度）和“破坏”（准确度）行为进行群体参与的综合长效评价，从而有效抵御多种隐蔽的投毒攻击范式。
-    \item Furthermore, we propose a new credit evaluation based on the ternary subjective logic model.
-This evaluation effectively integrates comprehensive and long-term assessments with the collective participation of heterogeneous UAV nodes, specifically extracting the ``manipulation'' (similarity) and ``disruption'' (accuracy) behaviors of poisoning attacks.
-This approach proves effective in defending against various covert poisoning attack paradigms.
-    %\item Then, we integrate community-specific differential privacy into the MR-FFL process, to achieve privacy amplification as well as efficient and personal collaborative training at the same time.
-    %\item More importantly, we proposed a community-based credit evaluation to resist poisoning attacks in heterogeneous environments.
-
-\end{itemize}
-
-%本文组织结构
-The remainder of this paper is organized as follows: The related works are reviewed in Section \uppercase\expandafter{\romannumeral2}.
-The system model is presented in Section \uppercase\expandafter{\romannumeral3}.
-Then, stratified community construction, adaptive training, and credit evaluation modules are expounded upon in Section \uppercase\expandafter{\romannumeral4} to \uppercase\expandafter{\romannumeral6}, respectively, providing a detailed account of availability, privacy, and integrity for FFL in heterogeneous UAV networks.
-Section \uppercase\expandafter{\romannumeral7} presents experimental results.
-Finally, Section \uppercase\expandafter{\romannumeral8} concludes this paper.
-%and briefly explores future directions.
-
-\section{Related work}
-
-% \begin{tabular}{|p{0.4\textwidth}|p{0.5\textwidth}|}
-% \hline
-% \textbf{论文的期刊名、年份、引用} & \textbf{简介} \\
-% \hline
-% 期刊名1, 2024, 引用1 & 这篇论文讨论了...... \\
-% \hline
-% 期刊名2, 2023, 引用2 & 本研究着重于...... \\
-% \hline
-% 期刊名3, 2022, 引用3 & 本文提出了...... \\
-% \hline
-% \end{tabular}
-
-\section{Related work}
-
-According to the three basic tenets of information security \cite{zhou2021augmented-globecom}, in this section, we systematically review the most crucial hindrances of existing FFL solutions in UAV networks: \textit{availability}, \textit{confidentiality}, and \textit{in tegrity} problems, which we settled in following sections, respectively.
-\subsection{FFL in heterogeneous environments (availability)}
-To accomplish learning tasks and ensure the availability of FFL in heterogeneous environments, existing solutions can adopt debiasing on the client or server side.
-\subsubsection{Server-side debiasing} %全局化
-As the name indicated, server-side debiasing methods usually monitor the composition of training data and design new loss functions like Ratio loss \cite{wang2021addressing} to mitigate the impact of heterogeneity.
-Besides, FairFed \cite{ezzeldin2023fairfed} adjusts the aggregation weights of heterogeneous participants based on equal opportunity difference (EOD).
-Hence, clients can conduct different debiasing processes.
-Likewise, FedProto \cite{tan2022fedproto} regularizes the training of local models with the aid of abstract class prototypes from the server. 
-To handle the performance degradation caused by heterogeneous and long-tailed data, CReFF\cite{shang2022federated} re-trains the biased classifier with federated features in a privacy-preserving manner.
-Different from the above methods, several clustered FLs provide separate models for heterogeneous clients \cite{sattler2020clustered-CFL}, which can incur exponentially growing computation costs.
-\subsubsection{Client-side debiasing} %个性化
-Diverging from server-side debiasing, client-side debiasing methods primarily enhance accuracy by altering the local model \cite{tan2022towards}. 
-For example, while retaining the standard FL mechanism as the inner optimizer, FairBatch \cite{roh2020fairbatch} further adds an outer optimizer to select minibatch sizes and improve model fairness adaptively.
-Similarly, Ditto \cite{li2021ditto} develops a regular term to optimize the local models without changing global aggregation rules.
-The robustness and fairness are jointly improved.
-Moreover, Mohri \textit{et al.} \cite{mohri2019agnostic} propose agnostic federated learning (AFL) and prove its fairness using data-dependent Rademacher complexity guarantees.
-
-%总结：现有FFL有两大问题，首先是效率不佳，往往需要多轮训练，不适合于能量受限的UAV network。其次是缺乏考虑对联邦学习可信技术的兼容。
-To summarize, existing FFLs encounter two drawbacks.
-Firstly, they exhibit unsatisfactory efficiency, often necessitating multiple training rounds, rendering them unsuitable for energy-constrained UAV networks.
-Secondly, the consideration for compatibility with reliable technologies is insufficient.
-\subsection{Reliability of information sharing (confidentiality)}%隐私安全
-\subsubsection{Cryptography solutions} 
-Homomorphic encryption (HE) and other cryptographic methods naturally serve as suitable privacy protection measures.
-For instance, ShieldFL \cite{ma2022shieldfl} employs secure cosine similarity to measure the distance between two encrypted gradients, utilizing dual-gate HE to resist model poisoning.
-BatchCrypt \cite{zhang2020batchcrypt} further enhances HE efficiency by incorporating batch gradient encoding and holistic encryption, effectively reducing training time and communication overhead.
-Additionally, FairFL \cite{zhang2020fairfl} adopts the principled deep multi-agent reinforcement learning framework and secure information aggregation protocol to simultaneously optimize the accuracy and the fairness of FFL while respecting the strict privacy constraints of the clients.
-Besides, Lyu \textit{et al.} \cite{lyu2020towards} develop a local credibility mutual evaluation mechanism to guarantee fairness, and a three-layer onion-style encryption scheme to guarantee both accuracy and privacy.
-\subsubsection{Obfuscation solutions}
-
-In comparison to encryption, obfuscation approaches such as differential privacy (DP) do not introduce excessive overhead or extensive mechanism modifications, thus garnering significant attention \cite{padala2021federated}.
-For instance, Wei \textit{et al.} \cite{wei2021low} consider both general training performance and individual client privacy requirements to mitigate latency on wireless channels, addressing challenges posed by channel fading and interference in unknown network environments.
-Furthermore, considering potential model distortion from obfuscation techniques, privacy amplification as Shuffle \cite{girgis2021shuffled} can enhance the deployment capabilities of privacy protection.
-NbAFL \cite{wei2020federated-NbAFL} further diminishes the accuracy loss associated with DP by injecting secondary noise into the uplink and downlink channels.
-
-%总结：密码学方法通信量和计算量过大，而DP方法缺乏对异构考量
-Upon analysis, privacy-preserving information-sharing methods based on cryptography often incur excessive communication and computational overhead.
-On the other hand, methods relying on obfuscation like differential privacy lack adaptability to heterogeneous network environments, usually resulting in significant accuracy losses.
-\subsection{Reliability of model aggregation (integrity)}%model安全
-To resist the stealthy yet destructive poisoning attacks \cite{lyu2023poisoning}, multiple defense methods are proposed, which can be divided into the following types based on the realization concepts:
-\subsubsection{Mitigation-oriented technologies} 
-To ensure the integrity of the aggregated model, various robust FL methods, such as Byzantine-robustness, have been proposed.
-For instance, Krum \cite{blanchard2017machine-krum} selects partial neighboring nodes as references, enabling the algorithm to choose updates with the highest consensus for the next iteration.
-Diverging from Krum's approach of selecting only one update, FABA \cite{xia2019faba} employs gradient outlier computation to discard few gradients while retaining the majority of clients' training results, significantly enhancing learning speed.
-Building upon these methods, Gong \textit{et al.} devise AGRamplifier \cite{gong2023agramplifier}, which enhances the "morality" of local updates by identifying the most suppressive features in each gradient update.
-This augmentation further elevates model robustness, fidelity, and efficiency.
-
-\subsubsection{Detection-oriented technologies} 
-An alternative approach to fortify against poisoning is the direct detection of the learning model using a validation dataset or predefined rules.
-For instance, Zeno \cite{xie2019zeno} evaluates the stochastic descendant score for each gradient based on a validation dataset, selectively discarding gradients with low scores for the stochastic descendant.
-In contrast to relying on an auxiliary validation set, Baffle \cite{andreina2021baffle} capitalizes on the diverse datasets accessible across various clients by integrating a feedback loop into the FL process.
-Besides, Fldetector \cite{zhang2022fldetector} anticipates a client's model update during each iteration by leveraging historical model updates and flags a client as potentially malicious if the received model update contradicts the predicted update.
-It is noteworthy that detection-centric solutions entail additional training costs and may not identify some zero-day attacks.
-
-\subsubsection{Credit-oriented technologies} 
-%鉴于联邦学习是协作式、多轮次的交互过程，通过维护信用评价机制同样可以很好地清除恶意用户。例如，Kang等人使用多权重主观逻辑模型设计基于声誉的可靠联邦学习用户选择方案，并利用区块链实现声誉管理。在不需要辅助验证数据集的情况下，Xu等人提出余弦梯度Shapley值来评估每个智能体上传的模型参数更新/梯度的期望边际贡献，以区别对待。Tan等人提出了一种基于声誉感知的随机整数规划的FL客户选择方法，可以最优地选择和补偿具有不同声誉档案的客户，从而对抗潜在的异常行为。
-Considering that FL is a collaborative and iterative process, the credit evaluation mechanism proves effective in poisoning resistance.
-For instance, Kang \textit{et al.} \cite{credit1-kang2019IOT} design a reputation-based reliable scheme utilizing a multi-weight subjective logic model, and implement reputation management through blockchain.
-Xu \textit{et al.} \cite{xu2020reputation, xu2021gradient}, without the need for auxiliary verification datasets, introduced the cosine gradient Shapley value to assess the model parameter updates/gradients uploaded by each client.
-Tan \textit{et al.} \cite{tan2022reputation} propose a reputation-aware stochastic integer programming client selection method, selecting and compensating clients with varying reputation profiles to counter potential anomalous behavior.
-
-%总结：现有方案缺乏对隐私的考量，计算量过大
-In general, existing solutions often struggle to achieve a satisfactory balance between privacy and defensive performance, while also lacking adaptability to heterogeneous and dynamically changing environments.
-Furthermore, some methods exhibit relatively large computational overhead, imposing a non-negligible burden on UAV nodes.
-
-\section{System model} %\& Preliminaries}
+\section{Related Works}
+\subsection{Covert backdoor attacks}
+%后门攻击对深度学习模型构成了严重的安全威胁，它旨在通过对模型输入添加特殊扰动来诱导目标模型产生不当行为，例如图像分类器中的错误分类等。我们将现有针对模型的后门攻击分为两种，即空间隐蔽性后门攻击和时间隐蔽性后门攻击。
+Backdoor attacks pose a significant security threat to deep learning models, aiming to induce improper behavior in the target model by adding specific perturbations to the input, such as misclassification in image classifiers.
+We classify existing backdoor attacks on models into two types: spatially covert backdoor attacks and temporally covert backdoor attacks.
+
+% 空间隐蔽性后门攻击是指攻击者通过微调模型参数、修改输入特征或操纵模型训练过程等方式，使得现有防御方法无法在特征空间中有效区分恶意攻击者与良性参与者，从而有效逃避检测。EDGE CASE\cite{EDGE_CASE}提出了一种针对联邦学习的边缘案例后门攻击方法，通过在训练和测试数据集中通常不存在但自然存在的输入数据点（即边缘样本）来注入后门。Shadowcast\cite{xu2024shadowcast}通过在特征空间中引入微小、不可察觉的扰动，操纵视觉语言模型（VLMs）在特定视觉输入下生成误导性的文本输出。Flip\cite{jha2023label}通过修改训练数据的标签，使得模型训练轨迹接近于带有后门的专家模型，从而在特征空间中达到隐蔽攻击的效果，即使在图像干净的情况下也能逃避现有检测方法。
+\textbf{Spatially Covert Backdoor Attacks} refer to attacks where adversaries fine-tune model parameters, modify input features, or manipulate the model training process in a way that existing defense cannot effectively distinguish between malicious attackers and benign participants in the feature space, thereby evading detection.
+EDGE CASE\cite{EDGE_CASE} proposes an edge-case backdoor attack method for federated learning by injecting backdoors using input data points that are naturally occurring but typically absent in both training and testing datasets (i.e., edge-case samples).
+Shadowcast \cite{xu2024shadowcast} manipulates vision-language models (VLMs) to produce misleading textual outputs for specific visual inputs by introducing subtle, imperceptible perturbations in the feature space.
+Flip \cite{jha2023label} modifies the labels of training data so that the model's training trajectory approximates that of an expert model with a backdoor, achieving covert attacks in the feature space that can evade existing detection methods even when the images are clean.
+
+% 时间隐蔽性后门攻击是指攻击者通过调整模型训练过程或优化后门植入等方式，使后门在恶意攻击者结束攻击后仍能长期存在，不被后续良性更新所覆盖，从而持续影响模型行为。 Neurotoxin\cite{zhang2022neurotoxin}提出了一种针对联邦学习的更持久的后门攻击方法，通过攻击在训练过程中变化较小的模型参数来增加后门的耐久性，避免与良性用户梯度的冲突，使其不易在后续的模型更新中被清除。ImgTrojan\cite{tao2024imgtrojan}通过在视觉语言模型的训练数据中注入少量恶意样本，使得这些后门即使在模型后续的良性训练中仍能保持有效，从而持续影响模型的行为。\cite{gu2023gradient}提出了一种新的更新控制方法，通过跨层更新幅度归一化和层内更新方向投影，解决了参数高效调优（PET）过程中后门攻击的遗忘问题，从而维持攻击的持久性和隐蔽性。A3FL\cite{zhang2024a3fl}通过对抗性适应损失函数来优化触发器的方式，使得后门能够在全局训练动态中持久存在，从而在联邦学习模型中实现高效且持久的攻击效果。
+% Chameleon \cite{dai2023chameleon} focuses on enhancing the spatial covert nature of backdoor attacks by adjusting the relationships between poisoned samples, interference samples, and promoting samples in contrastive learning.
+\textbf{Temporally Covert Backdoor Attacks} involve adjusting the model training process or optimizing backdoor implantation such that the backdoor persists even after the malicious attacker has stopped the attack, remaining undetected by subsequent benign updates, and continuing to affect the model’s behavior.
+NEUR\cite{zhang2022neurotoxin} proposes a more persistent backdoor attack method for federated learning by targeting model parameters that change less during training.
+This approach increases the durability of the backdoor, avoids conflicts with the gradients of benign users, and makes it less likely to be removed in subsequent model updates.
+ImgTrojan \cite{tao2024imgtrojan} injects a small number of malicious samples into the training data of vision-language models, ensuring that these backdoors remain effective even after subsequent benign training, thereby continuously affecting the model's behavior.
+\cite{gu2023gradient} proposes a novel update control method that normalizes cross-layer update magnitudes and projects intra-layer update directions to address the issue of backdoor forgetting during parameter-efficient tuning (PET), thus maintaining the persistence and concealment of the attack.
+A3FL \cite{zhang2024a3fl} optimizes the trigger by using an adversarial adaptation loss function, enabling the backdoor to persist throughout global training dynamics, thereby achieving efficient and persistent attack effects.
+% 总之，现有的后门攻击策略在空间隐蔽性和时间隐蔽性方面都有了显著的进展。空间隐蔽性后门攻击通过优化特征空间中的触发器或更新，使得恶意行为难以被现有的检测方法发现，从而实现了更高效、更难以检测的攻击。而时间隐蔽性后门攻击则专注于提高后门的持久性，使得即使在恶意攻击结束后，这些后门依然能够在模型中长期存在并继续影响其行为。通过这些攻击方式的结合，攻击者能够在各种应用场景中有效地躲避检测，并确保攻击效果的持续性，这对现有的防御机制提出了更高的挑战，强调了未来在开发更加鲁棒的防御方法方面的迫切需求。
+
+%总的来看，现有的后门攻击方法已展现出显著的隐蔽性和持久性，能够有效规避当前的检测机制。这些攻击不仅在特征空间中巧妙隐藏恶意意图，还能在长期训练过程中保持攻击效果，对模型行为产生持续而深远的影响，也对模型安全构成了严峻挑战。这对现有的防御机制提出了更高的挑战，强调了未来在开发更加鲁棒的防御方法方面的迫切需求。
+Overall, existing backdoor attack methods have demonstrated significant advances in both spatial and temporal concealment, effectively circumventing current detection mechanisms.
+These attacks not only cleverly hide malicious intent in the feature space but also maintain their effects throughout long-term training, posing a sustained and profound impact on model behavior, thus presenting a severe challenge to model security.
+This underscores the need for future research to focus on developing more robust defense methods.
+
+\subsection{Backdoor countermeasures}
+%在当前深度学习模型的安全性研究中，针对后门攻击的防御措施主要可以分为两大类：后门检测和后门缓解。% Backdoor Mitigation or Elimination
+In the current research on the defense technologies, defense measures against backdoor attacks can be also broadly categorized into two major types: %backdoor detection and backdoor mitigation.
+
+% 后门检测主要旨在识别模型中已存在的后门攻击。在这一类中，SEER\cite{zhu2024seer}提出了一种用于视觉-语言模型的后门检测算法，通过在图像和文本模态的特征空间中联合搜索目标文本和图像触发器，成功实现了在多种场景下的后门检测。FoolsGold\cite{foolsgold}提出了一种通过检测各客户端更新的相似性来识别攻击者方法，该方法利用攻击者的更新通常更为相似这一特征自适应调整每个客户端的学习率，从而减少攻击者对模型训练的影响，有效防御投毒攻击，即使在存在大量恶意客户端的情况下也能显著降低攻击成功率。ASSET\cite{pan2023asset}提出了一种通过主动诱导后门样本和干净样本在模型行为上的差异，从而实现跨多种深度学习范式的鲁棒后门数据检测方法，并在端到端监督学习、自监督学习和迁移学习中表现出色。DECREE\cite{feng2023detecting}提出了一种用于检测自监督学习中预训练图像编码器后门的创新方法，该方法无需依赖标签数据或下游分类器，且在多种数据集和攻击类型下表现出极高的检测准确率。
+\textbf{Backdoor Detection} primarily aims to identify existing backdoor attackers.
+In this category, FoolsGold\cite{foolsgold} proposes a method to identify attackers by detecting the similarity of updates from each client.
+This method adaptively adjusts the learning rate of each nodes based on the observation that the updates from attackers are usually more similar.
+It effectively defends against poisoning attacks and significantly lowers the attack success rate even with a large number of malicious nodes.
+ASSET \cite{pan2023asset} introduces a robust backdoor data detection method across multiple deep learning paradigms by actively inducing behavioral differences between backdoor and clean samples, demonstrating excellent performance in end-to-end supervised learning, self-supervised learning, and transfer learning.
+DECREE \cite{feng2023detecting} presents an innovative method for detecting backdoors in pre-trained image encoders used in self-supervised learning, achieving high detection accuracy across various datasets and attack types without relying on label data or downstream classifiers.
+
+% 后门缓解则侧重于通过各种技术手段来消除或减轻后门攻击的影响。FLAME\cite{FLAME}提出了一种防御联邦学习中后门攻击的方法，通过动态聚类和权重剪裁来识别并移除可能的恶意模型更新，同时注入差分隐私噪声以有效消除后门的影响，从而在保持全局模型性能的前提下，确保后门攻击的防御效果，即使面对多样的攻击者模型和数据分布也能显著降低攻击成功率。MCLDef\cite{yue2023model}提出了一种基于模型对比学习的两阶段后门防御方法，通过收缩或破坏中毒数据在特征空间中的聚类，并将中毒数据的特征拉向其干净对应物，从而有效去除深度神经网络中的后门，同时在不显著降低模型准确性的情况下提升防御效果。DPoE\cite{liu2023shortcuts}提出了一种基于端到端集成的后门防御框架，通过结合浅层模型和主模型来捕捉和抑制后门触发器，从而有效应对各种显性和隐性的后门攻击，同时减轻噪声标签对模型性能的影响。此外，PSIM\cite{zhao2024defending}提出了一种基于参数高效微调的防御模块，通过利用样本的置信度来识别被后门攻击污染的样本，显著增强了模型抵御权重中毒后门攻击的能力，并在不影响模型准确性的情况下有效过滤出被污染的样本。CleanCLIP\cite{bansal2023cleanclip}通过在视觉和文本编码器上进行无监督微调，独立调整每种模态的表示，以削弱视觉-语言对比学习模型中由后门攻击引入的错误关联，从而有效减少后门攻击的影响，同时保持模型在正常数据上的性能。
+\textbf{Backdoor Mitigation} focuses on eliminating or reducing the impact of backdoor attacks through various technical means.
+FLAME\cite{FLAME} proposes a method to defend against backdoor attacks in federated learning by dynamically clustering and pruning weights to identify and remove potential malicious model updates.
+It also injects differential privacy noise to effectively eliminate the impact of backdoors, thereby ensuring the defense against backdoor attacks while maintaining global model performance.
+This approach significantly reduces the attack success rate even when facing diverse attacker models and data distributions.
+MCLDef \cite{yue2023model} proposes a two-stage backdoor defense method based on model contrastive learning, effectively removing backdoors in deep neural networks by contracting or disrupting the clustering of poisoned data in the feature space and pulling the features of poisoned data toward their clean counterparts, while improving defense effectiveness without significantly reducing model accuracy.
+DPoE \cite{liu2023shortcuts} introduces an end-to-end integrated backdoor defense framework that captures and suppresses backdoor triggers by combining a shallow model and a main model, effectively countering various explicit and covert backdoor attacks while mitigating the impact of noisy labels on model performance.
+Additionally, PSIM \cite{zhao2024defending} proposes a defense module based on parameter-efficient fine-tuning, significantly enhancing the model's ability to resist weight poisoning backdoor attacks by identifying samples polluted by backdoor attacks using sample confidence, effectively filtering out polluted samples without affecting model accuracy.
+CleanCLIP \cite{bansal2023cleanclip} reduces the impact of backdoors in vision-language contrastive learning models by adjusting the representations of each modality through unsupervised fine-tuning of the visual and text encoders while maintaining model performance on clean data.
+
+%尽管这些方法在应对后门攻击方面展现了显著效果，但在面对更隐蔽或复杂的后门攻击时，效果依然可能不够理想。某些方法还依赖于外部知识或置信度的设定，可能导致误判或性能瓶颈。此外，这些方法在实际应用中也增加了计算开销和训练时间。因此，未来的研究仍需在提升整体性能与效率的同时，着力解决隐蔽或复杂后门攻击的防御挑战。
+Despite the effectiveness of these methods in countering explicit backdoors, their performance may still be insufficient when faced with more covert or complex backdoor attacks.
+Some methods also rely on external knowledge or confidence settings, which may lead to misjudgments or performance bottlenecks.
+Moreover, these methods increase computational overhead and training time in practical applications.
+%Therefore, future research must continue to focus on addressing the challenges posed by covert or complex backdoor attacks while enhancing overall performance and efficiency.
+
+\section{System model \& Preliminaries}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%symbols 表格
@@
 \centering
-\begin{tabular}{| c || l |}
+\begin{tabular}{| c || p{6cm}  |}
 \hline
@@
     \hline
-    $U_i,\mathcal{D}_i$ & The $i$-th UAV devices and its dataset\\
-    \hline
-    $n^{s_{m}, i},\mathcal{P}^i$ & The size and normalized distribution of $\mathcal{D}_i$\\
-    \hline
-    $\mathcal{P}^{Tar}, w$ & Target distribution and model of learning task $Job$\\
-    \hline
-    $T$ & The maximum communication rounds of $Job$\\
-    \hline
-    $C,K$ & The set and number of all peer communities\\
-    \hline
-    $S,M$ & The set and number of all colleague communities\\
-    \hline
-    %$L$ & The number of clients in each super node\\
-    %\hline
-    $c_k$ & The $k$-th peer community\\
-    \hline
-    $s_m$ & The $m$-th colleague community\\ 
-    \hline
-    $\Delta \widetilde{\omega}_{t}^{s_{m},i}$ & The weight updates from $U_i \in s_m$ in round $t$\\
-    \hline
-    $p^{s_{m}, i}$ & The aggregation coefficient for $U_i$ within $s_m$\\
-    \hline
-    $\Delta\widetilde{\omega}_{t}^{s_{m}}$ & The weight updates from $s_m$ in round $t$\\
-    \hline
-    $p^{s_{m}}$ & The aggregation coefficient for $\Delta\widetilde{\omega}_{t}^{s_{m}}$ from $s_m$\\
-    \hline
-    $E_k$ & The clipping bound of peer community $c_k$\\
-    \hline
-    $Sen_k$ & The maximum sensitivity of $c_k$\\
-    \hline
-    $\varepsilon_k,\delta_k$& The parameters of differential privacy \\
-    \hline
-    $L$& The minimum size of colleague community\\
-    \hline
-    $\alpha^{a,b}_{t}$& The cosine similarity between $a$ and $b$\\
-    \hline
-    $PI^{c_k \rightarrow i}_{t}$ & The positive interaction between $c_k$ and $U_i$\\
-    \hline
-    $NI^{c_k \rightarrow i}_{t}$& The positive interaction between $c_k$ and $U_i$\\
-    \hline
-    $\Upsilon^{c_k \rightarrow i}_{t}$& The peer reputation opinion vector of $c_k$\\
-    \hline
-    $\Phi^{c_k \rightarrow i}_{t}$& $c_k$'s credit evaluation towards $U_i$ in round $t$\\
-    \hline
-    $\Upsilon^{s_m}_{t}$ & The colleague reputation opinion vector towards $s_m$\\
-    \hline
-    $\Phi^{s_m \rightarrow i}_{t}$& The colleague credit evaluation for $\forall U_i \in s_m$\\
-    \hline
-    $\Upsilon^{i}_{t},\Phi^{i}_{t}$& The comprehensive reputation and credit of $U_i$\\
-    \hline
-    $\psi^{i}_t$& The fairness-guaranteed selection probability\\
-    \hline
+    $ N $ & Number of nodes participating in each round.\\ \hline
+    $R_i$ & The $i$-th robot node. \\ \hline
+    $D_i$ & Private local dataset of node $R_i$.\\ \hline
+    $\theta_g^t, \theta_i^t$ & Global model and local model of $R_i$ at round $t$. \\ \hline
+    $\triangledown \theta_i^t$ & Local update of $R_i$ during round $t$. \\ \hline
+    $G_i^t $ & Frequency component of $R_i$'s update at round $t$. \\ \hline
+    $m$ & Length of the low-frequency components. \\ \hline
+    $H^t$ & Matrix formed by stacking $G_i^t$, with dimensions $m \times N$ during round $t$. \\ \hline
+    $\tilde{G}_{0}^t $ & Clean ingredient extracted from $R_i$'s low-frequency components during round $t$. \\ \hline
+    $\lambda_{max}^t$ & Largest singular value of matrix $H^t$ during round $t$. \\ \hline
+    $\xi_{max}^t$ & Left singular vector corresponding to $\lambda_{max}^t$ during round $t$. \\ \hline
+    $Chi_i^t$ & Distance difference between $R_i$'s update and the clean ingredient during round $t$. \\ \hline
+    $t'$ & One of the total $T$ rounds. \\ \hline
+    $O_i^{t'}$ & Intention point of $R_i$ during round $t'$. \\ \hline
+    \( {v}_{i}^{t'} \) & Vector of the high-dimensional ball for $R_i$ during round $t'$. TODO: CHANGE THIS\\ \hline
+    $lof_i$ & The LOF score of $R_i$.\\ \hline
+    $cre_i$ & The credit of $R_i$.\\ \hline
 \end{tabular}
@@
  \end{table}
-
-\textbf{Heterogeneous UAV network scenario.} 
-%\subsection{Network scenario}
-%对于一个多无人机多任务联邦学习场景，有一个服务器与N个无人机，设无人机集合为$U=\{U_i\}$，$\vert\vert U\vert\vert=N$。所有无人机获取的数据集集合为$D=\{D_i\}$，第k个无人机的数据分布为$\mathcal{P}^k\in \mathbb{t}^F$，其中$F$为特征维度；任务场景集合为$T$，其中第k个任务场景中的数据分布为$\mathcal{P}^{tar_k}$。在同一现实场景中，无人机采集到的数据通常是类似的，即对于某个场景的分布$\phi$，所有属于该现实场景的设备集合$B'$均满足$\exists \epsilon\in \mathbb{t}^F,\forall k \in B', ||\phi-\mathcal{P}^k||_1 \leq \epsilon$。
-As shown in Figure \ref{fig1:UAV-Network}, assume a multi-UAV multi-task federated learning scenario for the classification problems.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{figure}[htbp]
+%     \centering
+%     % \includegraphics[width=0.5\textwidth]{figure}
+%     \label{fig:scenario}
+% \end{figure}
+
+%如图\ref{fig:scenario}所示，考虑在机器人物联网（IoRT）网络中对视觉大模型进行联邦微调的场景下，整个系统模型包括多个机器人节点和一个中心服务器。每轮，每个机器人节点在本地对视觉大模型进行微调并只上传微调部分的参数更新，随后中心服务器对所有更新进行聚合，然后下发聚合后的参数，开启新一轮的联邦微调。以下是系统模型的详细描述。
+As illustrated in Figure \ref{fig1:scene}, consider the federated learning scenario of fine-tuning of LVLMs in IoRT network.
+The system model consists of multiple robot nodes and a central server.
+In each round, every node calculates the fine-tuned model of LVLMs locally and uploads only the weights updates.
+The central server then aggregates all the updates and distributes the aggregated model to initiate the next round of the FFT process.
+Detailed description is provided below:
+
+%\textbf{参与者和数据集}：假设系统模型中存在 $N$ 个机器人节点，每个节点记作 $R_i$, 其中$i \in \{1, 2, \ldots, N\}$。 每个机器人节点 $R_i$ 拥有本地数据集 $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$，其中 $x_{i,j}$ 表示输入数据，$y_{i,j}$ 表示对应的标签数据，$|D_i|$ 为数据集的大小，所有节点本地数据集的并集$D = \bigcup_{i=1}^{N} D_i$构成整体数据集。
+\textbf{Participants and Datasets}:
+In the system model, there are $N$ robotic nodes, each denoted as $R_i$, where $i \in {1, 2, \ldots, N}$.
+Each robotic node $R_i$ has a local dataset $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$, where $x{i,j}$ represents the input data, $y_{i,j}$ represents the corresponding label, and $|D_i|$ is the size of the dataset.
+The union of the local datasets across all nodes, $D = \bigcup_{i=1}^{N} D_i$, forms the overall dataset.
+
+%\textbf{LoRA}： 在LoRA(Low-Rank Adaptation) \cite{lora}方法中，每个参数矩阵 $W$ 被表示为：
+\textbf{Fine-tuning}:
+Taking Low-Rank Adaptation (LoRA) \cite{lora} as an example, model parameter matrix $W$ can be expressed as:
+\begin{equation}
+    W = W_0 + \Delta W, \quad \Delta W = BA,
+\end{equation}
+    %其中，$W_0$ 为模型的原始权重矩阵，$\Delta W$ 是低秩增量矩阵，$B$ 和 $A$ 是低秩分解矩阵，$r$ 为矩阵的秩。在对视觉大模型进行联邦微调的场景中，全局模型原始参数为$\Theta_p = \sum {W_0}$，而LoRA引入的增量参数为$\theta_p = \sum {W}$，因此全局模型的整个参数集为$\Theta = \Theta_p + \theta_g$。在整个联邦微调过程中，仅对全局模型的增量参数$\theta_g$ 进行微调训练，保持原始参数$\Theta_p$不变。
+    where $W_0$ is the original weight matrix of the model, and $\Delta W$ is the low-rank update matrix, with $B$ and $A$ being low-rank decomposition matrices and $r$ being the rank of the matrix.
+In the federated fine-tuning scenario of the large-scale vision model, the global model's original parameters are $\Theta_p = \sum {W_0}$, while the incremental parameters introduced by LoRA are $\theta_p = \sum {W}$.
+Therefore, the global model's full parameter set is $\Theta = \Theta_p + \theta_g$.
+Only the incremental parameters $\theta_g$ are fine-tuned throughout the federated fine-tuning, while the original parameters $\Theta_p$ remain unchanged.
+
+%\textbf{本地模型训练}：
+\textbf{Local training}:
+    %在每轮联邦训练的开始时，中心服务器将全局模型的增量参数 $\theta_g^{t-1}$ 发送给每个机器人节点$R_i$。每个节点在获得增量参数$\theta_g^{t-1}$后，基于本地数据集 $D_i$ 进行微调训练。
+    At the beginning of each federated training round, the central server sends the global model's incremental parameters $\theta_g^{t-1}$ to each robotic node $R_i$.
+Upon receiving $\theta_g^{t-1}$, each node fine-tunes the model based on its local dataset $D_i$.
+    % 算法\ref{alg:local_update}展示了节点进行本地模型每轮训练的主要过程。
+    %假设本地训练的轮次为$E_l$，批次大小为$b$，学习率为$\eta$。对于每一轮，节点$R_i$首先从其本地数据集$D_i$中随机抽取一个批次数据$D_i^b \sim Sample(D_i, b)$，然后利用随机梯度下降等优化算法，对增量参数进行更新，
+    Assume the number of local training epochs is $E_l$, the batch size is $b$, and the learning rate is $\eta$.
+For each epoch, the node $R_i$ randomly samples a batch of data $D_i^b \sim Sample(D_i, b)$ from its local dataset and updates the incremental parameters using an optimization algorithm such as stochastic gradient descent (SGD):
+\begin{equation}
+    (\theta_i^{t})^e = (\theta_i^{t})^{e-1} - \eta \nabla f(D_i^b, (\theta_i^{t})^{e-1}),
+\end{equation}
+    %其中$(\theta_i^{t})^e$表示在第$e$轮微调后的参数，初始时$(\theta_i^{t})^0 = \theta_g^{t-1}$。
+    where $(\theta_i^{t})^e$ denotes the parameters after the $e$-th epoch, with the initial value $(\theta_i^{t})^0 = \theta_g^{t-1}$.
+
+    %本地训练的目标是最小化损失函数 $f(D_i^b, (\theta_i^{t})^e)$：
+    The local training objective to minimize the loss function $f(D_i^b, (\theta_i^{t})^e)$ is:
+\begin{equation}
+    f(D_i^b, (\theta_i^{t})^e) = \frac{1}{|D_i^b|} \sum_{j=1}^{|D_i^b|} \ell(x_{i,j}, y_{i,j}; \Theta_p + (\theta_i^{t})^e),
+\end{equation}
+    %其中$\Theta$是模型的原始参数， $\ell$表示损失函数（如交叉熵损失）。本地训练完成后，节点计算其增量参数更新 $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ 并上传至中心服务器。
+    where $\Theta_p$ represents the original parameters of the model, and $\ell$ denotes the loss function (e.g., cross-entropy loss).
+After local training is completed, the node computes the update to the incremental parameters $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ and uploads the result to the central server.
+
+    %\item \textbf{联邦聚合}：在每轮本地训练结束后，中心服务器从每个机器人节点 $R_i$ 收集本地更新$\triangledown \theta_i^t$，并利用相应的聚合算法进行聚合，以更新全局增量参数得到$\theta_g^t$，其计算公式为：
+    \textbf{Federated Aggregation}:
+    At the end of each local training round, the central server collects the local updates $\triangledown \theta_i^t$ from each robotic node $R_i$ and aggregates them using a specified aggregation algorithm to update the global incremental parameters $\theta_g^t$:
+\begin{equation}
+    \theta_g^t = \theta_g^{t-1} + Agg(\triangledown \theta_1^t, \triangledown \theta_2^t, \dots, \triangledown \theta_n^t),
+\end{equation}
+    %其中，$Agg$表示中心服务器使用到的聚合算法，例如FedAvg、FLTrust\cite{cao2020fltrust}、RoseAgg\cite{yang2024roseagg}等，$\theta_g^t$ 是第 $t$ 轮更新的全局增量参数，更新后的全局增量参数 $\theta_g^t$ 将在下一轮训练前下发给所有机器人节点，用于进一步的本地微调。
+    where $Agg$ denotes the aggregation algorithm employed by the central server, such as FedAvg, FLTrust \cite{cao2020fltrust}, or RoseAgg \cite{yang2024roseagg}.
+The global incremental parameters $\theta_g^t$, updated in round $t$, are then distributed to all robotic nodes before the next round of training to facilitate further local fine-tuning.
+
+\section{Threat Model}
+%Attacker's Goal：假设在对视觉语言模型进行联邦微调的场景中，存在一个或者多个由攻击者操纵的恶意节点。其目标是对全局模型$\Theta$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别，即$\Theta(x+\delta) = y'$，其中$x$代表正常输入，$y'$表示目标类别。同时尽可能保持对干净输入的分类准确性，即$\Theta(x) = y$，其中$y$为输出$x$的原始类别。
+\textbf{Attacker's Goal:} In the scenario of federated fine-tuning of a vision-language model, it is assumed that one or more malicious nodes controlled by attackers are present.
+The goal is to implant a backdoor into the global model $\Theta$, such that the model classifies any test input with a predefined trigger $\delta$ as the target class, i.e., $\Theta(x + \delta) = y'$, where $x$ represents a normal input and $y'$ denotes the target class.
+Simultaneously, the attacker aims to preserve the classification accuracy on clean inputs, such that $\Theta(x) = y$, where $y$ is the original class corresponding to $x$.
+
+%Attacker's Ability: 在对视觉大模型进行联邦微调的场景中，假设攻击者对恶意节点的本地训练过程具有完全的控制权。这意味着攻击者可以任意操控本地数据、触发器模式、优化策略和本地更新过程。此外，攻击者可以采用“智能”攻击策略，这种策略的特点是攻击效果不会在单轮训练中显现，而是通过多轮训练的累积效应逐步将后门植入全局模型中。这种场景在实际中是可能存在的，因为中央服务器只能接收到客户端上传的训练后模型更新，而无法知晓每个客户端的具体训练过程。然而，攻击者无法对中央服务器的操作进行干扰，例如，无法更改全局模型的聚合规则或篡改其他良性客户端的模型更新。
+\textbf{Attacker's Ability:} In the FFT processes of LVLMs, it is assumed that the attacker has complete control over the local training process of malicious nodes.
+This means the attacker can manipulate the local dataset, trigger patterns, optimization strategies, and the local update procedure at will.
+Additionally, the attacker can employ stealthy attack strategies, where the backdoor is not immediately apparent in a single training round but is gradually embedded into the global model through the cumulative effect of multiple training rounds.
+Such a scenario is feasible in practice since the central server only receives the model updates uploaded by clients after training and has no insight into the specific local training process of each client.
+However, the attacker is unable to interfere with the central server's operations, such as modifying the global model aggregation rules or tampering with the model updates from other benign clients.
+
+\section{Methodology}
+Our SecFFT method consists of two major Instantaneous Attack Behavior Perception with Frequency-domain Deep Outlier Feature Semantics
+
+\subsection{Instantaneous Attack Behavior Perception}
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig2.png}
+    \caption{SecFFT's instantaneous attack behavior perception module with frequency-domain deep outlier feature semantics extraction}
+    \label{fig2:instant}
+\end{figure}
+%^\textbf{Motivation:} 目前的防御策略主要集中于利用攻击的“浅层语义特征”来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向\cite{foolsgold}，范数\ref{sun2019can}以及几何中心\cite{pillutla2022robust}等几何或者统计特性。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。
+% Multi-metrics adaptively identifies backdoors in Federated learning
+%首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明\cite{huang2023multi}，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。但值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终在某种分布上具有偏移。
+\textbf{Motivation:} Current defense strategies primarily focus on identifying malicious nodes using “shallow semantic features” of attacks, such as geometric or statistical characteristics like the direction\cite{foolsgold}, norm\cite{sun2019can}, and geometric center\cite{pillutla2022robust} of node updates.
+However, these shallow feature-based defenses exhibit significant limitations in high-dimensional spaces.
+For instance, these methods often only work under specific assumptions and for certain types of attacks.
+For example, cosine distance can detect malicious updates with significant directional deviation, while Euclidean distance is typically employed to identify malicious updates that inflate the $L_2$ norm and influence the global model.
+Recent studies have also demonstrated \cite{huang2023multi} that traditional distance metrics like Euclidean distance are inadequate in distinguishing between malicious and benign updates in high-dimensional spaces due to the curse of dimensionality.
+Furthermore, attack strategies continue to evolve, with attackers now able to fine-tune their updates to resemble benign ones in terms of direction, norm, and other shallow features, thus effectively bypassing these shallow semantic-based defenses while still implanting backdoors into the global model.
+It is important to note, however, that the core of a backdoor attack lies in creating an association between a predefined trigger and the target.
+Regardless of how the attacker adjusts their attack methods or strategies, the uploaded updates will always exhibit a distributional shift compared to benign users.
+
+%\textbf{Overview:} 在深度神经网络模型中，每个权重代表两个神经元之间连接的强度。权重分布及其相关的能量在训练过程中会经历动态演变，以缩小模型预测结果与训练数据中的真实目标之间的差距。当后门攻击迫使神经网络模型学习一种在正常数据中不存在的关联模式时，根据后门触发器的设计和实现方式，这种模式可能是微妙的，也可能是相当明显的，但无论如何，它都代表了与模型从正常数据中学习到的模式的偏离。因此，为解决基于浅层语义特征的防御方法在高维空间中面临的局限性，我们从后门攻击的本质出发\cite{zeng2021rethinking}，提出了一种基于深层语义特征的防御策略，重点分析模型更新在频率分布上的差异。通过将本地模型更新转换到频域，我们能够更深入地捕捉恶意更新在低频成分上的异常表现，这些异常通常难以通过传统的浅层特征检测方法发现。通过对频率域上的特征进行分析，我们可以有效地区分出恶意节点与良性节点，从而增强联邦学习系统在面对复杂后门攻击时的鲁棒性和检测精度。
+\textbf{Overview:} In deep neural networks, each weight represents the strength of the connection between two neurons.
+The distribution of these weights and their corresponding energy dynamically evolve during training to minimize the gap between the model's predictions and the ground truth in the training data.
+When a backdoor attack forces the neural network to learn an association pattern that does not exist in normal data, this pattern—depending on the design and implementation of the backdoor trigger—can be subtle or quite evident.
+Nonetheless, it always represents a deviation from the patterns learned from normal data.
+To address the limitations of shallow feature-based defenses in high-dimensional spaces, we propose a defense strategy rooted in the essence of backdoor attacks\cite{zeng2021rethinking}, focusing on deeper semantic features by analyzing differences in the frequency distribution of model updates.
+By transforming local model updates into the frequency domain, we can more effectively capture the anomalous behavior of malicious updates in low-frequency components, which are typically difficult to detect using traditional shallow-feature detection methods.
+Through frequency domain feature analysis, we can effectively distinguish malicious nodes from benign ones, thereby enhancing the robustness and detection precision of federated learning systems when facing sophisticated backdoor attacks.
+
+\textbf{Frequency domain transformation:}
+%%%% 相比于目前基于浅层语义特征的防御方法，我们利用DCT进行频域转换，将模型的更新向量映射到频域空间，以探究其在频率域上的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的4-7行所示，假设每个本地模型的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，通过一维的DCT-II将其转换为对应的频率分布，并提取低频分量，得到频率向量\(G_i^t\)。这里的 $Trunc$ 操作表示仅保留前 $m$ 个低频分量，以捕捉频域中更具代表性的特征用于后续的恶意节点检测。
+%受高维空间中维度灾难的影响，传统的基于距离度量的方法已无法有效识别恶意节点。相反，将模型更新转换到频率域后，其差异将主要集中在低频成分上。因此，专注于低频成分的分析，在提升识别准确率的同时，将显著的降低计算开销。假设每个节点上传的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，对其进行归一化，然后通过一维的DCT-II\cite{ahmed1974discrete}变化将其转换为对应的频率分布，并提取$m$个低频分量，例如5000，得到低频向量\(G_i^t\)。
+Due to the curse of dimensionality in high-dimensional spaces, traditional distance-based methods are no longer effective in identifying malicious nodes.
+In contrast, by transforming model updates into the frequency domain, the discrepancies are primarily concentrated in the low-frequency components.
+Therefore, focusing on the analysis of low-frequency components not only improves identification accuracy but also significantly reduces computational overhead.
+Suppose each node uploads an update as \(\triangledown \theta_i^t \in \mathbb{R}^d\), where $i$ represents the robot node, $t$ denotes the communication round, and $d$ is the dimension of the local model update.
+For each update \(\triangledown \theta_i^t\), it is first normalized and then transformed into its corresponding frequency distribution using a one-dimensional DCT-II \cite{ahmed1974discrete}, from which $m$ low-frequency components (normally under 5000 \cite{fereidooni2023freqfed}) are extracted to form the low-frequency vector $G_i^t$.
+
+%%___________________________________________________________________________________________________________________________
+\begin{equation}
+G_i^t = Trunc(DCT(Flatten(\frac{\triangledown \theta_i^t}{{\|\triangledown \theta_i^t\|}_2})), m)
+\label{eq:DCT}
+\end{equation}
+% 频域转换的主要过程如公式\ref{eq:DCT}所示，这里的 $Trunc$ 操作表示仅保留前$m$个低频分量。
+The main process of frequency domain transformation is shown in Equation \ref{eq:DCT}, where the $Trunc$ operation indicates retaining only the first $m$ low-frequency components.
+
+\textbf{Clean ingredient extraction:}
+% 在提取到节点更新对应的低频向量\(G_i^t\)后，我们使用流行的聚类算法例如HDBSCAN\cite{mcinnes2017hdbscan}对这些更新进行聚类，得到多个簇$C_0^t, C_1^t, \ldots, C_{\kappa}^t$，其中$\kappa$表示簇的数量。在大多数联邦学习场景中，良性节点的数量通常多于恶意节点的数量，且良性节点的更新通常更接近全局模型的方向并表现出更高的聚集性。基于这一观察，我们选择节点数量最多的簇$C_{max} = \{R_{i_0}, R_{i_1}, \ldots, R_{i_n}\}$作为主要分析对象。为了进一步提取该簇的主要特征或模式，我们对其中所有节点组成的矩阵进行奇异值分解\cite{wang2023scfl}。由于，SVD分解的左奇异向量$\tilde{G}^t$对应于数据的主要方向，因此，$\tilde{G}^t$可以作为良性节点在低频域内的主要特征。
+After extracting the corresponding low-frequency vectors \(G_i^t\) from node updates, we use popular clustering algorithms such as HDBSCAN \cite{mcinnes2017hdbscan} to cluster these updates, resulting in multiple clusters \(C_0^t, C_1^t, \ldots, C_{\kappa}^t\), where \(\kappa\) denotes the number of clusters.
+In most federated learning scenarios, the number of benign nodes is generally greater than that of malicious nodes, and the updates from benign nodes are usually closer to the direction of the global model and exhibit higher cohesion.
+Based on this observation, we select the cluster with the largest number of nodes, \(C_{max} = \{R_{i_0}, R_{i_1}, \ldots, R_{i_n}\}\), as the primary subject for analysis.
+To further extract the main features or patterns of this cluster, we perform singular value decomposition (SVD)\cite{wang2023scfl} on the matrix composed of all nodes in this cluster.
+Since the left singular vectors of the SVD decomposition, \(\tilde{G}^t\), correspond to the main directions of the data, \(\tilde{G}^t\) can be regarded as the primary feature of benign nodes in the low-frequency domain.
+
+\begin{equation}
+\tilde{G}^t = \frac{H^t \xi_{\text{max}^t}}{\sqrt{\lambda_{\text{max}^t}}}
+\label{eq:singular}
+\end{equation}
+% 公式\ref{eq:singular}展示了计算左奇异向量$\tilde{G}^t$的主要过程，其中\(H^t = ({G_{i_0}^t}, {G_{i_1}^t}, \ldots, {G_{i_n}^t}) \in \mathbb{R}^{m \times n}\)为该簇节点的低频向量堆叠而成的矩阵，其中每一列代表一个节点的低频向量，$\lambda_{max}^t$与$xi_{max}^t$分别对应了矩阵$\hat{H}^t \gets (H^t)^{T} H^t$的最大特征值及其特征向量。通过这种方式，我们有效地提取了反映良性节点全局更新在频域上的主要特征，并将$\tilde{G}^t$作为“干净成分”，为后续恶意节点检测提供基准依据。
+Equation \ref{eq:singular} illustrates the main process of computing the left singular vector $\tilde{G}^t$, where \(H^t = ({G_{i_0}^t}, {G_{i_1}^t}, \ldots, {G_{i_n}^t}) \in \mathbb{R}^{m \times n}\) is a matrix formed by stacking the low-frequency vectors of nodes in the cluster, with each column representing a node's low-frequency vector.
+$\lambda_{max}^t$ and $\xi_{max}^t$ correspond to the largest eigenvalue and its eigenvector of the matrix $\hat{H}^t \gets (H^t)^{T} H^t$, respectively.
+In this way, we effectively extract the main features that reflect the global updates of benign nodes in the frequency domain, and $\tilde{G}^t$ is used as the "clean component," providing a benchmark for subsequent malicious node detection.
+
+\textbf{Chi-square distance calculation:}
+% 我们利用每个节点的低频向量与“干净成分”之间的差异度来作为衡量恶意节点和良性节点的依据。对于每个节点的低频向量 \(G_i^t\) 以及上一步中求得的“干净成分” \(\tilde{G}^t\)，通过卡方距离来计算两者之间的差异度，得到距离差异集合$S^t = Chi^t_i, Chi^t_2, \ldots, Chi^t_N$。卡方距离的计算公式为：
+We use the divergence between each node's low-frequency vector and the "clean component" as a basis for distinguishing between malicious and benign nodes.
+For each node's low-frequency vector \(G_i^t\) and the "clean component" \(\tilde{G}^t\) obtained in the previous step, we calculate their divergence using the Chi-square distance, resulting in a set of distance differences \(S^t = \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}\).
+The formula for calculating the Chi-square distance is given by:
+
+\begin{equation}
+{Chi^t_i}^2 = \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}
+\label{equation:KL}
+\end{equation}
+% 其中 \(m\) 是低频向量的维度，\(\epsilon\) 是一个小的常数，用于避免分母为零。相比于传统的欧氏距离，卡方距离根据两个向量对应分量的大小进行加权，使得特征值较大的部分对距离的影响更大，从而能够更准确地反映低频向量中重要特征之间的差异，同时忽略不重要的噪声成分。
+where \(m\) is the dimension of the low-frequency vector, and \(\epsilon\) is a small constant to avoid division by zero.
+Compared to the traditional Euclidean distance, the Chi-square distance weights according to the magnitude of the corresponding components of the two vectors, making the influence of components with larger feature values more significant on the distance.
+This allows for a more accurate reflection of the differences between important features in the low-frequency vectors, while ignoring unimportant noise components.
+
+\textbf{Single-round malicious node detection:}
+% 为了准确地识别恶意节点，我们利用良性节点的更新与干净成分的频率分布高度相似这一特性，对距离差异集合$S^t$进一步进行聚类分析。具体而言，我们采用流行的KMeans聚类算法\cite{wan2023four}对距离差异集合$S^t$进行聚类，并将类别数设置为2，因此聚类结果为两个簇\(C'_1, C'_2\)。基于在每轮训练中良性节点的数量通常多于恶意节点，以及良性节点与干净成分之间的距离差异通常更小，我们将 \(C'_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)。对于另一簇\(C'_k\)（\(k \neq {max}\)），则将其中所有节点标记为恶意节点，记作\(U_{mal}\)。
+To accurately identify malicious nodes, we leverage the characteristic that the updates of benign nodes exhibit a high degree of similarity in frequency distribution with the clean component.
+We perform a further clustering analysis on the set of distance differences \(S^t\).
+Specifically, we use the popular KMeans\cite{wan2023four} clustering algorithm to cluster the set \(S^t\), setting the number of clusters to 2.
+Consequently, the clustering results yield two clusters, \(C'_1, C'_2\).
+Based on the observation that in each round of training, the number of benign nodes is typically greater than that of malicious nodes, and the distance differences between benign nodes and the clean component are usually smaller, we label all nodes in \(C'_{max}\) as benign nodes, denoted as \(U_{nor}\).
+For the other cluster \(C'_k\) (\(k \neq {max}\)), all nodes within it are labeled as malicious nodes, denoted as \(U_{mal}\).
+
+% 算法\ref{alg:malicious-node-detection}展示了单轮恶意用户识别的整体过程，其中3-6行代表了频率转换的计算过程，7-12行代表了“干净分量”$\tilde G^t$的计算过程，13-16行代表了每个用户与“干净分量”间的卡方差异度的计算过程，最后17-18行代表了通过KMeans聚类算法进行恶意用户检测的计算过程。
+Algorithm \ref{alg:malicious-node-detection} presents the overall process of Instantaneous Attack Behavior Perception.
+Lines 3-6 represent the computation process of frequency transformation, lines 7-12 represent the computation process of the clean component $\tilde{G}^t$, lines 13-16 represent the calculation of the Chi-square divergence between each user and the clean component, and finally, lines 17-18 represent the computation process of malicious user detection using the KMeans clustering algorithm.
+
+\begin{algorithm}
+\caption{Instantaneous Attack Behavior Perception}
+\label{alg:malicious-node-detection}
+\begin{algorithmic}[1]
+\State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each node update; $N$ is the number of the nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from nodes during the $t$-th round; $m$ is the length of low-frequency components}
+\State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
+
+% \State Step 1: Frequency Domain Transformation
+\For {$R_i \in (R_1, \ldots, R_N)$}
+    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
+    \State $G_i^t \gets Trunc(DCT(\frac{\triangledown \theta_i^t}{{\|\triangledown \theta_i^t\|}_2})), m)$ \Comment{Compute DCT and retain only the top $m$ low-frequency components}
+\EndFor
+
+% \State
+
+% \State Step 2: Clean Ingredient Extraction
+\State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering (\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t)$ \Comment{$\kappa$ denotes the number of clusters}
+\State $ C_{max} \gets \underset{C_i}{\arg\max} \, |C_i|, \quad i = 1, 2, \ldots, \kappa $ \Comment{$|C_i|$ denotes the number of nodes in cluster $C_i$}
+\State $H^t \gets (G_0^t, G_1^t, \ldots, G_{n}^t) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $\quad R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C_{max}$.}
+
+\State $\hat{H}^t \gets (H^t)^{T} H^t$
+\State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
+\State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
+
+% \State
+
+% \State Step 3: Chi-square distance calculation
+% \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
+\For {$R_i \in (R_1, \ldots, R_N)$}
+    \State ${Chi}_i^2 \gets \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}$
+\EndFor
+\State $S \gets \{Chi_1, Chi_2, \ldots, Chi_n\}$ \Comment{The Distance differences calculated by Chi-square distance.}
+
+% \State
+
+% \State Step 4: Malicious Node Detection
+\State $\{C_1, C_2\} \gets KMeans(S, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
+\State $U_{nor} \gets C_{\text{max}}$, $U_{mal} \gets \{C_i \, | \, i \neq \text{max}\}$
+
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{Long-term Attack Intention Detection}
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig3.png}
+    \caption{SecFFT's long-term attack intention detection module and secure aggregation}
+    \label{fig2:instant}
+\end{figure}
+% \textbf{Motivation}: 为了规避异常检测，有很多通过多轮次的组合攻击来植入后门的攻击。这些攻击很难在单轮次中检测出来，大致分为三类：1)限制大小的攻击，如\cite{geisler2024attacking, chen2024optimal}，这些攻击方法会限制单次攻击的大小，使得攻击并不是很明显，从而变得难以检测；2)限制角度的攻击，如\cite{you2023three, sagliano2024powered, dong2023adaptive}，这些攻击会限制每次攻击的角度，使其与正常的攻击类似从而变得难以识别；3)限制符号的攻击，如\cite{wan2023average, zhu2023boosting}，这些攻击通过梯度缩放或者梯度合成，控制恶意攻击的梯度与正常客户端梯度的正负维持一致，从而增加识别难度。本部分结合每个客户端的历史记录，通过识别攻击者最终的模型引导意图点来识别恶意节点。
+\textbf{Motivation}: To evade anomaly detection systems, many backdoor attacks employ multi-round composite strategies that are difficult to detect in a single round.
+These attacks can be broadly classified into three types: (1) \textbf{Size-Limited Attacks} (e.g., \cite{geisler2024attacking, chen2024optimal}), which constrain the magnitude of each attack to make it subtle and less conspicuous, thereby reducing its detectability; (2) \textbf{Angle-Limited Attacks} (e.g., \cite{you2023three, sagliano2024powered, dong2023adaptive}), which restrict the direction of each attack so that it appears similar to legitimate updates, making them harder to recognize; and (3) \textbf{Sign-Limited Attacks} (e.g., \cite{wan2023average, zhu2023boosting}), which use techniques such as gradient scaling or gradient composition to ensure that the signs of the malicious gradients align with those of legitimate clients, thereby increasing the difficulty of detection.
+This section presents an approach that leverages each client's historical records to identify malicious nodes by analyzing their ultimate intent to manipulate the global model.
+
+% 前面的防御已经可以有效地针对单轮次攻击进行识别，本部分主要结合客户端的历史记录对客户端进行有效的识别。本部分将保留历史$T$轮次的全局模型$\theta_g^{t'}$，其中$\max\{t-T+1, 1\}\leq  t'\leq t$，并将其Flatten后视为高维空间中的一个点；同时保留每个客户端的历史更新变化，将其视为高维空间中的一个向量，将其延伸后视为一个射线。对于每个客户端，使用最小覆盖球算法计算得到一个最小的超球，覆盖$\zeta$比例的射线。最终球心的位置可以被视为对应客户端对全局模型的意图引导点，球心的半径可以视为对应客户端的置信度。
+
+\textbf{Overview}: The previous defense mechanisms have effectively identified single-round attacks; this section focuses on leveraging clients' historical records for effective identification.
+We maintain the global models $\theta_g^{t'}$ from the past $T$ rounds, where $\max\{t-T+1, 1\}\leq t'\leq t$, and consider their flattened versions as points in a high-dimensional space.
+Simultaneously, we keep track of each client's historical updates, viewing them as vectors in the high-dimensional space and extending them as rays.
+For each client, we use the Minimum Enclosing Ball algorithm to compute a minimal hypersphere that covers a $\zeta$ proportion of the ray.
+The final position of the hypersphere's center can be regarded as the intended steering point of the global model for the corresponding client, and the radius of the hypersphere can be considered the confidence level of that client.
+
+This section mainly consists of four steps:
+
+\subsubsection{Construction of Weights updates and model databases }
+
+% 像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$\theta_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_i$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$\theta^t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-\theta^t$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上轮次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。
+As in a typical federated learning process, the central server distributes a global model in each round.
+Upon receiving the global model, each client trains on its local data and uploads the updates to the central server.
+Let the global model in the $t$-th round be denoted as $\theta_t$, and the model of client $i$ after training in the $t$-th round be denoted as $\theta^t_i$.
+Client $i$ computes its update in the $t$-th round as the difference between the trained model $\theta^t_{i}$ and the global model received before training $\theta^t$, i.e., $\triangledown \theta^t_{i} = \theta^t_{i} - \theta^t$.
+The client uploads the update $\triangledown \theta^t_{i}$ to the central server.
+While aggregating, the central server records the flattened result of each client's update in the current round, $\bar{\theta_i^t}$, as well as the global model $\theta^{t-1}$ distributed by the central server in the previous round.
+The central server retains the models and update histories for up to $T$ rounds.% The main algorithm process for "Keep T-rounds History" is shown in lines 3-13 of Algorithm \ref{alg:malicious-node-detection-history}.
+
+\subsubsection{Construction of attack intention}
+% 这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。
+This problem can be abstracted as rays in a high-dimensional space with specific starting points.
+The starting point of a ray represents the global model from the previous round, and the direction of the ray represents the flattened update in the current round.
+The optimization goal of the problem is to find a minimum hypersphere that covers at least a $\zeta$ proportion of the rays.
+% 我们使用符号$O_i$代表客户端$i$在高维空间中超球的球心，使用符号$r_i$代表这个超球的半径。假设当前轮次为$t$，$t'$是最近$T$轮次中的其中一轮，使用符号$\tilde O_i^{t'}$代表球心到第$t'$对应射线的最近点。则可以定义优化问题：
+We use the symbol $O_i$ to represent the center of the hypersphere for client $i$ in the high-dimensional space and $r_i$ to represent the radius of this hypersphere.
+Suppose the current round is $t$, and $t'$ is one of the recent $T$ rounds.
+Let $\tilde O_i^{t'}$ denote the closest point from the hypersphere center to the ray corresponding to round $t'$.
+Then, the optimization problem can be defined as:
+
+\begin{equation}
+    \min_{O_i, r_i} \quad r_i
+\end{equation}
+
+\begin{equation} 
+\text{s.t.} \quad \left| \left\{ t' \mid \| O_i - \tilde{O}_{i}^{t'} \| \leq r_i \right\} \right| \geq \zeta T,
+\end{equation}
+\begin{equation} 
+    \quad\quad\max\{t-T+1, 1\}\leq  t'\leq t.
+\end{equation}
+% “Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
+The main algorithm process for "Obtain the Purpose Intention" is shown in lines 14-18 of Algorithm \ref{alg:malicious-node-detection-history}.
+This section can be further divided into two parts: "Construct Ray Model" and "Minimum Enclosing Hypersphere Calculation."
+% “Construct Ray Model”的主要过程如下。对于每个客户端 \(R_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的更新变化历史。设 \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(i\) 上传的展平后的梯度变化向量。
+The main process of "Construct Ray Model" is as follows.
+For each client \(R_i\), the central server retains the global model history and the update history for the most recent \(T\) rounds.
+Let \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) represent the global models of the most recent \(T\) rounds, which have been "flattened" to a point in a high-dimensional space.
+Similarly, let \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) represent the flattened gradient update vectors uploaded by client \(i\) in the most recent \(T\) rounds.
+% 对于每一轮 \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \))，我们将每个射线的起点表示为展平后的全局模型 \( \theta_g^{t'} \)，并将每个射线的方向向量表示为展平后的梯度变化 \( \overline{\triangledown\theta_{i}^{t'}} \)。因此，射线模型可以构建如下：
+For each round \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \)), the starting point of each ray is represented by the flattened global model \( \theta_g^{t'} \), and the direction vector of each ray is represented by the flattened gradient update \( \overline{\triangledown\theta_{i}^{t'}} \).
+Thus, the ray model can be constructed as follows:
+
+\begin{equation}
+    \left\{\begin{matrix}
+    \widetilde{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1})\\
+    {v}_{i}^{t'} = \overline{\triangledown\theta_{i}^{t'}}
+    \end{matrix}\right.,
+\end{equation}
+% 其中，\( \widetilde{\theta_{i}^{t'-1}} \) 是射线的起点，\( {v}_{i}^{t'} \) 是射线的方向向量。则射线方程为：
+where \( \widetilde{\theta_{i}^{t'-1}} \) is the starting point of the ray, and \( {v}_{i}^{t'} \) is the direction vector of the ray. The ray equation is then given by:
+
+\begin{equation}
+l_i^{t'}=\widetilde{\theta_{i}^{t'-1}}+\alpha {v}_{i}^{t'},
+\end{equation}
+% 其中，$\alpha\in [0, +\infty)$为射线的自变量参数。
+where $\alpha\in [0, +\infty)$ is the parameter of the ray.
+% “Minimum Enclosing Hypersphere Calculation”的主要过程如下。基于构建的射线模型，使用最小覆盖球算法找到一个能够覆盖至少 \( \zeta \) 比例的射线的最小超球。首先，设定初始球心 \( O_{i,0} \) 为所有射线起点的几何中心，计算公式如下：
+The main process of "Minimum Enclosing Hypersphere Calculation" is as follows.
+Based on the constructed ray model, the Minimum Enclosing Hypersphere Ball (MEHB) algorithm is used to find the smallest hypersphere that can cover at least a \( \zeta \) proportion of the rays.
+First, the initial center of the hypersphere \( O_{i,0} \) is set to the geometric center of all ray starting points, calculated as follows:
+
+\begin{equation}
+    O_{i,0} = \frac{1}{\min\{T, t\}} \sum_{t'=\max\{t-T+1, 1\}}^{t} \widetilde{\theta_g^{t'-1}}.
+\end{equation}
+
+% 初始半径 \( r_{i,0} \) 设定为从初始球心 \( O_{i,0} \) 到所有射线起点的最大距离：
+The initial radius \( r_{i,0} \) is set as the maximum distance from the initial center \( O_{i,0} \) to all ray starting points:
+
+\begin{equation}
+r_{i,0} = \max_{t'=\max\{t-T+1, 1\}}^{t}  \|O_{i,0} - \widetilde{\theta_{g}^{t'-1}}\|.
+\end{equation}
+% 接下来，采用迭代方法来更新球心和半径：
+
+% 对于每次迭代 \( k \)，计算当前球心 \( O_{i,k} \) 到所有射线的最近点 \( \tilde{O}_{i,k}^{t'} \)。对于每个节点$R_i$的第$t'(\max\{t-T+1, 1\}\leq  t'\leq t)$轮，对于射线 \( l_i^{t'} \)，找到球心 \( O_{i,k} \) 与当前射线的投影点 \( \hat O_{i,k}^{t'} \)，并计算参数 \( \alpha_k \)：
+Then, the center and radius are iteratively updated. 
+For each iteration \( k \), compute the nearest points \( \tilde{O}_{i,k}^{t'} \) from the current center \( O_{i,k} \) to all rays.
+For the $t'$-th round of each node $R_i$ (\(\max\{t-T+1, 1\}\leq  t'\leq t\)), for the ray \( l_i^{t'} \), find the projection point \( \hat O_{i,k}^{t'} \) of the center \( O_{i,k} \) onto the current ray, and compute the parameter \( \alpha_k \):
+
+\begin{equation}
+\alpha_k = \frac{(O_{i,k} - \widetilde{\theta_{i}^{t'-1}}) \cdot {v}_{i}^{t'}}{{v}_{i}^{t'}\cdot {v}_{i}^{t'}},
+\end{equation}
+% 则最近点 \( \tilde O_{i,k}^{t'} =\widetilde{\theta_{i}^{t'-1}}+\max \left\{ 0, \alpha_k\right\} {v}_{i}^{t'} \)。
+% 计算当前球心 \( O_{i,k} \) 到这些最近点 \( \tilde O_{i,k}^{t'} \) 的距离集合 \( Dis_{i,k}= \{ \| O_{i,k}-\tilde O_{i,k}^{t'} \|, \max\{t-T+1, 1\}\leq  t'\leq t\} \)，并按从小到大的顺序进行排序，然后暂时舍弃$1-\zeta$比例的射线来忽略离群点对计算过程的影响，得到集合${Dis}_{i,k}'$，保留射线对应轮次的集合记为$\tilde T$。将球心向着被保留的最近点中距离最远的点$\tilde{O}_{i,k}^{t_{max}'}$移动：
+
+Thus, the nearest point is given by \( \tilde O_{i,k}^{t'} =\widetilde{\theta_{i}^{t'-1}}+\max \left\{ 0, \alpha_k\right\} {v}_{i}^{t'} \). 
+Calculate the set of distances from the current center \( O_{i,k} \) to these nearest points \( \tilde O_{i,k}^{t'} \), denoted as \( Dis_{i,k}= \{ \| O_{i,k}-\tilde O_{i,k}^{t'} \|, \max\{t-T+1, 1\}\leq  t'\leq t\} \).
+Sort these distances in ascending order and temporarily discard a proportion of \(1-\zeta\) of the rays to ignore the impact of outliers, resulting in the set ${Dis}_{i,k}'$.
+The rounds corresponding to the retained rays are denoted as $\tilde T$.
+Move the center towards the farthest point $\tilde{O}_{i,k}^{t_{max}'}$ among the retained nearest points:
+
+\begin{equation}
+O_{i,k+1} = O_{i,k} + \eta' (\tilde{O}_{i,k}^{t_{max}'}-O_{i,k}),
+\end{equation}
+% 其中$\eta'$为学习率。移动后的球心半径为：
+where $\eta'$ is the learning rate.
+
+The radius of the moved center is:
+
+\begin{equation}
+r_{i,k+1} =  \{ \max\{\| O_{i,k+1}-\tilde O_{i,k+1}^{t'} \|\}, t'\in \tilde T\} ,
+\end{equation}
+
+% 其中$\tilde O_{i,k+1}^{t'}$为更新后的球心$O_{i,k+1}$到被保留射线的最近点。当更新后的半径 \( r_{i,k+1} \) 与上一次的半径 \( r_{i,k} \) 相差小于一个预设的阈值 \( \lambda \)，或者达到预设的最大迭代次数$k_{max}$时，停止迭代。
+where $\tilde O_{i,k+1}^{t'}$ is the nearest point from the updated center $O_{i,k+1}$ to the retained rays.
+When the difference between the updated radius \( r_{i,k+1} \) and the previous radius \( r_{i,k} \) is smaller than a predefined threshold \( \lambda \), or when the maximum number of iterations $k_{max}$ is reached, the iteration stops.
+
+\subsubsection{driven malicious intention detection}
+% “Abnormal Detection”的主要过程基于局部离群因子（Local Outlier Factor, LOF）得到异常点。LOF算法是一种基于密度的异常检测方法，算法的核心思想是通过计算一个数值$lof_i$来反应节点$i$的异常程度。$lof_i$大致意思是节点$i$目的意图点$O_i$周围意图点所处位置的平均密度比上$O_i$所在位置的密度。比值越大于$1$，则$O_i$所在位置的密度越小于周围其他意图点所在位置的密度，即$O_i$越有可能是异常点。首先定义意图点$O_i$的$q$距离$\widetilde{dis_i^q}$，假设高维空间中存在节点$j$的意图点$O_j$，则有$O_j$与$O_i$之间的距离为$\|O_i-O_j\|$，如果满足以下两个条件，我们就认为$\widetilde{dis_i^q}=\|O_i-O_j\|$：
+The main process of "Abnormal Detection" identifies outliers based on the Local Outlier Factor (LOF).
+The LOF algorithm is a density-based anomaly detection method.
+Its core idea is to calculate a value $lof_i$ to reflect the degree of abnormality of node $i$.
+The value of $lof_i$ represents the ratio of the average density of the intention points around the intention point $O_i$ to the density at the location of $O_i$.
+The greater this ratio is than $1$, the lower the density around $O_i$ compared to the surrounding intention points, indicating that $O_i$ is more likely to be an outlier.
+First, we define the $q$-distance $\widetilde{dis_i^q}$ of the intention point $O_i$.
+Assume there is an intention point $O_j$ for node $j$ in the high-dimensional space, and the distance between $O_j$ and $O_i$ is $\|O_i-O_j\|$.
+If the following two conditions are satisfied, we have $\widetilde{dis_i^q} = \|O_i-O_j\|$:
+
+% \begin{itemize}
+%     \item 在样本空间中，至少存在$q$个意图点$O_j'$，使得$\|O_i-O_j'\|\leq \|O_i-O_j\|$, 其中$j'\neq i$；
+%     \item 在样本空间中，至多存在$q-1$个意图点$O_j'$，使得$\|O_i-O_j'\|< \|O_i-O_j\|$, 其中$j'\neq i$。
+% \end{itemize}
+
+\begin{itemize}
+    \item In the sample space, there are at least $q$ intention points $O_j'$ such that $\|O_i-O_j'\| \leq \|O_i-O_j\|$, where $j' \neq i$;
+    \item There are at most $q-1$ intention points $O_j'$ such that $\|O_i-O_j'\| < \|O_i-O_j\|$, where $j' \neq i$.
+\end{itemize}
+
+% 总的来说，$O_i$的$q$距离$\widetilde{dis_i^q}$表示高维空间中距离第$q$远的点。之后定义意图点$O_i$的第$q$距离邻域$Nei_i$为到$O_i$距离不超过$\widetilde{dis_i^q}$的所有意图点的集合。由于可能同时存在多个第$q$距离的数据，所以$|Nei_i|\geq q$。可以想象，离群度越大的意图点的$q$距离往往较大，离群度越小的意图点的$q$距离往往较小。之后定义意图点$O_i$相对于意图点$O_j$的可达距离：
+In summary, the $q$-distance $\widetilde{dis_i^q}$ of $O_i$ represents the distance to the $q$-th farthest point in the high-dimensional space.
+Then, we define the $q$-distance neighborhood $Nei_i$ of the intention point $O_i$ as the set of all intention points whose distance to $O_i$ does not exceed $\widetilde{dis_i^q}$.
+Since multiple data points at the $q$-distance may exist simultaneously, $|Nei_i| \geq q$.
+It can be imagined that the $q$-distance of intention points with greater outlier degrees is often larger, while those with smaller outlier degrees tend to have smaller $q$-distances.
+Next, we define the reachable distance of intention point $O_i$ relative to point $O_j$:
+
+\begin{equation}
+rea_{i,j}=\max\{\widetilde{dis_i^q}, \|O_i-O_j\|\},
+\end{equation}
+% 也就是说，如果意图点$O_j$远离意图点$O_i$，则两者之间的可达距离就是他们之间的实际距离$\|O_i-O_j\|$；而如果二者距离足够近，则可达距离用意图点$O_i$的$q$距离$\widetilde{dis_i^q}$代替。之后定义意图点$O_i$的局部可达密度$lrd_i$为其$Nei_i$所有意图点的平均可达距离的倒数，即：
+That is, if the intention point $O_j$ is far from the intention point $O_i$, the reachable distance between them is their actual distance $\|O_i-O_j\|$; if they are close enough, the reachable distance is replaced by the $q$-distance $\widetilde{dis_i^q}$ of the intention point $O_i$.
+Next, we define the local reachable density $lrd_i$ of the intention point $O_i$ as the reciprocal of the average reachable distance of all intention points in its $Nei_i$:
+
+\begin{equation}
+lrd_i=1/(\frac{\sum_{j\in Nei_i} rea_{i,j}}{|Nei_i|})
+\end{equation}
+
+% 此时，若有重复点，则可能导致$lrd$变为无限大。$lrd_i$的可以理解为意图点$O_i$所处位置的密度，密度越高则意图点$O_i$越有可能属于同一簇，密度越低则意图点$O_i$越有可能是离群点。也就是说，如果意图点$O_i$和周围邻域点是同一簇，则可达距离可能为较小的$\widetilde{dis_i^q}$，导致可达距离之和较小，密度值较高；如果$O_i$和周围邻居意图点较远，则可达距离可能会取较大的$\|O_i-O_j\|$，导致可达距离之和较大，密度值较低，越有可能是离群点。最后，我们定义意图点$O_i$的局部离群因子$lof_i$为其$Nei_i$所有意图点的局部可达密度与其自身局部可达密度的比值的平均值，即：
+At this point, if there are duplicate points, $lrd$ may become infinite.
+$lrd_i$ can be understood as the density at the location of intention point $O_i$.
+The higher the density, the more likely intention point $O_i$ belongs to the same cluster; the lower the density, the more likely $O_i$ is an outlier.
+In other words, if intention point $O_i$ and its surrounding neighborhood points are in the same cluster, the reachable distance is likely to be the smaller $\widetilde{dis_i^q}$, resulting in a smaller sum of reachable distances and a higher density value; if $O_i$ is far from its neighboring intention points, the reachable distance is likely to take the larger $\|O_i-O_j\|$, resulting in a larger sum of reachable distances and a lower density value, making it more likely to be an outlier.
+Finally, we define the local outlier factor $lof_i$ of intention point $O_i$ as the average of the ratio of the local reachable densities of all intention points in its $Nei_i$ to its own local reachable density:
+
+\begin{equation}
+    lof_i=\frac{\sum_{j\in Nei_i}\frac{lrd_j}{lrd_i}}{|Nei_i|}=\frac{\sum_{j\in Nei_i} lrd_j}{|Nei_i|\cdot lrd_i}
+\end{equation}
+
+% 如果$lof_i$比较接近$1$，则说明意图点$O_i$与其邻域点密度差不多，$O_i$可能和邻域属于同一簇；如果$lof_i$小于$1$，则说明意图点$O_i$的密度高于其邻域点的密度，$O_i$为密集点；如果$lof_i$大于$1$，则说明意图点$O_i$的密度低于其邻域点的密度，$O_i$可能是离群点。总之，LOF算法主要通过比较每个意图点$O_i$和其邻域点的密度来判断$O_i$是否为离群点，密度越低，则越有可能是离群点。而密度主要是通过点之间的距离来计算的，点之间的距离越远密度越低，距离越近密度越高。计算每个节点$i$的局部离群因子$lof_i$，将$lof_i$大于$1$的客户端视为异常客户端，并将其梯度丢弃。
+If $lof_i$ is close to $1$, it indicates that the density of intention point $O_i$ is similar to its neighboring points, suggesting that $O_i$ and its neighborhood belong to the same cluster.
+If $lof_i$ is less than $1$, it means that the density of intention point $O_i$ is higher than its neighboring points, indicating that $O_i$ is a dense point.
+If $lof_i$ is greater than $1$, it means that the density of intention point $O_i$ is lower than its neighboring points, suggesting that $O_i$ may be an outlier.
+In conclusion, the LOF algorithm mainly determines whether $O_i$ is an outlier by comparing the density of each intention point $O_i$ with that of its neighboring points.
+The lower the density, the more likely it is an outlier.
+Density is primarily calculated based on the distance between points: the greater the distance between points, the lower the density; the closer the distance, the higher the density.
+After calculating the local outlier factor $lof_i$ for each node $i$, clients with $lof_i$ greater than $1$ are regarded as abnormal clients, and their gradients are discarded.
+% “Abnormal Detection”的主要过程如算法\ref{alg:malicious-node-detection-history}的19-30行所示。
+% The main process of "Abnormal Detection" is shown in lines 19-30 of Algorithm \ref{alg:malicious-node-detection-history}.
+
+\subsubsection{Gradients Aggregation}
+% 剔除了异常节点后，依据正常节点的置信度$cre$进行聚合。其中定义：
+After removing abnormal nodes, the aggregation is performed based on the confidence $cre$ of normal nodes. The definition is as follows:
+
+\begin{equation}
+    cre_i=\frac{1}{r_i+\rho},
+\end{equation}
+% $\rho$是一个很小的正数，以防分母为$0$。
+
+% 如图\ref{fig:before-agg}所示，使用LOF算法识别恶意客户端可以剔除潜在的恶意节点，但是在正常的节点中，同样存在一些置信度很低的节点。这些节点的最小覆盖球甚至可能和异常节点有一定交集。因此，在聚合的过程中，这些置信度较低的点所占的权重就应该越低。
+
+% 试想，假设有两个节点的最小覆盖超球的半径都很小，但是相差倍数很高，那么它们计算出来的置信度相差倍数也会很高。但其实它们的意图点都十分明确，因此权重应该都比较高且相差不应很大。所以我们可以使用激活函数Tanh来对置信度进行加权处理：
+
+where $\rho$ is a small positive number to prevent the denominator from being zero.
+
+As shown in Figure \ref{fig:before-agg}, the LOF algorithm can identify and remove potential malicious clients, but among the normal nodes, there are still some nodes with very low confidence.
+The minimum enclosing hypersphere of these nodes may even overlap with the abnormal nodes.
+Therefore, in the aggregation process, nodes with lower confidence should have lower weights.
+
+Consider the following scenario: suppose two nodes have very small minimum enclosing hypersphere radii, but their radii differ by a significant factor.
+Consequently, their computed confidences would also differ significantly.
+However, their intention points are quite clear, so their weights should both be relatively high and not differ too much.
+Therefore, we can use the Tanh activation function to adjust the confidence weights:
+
+\begin{equation}
+    cre_i'=\tanh(cre_i),
+\end{equation}
+% 激活函数Tanh在$0$到$\infty$范围内是一个上升又快到慢的单调递增函数。当$cre_i\to 0$时$cer_i'\to 0$，也就是说节点$i$的最小覆盖球半径$r_i$很大时该节点在聚合时的权重很小；当$cre_i\to \infty$时$cer_i'\to 1$，也就是说节点$i$的最小覆盖球半径$r_i$很小时该节点在聚合时的权重较大。这样，我们就可以对每个加权处理过的置信度$cer_i'$进行归一化处理，得到权重$w_i$。其中：
+The Tanh activation function is a monotonic increasing function that rises quickly at first and then slowly within the range of $0$ to $\infty$.
+When $cre_i \to 0$, $cer_i' \to 0$, which means that when the minimum enclosing hypersphere radius $r_i$ of node $i$ is large, its weight during aggregation is small.
+Conversely, when $cre_i \to \infty$, $cer_i' \to 1$, which indicates that when the radius $r_i$ is small, the weight of node $i$ in the aggregation is larger.
+This allows us to normalize each adjusted confidence $cer_i'$ to obtain the weight $w_i$.
+The formula is:
+
+\begin{equation}
+    w_i=\frac{cre_i'}{\sum_{i=1}^{N}cre_i'},
+\end{equation}
+% 因此第$t$轮模型的梯度聚合公式为：
+Thus, the gradient aggregation formula for the model in the $t$-th round is:
+
+\begin{equation}
+    \theta_g^t = \theta_g^{t-1}+\sum_{i=1}^{N}w_i\triangledown \theta_i^t,
+\end{equation}
+
+% \begin{figure}[!t]
+%     \centering
+%     \includegraphics[width=\linewidth]{results/prob-history-Visualization of Client Intentions and Anomalies.png}
+%     \centering \caption{Results obtained using simulated data}
+%     \label{fig:result-of-histry}
+% \end{figure}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig4.jpg}
+    \caption{Benign and Malicious Nodes Before Aggregation}
+    \label{fig:before-agg}
+\end{figure}
+% 如图\ref{fig:before-agg}所示展示了异常检测和梯度聚合的计算流程示意图。图中每个球都是某个节点的意图范围。蓝色的球代表良性节点，红色的球代表异常节点。在进行异常检测时我们只考虑每个节点的意图点，即图中的球心位置。在计算可达距离时，由于意图点$O_{j_1}$距离意图点$O_i$较近，故二者之间的可达距离为意图点$O_i$的$q$距离$\widetilde{dis_i^q}$；由于意图点$O_{j_2}$距离$O_i$较远，所以二者之间的可达距离为二者之间的实际距离$\|O_i-O_{j_2}\|$。意图点$O_i$的密度高于其邻域意图点的密度，$lof_i<1$；而意图点$O_{j_2}$的密度低于其邻域意图点的密度，因此$lof_{j_2} > 1$。
+As shown in Figure \ref{fig:before-agg}, the diagram illustrates the computational process of anomaly detection and gradient aggregation.
+Each sphere in the figure represents the intention range of a specific node.
+The blue spheres represent benign nodes, while the red spheres represent anomalous nodes.
+During anomaly detection, we only consider the intention point of each node, which is represented by the center of each sphere in the figure.
+When calculating the reachable distance, since intention point $O_{j_1}$ is close to intention point $O_i$, the reachable distance between them is the $q$-distance $\widetilde{dis_i^q}$ of intention point $O_i$.
+Since intention point $O_{j_2}$ is far from $O_i$, the reachable distance between them is the actual distance $\|O_i-O_{j_2}\|$ between them.
+The density of intention point $O_i$ is higher than that of its neighboring intention points, so $lof_i < 1$.
+On the other hand, the density of intention point $O_{j_2}$ is lower than that of its neighboring intention points, so $lof_{j_2} > 1$.
+
+% 将异常节点剔除，在聚合良性节点的梯度时，依据正常节点的置信度进行加权处理。图中可以看出，虽然节点$j_1$被划分为了良性节点，但其置信度非常低，其超球甚至已经与异常节点$j_2$有所重合。因此在梯度聚合的时候，其权重较小。
+After removing anomalous nodes, the gradients of benign nodes are aggregated with a weighting based on the confidence of the normal nodes.
+As shown in the figure, although node $j_1$ is classified as a benign node, its confidence is very low, and its hypersphere even overlaps with the anomalous node $j_2$.
+Therefore, its weight is small during gradient aggregation.
+
+% 我们将算法总结成了伪代码，如算法\ref{alg:malicious-node-detection-history}所示。其中第3-7行是步骤1，表示了保留T轮次历史记录的方法；第8-15行是步骤2，表示了使用最小覆盖超球算法求每个机器人节点意图点和置信度的方法；第16-27行是步骤3，表明了如何通过LOF算法求出正常节点和异常节点；第28-32行是步骤4，展示了依据每个机器人节点置信度进行加权聚合的方法。
+
+We summarize the algorithm in the form of pseudocode, as shown in Algorithm \ref{alg:malicious-node-detection-history}.
+Lines 3 to 7 correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds.
+Lines 8 to 15 correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level.
+Lines 16 to 27 correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm.
+Finally, lines 28 to 32 correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.
+
+\begin{algorithm}
+\caption{Attack intention detection and secure aggregation}
+\label{alg:malicious-node-detection-history}
+\begin{algorithmic}[1]
+\State \textbf{Input:} Global model history $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$
+\State \textbf{Output:} Sets of normal clients $U_{nor}$ and malicious clients $U_{mal}$
+
+\State \textbf{Step 1: Keep T-rounds History}
+\For {Client $i$}
+    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_{i}^t)$ \Comment{Record flattened gradients  and models $\theta_g^{t-1}$}
+    % \State $\widetilde{\theta_{i}^{t'-1}}  \gets Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'}  \gets \overline{\triangledown\theta_{i}^{t'}}$ for $t'  \gets \max\{t-T+1, 1\}, \ldots, t$ \Comment{Construct rays}
+    \State $\widetilde{\theta_{i}^{t'-1}}  \gets Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'}  \gets \overline{\triangledown\theta_{i}^{t'}}$ , $\max\{t-T+1, 1\}\leq t' \leq t$ \Comment{Construct rays}
+\EndFor
+
+\State \textbf{Step 2: Obtain the Purpose Intention}
+\For {Client $i$}
+    \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
+    \While {Not Converged}
+        \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
+    \EndWhile
+    \State  $cre_i  \gets \frac{1}{r_i + \rho}$ \Comment{Calculate confidence}
+\EndFor
+
+\State \textbf{Step 3: Abnormal Detection}
+\For {Client $i$}
+    \For {Each point $O_j \neq O_i$}
+        \State Calculate distance $\|O_i - O_j\|$
+    \EndFor
+    \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
+    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
+    \State $rea_{i,j}  \gets \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$  \Comment{Compute reachability distance}
+    \State  $lrd_i  \gets \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$ \Comment{Calculate local reachability density}
+    \State $lof_i  \gets \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
+\EndFor
+% \For {Client $i$}
+%     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
+%     \If {$lof_i > 1$}
+%         \State Mark client $i$ as malicious, add to $U_{mal}$
+%     \Else
+%         \State Mark client $i$ as normal, add to $U_{nor}$
+%     \EndIf
+% \EndFor
+% \State $U_{mal} = \{i \,|\, lof_i > 1\}$
+% \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
+\State $U_{mal}, U_{nor}  \gets \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$
+
+\State \textbf{Step 4: Gradients Aggregation}
+\For {Client $i\in U_{nor}$}
+        \State $cre_i'  \gets \tanh(cre_i)$\Comment{Compute adjusted confidence}
+        \State $w_i  \gets \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$\Comment{Normalize weights}
+\EndFor
+
+\State \textbf{Output:} $\theta_g^t \gets \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$\Comment{Aggregated global model update}
+\end{algorithmic}
+\end{algorithm}
+
+% \begin{figure}[!t]
+%     \centering
+%     % \includegraphics[width=\linewidth]{figures/fig2.pdf}
+%     \caption{Benign and Malicious Nodes Before Aggregation}
+%     \label{fig2:single}
+% \end{figure}
+
+% \subsection{Multi}
+
+% \begin{figure}[!t]
+%     \centering
+%     \includegraphics[width=\linewidth]{figures/fig3.jpg}
+%     \caption{Benign and Malicious Nodes Before Aggregation}
+%     \label{fig3:multi}
+% \end{figure}
+
+% \begin{figure}[!t]
+%     \centering
+%     \includegraphics[width=\linewidth]{figures/fig4.jpg}
+%     \caption{Benign and Malicious Nodes Before Aggregation}
+%     \label{fig4:before-agg}
+% \end{figure}
+
+\section{Experimental evaluation}
+% This section presents a thorough evaluation of SecFFT on two benchmark datasets, aiming to illustrate its effectiveness. 本实验在一台Windows操作系统的服务器上进行，28核心128GB内存，以及2块NVIDIA GeForce RTX 3090 GPU(24G)。
+This section thoroughly evaluates SecFFT on the benchmark dataset to illustrate its effectiveness, which begins by detailing the experimental setup and environment, followed by a presentation and analysis of the experimental results.
+
+\subsection{Experimental Setup}
+% 在本实验中，我们采用了常用的联邦学习场景进行评估。具体设置如下：
+We used the widely adopted FedAvg framework for evaluation.
+The experiments were conducted on a server running the Windows operating system with 28 cores, 128GB of memory, and two NVIDIA GeForce RTX 3090 GPUs (24GB).
+The specific settings are as follows:
+
+%\textbf{数据集}：我们使用FMNIST\cite{minist}作为实验数据集。FMNIST数据集包含60,000张28x28像素的灰度时尚商品图像，共分为10个类别，其中50,000张为训练集，10,000张为测试集。
+
+\textbf{Dataset:} We used the FMNIST\cite{minist} dataset as the experimental dataset.
+The FMNIST dataset contains 60,000 grayscale images of fashion items with a resolution of 28x28 pixels, divided into 10 categories, with 50,000 images for training and 10,000 for testing.
+
+ % \textbf{微调模型}：我们采用CLIP的CLIP-ViT-B/32\cite{huggingface_clip}模型作为微调所使用的预训练模型。CLIP是一种通过对比学习在文本和图像数据上进行预训练的模型，能将自然语言和视觉信息映射到同一特征空间中。CLIP-ViT-B/32基于ViT\cite{vit}架构，包含12层Transformer编码器，隐藏层维度为768，多头注意力头数为12，使用32x32的图像块作为输入。在微调过程中，我们使用LORA\cite{lora}方案仅在Vision Encoder模块插入低秩矩阵，保持Textual Encoder模块不变。我们设定低秩矩阵的秩为16，学习率为$10^{-4}$，以在有限计算资源下高效微调模型，使其更好地适应特定任务的数据分布。
+\textbf{Fine-tuning model:} We adopted the \textbf{CLIP-ViT-B/32}\cite{huggingface_clip} model from \cite{clip} as the pre-trained model for federated fine-tuning.
+CLIP is a model pre-trained on both text and image data through contrastive learning, capable of mapping natural language and visual information into the same feature space.
+CLIP-ViT-B/32 is based on the ViT\cite{vit} architecture and contains 12 layers of Transformer encoders, with a hidden dimension of 768 and 12 attention heads, using 32x32 image patches as input.
+During fine-tuning, we used the \textbf{LORA}\cite{lora} method to insert low-rank matrices only in the Vision Encoder module, keeping the Textual Encoder module unchanged.
+We set the rank of the low-rank matrices to 16 and the learning rate to \textbf{$10^{-4}$} to efficiently fine-tune the model under limited computational resources, allowing it to better adapt to the data distribution of specific tasks.
+
+% \textbf{攻击方式}：对于单轮恶意用户检测，我们使用包括MR\cite{MR}、EDGE CASE\cite{EDGE_CASE}、以及NEUR\cite{zhang2022neurotoxin}在内的三种针对联邦学习场景的最新攻击。MR攻击通过将中毒图像与正常图像混合来创建恶意数据集，并使用投影梯度下降法进行本地训练来达到植入后门的效果；EDGE CASE攻击利用罕见的“边缘情况”样本，通过数据或模型投毒在联邦学习模型中插入后门；Neurotoxin攻击则尝试通过识别在正常节点训练中不常更新的参数，并利用这些参数插入后门，以提高后门的持久性。
+\textbf{Attack methods:} For Instantaneous Attack Behavior Perception, we used three of the latest attacks targeting federated learning scenarios, including \textbf{MR}\cite{MR}, \textbf{EDGE CASE}\cite{EDGE_CASE}, and \textbf{NEUR}\cite{zhang2022neurotoxin}.
+The MR attack creates a malicious dataset by mixing poisoned images with normal ones and uses the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack utilizes rare "edge-case" samples to insert backdoors into the federated learning model through data or model poisoning; the NEUR attack attempts to identify parameters that are rarely updated during normal node training and uses these parameters to insert backdoors, enhancing the persistence of the backdoor.
+
+% \textbf{对比算法}：对于单轮恶意用户检测算法，我们对比了三种聚合算法：FedAVG\cite{FedAVG}、FLTrust\cite{FLTrust}和Flame\cite{FLAME}。其中FedAVG根据每个节点数据集的大小对其上传的更新进行加权聚合；FLTrust利用一个干净的数据集，仅聚合那些上传更新与该干净数据集上训练所得更新余弦相似度较高的节点；而Flame则通过模型聚类和权重剪裁来估计并注入适量噪声，有效消除联邦学习中的后门攻击。
+\textbf{Baseline defense algorithms:} For Instantaneous Attack Behavior Perception, we compared four aggregation algorithms: \textbf{FedAVG}\cite{FedAVG}, \textbf{Foolsgold}\cite{foolsgold}, \textbf{FLTrust}\cite{FLTrust}, and \textbf{Flame}\cite{FLAME}.
+FedAVG performs weighted aggregation of the updates uploaded by each node based on the size of their dataset; FoolsGold distinguishes between benign and malicious clients by assessing pairwise similarity among model updates, subsequently down-weighting abnormal updates on the FL server; FLTrust uses a clean dataset and only aggregates updates from nodes whose updates have a high cosine similarity with the updates obtained from the clean dataset; Flame estimates and injects an appropriate amount of noise through model clustering and weight clipping to effectively eliminate backdoor attacks in federated learning.
+
+\textbf{Evaluation metrics:}
+% 就像其他文章中的评价指标一样，我们使用两个关键指标来评估投毒攻击与防御方法的效果，即ASR（攻击成功率）和 TSR（测试成功率）。ASR表示恶意节点成功诱导全局模型成功预测指定目标的概率。攻击者的目标是最大化ASR，而有效的防御措施则旨在防止ASR上升。TSR表示全局模型在测试集上的预测正确率。攻击者的目标是尽量维持模型的TSR不变，以避免被轻易检测到，而有效的防御措施则不应显著降低全局模型的TSR。
+Similar to evaluation metrics used in other works\cite{tang2023port, jin2024learning, rong2023special}, we use two key metrics to assess the effectiveness of poisoning attacks and defense methods: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
+ASR represents the probability that malicious nodes successfully induce the global model to predict the specified target.
+The goal of the attacker is to maximize ASR, while effective defense measures aim to prevent an increase in ASR.
+TSR represents the accuracy of the global model on the test set.
+The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
+
+\subsection{Model integrity and poisoning resistance}
+% 为了验证我们所提方法“Instantaneous Attack Behavior Perception”的有效性，我们分别在MR、EDGE CASE、NEUR三种攻击下进行实验，并与FedAVG(Baseline)、Foolsgold、FLTrust、Flame进行对比，比较不同防御算法下相应的TSR以及ASR。图\ref{fig:lab1}分别展示了攻击相应的实验结果。
+To validate the effectiveness of our proposed method, we conducted experiments under three types of attacks: MR, Edge case, and NEUR.
+We compared our method with FedAVG (Baseline), FoolsGold, FLTrust, and Flame to evaluate the corresponding TSR and ASR under different defense algorithms.
+The experimental results are shown in Figure \ref{fig:lab1}.
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/lab1-combined.pdf}
+    \caption{ASR and TSR of various defense algorithms (FedAVG, FLTrust, Foolsgold, Flame, SecFFT) under three attacks (MR, NEUR, Edge case).}
+    \label{fig:lab1}
+\end{figure}
+
+% 从图中可以看出，SecFFT在面对三种攻击场景（MR、NEUROTOXIN、EDGE_CASE）时展现了最强的鲁棒性和出色的模型性能。在所有场景下，SecFFT的攻击成功率（ASR）始终接近于零，测试准确率（TSR）依然维持在高位，这意味着该算法能够有效防御攻击，能够成功识别并防御恶意用户，同时保持全局模型的性能和准确性。相比之下，其他防御算法表现则较为逊色。虽然Flame在降低ASR方面同样表现优异，能有效识别出恶意用户，但其在识别过程中引入了较多噪声，导致全局模型的准确率（TSR）下降，特别是在MR攻击下，性能损失更为显著。FLTrust在应对MR攻击时几乎完全失效，ASR迅速上升，未能有效防御；尽管在NEUROTOXIN和EDGE_CASE场景下表现有所改善，但防御效果依然不够稳定。Foolsgold在MR和NEUROTOXIN攻击下的防御效果较差，ASR依旧很高，仅在EDGE case下表现出一些效果，但并不显著。总体而言，这些算法在抵御攻击时未能同时兼顾模型的性能，进一步突显了SecFFT在联邦学习攻击防御中的显著优势，成为最优的防御选择。
+As shown in the figure, SecFFT demonstrates the strongest robustness and excellent model performance when faced with three types of attack scenarios (MR, NEUR, EDGE CASE).
+In all scenarios, SecFFT's ASR remains close to zero, while the TSR stays high, indicating that the algorithm can effectively defend against attacks by successfully identifying and mitigating malicious users while maintaining the performance and accuracy of the global model.
+In contrast, other defense algorithms perform less favorably.
+Although Flame also performs well in reducing ASR and effectively identifying malicious users, it introduces a significant amount of noise during the identification process, which leads to a decrease in the global model's accuracy (TSR), particularly under the MR attack, where the performance loss is more pronounced.
+FLTrust nearly fails to defend against MR attacks, with ASR rising rapidly, rendering it ineffective.
+While its performance improves under NEUR and EDGE CASE scenarios, the defense effectiveness remains unstable.
+FoolsGold exhibits poor defense performance under MR and NEUR attacks, with ASR still high, showing some effectiveness only in the EDGE CASE scenario, but not significantly.
+Overall, these algorithms fail to balance model performance while defending against attacks, further highlighting SecFFT's significant advantage in federated learning attack defense, making it the optimal choice for defense.
+
+\subsection{Performance of Attack Behavior Perception}
+% 为了验证我们所提方法在恶意用节点识别方面具有较高的准确度，我们总结了在三种攻击(MR, Edge case, NEUR)下所有轮次中SecFFT对恶意节点的识别情况，并与FoolsGold, FLTrust, and Flame三种防御算法进行了对比。具体对比结果如图\ref{fig:lab2}所示，我们利用t-sne算法将所有轮次中节点的更新降维到了二维平面，图中红色点表示被错误识别的节点，包括恶意节点被识别成良性节点以及良性节点被错误识别成恶意节点。对于无法直接获得节点识别情况的Foolsgold防御算法，我们通过利用KMeans聚合算法将该防御算法过程中分配给每个用户的聚合权重聚成两类，并取最大类作为良性节点其余作为恶意节点的结果作为统计标准。
+To validate the high accuracy of our proposed method in identifying malicious nodes, we summarized the detection results of SecFFT under three types of attacks (MR, Edge Case, NEUR) across all rounds and compared them with three defense algorithms: FoolsGold, FLTrust, and Flame.
+The specific comparison results are shown in Figure \ref{fig:lab2}.
+We used the t-SNE algorithm to reduce the dimensionality of the nodes' updates from all rounds to a two-dimensional plane.
+In the figure, red dots represent misidentified nodes, which include malicious nodes incorrectly identified as benign and benign nodes incorrectly identified as malicious.
+For the Foolsgold defense algorithm, which does not directly provide node identification results, we used the KMeans clustering algorithm to classify the aggregation weights assigned to each user during the defense process into two clusters, considering the larger cluster as benign nodes and the remaining as malicious nodes for evaluation purposes.
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/lab2-combined.pdf}
+    \caption{Visualization of node identification results under three different attack scenarios (MR, Edge Case, NEUR) for various defense algorithms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE dimensionality reduction.
+The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign and benign nodes incorrectly identified as malicious.
+}
+
+    \label{fig:lab2}
+\end{figure*}
+% 如图所示，SecFFT 的错误识别率最低，仅为 3%，表明其在各种攻击模式下具有更强的防御能力和鲁棒性，能够准确区分恶意节点和良性节点。而 Flame、FLTrust 和 FoolsGold 的错误识别率分别为 12%、19.5% 和 37.5%，错误识别的节点分布较为广泛，尤其是 FoolsGold 的错误识别率最高，显示出其在应对复杂攻击场景时的防御效果较差。相比之下，SecFFT 在应对多种攻击类型时表现最为优异，能有效降低错误识别率，展示了更好的泛化能力和准确性。
+As shown in the figure, SecFFT has the lowest misidentification rate, at only 3\%, indicating its stronger defense capability and robustness in various attack scenarios, accurately distinguishing between malicious and benign nodes.
+In contrast, the misidentification rates of Flame, FLTrust, and FoolsGold are 12\%, 19.5\%, and 37.5\%, respectively, with misidentified nodes more widely distributed.
+Notably, FoolsGold has the highest misidentification rate, demonstrating poor defense performance in handling complex attack scenarios.
+Comparatively, SecFFT performs the best in dealing with various attack types, effectively reducing the misidentification rate and showing better generalization ability and accuracy.
+
+\subsection{Performance of SecFFT}
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/lab3-combined.pdf}
+    \caption{lab3}
+    \label{fig:lab3}
+\end{figure*}
+
+\subsection{}
+
+\begin{table*}[h!]
+\small
+\centering
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+\hline
+Attack & Defense & TP & FP & TN & FN & Accuracy & Precision & Recall & Specificity & FPR & FNR & AUC & MCC \\ \hline
+
+\multirow{4}{*}{Original} & Foolsgold & 10 & 0 & 35 & 5 & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
+                      & FLTrust   & 6  & 0 & 35 & 9 & 0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\ \cline{2-14}
+                      & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
+                      & SecFFT    & \textbf{15} & 0 & 35 & 0  & \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & 0.00 & \textbf{1.00} & \textbf{1.00} \\ \hline
+\multirow{4}{*}{Size} & Foolsgold & 10 & 0 & 35 & 5 & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
+                      & FLTrust   & 6  & 0 & 35 & 9 & 0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\ \cline{2-14}
+                      & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
+                      & SecFFT    & \textbf{15} & 0 & 35 & 0  & \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & 0.00 & \textbf{1.00} & \textbf{1.00} \\ \hline
+\multirow{4}{*}{Angle} & Foolsgold & 10 & 0 & 35 & 5 & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
+                      & FLTrust   & 6  & 0 & 35 & 9 & 0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\ \cline{2-14}
+                      & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
+                      & SecFFT    & \textbf{15} & 0 & 35 & 0  & \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & 0.00 & \textbf{1.00} & \textbf{1.00} \\ \hline
+\end{tabular}
+\caption{Classification metrics results under different attack and defense methods}
+\end{table*}
+
+% As a preeminent collaborative artificial intelligence paradigm, Federated Learning (FL) has garnered substantial research focus \cite{ETT2}. 
+% By effectively mobilizing a substantial number of participants with a discrete distribution, FL can concurrently enhance learning performance, resource utilization, and data security. 
+% Besides, as intelligent applications proliferate, concerns regarding fairness-aware federated learning (FFL) have also captured significant attention \cite{zhou2021towards-KDDtutorial-FFL}.
+Due to the agnostic of multiple data sources, models trained through FL may exhibit discriminatory tendencies toward specific features or demographic groups, such as gender, race, and occupation (e.g., COMPAS recidivism algorithm \cite{angwin2022machine} and facial recognition system \cite{raji2019actionable}).
+In response to this inherent deficiency, various FFL algorithms, such as FairFed \cite{ezzeldin2023fairfed}, Ditto \cite{li2021ditto}, and FairFL \cite{zhang2020fairfl}, have been proposed.
+
+% %安全问题很重要
+% \subsection{Mutual reliability problem of FFL}
+% Meanwhile, along with the continual emergence of novel attack techniques, such as gradient leakage and model poisoning \cite{fang2020local}, the \textit{``trust crisis''} \cite{zhou2022multi} has become a critical bottleneck in determining FFL deployment capabilities \cite{rodriguez2023survey}.
+Establishing a robust \textit{mutual reliability} relationship between the FL aggregator (parameter server) and local participants has proven challenging \cite{zhou2022multi}.
+To be specific, on the one hand, concerns about data sharing leading to privacy breaches (\textit{aggregator's reliability}) \cite{wang2021variational} raise apprehensions among owners of data and computational resources, significantly diminishing enthusiasm for collaborative learning participation and giving rise to the phenomena of ``isolated data islands''.
+On the other hand, PSs are troubled by the difficulty of promptly and accurately thwarting stealthy attackers hidden among a vast client base.
+This concern  (\textit{client nodes' reliability}) raises the specter of manipulation or even invalidation of the entire model, resulting in severe economic and intellectual property losses.
+
+% %列举几个特点，导致现有安全技术不能适用
+% %尽管多种最新的安全增强技术能够取得显著的防御效果，但攻击者并不能
+% \subsection{Characteristics and motivation of mutual reliable FFL in heterogeneous UAV networks}
+% With the advancement of integrated sensing, computation and communication (ISCC) \cite{he2023integrated}, and the space-air-ground integrated network (SAGIN) \cite{shen2023survey}, unmanned aerial vehicle (UAV) networks have played a crucial role in various domains such as post-disaster reconstruction, emergency temporary communication, and medical monitoring \cite{lu2023uav}.
+FLs based on UAV networks have also found widespread applications \cite{ETT1, ETT3, pandya2023federated}.
+However, despite the proposal of various secure FL technologies, the inherent characteristics of UAV networks continue to pose significant challenges in establishing mutual reliability for FFL in UAV environments.
+Specifically, these challenges encompass the following aspects:
+
+% %异构：大范围异构，小范围相似.因此
+% \textbf{1) Heterogeneity among UAV nodes:} As illustrated in Figure \ref{fig1:UAV-Network}, constrained by the mobility and patrol paths of UAVs, individual nodes are often limited to conducting data collection within a specific regional scope.
+Hence, even when employing identical equipment, the data distributions among UAV nodes across the entire network exhibit significant heterogeneity, while UAVs within the same area are similar.
+Therefore, various existing reliable FL technologies lacking adaptive considerations (such as Krum \cite{blanchard2017machine-krum}, Baffle \cite{andreina2021baffle}, and AGRamplifier \cite{gong2023agramplifier}) can lead to substantial accuracy losses.
+
+% %资源受限：因此高消耗的安全策略并不能适用  高计算消耗和带宽占用的安全技术（例如，加密）
+% \textbf{2) Resource limitation of UAV devices:} As UAV nodes function as mobile devices and bear substantial flight-related loads, their communication and energy resources are relatively constrained.
+The efficiency of FFL training is equally important.
+Consequently, solutions integrating cryptography, auxiliary training, multi-round detection, or other security mechanisms with high computational costs and bandwidth utilization (e.g., ShieldFL \cite{ma2022shieldfl}, AFA \cite{munoz2019byzantine-AFA}, and FLdetector \cite{zhang2022fldetector}) are not applicable for real-world deployment.
+
+% %我们的目标是实现（1）异构容忍的FFL框架（2）强隐私保护的个性化训练交互（3）抗污染的可信评估
+% The aforementioned characteristics distinguish the reliable FFL in heterogeneous UAV networks from existing secure FFL technologies, thereby motivating the establishment of the following new criteria for its enhancement:
+
+% \textbf{1) Heterogeneity-tolerant FFL framework:} Suitable nodes from the highly heterogeneous UAV networks can be organized promptly to efficiently fulfill arbitrary fairness-aware FL tasks, which also mitigates redundant computational energy consumption and accuracy loss induced by heterogeneity.
+
+% \textbf{2) Privacy-preserving personalized training:} Throughout the iteration training and interaction process, sample-level privacy protection must be implemented to prevent the leakage of sensitive information.
+Additionally, considering the resource constraints of UAV nodes, computational and bandwidth demands should be limited.
+
+% \textbf{3) Poisoning-resilient credit evaluation:} In addition to robust defense capabilities against various poisoning attacks, compatibility with heterogeneity and privacy requisites is also essential.
+In other words, without compromising the effectiveness of privacy guarantee, heterogeneous benign UAV nodes should be treated equally during the whole FFL workflow.%Achieving fairness among heterogeneous benign users without compromising the effectiveness of privacy protection is a crucial aspect.
+
+% \subsection{Our solution and contributions}
+% %解决方案
+% % Hence, in this paper, we propose mutually reliable FFL (MR-FFL), a stratified community-based framework to facilitate privacy protection (FFL aggregator's reliability) and poisoning elimination (client nodes' reliability) jointly for FFL in heterogeneous UAV networks.
+% % We first divide UAV nodes into both peer communities and colleague communities according to cross-participant similarity and task-oriented fitness, respectively. 
+% % Thus, the arbitrarily settled learning tasks following fair principles can be efficiently completed by fine-tuned colleague communities, even in the presence of a large degree of heterogeneity among peer communities.
+% Therefore, this paper proposes mutual reliable FFL (MR-FFL), a stratified community-based framework that collectively promotes privacy protection during data sharing (reliability of FFL aggregators) and poisoning elimination during model aggregation (reliability of client nodes) in heterogeneous UAV networks.
+The contributions of the proposed MR-FFL are three-fold:
+
+% %贡献
+
+% \begin{itemize}
+%     %\item In light of shuffling-based MTD \cite{zhou2022multi} strategies, we propose a credit to identify the malicious attackers without compromising of privacy guarantees, which is also one of the design inspirations of our framework.
+%     \item Initially, UAV nodes are partitioned into peer communities and colleague communities based on cross-participant similarity and task-oriented adaptability.
+Thus, adhering to fairness principles, any arbitrarily determined learning task can be effectively accomplished through carefully selected colleague communities, even in the presence of significant heterogeneity among UAV nodes, while peer communities provide an amplified privacy guarantee.
+%     %随后，我们提出了PSDP的隐私模糊化方式进行自适应训练，通过参数动态约束差分隐私敏感度，从而在同等隐私保护水平下大幅降低异构环境下的噪声损失。
+%     \item Subsequently, inspired by cross-silo privacy protection, we introduce the new privacy perturbation notion of peer community-specific differential privacy (PSDP) with changeable privacy budget.
+Through dynamically constraining the DP sensitivity within each peer community, PSDP significantly reduces noise loss in heterogeneous environments under equivalent privacy protection levels.
+%     %此外，我们提出了基于三值主观逻辑模型的信用评估，分别抽离投毒攻击的“操纵”（相似度）和“破坏”（准确度）行为进行群体参与的综合长效评价，从而有效抵御多种隐蔽的投毒攻击范式。
+%     \item Furthermore, we propose a new credit evaluation based on the ternary subjective logic model.
+This evaluation effectively integrates comprehensive and long-term assessments with the collective participation of heterogeneous UAV nodes, specifically extracting the ``manipulation'' (similarity) and ``disruption'' (accuracy) behaviors of poisoning attacks.
+This approach proves effective in defending against various covert poisoning attack paradigms.
+%     %\item Then, we integrate community-specific differential privacy into the MR-FFL process, to achieve privacy amplification as well as efficient and personal collaborative training at the same time.
+%     %\item More importantly, we proposed a community-based credit evaluation to resist poisoning attacks in heterogeneous environments.
+
+% \end{itemize}
+
+% %本文组织结构
+% The remainder of this paper is organized as follows: The related works are reviewed in Section \uppercase\expandafter{\romannumeral2}.
+The system model is presented in Section \uppercase\expandafter{\romannumeral3}.
+Then, stratified community construction, adaptive training, and credit evaluation modules are expounded upon in Section \uppercase\expandafter{\romannumeral4} to \uppercase\expandafter{\romannumeral6}, respectively, providing a detailed account of availability, privacy, and integrity for FFL in heterogeneous UAV networks.
+Section \uppercase\expandafter{\romannumeral7} presents experimental results.
+Finally, Section \uppercase\expandafter{\romannumeral8} concludes this paper.
+%and briefly explores future directions.
+
+% \section{Related work}
+
+% % \begin{tabular}{|p{0.4\textwidth}|p{0.5\textwidth}|}
+% % \hline
+% % \textbf{论文的期刊名、年份、引用} & \textbf{简介} \\
+% % \hline
+% % 期刊名1, 2024, 引用1 & 这篇论文讨论了...... \\
+% % \hline
+% % 期刊名2, 2023, 引用2 & 本研究着重于...... \\
+% % \hline
+% % 期刊名3, 2022, 引用3 & 本文提出了...... \\
+% % \hline
+% % \end{tabular}
+
+% According to the three basic tenets of information security \cite{zhou2021augmented-globecom}, in this section, we systematically review the most crucial hindrances of existing FFL solutions in UAV networks: \textit{availability}, \textit{confidentiality}, and \textit{in tegrity} problems, which we settled in following sections, respectively.
+% \subsection{FFL in heterogeneous environments (availability)}
+% To accomplish learning tasks and ensure the availability of FFL in heterogeneous environments, existing solutions can adopt debiasing on the client or server side.
+% \subsubsection{Server-side debiasing} %全局化
+% As the name indicated, server-side debiasing methods usually monitor the composition of training data and design new loss functions like Ratio loss \cite{wang2021addressing} to mitigate the impact of heterogeneity.
+% Besides, FairFed \cite{ezzeldin2023fairfed} adjusts the aggregation weights of heterogeneous participants based on equal opportunity difference (EOD).
+Hence, clients can conduct different debiasing processes.
+% Likewise, FedProto \cite{tan2022fedproto} regularizes the training of local models with the aid of abstract class prototypes from the server. 
+% To handle the performance degradation caused by heterogeneous and long-tailed data, CReFF\cite{shang2022federated} re-trains the biased classifier with federated features in a privacy-preserving manner.
+% Different from the above methods, several clustered FLs provide separate models for heterogeneous clients \cite{sattler2020clustered-CFL}, which can incur exponentially growing computation costs.
+% \subsubsection{Client-side debiasing} %个性化
+% Diverging from server-side debiasing, client-side debiasing methods primarily enhance accuracy by altering the local model \cite{tan2022towards}. 
+% For example, while retaining the standard FL mechanism as the inner optimizer, FairBatch \cite{roh2020fairbatch} further adds an outer optimizer to select minibatch sizes and improve model fairness adaptively.
+Similarly, Ditto \cite{li2021ditto} develops a regular term to optimize the local models without changing global aggregation rules.
+The robustness and fairness are jointly improved.
+% Moreover, Mohri \textit{et al.} \cite{mohri2019agnostic} propose agnostic federated learning (AFL) and prove its fairness using data-dependent Rademacher complexity guarantees.
+
+% %总结：现有FFL有两大问题，首先是效率不佳，往往需要多轮训练，不适合于能量受限的UAV network。其次是缺乏考虑对联邦学习可信技术的兼容。
+% To summarize, existing FFLs encounter two drawbacks.
+Firstly, they exhibit unsatisfactory efficiency, often necessitating multiple training rounds, rendering them unsuitable for energy-constrained UAV networks.
+Secondly, the consideration for compatibility with reliable technologies is insufficient.
+% \subsection{Reliability of information sharing (confidentiality)}%隐私安全
+% \subsubsection{Cryptography solutions} 
+% Homomorphic encryption (HE) and other cryptographic methods naturally serve as suitable privacy protection measures.
+For instance, ShieldFL \cite{ma2022shieldfl} employs secure cosine similarity to measure the distance between two encrypted gradients, utilizing dual-gate HE to resist model poisoning.
+BatchCrypt \cite{zhang2020batchcrypt} further enhances HE efficiency by incorporating batch gradient encoding and holistic encryption, effectively reducing training time and communication overhead.
+Additionally, FairFL \cite{zhang2020fairfl} adopts the principled deep multi-agent reinforcement learning framework and secure information aggregation protocol to simultaneously optimize the accuracy and the fairness of FFL while respecting the strict privacy constraints of the clients.
+% Besides, Lyu \textit{et al.} \cite{lyu2020towards} develop a local credibility mutual evaluation mechanism to guarantee fairness, and a three-layer onion-style encryption scheme to guarantee both accuracy and privacy.
+% \subsubsection{Obfuscation solutions}
+
+% In comparison to encryption, obfuscation approaches such as differential privacy (DP) do not introduce excessive overhead or extensive mechanism modifications, thus garnering significant attention \cite{padala2021federated}.
+For instance, Wei \textit{et al.} \cite{wei2021low} consider both general training performance and individual client privacy requirements to mitigate latency on wireless channels, addressing challenges posed by channel fading and interference in unknown network environments.
+Furthermore, considering potential model distortion from obfuscation techniques, privacy amplification as Shuffle \cite{girgis2021shuffled} can enhance the deployment capabilities of privacy protection.
+NbAFL \cite{wei2020federated-NbAFL} further diminishes the accuracy loss associated with DP by injecting secondary noise into the uplink and downlink channels.
+
+% %总结：密码学方法通信量和计算量过大，而DP方法缺乏对异构考量
+% Upon analysis, privacy-preserving information-sharing methods based on cryptography often incur excessive communication and computational overhead.
+On the other hand, methods relying on obfuscation like differential privacy lack adaptability to heterogeneous network environments, usually resulting in significant accuracy losses.
+% \subsection{Reliability of model aggregation (integrity)}%model安全
+% To resist the stealthy yet destructive poisoning attacks \cite{lyu2023poisoning}, multiple defense methods are proposed, which can be divided into the following types based on the realization concepts:
+% \subsubsection{Mitigation-oriented technologies} 
+% To ensure the integrity of the aggregated model, various robust FL methods, such as Byzantine-robustness, have been proposed.
+For instance, Krum \cite{blanchard2017machine-krum} selects partial neighboring nodes as references, enabling the algorithm to choose updates with the highest consensus for the next iteration.
+Diverging from Krum's approach of selecting only one update, FABA \cite{xia2019faba} employs gradient outlier computation to discard few gradients while retaining the majority of clients' training results, significantly enhancing learning speed.
+Building upon these methods, Gong \textit{et al.} devise AGRamplifier \cite{gong2023agramplifier}, which enhances the "morality" of local updates by identifying the most suppressive features in each gradient update.
+This augmentation further elevates model robustness, fidelity, and efficiency.
+
+% \subsubsection{Detection-oriented technologies} 
+% An alternative approach to fortify against poisoning is the direct detection of the learning model using a validation dataset or predefined rules.
+For instance, Zeno \cite{xie2019zeno} evaluates the stochastic descendant score for each gradient based on a validation dataset, selectively discarding gradients with low scores for the stochastic descendant.
+In contrast to relying on an auxiliary validation set, Baffle \cite{andreina2021baffle} capitalizes on the diverse datasets accessible across various clients by integrating a feedback loop into the FL process.
+Besides, Fldetector \cite{zhang2022fldetector} anticipates a client's model update during each iteration by leveraging historical model updates and flags a client as potentially malicious if the received model update contradicts the predicted update.
+% It is noteworthy that detection-centric solutions entail additional training costs and may not identify some zero-day attacks.
+
+% \subsubsection{Credit-oriented technologies} 
+% %鉴于联邦学习是协作式、多轮次的交互过程，通过维护信用评价机制同样可以很好地清除恶意用户。例如，Kang等人使用多权重主观逻辑模型设计基于声誉的可靠联邦学习用户选择方案，并利用区块链实现声誉管理。在不需要辅助验证数据集的情况下，Xu等人提出余弦梯度Shapley值来评估每个智能体上传的模型参数更新/梯度的期望边际贡献，以区别对待。Tan等人提出了一种基于声誉感知的随机整数规划的FL客户选择方法，可以最优地选择和补偿具有不同声誉档案的客户，从而对抗潜在的异常行为。
+% Considering that FL is a collaborative and iterative process, the credit evaluation mechanism proves effective in poisoning resistance.
+For instance, Kang \textit{et al.} \cite{credit1-kang2019IOT} design a reputation-based reliable scheme utilizing a multi-weight subjective logic model, and implement reputation management through blockchain.
+Xu \textit{et al.} \cite{xu2020reputation, xu2021gradient}, without the need for auxiliary verification datasets, introduced the cosine gradient Shapley value to assess the model parameter updates/gradients uploaded by each client.
+Tan \textit{et al.} \cite{tan2022reputation} propose a reputation-aware stochastic integer programming client selection method, selecting and compensating clients with varying reputation profiles to counter potential anomalous behavior.
+
+% %总结：现有方案缺乏对隐私的考量，计算量过大
+% In general, existing solutions often struggle to achieve a satisfactory balance between privacy and defensive performance, while also lacking adaptability to heterogeneous and dynamically changing environments.
+Furthermore, some methods exhibit relatively large computational overhead, imposing a non-negligible burden on UAV nodes.
+
+% \section{System model \& Preliminaries}
+% %%symbols 表格
+% \begin{table}[!t]
+% {
+% \renewcommand{\arraystretch}{1.2}
+% \caption{Summary of Main Notation}
+% \label{notations}
+% \vspace{0em}
+% \centering
+% \begin{tabular}{| c || l |}
+% \hline
+% \textbf{Symbol} & \multicolumn{1}{c |}{\textbf{Description}}\\
+%     \hline
+%     $U_i,\mathcal{D}_i$ & The $i$-th UAV devices and its dataset\\
+%     \hline
+%     $n^{s_{m}, i},\mathcal{P}^i$ & The size and normalized distribution of $\mathcal{D}_i$\\
+%     \hline
+%     $\mathcal{P}^{Tar}, w$ & Target distribution and model of learning task $Job$\\
+%     \hline
+%     $T$ & The maximum communication rounds of $Job$\\
+%     \hline
+%     $C,K$ & The set and number of all peer communities\\
+%     \hline
+%     $S,M$ & The set and number of all colleague communities\\
+%     \hline
+%     %$L$ & The number of clients in each super node\\
+%     %\hline
+%     $c_k$ & The $k$-th peer community\\
+%     \hline
+%     $s_m$ & The $m$-th colleague community\\ 
+%     \hline
+%     $\Delta \widetilde{\omega}_{t}^{s_{m},i}$ & The weight updates from $U_i \in s_m$ in round $t$\\
+%     \hline
+%     $p^{s_{m}, i}$ & The aggregation coefficient for $U_i$ within $s_m$\\
+%     \hline
+%     $\Delta\widetilde{\omega}_{t}^{s_{m}}$ & The weight updates from $s_m$ in round $t$\\
+%     \hline
+%     $p^{s_{m}}$ & The aggregation coefficient for $\Delta\widetilde{\omega}_{t}^{s_{m}}$ from $s_m$\\
+%     \hline
+%     $E_k$ & The clipping bound of peer community $c_k$\\
+%     \hline
+%     $Sen_k$ & The maximum sensitivity of $c_k$\\
+%     \hline
+%     $\varepsilon_k,\delta_k$& The parameters of differential privacy \\
+%     \hline
+%     $L$& The minimum size of colleague community\\
+%     \hline
+%     $\alpha^{a,b}_{t}$& The cosine similarity between $a$ and $b$\\
+%     \hline
+%     $PI^{c_k \rightarrow i}_{t}$ & The positive interaction between $c_k$ and $U_i$\\
+%     \hline
+%     $NI^{c_k \rightarrow i}_{t}$& The positive interaction between $c_k$ and $U_i$\\
+%     \hline
+%     $\Upsilon^{c_k \rightarrow i}_{t}$& The peer reputation opinion vector of $c_k$\\
+%     \hline
+%     $\Phi^{c_k \rightarrow i}_{t}$& $c_k$'s credit evaluation towards $U_i$ in round $t$\\
+%     \hline
+%     $\Upsilon^{s_m}_{t}$ & The colleague reputation opinion vector towards $s_m$\\
+%     \hline
+%     $\Phi^{s_m \rightarrow i}_{t}$& The colleague credit evaluation for $\forall U_i \in s_m$\\
+%     \hline
+%     $\Upsilon^{i}_{t},\Phi^{i}_{t}$& The comprehensive reputation and credit of $U_i$\\
+%     \hline
+%     $\psi^{i}_t$& The fairness-guaranteed selection probability\\
+%     \hline
+%     \end{tabular}
+%         }
+%      \vspace{-1.5em}
+%      \end{table}
+
+% \textbf{Heterogeneous UAV network scenario.} 
+% %\subsection{Network scenario}
+% %对于一个多无人机多任务联邦学习场景，有一个服务器与N个无人机，设无人机集合为$U=\{U_i\}$，$\vert\vert U\vert\vert=N$。所有无人机获取的数据集集合为$D=\{D_i\}$，第k个无人机的数据分布为$\mathcal{P}^k\in \mathbb{t}^F$，其中$F$为特征维度；任务场景集合为$T$，其中第k个任务场景中的数据分布为$\mathcal{P}^{tar_k}$。在同一现实场景中，无人机采集到的数据通常是类似的，即对于某个场景的分布$\phi$，所有属于该现实场景的设备集合$B'$均满足$\exists \epsilon\in \mathbb{t}^F,\forall k \in B', ||\phi-\mathcal{P}^k||_1 \leq \epsilon$。
+% As shown in Figure \ref{fig1:UAV-Network}, assume a multi-UAV multi-task federated learning scenario for the classification problems.
 There exists a parameter server (PS)/aggregator (normally equipped with ground base station) and $N$ UAV nodes (UN) $\mathbf{U}\triangleq\{U_1,...U_i,...U_N\}$.
@@
 %with varied size $n_i$.
-Here $x$ and $y$ are raw data and label, respectively.
+% Here $x$ and $y$ are raw data and label, respectively.
 As the nodes with overlapped aerial areas or patrol routines may have similar data distributions, we have $\exists \epsilon\in \mathbb{R}^F,\forall U_i, U_j \sim \phi_q, ||\mathcal{P}^i-\mathcal{P}^j||_p \leq \epsilon^{\prime}$, where $\mathcal{P}^i$ is the normalized distribution of $\mathcal{D}_i$.
@@
 
-%\subsection{Threat model}
-%值得一提的是，方便起见，我们此处仅以多分类问题中的数据类别作为公平性感知针对的对象，实际使用中可以通过特征extractor扩展到数据包含的任意抽象特征。此外，我们以范数差异度作为公平性衡量标准，实际应用中，也可以选取AIDD、DSF、SF等衡量方式并在特定方面取得更好的效果。
-It is crucial to highlight that, for better understanding, our focus in this paper is solely on the data distribution of multi-classification problems as the target for fairness awareness.
+% %\subsection{Threat model}
+% %值得一提的是，方便起见，我们此处仅以多分类问题中的数据类别作为公平性感知针对的对象，实际使用中可以通过特征extractor扩展到数据包含的任意抽象特征。此外，我们以范数差异度作为公平性衡量标准，实际应用中，也可以选取AIDD、DSF、SF等衡量方式并在特定方面取得更好的效果。
+% It is crucial to highlight that, for better understanding, our focus in this paper is solely on the data distribution of multi-classification problems as the target for fairness awareness.
 In practical scenarios, this concept can be easily extended to any abstract features derived from specific demographic groups through feature extractor as exemplified in \cite{shuai2022balancefl}.
@@
 
-\textbf{Fairness-aware learning task.} Without loss of generality, the fairness-aware learning task can be denoted with the quadruple as $Job\triangleq(w,\mathcal{P}^{tar},t_0, T)$, which consists of the model $w$, target distribution $\mathcal{P}^{tar}$, arrival time $t_0$, and duration $T$.
+% \textbf{Fairness-aware learning task.} Without loss of generality, the fairness-aware learning task can be denoted with the quadruple as $Job\triangleq(w,\mathcal{P}^{tar},t_0, T)$, which consists of the model $w$, target distribution $\mathcal{P}^{tar}$, arrival time $t_0$, and duration $T$.
 Different from existing solutions designed for certain $\mathcal{P}^{tar}$ \cite{li2022data,zeng2022heterogeneous,hiessl2022cohort}, our method can adaptively choose and schedule suitable UAV groups when a new learning task arrives.
 
-\textbf{Optimization objective.} We start with vanilla FL algorithms like FedAvg \cite{li2019convergence-fedavg} without consideration of heterogeneity.
+% \textbf{Optimization objective.} We start with vanilla FL algorithms like FedAvg \cite{li2019convergence-fedavg} without consideration of heterogeneity.
 The optimization objective can be expressed as:
-%考虑一个联邦学习场景，有1个服务器和$N$个客户。具体来说，客户i的本地数据集为$D_{i}$，其类别分布被定义为$\mathcal{P}^{c_{k},i}$。不同客户的本地数据类别分布高度异构，与全局类别分布$\mathcal{P}^{real}$有巨大差距。为了最小化全局损失函数，得到普适的全局模型，我们有：
-\begin{equation}
-    w^{*}\triangleq \underset{w}{\arg \min } \sum_{i=1}^N p_i\mathcal{L}\left(w, \mathcal{D}_{i}\right) ,
-\end{equation}
-%其中，$\mathcal{L}_{i}(\cdot)$是客户i的由其本地经验风险得出的本地损失函数。然而，由于客户的数据间的高度异构性与客户数据分布与任务场景数据分布间的高度异构性，客户间的本地损失函数不尽相同，难以获得同时最小化各个模型经验风险的最优全局模型参数$w^{*}$并满足任务场景。因此，在上述场景中进行传统FL会导致全局模型无法正常收敛，无法得到满足任务场景的高性能全局模型。
-where $\mathcal{L}(.)$ represents the loss function derived from the local empirical risk of $U_i$, $p_i$ is the aggregation weight.
+% %考虑一个联邦学习场景，有1个服务器和$N$个客户。具体来说，客户i的本地数据集为$D_{i}$，其类别分布被定义为$\mathcal{P}^{c_{k},i}$。不同客户的本地数据类别分布高度异构，与全局类别分布$\mathcal{P}^{real}$有巨大差距。为了最小化全局损失函数，得到普适的全局模型，我们有：
+% \begin{equation}
+%     w^{*}\triangleq \underset{w}{\arg \min } \sum_{i=1}^N p_i\mathcal{L}\left(w, \mathcal{D}_{i}\right) ,
+% \end{equation}
+% %其中，$\mathcal{L}_{i}(\cdot)$是客户i的由其本地经验风险得出的本地损失函数。然而，由于客户的数据间的高度异构性与客户数据分布与任务场景数据分布间的高度异构性，客户间的本地损失函数不尽相同，难以获得同时最小化各个模型经验风险的最优全局模型参数$w^{*}$并满足任务场景。因此，在上述场景中进行传统FL会导致全局模型无法正常收敛，无法得到满足任务场景的高性能全局模型。
+% where $\mathcal{L}(.)$ represents the loss function derived from the local empirical risk of $U_i$, $p_i$ is the aggregation weight.
 Due to the high heterogeneity among UAV nodes and the substantial mismatch between participants' data distributions and task requirements, obtaining the globally optimal model parameters $\omega^{*}$ that simultaneously minimize the empirical risks of each model and align with task requirements is challenging.
@@
 
-Hence, similar to the existing fair FL solutions in \cite{mohri2019agnostic,zhang2020fairfl,ezzeldin2023fairfed}, we define the optimization objective as follows:
-\begin{equation}
-    w^{*}\triangleq \underset{w}{\arg \min } \ \mathcal{L}_{FFL}(\omega)=\underset{(x, y) \sim \mathcal{P}^{Tar}}{\mathbb{E}}[\mathcal{L}{(\omega,(x, y))}]
-\end{equation}
-%（我这里想的是为了便于之后的凝聚聚类）此外，由于不同现实场景之间可能有较大的数据分布差异，与任务数据分布高度异构。为了最小化全局损失函数，得到适用于特定任务场景的全局模型，我们有：
-
-\section{Stratified community construction in heterogeneous environment}\label{sec:community}
-%为了实现高度异构的UAV节点集合与动态变化的学习任务之间的良好适配，我们提出了SCC。如图所示，该机制主要包含两个部分：PCC和CCC。其中PCC在网络初始化时运行一次，CCC则在每次收到新任务时运行一次。
-To achieve a robust alignment between highly heterogeneous UAV nodes and dynamically evolving learning tasks, we propose the stratified community construction (SCC) mechanism.
+% Hence, similar to the existing fair FL solutions in \cite{mohri2019agnostic,zhang2020fairfl,ezzeldin2023fairfed}, we define the optimization objective as follows:
+% \begin{equation}
+%     w^{*}\triangleq \underset{w}{\arg \min } \ \mathcal{L}_{FFL}(\omega)=\underset{(x, y) \sim \mathcal{P}^{Tar}}{\mathbb{E}}[\mathcal{L}{(\omega,(x, y))}]
+% \end{equation}
+% %（我这里想的是为了便于之后的凝聚聚类）此外，由于不同现实场景之间可能有较大的数据分布差异，与任务数据分布高度异构。为了最小化全局损失函数，得到适用于特定任务场景的全局模型，我们有：
+
+% \section{Stratified community construction in heterogeneous environment}\label{sec:community}
+% %为了实现高度异构的UAV节点集合与动态变化的学习任务之间的良好适配，我们提出了SCC。如图所示，该机制主要包含两个部分：PCC和CCC。其中PCC在网络初始化时运行一次，CCC则在每次收到新任务时运行一次。
+% To achieve a robust alignment between highly heterogeneous UAV nodes and dynamically evolving learning tasks, we propose the stratified community construction (SCC) mechanism.
 As illustrated in Figure \ref{fig2:framework}, SCC comprises two main components: peer community construction (PCC) and colleague community construction (CCC).
 PCC executes once during network initialization, while the CCC executes each time a new task is received.
-\subsection{Peer community construction (PCC)}
-Based on norm-based pair distance, we first cluster UAV nodes with similar data distributions into $K$ peer community $C=\{ c_{1}, \ldots, c_{K} \}$. The pair distance is calculated as:
-\begin{equation}
-d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}, \forall U_i,U_j\in \mathbf{U}.
-\end{equation}
-
-%基于客户的数据分布$\mathcal{P}^{i},i\in B$。我们用最大链接法对客户进行层次凝聚聚类。两个簇间的距离为它们中任意两个客户分布之间曼哈顿距离的最大值，当簇间距离大于合并阈值$\zeta$时停止合并，得到最终的聚类结果。由此可知同簇的任意客户分布之间的最大曼哈顿距离小于$\zeta$, 即$\forall i,j \in c, d_{i,j}<\zeta$。
-Then, we employ the complete-linkage method to achieve agglomerative hierarchical clustering (AHC) among UAV nodes.
+% \subsection{Peer community construction (PCC)}
+% Based on norm-based pair distance, we first cluster UAV nodes with similar data distributions into $K$ peer community $C=\{ c_{1}, \ldots, c_{K} \}$. The pair distance is calculated as:
+% \begin{equation}
+% d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}, \forall U_i,U_j\in \mathbf{U}.
+% \end{equation}
+
+% %基于客户的数据分布$\mathcal{P}^{i},i\in B$。我们用最大链接法对客户进行层次凝聚聚类。两个簇间的距离为它们中任意两个客户分布之间曼哈顿距离的最大值，当簇间距离大于合并阈值$\zeta$时停止合并，得到最终的聚类结果。由此可知同簇的任意客户分布之间的最大曼哈顿距离小于$\zeta$, 即$\forall i,j \in c, d_{i,j}<\zeta$。
+% Then, we employ the complete-linkage method to achieve agglomerative hierarchical clustering (AHC) among UAV nodes.
 The distance between two peer communities is defined as the maximum Euclidean distance between any two UNs' distributions.
@@
 Hence, the maximum distance between any pair of client distributions within the same PC is less than $\zeta$, i.e., $\forall U_i, U_j \in c_k, d_{i,j} < \zeta$, which is denoted as:
-\begin{equation}\label{eq:peer-construct}
- C\triangleq \underset{c_{1} \cup c_{2} \cup \ldots c_{K}=C}{\arg \min} \left(\max _{\forall c_{k},c_{k'} \in C ,U_i \in c_{k}, U_j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .
-\end{equation}
-
-%根据上述公式，我们得到具有相似类别分布的$K$个簇$C=\{c_{1},\ldots,c_{K}\}$。可以计算每个簇的平均数据分布，簇$c$的平均数据分布$\mathcal{P}^{c}$计算为：
-The average distribution of each peer community $c_k$ is:
-\begin{equation}
-    	 \mathcal{P}^{c_k}=\operatorname{norm}\left(\sum_{i \in c} n^{c,i} \mathcal{P}^{c,i} \right),
-\end{equation}
-%其中，$\mathcal{P}^{c,i}$是簇$c$中客户$i$的数据分布，$n^{c,i}$是簇$c$中客户$i$的数据量。为了保证隐私与数据安全，需要保证簇的个数，否则参与方将可能更容易推断出数据属于哪一簇。同时，当簇的数量较少时，每个簇代表的数据子集更大，这可能会导致更多的敏感信息聚集在同一簇中。如果某个恶意参与方能够成功识别并攻击一个簇，他们可能能够访问或推断出更多敏感信息，增加了数据泄露的风险。因此，需要添加约束：$K \geq \eta$，以确保隐私性。
-where $\mathcal{P}^{k,i}$ represents the data distribution of $U_i$ within cluster $c_k$, and $n^{k,i}$ denotes the size of $\mathcal{D}_i$. 
-To jointly ensure performance and security, it is imperative to control the number of peer communities.
+% \begin{equation}\label{eq:peer-construct}
+%  C\triangleq \underset{c_{1} \cup c_{2} \cup \ldots c_{K}=C}{\arg \min} \left(\max _{\forall c_{k},c_{k'} \in C ,U_i \in c_{k}, U_j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .
+% \end{equation}
+
+% %根据上述公式，我们得到具有相似类别分布的$K$个簇$C=\{c_{1},\ldots,c_{K}\}$。可以计算每个簇的平均数据分布，簇$c$的平均数据分布$\mathcal{P}^{c}$计算为：
+% The average distribution of each peer community $c_k$ is:
+% \begin{equation}
+%     	 \mathcal{P}^{c_k}=\operatorname{norm}\left(\sum_{i \in c} n^{c,i} \mathcal{P}^{c,i} \right),
+% \end{equation}
+% %其中，$\mathcal{P}^{c,i}$是簇$c$中客户$i$的数据分布，$n^{c,i}$是簇$c$中客户$i$的数据量。为了保证隐私与数据安全，需要保证簇的个数，否则参与方将可能更容易推断出数据属于哪一簇。同时，当簇的数量较少时，每个簇代表的数据子集更大，这可能会导致更多的敏感信息聚集在同一簇中。如果某个恶意参与方能够成功识别并攻击一个簇，他们可能能够访问或推断出更多敏感信息，增加了数据泄露的风险。因此，需要添加约束：$K \geq \eta$，以确保隐私性。
+% where $\mathcal{P}^{k,i}$ represents the data distribution of $U_i$ within cluster $c_k$, and $n^{k,i}$ denotes the size of $\mathcal{D}_i$. 
+% To jointly ensure performance and security, it is imperative to control the number of peer communities.
 A large $K$ enhances the chance of attackers inferring the sensitive information.
@@
 
-\subsection{Colleague community construction (CCC)}
-After peer community construction, we further select suitable UAV nodes to form colleague communities $S\triangleq\{s_1, \ldots, s_{M}\}$ with desirable distribution $\mathcal{P}^{tar}$, which avoids the performance degradation caused by heterogeneity.
-
-\subsubsection{Problem formulation}
-As shown in Figure \ref{fig2:framework}, based on the requirements of task $job_i$, we first generate the ``\textit{template}'' $\mathbf{h}$ of the colleague community (i.e., required ratio of clients $h_k$ from each peer community $c_k$ in a colleague community $s_{m}$).
+% \subsection{Colleague community construction (CCC)}
+% After peer community construction, we further select suitable UAV nodes to form colleague communities $S\triangleq\{s_1, \ldots, s_{M}\}$ with desirable distribution $\mathcal{P}^{tar}$, which avoids the performance degradation caused by heterogeneity.
+
+% \subsubsection{Problem formulation}
+% As shown in Figure \ref{fig2:framework}, based on the requirements of task $job_i$, we first generate the ``\textit{template}'' $\mathbf{h}$ of the colleague community (i.e., required ratio of clients $h_k$ from each peer community $c_k$ in a colleague community $s_{m}$).
 $\mathbf{h}\triangleq\{h_{1}, \ldots, h_{K}\}$ is a vector to stipulate this composition.
@@
 
-The optimization problem can be defined as:
-\begin{equation}\label{eq:problem}
-\begin{aligned}
-\mathbf{h}^*\triangleq &\underset{\mathbf{h}}{\arg \min} \vert\vert \mathbf{h}\cdot\mathbf{P}-\mathcal{P}^{tar}\vert\vert_2 \\
-\text{s.t. }& \forall c_k \in C, h_k\leq b_k, \\
-&\sum_{i=1} ^K h_i\geq r,
-\end{aligned}
-\end{equation}
-where $\mathbf{P}$ is a $K \times F$ matrix to denote the average feature values for all peer communities.
+% The optimization problem can be defined as:
+% \begin{equation}\label{eq:problem}
+% \begin{aligned}
+% \mathbf{h}^*\triangleq &\underset{\mathbf{h}}{\arg \min} \vert\vert \mathbf{h}\cdot\mathbf{P}-\mathcal{P}^{tar}\vert\vert_2 \\
+% \text{s.t. }& \forall c_k \in C, h_k\leq b_k, \\
+% &\sum_{i=1} ^K h_i\geq r,
+% \end{aligned}
+% \end{equation}
+% where $\mathbf{P}$ is a $K \times F$ matrix to denote the average feature values for all peer communities.
 Every row $\mathcal{P}^{c_k}\in \mathbb{R}^F$ denotes the average feature values of one peer community.
@@
 
-\subsubsection{Problem transformation} As the above problem is an NP-C quadratic integer optimization problem \cite{murty1985some}, we want to further reduce it to a linear programming problem to meet the efficiency requirements of UAVs.
-%即将$\mathcal{P}^{c_k}$拆成$l_k=\lceil \log_2(b_k+1) \rceil$行，拆成的新行中，第$i,1\leq i <l_k$行$d_i=2^{i-1}\mathcal{P}^{c_k},e_{k,i}=2^{i-1}$，第$l_k$行为$(b_k-2^i+1)\mathcal{P}^{c_k},e_{k,l_k}=(b_k-2^i+1)$。新矩阵有$R=\sum_{i=1}^k l_i$行，将原$\mathcal{P}$矩阵二进制拆分为一个$R\cdot F$的矩阵$\mathcal{Q}$，将整数规划问题转化成了一个0-1规划问题。
-For each $c_k$, to remove the constraint $B_k$, we conduct binary split on $\mathcal{P}^{c_k}$ to get $l_k=\lceil \log_2(B_k+1) \rceil$ new rows.
+% \subsubsection{Problem transformation} As the above problem is an NP-C quadratic integer optimization problem \cite{murty1985some}, we want to further reduce it to a linear programming problem to meet the efficiency requirements of UAVs.
+% %即将$\mathcal{P}^{c_k}$拆成$l_k=\lceil \log_2(b_k+1) \rceil$行，拆成的新行中，第$i,1\leq i <l_k$行$d_i=2^{i-1}\mathcal{P}^{c_k},e_{k,i}=2^{i-1}$，第$l_k$行为$(b_k-2^i+1)\mathcal{P}^{c_k},e_{k,l_k}=(b_k-2^i+1)$。新矩阵有$R=\sum_{i=1}^k l_i$行，将原$\mathcal{P}$矩阵二进制拆分为一个$R\cdot F$的矩阵$\mathcal{Q}$，将整数规划问题转化成了一个0-1规划问题。
+% For each $c_k$, to remove the constraint $B_k$, we conduct binary split on $\mathcal{P}^{c_k}$ to get $l_k=\lceil \log_2(B_k+1) \rceil$ new rows.
 Hence, the new matrix has $R=\sum_{i=1}^k l_i$ rows.
@@
 
-\begin{equation}
-\begin{aligned}
-\mathbf{x}^*\triangleq &\underset{\mathbf{x}}{\arg \min} \vert\vert \mathbf{x}\mathcal{Q}-\mathcal{P}^{tar}\vert\vert_2 \\
-\text{s.t. } &\forall c_k \in C, x_i\in\{0,1\}, \\
-&\sum_{i=1} ^K h_i\geq r,
-\end{aligned}
-\end{equation} 
-where $\mathbf{x}$ can map to $\mathbf{h}$, i.e., $h_k = \sum _{i=1} ^{l_k} e_{k,i}x_{\sum_{j=1}^{k-1} l_j +i}$, and $e_{k,l_k}=(B_k-2^i+1)$.
+% \begin{equation}
+% \begin{aligned}
+% \mathbf{x}^*\triangleq &\underset{\mathbf{x}}{\arg \min} \vert\vert \mathbf{x}\mathcal{Q}-\mathcal{P}^{tar}\vert\vert_2 \\
+% \text{s.t. } &\forall c_k \in C, x_i\in\{0,1\}, \\
+% &\sum_{i=1} ^K h_i\geq r,
+% \end{aligned}
+% \end{equation} 
+% where $\mathbf{x}$ can map to $\mathbf{h}$, i.e., $h_k = \sum _{i=1} ^{l_k} e_{k,i}x_{\sum_{j=1}^{k-1} l_j +i}$, and $e_{k,l_k}=(B_k-2^i+1)$.
 Hence, the above problem is equal to finding the minimum of $(\mathbf{x}\mathcal{Q}-\mathcal{P}^{tar})\cdot (\mathbf{x}\mathcal{Q}-\mathcal{P}^{tar})^T$ as:
 
-\begin{equation}
-\begin{aligned}
-\mathbf{x}^*\triangleq\underset{\mathbf{x}}{\arg \min}\ \mathbf{x}\mathcal{Q} &\mathcal{Q}^T\mathbf{x}^T-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+\mathcal{P}^{tar}\mathcal{P}^{tar^T}\\
-\text{s.t. }&\mathbf{x}\in\{0,1\}^R,\\
-&\sum_{i=1} ^K h_i\geq r.
-\end{aligned}
-\end{equation}
-
-We further introduce variable $z_{ij} \in \{0,1\}$ and have $z_{ij}\leq x_i$,$z_{ij}\leq x_j$,$z_{ij}\geq x_i+x_j-1$, to linearize the problem:
-
-\begin{equation}%\label{eq:problem}
-\begin{aligned}
-\min\ &\mathcal{Q}\mathcal{Q}^T\mathbf{y}-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+P^{tar}P^{tar^T}\\
-\text{s.t. }& \mathbf{x}\in\{0,1\}^R,
-\\
-&x_{ij}\leq x_i, x_{ij}\leq x_j, x_{ij}\geq x_i+x_j-1,
-\\&\sum_{i=1} ^K h_i\geq r.
-\end{aligned}
-\end{equation}
-
-Thus, the problem can be efficiently solved by linear programming solvers\footnote{For example, https://coin-or.github.io/pulp/}.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig2.PNG}
-\caption{Stratified community construction in a heterogeneous environment.}
-\label{fig2:framework}
-\end{figure}
-
-\section{Adaptive FFL training with privacy amplification}
-\subsection{Training workflow of MR-FFL}
-% 初始化过程: task generation & community initiation
-% Step 1: Local training
-% Step 2: Noise obfuscation
-% 中间过程: Upload gradient
-% Step 3: Inner-community aggregation
-% Step 4: Global aggregation
-% Step 5: Personalisation
-% 中间过程: Download model
-% Step 6: Local update
-
-As shown in Figure \ref{fig3:workflow}, the training workflow of MR-FFL mainly consists of the following steps in one round of iteration:
-
-\begin{itemize}
-    \item \textbf{Initialization:} Once the FFL task arrives, server conducts the CCC algorithm to quickly select $M$ colleague communities with similar average distributions near to $\mathcal{P}^{tar}$.
-    \item \textbf{Step 1:} First, each node $U_i \in s_m$ trains the current model with personal data to generate the local model $\omega_t^{s_m, i}$.
-    \item \textbf{Step 2:} Then, $U_i$ obfuscates the weights update $\widetilde{\omega}_{t}^{s_{m}, i}$ with differential private noise, and uploads it to the server.
-    \item \textbf{Step 3:} Colleague community aggregates $\widetilde{\omega}_{t}^{s_{m}, i}, \forall U_i \in s_m$ to generate a colleague model $\omega_{t}^{s_{m}}$.
-    \item \textbf{Step 4:} The server aggregates result $\omega^{s_k}$ from each colleague community $s_k \in S$ to get new global model.
-    \item \textbf{Step 5:} Besides, UAV peer community can maintain a personalized peer model $\omega_{t}^{c_{k}}$ to further improve local performance. 
-    \item \textbf{Step 6:} Finally, the global model is distributed to selected UAV nodes for the next round of training.
-\end{itemize}
-
-As Step 1, 2, and 6 aligns with existing secure FL training process \cite{wei2020federated-NbAFL,padala2021federated}, we focus on Step 3,4 and 5 subsequently.
-
-\subsubsection{Colleague community aggregation} 
-%为了尽可能地减小异构数据带来的模型方向的差异，以便更好地聚合普适的全局模型，在服务器聚合前，先在super node 内部聚合。也就是说，本地训练后，客户$i, i\in s_{m}$的加噪模型更新量$\Delta \widetilde{\omega}_{t}^{s_{m},i}$被上传到super node进行super node的内部同步。
-To reduce the canceling phenomenon caused by heterogeneous data and improve training efficiency,  we first aggregate all $\Delta \widetilde{\omega}_{t}^{s_{m}, i}$ within $s_m$ to generate more homogeneous weight updates $\Delta\widetilde{\omega}_{t}^{s_{m}}$ of colleague model $s_m$ before the global aggregation: %In other words, following local training, the perturbed model update quantity, denoted as $\Delta \widetilde{\omega}{t}^{s{m},i}$ for client $i$ where $i\in s_{m}$, is uploaded to the super node for internal synchronization before server-level aggregation.
-\begin{equation}
-    \begin{gathered}
-     \Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}
-     = \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i},
-     \end{gathered}
-\end{equation}
-where $p^{s_{m}, i}= {n^{s_{m}, i}}/{n^{s_{m}}}$ is aggregation coefficent, $n^{s_{m}}=\sum_{i \in s_{m}} n^{s_{m}, i}$.
-
-\subsubsection{Global aggregation} 
-Then, the server aggregates the learning results from all $s_m$ and updates the global model:
-\begin{equation}
-\widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}},
-\end{equation}
-where $p^{s_{m}}= \frac{n^{s_m}}{\sum_{s_{m} \in S} n^{s_m}}$, and $\widetilde{\omega}_{t}$ is the global model.
+% \begin{equation}
+% \begin{aligned}
+% \mathbf{x}^*\triangleq\underset{\mathbf{x}}{\arg \min}\ \mathbf{x}\mathcal{Q} &\mathcal{Q}^T\mathbf{x}^T-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+\mathcal{P}^{tar}\mathcal{P}^{tar^T}\\
+% \text{s.t. }&\mathbf{x}\in\{0,1\}^R,\\
+% &\sum_{i=1} ^K h_i\geq r.
+% \end{aligned}
+% \end{equation}
+
+% We further introduce variable $z_{ij} \in \{0,1\}$ and have $z_{ij}\leq x_i$,$z_{ij}\leq x_j$,$z_{ij}\geq x_i+x_j-1$, to linearize the problem:
+
+% \begin{equation}%\label{eq:problem}
+% \begin{aligned}
+% \min\ &\mathcal{Q}\mathcal{Q}^T\mathbf{y}-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+P^{tar}P^{tar^T}\\
+% \text{s.t. }& \mathbf{x}\in\{0,1\}^R,
+% \\
+% &x_{ij}\leq x_i, x_{ij}\leq x_j, x_{ij}\geq x_i+x_j-1,
+% \\&\sum_{i=1} ^K h_i\geq r.
+% \end{aligned}
+% \end{equation}
+
+% Thus, the problem can be efficiently solved by linear programming solvers\footnote{For example, https://coin-or.github.io/pulp/}.
+
+% % \begin{figure}[!t]
+% % \centering
+% % \includegraphics[width=\linewidth]{figures/fig2.PNG}
+% % \caption{Stratified community construction in a heterogeneous environment.}
+% % \label{fig2:framework}
+% % \end{figure}
+
+% \section{Adaptive FFL training with privacy amplification}
+% \subsection{Training workflow of MR-FFL}
+% % 初始化过程: task generation & community initiation
+% % Step 1: Local training
+% % Step 2: Noise obfuscation
+% % 中间过程: Upload gradient
+% % Step 3: Inner-community aggregation
+% % Step 4: Global aggregation
+% % Step 5: Personalisation
+% % 中间过程: Download model
+% % Step 6: Local update
+
+% As shown in Figure \ref{fig3:workflow}, the training workflow of MR-FFL mainly consists of the following steps in one round of iteration:
+
+% \begin{itemize}
+%     \item \textbf{Initialization:} Once the FFL task arrives, server conducts the CCC algorithm to quickly select $M$ colleague communities with similar average distributions near to $\mathcal{P}^{tar}$.
+%     \item \textbf{Step 1:} First, each node $U_i \in s_m$ trains the current model with personal data to generate the local model $\omega_t^{s_m, i}$.
+%     \item \textbf{Step 2:} Then, $U_i$ obfuscates the weights update $\widetilde{\omega}_{t}^{s_{m}, i}$ with differential private noise, and uploads it to the server.
+%     \item \textbf{Step 3:} Colleague community aggregates $\widetilde{\omega}_{t}^{s_{m}, i}, \forall U_i \in s_m$ to generate a colleague model $\omega_{t}^{s_{m}}$.
+%     \item \textbf{Step 4:} The server aggregates result $\omega^{s_k}$ from each colleague community $s_k \in S$ to get new global model.
+%     \item \textbf{Step 5:} Besides, UAV peer community can maintain a personalized peer model $\omega_{t}^{c_{k}}$ to further improve local performance. 
+%     \item \textbf{Step 6:} Finally, the global model is distributed to selected UAV nodes for the next round of training.
+% \end{itemize}
+
+% As Step 1, 2, and 6 aligns with existing secure FL training process \cite{wei2020federated-NbAFL,padala2021federated}, we focus on Step 3,4 and 5 subsequently.
+
+% \subsubsection{Colleague community aggregation} 
+% %为了尽可能地减小异构数据带来的模型方向的差异，以便更好地聚合普适的全局模型，在服务器聚合前，先在super node 内部聚合。也就是说，本地训练后，客户$i, i\in s_{m}$的加噪模型更新量$\Delta \widetilde{\omega}_{t}^{s_{m},i}$被上传到super node进行super node的内部同步。
+% To reduce the canceling phenomenon caused by heterogeneous data and improve training efficiency,  we first aggregate all $\Delta \widetilde{\omega}_{t}^{s_{m}, i}$ within $s_m$ to generate more homogeneous weight updates $\Delta\widetilde{\omega}_{t}^{s_{m}}$ of colleague model $s_m$ before the global aggregation: %In other words, following local training, the perturbed model update quantity, denoted as $\Delta \widetilde{\omega}{t}^{s{m},i}$ for client $i$ where $i\in s_{m}$, is uploaded to the super node for internal synchronization before server-level aggregation.
+% \begin{equation}
+%     \begin{gathered}
+%      \Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}
+%      = \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i},
+%      \end{gathered}
+% \end{equation}
+% where $p^{s_{m}, i}= {n^{s_{m}, i}}/{n^{s_{m}}}$ is aggregation coefficent, $n^{s_{m}}=\sum_{i \in s_{m}} n^{s_{m}, i}$.
+
+% \subsubsection{Global aggregation} 
+% Then, the server aggregates the learning results from all $s_m$ and updates the global model:
+% \begin{equation}
+% \widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}},
+% \end{equation}
+% where $p^{s_{m}}= \frac{n^{s_m}}{\sum_{s_{m} \in S} n^{s_m}}$, and $\widetilde{\omega}_{t}$ is the global model.
 The global aggregation iteratively executes $T$ rounds to complete the learning task $Job=(w,\mathcal{P}^{tar},t_0, T)$\footnote{The termination condition for the learning task can also be set based on accuracy $\epsilon^{\prime\prime}>0$ rather than a fixed number of rounds $T$, i.e., $\mathcal{L}_{FFL}(\omega_t)\leq \epsilon^{\prime\prime}$, by only modifying the quadruple to $(w,\mathcal{P}^{tar},t_0, \epsilon^{\prime\prime})$.}.
 
-\subsubsection{Peer community personalization} Finally, to further improve the performance on local datasets, we personalize the local model for peer community by adding the proximal term:
-\begin{equation}\label{eq:personal}
-\omega_{t}^{k} = \omega_{t-1}^{k} - \eta\left(\sum_{i=1}^{\vert\vert c_{k}\vert\vert}p^{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega_{t-1} \right)\right)
-\end{equation}
-    where $p^{c_k}= \frac{n^{s_m}}{\sum_{c_k \in C} \vert\vert c_k\vert\vert}$, $\eta$ is the learning rate, $\lambda$ is the regularization coefficient.
+% \subsubsection{Peer community personalization} Finally, to further improve the performance on local datasets, we personalize the local model for peer community by adding the proximal term:
+% \begin{equation}\label{eq:personal}
+% \omega_{t}^{k} = \omega_{t-1}^{k} - \eta\left(\sum_{i=1}^{\vert\vert c_{k}\vert\vert}p^{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega_{t-1} \right)\right)
+% \end{equation}
+%     where $p^{c_k}= \frac{n^{s_m}}{\sum_{c_k \in C} \vert\vert c_k\vert\vert}$, $\eta$ is the learning rate, $\lambda$ is the regularization coefficient.
 The smaller $\lambda$, the more the local models $\omega_t^{k}$ can deviate from the (corrupted) global model $\omega_t$, achieving robustness at the expense of generalization \cite{li2021ditto}.
 
-In Algorithm \ref{algorithm1}, we present the pseudocode for the complete adaptive training process described above.
+% In Algorithm \ref{algorithm1}, we present the pseudocode for the complete adaptive training process described above.
 It is evident from the algorithm that our approach only requires participants to provide distribution information, enabling significant improvements in efficiency, accuracy, and privacy in heterogeneous environments.
@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{figures/fig3.PNG}
-\caption{The workflow of MR-FFL.}
-\label{fig3:workflow}
-\end{figure}
-
-\subsection{Analysis of privacy amplification}
-
-Different from existing central differential privacy (CDP) or local differential privacy (LDP) methods, which inevitably introduce excessive large noise and thus deteriorate the learning performance in heterogeneous environments, inspired by \cite{liu2022privacy}, we propose a novel DP notion: \textit{community-specific differential privacy} (CSDP) for heterogeneous federated learning.
+% % \begin{figure}[!t]
+% % \centering
+% % \includegraphics[width=\linewidth]{figures/fig3.PNG}
+% % \caption{The workflow of MR-FFL.}
+% % \label{fig3:workflow}
+% % \end{figure}
+
+% \subsection{Analysis of privacy amplification}
+
+% Different from existing central differential privacy (CDP) or local differential privacy (LDP) methods, which inevitably introduce excessive large noise and thus deteriorate the learning performance in heterogeneous environments, inspired by \cite{liu2022privacy}, we propose a novel DP notion: \textit{community-specific differential privacy} (CSDP) for heterogeneous federated learning.
 The anonymity is achieved within a peer community instead of the whole UAV network, which significantly reduces privacy loss under the same DP guarantee.
@@
 
-\subsubsection{Noise calculation} We first calculate the noise scale needed for the MR-FFL workflow to achieve our $(\varepsilon_k,\delta_k)$-CSDP.
+% \subsubsection{Noise calculation} We first calculate the noise scale needed for the MR-FFL workflow to achieve our $(\varepsilon_k,\delta_k)$-CSDP.
 Assume a pair of neighbor datasets $\mathcal{D}^{s_{m}, i}_{t}$ and $\mathcal{D}^{s_{m}, i'}_{t}$ sampled from same $s_m$ with size $n^{s_{m}, i}$, there is only one pair of nonidentical samples $\xi^{i}_{t}$ and $\xi^{i\prime}_{t}$ within the neighbor datasets.
@@
 
-\begin{equation}
-     \begin{aligned}
-    \Delta F&=\max _{\xi^{i}_{t},\xi^{i\prime}_{t}}\left\|F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i}_{t}\right) -F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i'}_{t}\right)\right\|\\
-    &\leq \frac{n^{s_{m},i}}{n^{s_{m}} M}\left(  \max \left\| \Delta\omega_{r,t}^{s_{m},i}\right\|   + \max  \left\| \Delta\omega_{r,t}^{s_{m},i}\right\| \right)
-     \end{aligned}
-\end{equation}
-
-The second inequality can be deduced through a similar analysis as in \cite{wei2020federated-NbAFL}. We omit the specific process for simplicity. 
-After DP weights clipping \cite{abadi2016deep}, assuming an equal volume of data for clients and a minimum node count $L$ ($L\geq r$) within the colleague community, we have the best sensitivity as:
-\begin{equation}
-    Sen_k=\max _{i \in c_{k}}\left\{\Delta f\right\} \leq \frac{2 E_{k}}{L M},
-    \end{equation}
- where $E_k$ is the clipping bound of $c_k$.
-The standard deviation of the Gaussian noise to achieve $(\varepsilon_k,\delta_k)$-CSDP is:
-\begin{equation}
-    \sigma_{k}=\frac{\ell_{k} Sen_k }{\varepsilon_{k}}=\frac{2 \ell_{k} E_{k}}{L M\varepsilon_{k}},
-    \end{equation}
-where constant $\ell_{k} =\sqrt{2 \ln (1.25 / \delta_{k})}$ \cite{dwork2014algorithmic}.
-
-\subsubsection{Privacy analysis}
-
-%我们假设客户的类别分布$\mathcal{P}^{c_{k}}$符合高斯分布$\varphi_{c_{k}} $，即客户类别以方差$\sigma_{c_{k}}^{2}$正态分布在簇心$\mu_{c_{k}}$周围，即簇$c_{k}$的类别分布可以用$\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$的高斯分布表示。
-We assume that the data distribution of the UAV clients, denoted as $\mathcal{P}^{c_{k}}$, follows a Gaussian distribution $\varphi_{c_{k}}$, where the data are normally distributed around the community center $\mu_{c_{k}}$ with a variance of $\sigma_{c_{k}}^{2}$.
+% \begin{equation}
+%      \begin{aligned}
+%     \Delta F&=\max _{\xi^{i}_{t},\xi^{i\prime}_{t}}\left\|F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i}_{t}\right) -F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i'}_{t}\right)\right\|\\
+%     &\leq \frac{n^{s_{m},i}}{n^{s_{m}} M}\left(  \max \left\| \Delta\omega_{r,t}^{s_{m},i}\right\|   + \max  \left\| \Delta\omega_{r,t}^{s_{m},i}\right\| \right)
+%      \end{aligned}
+% \end{equation}
+
+% The second inequality can be deduced through a similar analysis as in \cite{wei2020federated-NbAFL}. We omit the specific process for simplicity. 
+% After DP weights clipping \cite{abadi2016deep}, assuming an equal volume of data for clients and a minimum node count $L$ ($L\geq r$) within the colleague community, we have the best sensitivity as:
+% \begin{equation}
+%     Sen_k=\max _{i \in c_{k}}\left\{\Delta f\right\} \leq \frac{2 E_{k}}{L M},
+%     \end{equation}
+%  where $E_k$ is the clipping bound of $c_k$.
+% The standard deviation of the Gaussian noise to achieve $(\varepsilon_k,\delta_k)$-CSDP is:
+% \begin{equation}
+%     \sigma_{k}=\frac{\ell_{k} Sen_k }{\varepsilon_{k}}=\frac{2 \ell_{k} E_{k}}{L M\varepsilon_{k}},
+%     \end{equation}
+% where constant $\ell_{k} =\sqrt{2 \ln (1.25 / \delta_{k})}$ \cite{dwork2014algorithmic}.
+
+% \subsubsection{Privacy analysis}
+
+% %我们假设客户的类别分布$\mathcal{P}^{c_{k}}$符合高斯分布$\varphi_{c_{k}} $，即客户类别以方差$\sigma_{c_{k}}^{2}$正态分布在簇心$\mu_{c_{k}}$周围，即簇$c_{k}$的类别分布可以用$\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$的高斯分布表示。
+% We assume that the data distribution of the UAV clients, denoted as $\mathcal{P}^{c_{k}}$, follows a Gaussian distribution $\varphi_{c_{k}}$, where the data are normally distributed around the community center $\mu_{c_{k}}$ with a variance of $\sigma_{c_{k}}^{2}$.
 In other words, the data distribution of community $c_{k}$ can be represented by a distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$ \cite{wei2020federated-NbAFL}.
-%对于某一簇$c_{i}$,整体类别分布符合高斯分布$\varphi_{c_{i}} \sim \mathcal{N}\left(\mu_{c_{i}}, \sigma_{c_i}^{2}\right)$，从中随机抽取任意客户$\forall i,i'\in c_{i}$，客户类别分布也符合$\varphi_{c_{i}}$。
-For a specific peer community $c_{k}$, the overall data distribution follows distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_i}^{2}\right)$.
+% %对于某一簇$c_{i}$,整体类别分布符合高斯分布$\varphi_{c_{i}} \sim \mathcal{N}\left(\mu_{c_{i}}, \sigma_{c_i}^{2}\right)$，从中随机抽取任意客户$\forall i,i'\in c_{i}$，客户类别分布也符合$\varphi_{c_{i}}$。
+% For a specific peer community $c_{k}$, the overall data distribution follows distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_i}^{2}\right)$.
 Hence, selecting any UAV client $\forall i,i'\in c_{k}$ from it, the client's distribution also follows $\varphi_{c_{k}}$ \cite{wei2021low}.
 
-%由公式（9）可知，在本地训练中，客户最小化本地经验风险得到的梯度与客户的本地数据有关，且客户梯度间的最大距离与数据分布的分散程度正相关，可以得到簇$c_{i}$客户梯度间的最大距离：
-As indicated by \cite{sattler2020clustered-CFL}, it is evident that in local training, the gradient obtained by a client, which minimizes the local empirical risk, is related to the client's local data.
+% %由公式（9）可知，在本地训练中，客户最小化本地经验风险得到的梯度与客户的本地数据有关，且客户梯度间的最大距离与数据分布的分散程度正相关，可以得到簇$c_{i}$客户梯度间的最大距离：
+% As indicated by \cite{sattler2020clustered-CFL}, it is evident that in local training, the gradient obtained by a client, which minimizes the local empirical risk, is related to the client's local data.
 The maximum distance between client gradients is positively correlated with the dispersion of the distribution.
@@
 
-%super node按照数量$n=[n_{1},\ldots,n_{k},\ldots,n_{K}],  n_{k} \in \mathbb{N}$从簇$\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中选择$L$个客户:$\sum^{K}_{k=1} n_{k}=L$。通过卷积求和上述簇分布，可以得到super node 的类别分布$\varphi_{s}$：
-We choose UAV nodes from each peer communities $c_{k},\forall c_k \in C$ to constitute colleague communities according to composition vector $\textbf{h}=[h_{1},\ldots,h_{k},\ldots,h_{K}],  h_{k} \in \mathbb{N}$.
+% %super node按照数量$n=[n_{1},\ldots,n_{k},\ldots,n_{K}],  n_{k} \in \mathbb{N}$从簇$\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中选择$L$个客户:$\sum^{K}_{k=1} n_{k}=L$。通过卷积求和上述簇分布，可以得到super node 的类别分布$\varphi_{s}$：
+% We choose UAV nodes from each peer communities $c_{k},\forall c_k \in C$ to constitute colleague communities according to composition vector $\textbf{h}=[h_{1},\ldots,h_{k},\ldots,h_{K}],  h_{k} \in \mathbb{N}$.
 Hence, by convolution summation among those peer distributions, we can obtain the distribution of colleague communities $\varphi_{s}$ as:
 
-\begin{equation}    \varphi_{s}=h_{1}\varphi_{c_{1}}\oplus\ldots\oplus h_{k}\varphi_{c_{k}}\oplus\ldots\oplus h_{K}\varphi_{c_{K}}
-\end{equation}
-
-%因为簇分布$\varphi_{c_{k}} \forall c_{k} \in C$是相互独立的高斯分布，可以得到上述簇分布的卷积和。
-As $\varphi_{c_{k}}, \forall c_{k} \in C$ are i.i.d.
+% \begin{equation}    \varphi_{s}=h_{1}\varphi_{c_{1}}\oplus\ldots\oplus h_{k}\varphi_{c_{k}}\oplus\ldots\oplus h_{K}\varphi_{c_{K}}
+% \end{equation}
+
+% %因为簇分布$\varphi_{c_{k}} \forall c_{k} \in C$是相互独立的高斯分布，可以得到上述簇分布的卷积和。
+% As $\varphi_{c_{k}}, \forall c_{k} \in C$ are i.i.d.
 Gaussian distributions, we have $\varphi_{s} \sim \mathcal{N}\left(\mu_{s}, \sigma_{s}^{2}\right)$, where $\mu_{s}=\sum_{k}^{K} h_{k} \mu_{c_{k}}$, $\sigma_{s}^{2}=\sum_{k}^{K} h_{k}^{2} \sigma_{c_k}^{2}$.
-Define the maximum distance between weight updates of two UAV nodes $U_i$ and $U_{i^{\prime}}$ from the same colleague community $s$ as $\max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\| \simeq \sigma_{s}$.
+% Define the maximum distance between weight updates of two UAV nodes $U_i$ and $U_{i^{\prime}}$ from the same colleague community $s$ as $\max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\| \simeq \sigma_{s}$.
 As $\sigma_{s}=\sqrt{\sum_{k}^{K} h_{k}^{2} \sigma_{c_k}^{2}}$, easy to prove $\sigma_{s}\geq\sigma_{c_{k}}, \forall c_k \in C$.
-Then, we have:
-\begin{equation}
-    \max_{i,i'\in c_{i}} \left\| \Delta\omega_{t}^{c_{i},i}-\Delta\omega_{t}^{c_{i},i'}\right\|\leq \max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\|.
-\end{equation}
-
-%根据敏感度的定义，可知在super node 中计算supernode内的敏感度将远大于簇内的敏感度。
-According to the definition of sensitivity, our peer community-specific $Sen_k$ and noise scale is much smaller than existing global-wide or colleague-wide DP methods.
+% Then, we have:
+% \begin{equation}
+%     \max_{i,i'\in c_{i}} \left\| \Delta\omega_{t}^{c_{i},i}-\Delta\omega_{t}^{c_{i},i'}\right\|\leq \max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\|.
+% \end{equation}
+
+% %根据敏感度的定义，可知在super node 中计算supernode内的敏感度将远大于簇内的敏感度。
+% According to the definition of sensitivity, our peer community-specific $Sen_k$ and noise scale is much smaller than existing global-wide or colleague-wide DP methods.
 Hence, to achieve the same FFL performance, the clipping bound of our method is also much smaller, which requires less obfuscation.
 
-\begin{comment}
-
-\subsection{Analysis of personalization}
-在$K$个簇$C=\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中，每个簇$c_{k}$有相同的客户数$n$。$X^k \triangleq\left\{\omega^{k, i} \in\right.\mathbb{t}\}_{i \in[n]}$，且客户模型以方差$\upsilon^{2}$正态分布在簇心$\omega^{k}$周围，即$\omega^{k, i}=\omega^{k}+z^{k, i}$,其中$z^{k, i} \sim \mathcal{N}\left(0, \upsilon^{2}\right)$。具体来说，为了量化簇的异质性，我们假设簇心$\{\omega^{k}\}_{k \in \left[K\right]}$也以方差$\tau^{2}$正态分布在未知的固定元中心$\theta$周围,即$\omega^{k}=\theta+z^{k}$,其中$z^{k} \sim \mathcal{N}\left(0, \tau^{2}\right)$。其中，$\tau$表示簇心间的分散程度，$\tau$越大，簇越分散，整体分布的异构性越高。在此基础上，簇$c_{k}$为其中客户选择隐私预算$(\varepsilon_{k},\delta_{k})-DP$以最小化整体的泛化误差。每个簇$k$具有不同的裁剪边界$C_{k}$，并以$\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$的标准差在本地客户上传的模型加噪,在此基础上，簇$c_{k}$的优化目标可以表示为：
-\begin{equation}
-h_k(\omega)=\tilde{F}_k(\omega)+\frac{\lambda}{2}\|\omega-\omega^{g}\|_2^2
-\end{equation}
-其中，$\tilde{F}_k(\omega) \triangleq \frac{1}{2}\left(\omega-\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i} \cdot \min \left(1, C_{k} /\left\|\omega^{k, i}\right\|_2\right)\right)\right)^2$是簇$c_{k}$的优化目标，簇$c_{k}$客户梯度加噪大小为$\xi^k \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$。由于数据是亚高斯的，我们可以选择裁剪的边界$C_{k}$避免引入削波误差。因此，簇$c_{k}$的最优本地优化结果为$\widehat{\omega}^k \triangleq \operatorname{argmin} \tilde{F}_k(w)=\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i}\right)$。由于服务器聚合全部参与客户的模型而客户分布在各簇中，因此可得$\omega^{g}=\frac{1}{Kn} \sum_{k=1}^{K}\left(\xi^k+\sum_{i=1}^{n}\omega^{k,i}\right)=\frac{1}{K}\sum_{k=1}^{K}\widehat{\omega}^{k}$。由此可得簇$c_{k}$外各簇的平均估计结果$\widehat{\omega}^{\backslash k}=\frac{1}{K-1}\sum_{j \neq k}\widehat{\omega}^{j}$。
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{algorithm}[!t]% !t top !b bottom !h right here !p float pages
-\caption{Adaptive training with privacy amplification}
-\label{algorithm1}
-	\begin{algorithmic} [1]
-    \State \textit{\textbf{ Input: }Learning task $Job\triangleq(w^0,\mathcal{P}^{tar},t_0, T)$; Maximum
-local training iterations $R$; all participant UAV nodes $\mathbf{U}$ and their local dataset $\mathcal{D}_i$.}
-    \State \textit{\textbf{Output: }The global FFL model $\omega$ for task $Job$, personalized local models $\{ \omega^{k}\}_{k \in [K]}$} for peer communities.
-            \State \textbf{Initialize:} $w^{0}_{i} \leftarrow\ w^{0}$%,$\mathcal{P}^{real}=\operatorname{norm}\left(\sum_{i \in B} N^{i} \mathcal{P}^{i} \right)$
-            %\State {\color{CadetBlue}/* \textbf{Peer community construction */} } 
-            %\State $d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}$
-            %\State $C=\{ c_{1}, \ldots , c_{K} \} \leftarrow \arg \min _{c_{1} \cup c_{2} \cup \ldots c_{K}=C}\left(\max _{\forall c_{k},c_{k'} \in C ,i \in c_{k}, j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .$
-            \State Construct $C=\{ c_{1}, \ldots , c_{K} \}$ with Eq. (\ref{eq:peer-construct});
-             %\For { $r \in 1, \cdots, R$}
-                %\State{\color{CadetBlue} /* \textbf{Initialization} */} %$S \leftarrow Select-Clients()$}
-            \State Calculate composition vector $\mathbf{h}$ by Eq. (\ref{eq:problem}) for $Job$;
-            \State Construct colleague communities as $S^t=\{s_{1}, \ldots , s_{M}\}$ according to template $\mathbf{h}$;
-                \For {each colleague community $s_{m}$ in $S^{t}$ in parallel }
-                    \For {each UAV node $U_i$ in $s_{m}$ in parallel}
-                        \State {\color{CadetBlue}/*\textbf{Local Training*/}} 
-                        %\State $\omega_{t}^{s_{m},i} \leftarrow \omega_{t-1}^{s_{m},i}-\frac{\eta}{NI^{s_{m},i}} \nabla_\omega \mathcal{L}_{s_{m},i}\left(\omega_{t-1}^{s_{m},i}, \mathcal{D}^{s_{m},i}_{t}\right)$
-                        \State Update $\omega_{t}^{s_{m},i}$ with $\mathcal{D}_i$ for $R$ iterations;
-                        \State $\Delta \omega_{t}^{s_{m},i}=\omega_{t-1}^{s_{m},i}-\omega_{t}^{s_{m},i}$;
-                        \State{\color{CadetBlue}/* \textbf{Privacy obfuscation */}} 
-                        %\State \textbf{DP:} client $i \in c_{k}$, guarantee ($\varepsilon_{k}$,$\delta_{k}$)-DP
-                        \State Calculate noise $z^{k} \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$, $\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$;
-                        \State $\Delta \widetilde{\omega}_{t}^{s_{m},i}=\Delta \omega_{t}^{s_{m},i}+z^{k}$;
-                    \EndFor
-                    \State{\color{CadetBlue}/* \textbf{Colleague community aggregation */}} 
-                    \State $\widetilde{\omega}_{t}^{s_{m}} \leftarrow \widetilde{\omega}_{t-1}^{s_{m}} -  \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i}$;
-                    \State $\Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}$;
-                \EndFor
-                \State {\color{CadetBlue}/* \textbf{Global aggregation */}}
-                \State $\widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$;%$\widetilde{\omega}_{t} \leftarrow \widetilde{\omega}_{t-1} - PI^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$
-                \State{\color{CadetBlue}/* \textbf{Peer community personalization */}}
-                    \State Update the personalized model $\omega_{t}^{k}$ for each peer community $c_k$ with Eq.
+% \begin{comment}
+
+% \subsection{Analysis of personalization}
+% 在$K$个簇$C=\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中，每个簇$c_{k}$有相同的客户数$n$。$X^k \triangleq\left\{\omega^{k, i} \in\right.\mathbb{t}\}_{i \in[n]}$，且客户模型以方差$\upsilon^{2}$正态分布在簇心$\omega^{k}$周围，即$\omega^{k, i}=\omega^{k}+z^{k, i}$,其中$z^{k, i} \sim \mathcal{N}\left(0, \upsilon^{2}\right)$。具体来说，为了量化簇的异质性，我们假设簇心$\{\omega^{k}\}_{k \in \left[K\right]}$也以方差$\tau^{2}$正态分布在未知的固定元中心$\theta$周围,即$\omega^{k}=\theta+z^{k}$,其中$z^{k} \sim \mathcal{N}\left(0, \tau^{2}\right)$。其中，$\tau$表示簇心间的分散程度，$\tau$越大，簇越分散，整体分布的异构性越高。在此基础上，簇$c_{k}$为其中客户选择隐私预算$(\varepsilon_{k},\delta_{k})-DP$以最小化整体的泛化误差。每个簇$k$具有不同的裁剪边界$C_{k}$，并以$\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$的标准差在本地客户上传的模型加噪,在此基础上，簇$c_{k}$的优化目标可以表示为：
+% \begin{equation}
+% h_k(\omega)=\tilde{F}_k(\omega)+\frac{\lambda}{2}\|\omega-\omega^{g}\|_2^2
+% \end{equation}
+% 其中，$\tilde{F}_k(\omega) \triangleq \frac{1}{2}\left(\omega-\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i} \cdot \min \left(1, C_{k} /\left\|\omega^{k, i}\right\|_2\right)\right)\right)^2$是簇$c_{k}$的优化目标，簇$c_{k}$客户梯度加噪大小为$\xi^k \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$。由于数据是亚高斯的，我们可以选择裁剪的边界$C_{k}$避免引入削波误差。因此，簇$c_{k}$的最优本地优化结果为$\widehat{\omega}^k \triangleq \operatorname{argmin} \tilde{F}_k(w)=\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i}\right)$。由于服务器聚合全部参与客户的模型而客户分布在各簇中，因此可得$\omega^{g}=\frac{1}{Kn} \sum_{k=1}^{K}\left(\xi^k+\sum_{i=1}^{n}\omega^{k,i}\right)=\frac{1}{K}\sum_{k=1}^{K}\widehat{\omega}^{k}$。由此可得簇$c_{k}$外各簇的平均估计结果$\widehat{\omega}^{\backslash k}=\frac{1}{K-1}\sum_{j \neq k}\widehat{\omega}^{j}$。
+% \end{comment}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{algorithm}[!t]% !t top !b bottom !h right here !p float pages
+% \caption{Adaptive training with privacy amplification}
+% \label{algorithm1}
+% 	\begin{algorithmic} [1]
+%     \State \textit{\textbf{ Input: }Learning task $Job\triangleq(w^0,\mathcal{P}^{tar},t_0, T)$; Maximum
+% local training iterations $R$; all participant UAV nodes $\mathbf{U}$ and their local dataset $\mathcal{D}_i$.}
+%     \State \textit{\textbf{Output: }The global FFL model $\omega$ for task $Job$, personalized local models $\{ \omega^{k}\}_{k \in [K]}$} for peer communities.
+%             \State \textbf{Initialize:} $w^{0}_{i} \leftarrow\ w^{0}$%,$\mathcal{P}^{real}=\operatorname{norm}\left(\sum_{i \in B} N^{i} \mathcal{P}^{i} \right)$
+%             %\State {\color{CadetBlue}/* \textbf{Peer community construction */} } 
+%             %\State $d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}$
+%             %\State $C=\{ c_{1}, \ldots , c_{K} \} \leftarrow \arg \min _{c_{1} \cup c_{2} \cup \ldots c_{K}=C}\left(\max _{\forall c_{k},c_{k'} \in C ,i \in c_{k}, j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .$
+%             \State Construct $C=\{ c_{1}, \ldots , c_{K} \}$ with Eq. (\ref{eq:peer-construct});
+%              %\For { $r \in 1, \cdots, R$}
+%                 %\State{\color{CadetBlue} /* \textbf{Initialization} */} %$S \leftarrow Select-Clients()$}
+%             \State Calculate composition vector $\mathbf{h}$ by Eq. (\ref{eq:problem}) for $Job$;
+%             \State Construct colleague communities as $S^t=\{s_{1}, \ldots , s_{M}\}$ according to template $\mathbf{h}$;
+%                 \For {each colleague community $s_{m}$ in $S^{t}$ in parallel }
+%                     \For {each UAV node $U_i$ in $s_{m}$ in parallel}
+%                         \State {\color{CadetBlue}/*\textbf{Local Training*/}} 
+%                         %\State $\omega_{t}^{s_{m},i} \leftarrow \omega_{t-1}^{s_{m},i}-\frac{\eta}{NI^{s_{m},i}} \nabla_\omega \mathcal{L}_{s_{m},i}\left(\omega_{t-1}^{s_{m},i}, \mathcal{D}^{s_{m},i}_{t}\right)$
+%                         \State Update $\omega_{t}^{s_{m},i}$ with $\mathcal{D}_i$ for $R$ iterations;
+%                         \State $\Delta \omega_{t}^{s_{m},i}=\omega_{t-1}^{s_{m},i}-\omega_{t}^{s_{m},i}$;
+%                         \State{\color{CadetBlue}/* \textbf{Privacy obfuscation */}} 
+%                         %\State \textbf{DP:} client $i \in c_{k}$, guarantee ($\varepsilon_{k}$,$\delta_{k}$)-DP
+%                         \State Calculate noise $z^{k} \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$, $\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$;
+%                         \State $\Delta \widetilde{\omega}_{t}^{s_{m},i}=\Delta \omega_{t}^{s_{m},i}+z^{k}$;
+%                     \EndFor
+%                     \State{\color{CadetBlue}/* \textbf{Colleague community aggregation */}} 
+%                     \State $\widetilde{\omega}_{t}^{s_{m}} \leftarrow \widetilde{\omega}_{t-1}^{s_{m}} -  \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i}$;
+%                     \State $\Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}$;
+%                 \EndFor
+%                 \State {\color{CadetBlue}/* \textbf{Global aggregation */}}
+%                 \State $\widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$;%$\widetilde{\omega}_{t} \leftarrow \widetilde{\omega}_{t-1} - PI^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$
+%                 \State{\color{CadetBlue}/* \textbf{Peer community personalization */}}
+%                     \State Update the personalized model $\omega_{t}^{k}$ for each peer community $c_k$ with Eq.
 (\ref{eq:personal});%$\omega_{t}^{k} \leftarrow \omega_{t-1}^{k} - \eta_{c_{k}}\left(\sum_{i=1}^{n_{c_{k}}}p_{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega^{g}_{t-1} \right)\right)$
-                    %\State Update $\omega_{t}^{k}$
+%                     %\State Update $\omega_{t}^{k}$
+%             % \EndFor
+% \State \Return $w^g,\{w^k\}$
+% \end{algorithmic}
+% \end{algorithm}
+
+% \begin{algorithm}
+% \caption{Single}
+% \label{alg:malicious-node-detection-history}
+% \begin{algorithmic}[1]
+% \State \textit{\textbf{Input:} Global model $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical updates for each nodes $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$, threshold $\varepsilon$.}
+% \State \textit{\textbf{Output:} Sets of normal/malicious nodes $U_{nor}$ and $U_{mal}$.}
+
+% \State {\color{CadetBlue}/*\textbf{Step 1: historical database construction*/}}
+% \For {Client $i \in $}
+%     \State Record flattened gradients $\bar{\theta_i^t}$ and models $\theta_g^{t-1};$
+%     \State Establish a ray with Eq. () for each of the $t'$ most recent gradients, $t' = \max\{t-T+1, 1\}, \ldots, t$;
 % \EndFor
-\State \Return $w^g,\{w^k\}$
-\end{algorithmic}
-\end{algorithm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Community-based credit evaluation of UAV nodes}
-In this section, we design a community-based credit evaluation method with a modified three-valued subjective logic model (SLM) \cite{al2021subjective}, to eliminate malicious attackers hiding in heterogeneous UAV networks.
+
+% \State \textbf{Step 2: Obtain the Purpose Intention}
+% \For {Client $i$}
+%     \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
+%     \While {Not Converged}
+%         \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
+%     \EndWhile
+%     \State Calculate confidence $cre_i = \frac{1}{r_i + \rho}$
+% \EndFor
+
+% \State \textbf{Step 3: Abnormal Detection}
+% \For {Client $i$}
+%     \For {Each point $O_j \neq O_i$}
+%         \State Calculate distance $\|O_i - O_j\|$
+%     \EndFor
+%     \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
+%     \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
+%     \State Compute reachability distance $rea_{i,j} = \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$
+%     \State Calculate local reachability density $lrd_i = \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$
+% \EndFor
+% % \For {Client $i$}
+% %     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
+% %     \If {$lof_i > 1$}
+% %         \State Mark client $i$ as malicious, add to $U_{mal}$
+% %     \Else
+% %         \State Mark client $i$ as normal, add to $U_{nor}$
+% %     \EndIf
+% % \EndFor
+% \State Calculate $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$ for each client $i$
+% % \State $U_{mal} = \{i \,|\, lof_i > 1\}$
+% % \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
+% \State $U_{mal}, U_{nor} = \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$
+
+% \State \textbf{Step 4: Gradients Aggregation}
+% \For {Client $i\in U_{nor}$}
+%         \State Compute adjusted confidence $cre_i' = \tanh(cre_i)$
+%         \State Normalize weights $w_i = \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$
+% \EndFor
+
+% \State \textbf{Output:} Aggregated global model update $\theta_g^t = \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$
+% \end{algorithmic}
+% \end{algorithm}
+
+% \begin{algorithm}
+% \caption{Malicious Node Detection via DCT}
+% \label{alg:malicious-node-detection}
+% \begin{algorithmic}[1]
+% \State \textbf{Input:} $d$, $n$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$, $m$ \Comment{$d$ is the dimension of each node update; $n$ is the number of the nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$is the local updates from nodes during the $t$-th round; $m$ is the length of low-frequency components}
+% \State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
+
+% \State Step 1: Frequency Domain Transformation
+% \For {Node $R_i$}
+%     \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
+%     \State $G_i^t = Trunc(DCT(\bar{\theta_i^t}), m)$ \Comment{Compute DCT and retain only the top $m$ low-frequency components}
+% \EndFor
+
+% \State
+
+% \State Step 2: Clean Ingredient Extraction
+% \State $H^t \gets (G_0^t, G_1^t, \ldots, G_{n}^t) \in \mathbb{R}^{d \times m}$ \Comment{Stacking to form Matrix $H^t$.}
+
+% \State $\hat{H}^t \gets (H^t)^{T} H^t$
+% \State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
+% \State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
+
+% \State
+
+% \State Step 3: Kullback-Leibler Divergence Calculation
+% \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
+% \For {Node $R_i$}
+%     \State $Ki \gets \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)$
+% \EndFor
+% \State $S \gets \{KL_1, KL_2, \ldots, KL_n\}$ \Comment{The distribution differences calculated by KL divergence.}
+
+% \State
+
+% \State Step 4: Malicious Node Detection
+% \State $\{C_1, C_2, \ldots, C_K\} \gets \text{HDBSCAN}(S)$
+% \State $U_{nor} \gets C_{\text{max}}$, $U_{mal} \gets \{C_i \, | \, i \neq \text{max}\}$
+
+% \end{algorithmic}
+% \end{algorithm}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \section{Community-based credit evaluation of UAV nodes}
+% In this section, we design a community-based credit evaluation method with a modified three-valued subjective logic model (SLM) \cite{al2021subjective}, to eliminate malicious attackers hiding in heterogeneous UAV networks.
 By integrating credits from both similarity-dominated intra-community (peer) and performance-dominated inter-community (colleague), multiple poisoning paradigms can be efficiently thwarted.
-\subsection{Similarity-dominated peer credit evaluation}
-%首先，同一community内的用户在训练过程中上传的weights往往相似性较高。因此，通过社区内相似度比较，可以快速识别出离群的恶意用户。
-UAV nodes' weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ within the same peer community $c_k$ often exhibit a high degree of similarity during the training process.
+% \subsection{Similarity-dominated peer credit evaluation}
+% %首先，同一community内的用户在训练过程中上传的weights往往相似性较高。因此，通过社区内相似度比较，可以快速识别出离群的恶意用户。
+% UAV nodes' weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ within the same peer community $c_k$ often exhibit a high degree of similarity during the training process.
 Therefore, by leveraging community-based similarity, one can promptly identify malicious nodes that deviate significantly from the average norm.
 
-\subsubsection{Basic setting}
-For $\forall U_i \in c_k$, we first calculate the cosine similarity $\alpha_{c,i}^{t} \in [-1,1]$ between weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ from $U_i$ and average weight updates $\Delta\widetilde{\omega}^{c_k}_{t}$ from its peer community $c_k$:
-\begin{equation}
-    	  \alpha^{c_k,i}_{t} = \alpha( \Delta\widetilde{\omega}^{c_k}_{t-1}, \Delta\widetilde{\omega}^{i}_{t}) = \frac{\langle \Delta\widetilde{\omega}^{c_k}_{t-1},\Delta\widetilde{\omega}^{i}_{t}\rangle}{\Vert \Delta\widetilde{\omega}^{c_k}_{t-1}\Vert\cdot\Vert \Delta\widetilde{\omega}^{i}_{t}\Vert },\forall c_k \cap S.
-\end{equation}
-
-We further define the positive interaction $p^{c \rightarrow i}_{t} \in [0,2]$ as:
-\begin{equation}
-    	 PI^{c_k \rightarrow i}_{t} = \alpha^{c_k,i}_{t} -(-1),
-\end{equation}
-and the negative interaction $n^{c_k \rightarrow i}_{t} \in [0,2]$ as:
-\begin{equation}
-    	 NI^{c_k \rightarrow i}_{t} = 1-\alpha^{c_k,j}_{t}.
-\end{equation}
-
-%在FL的过程中，客户与簇的交互作用影响客户的信誉评估。诚实的交互行为将为客户的信誉评估带来正向的影响，具有攻击性的或不诚实的交互则会降低客户的信誉评分。我们分别用系数$b$和$c$表示内客户间正负交互作用对信任评价的影响比例，其中，$b>0,c>0$ 且 $b+c=1$。为了惩罚恶意客户，我们为客户间的负面交互设置更大的权重,即$b>c$。
-During the FFL process, benign behaviors positively impact the reputation assessment, while aggressive or deceptive interactions diminish the client's reputation.
+% \subsubsection{Basic setting}
+% For $\forall U_i \in c_k$, we first calculate the cosine similarity $\alpha_{c,i}^{t} \in [-1,1]$ between weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ from $U_i$ and average weight updates $\Delta\widetilde{\omega}^{c_k}_{t}$ from its peer community $c_k$:
+% \begin{equation}
+%     	  \alpha^{c_k,i}_{t} = \alpha( \Delta\widetilde{\omega}^{c_k}_{t-1}, \Delta\widetilde{\omega}^{i}_{t}) = \frac{\langle \Delta\widetilde{\omega}^{c_k}_{t-1},\Delta\widetilde{\omega}^{i}_{t}\rangle}{\Vert \Delta\widetilde{\omega}^{c_k}_{t-1}\Vert\cdot\Vert \Delta\widetilde{\omega}^{i}_{t}\Vert },\forall c_k \cap S.
+% \end{equation}
+
+% We further define the positive interaction $p^{c \rightarrow i}_{t} \in [0,2]$ as:
+% \begin{equation}
+%     	 PI^{c_k \rightarrow i}_{t} = \alpha^{c_k,i}_{t} -(-1),
+% \end{equation}
+% and the negative interaction $n^{c_k \rightarrow i}_{t} \in [0,2]$ as:
+% \begin{equation}
+%     	 NI^{c_k \rightarrow i}_{t} = 1-\alpha^{c_k,j}_{t}.
+% \end{equation}
+
+% %在FL的过程中，客户与簇的交互作用影响客户的信誉评估。诚实的交互行为将为客户的信誉评估带来正向的影响，具有攻击性的或不诚实的交互则会降低客户的信誉评分。我们分别用系数$b$和$c$表示内客户间正负交互作用对信任评价的影响比例，其中，$b>0,c>0$ 且 $b+c=1$。为了惩罚恶意客户，我们为客户间的负面交互设置更大的权重,即$b>c$。
+% During the FFL process, benign behaviors positively impact the reputation assessment, while aggressive or deceptive interactions diminish the client's reputation.
 We use coefficients $b$ and $c$ to quantify the impact of positive/negative interactions in credit evaluation, respectively.
@@
 To penalize malicious UAV nodes, we assign a greater weight $b>c$ to negative interactions among clients.
-Hence, we obtain the temporary three-valued peer reputation opinion \cite{liu2019trust} vector $\Upsilon^{c_k \rightarrow i}_{t,temp}\triangleq \{b^{c_k \rightarrow i}_{t,temp}, d^{c_k \rightarrow i}_{t,temp}, u^{c_k \rightarrow i}_{t,temp}\}$ based on SLM as:
-\begin{equation}
-\Upsilon^{c_k \rightarrow i}_{t,temp}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{bPI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
-        d^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{cNI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
-        u^{c_k \rightarrow i}_{t,temp}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}},                
-    \end{array}
-\right.
-\end{equation}
-%$ \sigma_{c}$为簇c中满足$\varepsilon-DP$所加噪声的标准差，体现了根据客户上传加噪梯度计算可信度的不确定性，$ \sigma^{C}_{max}$和$\sigma^{C}_{min}$分别是所有簇$c\in C$中为满足$\varepsilon-DP$所添加的最大噪声和最小噪声。
-where the standard deviation $ \sigma_{c_k}$ of peer community $c_k$ depicts the uncertainty in the credit calculation based on the noisy $\Delta\widetilde{\omega}^{c_k}_{t}$ to achieve DP guarantee.
+% Hence, we obtain the temporary three-valued peer reputation opinion \cite{liu2019trust} vector $\Upsilon^{c_k \rightarrow i}_{t,temp}\triangleq \{b^{c_k \rightarrow i}_{t,temp}, d^{c_k \rightarrow i}_{t,temp}, u^{c_k \rightarrow i}_{t,temp}\}$ based on SLM as:
+% \begin{equation}
+% \Upsilon^{c_k \rightarrow i}_{t,temp}=
+% \left  \{
+%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
+%         b^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{bPI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
+%         d^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{cNI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
+%         u^{c_k \rightarrow i}_{t,temp}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}},                
+%     \end{array}
+% \right.
+% \end{equation}
+% %$ \sigma_{c}$为簇c中满足$\varepsilon-DP$所加噪声的标准差，体现了根据客户上传加噪梯度计算可信度的不确定性，$ \sigma^{C}_{max}$和$\sigma^{C}_{min}$分别是所有簇$c\in C$中为满足$\varepsilon-DP$所添加的最大噪声和最小噪声。
+% where the standard deviation $ \sigma_{c_k}$ of peer community $c_k$ depicts the uncertainty in the credit calculation based on the noisy $\Delta\widetilde{\omega}^{c_k}_{t}$ to achieve DP guarantee.
 $ \sigma_{max}=\max_{c_k \in C}{\sigma_{c_k}}, \sigma_{min}=\min{c_k \in C}{\sigma_{c_k}}$.
 %Furthermore, $ \sigma^{C}{max}$ and $ \sigma^{C}{min}$ denote the maximum and minimum noise added, respectively, among all clusters $c\in C$ to satisfy $\varepsilon-DP$.
-Besides, $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp}$ denote \textit{belief}, \textit{disbelief}, and \textit{uncertainty}, respectively.
+% Besides, $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp}$ denote \textit{belief}, \textit{disbelief}, and \textit{uncertainty}, respectively.
 We have $b^{c_k \rightarrow i}_{t,temp}+d^{c_k \rightarrow i}_{t,temp}+u^{c_k \rightarrow i}_{t,temp}=1$ and $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp} \in [0,1]$.
 
-Then $c_k$'s temporary credit evaluation towards UAV $U_i$ is:
-\begin{equation}
-\Phi^{c_k \rightarrow i}_{t}=b^{c_k \rightarrow i}_{t} + a u^{c_k \rightarrow i}_{t}, \forall c_k \cap S,
-\end{equation}
-%其中$a\in[0,1]$是信誉不确定影响程度的系数。基于上式，根据客户的信誉度可以更明显地区分出恶意客户，从而抑制客户间的负面交互。
-where $a\in[0,1]$ is a coefficient regulating the importance of uncertainty. 
-Based on the above equation, malicious clients can be distinctly distinguished via reputation scores, thereby mitigating negative interactions among clients.
-
-\subsubsection{Long-term consideration}
-%在r个同步轮次内，客户的信誉不总是一成不变的。由于客户的信誉随着时间的推移而变化，我们考虑客户间历史信誉的影响。定义信誉的时间衰减因子为：
-During the iterative training, clients' reputations may not remain constant.
+% Then $c_k$'s temporary credit evaluation towards UAV $U_i$ is:
+% \begin{equation}
+% \Phi^{c_k \rightarrow i}_{t}=b^{c_k \rightarrow i}_{t} + a u^{c_k \rightarrow i}_{t}, \forall c_k \cap S,
+% \end{equation}
+% %其中$a\in[0,1]$是信誉不确定影响程度的系数。基于上式，根据客户的信誉度可以更明显地区分出恶意客户，从而抑制客户间的负面交互。
+% where $a\in[0,1]$ is a coefficient regulating the importance of uncertainty. 
+% Based on the above equation, malicious clients can be distinctly distinguished via reputation scores, thereby mitigating negative interactions among clients.
+
+% \subsubsection{Long-term consideration}
+% %在r个同步轮次内，客户的信誉不总是一成不变的。由于客户的信誉随着时间的推移而变化，我们考虑客户间历史信誉的影响。定义信誉的时间衰减因子为：
+% During the iterative training, clients' reputations may not remain constant.
 Some sophisticated attackers even take advantage of this phenomenon and conduct more stealthy poisoning behaviors \cite{credit1-kang2019IOT}.
@@
 The time decay factor $v_{\tau}$ is defined as:
-\begin{equation}
-v_{\tau}=\frac{1}{e^{\iota(Y-\tau)}}=e^{-z(Y-\tau)},
-\end{equation}
-%其中$z>0$为冷却系数, $\tau \in [1,Y]$为历史交互时间的时隙,在内部通信中当前时隙$Y=r$。由于过于久远的信誉的时间衰减因子接近0，并且考虑到信誉交互中的内存与计算成本，我们只保留$\vert Y-\tau \vert \leq T$的历史信誉 ,即只记录并维护距离当前通信轮次的$T$轮历史信誉$\Phi^{c \rightarrow i}_{\tau}$。公式(7)表示，越接近当前同步轮次的信誉的时效性越高，即更相信近期交互的信誉度，而不是历史交互。
-where $\iota>0$ is the cooling coefficient, $\tau \in [1,Y]$ represents the time slot of historical interaction, and $Y$ in the current time slot of internal communication.
+% \begin{equation}
+% v_{\tau}=\frac{1}{e^{\iota(Y-\tau)}}=e^{-z(Y-\tau)},
+% \end{equation}
+% %其中$z>0$为冷却系数, $\tau \in [1,Y]$为历史交互时间的时隙,在内部通信中当前时隙$Y=r$。由于过于久远的信誉的时间衰减因子接近0，并且考虑到信誉交互中的内存与计算成本，我们只保留$\vert Y-\tau \vert \leq T$的历史信誉 ,即只记录并维护距离当前通信轮次的$T$轮历史信誉$\Phi^{c \rightarrow i}_{\tau}$。公式(7)表示，越接近当前同步轮次的信誉的时效性越高，即更相信近期交互的信誉度，而不是历史交互。
+% where $\iota>0$ is the cooling coefficient, $\tau \in [1,Y]$ represents the time slot of historical interaction, and $Y$ in the current time slot of internal communication.
 Since the time decay factor for too-old reputations approaches 0, and considering the memory and computational costs in reputation interactions, we set an expiration threshold and retain only $T$ historical reputations $\Phi^{c_ \rightarrow i}_{\tau}$, i.e., $\vert Y-\tau \vert \leq T$.
@@
 
-\subsubsection{Stability consideration} 
-%\item \textbf{更新：}在联合学习的迭代交互$r\in[1,R]$中，服务器选择参与本地训练的随机客户子集为$Set_{t}$,在第$r$轮迭代中，只有集合$Set_{t}$中的客户上传模型更新量并彼此交互评估信誉。然而，由于参与训练和客户数量远少于客户总数,即$\vert Set_{t}\vert \ll N$，当前轮次的评估结果不足以给出完整的评估结果。因此，我们使用每个客户端的最新信誉更新值来更新其当前信誉值。设$\left\{ \Phi^{c \rightarrow i}_{t} \right\}_{i}^N$表示在服务器上维护的每个客户的簇内直接信誉。在每一轮交互后，全部客户执行以下更新操作：
-Moreover, as only chosen UAV nodes $U_i\in S$ participate in the FFL at round $t$, cross-slot reputation values can have erratic fluctuation or asynchronous obsolescence problems.
+% \subsubsection{Stability consideration} 
+% %\item \textbf{更新：}在联合学习的迭代交互$r\in[1,R]$中，服务器选择参与本地训练的随机客户子集为$Set_{t}$,在第$r$轮迭代中，只有集合$Set_{t}$中的客户上传模型更新量并彼此交互评估信誉。然而，由于参与训练和客户数量远少于客户总数,即$\vert Set_{t}\vert \ll N$，当前轮次的评估结果不足以给出完整的评估结果。因此，我们使用每个客户端的最新信誉更新值来更新其当前信誉值。设$\left\{ \Phi^{c \rightarrow i}_{t} \right\}_{i}^N$表示在服务器上维护的每个客户的簇内直接信誉。在每一轮交互后，全部客户执行以下更新操作：
+% Moreover, as only chosen UAV nodes $U_i\in S$ participate in the FFL at round $t$, cross-slot reputation values can have erratic fluctuation or asynchronous obsolescence problems.
 Hence, inspired by \cite{jhunjhunwala2022fedvarp}, We introduce the momentum term to the reputation updating as:
-\begin{equation}
-\Upsilon^{c_k \rightarrow i}_{t}=
-\left\{\begin{array}{ll}
-\Upsilon^{c_k \rightarrow i}_{t} ,& \text { if } U_i \in S\\
-\Upsilon^{c_k \rightarrow i}_{t-1},& \text { otherwise }
-\end{array}\right.
-\end{equation}
-
-%在训练开始前，初始化所有客户$\forall i \in [N]$的信誉评价$\Upsilon^{c \rightarrow i}_{0}$可以表示为：
-%可以看出我们提供较高的初始信誉并保证非参与客户历史信誉的连续性。
-Then, in the initialization phase $t=0$, we have:
-\begin{equation}
-\Upsilon^{c_k \rightarrow i}_{0}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{c_k \rightarrow i}_{0}=1-u^{c_k \rightarrow i}_{0},\\
-        d^{c_k \rightarrow i}_{0}=0,\\
-        u^{c_k \rightarrow i}_{0}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}
-      \end{array}
-\right.
-\forall U_i\in c_k.
-\end{equation}
-
-%上式确保了客户簇内直接信誉的实时性，即维护了包括参与和非参与交互客户在内的全部客户的当前信誉均为其最近的信誉更新值。
-The above design ensures the stability of credit evaluation for both participating and non-participating UAV nodes in the current round.
-
-By integrating both stability and long-term consideration, we obtain the final peer reputation opinion: 
-\begin{equation}
-\Upsilon^{c_k \rightarrow i}_{t}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} b^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
-        d^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} d^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
-        u^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} u^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}  ,              
-    \end{array}
-\right.
-\forall U_i\in c_k,
-\end{equation}
-%第r轮同步，簇$c$中客户i的信誉评价为：
-and $c_k$'s credit evaluation towards UAV node $U_i$ at round $t$:
-\begin{equation}
-\Phi^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} \Phi^{c \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}, \forall U_i\in c_k.             
-\end{equation}
-
-\subsection{Performance-dominated colleague credit evaluation}
-Performance-dominated colleague credit evaluation generates the general judgment $\Phi^{s_m}_{t}, \forall s_m\in S$ from other colleague communities. 
-As colleague communities are regrouped after every iteration, different from peer credit, colleague credit pays more attention to comprehensive consideration of both performance and similarity between $s_m$ and $s_{m^{\prime}}, \forall s_{m^{\prime}} \in S_{\neg s_m}$.
-
-Hence, we first calculate the similarity between $s_m$ and $s_{m^{\prime}}$:
-\begin{equation}
-    	  \alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega}^{s_{m}}_{t},  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}) = \frac{\langle  \Delta\widetilde{\omega}^{s_{m}}_{t}, \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\rangle}{\Vert  \Delta\widetilde{\omega}^{s_{m}}_{t}\Vert\cdot\Vert  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\Vert }.
-\end{equation}
-
-The positive and negative interactions are $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$ and $NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$, respectively.
+% \begin{equation}
+% \Upsilon^{c_k \rightarrow i}_{t}=
+% \left\{\begin{array}{ll}
+% \Upsilon^{c_k \rightarrow i}_{t} ,& \text { if } U_i \in S\\
+% \Upsilon^{c_k \rightarrow i}_{t-1},& \text { otherwise }
+% \end{array}\right.
+% \end{equation}
+
+% %在训练开始前，初始化所有客户$\forall i \in [N]$的信誉评价$\Upsilon^{c \rightarrow i}_{0}$可以表示为：
+% %可以看出我们提供较高的初始信誉并保证非参与客户历史信誉的连续性。
+% Then, in the initialization phase $t=0$, we have:
+% \begin{equation}
+% \Upsilon^{c_k \rightarrow i}_{0}=
+% \left  \{
+%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
+%         b^{c_k \rightarrow i}_{0}=1-u^{c_k \rightarrow i}_{0},\\
+%         d^{c_k \rightarrow i}_{0}=0,\\
+%         u^{c_k \rightarrow i}_{0}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}
+%       \end{array}
+% \right.
+% \forall U_i\in c_k.
+% \end{equation}
+
+% %上式确保了客户簇内直接信誉的实时性，即维护了包括参与和非参与交互客户在内的全部客户的当前信誉均为其最近的信誉更新值。
+% The above design ensures the stability of credit evaluation for both participating and non-participating UAV nodes in the current round.
+
+% By integrating both stability and long-term consideration, we obtain the final peer reputation opinion: 
+% \begin{equation}
+% \Upsilon^{c_k \rightarrow i}_{t}=
+% \left  \{
+%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
+%         b^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} b^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
+%         d^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} d^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
+%         u^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} u^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}  ,              
+%     \end{array}
+% \right.
+% \forall U_i\in c_k,
+% \end{equation}
+% %第r轮同步，簇$c$中客户i的信誉评价为：
+% and $c_k$'s credit evaluation towards UAV node $U_i$ at round $t$:
+% \begin{equation}
+% \Phi^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} \Phi^{c \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}, \forall U_i\in c_k.             
+% \end{equation}
+
+% \subsection{Performance-dominated colleague credit evaluation}
+% Performance-dominated colleague credit evaluation generates the general judgment $\Phi^{s_m}_{t}, \forall s_m\in S$ from other colleague communities. 
+% As colleague communities are regrouped after every iteration, different from peer credit, colleague credit pays more attention to comprehensive consideration of both performance and similarity between $s_m$ and $s_{m^{\prime}}, \forall s_{m^{\prime}} \in S_{\neg s_m}$.
+
+% Hence, we first calculate the similarity between $s_m$ and $s_{m^{\prime}}$:
+% \begin{equation}
+%     	  \alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega}^{s_{m}}_{t},  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}) = \frac{\langle  \Delta\widetilde{\omega}^{s_{m}}_{t}, \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\rangle}{\Vert  \Delta\widetilde{\omega}^{s_{m}}_{t}\Vert\cdot\Vert  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\Vert }.
+% \end{equation}
+
+% The positive and negative interactions are $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$ and $NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$, respectively.
 $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} + NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 2$.
 
-Thereafter, the \textit{belief} $b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u_t^{s_{m} \rightarrow s_{m^{\prime}}})\frac{bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$
-\textit{disbelief} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u^{s_{m} \rightarrow s_{m^{\prime}}}_{t})\frac{cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$ and \textit{uncertainty} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=\Vert PI^{s_{m}}-PI^{s_{m^{\prime}}}\Vert/2.$$
-
-For round $t$, the reputation opinion vector can be defined as follows:
-
-\begin{equation}
-\Upsilon^{s_m}_{t}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  b^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
-        d^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  d^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
-        u^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  u^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},
-    \end{array}
-\right.
-\end{equation}
-where $\rho^{s_m}_{t}=acc^{s_m}_{t}$ is the accuracy of colleague community $s_m$.
+% Thereafter, the \textit{belief} $b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u_t^{s_{m} \rightarrow s_{m^{\prime}}})\frac{bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$
+% \textit{disbelief} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u^{s_{m} \rightarrow s_{m^{\prime}}}_{t})\frac{cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$ and \textit{uncertainty} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=\Vert PI^{s_{m}}-PI^{s_{m^{\prime}}}\Vert/2.$$
+
+% For round $t$, the reputation opinion vector can be defined as follows:
+
+% \begin{equation}
+% \Upsilon^{s_m}_{t}=
+% \left  \{
+%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
+%         b^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  b^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
+%         d^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  d^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
+%         u^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  u^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},
+%     \end{array}
+% \right.
+% \end{equation}
+% where $\rho^{s_m}_{t}=acc^{s_m}_{t}$ is the accuracy of colleague community $s_m$.
 From the perspective of model security, we assign lower weights to attackers who dishonestly report data distributions based on the model accuracy $acc^{s_m}_{t}$ of $s_m$.
@@
 
-The final colleague credit evaluation for $\forall U_i \in s_m$ can be calculated as:
-\begin{equation}
-\Phi^{s_m \rightarrow i}_{t}=\Phi^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{(\rho^{s_{m^{\prime}}}_{t} b^{s_{m^{\prime}} \rightarrow s_{m}}_{t}+ a u^{s_{m^{\prime}} \rightarrow s_{m}}_{t})}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},
-\end{equation}
-
-\subsection{UAV nodes selection with comprehensive
-community-based credit}
-\subsubsection{Comprehensive community-based credit} 
-Finally, by merging peer credit and colleague credit evaluation results, we can obtain comprehensive evaluations of participant UAV nodes based on similarity and performance jointly. 
-The comprehensive reputation opinion $\Upsilon^{i}_{t}$ can be calculated by conducting consensus mechanism between $\Upsilon^{c_k\rightarrow i}_{t}$ and $\Upsilon^{s_m\rightarrow i}_{t}$ as:
-\begin{equation}
-\Upsilon^{i}_{t}=
-\left  \{
-      \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-        b^{i}_{t}=\frac{b^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+b^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
-        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
-        d^{i}_{t}=\frac{d^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+d^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
-        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
-        u^{i}_{t}=\frac{u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}
-        {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}         
-    \end{array}
-\right.
-\end{equation}
-
-%因此，可得客户 $j$ 的综合信任度为：
-The comprehensive community-based credit of $U_i$ is: 
-\begin{equation}
-\Phi^{i}_{t}=b^{i}_{t}+a u^{i}_{t}
-\end{equation}
-
-%通过上述信誉评估过程，服务器可以从簇和super node两个维度综合选择具有高性能和可靠数据的高信誉候选客户作为联邦学习任务中的参与者。该方法能够与FEDGS框架紧密结合，在FEDGS内部同步和外部同步的过程中分别从簇内和super node间评估客户信誉，将信誉评估细化到每轮迭代中，能够及时发现并排除攻击者，尽可能地减少其对联合学习的干扰。
-
-Similar to peer credit evaluation, the updating rule of $\Phi^{i}_{t}$ is also designed with stability consideration as follows:
-%\textbf{更新：}第$r$轮迭代，被选中参与联合学习的客户集合为$Set_{t}$。设$\left\{ \Phi^{i}_{t} \right\}_{i=1}^N$表示维护的第$r$轮每个客户的综合信誉。在迭代学习的过程中，对于未被选中构建supernode并参与训练的客户，保持其最近轮次的信用评分，并根据最近的综合信任度计算其下一轮次的选择概率：
-\begin{equation}
-\Phi^{i}_{t}=
-\left\{\begin{array}{ll}
-\Phi^{i}_{t} & \text { if } i \in Set_{t} \\
-\Phi^{i}_{t-1}& \text { otherwise }
-\end{array}, \text { for all } i\in[N]\right.
-\end{equation}
-
-\textbf{Resistance ability against collusion attack:} 
-%当攻击者拥有多个compromised节点时，多个节点可以进行共谋攻击。MR-FFL可以通过简单的设置实现对共谋攻击的阻断。具体来说，在MR-FFL中，攻击者可以采取“集中合谋”或者“分散合谋”策略：（1）分散合谋的攻击者上报不同的数据分布，从而隐藏进不同的异构Peer社区中。显然，这一策略面对传统防御方法或许能够实现绕过，面对MR-FFL时则会被社区内其他用户发现；（2）顾名思义，集中合谋下的攻击者攻击者通过汇报相同的分布而集中在同一个peer社区中。显然，由于我们的综合信用评价同时综合相似度和性能的影响，因此攻击者仍会因为性能不佳而降低评价。我们可以设定一个参与FFL的最低信用值，拥有过多恶意用户的peer社区也会被排除出后续训练。
-When attackers possess multiple compromised UAV nodes, these nodes can conspire to launch collusion attacks.
+% The final colleague credit evaluation for $\forall U_i \in s_m$ can be calculated as:
+% \begin{equation}
+% \Phi^{s_m \rightarrow i}_{t}=\Phi^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{(\rho^{s_{m^{\prime}}}_{t} b^{s_{m^{\prime}} \rightarrow s_{m}}_{t}+ a u^{s_{m^{\prime}} \rightarrow s_{m}}_{t})}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},
+% \end{equation}
+
+% \subsection{UAV nodes selection with comprehensive
+% community-based credit}
+% \subsubsection{Comprehensive community-based credit} 
+% Finally, by merging peer credit and colleague credit evaluation results, we can obtain comprehensive evaluations of participant UAV nodes based on similarity and performance jointly. 
+% The comprehensive reputation opinion $\Upsilon^{i}_{t}$ can be calculated by conducting consensus mechanism between $\Upsilon^{c_k\rightarrow i}_{t}$ and $\Upsilon^{s_m\rightarrow i}_{t}$ as:
+% \begin{equation}
+% \Upsilon^{i}_{t}=
+% \left  \{
+%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
+%         b^{i}_{t}=\frac{b^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+b^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
+%         {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
+%         d^{i}_{t}=\frac{d^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+d^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
+%         {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
+%         u^{i}_{t}=\frac{u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}
+%         {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}         
+%     \end{array}
+% \right.
+% \end{equation}
+
+% %因此，可得客户 $j$ 的综合信任度为：
+% The comprehensive community-based credit of $U_i$ is: 
+% \begin{equation}
+% \Phi^{i}_{t}=b^{i}_{t}+a u^{i}_{t}
+% \end{equation}
+
+% %通过上述信誉评估过程，服务器可以从簇和super node两个维度综合选择具有高性能和可靠数据的高信誉候选客户作为联邦学习任务中的参与者。该方法能够与FEDGS框架紧密结合，在FEDGS内部同步和外部同步的过程中分别从簇内和super node间评估客户信誉，将信誉评估细化到每轮迭代中，能够及时发现并排除攻击者，尽可能地减少其对联合学习的干扰。
+
+% Similar to peer credit evaluation, the updating rule of $\Phi^{i}_{t}$ is also designed with stability consideration as follows:
+% %\textbf{更新：}第$r$轮迭代，被选中参与联合学习的客户集合为$Set_{t}$。设$\left\{ \Phi^{i}_{t} \right\}_{i=1}^N$表示维护的第$r$轮每个客户的综合信誉。在迭代学习的过程中，对于未被选中构建supernode并参与训练的客户，保持其最近轮次的信用评分，并根据最近的综合信任度计算其下一轮次的选择概率：
+% \begin{equation}
+% \Phi^{i}_{t}=
+% \left\{\begin{array}{ll}
+% \Phi^{i}_{t} & \text { if } i \in Set_{t} \\
+% \Phi^{i}_{t-1}& \text { otherwise }
+% \end{array}, \text { for all } i\in[N]\right.
+% \end{equation}
+
+% \textbf{Resistance ability against collusion attack:} 
+% %当攻击者拥有多个compromised节点时，多个节点可以进行共谋攻击。MR-FFL可以通过简单的设置实现对共谋攻击的阻断。具体来说，在MR-FFL中，攻击者可以采取“集中合谋”或者“分散合谋”策略：（1）分散合谋的攻击者上报不同的数据分布，从而隐藏进不同的异构Peer社区中。显然，这一策略面对传统防御方法或许能够实现绕过，面对MR-FFL时则会被社区内其他用户发现；（2）顾名思义，集中合谋下的攻击者攻击者通过汇报相同的分布而集中在同一个peer社区中。显然，由于我们的综合信用评价同时综合相似度和性能的影响，因此攻击者仍会因为性能不佳而降低评价。我们可以设定一个参与FFL的最低信用值，拥有过多恶意用户的peer社区也会被排除出后续训练。
+% When attackers possess multiple compromised UAV nodes, these nodes can conspire to launch collusion attacks.
 MR-FFL can effectively thwart collusion attacks through simple configurations.
@@
 
-\subsubsection{UAV nodes selection}
-%在每轮外部同步结束，我们重新选择客户构建下一轮参与联合学习的super node。
-%为了尽可能地消除攻击者的干扰，我们设计簇内客户选择机制，客户被选中参与联合学习的概率由其上一轮次的综合信用评价决定。在簇$c$中，用sigmoid函数量化客户$i$被选中的概率：
-After each round of FFL training, we reconstruct colleague communities as participants for the next round.
+% \subsubsection{UAV nodes selection}
+% %在每轮外部同步结束，我们重新选择客户构建下一轮参与联合学习的super node。
+% %为了尽可能地消除攻击者的干扰，我们设计簇内客户选择机制，客户被选中参与联合学习的概率由其上一轮次的综合信用评价决定。在簇$c$中，用sigmoid函数量化客户$i$被选中的概率：
+% After each round of FFL training, we reconstruct colleague communities as participants for the next round.
 To mitigate the impact of potential attacks, we introduce a client selection mechanism within the peer community.
@@
 Drawing inspiration from \cite{zhou2022defta}, we employ a Sigmoid-like function to quantify this probability of UAV $U_i$:
-\begin{equation}
-\psi^{i}_t=\frac{1}{1+e^{-k (\Phi^{i}_{t}-\gamma)}},\forall U_i \in \mathbf{U}, \forall t
-\end{equation}
-%其中$k$为控制sigmoid斜率的参数。由于$\Phi^{i}_{t}\in [0,1]$,我们规定选择概率函数的定义域在[0,1]区间内。可以看出选择概率函数在定义域内的值域$[\frac{1}{1+e^{0.5k}},\frac{1}{1+e^{-0.5k}}]$取决于参数$k$。在实际应用中，为了使选择概率在定义域内尽可能接近0和1，一般选择较大的斜率$k$。
-where $k$ controls the slope of the Sigmoid function.
+% \begin{equation}
+% \psi^{i}_t=\frac{1}{1+e^{-k (\Phi^{i}_{t}-\gamma)}},\forall U_i \in \mathbf{U}, \forall t
+% \end{equation}
+% %其中$k$为控制sigmoid斜率的参数。由于$\Phi^{i}_{t}\in [0,1]$,我们规定选择概率函数的定义域在[0,1]区间内。可以看出选择概率函数在定义域内的值域$[\frac{1}{1+e^{0.5k}},\frac{1}{1+e^{-0.5k}}]$取决于参数$k$。在实际应用中，为了使选择概率在定义域内尽可能接近0和1，一般选择较大的斜率$k$。
+% where $k$ controls the slope of the Sigmoid function.
 As $\Phi^{i}_{t}\in [0,1]$, we stipulate that the domain of the probability function $\psi^{i}_t$ lies within $[0,1]$.
@@
 
-\textbf{Positive assumption for fairness among benign UAVs:} It is worth mentioning that, different from existing methods' negative assumption, we initiate the selection with positive assumption, i.e., $\Phi^{i}_{0}=1 ,\forall U_i\in \mathbf{U}$, which provides high selective probability for inexperienced new participants.
+% \textbf{Positive assumption for fairness among benign UAVs:} It is worth mentioning that, different from existing methods' negative assumption, we initiate the selection with positive assumption, i.e., $\Phi^{i}_{0}=1 ,\forall U_i\in \mathbf{U}$, which provides high selective probability for inexperienced new participants.
 Therefore, this approach can achieve more fair selection results among benign UAV nodes and maximize client participation.
@@
 
-%服务器基于本轮综合信用评分选择客户参与下一轮次的训练，为了尽可能地提高客户的参与率，得到更全面、完整的客户信誉评估结果，将综合信誉作为客户属性进行持久化存储，服务器将赋予客户乐观的初始综合信誉并在每轮交互中更新客户的最新综合信誉。
-%The server selects clients for the next training round based on the current comprehensive credit score.
+% %服务器基于本轮综合信用评分选择客户参与下一轮次的训练，为了尽可能地提高客户的参与率，得到更全面、完整的客户信誉评估结果，将综合信誉作为客户属性进行持久化存储，服务器将赋予客户乐观的初始综合信誉并在每轮交互中更新客户的最新综合信誉。
+% %The server selects clients for the next training round based on the current comprehensive credit score.
 In order to maximize client participation, achieve a more comprehensive and complete client credit assessment, and persistently store the comprehensive credit as a client attribute, the server endows clients with an optimistic initial comprehensive credit.
-%乐观的初始信誉和时间延迟的信誉更新增加了参与训练次数较少的客户被选中的概率，能够更全面、完善地评估所有客户的信誉，避免潜在攻击的影响。
-%This initial credit, along with delayed credit updates over time, increases the probability of selecting clients with fewer training participations.
+% %乐观的初始信誉和时间延迟的信誉更新增加了参与训练次数较少的客户被选中的概率，能够更全面、完善地评估所有客户的信誉，避免潜在攻击的影响。
+% %This initial credit, along with delayed credit updates over time, increases the probability of selecting clients with fewer training participations.
 This approach aims to provide a more comprehensive and thorough evaluation of all clients' reputations, mitigating the potential impact of adversarial behavior.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{algorithm}[t]
-% \caption{algorithm credit} %算法的名字
-% \begin{algorithmic}[1]
-%  \State \textbf{\bf Input:Model Variation of Client i $\Delta\widetilde{\omega^{i}_{t}}$, Model Variation of Cluster c $\Delta\widetilde{\omega^{c}_{t-1}}$}
-% \State\textbf{Output:Comprehensive Credit of Client $\Phi^{i}_{t}$,Peputation Opinion Vector $\Upsilon^{i}_{t}$} 
-% \State \textbf{Initialize:$u^{c \rightarrow i}_{0}=\frac{\sigma_{c}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}$,$b^{c \rightarrow i}_{0}=1-u^{c \rightarrow i}_{0}$,$d^{c \rightarrow i}_{0}=0$}
-% \For{$r \in 1,\cdots,R$}
-%     \State {\color{CadetBlue}/*\textbf{Credit in cluster $c$ */}}
-%         \For{each client $i \in c$ }
-%             \If{client $i \in C \cap S$ }
-%                 \State $ \alpha^{c,i}_{t} = \alpha( \Delta\widetilde{\omega^{c}_{t-1}}, \Delta\widetilde{\omega^{i}_{t}}) = \frac{\langle \Delta\widetilde{\omega^{c}_{t-1}},\Delta\widetilde{\omega^{i}_{t}}\rangle}{\Vert \Delta\widetilde{\omega^{c}_{t-1}}\Vert\cdot\Vert \Delta\widetilde{\omega^{i}_{t}}\Vert }$,
-%                 \State$p^{c \rightarrow i}_{t} = \alpha^{c,i}_{t} -(-1)$,$n^{c \rightarrow i}_{t} = 1-\alpha^{i,j}_{t}$,
-%                 \State \textbf{update  $\Upsilon^{c \rightarrow i}_{t},\Phi^{c \rightarrow i}_{r,time}$ with equation}
-%                 \State $\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{r,time}$
-%             \Else
-%                 \State$\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{t-1}$
-%             \EndIf
-%          \EndFor
-%     \State {\color{CadetBlue}/*\textbf{Credit in supernode $s$ */}}
-%     \For{each supernode $s_{m} \in S-s_{m}$}
-%         \State $\alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega^{s_{m}}_{t}},  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}) = \frac{\langle  \Delta\widetilde{\omega^{s_{m}}_{t}}, \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\rangle}{\Vert  \Delta\widetilde{\omega^{s_{m}}_{t}}\Vert\cdot\Vert  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\Vert }$,
-%         \State $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$,$ NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$
-%         \State \textbf{update $\UpsiloNI^{s_{m} \rightarrow s}_{t},\Phi^{s}_{t}$ with equation}
-%     \EndFor
-%     \For{each client $i \in S$}
-%         \State $\Phi^{s \rightarrow i}_{t}=\Phi^{s}_{t} $
-%     \EndFor
-%     \State {\color{CadetBlue} /*\textbf{Comprehensive credit */}}
-%     \For{each client $i \in Clients$}
-%         \If{client $i \in C\cap S$ }
-%         \State \textbf{update $\Upsilon^{i}_{t},\Phi^{i}_{t}$ with equation}
-%         \Else 
-%         \State $\Phi^{i}_{t} = \Phi^{i}_{t-1}$
-%         \EndIf
-%     \EndFor
-% \EndFor
-% \end{algorithmic}
-% \end{algorithm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tb]
-	\begin{minipage}[!t]{0.49\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{results/SCC_diff.pdf}
-		%\vspace{-2em}
-		\caption{$L_2$-divergence}
-		\label{results:1-diff}
-	\end{minipage}
-        \begin{minipage}[!t]{0.49\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{results/SCC_time.pdf}
-		%\vspace{-2em}
-		\caption{Running time}
-		\label{results:1-time}
-	\end{minipage}
-\end{figure}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\linewidth]{results/SCC_acc.pdf}
-\caption{The accuracy comparison between MR-FFL with existing heterogeneity-robust methods.}
-\label{results:1-acc}
-\end{figure}
-
-\section{Experimental results}
-\subsection{Experimental settings}
-Experiments were conducted using the PyTorch deep learning framework, employing two widely adopted benchmark datasets (EMNIST and CIFAR).
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % \begin{algorithm}[t]
+% % \caption{algorithm credit} %算法的名字
+% % \begin{algorithmic}[1]
+% %  \State \textbf{\bf Input:Model Variation of Client i $\Delta\widetilde{\omega^{i}_{t}}$, Model Variation of Cluster c $\Delta\widetilde{\omega^{c}_{t-1}}$}
+% % \State\textbf{Output:Comprehensive Credit of Client $\Phi^{i}_{t}$,Peputation Opinion Vector $\Upsilon^{i}_{t}$} 
+% % \State \textbf{Initialize:$u^{c \rightarrow i}_{0}=\frac{\sigma_{c}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}$,$b^{c \rightarrow i}_{0}=1-u^{c \rightarrow i}_{0}$,$d^{c \rightarrow i}_{0}=0$}
+% % \For{$r \in 1,\cdots,R$}
+% %     \State {\color{CadetBlue}/*\textbf{Credit in cluster $c$ */}}
+% %         \For{each client $i \in c$ }
+% %             \If{client $i \in C \cap S$ }
+% %                 \State $ \alpha^{c,i}_{t} = \alpha( \Delta\widetilde{\omega^{c}_{t-1}}, \Delta\widetilde{\omega^{i}_{t}}) = \frac{\langle \Delta\widetilde{\omega^{c}_{t-1}},\Delta\widetilde{\omega^{i}_{t}}\rangle}{\Vert \Delta\widetilde{\omega^{c}_{t-1}}\Vert\cdot\Vert \Delta\widetilde{\omega^{i}_{t}}\Vert }$,
+% %                 \State$p^{c \rightarrow i}_{t} = \alpha^{c,i}_{t} -(-1)$,$n^{c \rightarrow i}_{t} = 1-\alpha^{i,j}_{t}$,
+% %                 \State \textbf{update  $\Upsilon^{c \rightarrow i}_{t},\Phi^{c \rightarrow i}_{r,time}$ with equation}
+% %                 \State $\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{r,time}$
+% %             \Else
+% %                 \State$\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{t-1}$
+% %             \EndIf
+% %          \EndFor
+% %     \State {\color{CadetBlue}/*\textbf{Credit in supernode $s$ */}}
+% %     \For{each supernode $s_{m} \in S-s_{m}$}
+% %         \State $\alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega^{s_{m}}_{t}},  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}) = \frac{\langle  \Delta\widetilde{\omega^{s_{m}}_{t}}, \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\rangle}{\Vert  \Delta\widetilde{\omega^{s_{m}}_{t}}\Vert\cdot\Vert  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\Vert }$,
+% %         \State $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$,$ NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$
+% %         \State \textbf{update $\UpsiloNI^{s_{m} \rightarrow s}_{t},\Phi^{s}_{t}$ with equation}
+% %     \EndFor
+% %     \For{each client $i \in S$}
+% %         \State $\Phi^{s \rightarrow i}_{t}=\Phi^{s}_{t} $
+% %     \EndFor
+% %     \State {\color{CadetBlue} /*\textbf{Comprehensive credit */}}
+% %     \For{each client $i \in Clients$}
+% %         \If{client $i \in C\cap S$ }
+% %         \State \textbf{update $\Upsilon^{i}_{t},\Phi^{i}_{t}$ with equation}
+% %         \Else 
+% %         \State $\Phi^{i}_{t} = \Phi^{i}_{t-1}$
+% %         \EndIf
+% %     \EndFor
+% % \EndFor
+% % \end{algorithmic}
+% % \end{algorithm}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[tb]
+% 	\begin{minipage}[!t]{0.49\linewidth}
+% 		\centering
+% 		\includegraphics[width=\linewidth]{results/SCC_diff.pdf}
+% 		%\vspace{-2em}
+% 		\caption{$L_2$-divergence}
+% 		\label{results:1-diff}
+% 	\end{minipage}
+%         \begin{minipage}[!t]{0.49\linewidth}
+% 		\centering
+% 		\includegraphics[width=\linewidth]{results/SCC_time.pdf}
+% 		%\vspace{-2em}
+% 		\caption{Running time}
+% 		\label{results:1-time}
+% 	\end{minipage}
+% \end{figure}
+
+% \begin{figure}[!t]
+% \centering
+% \includegraphics[width=\linewidth]{results/SCC_acc.pdf}
+% \caption{The accuracy comparison between MR-FFL with existing heterogeneity-robust methods.}
+% \label{results:1-acc}
+% \end{figure}
+
+% \section{Experimental results}
+% \subsection{Experimental settings}
+% Experiments were conducted using the PyTorch deep learning framework, employing two widely adopted benchmark datasets (EMNIST and CIFAR).
 To demonstrate the defense performance of the proposed MR-FFL scheme, we conduct both explicit (Flipping attack) and implicit (Backdoor attack) attack paradigms.
@@
 All images have dimensions of 28x28 pixels.
-In line with the methodologies of previous studies \cite{mohri2019agnostic,tan2022fedproto, zeng2022heterogeneous}, our experiments were conducted under a non-iid setting, implementing non-uniform sampling within the dataset.
-To create an equitable but dissimilar distribution among clients, we extracted 12,0000 training samples and 30,000 testing samples, allocating them in an 8:2 ratio between the training set and the validation set.
+% In line with the methodologies of previous studies \cite{mohri2019agnostic,tan2022fedproto, zeng2022heterogeneous}, our experiments were conducted under a non-iid setting, implementing non-uniform sampling within the dataset.
+% To create an equitable but dissimilar distribution among clients, we extracted 12,0000 training samples and 30,000 testing samples, allocating them in an 8:2 ratio between the training set and the validation set.
 This ensured that each client possessed an equal number of samples in the training dataset, albeit with distinct data distributions.
@@
 The detailed configurations of the local network models are delineated in Tables 2 and 3.
-Throughout our experiments, we configured $200\sim 500$ UAV nodes.
+% Throughout our experiments, we configured $200\sim 500$ UAV nodes.
 A total of 200 communication rounds were executed, where the local training epoch for each $U_i$ is 5, the batch size is 128, the learning rate $\eta$ is 0.1, and the momentum is 0.9.
 
-\subsection{The effectiveness of MR-FFL in heterogeneous UAV network}
-
-To verify the effectiveness of our stratified community construction mechanism, we compare it with existing heterogeneity-robust methods in terms of divergence reduction, running time, and learning performance.
+% \subsection{The effectiveness of MR-FFL in heterogeneous UAV network}
+
+% To verify the effectiveness of our stratified community construction mechanism, we compare it with existing heterogeneity-robust methods in terms of divergence reduction, running time, and learning performance.
 We choose three benchmark methods (\textbf{Random}, \textbf{Bayesian}, \textbf{Generic algorithms}) and two latest methods (\textbf{Cohort} \cite{hiessl2022cohort} and \textbf{GBP-CS} \cite{li2022data}).
-In terms of divergence reduction, as shown in Figure \ref{results:1-diff}, our method significantly reduces both the average maximum divergences and deviation among clients, which indicates better robustness.
-Regarding execution time, SCC requires only one operation to generate a sampling template.
+% In terms of divergence reduction, as shown in Figure \ref{results:1-diff}, our method significantly reduces both the average maximum divergences and deviation among clients, which indicates better robustness.
+% Regarding execution time, SCC requires only one operation to generate a sampling template.
 Subsequently, it performs random sampling based on the template, resulting in a short execution time.
@@
 
-In terms of learning performance, we also compared three representative algorithms (\textbf{FedAvg} \cite{li2019convergence-fedavg}, \textbf{FedNova} \cite{wang2020tackling-fednova}, \textbf{FedProx} \cite{yuan2022convergence-fedprox}) with MR-FFL.
+% In terms of learning performance, we also compared three representative algorithms (\textbf{FedAvg} \cite{li2019convergence-fedavg}, \textbf{FedNova} \cite{wang2020tackling-fednova}, \textbf{FedProx} \cite{yuan2022convergence-fedprox}) with MR-FFL.
 As illustrated in Figure \ref{results:1-acc}, vanilla FL algorithms exhibit slow convergence rates and poor performance with large fluctuations in heterogeneous environments.
@@
 
-\subsection{The performance of MR-FFL against poisoning attacks}
-\begin{figure*}[!t]
-\centering
-\subfloat[EMNIST (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_MINIST_acc.pdf}%
-\label{result0:acc-EMNIST-FLIP}}
-\hfil
-\subfloat[CIFAR (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_Cifar_acc.pdf}%
-\label{result0:acc-CIFAR-FLIP}}
-\hfil
-\subfloat[EMNIST (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_MINIST_att_acc.pdf}%
-\label{result0:acc-EMNIST-Backdoor}}
-\hfil
-\subfloat[CIFAR (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_Cifar_att_acc.pdf}%
-\label{result0:acc-CIFAR-Backdoor}}
-\caption{The defense performance comparison between MR-FFL with existing poisoning-resistant methods against Flipping and Backdoor attacks.}
-\label{results:0-acc}
-\end{figure*}
-
-% %%%%%%%%%%%%EMNIST+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}[!t]
+% \subsection{The performance of MR-FFL against poisoning attacks}
+% \begin{figure*}[!t]
 % \centering
-% \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_MINIST_cr_1.pdf}%
-% \label{result1:credit-AAD}}
+% \subfloat[EMNIST (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_MINIST_acc.pdf}%
+% \label{result0:acc-EMNIST-FLIP}}
 % \hfil
-% \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_MINIST_pr_1.pdf}%
-% \label{result1:prob-AAD}}
+% \subfloat[CIFAR (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_Cifar_acc.pdf}%
+% \label{result0:acc-CIFAR-FLIP}}
 % \hfil
-% \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_MINIST_cr_1.pdf}%
-% \label{result1:credit-FLtrust}}
+% \subfloat[EMNIST (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_MINIST_att_acc.pdf}%
+% \label{result0:acc-EMNIST-Backdoor}}
 % \hfil
-% \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_MINIST_pr_1.pdf}%
-% \label{result1:prob-FLtrust}}
-% \hfil
-% \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_MINIST_cr_1.pdf}%
-% \label{result1:credit-MRFFL}}
-% \hfil
-% \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_Flip_MINIST_pr_1.pdf}%
-% \label{result1:prob-MRFFL}}
-% \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on EMNIST.}
-% \label{results_EMNIST_flip}
-% \end{figure}
-
-% %%%%%%%%%%%EMNIST+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}[!t]
-% \centering
-% \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_MINIST_cr_1.pdf}%
-% \label{result2:credit-AAD}}
-% \hfil
-% \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_MINIST_pr_1.pdf}%
-% \label{result2:prob-AAD}}
-% \hfil
-% \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_MINIST_cr_1.pdf}%
-% \label{result2:credit-FLtrust}}
-% \hfil
-% \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_MINIST_pr_1.pdf}%
-% \label{result2:prob-FLtrust}}
-% \hfil
-% \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_MINIST_cr_1.pdf}%
-% \label{result2:credit-MRFFL}}
-% \hfil
-% \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_BACKDOOR_MINIST_pr_1.pdf}%
-% \label{result2:prob-MRFFL}}
-% \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on EMNIST.}
-% \label{results_EMNIST_Backdoor}
-% \end{figure}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%CIFAR+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}[!t]
-% \centering
-% \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_Cifar_cr_1.pdf}%
-% \label{result3:credit-AAD}}
-% \hfil
-% \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_Cifar_pr_1.pdf}%
-% \label{result3:prob-AAD}}
-% \hfil
-% \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_Cifar_cr_1.pdf}%
-% \label{result3:credit-FLtrust}}
-% \hfil
-% \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_Cifar_pr_1.pdf}%
-% \label{result3:prob-FLtrust}}
-% \hfil
-% \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_Cifar_cr_1.pdf}%
-% \label{result3:credit-MRFFL}}
-% \hfil
-% \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_Flip_Cifar_pr_1.pdf}%
-% \label{result3:prob-MRFFL}}
-% \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on CIFAR.}
-% \label{results_Cifar_flip}
-% \end{figure}
-% %%%%%%%%%%%CIFAR+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}[!t]
-% \centering
-% \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_Cifar_cr_1.pdf}%
-% \label{result4:credit-AAD}}
-% \hfil
-% \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_Cifar_pr_1.pdf}%
-% \label{result4:prob-AAD}}
-% \hfil
-% \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_Cifar_cr_1.pdf}%
-% \label{result4:credit-FLtrust}}
-% \hfil
-% \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_Cifar_pr_1.pdf}%
-% \label{result4:prob-FLtrust}}
-% \hfil
-% \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_Cifar_cr_1.pdf}%
-% \label{result4:credit-MRFFL}}
-% \hfil
-% \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_BACKDOOR_Cifar_pr_1.pdf}%
-% \label{result4:prob-MRFFL}}
-% \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on CIFAR.}
-% \label{results_Cifar_Backdoor}
-% \end{figure}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Subsequently, to further demonstrate the advantages of the MR-FFL method in ensuring model integrity, we compare our approach with existing representative reliable FL algorithms, including \textit{mitigation-oriented} \cite{blanchard2017machine-krum,yin2018byzantine-trimmedmean}, \textit{detection-oriented} \cite{andreina2021baffle}, and \textit{credit-oriented} \cite{li2019abnormal,cao2020fltrust}.
+% \subfloat[CIFAR (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_Cifar_att_acc.pdf}%
+% \label{result0:acc-CIFAR-Backdoor}}
+% \caption{The defense performance comparison between MR-FFL with existing poisoning-resistant methods against Flipping and Backdoor attacks.}
+% \label{results:0-acc}
+% \end{figure*}
+
+% % %%%%%%%%%%%%EMNIST+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % \begin{figure}[!t]
+% % \centering
+% % \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_MINIST_cr_1.pdf}%
+% % \label{result1:credit-AAD}}
+% % \hfil
+% % \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_MINIST_pr_1.pdf}%
+% % \label{result1:prob-AAD}}
+% % \hfil
+% % \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_MINIST_cr_1.pdf}%
+% % \label{result1:credit-FLtrust}}
+% % \hfil
+% % \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_MINIST_pr_1.pdf}%
+% % \label{result1:prob-FLtrust}}
+% % \hfil
+% % \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_MINIST_cr_1.pdf}%
+% % \label{result1:credit-MRFFL}}
+% % \hfil
+% % \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_Flip_MINIST_pr_1.pdf}%
+% % \label{result1:prob-MRFFL}}
+% % \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on EMNIST.}
+% % \label{results_EMNIST_flip}
+% % \end{figure}
+
+% % %%%%%%%%%%%EMNIST+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
+% % \begin{figure}[!t]
+% % \centering
+% % \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_MINIST_cr_1.pdf}%
+% % \label{result2:credit-AAD}}
+% % \hfil
+% % \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_MINIST_pr_1.pdf}%
+% % \label{result2:prob-AAD}}
+% % \hfil
+% % \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_MINIST_cr_1.pdf}%
+% % \label{result2:credit-FLtrust}}
+% % \hfil
+% % \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_MINIST_pr_1.pdf}%
+% % \label{result2:prob-FLtrust}}
+% % \hfil
+% % \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_MINIST_cr_1.pdf}%
+% % \label{result2:credit-MRFFL}}
+% % \hfil
+% % \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_BACKDOOR_MINIST_pr_1.pdf}%
+% % \label{result2:prob-MRFFL}}
+% % \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on EMNIST.}
+% % \label{results_EMNIST_Backdoor}
+% % \end{figure}
+% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % %%%%%%%%%%%%CIFAR+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % \begin{figure}[!t]
+% % \centering
+% % \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_Cifar_cr_1.pdf}%
+% % \label{result3:credit-AAD}}
+% % \hfil
+% % \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_Cifar_pr_1.pdf}%
+% % \label{result3:prob-AAD}}
+% % \hfil
+% % \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_Cifar_cr_1.pdf}%
+% % \label{result3:credit-FLtrust}}
+% % \hfil
+% % \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_Cifar_pr_1.pdf}%
+% % \label{result3:prob-FLtrust}}
+% % \hfil
+% % \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_Cifar_cr_1.pdf}%
+% % \label{result3:credit-MRFFL}}
+% % \hfil
+% % \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_Flip_Cifar_pr_1.pdf}%
+% % \label{result3:prob-MRFFL}}
+% % \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on CIFAR.}
+% % \label{results_Cifar_flip}
+% % \end{figure}
+% % %%%%%%%%%%%CIFAR+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
+% % \begin{figure}[!t]
+% % \centering
+% % \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_Cifar_cr_1.pdf}%
+% % \label{result4:credit-AAD}}
+% % \hfil
+% % \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_Cifar_pr_1.pdf}%
+% % \label{result4:prob-AAD}}
+% % \hfil
+% % \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_Cifar_cr_1.pdf}%
+% % \label{result4:credit-FLtrust}}
+% % \hfil
+% % \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_Cifar_pr_1.pdf}%
+% % \label{result4:prob-FLtrust}}
+% % \hfil
+% % \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_Cifar_cr_1.pdf}%
+% % \label{result4:credit-MRFFL}}
+% % \hfil
+% % \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_BACKDOOR_Cifar_pr_1.pdf}%
+% % \label{result4:prob-MRFFL}}
+% % \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on CIFAR.}
+% % \label{results_Cifar_Backdoor}
+% % \end{figure}
+% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Subsequently, to further demonstrate the advantages of the MR-FFL method in ensuring model integrity, we compare our approach with existing representative reliable FL algorithms, including \textit{mitigation-oriented} \cite{blanchard2017machine-krum,yin2018byzantine-trimmedmean}, \textit{detection-oriented} \cite{andreina2021baffle}, and \textit{credit-oriented} \cite{li2019abnormal,cao2020fltrust}.
 The total number of UAV ndoes is set to 200.
@@
 Lower backdoor accuracy indicates better defense performance.
-Based on the results, it is evident that mitigation-oriented schemes such as \textbf{Trimmed-mean} \cite{yin2018byzantine-trimmedmean} exhibit significant deviations from the global objectives in heterogeneous environments, resulting in lower accuracy.
+% Based on the results, it is evident that mitigation-oriented schemes such as \textbf{Trimmed-mean} \cite{yin2018byzantine-trimmedmean} exhibit significant deviations from the global objectives in heterogeneous environments, resulting in lower accuracy.
 \textbf{BaFFLe} \cite{andreina2021baffle}, as a detection-oriented method, struggles to converge rapidly and requires additional validation rounds, incurring substantial communication and time overhead.
@@
 
-Furthermore, in Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, through a comparative analysis of credit assessment values and selection probabilities with existing methods such as AAD (based on autoencoder) and FLTrust (based on bootstrapping), we validate the effectiveness of the credit evaluation mechanism in the MR-FFL scheme.
+% Furthermore, in Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, through a comparative analysis of credit assessment values and selection probabilities with existing methods such as AAD (based on autoencoder) and FLTrust (based on bootstrapping), we validate the effectiveness of the credit evaluation mechanism in the MR-FFL scheme.
 This validation is crucial for guiding subsequent hyperparameter tuning and adaptive configurations.
@@
 
-\subsection{The fairness of MR-FFL under adversarial environments}
-One of the important drawbacks of existing security technologies is unfairness.
+% \subsection{The fairness of MR-FFL under adversarial environments}
+% One of the important drawbacks of existing security technologies is unfairness.
 As shown in the second columns of Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, except for the low accuracy, AAD and FLTrust also assign vastly different selection probabilities to benign UAV nodes.

### 2024-09-18 attack-zh.tex
final: 初稿
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 % 联邦学习
-$ N $ & The number of the nodes participating during each round. \\ \hline
+$ N $ & The number of nodes participating during each round. \\ \hline
 % $\mathcal{M}$ & The number of the participants during each round. \\ \hline
@@
 
-\begin{algorithm}
-\caption{Malicious Node Detection and Gradient Aggregation}
-\label{alg:malicious-node-detection-history}
-\begin{algorithmic}[1]
-\State \textbf{Input:} Global model history $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$, threshold $\varepsilon$
-\State \textbf{Output:} Sets of normal clients $U_{nor}$ and malicious clients $U_{mal}$
-
-\State \textbf{Step 1: Keep T-rounds History}
-\For {Client $i$}
-    \State Record flattened gradients $\bar{\theta_i^t} = Flatten(\triangledown \theta_{i}^t)$ and models $\theta_g^{t-1}$
-    \State Construct rays: $\widetilde{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'} = \overline{\triangledown\theta_{i}^{t'}}$ for $t' = \max\{t-T+1, 1\}, \ldots, t$
-\EndFor
-
-\State \textbf{Step 2: Obtain the Purpose Intention}
-\For {Client $i$}
-    \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
-    \While {Not Converged}
-        \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
-    \EndWhile
-    \State Calculate confidence $cre_i = \frac{1}{r_i + \rho}$
-\EndFor
-
-\State \textbf{Step 3: Abnormal Detection}
-\For {Client $i$}
-    \For {Each point $O_j \neq O_i$}
-        \State Calculate distance $\|O_i - O_j\|$
-    \EndFor
-    \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
-    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
-    \State Compute reachability distance $rea_{i,j} = \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$
-    \State Calculate local reachability density $lrd_i = \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$
-\EndFor
-% \For {Client $i$}
-%     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
-%     \If {$lof_i > 1$}
-%         \State Mark client $i$ as malicious, add to $U_{mal}$
-%     \Else
-%         \State Mark client $i$ as normal, add to $U_{nor}$
-%     \EndIf
-% \EndFor
-\State Calculate $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$ for each client $i$
-% \State $U_{mal} = \{i \,|\, lof_i > 1\}$
-% \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
-\State $U_{mal}, U_{nor} = \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$
-
-\State \textbf{Step 4: Gradients Aggregation}
-\For {Client $i\in U_{nor}$}
-        \State Compute adjusted confidence $cre_i' = \tanh(cre_i)$
-        \State Normalize weights $w_i = \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$
-\EndFor
-
-\State \textbf{Output:} Aggregated global model update $\theta_g^t = \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$
-\end{algorithmic}
-\end{algorithm}
-
 % 算法\ref{alg:malicious-node-detection-history}展示了根据每个客户端历史记录进行识别的识别过程，主要包含4个步骤：
@@
     计算当前球心 \( O_{i,k} \) 到这些最近点 \( \tilde O_{i,k}^{t'} \) 的距离集合 \( Dis_{i,k}= \{ \| O_{i,k}-\tilde O_{i,k}^{t'} \|, \max\{t-T+1, 1\}\leq  t'\leq t\} \)，并按从小到大的顺序进行排序，然后暂时舍弃$1-\zeta$比例的射线来忽略离群点对计算过程的影响，得到集合${Dis}_{i,k}'$，保留射线对应轮次的集合记为$\tilde T$。将球心向着被保留的最近点中距离最远的点$\tilde{O}_{i,k}^{t_{max}'}$移动：
-    % ，$ {Dis}_{i,k}'=\text{Sort}(Dis_{i,k})$。
-        % 并计算这些投影点的最大距离 \( D_k \)：
-
-        % \begin{equation}
-        % D_k = \max_{1\leq j\leq \lceil n\times \varepsilon\rceil} \|O_k - Q_{i}^{t-j}\|.
-        % \end{equation}
 
@@
 
-    % 其中$\tilde O_{i,k+1}^{t'}$为更新后的球心$O_{i,k+1}$到被保留射线的最近点。终止条件：当更新后的半径 \( r_{i,k+1} \) 与上一次的半径 \( r_{i,k} \) 相差小于一个预设的阈值 \( \lambda \)，或者达到预设的最大迭代次数$k_{max}$时，停止迭代。这部分可以定义为一个有约束的最优化问题：
     其中$\tilde O_{i,k+1}^{t'}$为更新后的球心$O_{i,k+1}$到被保留射线的最近点。当更新后的半径 \( r_{i,k+1} \) 与上一次的半径 \( r_{i,k} \) 相差小于一个预设的阈值 \( \lambda \)，或者达到预设的最大迭代次数$k_{max}$时，停止迭代。
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{results/prob-history-Visualization of Client Intentions and Anomalies.png}
-    \centering \caption{使用模拟数据得到的结果}
-    \label{fig:result-of-histry}
-\end{figure}
+% \begin{figure}[!t]
+%     \centering
+%     \includegraphics[width=\linewidth]{results/prob-history-Visualization of Client Intentions and Anomalies.png}
+%     \centering \caption{使用模拟数据得到的结果}
+%     \label{fig:result-of-histry}
+% \end{figure}
 
@@
 
-This section presents a thorough evaluation of SecFFT on two benchmark datasets, aiming to illustrate its effectiveness.
+This section presents a thorough evaluation of SecFFT on two benchmark datasets, aiming to illustrate its effectiveness. 本实验在一台Windows操作系统的服务器上进行，28核心128GB内存，以及2块NVIDIA GeForce RTX 3090 GPU(24G)。
 
@@
 \begin{itemize}
-    \item \textbf{数据集}：我们使用FMNIST\cite{minist}和CIFAR-10\cite{cifar10}数据集作为实验数据集。FMNIST数据集包含60,000张28x28像素的灰度时尚商品图像，共分为10个类别，其中50,000张为训练集，10,000张为测试集。CIFAR-10数据集包含60,000张32x32像素的彩色图像，也分为10个类别，其中50,000张为训练集，10,000张为测试集。
+    \item \textbf{数据集}：我们使用FMNIST\cite{minist}作为实验数据集。FMNIST数据集包含60,000张28x28像素的灰度时尚商品图像，共分为10个类别，其中50,000张为训练集，10,000张为测试集。
 
-    \item \textbf{微调模型}：我们采用CLIP的CLIP-ViT-B/32\cite{huggingface_clip}模型作为微调所使用的预训练模型。CLIP是一种通过对比学习在文本和图像数据上进行预训练的模型，能将自然语言和视觉信息映射到同一特征空间中。CLIP-ViT-B/32基于ViT\cite{vit}架构，包含12层Transformer编码器，隐藏层维度为768，多头注意力头数为12，使用32x32的图像块作为输入。在微调过程中，我们使用LORA\cite{lora}方案仅在Vision Encoder部分插入低秩矩阵，保持Textual Encoder不变。我们设定低秩矩阵的秩为16，学习率为$10^{-3}$，以在有限计算资源下高效微调模型，使其更好地适应特定任务的数据分布。
+    \item \textbf{微调模型}：我们采用CLIP的CLIP-ViT-B/32\cite{huggingface_clip}模型作为微调所使用的预训练模型。CLIP是一种通过对比学习在文本和图像数据上进行预训练的模型，能将自然语言和视觉信息映射到同一特征空间中。CLIP-ViT-B/32基于ViT\cite{vit}架构，包含12层Transformer编码器，隐藏层维度为768，多头注意力头数为12，使用32x32的图像块作为输入。在微调过程中，我们使用LORA\cite{lora}方案仅在Vision Encoder模块插入低秩矩阵，保持Textual Encoder模块不变。我们设定低秩矩阵的秩为16，学习率为$10^{-4}$，以在有限计算资源下高效微调模型，使其更好地适应特定任务的数据分布。
 
@@
 
-    % \item \textbf{联邦相关机制（聚合算法）}：我们采用了经典的联邦平均（Federated Averaging, FedAvg）算法作为聚合机制。FedAvg算法通过聚合每个客户端在本地计算的模型更新，来生成全局模型。
-
 \end{itemize}
-
-\subsection{硬件设施}
-
-本实验在一台Windows操作系统的服务器上进行，28核心128GB内存，以及2块NVIDIA GeForce RTX 3090 GPU(24G)。
 

### 2024-09-18 temp.mouse.1.py
arcihve: final.初稿
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,20 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-08 02:53:30
-LastEditors: LetMeFly
-LastEditTime: 2024-09-08 02:53:41
-'''
-from pynput import mouse
-import pyautogui
-
-# 定义鼠标单击事件的回调函数
-def on_click(x, y, button, pressed):
-    if button == mouse.Button.left and pressed:  # 只处理左键按下事件
-        # 获取当前鼠标位置
-        current_position = pyautogui.position()
-        print(f"鼠标当前位置: {current_position}")
-        return False  # 返回False以停止监听器
-
-# 监听鼠标事件
-with mouse.Listener(on_click=on_click) as listener:
-    listener.join()

### 2024-09-18 temp.mouse.2.py

@@ -1,62 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-08 02:58:47
-LastEditors: LetMeFly
-LastEditTime: 2024-09-08 03:15:04
-'''
-import pyautogui
-import time
-from datetime import datetime, timedelta
-from ctypes import windll
-
-# 定义Chrome和微信窗口的点击位置
-chrome_position = (383, 291)
-wechat_position = (1184, 748)
-
-def perform_actions():
-    # 移动鼠标到Chrome窗口的指定位置并点击
-    pyautogui.moveTo(chrome_position[0], chrome_position[1], duration=0.5)
-    pyautogui.click()
-
-    # 输入快捷键 Ctrl+A 和 Ctrl+V
-    pyautogui.hotkey('ctrl', 'a')
-    time.sleep(0.5)
-    pyautogui.hotkey('ctrl', 'v')
-    time.sleep(0.5)
-    pyautogui.hotkey('ctrl', 's')
-
-    # 等待时间（切换到微信窗口的时间）
-    time.sleep(3)
-
-    # 移动鼠标到微信窗口的指定位置并点击
-    pyautogui.moveTo(wechat_position[0], wechat_position[1], duration=0.5)
-    pyautogui.click()
-
-    # 输入回车键
-    pyautogui.press('enter')
-
-    # 等待几秒后执行锁屏操作
-    time.sleep(5)
-    # pyautogui.hotkey('win', 'l')
-    user32 = windll.LoadLibrary('user32.dll')
-    user32.LockWorkStation()
-
-# 计算从当前时间到下一个凌晨3点02分的时间差
-now = datetime.now()
-target_time = now.replace(hour=6, minute=12, second=0, microsecond=0)
-
-# 如果当前时间已经过了今天的3点02分，则计算到明天3点02分的时间
-if now > target_time:
-    target_time += timedelta(days=1)
-
-# 计算等待时间（秒）
-wait_time = (target_time - now).total_seconds()
-print(f"将休眠 {wait_time} 秒，直到 {target_time} 执行操作...")
-
-# 休眠直到指定时间
-time.sleep(wait_time)
-
-# 执行所有操作
-perform_actions()
-
-print("操作已完成！")

### 2024-09-18 temp.sgd.py

@@ -1,38 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-06 15:38:44
-LastEditors: LetMeFly
-LastEditTime: 2024-09-06 15:38:52
-'''
-import matplotlib.pyplot as plt
-import numpy as np
-
-# 创建数据
-x = np.linspace(-3, 3, 100)
-y = np.linspace(-3, 3, 100)
-X, Y = np.meshgrid(x, y)
-Z = X**2 + Y**2  # 损失函数的例子，这里使用了一个简单的二次函数
-
-# 绘制等高线图
-plt.figure(figsize=(6, 6))
-plt.contour(X, Y, Z, levels=20, cmap='RdGy')
-
-# 绘制梯度下降路径
-x_path = [-2, -1.5, -1, -0.7, -0.5, -0.3, -0.1, 0]
-y_path = [-2, -1.2, -0.8, -0.5, -0.3, -0.1, -0.05, 0]
-plt.plot(x_path, y_path, marker='o', color='blue', linestyle='-', linewidth=1, markersize=5)
-
-# 标注起点和终点
-plt.text(x_path[0], y_path[0], 'Start', fontsize=12, ha='right')
-plt.text(x_path[-1], y_path[-1], 'End', fontsize=12, ha='left')
-
-# 设置图形标题和坐标轴
-plt.title('Gradient Descent Path on Contour Plot')
-plt.xlabel('X')
-plt.ylabel('Y')
-
-# 保存为SVG文件
-plt.savefig('gradient_descent.svg', format='svg')
-
-# 显示图形
-plt.show()

### 2024-09-18 tempCodes/temp.234.01.py

@@ -1,0 +1,106 @@
+'''
+Author: LetMeFly
+Date: 2024-09-10 02:07:00
+LastEditors: LetMeFly
+LastEditTime: 2024-09-10 02:29:13
+'''
+import numpy as np
+from sklearn.neighbors import LocalOutlierFactor
+
+# 第二步: 获取意图点 (Obtain the Purpose Intention)
+def obtain_purpose_intention(clients_data, T, zeta, eta_prime, max_iter, lambda_thresh):
+    # 初始化每个客户端的意图点
+    client_intentions = {}
+    
+    for client_id, data in clients_data.items():
+        # 构建射线模型
+        theta_history = data['theta_history']  # T轮次的展平全局模型
+        grad_updates = data['grad_updates']  # T轮次的展平梯度更新
+        
+        # 初始球心为射线起点的几何中心
+        O_i = np.mean(theta_history, axis=0)
+        # 初始半径为球心到射线起点的最大距离
+        r_i = max(np.linalg.norm(O_i - theta_history, axis=1))
+        
+        # 最小覆盖超球迭代
+        for k in range(max_iter):
+            projection_points = []
+            # 计算每个射线的投影点
+            for t in range(T):
+                theta_t = theta_history[t]
+                v_t = grad_updates[t]
+                alpha_k = max(0, np.dot(O_i - theta_t, v_t) / np.dot(v_t, v_t))
+                proj_point = theta_t + alpha_k * v_t
+                projection_points.append(proj_point)
+            
+            # 计算所有投影点到球心的距离
+            distances = np.linalg.norm(O_i - np.array(projection_points), axis=1)
+            # 排序并选择覆盖ζ比例射线的点
+            selected_indices = np.argsort(distances)[:int(zeta * T)]
+            max_proj_point = projection_points[selected_indices[-1]]
+            
+            # 更新球心和半径
+            O_i = O_i + eta_prime * (max_proj_point - O_i)
+            r_new = max(np.linalg.norm(O_i - np.array(projection_points)[selected_indices], axis=1))
+            
+            # 检查收敛条件
+            if abs(r_new - r_i) < lambda_thresh:
+                break
+            
+            r_i = r_new
+        
+        client_intentions[client_id] = {'center': O_i, 'radius': r_i}
+    
+    return client_intentions
+
[…]

### 2024-09-18 tempCodes/temp.234.02.py

@@ -1,0 +1,93 @@
+'''
+Author: LetMeFly
+Date: 2024-09-10 02:34:55
+LastEditors: LetMeFly
+LastEditTime: 2024-09-10 02:34:59
+'''
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.decomposition import PCA
+from sklearn.neighbors import LocalOutlierFactor
+
+# 第二步: 获取意图点 (Obtain the Purpose Intention)
+def obtain_purpose_intention(clients_data, T, zeta, eta_prime, max_iter, lambda_thresh):
+    client_intentions = {}
+    
+    for client_id, data in clients_data.items():
+        theta_history = data['theta_history']  # T轮次的展平全局模型
+        grad_updates = data['grad_updates']  # T轮次的展平梯度更新
+        
+        O_i = np.mean(theta_history, axis=0)
+        r_i = max(np.linalg.norm(O_i - theta_history, axis=1))
+        
+        for k in range(max_iter):
+            projection_points = []
+            for t in range(T):
+                theta_t = theta_history[t]
+                v_t = grad_updates[t]
+                alpha_k = max(0, np.dot(O_i - theta_t, v_t) / np.dot(v_t, v_t))
+                proj_point = theta_t + alpha_k * v_t
+                projection_points.append(proj_point)
+            
+            distances = np.linalg.norm(O_i - np.array(projection_points), axis=1)
+            selected_indices = np.argsort(distances)[:int(zeta * T)]
+            max_proj_point = projection_points[selected_indices[-1]]
+            
+            O_i = O_i + eta_prime * (max_proj_point - O_i)
+            r_new = max(np.linalg.norm(O_i - np.array(projection_points)[selected_indices], axis=1))
+            
+            if abs(r_new - r_i) < lambda_thresh:
+                break
+            
+            r_i = r_new
+        
+        client_intentions[client_id] = {'center': O_i, 'radius': r_i}
+    
+    return client_intentions
+
+# 第三步: 异常检测 (Abnormal Detection)
+def abnormal_detection(client_intentions, k_neighbors=5):
+    intention_points = np.array([v['center'] for v in client_intentions.values()])
+    lof = LocalOutlierFactor(n_neighbors=k_neighbors)
+    lof_scores = lof.fit_predict(intention_points)
+    
[…]

### 2024-09-18 tempCodes/temp.234.03.py

@@ -1,0 +1,103 @@
+'''
+Author: LetMeFly
+Date: 2024-09-10 02:35:55
+LastEditors: LetMeFly
+LastEditTime: 2024-09-10 02:36:52
+'''
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.decomposition import PCA
+from sklearn.neighbors import LocalOutlierFactor
+
+# 第二步: 获取意图点 (Obtain the Purpose Intention)
+def obtain_purpose_intention(clients_data, T, zeta, eta_prime, max_iter, lambda_thresh):
+    client_intentions = {}
+    
+    for client_id, data in clients_data.items():
+        theta_history = data['theta_history']  # T轮次的展平全局模型
+        grad_updates = data['grad_updates']  # T轮次的展平梯度更新
+        
+        O_i = np.mean(theta_history, axis=0)
+        r_i = max(np.linalg.norm(O_i - theta_history, axis=1))
+        
+        for k in range(max_iter):
+            projection_points = []
+            for t in range(T):
+                theta_t = theta_history[t]
+                v_t = grad_updates[t]
+                alpha_k = max(0, np.dot(O_i - theta_t, v_t) / np.dot(v_t, v_t))
+                proj_point = theta_t + alpha_k * v_t
+                projection_points.append(proj_point)
+            
+            distances = np.linalg.norm(O_i - np.array(projection_points), axis=1)
+            selected_indices = np.argsort(distances)[:int(zeta * T)]
+            max_proj_point = projection_points[selected_indices[-1]]
+            
+            O_i = O_i + eta_prime * (max_proj_point - O_i)
+            r_new = max(np.linalg.norm(O_i - np.array(projection_points)[selected_indices], axis=1))
+            
+            if abs(r_new - r_i) < lambda_thresh:
+                break
+            
+            r_i = r_new
+        
+        client_intentions[client_id] = {'center': O_i, 'radius': r_i}
+    
+    return client_intentions
+
+# 第三步: 异常检测 (Abnormal Detection)
+def abnormal_detection(client_intentions, k_neighbors=5):
+    intention_points = np.array([v['center'] for v in client_intentions.values()])
+    lof = LocalOutlierFactor(n_neighbors=k_neighbors)
+    lof_scores = lof.fit_predict(intention_points)
+    
[…]

### 2024-09-18 tempCodes/temp.234.04.ok.py

@@ -1,0 +1,112 @@
+'''
+Author: LetMeFly
+Date: 2024-09-10 02:38:05
+LastEditors: LetMeFly
+LastEditTime: 2024-09-10 02:38:43
+'''
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.decomposition import PCA
+from sklearn.neighbors import LocalOutlierFactor
+
+# 第二步: 获取意图点 (Obtain the Purpose Intention)
+def obtain_purpose_intention(clients_data, T, zeta, eta_prime, max_iter, lambda_thresh):
+    client_intentions = {}
+    
+    for client_id, data in clients_data.items():
+        theta_history = data['theta_history']  # T轮次的展平全局模型
+        grad_updates = data['grad_updates']  # T轮次的展平梯度更新
+        
+        O_i = np.mean(theta_history, axis=0)
+        r_i = max(np.linalg.norm(O_i - theta_history, axis=1))
+        
+        for k in range(max_iter):
+            projection_points = []
+            for t in range(T):
+                theta_t = theta_history[t]
+                v_t = grad_updates[t]
+                alpha_k = max(0, np.dot(O_i - theta_t, v_t) / np.dot(v_t, v_t))
+                proj_point = theta_t + alpha_k * v_t
+                projection_points.append(proj_point)
+            
+            distances = np.linalg.norm(O_i - np.array(projection_points), axis=1)
+            selected_indices = np.argsort(distances)[:int(zeta * T)]
+            max_proj_point = projection_points[selected_indices[-1]]
+            
+            O_i = O_i + eta_prime * (max_proj_point - O_i)
+            r_new = max(np.linalg.norm(O_i - np.array(projection_points)[selected_indices], axis=1))
+            
+            if abs(r_new - r_i) < lambda_thresh:
+                break
+            
+            r_i = r_new
+        
+        client_intentions[client_id] = {'center': O_i, 'radius': r_i}
+    
+    return client_intentions
+
+# 第三步: 异常检测 (Abnormal Detection)
+def abnormal_detection(client_intentions, k_neighbors=5):
+    intention_points = np.array([v['center'] for v in client_intentions.values()])
+    lof = LocalOutlierFactor(n_neighbors=k_neighbors)
+    lof_scores = lof.fit_predict(intention_points)
[…]

### 2024-09-18 tempCodes/temp.format.py

@@ -1,0 +1,9 @@
+'''
+Author: LetMeFly
+Date: 2024-09-09 19:33:37
+LastEditors: LetMeFly
+LastEditTime: 2024-09-09 19:34:34
+'''
+a = 1
+f = 3.2
+print(f'{a:7}\t{f:10f}')

### 2024-09-18 tempCodes/temp.print.py

@@ -1,0 +1,8 @@
+'''
+Author: LetMeFly
+Date: 2024-09-12 23:19:41
+LastEditors: LetMeFly
+LastEditTime: 2024-09-12 23:20:03
+'''
+for i in range(50):
+    print(i, end=',')

### 2024-09-18 tempCodes/temp.relitu.py

@@ -1,0 +1,19 @@
+'''
+Author: LetMeFly
+Date: 2024-09-12 16:54:05
+LastEditors: LetMeFly
+LastEditTime: 2024-09-13 21:07:37
+'''
+import matplotlib.pyplot as plt
+import seaborn as sns
+import numpy as np
+
+# 生成示例数据
+data = np.random.rand(10, 12)  # 10 行 12 列的随机数据
+
+# 创建热力图
+plt.figure(figsize=(10, 8))  # 设置图表大小
+sns.heatmap(data, annot=True, cmap='YlGnBu')  # 使用绿色到蓝色的渐变配色
+plt.title('Heatmap Example')  # 设置标题
+plt.show()  # 显示热力图
+plt.savefig('temp.relitu.jpg', format='jpg')

### 2024-09-18 tempCodes/temp.relitu2.py

@@ -1,0 +1,55 @@
+'''
+Author: LetMeFly
+Date: 2024-09-13 22:56:00
+LastEditors: LetMeFly
+LastEditTime: 2024-09-13 23:07:43
+'''
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+# 生成模拟数据
+def generate_heatmap_data(num_clients=20, num_malicious=4):
+    data = np.random.rand(num_clients, num_clients)  # 随机生成数据
+    
+    # 模拟恶意客户端和良性客户端的识别情况
+    # 恶意客户端的相似度较高，良性客户端的相似度较低
+    for i in range(num_clients):
+        for j in range(num_clients):
+            if i < num_malicious and j < num_malicious:  # 恶意客户端之间的高相似度
+                data[i, j] = np.random.uniform(0.7, 1.0)
+            elif i >= num_malicious and j >= num_malicious:  # 良性客户端之间的低相似度
+                data[i, j] = np.random.uniform(0.0, 0.3)
+            else:  # 恶意和良性之间的相似度中等
+                data[i, j] = np.random.uniform(0.3, 0.7)
+    # print(data)
+    # exit(0)
+    return data
+
+# 创建图像和子图
+fig, axes = plt.subplots(nrows=2, ncols=4, figsize=(20, 10))
+
+# 标题和标签
+attacks = ['Attack A', 'Attack B']
+methods = ['Cosine Similarity Detection', 'FLTrust', 'FLAME', 'SecFFT']
+
+# 生成热力图数据并绘制
+for i in range(2):  # 两行，分别为Attack A和Attack B
+    for j in range(4):  # 四列，分别为四种方法
+        # 生成模拟数据
+        heatmap_data = generate_heatmap_data()
+        ax = axes[i, j]
+        
+        # 绘制热力图
+        sns.heatmap(heatmap_data, ax=ax, cmap='coolwarm', cbar=False)
+        
+        # 设置标题
+        ax.set_title(f'{attacks[i]} - {methods[j]}', fontsize=12)
+        ax.set_xlabel('Client Index', fontsize=10)
+        ax.set_ylabel('Client Index', fontsize=10)
+
+# 调整子图布局
+plt.tight_layout()
+
+# 保存为jpg文件
+plt.savefig('temp.relitu.2x4.jpg', format='jpg')

### 2024-09-18 tempCodes/temp.relitu3.py

@@ -1,0 +1,54 @@
+'''
+Author: LetMeFly
+Date: 2024-09-13 23:38:43
+LastEditors: LetMeFly
+LastEditTime: 2024-09-13 23:39:17
+'''
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+# 生成模拟数据
+def generate_score_data(num_clients=20, num_malicious=4):
+    scores = np.random.rand(num_clients)  # 随机生成评分
+    
+    # 模拟恶意客户端和良性客户端的评分情况
+    # 恶意客户端评分较高，良性客户端评分较低
+    for i in range(num_clients):
+        if i < num_malicious:  # 恶意客户端
+            scores[i] = np.random.uniform(0.7, 1.0)
+        else:  # 良性客户端
+            scores[i] = np.random.uniform(0.0, 0.3)
+    
+    return scores
+
+# 创建图像和子图
+fig, axes = plt.subplots(nrows=2, ncols=4, figsize=(20, 10))
+
+# 标题和标签
+attacks = ['Attack A', 'Attack B']
+methods = ['Cosine Similarity Detection', 'FLTrust', 'FLAME', 'SecFFT']
+
+# 生成热力图数据并绘制
+for i in range(2):  # 两行，分别为Attack A和Attack B
+    for j in range(4):  # 四列，分别为四种方法
+        # 生成模拟数据
+        scores = generate_score_data()
+        ax = axes[i, j]
+        
+        # 生成一维热力图数据
+        heatmap_data = scores.reshape(1, -1)
+        
+        # 绘制热力图
+        sns.heatmap(heatmap_data, ax=ax, cmap='coolwarm', cbar=False, annot=True)
+        
+        # 设置标题和轴标签
+        ax.set_title(f'{attacks[i]} - {methods[j]}', fontsize=12)
+        ax.set_xlabel('Client Index', fontsize=10)
+        ax.set_yticks([])  # 隐藏y轴刻度
+
+# 调整子图布局
+plt.tight_layout()
+
+# 保存为jpg文件
+plt.savefig('detection_results.jpg', format='jpg')

### 2024-09-18 tempCodes/temp.relitu4-kexing.py

@@ -1,0 +1,66 @@
+'''
+Author: LetMeFly
+Date: 2024-09-13 23:43:25
+LastEditors: LetMeFly
+LastEditTime: 2024-09-13 23:43:28
+'''
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+# 生成模拟数据的评分
+def generate_score_data(num_clients=20, num_malicious=4):
+    scores = np.random.rand(num_clients)  # 随机生成评分
+    
+    # 模拟恶意客户端和良性客户端的评分情况
+    # 恶意客户端评分较高，良性客户端评分较低
+    for i in range(num_clients):
+        if i < num_malicious:  # 恶意客户端
+            scores[i] = np.random.uniform(0.7, 1.0)
+        else:  # 良性客户端
+            scores[i] = np.random.uniform(0.0, 0.3)
+    
+    return scores
+
+# 生成两两客户端对比矩阵 (这里使用绝对差值作为示例)
+def generate_comparison_matrix(scores):
+    num_clients = len(scores)
+    comparison_matrix = np.zeros((num_clients, num_clients))
+    
+    # 计算客户端对之间的评分差异
+    for i in range(num_clients):
+        for j in range(num_clients):
+            comparison_matrix[i, j] = abs(scores[i] - scores[j])  # 使用绝对差值
+            
+    return comparison_matrix
+
+# 创建图像和子图
+fig, axes = plt.subplots(nrows=2, ncols=4, figsize=(20, 10))
+
+# 标题和标签
+attacks = ['Attack A', 'Attack B']
+methods = ['Cosine Similarity Detection', 'FLTrust', 'FLAME', 'SecFFT']
+
+# 生成热力图数据并绘制
+for i in range(2):  # 两行，分别为Attack A和Attack B
+    for j in range(4):  # 四列，分别为四种方法
+        # 生成模拟评分数据
+        scores = generate_score_data()
+        
+        # 生成两两对比矩阵
+        comparison_matrix = generate_comparison_matrix(scores)
+        ax = axes[i, j]
+        
+        # 绘制热力图
+        sns.heatmap(comparison_matrix, ax=ax, cmap='coolwarm', cbar=True, annot=False)
+        
+        # 设置标题和轴标签
+        ax.set_title(f'{attacks[i]} - {methods[j]}', fontsize=12)
+        ax.set_xlabel('Client Index', fontsize=10)
[…]

### 2024-09-18 tempCodes/temp.score-kexing.py

@@ -1,0 +1,60 @@
+'''
+Author: LetMeFly
+Date: 2024-09-14 00:47:51
+LastEditors: LetMeFly
+LastEditTime: 2024-09-14 00:48:24
+'''
+from sklearn.metrics import matthews_corrcoef, roc_auc_score
+
+# 假设共有20个客户端，前4个为恶意客户端
+total_clients = 20
+malicious_clients = {0, 1, 2, 3}  # 实际恶意客户端的索引
+
+# 假设识别出来的恶意客户端结果（可以修改此数组来测试不同情况）
+identified_malicious = [0, 1, 4, 5]  # 被识别为恶意的客户端索引
+
+# 计算TP, FP, TN, FN
+TP = len(malicious_clients.intersection(identified_malicious))
+FP = len(set(identified_malicious) - malicious_clients)
+FN = len(malicious_clients - set(identified_malicious))
+TN = total_clients - TP - FP - FN
+
+# 准确率（Accuracy）
+accuracy = (TP + TN) / total_clients
+
+# 精确率（Precision）
+precision = TP / (TP + FP) if (TP + FP) > 0 else 0
+
+# 召回率（Recall）
+recall = TP / (TP + FN) if (TP + FN) > 0 else 0
+
+# 特异度（Specificity）
+specificity = TN / (TN + FP) if (TN + FP) > 0 else 0
+
+# 误报率（False Positive Rate, FPR）
+fpr = FP / (FP + TN) if (FP + TN) > 0 else 0
+
+# 假阴率（False Negative Rate, FNR）
+fnr = FN / (TP + FN) if (TP + FN) > 0 else 0
+
+# 计算AUC（此处假设预测的概率值，以便计算AUC）
+y_true = [1 if i in malicious_clients else 0 for i in range(total_clients)]
+y_scores = [1 if i in identified_malicious else 0 for i in range(total_clients)]
+auc = roc_auc_score(y_true, y_scores)
+
+# 计算MCC（Matthews Correlation Coefficient）
+mcc = matthews_corrcoef(y_true, y_scores)
+
+# 打印结果
+print(f"TP (True Positive): {TP}")
+print(f"FP (False Positive): {FP}")
+print(f"FN (False Negative): {FN}")
+print(f"TN (True Negative): {TN}")
+print(f"准确率（Accuracy）: {accuracy:.2f}")
+print(f"精确率（Precision）: {precision:.2f}")
[…]

### 2024-09-18 tempCodes/temp.score.verify.py

@@ -1,0 +1,64 @@
+'''
+Author: LetMeFly
+Date: 2024-09-14 00:47:51
+LastEditors: LetMeFly
+LastEditTime: 2024-09-15 10:34:39
+'''
+from sklearn.metrics import matthews_corrcoef, roc_auc_score
+
+# 假设共有20个客户端，前4个为恶意客户端
+total_clients = 20
+malicious_clients = {0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14}  # 实际恶意客户端的索引
+
+# 假设识别出来的恶意客户端结果（可以修改此数组来测试不同情况）
+identified_malicious = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]  # 被识别为恶意的客户端索引
+
+# 计算TP, FP, TN, FN
+TP = len(malicious_clients.intersection(identified_malicious))
+FP = len(set(identified_malicious) - malicious_clients)
+FN = len(malicious_clients - set(identified_malicious))
+TN = total_clients - TP - FP - FN
+
+total_clients = 50
+TP, FP, TN, FN = 13, 0, 35, 2
+
+
+# 准确率（Accuracy）
+accuracy = (TP + TN) / total_clients
+
+# 精确率（Precision）
+precision = TP / (TP + FP) if (TP + FP) > 0 else 0
+
+# 召回率（Recall）
+recall = TP / (TP + FN) if (TP + FN) > 0 else 0
+
+# 特异度（Specificity）
+specificity = TN / (TN + FP) if (TN + FP) > 0 else 0
+
+# 误报率（False Positive Rate, FPR）
+fpr = FP / (FP + TN) if (FP + TN) > 0 else 0
+
+# 假阴率（False Negative Rate, FNR）
+fnr = FN / (TP + FN) if (TP + FN) > 0 else 0
+
+# 计算AUC（此处假设预测的概率值，以便计算AUC）
+y_true = [1 if i in malicious_clients else 0 for i in range(total_clients)]
+y_scores = [1 if i in identified_malicious else 0 for i in range(total_clients)]
+auc = roc_auc_score(y_true, y_scores)
+
+# 计算MCC（Matthews Correlation Coefficient）
+mcc = matthews_corrcoef(y_true, y_scores)
+
+# 打印结果
+print(f"TP (True Positive): {TP}")
+print(f"FP (False Positive): {FP}")
[…]

### 2024-09-19 tempCodes/temp.234.01.py
tmp: before merge(pr of) branch z.001.tip-adapter
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,106 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-10 02:07:00
-LastEditors: LetMeFly
-LastEditTime: 2024-09-10 02:29:13
-'''
-import numpy as np
-from sklearn.neighbors import LocalOutlierFactor
-
-# 第二步: 获取意图点 (Obtain the Purpose Intention)
-def obtain_purpose_intention(clients_data, T, zeta, eta_prime, max_iter, lambda_thresh):
-    # 初始化每个客户端的意图点
-    client_intentions = {}
-    
-    for client_id, data in clients_data.items():
-        # 构建射线模型
-        theta_history = data['theta_history']  # T轮次的展平全局模型
-        grad_updates = data['grad_updates']  # T轮次的展平梯度更新
-        
-        # 初始球心为射线起点的几何中心
-        O_i = np.mean(theta_history, axis=0)
-        # 初始半径为球心到射线起点的最大距离
-        r_i = max(np.linalg.norm(O_i - theta_history, axis=1))
-        
-        # 最小覆盖超球迭代
-        for k in range(max_iter):
-            projection_points = []
-            # 计算每个射线的投影点
-            for t in range(T):
-                theta_t = theta_history[t]
-                v_t = grad_updates[t]
-                alpha_k = max(0, np.dot(O_i - theta_t, v_t) / np.dot(v_t, v_t))
-                proj_point = theta_t + alpha_k * v_t
-                projection_points.append(proj_point)
-            
-            # 计算所有投影点到球心的距离
-            distances = np.linalg.norm(O_i - np.array(projection_points), axis=1)
-            # 排序并选择覆盖ζ比例射线的点
-            selected_indices = np.argsort(distances)[:int(zeta * T)]
-            max_proj_point = projection_points[selected_indices[-1]]
-            
-            # 更新球心和半径
-            O_i = O_i + eta_prime * (max_proj_point - O_i)
-            r_new = max(np.linalg.norm(O_i - np.array(projection_points)[selected_indices], axis=1))
-            
-            # 检查收敛条件
-            if abs(r_new - r_i) < lambda_thresh:
-                break
-            
-            r_i = r_new
-        
-        client_intentions[client_id] = {'center': O_i, 'radius': r_i}
-    
-    return client_intentions
-
[…]

### 2024-09-19 tempCodes/temp.234.02.py

@@ -1,93 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-10 02:34:55
-LastEditors: LetMeFly
-LastEditTime: 2024-09-10 02:34:59
-'''
-import numpy as np
-import matplotlib.pyplot as plt
-from sklearn.decomposition import PCA
-from sklearn.neighbors import LocalOutlierFactor
-
-# 第二步: 获取意图点 (Obtain the Purpose Intention)
-def obtain_purpose_intention(clients_data, T, zeta, eta_prime, max_iter, lambda_thresh):
-    client_intentions = {}
-    
-    for client_id, data in clients_data.items():
-        theta_history = data['theta_history']  # T轮次的展平全局模型
-        grad_updates = data['grad_updates']  # T轮次的展平梯度更新
-        
-        O_i = np.mean(theta_history, axis=0)
-        r_i = max(np.linalg.norm(O_i - theta_history, axis=1))
-        
-        for k in range(max_iter):
-            projection_points = []
-            for t in range(T):
-                theta_t = theta_history[t]
-                v_t = grad_updates[t]
-                alpha_k = max(0, np.dot(O_i - theta_t, v_t) / np.dot(v_t, v_t))
-                proj_point = theta_t + alpha_k * v_t
-                projection_points.append(proj_point)
-            
-            distances = np.linalg.norm(O_i - np.array(projection_points), axis=1)
-            selected_indices = np.argsort(distances)[:int(zeta * T)]
-            max_proj_point = projection_points[selected_indices[-1]]
-            
-            O_i = O_i + eta_prime * (max_proj_point - O_i)
-            r_new = max(np.linalg.norm(O_i - np.array(projection_points)[selected_indices], axis=1))
-            
-            if abs(r_new - r_i) < lambda_thresh:
-                break
-            
-            r_i = r_new
-        
-        client_intentions[client_id] = {'center': O_i, 'radius': r_i}
-    
-    return client_intentions
-
-# 第三步: 异常检测 (Abnormal Detection)
-def abnormal_detection(client_intentions, k_neighbors=5):
-    intention_points = np.array([v['center'] for v in client_intentions.values()])
-    lof = LocalOutlierFactor(n_neighbors=k_neighbors)
-    lof_scores = lof.fit_predict(intention_points)
-    
[…]

### 2024-09-19 tempCodes/temp.234.03.py

@@ -1,103 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-10 02:35:55
-LastEditors: LetMeFly
-LastEditTime: 2024-09-10 02:36:52
-'''
-import numpy as np
-import matplotlib.pyplot as plt
-from sklearn.decomposition import PCA
-from sklearn.neighbors import LocalOutlierFactor
-
-# 第二步: 获取意图点 (Obtain the Purpose Intention)
-def obtain_purpose_intention(clients_data, T, zeta, eta_prime, max_iter, lambda_thresh):
-    client_intentions = {}
-    
-    for client_id, data in clients_data.items():
-        theta_history = data['theta_history']  # T轮次的展平全局模型
-        grad_updates = data['grad_updates']  # T轮次的展平梯度更新
-        
-        O_i = np.mean(theta_history, axis=0)
-        r_i = max(np.linalg.norm(O_i - theta_history, axis=1))
-        
-        for k in range(max_iter):
-            projection_points = []
-            for t in range(T):
-                theta_t = theta_history[t]
-                v_t = grad_updates[t]
-                alpha_k = max(0, np.dot(O_i - theta_t, v_t) / np.dot(v_t, v_t))
-                proj_point = theta_t + alpha_k * v_t
-                projection_points.append(proj_point)
-            
-            distances = np.linalg.norm(O_i - np.array(projection_points), axis=1)
-            selected_indices = np.argsort(distances)[:int(zeta * T)]
-            max_proj_point = projection_points[selected_indices[-1]]
-            
-            O_i = O_i + eta_prime * (max_proj_point - O_i)
-            r_new = max(np.linalg.norm(O_i - np.array(projection_points)[selected_indices], axis=1))
-            
-            if abs(r_new - r_i) < lambda_thresh:
-                break
-            
-            r_i = r_new
-        
-        client_intentions[client_id] = {'center': O_i, 'radius': r_i}
-    
-    return client_intentions
-
-# 第三步: 异常检测 (Abnormal Detection)
-def abnormal_detection(client_intentions, k_neighbors=5):
-    intention_points = np.array([v['center'] for v in client_intentions.values()])
-    lof = LocalOutlierFactor(n_neighbors=k_neighbors)
-    lof_scores = lof.fit_predict(intention_points)
-    
[…]

### 2024-09-19 tempCodes/temp.234.04.ok.py

@@ -1,112 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-10 02:38:05
-LastEditors: LetMeFly
-LastEditTime: 2024-09-10 02:38:43
-'''
-import numpy as np
-import matplotlib.pyplot as plt
-from sklearn.decomposition import PCA
-from sklearn.neighbors import LocalOutlierFactor
-
-# 第二步: 获取意图点 (Obtain the Purpose Intention)
-def obtain_purpose_intention(clients_data, T, zeta, eta_prime, max_iter, lambda_thresh):
-    client_intentions = {}
-    
-    for client_id, data in clients_data.items():
-        theta_history = data['theta_history']  # T轮次的展平全局模型
-        grad_updates = data['grad_updates']  # T轮次的展平梯度更新
-        
-        O_i = np.mean(theta_history, axis=0)
-        r_i = max(np.linalg.norm(O_i - theta_history, axis=1))
-        
-        for k in range(max_iter):
-            projection_points = []
-            for t in range(T):
-                theta_t = theta_history[t]
-                v_t = grad_updates[t]
-                alpha_k = max(0, np.dot(O_i - theta_t, v_t) / np.dot(v_t, v_t))
-                proj_point = theta_t + alpha_k * v_t
-                projection_points.append(proj_point)
-            
-            distances = np.linalg.norm(O_i - np.array(projection_points), axis=1)
-            selected_indices = np.argsort(distances)[:int(zeta * T)]
-            max_proj_point = projection_points[selected_indices[-1]]
-            
-            O_i = O_i + eta_prime * (max_proj_point - O_i)
-            r_new = max(np.linalg.norm(O_i - np.array(projection_points)[selected_indices], axis=1))
-            
-            if abs(r_new - r_i) < lambda_thresh:
-                break
-            
-            r_i = r_new
-        
-        client_intentions[client_id] = {'center': O_i, 'radius': r_i}
-    
-    return client_intentions
-
-# 第三步: 异常检测 (Abnormal Detection)
-def abnormal_detection(client_intentions, k_neighbors=5):
-    intention_points = np.array([v['center'] for v in client_intentions.values()])
-    lof = LocalOutlierFactor(n_neighbors=k_neighbors)
-    lof_scores = lof.fit_predict(intention_points)
[…]

### 2024-09-19 tempCodes/temp.format.py

@@ -1,9 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-09 19:33:37
-LastEditors: LetMeFly
-LastEditTime: 2024-09-09 19:34:34
-'''
-a = 1
-f = 3.2
-print(f'{a:7}\t{f:10f}')

### 2024-09-19 tempCodes/temp.print.py

@@ -1,8 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-12 23:19:41
-LastEditors: LetMeFly
-LastEditTime: 2024-09-12 23:20:03
-'''
-for i in range(50):
-    print(i, end=',')

### 2024-09-19 tempCodes/temp.relitu.py

@@ -1,19 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-12 16:54:05
-LastEditors: LetMeFly
-LastEditTime: 2024-09-13 21:07:37
-'''
-import matplotlib.pyplot as plt
-import seaborn as sns
-import numpy as np
-
-# 生成示例数据
-data = np.random.rand(10, 12)  # 10 行 12 列的随机数据
-
-# 创建热力图
-plt.figure(figsize=(10, 8))  # 设置图表大小
-sns.heatmap(data, annot=True, cmap='YlGnBu')  # 使用绿色到蓝色的渐变配色
-plt.title('Heatmap Example')  # 设置标题
-plt.show()  # 显示热力图
-plt.savefig('temp.relitu.jpg', format='jpg')

### 2024-09-19 tempCodes/temp.relitu2.py

@@ -1,55 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-13 22:56:00
-LastEditors: LetMeFly
-LastEditTime: 2024-09-13 23:07:43
-'''
-import numpy as np
-import matplotlib.pyplot as plt
-import seaborn as sns
-
-# 生成模拟数据
-def generate_heatmap_data(num_clients=20, num_malicious=4):
-    data = np.random.rand(num_clients, num_clients)  # 随机生成数据
-    
-    # 模拟恶意客户端和良性客户端的识别情况
-    # 恶意客户端的相似度较高，良性客户端的相似度较低
-    for i in range(num_clients):
-        for j in range(num_clients):
-            if i < num_malicious and j < num_malicious:  # 恶意客户端之间的高相似度
-                data[i, j] = np.random.uniform(0.7, 1.0)
-            elif i >= num_malicious and j >= num_malicious:  # 良性客户端之间的低相似度
-                data[i, j] = np.random.uniform(0.0, 0.3)
-            else:  # 恶意和良性之间的相似度中等
-                data[i, j] = np.random.uniform(0.3, 0.7)
-    # print(data)
-    # exit(0)
-    return data
-
-# 创建图像和子图
-fig, axes = plt.subplots(nrows=2, ncols=4, figsize=(20, 10))
-
-# 标题和标签
-attacks = ['Attack A', 'Attack B']
-methods = ['Cosine Similarity Detection', 'FLTrust', 'FLAME', 'SecFFT']
-
-# 生成热力图数据并绘制
-for i in range(2):  # 两行，分别为Attack A和Attack B
-    for j in range(4):  # 四列，分别为四种方法
-        # 生成模拟数据
-        heatmap_data = generate_heatmap_data()
-        ax = axes[i, j]
-        
-        # 绘制热力图
-        sns.heatmap(heatmap_data, ax=ax, cmap='coolwarm', cbar=False)
-        
-        # 设置标题
-        ax.set_title(f'{attacks[i]} - {methods[j]}', fontsize=12)
-        ax.set_xlabel('Client Index', fontsize=10)
-        ax.set_ylabel('Client Index', fontsize=10)
-
-# 调整子图布局
-plt.tight_layout()
-
-# 保存为jpg文件
-plt.savefig('temp.relitu.2x4.jpg', format='jpg')

### 2024-09-19 tempCodes/temp.relitu3.py

@@ -1,54 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-13 23:38:43
-LastEditors: LetMeFly
-LastEditTime: 2024-09-13 23:39:17
-'''
-import numpy as np
-import matplotlib.pyplot as plt
-import seaborn as sns
-
-# 生成模拟数据
-def generate_score_data(num_clients=20, num_malicious=4):
-    scores = np.random.rand(num_clients)  # 随机生成评分
-    
-    # 模拟恶意客户端和良性客户端的评分情况
-    # 恶意客户端评分较高，良性客户端评分较低
-    for i in range(num_clients):
-        if i < num_malicious:  # 恶意客户端
-            scores[i] = np.random.uniform(0.7, 1.0)
-        else:  # 良性客户端
-            scores[i] = np.random.uniform(0.0, 0.3)
-    
-    return scores
-
-# 创建图像和子图
-fig, axes = plt.subplots(nrows=2, ncols=4, figsize=(20, 10))
-
-# 标题和标签
-attacks = ['Attack A', 'Attack B']
-methods = ['Cosine Similarity Detection', 'FLTrust', 'FLAME', 'SecFFT']
-
-# 生成热力图数据并绘制
-for i in range(2):  # 两行，分别为Attack A和Attack B
-    for j in range(4):  # 四列，分别为四种方法
-        # 生成模拟数据
-        scores = generate_score_data()
-        ax = axes[i, j]
-        
-        # 生成一维热力图数据
-        heatmap_data = scores.reshape(1, -1)
-        
-        # 绘制热力图
-        sns.heatmap(heatmap_data, ax=ax, cmap='coolwarm', cbar=False, annot=True)
-        
-        # 设置标题和轴标签
-        ax.set_title(f'{attacks[i]} - {methods[j]}', fontsize=12)
-        ax.set_xlabel('Client Index', fontsize=10)
-        ax.set_yticks([])  # 隐藏y轴刻度
-
-# 调整子图布局
-plt.tight_layout()
-
-# 保存为jpg文件
-plt.savefig('detection_results.jpg', format='jpg')

### 2024-09-19 tempCodes/temp.relitu4-kexing.py

@@ -1,66 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-13 23:43:25
-LastEditors: LetMeFly
-LastEditTime: 2024-09-13 23:43:28
-'''
-import numpy as np
-import matplotlib.pyplot as plt
-import seaborn as sns
-
-# 生成模拟数据的评分
-def generate_score_data(num_clients=20, num_malicious=4):
-    scores = np.random.rand(num_clients)  # 随机生成评分
-    
-    # 模拟恶意客户端和良性客户端的评分情况
-    # 恶意客户端评分较高，良性客户端评分较低
-    for i in range(num_clients):
-        if i < num_malicious:  # 恶意客户端
-            scores[i] = np.random.uniform(0.7, 1.0)
-        else:  # 良性客户端
-            scores[i] = np.random.uniform(0.0, 0.3)
-    
-    return scores
-
-# 生成两两客户端对比矩阵 (这里使用绝对差值作为示例)
-def generate_comparison_matrix(scores):
-    num_clients = len(scores)
-    comparison_matrix = np.zeros((num_clients, num_clients))
-    
-    # 计算客户端对之间的评分差异
-    for i in range(num_clients):
-        for j in range(num_clients):
-            comparison_matrix[i, j] = abs(scores[i] - scores[j])  # 使用绝对差值
-            
-    return comparison_matrix
-
-# 创建图像和子图
-fig, axes = plt.subplots(nrows=2, ncols=4, figsize=(20, 10))
-
-# 标题和标签
-attacks = ['Attack A', 'Attack B']
-methods = ['Cosine Similarity Detection', 'FLTrust', 'FLAME', 'SecFFT']
-
-# 生成热力图数据并绘制
-for i in range(2):  # 两行，分别为Attack A和Attack B
-    for j in range(4):  # 四列，分别为四种方法
-        # 生成模拟评分数据
-        scores = generate_score_data()
-        
-        # 生成两两对比矩阵
-        comparison_matrix = generate_comparison_matrix(scores)
-        ax = axes[i, j]
-        
-        # 绘制热力图
-        sns.heatmap(comparison_matrix, ax=ax, cmap='coolwarm', cbar=True, annot=False)
-        
-        # 设置标题和轴标签
-        ax.set_title(f'{attacks[i]} - {methods[j]}', fontsize=12)
-        ax.set_xlabel('Client Index', fontsize=10)
[…]

### 2024-09-19 tempCodes/temp.score-kexing.py

@@ -1,60 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-14 00:47:51
-LastEditors: LetMeFly
-LastEditTime: 2024-09-14 00:48:24
-'''
-from sklearn.metrics import matthews_corrcoef, roc_auc_score
-
-# 假设共有20个客户端，前4个为恶意客户端
-total_clients = 20
-malicious_clients = {0, 1, 2, 3}  # 实际恶意客户端的索引
-
-# 假设识别出来的恶意客户端结果（可以修改此数组来测试不同情况）
-identified_malicious = [0, 1, 4, 5]  # 被识别为恶意的客户端索引
-
-# 计算TP, FP, TN, FN
-TP = len(malicious_clients.intersection(identified_malicious))
-FP = len(set(identified_malicious) - malicious_clients)
-FN = len(malicious_clients - set(identified_malicious))
-TN = total_clients - TP - FP - FN
-
-# 准确率（Accuracy）
-accuracy = (TP + TN) / total_clients
-
-# 精确率（Precision）
-precision = TP / (TP + FP) if (TP + FP) > 0 else 0
-
-# 召回率（Recall）
-recall = TP / (TP + FN) if (TP + FN) > 0 else 0
-
-# 特异度（Specificity）
-specificity = TN / (TN + FP) if (TN + FP) > 0 else 0
-
-# 误报率（False Positive Rate, FPR）
-fpr = FP / (FP + TN) if (FP + TN) > 0 else 0
-
-# 假阴率（False Negative Rate, FNR）
-fnr = FN / (TP + FN) if (TP + FN) > 0 else 0
-
-# 计算AUC（此处假设预测的概率值，以便计算AUC）
-y_true = [1 if i in malicious_clients else 0 for i in range(total_clients)]
-y_scores = [1 if i in identified_malicious else 0 for i in range(total_clients)]
-auc = roc_auc_score(y_true, y_scores)
-
-# 计算MCC（Matthews Correlation Coefficient）
-mcc = matthews_corrcoef(y_true, y_scores)
-
-# 打印结果
-print(f"TP (True Positive): {TP}")
-print(f"FP (False Positive): {FP}")
-print(f"FN (False Negative): {FN}")
-print(f"TN (True Negative): {TN}")
-print(f"准确率（Accuracy）: {accuracy:.2f}")
-print(f"精确率（Precision）: {precision:.2f}")
[…]

### 2024-09-19 tempCodes/temp.score.verify.py

@@ -1,64 +1,0 @@
-'''
-Author: LetMeFly
-Date: 2024-09-14 00:47:51
-LastEditors: LetMeFly
-LastEditTime: 2024-09-15 10:34:39
-'''
-from sklearn.metrics import matthews_corrcoef, roc_auc_score
-
-# 假设共有20个客户端，前4个为恶意客户端
-total_clients = 20
-malicious_clients = {0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14}  # 实际恶意客户端的索引
-
-# 假设识别出来的恶意客户端结果（可以修改此数组来测试不同情况）
-identified_malicious = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]  # 被识别为恶意的客户端索引
-
-# 计算TP, FP, TN, FN
-TP = len(malicious_clients.intersection(identified_malicious))
-FP = len(set(identified_malicious) - malicious_clients)
-FN = len(malicious_clients - set(identified_malicious))
-TN = total_clients - TP - FP - FN
-
-total_clients = 50
-TP, FP, TN, FN = 13, 0, 35, 2
-
-
-# 准确率（Accuracy）
-accuracy = (TP + TN) / total_clients
-
-# 精确率（Precision）
-precision = TP / (TP + FP) if (TP + FP) > 0 else 0
-
-# 召回率（Recall）
-recall = TP / (TP + FN) if (TP + FN) > 0 else 0
-
-# 特异度（Specificity）
-specificity = TN / (TN + FP) if (TN + FP) > 0 else 0
-
-# 误报率（False Positive Rate, FPR）
-fpr = FP / (FP + TN) if (FP + TN) > 0 else 0
-
-# 假阴率（False Negative Rate, FNR）
-fnr = FN / (TP + FN) if (TP + FN) > 0 else 0
-
-# 计算AUC（此处假设预测的概率值，以便计算AUC）
-y_true = [1 if i in malicious_clients else 0 for i in range(total_clients)]
-y_scores = [1 if i in identified_malicious else 0 for i in range(total_clients)]
-auc = roc_auc_score(y_true, y_scores)
-
-# 计算MCC（Matthews Correlation Coefficient）
-mcc = matthews_corrcoef(y_true, y_scores)
-
-# 打印结果
-print(f"TP (True Positive): {TP}")
-print(f"FP (False Positive): {FP}")
[…]

### 2024-09-19 getResult/genReLiTu.py
final: 初稿最终版代码
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,13 +1,7 @@
-'''
-Author: LetMeFly
-Date: 2024-09-13 23:43:25
-LastEditors: LetMeFly
-LastEditTime: 2024-09-14 01:52:38
-'''
-import numpy as np
 import matplotlib.pyplot as plt
 import seaborn as sns
 import torch
+import numpy as np
 
 def plot_detection_heatmaps_3x4(*heatmap_params):
     """
@@ -46,6 +40,35 @@ def plot_detection_heatmaps_3x4(*heatmap_params):
         
         return similarity_matrix
 
+    # 计算每组热力图数据的全局最小值和最大值
+    first_column_min_val, first_column_max_val = float('inf'), float('-inf')
+    other_columns_min_val, other_columns_max_val = float('inf'), float('-inf')
+
+    heatmap_arrays = []
+
+    for idx, heatmap_data in enumerate(heatmap_params):
+        # 如果是二维 tensor，直接转换为 numpy
+        if len(heatmap_data.shape) == 2:
+            if isinstance(heatmap_data, torch.Tensor):
+                heatmap_array = heatmap_data.cpu().numpy()
+            else:
+                heatmap_array = heatmap_data
+        # 如果是一维 tensor，计算相似度矩阵
+        elif len(heatmap_data.shape) == 1:
+            heatmap_array = compute_similarity_matrix(heatmap_data)
+        else:
+            raise ValueError("参数必须是 1D 或 2D 的 torch.Tensor。")
+        
+        # 根据图的位置更新不同的全局最小值和最大值
+        if idx % 4 == 0:  # 第一列的图
+            first_column_min_val = min(first_column_min_val, heatmap_array.min())
+            first_column_max_val = max(first_column_max_val, heatmap_array.max())
+        else:  # 其他列的图
+            other_columns_min_val = min(other_columns_min_val, heatmap_array.min())
+            other_columns_max_val = max(other_columns_max_val, heatmap_array.max())
+        
+        heatmap_arrays.append(heatmap_array)
+
     # 创建图像和子图
     fig, axes = plt.subplots(nrows=3, ncols=4, figsize=(20, 15))
 
@@ -57,22 +80,18 @@ def plot_detection_heatmaps_3x4(*heatmap_params):
     for i in range(3):  # 三行，分别为不同的攻击
         for j in range(4):  # 四列，分别为四种防御方法
             ax = axes[i, j]
[…]

### 2024-09-19 main-v2.tex

@@
 \usepackage{graphicx}
+% \usepackage{tabularx}
 \usepackage{cite}
@@
 \usepackage{enumerate}
+\usepackage{threeparttable}
 
@@
 \author{Zan Zhou, %~\IEEEmembership{Student Member,~IEEE}, 
- Bo Wang, Tengfei Li, Shujie Yang, Changqiao Xu, Su Yao, 
+  Changqiao Xu, Bo Wang, Tengfei Li, Sizhe Huang, Shujie Yang$^{\ast}$\thanks{*Corresponding authors}, Su Yao$^{\ast}$
 % <-this % stops a space
 \thanks{Z.
-Zhou, H.
+Zhou, B.
+Wang, T.
 Li, S.
-Huang, S.
-Yang, P.
-Guo, and C.
-Xu are with the State Key Laboratory of Networking and Switching Technology, Beijing University of Posts and Telecommunications, Beijing 100876, P.R.
+Huang, C.
+Xu, and S.
+Yang are with the State Key Laboratory of Networking and Switching Technology, Beijing University of Posts and Telecommunications, Beijing 100876, P.R.
 China.
-E-mail: \{zan.zhou, lihongjing, swhsz, sjyang, guopeng, cqxu\}@bupt.edu.cn.
+E-mail: \{zan.zhou, cqxu, bowang, tf, swhsz, sjyang\}@bupt.edu.cn.
 	}  % <-this % stops a space
@@
 % \thanks{L. Zhong is with the Information Engineering College, Capital Normal University, Beijing 100048, China. E-mail: zhonglj@cnu.edu.cn (Corresponding author).}% <-this % stops a space
-\thanks{Su Yao is with Tsinghua University, China. E-mail: XXXX@xxx.}% <-this % stops a space
+\thanks{Su Yao is with the Beijing National Research Center for Information Science and Technology (BNRist), Tsinghua University, Beijing 100190, China.
+E-mail: yaosu@tsinghua.edu.cn}% <-this % stops a space
 %\thanks{This paper was produced by the IEEE Publication Technology Group. They are in Piscataway, NJ.}% <-this % stops a space
@@
 \begin{abstract}
-%攻击者
-
-Fairness-aware federated learning (FFL) plays a crucial role in miti
+%随着大模型与具身智能机器人网络的迅速发展，以及在智慧城市、电网、工厂、交通运输等领域的应用，视觉感知理解成为了突破具身智能节点性能瓶颈的基础性要素之一。而由于通用的预训练模型并不能很好应对特定任务，联邦微调技术由于其能够最大限度利用离散节点数据、算力的优势，成为了提升视觉感知模型能力的热带技术。然而，随着多种针对性高级持续性威胁的涌现，现有的污染防治方案，并不能有效应对这一新场景下的隐蔽后门攻击。本文因此提出SecFFT方法，其核心在于针对攻击隐蔽性高与攻击策略复杂的问题，分别设计了基于频域分布一致性提取的瞬时攻击行为识别，和基于隐藏攻击意图检测的长效安全聚合机制。从最终目的出发，有效限缩了智能化攻击者通过隐藏自身行为来绕过防御方案的可行域。在公共数据集上的实验表明，我们所提出的方法能够显著提升面对后门攻击时的防御成功率、模型性能和识别精度，尤其是面对具有多轮次复杂策略的高隐蔽后门范式。
+As the large vision language models and embodied intelligent robotic networks continue to advance at a remarkable pace, particularly in applications spanning smart cities, power grids, factories, and transportation, visual perception and understanding have emerged as foundational elements to overcoming performance limitations in such intelligent systems.
+However, since general pre-trained models are not well-suited to specific tasks, federated fine-tuning (FFT) has gained attention as a promising technique for enhancing the performance of vision-based perception models by leveraging data and computational power distributed across nodes.
+The rise of advanced persistent threats has revealed significant vulnerabilities in existing defense mechanisms, which struggle to mitigate sophisticated backdoor attacks toward FFT for LVLMs.
+To address these challenges, this paper proposes the SecFFT method, which tackles both the stealthiness and complexity of backdoor strategies.
+The approach incorporates instantaneous attack behavior detection based on frequency-domain distribution consistency and introduces a long-term secure aggregation mechanism aimed at identifying hidden attack intentions.
+These strategies effectively limit the feasibility of adversaries attempting to bypass defense measures by concealing their behaviors.
+Experiments conducted on public datasets demonstrate that SecFFT significantly improves defense success rates, model performance, and detection accuracy, particularly in response to highly covert, multi-round backdoor attacks.
 
@@
 \begin{IEEEkeywords}
-Federated learning, fairness, privacy, integrity, heterogeneous UAV network.
+Vision Language Model, Federated learning, Fine-tuning, Security, Backdoor, Internet of Robotic Things.
 \end{IEEEkeywords}
@@
 %随着具身智能技术的迅猛进步和在智慧城市、智能交通、无人机等领域的广泛应用，机器人节点从执行等单一任务的agent，逐步向集合了感知交互和自主决策的智能体进行了演进，这也成为了未来IORT网络的重要发展趋势之一。而视觉大模型作为一种新兴热门的图像感知和物体识别技术，能够成为支撑智能机器人对周围环境进行认识和理解不可或缺的基础。
-With the rapid advancements in embodied intelligence technology and its widespread application in multiple areas such as smart cities, intelligent transportation, and unmanned aerial vehicles, robotic nodes have evolved from agents performing singular tasks to intelligent entities that integrate perception, interaction, and autonomous decision-making jointly.
-This evolution has become one of the critical developmental trends for Internet of Robotic Things (IoRT) networks.
-Meanwhile, the Large Vision Language Model (LVLM), as an emerging and popular image perception and object recognition technology, has the potential to be an indispensable foundation supporting intelligent robots in understanding and interpreting their surrounding environments.
+With the rapid advancements of embodied intelligence technology and its widespread application in multiple areas such as smart cities, intelligent transportation, and unmanned aerial vehicles, robotic nodes have evolved from agents performing singular tasks to intelligent entities that integrate perception, interaction, and autonomous decision-making.
+This evolution has become one of the critical developmental trends for Internet of Robotic Things (IoRT) networks\cite{andronie2023big}.
+Meanwhile, the Large Vision Language Model (LVLM)\cite{liu2024survey}, as an emerging and popular image perception and object recognition technology, has the potential to support intelligent robots in understanding and interpreting their surrounding environments.
 
 %视觉大模型极大地增强了机器人的视觉语义理解能力，使其能够对多模态任务进行更加智能化的决策响应，然而在真实应用环境中，仍存在以下问题：1）由于真实世界的多样性和异构性，通用大模型在特定任务上往往无法较好迁移通用知识，需要进行微调才能显著提升识别精度（例如，针对动目标检测任务，交通机器人主要针对车辆、行人，而工厂机器人则主要针对机床，两者轮廓、行为模式范围均存在较大差异）；2）此外，将来自不同源头的离散化、碎片化分布的海量数据进行传输并汇聚于主服务器，将会导致巨大的通信开销和时间延迟，无法满足具身智能业务的需求，且存在潜在的隐私风险。
-Although LVLMs significantly enhance the visual semantic understanding capabilities of robots, enabling them to make more intelligent decisions in multi-modal tasks, there are still challenges in real-world applications: 1) Due to the diversity and heterogeneity of the real world, general foundation models often cannot effectively transfer their general knowledge to specific tasks, necessitating fine-tuning to significantly improve recognition accuracy (for example, traffic robots primarily focus on vehicles and pedestrians for moving object detection tasks, while factory robots mainly target machine tools, with significant differences in their contours and behavioral patterns); 2) Additionally, transmitting and aggregating massive amounts of discretized and fragmented data from different sources to a central server can result in significant communication overhead and latency, failing to meet the demands of embodied intelligence applications and posing potential privacy risks.
+Although LVLMs significantly enhance the visual semantic understanding capabilities of robots, enabling them to make more intelligent decisions in multi-modal tasks, there are still challenges in real-world applications: (1) Due to the diversity and heterogeneity of the real world\cite{dai2023tackling}, general foundation models often cannot effectively transfer their general knowledge to specific tasks, necessitating fine-tuning\cite{fu2023effectiveness} to significantly improve recognition accuracy (for example, traffic robots primarily focus on vehicles and pedestrians for moving object detection tasks, while factory robots mainly target machine tools, with significant differences in their contours and behavioral patterns); (2) Additionally, transmitting and aggregating massive amounts of discretized and fragmented data from different sources to a central server can result in significant communication overhead and latency\cite{zhao2023towards}, failing to meet the demands of embodied intelligence applications and posing potential privacy risks\cite{wen2023survey, khan2023federated}.
 
@@
 
-%不幸的是，FFT的分布式特性为多种后门攻击提供了存续的空间。尽管多种防御手段相继提出，但是尽我们所知，目前尚未有针对LVM的FFT过程进行污染防治的后门对抗技术提出。现有技术大多是针对普通联邦学习场景或集中式的VLM训练进行设计，这暴露出两大核心问题：（1）高隐蔽的攻击行为感知困难：攻击者在设计攻击行为时，(2)复杂攻击策略的检测困难：
-
-% 因此，在本文中，我们提出了一种
+%不幸的是，FFT的分布式特性为多种后门攻击提供了存续的空间。尽管多种防御手段相继提出，但是尽我们所知，目前尚未有针对LVM的FFT过程进行污染防治的后门对抗技术提出。现有技术大多是针对普通联邦学习场景或集中式的VLM训练进行设计，这暴露出两大核心问题：（1）高隐蔽的攻击行为感知困难：攻击者在设计攻击行为时，尽量在行为特征上拟合正常用户，perception的区分度越来越narrow；(2)复杂攻击策略的检测困难：为了规避防御，攻击者可能采用限制角度、大小、符号等方式，将原有单次攻击转化为多轮次长时间尺度的持续性威胁，攻击识别更加困难。
+Unfortunately, the distributed nature of FFT provides a persistent space for various backdoor attacks.
+While several defense strategies have been proposed, to the best of our knowledge, no countermeasures specifically address backdoor attacks in the FFT process for LLVMs.
+Most existing techniques are designed for conventional federated learning scenarios or centralized VLM training, exposing two critical issues: (1) \textbf{The high stealthy nature of attack behavior:} Attackers increasingly design their actions to mimic normal users, narrowing the perception’s distinguishing capability\cite{xu2024shadowcast, zhang2024a3fl}; and (2) \textbf{The complexity of detecting sophisticated attack strategies:} To evade defenses, attackers may employ techniques such as limiting angle, magnitude, or sign, transforming a single attack into a multi-round, long-term threat, further complicating attack detection\cite{geisler2024attacking, chen2024optimal, sagliano2024powered, dong2023adaptive,wan2023average}.
+
+% 因此，在本文中，我们针对LVLM的FFT过程，提出了一种新型的抗backdoor防御方案。针对攻击行为感知难题，我们创新地从频域分布一致性入手，将隐性的梯度更新分布差异而非显性的更新离群性作为新的鉴别角度，从而实现对高隐蔽攻击的感知；在此基础上，进一步针对智能化攻击者可能采取的复杂多轮次策略，我们创新地提出了基于意图识别的长效评估架构，有效分离高级持续性威胁，并据此设计安全聚合方法。
 % 主要包括以下几方面贡献：
-% 我们首先提出了针对进行防御
-% 针对意图
-% 防御策略
-
-The remainder of this paper is organized as follows: Section \uppercase\expandafter{\romannumeral2} reviews the related works.
+Therefore, in this paper, we propose a novel backdoor defense scheme tailored for the FFT process of LVLMs.
+To address the challenge of detecting attack behaviors, we introduce a groundbreaking approach based on consistency in frequency domain distributions.
+Rather than focusing on explicit gradient outliers, we leverage the implicit differences in gradient update distributions as a new identification criterion, enabling the detection of highly covert attacks.
+Building on this, we further address the issue of complex multi-round strategies employed by intelligent attackers by proposing an innovative long-term evaluation framework based on intent recognition.
+This framework effectively isolates advanced persistent threats and informs the design of a secure aggregation method.
+
+The main contributions of this scheme include:
+\begin{enumerate}
+    \item Based on an in-depth analysis of emerging covert backdoor attacks, we first define two core challenges: detecting highly covert attack behaviors and identifying complex attack strategies.
+We then provide a case study of these issues within the FFT process of large vision models.
+To the best of our knowledge, this is the first framework capable of recognizing deep-level attack intentions during the fine-tuning process in IoRT networks, effectively defending against covert attacks.
+    \item In response to the potential threat of intelligent attackers fragmenting their behaviors to evade detection, we propose an innovative method for constructing attack intentions based on historical behavior sequences.
+By building an approximate minimal covering hypersphere from these behaviors, the malicious intent hidden behind seemingly disordered, benign actions is fully exposed.
+    \item SecFFT also adopts a novel nonlinear defense strategy, dynamically adjusting aggregation weights using local outlier factors while ensuring fairness for benign nodes and effectively eliminating malicious ones.
+A series of experiments on public datasets demonstrate that our approach significantly improves model integrity, effectively suppresses covert backdoor attacks, and maintains a low false positive rate.
+\end{enumerate}
+% 基于对现有新型隐蔽后门攻击的分析，我们首先定义了高隐蔽攻击行为感知和复杂攻击策略识别这两大核心问题，并基于视觉大模型的FFT过程进行实例分析。据我们所知，这是首个在IORT网络中能够实现对微调过程中深层次攻击目的识别，从而抵御高隐蔽攻击的方案。
+% 针对智能攻击者可能将攻击行为切片化拆解从而规避防御检测的潜在威胁，我们创新地设计了基于历史行为序列进行攻击意图构建的方法。通过构建历史行为的近似最小覆盖超球，将智能攻击者隐藏在看似杂乱无序、良性无害的攻击行为背后的恶意意图充分暴露。
+% 基于意图识别架构，SecFFT能够设计一种非线性的新型防御策略，利用局部离群因子动态调整聚合权重，同时保障良性用户公平性和恶意用户的消除。公有数据集上的系列实验表明，我们的方法能够显著提升模型完整性，有效遏制隐蔽后门攻击，并同时保证极低的误判率。
+
+The remainder of this paper is organized as follows: Section \uppercase\expandafter{\romannumeral2} reviews related works.
 Section \uppercase\expandafter{\romannumeral3} and \uppercase\expandafter{\romannumeral4} present the system and threat models, respectively.
@@
     \label{fig1:scene}
+    %\vspace{-0.7cm}
 \end{figure}
@@
 EDGE CASE\cite{EDGE_CASE} proposes an edge-case backdoor attack method for federated learning by injecting backdoors using input data points that are naturally occurring but typically absent in both training and testing datasets (i.e., edge-case samples).
-Shadowcast \cite{xu2024shadowcast} manipulates vision-language models (VLMs) to produce misleading textual outputs for specific visual inputs by introducing subtle, imperceptible perturbations in the feature space.
-Flip \cite{jha2023label} modifies the labels of training data so that the model's training trajectory approximates that of an expert model with a backdoor, achieving covert attacks in the feature space that can evade existing detection methods even when the images are clean.
+Shadowcast \cite{xu2024shadowcast} manipulates VLMs to produce misleading textual outputs for specific visual inputs by introducing subtle, imperceptible perturbations in the feature space.
+Flip \cite{jha2023label} modifies the labels of training data so that the model's training trajectory approximates that of an expert model with a backdoor.
+This hidden process completes covert attacks in the feature space, thus evading existing detection methods even when the images are clean.
 
@@
 NEUR\cite{zhang2022neurotoxin} proposes a more persistent backdoor attack method for federated learning by targeting model parameters that change less during training.
-This approach increases the durability of the backdoor, avoids conflicts with the gradients of benign users, and makes it less likely to be removed in subsequent model updates.
+This approach increases the durability of the backdoor, avoids conflicts with the gradients of benign nodes, and makes it less likely to be removed in subsequent model updates.
 ImgTrojan \cite{tao2024imgtrojan} injects a small number of malicious samples into the training data of vision-language models, ensuring that these backdoors remain effective even after subsequent benign training, thereby continuously affecting the model's behavior.
@@
 These attacks not only cleverly hide malicious intent in the feature space but also maintain their effects throughout long-term training, posing a sustained and profound impact on model behavior, thus presenting a severe challenge to model security.
-This underscores the need for future research to focus on developing more robust defense methods.
+This underscores the need for developing more robust defense methods.
 
@@
 %在当前深度学习模型的安全性研究中，针对后门攻击的防御措施主要可以分为两大类：后门检测和后门缓解。% Backdoor Mitigation or Elimination
-In the current research on the defense technologies, defense measures against backdoor attacks can be also broadly categorized into two major types: %backdoor detection and backdoor mitigation.
+In current research on defense technologies, defense measures against backdoor attacks can be also broadly categorized into two major types: %backdoor detection and backdoor mitigation.
 
@@
 This approach significantly reduces the attack success rate even when facing diverse attacker models and data distributions.
-MCLDef \cite{yue2023model} proposes a two-stage backdoor defense method based on model contrastive learning, effectively removing backdoors in deep neural networks by contracting or disrupting the clustering of poisoned data in the feature space and pulling the features of poisoned data toward their clean counterparts, while improving defense effectiveness without significantly reducing model accuracy.
+MCLDef \cite{yue2023model} proposes a two-stage backdoor defense method based on model contrastive learning, effectively removing backdoors in deep neural networks by disrupting the clustering of poisoned data in the feature space and pulling the features of poisoned data toward their clean counterparts, while improving defense effectiveness without significantly reducing model accuracy.
 DPoE \cite{liu2023shortcuts} introduces an end-to-end integrated backdoor defense framework that captures and suppresses backdoor triggers by combining a shallow model and a main model, effectively countering various explicit and covert backdoor attacks while mitigating the impact of noisy labels on model performance.
@@
 Despite the effectiveness of these methods in countering explicit backdoors, their performance may still be insufficient when faced with more covert or complex backdoor attacks.
-Some methods also rely on external knowledge or confidence settings, which may lead to misjudgments or performance bottlenecks.
+Some methods rely on external knowledge or confidence settings, which may lead to misjudgments or performance bottlenecks.
 Moreover, these methods increase computational overhead and training time in practical applications.
@@
     \hline
-    $ N $ & Number of nodes participating in each round.\\ \hline
+    $ N $ & The number of nodes participating in each round.\\ \hline
     $R_i$ & The $i$-th robot node. \\ \hline
-    $D_i$ & Private local dataset of node $R_i$.\\ \hline
-    $\theta_g^t, \theta_i^t$ & Global model and local model of $R_i$ at round $t$. \\ \hline
+    $D_i$ & The private local dataset of node $R_i$.\\ \hline
+    $\theta_g^t, \theta_i^t$ & The global model and local model of $R_i$ at round $t$. \\ \hline
     $\triangledown \theta_i^t$ & Local update of $R_i$ during round $t$. \\ \hline
     $G_i^t $ & Frequency component of $R_i$'s update at round $t$. \\ \hline
-    $m$ & Length of the low-frequency components. \\ \hline
-    $H^t$ & Matrix formed by stacking $G_i^t$, with dimensions $m \times N$ during round $t$. \\ \hline
-    $\tilde{G}_{0}^t $ & Clean ingredient extracted from $R_i$'s low-frequency components during round $t$. \\ \hline
-    $\lambda_{max}^t$ & Largest singular value of matrix $H^t$ during round $t$. \\ \hline
-    $\xi_{max}^t$ & Left singular vector corresponding to $\lambda_{max}^t$ during round $t$. \\ \hline
-    $Chi_i^t$ & Distance difference between $R_i$'s update and the clean ingredient during round $t$. \\ \hline
-    $t'$ & One of the total $T$ rounds. \\ \hline
-    $O_i^{t'}$ & Intention point of $R_i$ during round $t'$. \\ \hline
-    \( {v}_{i}^{t'} \) & Vector of the high-dimensional ball for $R_i$ during round $t'$. TODO: CHANGE THIS\\ \hline
-    $lof_i$ & The LOF score of $R_i$.\\ \hline
-    $cre_i$ & The credit of $R_i$.\\ \hline
+    $m$ & The length of the low-frequency components. \\ \hline
+    $H^t$ & The matrix formed by stacking $G_i^t$. \\ \hline
+    $\tilde{G}^t $ & The extracted global clean ingredient at round $t$. \\ \hline
+    $\lambda_{max}^t$ & The largest singular value of matrix $H^t$ at round $t$. \\ \hline
+    $\xi_{max}^t$ & The left singular vector corresponding to $\lambda_{max}^t$. \\ \hline
+    $Chi_i^t$ & The difference between $\triangledown \theta_i^t$ and $\tilde{G}^t $ at round $t$. \\ \hline
+    $t'$ & The round number within total $T$ rounds. \\ \hline
+    $O_i^{t'}$ & The intention point of $R_i$ at round $t'$. \\ \hline
+    \( {v}_{i}^{t'} \) & The vector of the behavior ray for $R_i$ at round $t'$. \\ \hline
+    $lof_i$ & The outlier level of $R_i$.\\ \hline
+    $cre_i$ & The credit score of $R_i$.\\ \hline
 \end{tabular}
@@
     Assume the number of local training epochs is $E_l$, the batch size is $b$, and the learning rate is $\eta$.
-For each epoch, the node $R_i$ randomly samples a batch of data $D_i^b \sim Sample(D_i, b)$ from its local dataset and updates the incremental parameters using an optimization algorithm such as stochastic gradient descent (SGD):
+For each epoch, the node $R_i$ randomly samples a batch of data $D_i^b \sim Sample(D_i, b)$ from its local dataset and updates the incremental parameters using an optimization procedure as:
 \begin{equation}
@@
     %本地训练的目标是最小化损失函数 $f(D_i^b, (\theta_i^{t})^e)$：
-    The local training objective to minimize the loss function $f(D_i^b, (\theta_i^{t})^e)$ is:
+    The local training objective to minimize the loss $f(D_i^b, (\theta_i^{t})^e)$ is:
 \begin{equation}
@@
     \textbf{Federated Aggregation}:
-    At the end of each local training round, the central server collects the local updates $\triangledown \theta_i^t$ from each robotic node $R_i$ and aggregates them using a specified aggregation algorithm to update the global incremental parameters $\theta_g^t$:
+    At the end of each round, the central server collects the local updates $\triangledown \theta_i^t$ from each robotic node $R_i$ and aggregates them using a specified aggregation algorithm to update the global model parameters $\theta_g^t$:
 \begin{equation}
@@
 %Attacker's Goal：假设在对视觉语言模型进行联邦微调的场景中，存在一个或者多个由攻击者操纵的恶意节点。其目标是对全局模型$\Theta$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别，即$\Theta(x+\delta) = y'$，其中$x$代表正常输入，$y'$表示目标类别。同时尽可能保持对干净输入的分类准确性，即$\Theta(x) = y$，其中$y$为输出$x$的原始类别。
-\textbf{Attacker's Goal:} In the scenario of federated fine-tuning of a vision-language model, it is assumed that one or more malicious nodes controlled by attackers are present.
+\textbf{Attacker's Goal:} In the scenario of the FFT process of LVLMs, it is assumed that one or more malicious nodes are controlled by attackers.
 The goal is to implant a backdoor into the global model $\Theta$, such that the model classifies any test input with a predefined trigger $\delta$ as the target class, i.e., $\Theta(x + \delta) = y'$, where $x$ represents a normal input and $y'$ denotes the target class.
@@
 \section{Methodology}
-Our SecFFT method consists of two major Instantaneous Attack Behavior Perception with Frequency-domain Deep Outlier Feature Semantics
+Our SecFFT method consists of two major modules: Instantaneous Attack Behavior Perception and Long-term Attack Intention Detection, which are elaborated, respectively.
 
@@
 %首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明\cite{huang2023multi}，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。但值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终在某种分布上具有偏移。
-\textbf{Motivation:} Current defense strategies primarily focus on identifying malicious nodes using “shallow semantic features” of attacks, such as geometric or statistical characteristics like the direction\cite{foolsgold}, norm\cite{sun2019can}, and geometric center\cite{pillutla2022robust} of node updates.
+\textbf{Motivation:} 
+% Current defense strategies primarily focus on identifying malicious nodes using “shallow semantic features” of attacks, such as geometric or statistical characteristics like the direction\cite{foolsgold}, norm\cite{sun2019can}, and geometric center\cite{pillutla2022robust} of node updates.
 However, these shallow feature-based defenses exhibit significant limitations in high-dimensional spaces.
@@
 It is important to note, however, that the core of a backdoor attack lies in creating an association between a predefined trigger and the target.
-Regardless of how the attacker adjusts their attack methods or strategies, the uploaded updates will always exhibit a distributional shift compared to benign users.
+Regardless of how the attacker adjusts their attack methods or strategies, the uploaded updates will always exhibit a distributional shift compared to benign nodes.
+Current defense strategies primarily focus on identifying malicious nodes using "shallow semantic features" of attacks, such as geometric or statistical characteristics like the direction\cite{foolsgold}, magnitude\cite{sun2019can}, and geometric center\cite{pillutla2022robust} of node updates.
+However, these shallow feature-based defenses have significant limitations in high-dimensional spaces.
+For instance, these methods often function effectively only under specific assumptions and for certain types of attacks.
+For example, cosine distance can detect malicious updates with significant directional deviations, while Euclidean distance is typically employed to identify malicious updates that inflate the $L_2$ norm and affect the global model.
+Recent studies have also shown \cite{huang2023multi} that traditional distance metrics like Euclidean distance are inadequate for distinguishing between malicious and benign updates in high-dimensional spaces due to the curse of dimensionality.
+Moreover, attack strategies continue to evolve, with attackers now able to fine-tune their updates to resemble benign ones in terms of direction, norm, and other shallow features, effectively bypassing these shallow semantic-based defenses while still implanting backdoors into the global model.
+It is important to note, however, that the core of a backdoor attack lies in establishing an association between a predefined trigger and the target.
+Regardless of how the attacker adjusts their attack methods or strategies, the uploaded updates will always display a distributional shift compared to benign nodes.
 
 %\textbf{Overview:} 在深度神经网络模型中，每个权重代表两个神经元之间连接的强度。权重分布及其相关的能量在训练过程中会经历动态演变，以缩小模型预测结果与训练数据中的真实目标之间的差距。当后门攻击迫使神经网络模型学习一种在正常数据中不存在的关联模式时，根据后门触发器的设计和实现方式，这种模式可能是微妙的，也可能是相当明显的，但无论如何，它都代表了与模型从正常数据中学习到的模式的偏离。因此，为解决基于浅层语义特征的防御方法在高维空间中面临的局限性，我们从后门攻击的本质出发\cite{zeng2021rethinking}，提出了一种基于深层语义特征的防御策略，重点分析模型更新在频率分布上的差异。通过将本地模型更新转换到频域，我们能够更深入地捕捉恶意更新在低频成分上的异常表现，这些异常通常难以通过传统的浅层特征检测方法发现。通过对频率域上的特征进行分析，我们可以有效地区分出恶意节点与良性节点，从而增强联邦学习系统在面对复杂后门攻击时的鲁棒性和检测精度。
-\textbf{Overview:} In deep neural networks, each weight represents the strength of the connection between two neurons.
+\textbf{Overview:} 
+% In deep neural networks, each weight represents the strength of the connection between two neurons.
 The distribution of these weights and their corresponding energy dynamically evolve during training to minimize the gap between the model's predictions and the ground truth in the training data.
@@
 Through frequency domain feature analysis, we can effectively distinguish malicious nodes from benign ones, thereby enhancing the robustness and detection precision of federated learning systems when facing sophisticated backdoor attacks.
-
-\textbf{Frequency domain transformation:}
+In deep neural networks, each weight signifies the strength of the connection between two neurons.
+The distribution of these weights and their corresponding energy dynamically evolves during training to minimize the gap between the model's predictions and the ground truth in the training data.
+When a backdoor attack compels the neural network to learn an association pattern that does not exist in normal data, this pattern depending on the design and implementation of the backdoor trigger can be subtle or quite evident.
+Nonetheless, it always signifies a deviation from the patterns learned from normal data.
+To address the limitations of shallow feature-based defenses in high-dimensional spaces, we propose a defense strategy grounded in the essence of backdoor attacks\cite{zeng2021rethinking}, focusing on deeper semantic features by analyzing differences in the frequency distribution of model updates.
+By transforming local model updates into the frequency domain, we can more effectively capture the anomalous behavior of malicious updates in low-frequency components, which are typically challenging to detect using traditional shallow-feature detection methods.
+Through frequency domain feature analysis, we can effectively distinguish malicious nodes from benign ones, thereby enhancing the robustness and detection accuracy of federated learning systems when confronted with sophisticated backdoor attacks.
+Figure \ref{fig2:instant} formalizes this method we proposed.
+
+\subsubsection{Frequency domain transformation}
 %%%% 相比于目前基于浅层语义特征的防御方法，我们利用DCT进行频域转换，将模型的更新向量映射到频域空间，以探究其在频率域上的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的4-7行所示，假设每个本地模型的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，通过一维的DCT-II将其转换为对应的频率分布，并提取低频分量，得到频率向量\(G_i^t\)。这里的 $Trunc$ 操作表示仅保留前 $m$ 个低频分量，以捕捉频域中更具代表性的特征用于后续的恶意节点检测。
 %受高维空间中维度灾难的影响，传统的基于距离度量的方法已无法有效识别恶意节点。相反，将模型更新转换到频率域后，其差异将主要集中在低频成分上。因此，专注于低频成分的分析，在提升识别准确率的同时，将显著的降低计算开销。假设每个节点上传的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，对其进行归一化，然后通过一维的DCT-II\cite{ahmed1974discrete}变化将其转换为对应的频率分布，并提取$m$个低频分量，例如5000，得到低频向量\(G_i^t\)。
-Due to the curse of dimensionality in high-dimensional spaces, traditional distance-based methods are no longer effective in identifying malicious nodes.
-In contrast, by transforming model updates into the frequency domain, the discrepancies are primarily concentrated in the low-frequency components.
-Therefore, focusing on the analysis of low-frequency components not only improves identification accuracy but also significantly reduces computational overhead.
-Suppose each node uploads an update as \(\triangledown \theta_i^t \in \mathbb{R}^d\), where $i$ represents the robot node, $t$ denotes the communication round, and $d$ is the dimension of the local model update.
-For each update \(\triangledown \theta_i^t\), it is first normalized and then transformed into its corresponding frequency distribution using a one-dimensional DCT-II \cite{ahmed1974discrete}, from which $m$ low-frequency components (normally under 5000 \cite{fereidooni2023freqfed}) are extracted to form the low-frequency vector $G_i^t$.
+Due to the curse of dimensionality in high-dimensional spaces, traditional distance-based methods become ineffective in identifying malicious nodes.
+In contrast, by transforming model updates into the frequency domain, discrepancies primarily concentrate in the low-frequency components.
+Therefore, focusing on the analysis of low-frequency components not only enhances identification accuracy but also significantly reduces computational overhead.
+Suppose each node uploads an update \(\triangledown \theta_i^t \in \mathbb{R}^d\), where $i$ represents the robot node, $t$ denotes the communication round, and $d$ denotes the dimension of the local model update.
+For each update \(\triangledown \theta_i^t\), it is first normalized and then transformed into its corresponding frequency distribution using a one-dimensional DCT-II \cite{ahmed1974discrete}, from which $m$ low-frequency components\cite{fereidooni2023freqfed} (e.g.
+5000 )\cite{fereidooni2023freqfed} are extracted to form the low-frequency vector $G_i^t$.
 
@@
 \end{equation}
+
 % 频域转换的主要过程如公式\ref{eq:DCT}所示，这里的 $Trunc$ 操作表示仅保留前$m$个低频分量。
@@
 
-\textbf{Clean ingredient extraction:}
+\subsubsection{Clean ingredient extraction}
 % 在提取到节点更新对应的低频向量\(G_i^t\)后，我们使用流行的聚类算法例如HDBSCAN\cite{mcinnes2017hdbscan}对这些更新进行聚类，得到多个簇$C_0^t, C_1^t, \ldots, C_{\kappa}^t$，其中$\kappa$表示簇的数量。在大多数联邦学习场景中，良性节点的数量通常多于恶意节点的数量，且良性节点的更新通常更接近全局模型的方向并表现出更高的聚集性。基于这一观察，我们选择节点数量最多的簇$C_{max} = \{R_{i_0}, R_{i_1}, \ldots, R_{i_n}\}$作为主要分析对象。为了进一步提取该簇的主要特征或模式，我们对其中所有节点组成的矩阵进行奇异值分解\cite{wang2023scfl}。由于，SVD分解的左奇异向量$\tilde{G}^t$对应于数据的主要方向，因此，$\tilde{G}^t$可以作为良性节点在低频域内的主要特征。
-After extracting the corresponding low-frequency vectors \(G_i^t\) from node updates, we use popular clustering algorithms such as HDBSCAN \cite{mcinnes2017hdbscan} to cluster these updates, resulting in multiple clusters \(C_0^t, C_1^t, \ldots, C_{\kappa}^t\), where \(\kappa\) denotes the number of clusters.
-In most federated learning scenarios, the number of benign nodes is generally greater than that of malicious nodes, and the updates from benign nodes are usually closer to the direction of the global model and exhibit higher cohesion.
-Based on this observation, we select the cluster with the largest number of nodes, \(C_{max} = \{R_{i_0}, R_{i_1}, \ldots, R_{i_n}\}\), as the primary subject for analysis.
-To further extract the main features or patterns of this cluster, we perform singular value decomposition (SVD)\cite{wang2023scfl} on the matrix composed of all nodes in this cluster.
-Since the left singular vectors of the SVD decomposition, \(\tilde{G}^t\), correspond to the main directions of the data, \(\tilde{G}^t\) can be regarded as the primary feature of benign nodes in the low-frequency domain.
+After extracting the corresponding low-frequency vectors \(G_i^t\) from node updates, we employ popular clustering algorithms such as HDBSCAN \cite{mcinnes2017hdbscan} to cluster these updates, resulting in multiple clusters \(C_0^t, C_1^t, \ldots, C_{\kappa}^t\), where \(\kappa\) denotes the number of clusters.
+In most federated learning scenarios, the number of benign nodes is generally greater than that of malicious nodes, and the updates from benign nodes are usually closer to the direction of the global model and exhibit greater cohesion.
+Based on this observation, we select the cluster with the largest number of nodes, \(C_{max} = \{R_{i_0}, R_{i_1}, \ldots, R_{i_n}\}\), as the primary focus for analysis.
+To further extract the main features or patterns of this cluster, we perform singular value decomposition (SVD)\cite{wang2023scfl} on the matrix formed by all nodes in this cluster.
+Since the left singular vectors of the SVD decomposition, \(\tilde{G}^t\), represent the main directions of the data, \(\tilde{G}^t\) can be considered the primary feature of benign nodes in the low-frequency domain.
 
@@
 \end{equation}
+
 % 公式\ref{eq:singular}展示了计算左奇异向量$\tilde{G}^t$的主要过程，其中\(H^t = ({G_{i_0}^t}, {G_{i_1}^t}, \ldots, {G_{i_n}^t}) \in \mathbb{R}^{m \times n}\)为该簇节点的低频向量堆叠而成的矩阵，其中每一列代表一个节点的低频向量，$\lambda_{max}^t$与$xi_{max}^t$分别对应了矩阵$\hat{H}^t \gets (H^t)^{T} H^t$的最大特征值及其特征向量。通过这种方式，我们有效地提取了反映良性节点全局更新在频域上的主要特征，并将$\tilde{G}^t$作为“干净成分”，为后续恶意节点检测提供基准依据。
@@
 $\lambda_{max}^t$ and $\xi_{max}^t$ correspond to the largest eigenvalue and its eigenvector of the matrix $\hat{H}^t \gets (H^t)^{T} H^t$, respectively.
-In this way, we effectively extract the main features that reflect the global updates of benign nodes in the frequency domain, and $\tilde{G}^t$ is used as the "clean component," providing a benchmark for subsequent malicious node detection.
-
-\textbf{Chi-square distance calculation:}
+In this way, we effectively extract the main features that reflect the global updates of benign nodes in the frequency domain, and $\tilde{G}^t$ is used as the clean ingredient for subsequent malicious node detection.
+
+\subsubsection{Chi-square distance calculation}
 % 我们利用每个节点的低频向量与“干净成分”之间的差异度来作为衡量恶意节点和良性节点的依据。对于每个节点的低频向量 \(G_i^t\) 以及上一步中求得的“干净成分” \(\tilde{G}^t\)，通过卡方距离来计算两者之间的差异度，得到距离差异集合$S^t = Chi^t_i, Chi^t_2, \ldots, Chi^t_N$。卡方距离的计算公式为：
-We use the divergence between each node's low-frequency vector and the "clean component" as a basis for distinguishing between malicious and benign nodes.
-For each node's low-frequency vector \(G_i^t\) and the "clean component" \(\tilde{G}^t\) obtained in the previous step, we calculate their divergence using the Chi-square distance, resulting in a set of distance differences \(S^t = \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}\).
-The formula for calculating the Chi-square distance is given by:
+We use the divergence between each node's low-frequency vector and the clean ingredient as a basis for distinguishing between malicious and benign nodes.
+For each node's low-frequency vector \(G_i^t\) and the clean ingredient \(\tilde{G}^t\) obtained in the previous step, we calculate their divergence using the Chi-square distance, resulting in a set of distance differences \(S^t = \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}\).
+The formula for the Chi-square distance is expressed as:
 
@@
 
-\textbf{Single-round malicious node detection:}
+\subsubsection{Single-round malicious behavior perception}
 % 为了准确地识别恶意节点，我们利用良性节点的更新与干净成分的频率分布高度相似这一特性，对距离差异集合$S^t$进一步进行聚类分析。具体而言，我们采用流行的KMeans聚类算法\cite{wan2023four}对距离差异集合$S^t$进行聚类，并将类别数设置为2，因此聚类结果为两个簇\(C'_1, C'_2\)。基于在每轮训练中良性节点的数量通常多于恶意节点，以及良性节点与干净成分之间的距离差异通常更小，我们将 \(C'_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)。对于另一簇\(C'_k\)（\(k \neq {max}\)），则将其中所有节点标记为恶意节点，记作\(U_{mal}\)。
-To accurately identify malicious nodes, we leverage the characteristic that the updates of benign nodes exhibit a high degree of similarity in frequency distribution with the clean component.
-We perform a further clustering analysis on the set of distance differences \(S^t\).
-Specifically, we use the popular KMeans\cite{wan2023four} clustering algorithm to cluster the set \(S^t\), setting the number of clusters to 2.
-Consequently, the clustering results yield two clusters, \(C'_1, C'_2\).
-Based on the observation that in each round of training, the number of benign nodes is typically greater than that of malicious nodes, and the distance differences between benign nodes and the clean component are usually smaller, we label all nodes in \(C'_{max}\) as benign nodes, denoted as \(U_{nor}\).
-For the other cluster \(C'_k\) (\(k \neq {max}\)), all nodes within it are labeled as malicious nodes, denoted as \(U_{mal}\).
+To accurately identify malicious nodes, we leverage the fact that the updates of benign nodes exhibit a high degree of similarity in frequency distribution with the clean component.
+We conduct a further clustering analysis on the set of distance differences \(S^t\).
+Specifically, we employ the popular KMeans\cite{wan2023four} clustering algorithm to cluster the set \(S^t\), setting the number of clusters to 2.
+Consequently, the clustering algorithm produce two clusters, \(C'_1, C'_2\).
+Based on the observation that in each round of training, the number of benign nodes is typically greater than that of malicious nodes, and the distance differences between benign nodes and the clean component are generally smaller, we label all nodes in \(C'_{max}\) as benign nodes, denoted by \(U_{nor}\).
+For the other cluster \(C'_k\) (\(k \neq {max}\)), all nodes within it are labeled as malicious nodes, denoted by \(U_{mal}\).
 
 % 算法\ref{alg:malicious-node-detection}展示了单轮恶意用户识别的整体过程，其中3-6行代表了频率转换的计算过程，7-12行代表了“干净分量”$\tilde G^t$的计算过程，13-16行代表了每个用户与“干净分量”间的卡方差异度的计算过程，最后17-18行代表了通过KMeans聚类算法进行恶意用户检测的计算过程。
-Algorithm \ref{alg:malicious-node-detection} presents the overall process of Instantaneous Attack Behavior Perception.
-Lines 3-6 represent the computation process of frequency transformation, lines 7-12 represent the computation process of the clean component $\tilde{G}^t$, lines 13-16 represent the calculation of the Chi-square divergence between each user and the clean component, and finally, lines 17-18 represent the computation process of malicious user detection using the KMeans clustering algorithm.
+Algorithm \ref{alg:malicious-node-detection} outlines the overall process of Instantaneous Attack Behavior Perception. 
+% Lines 3-6 represent the computation process of frequency transformation, lines 7-12 represent the computation process of the clean component $\tilde{G}^t$, lines 13-16 represent the calculation of the Chi-square divergence between each user and the clean component, and finally, lines 17-18 represent the computation process of malicious user detection using the KMeans clustering algorithm.
+Lines 3-6 describe the computation process of frequency transformation, lines 7-12 detail the computation of the clean component $\tilde{G}^t$, lines 13-16 cover the calculation of the Chi-square divergence between each user and the clean component, and finally, lines 17-18 outline the computation process of malicious user detection using the KMeans clustering algorithm.
 
@@
 \State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
-
+\State{\color{CadetBlue}/* \textbf{Frequency Domain Transformation */}} 
 % \State Step 1: Frequency Domain Transformation
@@
 % \State
-
+\State{\color{CadetBlue}/* \textbf{Clean Ingredient Extraction */}} 
 % \State Step 2: Clean Ingredient Extraction
@@
 % \State
-
+\State{\color{CadetBlue}/* \textbf{Chi-square distance calculation */}} 
 % \State Step 3: Chi-square distance calculation
@@
 % \State
-
-% \State Step 4: Malicious Node Detection
+\State{\color{CadetBlue}/* \textbf{Single-round malicious behavior perception */}} 
+% \State Step 4: Single-round malicious behavior perception
 \State $\{C_1, C_2\} \gets KMeans(S, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
@@
 \subsection{Long-term Attack Intention Detection}
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=\linewidth]{figures/fig3.png}
-    \caption{SecFFT's long-term attack intention detection module and secure aggregation}
-    \label{fig2:instant}
-\end{figure}
+
 % \textbf{Motivation}: 为了规避异常检测，有很多通过多轮次的组合攻击来植入后门的攻击。这些攻击很难在单轮次中检测出来，大致分为三类：1)限制大小的攻击，如\cite{geisler2024attacking, chen2024optimal}，这些攻击方法会限制单次攻击的大小，使得攻击并不是很明显，从而变得难以检测；2)限制角度的攻击，如\cite{you2023three, sagliano2024powered, dong2023adaptive}，这些攻击会限制每次攻击的角度，使其与正常的攻击类似从而变得难以识别；3)限制符号的攻击，如\cite{wan2023average, zhu2023boosting}，这些攻击通过梯度缩放或者梯度合成，控制恶意攻击的梯度与正常客户端梯度的正负维持一致，从而增加识别难度。本部分结合每个客户端的历史记录，通过识别攻击者最终的模型引导意图点来识别恶意节点。
@@
 
-\textbf{Overview}: The previous defense mechanisms have effectively identified single-round attacks; this section focuses on leveraging clients' historical records for effective identification.
+\textbf{Overview}: The previous defense algorithms have effectively identified single-round attacks; this section focuses on leveraging clients' historical records for effective identification.
 We maintain the global models $\theta_g^{t'}$ from the past $T$ rounds, where $\max\{t-T+1, 1\}\leq t'\leq t$, and consider their flattened versions as points in a high-dimensional space.
@@
 For each client, we use the Minimum Enclosing Ball algorithm to compute a minimal hypersphere that covers a $\zeta$ proportion of the ray.
-The final position of the hypersphere's center can be regarded as the intended steering point of the global model for the corresponding client, and the radius of the hypersphere can be considered the confidence level of that client.
+The final position of the hypersphere's center can be regarded as the intended steering point of the global model for the corresponding node, and the radius of the hypersphere can be regarded as the reliability level.
 
@@
 
-\subsubsection{Construction of Weights updates and model databases }
+\subsubsection{Construction of weights updates and model databases}
 
@@
 Let the global model in the $t$-th round be denoted as $\theta_t$, and the model of client $i$ after training in the $t$-th round be denoted as $\theta^t_i$.
-Client $i$ computes its update in the $t$-th round as the difference between the trained model $\theta^t_{i}$ and the global model received before training $\theta^t$, i.e., $\triangledown \theta^t_{i} = \theta^t_{i} - \theta^t$.
+Client $i$ computes its update in the $t$-th round as the difference between the trained model $\theta^t_{i}$ and the global model received before training $\theta^t$, i.e., $\triangledown \theta^t_{i} = \theta^t_{i} - \theta_g^t$.
 The client uploads the update $\triangledown \theta^t_{i}$ to the central server.
 While aggregating, the central server records the flattened result of each client's update in the current round, $\bar{\theta_i^t}$, as well as the global model $\theta^{t-1}$ distributed by the central server in the previous round.
-The central server retains the models and update histories for up to $T$ rounds.% The main algorithm process for "Keep T-rounds History" is shown in lines 3-13 of Algorithm \ref{alg:malicious-node-detection-history}.
+The central server retains the models and weights update histories for up to $T$ rounds.% The main algorithm process for "Keep T-rounds History" is shown in lines 3-13 of Algorithm \ref{alg:malicious-node-detection-history}.
 
@@
 % “Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
-The main algorithm process for "Obtain the Purpose Intention" is shown in lines 14-18 of Algorithm \ref{alg:malicious-node-detection-history}.
+%The main algorithm process for "Obtain the Purpose Intention" is shown in lines 14-18 of Algorithm \ref{alg:malicious-node-detection-history}.
 This section can be further divided into two parts: "Construct Ray Model" and "Minimum Enclosing Hypersphere Calculation."
 % “Construct Ray Model”的主要过程如下。对于每个客户端 \(R_i\)，中央服务器保留了最近 \(T\) 轮的全局模型历史以及每轮次的更新变化历史。设 \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) 是最近 \(T\) 轮次的全局模型，且这些全局模被“展平”到了高维空间中的一个点。类似地，设 \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) 是最近 \(T\) 轮次客户端 \(i\) 上传的展平后的梯度变化向量。
-The main process of "Construct Ray Model" is as follows.
+
+%The main process of "Construct Ray Model" is as follows. 
 For each client \(R_i\), the central server retains the global model history and the update history for the most recent \(T\) rounds.
@@
 % “Minimum Enclosing Hypersphere Calculation”的主要过程如下。基于构建的射线模型，使用最小覆盖球算法找到一个能够覆盖至少 \( \zeta \) 比例的射线的最小超球。首先，设定初始球心 \( O_{i,0} \) 为所有射线起点的几何中心，计算公式如下：
-The main process of "Minimum Enclosing Hypersphere Calculation" is as follows.
-Based on the constructed ray model, the Minimum Enclosing Hypersphere Ball (MEHB) algorithm is used to find the smallest hypersphere that can cover at least a \( \zeta \) proportion of the rays.
+Therefore, we approximate the attack intention hiddden behind the series of behaviors based on Minimum Enclosing Hypersphere Ball (MEHB) construction as follows.
+Based on the constructed ray model, the MEHB model is adopted to find the smallest hypersphere that can cover at least a \( \zeta \) proportion of the rays, which denotes the intention of the current node.
 First, the initial center of the hypersphere \( O_{i,0} \) is set to the geometric center of all ray starting points, calculated as follows:
@@
 
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=\linewidth]{figures/fig3.png}
+    \caption{Long-term attack intention detection module and secure aggregation}
+    \label{fig3:longterm}
+\end{figure}
+
 The radius of the moved center is:
@@
 
-\subsubsection{driven malicious intention detection}
+\subsubsection{LOF-driven malicious intention detection}
 % “Abnormal Detection”的主要过程基于局部离群因子（Local Outlier Factor, LOF）得到异常点。LOF算法是一种基于密度的异常检测方法，算法的核心思想是通过计算一个数值$lof_i$来反应节点$i$的异常程度。$lof_i$大致意思是节点$i$目的意图点$O_i$周围意图点所处位置的平均密度比上$O_i$所在位置的密度。比值越大于$1$，则$O_i$所在位置的密度越小于周围其他意图点所在位置的密度，即$O_i$越有可能是异常点。首先定义意图点$O_i$的$q$距离$\widetilde{dis_i^q}$，假设高维空间中存在节点$j$的意图点$O_j$，则有$O_j$与$O_i$之间的距离为$\|O_i-O_j\|$，如果满足以下两个条件，我们就认为$\widetilde{dis_i^q}=\|O_i-O_j\|$：
-The main process of "Abnormal Detection" identifies outliers based on the Local Outlier Factor (LOF).
+The main process of Abnormal Detection identifies outliers based on the Local Outlier Factor (LOF).
 The LOF algorithm is a density-based anomaly detection method.
@@
 \end{equation}
+
 % 也就是说，如果意图点$O_j$远离意图点$O_i$，则两者之间的可达距离就是他们之间的实际距离$\|O_i-O_j\|$；而如果二者距离足够近，则可达距离用意图点$O_i$的$q$距离$\widetilde{dis_i^q}$代替。之后定义意图点$O_i$的局部可达密度$lrd_i$为其$Nei_i$所有意图点的平均可达距离的倒数，即：
-That is, if the intention point $O_j$ is far from the intention point $O_i$, the reachable distance between them is their actual distance $\|O_i-O_j\|$; if they are close enough, the reachable distance is replaced by the $q$-distance $\widetilde{dis_i^q}$ of the intention point $O_i$.
+In another word, if the intention point $O_j$ is far from the intention point $O_i$, the reachable distance between them is their actual distance $\|O_i-O_j\|$; if they are close enough, the reachable distance is replaced by the $q$-distance $\widetilde{dis_i^q}$ of the intention point $O_i$.
 Next, we define the local reachable density $lrd_i$ of the intention point $O_i$ as the reciprocal of the average reachable distance of all intention points in its $Nei_i$:
@@
 
-\subsubsection{Gradients Aggregation}
+\subsubsection{Secure Aggregation}
 % 剔除了异常节点后，依据正常节点的置信度$cre$进行聚合。其中定义：
@@
 \end{equation}
+
 % 激活函数Tanh在$0$到$\infty$范围内是一个上升又快到慢的单调递增函数。当$cre_i\to 0$时$cer_i'\to 0$，也就是说节点$i$的最小覆盖球半径$r_i$很大时该节点在聚合时的权重很小；当$cre_i\to \infty$时$cer_i'\to 1$，也就是说节点$i$的最小覆盖球半径$r_i$很小时该节点在聚合时的权重较大。这样，我们就可以对每个加权处理过的置信度$cer_i'$进行归一化处理，得到权重$w_i$。其中：
@@
 \end{equation}
+
 % 因此第$t$轮模型的梯度聚合公式为：
-Thus, the gradient aggregation formula for the model in the $t$-th round is:
+Thus, the secure aggregation formula for the model in the $t$-th round is:
 
@@
 
-\State \textbf{Step 1: Keep T-rounds History}
 \For {Client $i$}
-    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_{i}^t)$ \Comment{Record flattened gradients  and models $\theta_g^{t-1}$}
+\State{\color{CadetBlue}/* \textbf{Construction of updates and model databases */}} 
+    \State Record flattened gradients $\bar{\theta_i^t}$ and models $\theta_g^{t-1}$
     % \State $\widetilde{\theta_{i}^{t'-1}}  \gets Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'}  \gets \overline{\triangledown\theta_{i}^{t'}}$ for $t'  \gets \max\{t-T+1, 1\}, \ldots, t$ \Comment{Construct rays}
-    \State $\widetilde{\theta_{i}^{t'-1}}  \gets Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'}  \gets \overline{\triangledown\theta_{i}^{t'}}$ , $\max\{t-T+1, 1\}\leq t' \leq t$ \Comment{Construct rays}
-\EndFor
-
-\State \textbf{Step 2: Obtain the Purpose Intention}
-\For {Client $i$}
+    \State Construct rays for each $'$, $\max\{t-T+1, 1\}\leq t' \leq t$
+
+\State{\color{CadetBlue}/* \textbf{Construction of attack intention */}}
+
     \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
@@
     \State  $cre_i  \gets \frac{1}{r_i + \rho}$ \Comment{Calculate confidence}
-\EndFor
-
-\State \textbf{Step 3: Abnormal Detection}
-\For {Client $i$}
+
+\State{\color{CadetBlue}/* \textbf{LOF-driven malicious intention detection*/}}
+
     \For {Each point $O_j \neq O_i$}
@@
     \State $rea_{i,j}  \gets \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$  \Comment{Compute reachability distance}
-    \State  $lrd_i  \gets \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$ \Comment{Calculate local reachability density}
+    \State  $lrd_i  \gets \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$ \Comment{Calculate reachability density}
     \State $lof_i  \gets \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
-\EndFor
+
 % \For {Client $i$}
@@
 
-\State \textbf{Step 4: Gradients Aggregation}
-\For {Client $i\in U_{nor}$}
+\State{\color{CadetBlue}/* \textbf{Secure aggregation of global FFT model*/}} 
         \State $cre_i'  \gets \tanh(cre_i)$\Comment{Compute adjusted confidence}
@@
 
-\State \textbf{Output:} $\theta_g^t \gets \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$\Comment{Aggregated global model update}
+\State \textbf{Output:} $\theta_g^t \gets \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$\Comment{Aggregate global model}
 \end{algorithmic}
@@
 % This section presents a thorough evaluation of SecFFT on two benchmark datasets, aiming to illustrate its effectiveness. 本实验在一台Windows操作系统的服务器上进行，28核心128GB内存，以及2块NVIDIA GeForce RTX 3090 GPU(24G)。
-This section thoroughly evaluates SecFFT on the benchmark dataset to illustrate its effectiveness, which begins by detailing the experimental setup and environment, followed by a presentation and analysis of the experimental results.
+This section thoroughly evaluates SecFFT on the benchmark dataset to illustrate its effectiveness, which begins by detailing the experimental setup and environment, followed by the analysis of the experimental results.
 
@@
  % \textbf{微调模型}：我们采用CLIP的CLIP-ViT-B/32\cite{huggingface_clip}模型作为微调所使用的预训练模型。CLIP是一种通过对比学习在文本和图像数据上进行预训练的模型，能将自然语言和视觉信息映射到同一特征空间中。CLIP-ViT-B/32基于ViT\cite{vit}架构，包含12层Transformer编码器，隐藏层维度为768，多头注意力头数为12，使用32x32的图像块作为输入。在微调过程中，我们使用LORA\cite{lora}方案仅在Vision Encoder模块插入低秩矩阵，保持Textual Encoder模块不变。我们设定低秩矩阵的秩为16，学习率为$10^{-4}$，以在有限计算资源下高效微调模型，使其更好地适应特定任务的数据分布。
-\textbf{Fine-tuning model:} We adopted the \textbf{CLIP-ViT-B/32}\cite{huggingface_clip} model from \cite{clip} as the pre-trained model for federated fine-tuning.
-CLIP is a model pre-trained on both text and image data through contrastive learning, capable of mapping natural language and visual information into the same feature space.
+\textbf{Models:} 
+% We adopted the \textbf{CLIP-ViT-B/32}\cite{huggingface_clip} model from \cite{clip} as the pre-trained model for federated fine-tuning.
+CLIP is a vision language model pre-trained on both text and image data through contrastive learning, capable of mapping natural language and visual information into the same feature space.
 CLIP-ViT-B/32 is based on the ViT\cite{vit} architecture and contains 12 layers of Transformer encoders, with a hidden dimension of 768 and 12 attention heads, using 32x32 image patches as input.
@@
 We set the rank of the low-rank matrices to 16 and the learning rate to \textbf{$10^{-4}$} to efficiently fine-tune the model under limited computational resources, allowing it to better adapt to the data distribution of specific tasks.
-
-% \textbf{攻击方式}：对于单轮恶意用户检测，我们使用包括MR\cite{MR}、EDGE CASE\cite{EDGE_CASE}、以及NEUR\cite{zhang2022neurotoxin}在内的三种针对联邦学习场景的最新攻击。MR攻击通过将中毒图像与正常图像混合来创建恶意数据集，并使用投影梯度下降法进行本地训练来达到植入后门的效果；EDGE CASE攻击利用罕见的“边缘情况”样本，通过数据或模型投毒在联邦学习模型中插入后门；Neurotoxin攻击则尝试通过识别在正常节点训练中不常更新的参数，并利用这些参数插入后门，以提高后门的持久性。
-\textbf{Attack methods:} For Instantaneous Attack Behavior Perception, we used three of the latest attacks targeting federated learning scenarios, including \textbf{MR}\cite{MR}, \textbf{EDGE CASE}\cite{EDGE_CASE}, and \textbf{NEUR}\cite{zhang2022neurotoxin}.
-The MR attack creates a malicious dataset by mixing poisoned images with normal ones and uses the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack utilizes rare "edge-case" samples to insert backdoors into the federated learning model through data or model poisoning; the NEUR attack attempts to identify parameters that are rarely updated during normal node training and uses these parameters to insert backdoors, enhancing the persistence of the backdoor.
+We adopted the \textbf{CLIP-ViT-B/32}\cite{huggingface_clip} model from \cite{clip} as the pre-trained model for federated fine-tuning.
+CLIP is a vision-language model pre-trained on both text and image data through contrastive learning, capable of mapping natural language and visual information into a shared feature space.
+CLIP-ViT-B/32 is based on the ViT\cite{vit} architecture and consists of 12 layers of Transformer encoders, with a hidden dimension of 768 and 12 attention heads, processing 32x32 image patches as input.
+During fine-tuning, we employed the \textbf{LORA}\cite{lora} method to introduce low-rank matrices only into the Vision Encoder module, while keeping the Textual Encoder module unchanged.
+We set the rank of the low-rank matrices to 16 and the learning rate to \textbf{$10^{-4}$} to efficiently fine-tune the model under limited computational resources, enabling it to better adapt to the data distribution of specific tasks.
+
+% \textbf{攻击方式}：对于单轮恶意用户检测，我们使用包括MR\cite{MR}、EDGE CASE\cite{EDGE_CASE}、以及NEUR\cite{zhang2022neurotoxin}在内的三种针对联邦学习场景的最新攻击。MR攻击通过将中毒图像与正常图像混合来创建恶意数据集，并使用投影梯度下降法进行本地训练来达到植入后门的效果；EDGE CASE攻击利用罕见的“边缘情况”样本，通过数据或模型投毒在联邦学习模型中插入后门；Neurotoxin攻击则尝试通过识别在正常节点训练中不常更新的参数，并利用这些参数插入后门，以提高后门的持久性。For Instantaneous Attack Behavior Perception,?
+\textbf{Attack paradigms:} we employed three state-of-the-art attacks targeting federated learning scenarios, namely \textbf{MR}\cite{MR}, \textbf{EDGE CASE}\cite{EDGE_CASE}, and \textbf{NEUR}\cite{zhang2022neurotoxin}.
+The MR attack generates a malicious dataset by combining poisoned images with normal ones and employing the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack employs rare "edge-case" samples to inject backdoors into the federated learning model through data or model poisoning; the NEUR attack seeks to identify parameters that are seldom updated during normal node training and uses these parameters to insert backdoors, thereby enhancing the persistence of the backdoor.
+
+\begin{figure*}[!ht]
+    \centering
+    \includegraphics[width=0.9\linewidth]{figures/lab1-combined.pdf}
+    \caption{ASR and TSR of various defense mechanisms (FedAVG, FLTrust, Foolsgold, Flame, SecFFT) under three attacks (MR, NEUR, Edge case).}
+    \label{fig:lab1}
+\end{figure*}
 
 % \textbf{对比算法}：对于单轮恶意用户检测算法，我们对比了三种聚合算法：FedAVG\cite{FedAVG}、FLTrust\cite{FLTrust}和Flame\cite{FLAME}。其中FedAVG根据每个节点数据集的大小对其上传的更新进行加权聚合；FLTrust利用一个干净的数据集，仅聚合那些上传更新与该干净数据集上训练所得更新余弦相似度较高的节点；而Flame则通过模型聚类和权重剪裁来估计并注入适量噪声，有效消除联邦学习中的后门攻击。
-\textbf{Baseline defense algorithms:} For Instantaneous Attack Behavior Perception, we compared four aggregation algorithms: \textbf{FedAVG}\cite{FedAVG}, \textbf{Foolsgold}\cite{foolsgold}, \textbf{FLTrust}\cite{FLTrust}, and \textbf{Flame}\cite{FLAME}.
+\textbf{Baseline defense mechanisms:} 
+% For Instantaneous Attack Behavior Perception, we compared four aggregation algorithms: \textbf{FedAVG}\cite{FedAVG}, \textbf{Foolsgold}\cite{foolsgold}, \textbf{FLTrust}\cite{FLTrust}, and \textbf{Flame}\cite{FLAME}.
 FedAVG performs weighted aggregation of the updates uploaded by each node based on the size of their dataset; FoolsGold distinguishes between benign and malicious clients by assessing pairwise similarity among model updates, subsequently down-weighting abnormal updates on the FL server; FLTrust uses a clean dataset and only aggregates updates from nodes whose updates have a high cosine similarity with the updates obtained from the clean dataset; Flame estimates and injects an appropriate amount of noise through model clustering and weight clipping to effectively eliminate backdoor attacks in federated learning.
+we compared four aggregation mechanisms: \textbf{FedAVG}\cite{FedAVG}, \textbf{Foolsgold}\cite{foolsgold}, \textbf{FLTrust}\cite{FLTrust}, and \textbf{Flame}\cite{FLAME}.
+FedAVG conducts weighted aggregation of updates uploaded by each node based on the size of its dataset.
+FoolsGold differentiates between benign and malicious clients by evaluating pairwise similarity among model updates and subsequently down-weighting anomalous updates on the FL server.
+FLTrust employs a clean dataset and aggregates only those updates from nodes that exhibit high cosine similarity with the updates derived from the clean dataset.
+Flame estimates and injects an appropriate amount of noise via model clustering and weight clipping to mitigate backdoor attacks in federated learning effectively.
 
@@
 % 就像其他文章中的评价指标一样，我们使用两个关键指标来评估投毒攻击与防御方法的效果，即ASR（攻击成功率）和 TSR（测试成功率）。ASR表示恶意节点成功诱导全局模型成功预测指定目标的概率。攻击者的目标是最大化ASR，而有效的防御措施则旨在防止ASR上升。TSR表示全局模型在测试集上的预测正确率。攻击者的目标是尽量维持模型的TSR不变，以避免被轻易检测到，而有效的防御措施则不应显著降低全局模型的TSR。
-Similar to evaluation metrics used in other works\cite{tang2023port, jin2024learning, rong2023special}, we use two key metrics to assess the effectiveness of poisoning attacks and defense methods: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
+% Similar to evaluation metrics used in other works\cite{tang2023port, jin2024learning, rong2023special}, we use two key metrics to assess the effectiveness of poisoning attacks and defense methods: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
 ASR represents the probability that malicious nodes successfully induce the global model to predict the specified target.
@@
 The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
+Similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
+ASR denotes the probability that malicious nodes successfully manipulate the global model to predict a specified target.
+The attacker aims to maximize the ASR, whereas effective defense mechanisms strive to prevent an increase in ASR.
+TSR indicates the accuracy of the global model on the test set.
+The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR.
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figures/lab2-combined.pdf}
+    \caption{Visualization of node identification results under three different attack scenarios (MR, Edge Case, NEUR) for various defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE dimensionality reduction.
+The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign and benign nodes incorrectly identified as malicious.
+}
+    \label{fig:lab2}
+\end{figure*}
 
@@
 To validate the effectiveness of our proposed method, we conducted experiments under three types of attacks: MR, Edge case, and NEUR.
-We compared our method with FedAVG (Baseline), FoolsGold, FLTrust, and Flame to evaluate the corresponding TSR and ASR under different defense algorithms.
+We compared our method with FedAVG (Baseline), FoolsGold, FLTrust, and Flame to evaluate the corresponding TSR and ASR under different defense mechanisms.
 The experimental results are shown in Figure \ref{fig:lab1}.
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{figures/lab1-combined.pdf}
-    \caption{ASR and TSR of various defense algorithms (FedAVG, FLTrust, Foolsgold, Flame, SecFFT) under three attacks (MR, NEUR, Edge case).}
-    \label{fig:lab1}
-\end{figure}
-
 % 从图中可以看出，SecFFT在面对三种攻击场景（MR、NEUROTOXIN、EDGE_CASE）时展现了最强的鲁棒性和出色的模型性能。在所有场景下，SecFFT的攻击成功率（ASR）始终接近于零，测试准确率（TSR）依然维持在高位，这意味着该算法能够有效防御攻击，能够成功识别并防御恶意用户，同时保持全局模型的性能和准确性。相比之下，其他防御算法表现则较为逊色。虽然Flame在降低ASR方面同样表现优异，能有效识别出恶意用户，但其在识别过程中引入了较多噪声，导致全局模型的准确率（TSR）下降，特别是在MR攻击下，性能损失更为显著。FLTrust在应对MR攻击时几乎完全失效，ASR迅速上升，未能有效防御；尽管在NEUROTOXIN和EDGE_CASE场景下表现有所改善，但防御效果依然不够稳定。Foolsgold在MR和NEUROTOXIN攻击下的防御效果较差，ASR依旧很高，仅在EDGE case下表现出一些效果，但并不显著。总体而言，这些算法在抵御攻击时未能同时兼顾模型的性能，进一步突显了SecFFT在联邦学习攻击防御中的显著优势，成为最优的防御选择。
-As shown in the figure, SecFFT demonstrates the strongest robustness and excellent model performance when faced with three types of attack scenarios (MR, NEUR, EDGE CASE).
+% As shown in the figure, SecFFT demonstrates the strongest robustness and excellent model performance when faced with three types of attack scenarios (MR, NEUR, EDGE CASE).
 In all scenarios, SecFFT's ASR remains close to zero, while the TSR stays high, indicating that the algorithm can effectively defend against attacks by successfully identifying and mitigating malicious users while maintaining the performance and accuracy of the global model.
-In contrast, other defense algorithms perform less favorably.
+In contrast, other defense mechanisms perform less favorably.
 Although Flame also performs well in reducing ASR and effectively identifying malicious users, it introduces a significant amount of noise during the identification process, which leads to a decrease in the global model's accuracy (TSR), particularly under the MR attack, where the performance loss is more pronounced.
@@
 FoolsGold exhibits poor defense performance under MR and NEUR attacks, with ASR still high, showing some effectiveness only in the EDGE CASE scenario, but not significantly.
-Overall, these algorithms fail to balance model performance while defending against attacks, further highlighting SecFFT's significant advantage in federated learning attack defense, making it the optimal choice for defense.
+Overall, these mechanisms fail to balance model performance while defending against attacks, further highlighting SecFFT's significant advantage, making it the optimal choice for defense.
+As depicted in the figure, SecFFT exhibits the highest robustness and superior model performance when confronted with three types of attack scenarios (MR, NEUR, EDGE CASE).
+Across all scenarios, SecFFT's ASR remains near zero, whereas the TSR remains high, indicating that the algorithm effectively defends against attacks by accurately identifying and mitigating malicious nodes while preserving the performance and accuracy of the global model.
+Conversely, other defense algorithms perform less effectively.
+Although Flame is also effective in reducing ASR and identifying malicious nodes, it introduces substantial noise during the identification process, leading to a decline in the global model's accuracy (TSR), especially under the MR attack, where the performance degradation is more pronounced.
+FLTrust almost fails to defend against MR attacks, with ASR rising rapidly, rendering it ineffective.
+While its performance improves under NEUR and EDGE CASE scenarios, its defense effectiveness remains inconsistent.
+FoolsGold demonstrates weak defense performance under MR and NEUR attacks, with ASR remaining high, showing limited effectiveness only in the EDGE CASE scenario.
+Overall, these algorithms fail to balance model performance and defense against attacks, further underscoring SecFFT's substantial advantage, establishing it as the optimal choice for defense.
 
@@
 % 为了验证我们所提方法在恶意用节点识别方面具有较高的准确度，我们总结了在三种攻击(MR, Edge case, NEUR)下所有轮次中SecFFT对恶意节点的识别情况，并与FoolsGold, FLTrust, and Flame三种防御算法进行了对比。具体对比结果如图\ref{fig:lab2}所示，我们利用t-sne算法将所有轮次中节点的更新降维到了二维平面，图中红色点表示被错误识别的节点，包括恶意节点被识别成良性节点以及良性节点被错误识别成恶意节点。对于无法直接获得节点识别情况的Foolsgold防御算法，我们通过利用KMeans聚合算法将该防御算法过程中分配给每个用户的聚合权重聚成两类，并取最大类作为良性节点其余作为恶意节点的结果作为统计标准。
-To validate the high accuracy of our proposed method in identifying malicious nodes, we summarized the detection results of SecFFT under three types of attacks (MR, Edge Case, NEUR) across all rounds and compared them with three defense algorithms: FoolsGold, FLTrust, and Flame.
+% To validate the high accuracy of our proposed method in identifying malicious nodes, we summarized the detection results of SecFFT under three types of attacks (MR, Edge Case, NEUR) across all rounds and compared them with three defense mechanisms: FoolsGold, FLTrust, and Flame.
 The specific comparison results are shown in Figure \ref{fig:lab2}.
@@
 For the Foolsgold defense algorithm, which does not directly provide node identification results, we used the KMeans clustering algorithm to classify the aggregation weights assigned to each user during the defense process into two clusters, considering the larger cluster as benign nodes and the remaining as malicious nodes for evaluation purposes.
-
-\begin{figure*}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{figures/lab2-combined.pdf}
-    \caption{Visualization of node identification results under three different attack scenarios (MR, Edge Case, NEUR) for various defense algorithms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE dimensionality reduction.
-The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign and benign nodes incorrectly identified as malicious.
-}
-
-    \label{fig:lab2}
-\end{figure*}
+To validate the high accuracy of our proposed method in identifying malicious nodes, we summarized the detection results of SecFFT under three types of attacks (MR, EDGE CASE, NEUR) across all rounds and compared them with three defense mechanisms: FoolsGold, FLTrust, and Flame.
+The specific comparison results are illustrated in Figure \ref{fig:lab2}.
+We employed the t-SNE algorithm to reduce the dimensionality of the nodes' updates across all rounds to a two-dimensional plane.
+In the figure, red dots represent misidentified nodes, which include malicious nodes mistakenly identified as benign and benign nodes mistakenly identified as malicious.
+For the FoolsGold defense algorithm, which does not directly provide node identification results, we employed the KMeans clustering algorithm to classify the aggregation weights assigned to each user during the defense process into two clusters, considering the larger cluster as benign nodes and the remaining as malicious nodes for evaluation purposes.
+
 % 如图所示，SecFFT 的错误识别率最低，仅为 3%，表明其在各种攻击模式下具有更强的防御能力和鲁棒性，能够准确区分恶意节点和良性节点。而 Flame、FLTrust 和 FoolsGold 的错误识别率分别为 12%、19.5% 和 37.5%，错误识别的节点分布较为广泛，尤其是 FoolsGold 的错误识别率最高，显示出其在应对复杂攻击场景时的防御效果较差。相比之下，SecFFT 在应对多种攻击类型时表现最为优异，能有效降低错误识别率，展示了更好的泛化能力和准确性。
-As shown in the figure, SecFFT has the lowest misidentification rate, at only 3\%, indicating its stronger defense capability and robustness in various attack scenarios, accurately distinguishing between malicious and benign nodes.
+% As shown in the figure, SecFFT has the lowest misidentification rate, at only 3\%, indicating its stronger defense capability and robustness in various attack scenarios, accurately distinguishing between malicious and benign nodes.
 In contrast, the misidentification rates of Flame, FLTrust, and FoolsGold are 12\%, 19.5\%, and 37.5\%, respectively, with misidentified nodes more widely distributed.
@@
 Comparatively, SecFFT performs the best in dealing with various attack types, effectively reducing the misidentification rate and showing better generalization ability and accuracy.
-
-\subsection{Performance of SecFFT}
+As illustrated in the figure, SecFFT achieves the lowest misidentification rate, at only 3\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes.
+Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 12\%, 19.5\%, and 37.5\%, respectively, with misidentified nodes more broadly distributed.
+Notably, FoolsGold exhibits the highest misidentification rate, demonstrating suboptimal defense performance in managing complex attack scenarios.
+Comparatively, SecFFT outperforms other methods in handling various attack types, effectively reducing the misidentification rate and demonstrating superior generalization ability and accuracy.
+
+\vspace{-0.28cm}
+\subsection{Performance of Attack intention detection}
 
@@
     \includegraphics[width=\linewidth]{figures/lab3-combined.pdf}
-    \caption{lab3}
+    \caption{Detection performance of different defense technologies against intelligent attackers with sophisticated multi-round strategies}
     \label{fig:lab3}
@@
 
-\subsection{}
-
-\begin{table*}[h!]
+%为了验证SecFFT面对具有复杂攻击策略的高级隐蔽后门攻击时候的攻击意图构建和有效防御能力，我们在NEUR攻击的基础之上，分别加上了Size约束跟Angle约束等多轮次策略。如图\ref{fig:lab3}所示，通过对比Foolsgold、Fltrust、Flame等仅基于行为的典型防御机制可以看出，基于意图的SecFFT能够显著提升攻击识别能力。即便部分防御手段如Flame能够对一些高隐蔽攻击行为进行有效识别，在叠加了复杂的多轮次攻击策略后，防御机制的识别能力迅速被绕过。而与之相反，我们的方法即便在面对最复杂的“size+angle”策略时，虽然绝对值变小，但是差距依然显著，因而依旧能够区分出攻击者与正常节点之间意图的不同。
+%表\ref{tab:detect} 则详细列出了四种防御手段面对不同策略时的分类量化指标情况，可见，SecFFT不仅能够保持较好的抵御后门攻击的能力，同时也维持了相对最好的判别精度，误判率得到很好限缩，可靠性有保障。
+To validate the capability of SecFFT in constructing attack intent and effectively defending against advanced covert backdoor attacks employing complex strategies, we added Size and Angle constraints to the NEUR attack over multiple rounds.
+As shown in Fig.
+\ref{fig:lab3}, by comparing with typical behavior-based defense mechanisms such as Foolsgold, FLTrust, and Flame, it is evident that the intent-based SecFFT significantly enhances attack detection capabilities.
+Even though certain defense methods like Flame can effectively identify some highly covert attack behaviors, their detection performance is quickly bypassed when more complex multi-round attack strategies are introduced.
+In contrast, our method, even when facing the most sophisticated "size+angle" strategy, maintains a notable difference, enabling the continued distinction between the attacker's intent and that of benign nodes, despite a decrease in absolute values.
+
+Table \ref{tab:detect} provides a detailed quantitative analysis of the classification metrics for the four defense mechanisms against different strategies.
+It is clear that SecFFT not only consistently preserves its strong backdoor attack mitigation capability but also achieves the best detection accuracy, with significantly reduced false positive rates, ensuring reliable and robust performance.
+
+\begin{table}[h!]
 \small
 \centering
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
+\caption{Metrics results with different attack and defense methods.}
+\begin{tabular}{c|c|c|c|c|c|c|c}
 \hline
-Attack & Defense & TP & FP & TN & FN & Accuracy & Precision & Recall & Specificity & FPR & FNR & AUC & MCC \\ \hline
-
-\multirow{4}{*}{Original} & Foolsgold & 10 & 0 & 35 & 5 & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
-                      & FLTrust   & 6  & 0 & 35 & 9 & 0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\ \cline{2-14}
-                      & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
-                      & SecFFT    & \textbf{15} & 0 & 35 & 0  & \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & 0.00 & \textbf{1.00} & \textbf{1.00} \\ \hline
-\multirow{4}{*}{Size} & Foolsgold & 10 & 0 & 35 & 5 & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
-                      & FLTrust   & 6  & 0 & 35 & 9 & 0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\ \cline{2-14}
-                      & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
-                      & SecFFT    & \textbf{15} & 0 & 35 & 0  & \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & 0.00 & \textbf{1.00} & \textbf{1.00} \\ \hline
-\multirow{4}{*}{Angle} & Foolsgold & 10 & 0 & 35 & 5 & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
-                      & FLTrust   & 6  & 0 & 35 & 9 & 0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\ \cline{2-14}
-                      & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ \cline{2-14}
-                      & SecFFT    & \textbf{15} & 0 & 35 & 0  & \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & 0.00 & \textbf{1.00} & \textbf{1.00} \\ \hline
+Strategy & Defense & Acc. & Rec. & FPR & FNR & AUC & MCC \\ \hline
+
+\multirow{4}{*}{None} & Foolsgold & 0.90 & 0.67 & 0.00 & 0.33 & 0.83 & 0.76 \\
+                      & FLTrust   & 0.82 & 0.40 & 0.00 & 0.60 & 0.70 & 0.56 \\
+                      & Flame     & 0.90 & 0.67 & 0.00 & 0.33 & 0.83 & 0.76 \\
+                      & SecFFT    & \textbf{1.00} & \textbf{1.00} & 0.00 & \textbf{0.00} & \textbf{1.00} & \textbf{1.00} \\ \hline
+
+\multirow{4}{*}{Size} & Foolsgold & 0.92 & 0.80 & 0.03 & 0.20 & 0.88 & 0.72 \\ 
+                      & FLTrust   & 0.82 & 0.53 & 0.06 & 0.47 & 0.74 & 0.61 \\ 
+                      & Flame     & 0.92 & 0.73 & \textbf{0.00} & 0.27 & 0.87 & 0.78 \\ 
+                      & SecFFT    & \textbf{0.98} & \textbf{0.93} & \textbf{0.00} & \textbf{0.07} & \textbf{0.96} & \textbf{0.91} \\ \hline
+
+\multirow{4}{*}{Angle} & Foolsgold & 0.88 & 0.73 & 0.06 & 0.27 & 0.84 & 0.68 \\ 
+                       & FLTrust   & 0.86 & 0.60 & 0.03 & 0.40 & 0.80 & 0.65 \\ 
+                       & Flame     & 0.90 & 0.67 & \textbf{0.00} & 0.33 & 0.83 & 0.76 \\ 
+                       & SecFFT    & \textbf{0.96} & \textbf{0.87} & \textbf{0.00} & \textbf{0.13} & \textbf{0.94} & \textbf{0.88} \\ \hline
 \end{tabular}
-\caption{Classification metrics results under different attack and defense methods}
-\end{table*}
+\vspace{1em}
+\begin{tablenotes}
+\scriptsize
+\item ``Acc." stands for Accuracy, ``Rec." for Recall, ``FPR" for False Positive Rate, ``FNR" for False Negative Rate, ``AUC" for Area Under Curve, and ``MCC" for Matthews Correlation Coefficient.
+The strategies are abbreviated as ``None" (No strategy), ``Size" (Size-limited strategy), and ``Angle" (Angle-limited strategy).
+\end{tablenotes}
+
+\label{tab:detect}
+\end{table}
+
+% \begin{table}[h!]
+% \small
+% \centering
+% \begin{tabular}{c|c|c|c|c|c|c|c|c|c}
+% \hline
+% \makecell{Attack \\ strategy} & Defense & Accuracy & Precision & Recall & \makecell{Specificity} & FPR & FNR & AUC & MCC \\ \hline
+
+% \multirow{4}{*}{\makecell{No \\ strategy}} & Foolsgold & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\
+%                       & FLTrust   &  0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\
+%                       & Flame     &  0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\
+%                       & SecFFT    &  \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & \textbf{0.00} & \textbf{1.00} & \textbf{1.00} \\ \hline
+
+% \multirow{4}{*}{\makecell{Size-limited \\ strategy}} & Foolsgold &  0.92 & 0.92 & 0.80 & 0.97 & 0.03 & 0.20 & 0.88 & 0.72 \\ 
+%                       & FLTrust   & 0.82 & 0.80 & 0.53 & 0.94 & 0.06 & 0.47 & 0.74 & 0.61 \\ 
+%                       & Flame     & 0.92 &1.00 & 0.73 & 1.00 & 0.00 & 0.27 & 0.87 & 0.78 \\ 
+%                       & SecFFT    & \textbf{0.98} & 1.00 & \textbf{0.93} & 1.00 & 0.00 & \textbf{0.07} & \textbf{0.96} & \textbf{0.91} \\ \hline
+
+% \multirow{4}{*}{\makecell{Angle-limited \\ strategy}} & Foolsgold &  0.88 & 0.85 & 0.73 & 0.94 & 0.06 & 0.27 & 0.84 & 0.68 \\ 
+%                        & FLTrust   &  0.86 & 0.90 & 0.60 & 0.97 & 0.03 & 0.40 & 0.80 & 0.65 \\ 
+%                        & Flame     &  0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ 
+%                        & SecFFT    &  \textbf{0.96} & 1.00 & \textbf{0.87} & 1.00 & 0.00 & \textbf{0.13} & \textbf{0.94} & \textbf{0.88} \\ \hline
+% \end{tabular}
+% \vspace{1em}
+% \caption{Classification metrics results with different attack and defense methods}\label{tab:detect}
+% \end{table}
+
+% \begin{table*}[h!]
+% \small
+% \centering
+% \begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c}
+% \hline
+% \makecell{Attack \\ strategy} & Defense & TP & FP & TN & FN & Accuracy & Precision & Recall & \makecell{Specificity} & FPR & FNR & AUC & MCC \\ \hline
+
+% \multirow{4}{*}{\makecell{No \\ strategy}} & Foolsgold & 10 & 0 & 35 & 5 & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\
+%                       & FLTrust   & 6  & 0 & 35 & 9 & 0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\
+%                       & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\
+%                       & SecFFT    & \textbf{15} & 0 & 35 & \textbf{0}  & \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & \textbf{0.00} & \textbf{1.00} & \textbf{1.00} \\ \hline
+
+% \multirow{4}{*}{\makecell{Size-limited \\ strategy}} & Foolsgold & 12 & 1 & 34 & 3 & 0.92 & 0.92 & 0.80 & 0.97 & 0.03 & 0.20 & 0.88 & 0.72 \\ 
+%                       & FLTrust   & 8  & 2 & 33 & 7 & 0.82 & 0.80 & 0.53 & 0.94 & 0.06 & 0.47 & 0.74 & 0.61 \\ 
+%                       & Flame     & 11 & 0 & 35 & 4  & 0.92 &1.00 & 0.73 & 1.00 & 0.00 & 0.27 & 0.87 & 0.78 \\ 
+%                       & SecFFT    & \textbf{14} & 0 & 35 & \textbf{1}  & \textbf{0.98} & 1.00 & \textbf{0.93} & 1.00 & 0.00 & \textbf{0.07} & \textbf{0.96} & \textbf{0.91} \\ \hline
+
+% \multirow{4}{*}{\makecell{Angle-limited \\ strategy}} & Foolsgold & 11 & 2 & 33 & 4 & 0.88 & 0.85 & 0.73 & 0.94 & 0.06 & 0.27 & 0.84 & 0.68 \\ 
+%                        & FLTrust   & 9  & 1 & 34 & 6 & 0.86 & 0.90 & 0.60 & 0.97 & 0.03 & 0.40 & 0.80 & 0.65 \\ 
+%                        & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ 
+%                        & SecFFT    & \textbf{13} & 0 & 35 & \textbf{2}  & \textbf{0.96} & 1.00 & \textbf{0.87} & 1.00 & 0.00 & \textbf{0.13} & \textbf{0.94} & \textbf{0.88} \\ \hline
+% \end{tabular}
+% \vspace{1em}
+% \caption{Classification metrics results with different attack and defense methods}\label{tab:detect}
+% \end{table*}
 
@@
 \section{Conclusion}
-%随着泛在通信和技术的发展，UAV网络得到越来越广泛的应用。基于无人机的联邦学习等智能化方法能够自适应地优化部署和业务，成为重要发展趋势之一。然而，受限于有限的巡航范围，UAV设备往往高度异构，同时UAV设备资源和能量极其有限，这些约束均导致现有安全技术难以移植到UAV网络中。因此，在本文中，我们针对异构和资源受限的UAV网络下的公平联邦学习的安全问题进行了研究。基于一种分层社区构建机制，我们提出了双向可信的公平联邦学习架构，来应对异构UAV网络中的攻击威胁。在公有数据集上的系列实验表明，我们的方案相比现有技术，在异构缓解、隐私增强和污染防治方面均取得明显提升。
-With the development of ISCC and SAGIN, UAV networks are experiencing increasingly widespread applications.
-AI technologies such as FL based on UAV enable adaptive optimization of deployment and operations, emerging as a crucial development trend.
-However, due to the restricted patrol area, UAV devices exhibit high heterogeneity, and their resources and energy are also extremely limited.
-These constraints make it challenging to directly implant existing high-consumption security methods in UAV networks.
-Therefore, in this paper, we investigate the security issues of FFL in heterogeneous and resource-constrained UAV networks.
-Leveraging a stratified community construction mechanism, we propose a mutual reliability FFL framework (MR-FFL) to address multiple security threats.
-%in heterogeneous UAV networks.
-A series of experiments on public datasets demonstrate significant improvements of MR-FFL in heterogeneity remission, fairness guarantee, and poisoning resistance compared to existing technologies.
+%。本文聚焦于Covert backdoor attacks对于IoRT网络中进行视觉大模型联邦微调过程的威胁，针对性地提出了SecFFT防御架构。不同于现有的浅层信息捕捉的防御方法，我们抓住了频域分布差异中隐含的深层语义进行攻击感知，在此基础上创新地重构出攻击者的意图，从而在保障微调业务模型精度的同时，有效识别和阻断后门攻击，提升可靠性和完整性。在公有数据集上的系列实验表明，我们的方案相比现有技术，在性能提升、误判控制和污染防治方面均取得明显提升。未来方向方面，尽管SecFFT实现了对攻击意图的良好捕捉，但是目前仅仅是较为单一的网络场景。真实IoRT网络中的诸多特性，比如异构、多模态等因素并未纳入考虑，可能对防御性能产生影响。因此，未来将会更加贴近真实网络环境，设计实现异构容忍、抗噪声扰动的强鲁棒意图识别和防御方案。
+This paper focuses on the threat posed by covert backdoor attacks during the federated fine-tuning of large vision language models within IoRT networks and proposes the SecFFT defense framework.
+Unlike existing defense methods that capture only shallow-level information, our approach leverages the latent deep semantic differences in frequency-domain distributions to enhance attack detection.
+Building on this, we innovatively reconstruct the attacker’s intent, enabling effective backdoor attack detection while preserving the fine-tuning model's accuracy and improving its reliability and integrity.
+A series of experiments demonstrate that our approach significantly outperforms existing techniques. %in terms of performance improvement, false-positive control, and backdoor mitigation.
+
+Regarding future directions, although SecFFT demonstrates effective intent detection, it currently targets relatively homogeneous network scenarios.
+Real-world IoRT networks exhibit characteristics such as heterogeneity and multimodality, which are not yet fully considered and may impact defense performance.
+Hence, future work will focus on designing and implementing robust intent recognition and defense strategies that are tolerant to heterogeneity and resilient to noise disturbances, closely aligning with real network environments.
 
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Zan Zhou.jpg}}]{Zan Zhou} (Student Member, IEEE)
-received his Ph.D. degree in Computer Science from the Beijing University of Posts and Telecommunications (BUPT) in 2022. 
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Zan Zhou.jpg}}]{Zan Zhou} received his Ph.D.
+degree in Computer Science from the Beijing University of Posts and Telecommunications (BUPT) in 2022.
 From 2021 to 2022, he was a visiting student at Nanyang Technology University (NTU), Singapore. 
@@
 %He is Student member of IEEE.
-\end{IEEEbiography}
-
-\vspace{11pt}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Shujie Yang.jpg}}]{Shujie Yang} received the Ph.D.
-degree from the Institute of Network Technology, Beijing University of Posts and Telecommunications, Beijing, China, in 2017.
-He is currently a lecturer with the State Key Laboratory of Networking and Switching Technology.
-His major research interests include network security and artificial intelligence.
 \end{IEEEbiography}
@@
 \end{IEEEbiography}
+
+\vspace{11pt}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/bowang.jpg}}]{Bo Wang} received his B.E.
+degree from the School of Computer Science, Beijing University of Posts and Telecommunications, Beijing, China, in 2023.
+He is currently pursuing the Ph.D.
+degree at the same institution.
+His major research interests include network security and artificial intelligence.
+\end{IEEEbiography}
+
+\vspace{11pt}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/tengfeili.jpg}}]{Tengfei Li} received his B.E.
+degree from Beijing University of Chemical Technology, Beijing, China, in 2023.
+He is currently pursuing the M.E.
+degree at the School of Computer Science, Beijing University of Posts and Telecommunications, Beijing, China.
+His major research interests include network security and artificial intelligence.
+\end{IEEEbiography}
+
+\vspace{11pt}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Sizhe Huang.jpg}}]{Sizhe Huang} is currently pursuing a Bachelor's degree in the School of Computer Science, BUPT.
+He is also a research assistant with the State Key Laboratory of Networking and Switching Technology, BUPT.
+His research interests include network security and active defense.
+\end{IEEEbiography}
+
+\vspace{11pt}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/Shujie Yang.jpg}}]{Shujie Yang} received the Ph.D.
+degree from the Institute of Network Technology, Beijing University of Posts and Telecommunications, Beijing, China, in 2017.
+He is currently a lecturer with the State Key Laboratory of Networking and Switching Technology.
+His major research interests include network security and artificial intelligence.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in, clip,keepaspectratio]{photos/Su Yao.jpg}}]{Su Yao} received the Ph.D.
+degree from the National Engineering Laboratory for Next Generation Internet Interconnection Devices, Beijing Jiaotong University.
+Currently, he is with the Beijing National Research Center for Information Science and Technology (BNRist), Tsinghua University, as an Assistant Research Fellow.
+His research interests include future network architecture, IoT security, and artificial intelligence for network systems.
+\end{IEEEbiography}
+
 % \bf{If you include a photo:}\vspace{-33pt}

### 2024-09-19 clip_lora.py
temp: before merging the final branch wb.002.clip_lora
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,340 +1,0 @@
-# backdoor on CIFAR-100 with 10 workers and 3 attackers
-import os
-import torch
-from torch.utils.data import random_split, DataLoader
-from torchvision import transforms
-from torchvision.datasets import CIFAR100
-from transformers import CLIPProcessor
-from peft import LoraConfig
-import matplotlib.pyplot as plt
-import seaborn as sns
-from src import Worker
-from src import Aggregator
-from scipy.fftpack import dct
-from transformers import CLIPProcessor, CLIPModel
-from peft import get_peft_model
-import logging
-import pandas as pd
-import warnings
-import argparse
-import copy
-
-
-# command line arguments
-parser = argparse.ArgumentParser(description="Run PEFT on CIFAR-100 dataset")
-parser.add_argument("-n", "--num_workers", type=int, help="Number of workers")
-parser.add_argument("-r", "--rounds", type=int, help="Number of rounds")
-parser.add_argument(
-    "-s", "--round_to_start_attack", type=int, help="Round to start attack"
-)
-parser.add_argument("-o", "--output_dir", type=str, help="Output directory")
-parser.add_argument("-a", "--advertiser_num", type=int, help="Number of attackers")
-args = parser.parse_args()
-
-warnings.filterwarnings(
-    "ignore", message=".*Torch was not compiled with flash attention.*"
-)
-
-logging.basicConfig(level=logging.INFO)
-logger = logging.getLogger(__name__)
-
-torch.manual_seed(200)
-
-
-# Load CIFAR-100 dataset
-os.environ["HF_HUB_DISABLE_SYMLINKS_WARNING"] = "1"
-cache_dir = os.path.expanduser("~/Desktop/clip_lora/.cache/models")
-
-output_dir = args.output_dir
-os.makedirs(output_dir, exist_ok=True)
-
-# load the processor
-processor = CLIPProcessor.from_pretrained(
-    "openai/clip-vit-base-patch32", cache_dir=cache_dir
-)
-device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
-
-assert device.type == "cuda", "Please make sure CUDA is available"
-
-# Load the CIFAR-100 dataset
-cifar100_train = CIFAR100(
-    os.path.expanduser("~\Desktop\clip_lora\.cache"),
-    train=True,
-    transform=transforms.ToTensor(),
-    download=False,
-)
-cifar100_test = CIFAR100(
[…]

### 2024-09-19 src/Aggregator.py

@@ -1,74 +1,0 @@
-import torch
-from tqdm import tqdm
-import copy
-
-
-class Aggregator:
-    def __init__(
-        self, class_names, processor, target_model, device=torch.device("cpu")
-    ):
-        self.device = device
-        self.processor = processor
-        self.class_names = class_names
-        self.model = target_model
-
-    def to(self, device):
-        self.device = device
-        self.model = self.model.to(device)
-
-    def save(self, path):
-        torch.save(self.model.state_dict(), path)
-
-    def load(self, path):
-        self.model.load_state_dict(torch.load(path))
-
-    def predict(self, images):
-        self.model.eval()
-        text_inputs = [f"This is a photo of a {label}" for label in self.class_names]
-        with torch.no_grad():
-            inputs = self.processor(
-                text=text_inputs, images=images, return_tensors="pt", padding=True
-            ).to(self.device)
-            outputs = self.model(**inputs)
-            logits_per_image = outputs.logits_per_image
-            return logits_per_image.softmax(dim=1)
-
-    def eval(self, data_loader, attack_params={}):
-        self.model.eval()
-        correct = 0
-        loss = 0
-        total = 0
-        loss_fn_image = torch.nn.CrossEntropyLoss()
-        text_inputs = [f"This is a photo of a {label}" for label in self.class_names]
-
-        with torch.no_grad():
-            for images, labels in tqdm(data_loader, desc="Evaluating"):
-                print(f"evaluating {len(images)} images images.shape: {images.shape}")
-                if attack_params:
-                    x, y = attack_params["trigger_position"]
-                    h, w = attack_params["trigger_size"]
-                    for idx in range(len(images)):
-                        images[idx][:, x : x + h, y : y + w] = attack_params[
-                            "trigger_value"
-                        ]
-                        labels[idx] = attack_params["target_label"]
-                inputs = self.processor(
-                    text=text_inputs,
-                    images=images,
-                    return_tensors="pt",
-                    padding=True,
-                    do_rescale=False,
-                ).to(self.device)
-                labels = labels.to(self.device)
-                outputs = self.model(**inputs)
-
-                logits_per_image = outputs.logits_per_image
-
-                probs = logits_per_image.softmax(dim=1)
-
-                correct += (probs.argmax(dim=1) == labels).sum().item()
-                loss += loss_fn_image(logits_per_image, labels).item() * len(images)
-
-                total += len(images)
-
-        return correct / total, loss / total

### 2024-09-19 src/Plot.py

@@ -1,41 +1,0 @@
-import numpy as np
-
-
-def plot_loss_curve(ax, loss_values):
-    ax.plot(loss_values)
-    ax.set_xlabel("Epochs")
-    ax.set_ylabel("Loss")
-    ax.set_title("Training Loss Curve Per Epoch")
-    ax.grid(True)
-    ax.set_xticks(range(0, len(loss_values), 10))
-
-def plot_accuracy_curve(ax, accuracy_values):
-    ax.plot(accuracy_values)
-    ax.set_xlabel("Epochs")
-    ax.set_ylabel("Accuracy")
-    ax.set_title("Training Accuracy Curve Per Epoch")
-    ax.grid(True)
-    ax.set_xticks(range(0, len(accuracy_values), 10))
-
-def plot_epoch_loss_curve(ax, loss_summaries, train_subset_length):
-    epoch_losses = np.array([summary["loss"] for summary in loss_summaries]).reshape(
-        -1, train_subset_length
-    )
-    epoch_losses = np.mean(epoch_losses, axis=1)
-    ax.plot(epoch_losses)
-    ax.set_xlabel("Rounds")
-    ax.set_ylabel("Loss")
-    ax.set_title("Training Loss Curve Per Round")
-    ax.grid(True)
-
-def plot_epoch_accuracy_curve(ax, loss_summaries, train_subset_length):
-    epoch_accuracies = np.array(
-        [summary["accuracy"] for summary in loss_summaries]
-    ).reshape(-1, train_subset_length)
-    epoch_accuracies = np.mean(epoch_accuracies, axis=1)
-    ax.plot(epoch_accuracies)
-    ax.set_xlabel("Rounds")
-    ax.set_ylabel("Accuracy")
-    ax.set_title("Training Accuracy Curve Per Round")
-    ax.grid(True)
-    

### 2024-09-19 src/Worker.py

@@ -1,152 +1,0 @@
-import torch
-from tqdm import tqdm
-import random
-import logging
-
-
-logging.basicConfig(level=logging.INFO)
-logger = logging.getLogger(__name__)
-random.seed(200)
-
-
-class Worker:
-    def __init__(
-        self,
-        idx,
-        processor,
-        model,
-        data_set,
-        device,
-        class_names,
-        round_to_start_attack,
-        inner_epochs,
-        start_round=0,
-        attack_type="",
-        attack_params={},
-        batch_size=256,
-    ):
-        self.device = device
-        self.processor = processor
-        self.model = model
-        self.idx = idx
-        self.data_set = data_set
-        self.class_names = class_names
-        self.epochs = inner_epochs
-        self.start_round = start_round
-        self.attack_type = attack_type
-        self.round_to_start_attack = round_to_start_attack
-        self.attack_params = attack_params
-        self.lr_init = 1e-3
-        self.has_flip = False
-        self.backdoored = False
-
-        self.train_summaries = []
-
-        if self.attack_type == "backdoor":
-            assert "trigger_position" in self.attack_params
-            assert "trigger_size" in self.attack_params
-            assert "trigger_value" in self.attack_params
-            assert "backdoor_rate" in self.attack_params
-            assert "target_label" in self.attack_params
-
-        self.data_loader = torch.utils.data.DataLoader(
-            self.data_set, batch_size=batch_size, shuffle=True
-        )
-
-    def add_trigger(self, images, labels):
-        n_backdoor = int(len(images) * self.attack_params["backdoor_rate"])
-        backdoor_indices = range(n_backdoor)
-        x, y = self.attack_params["trigger_position"]
-        h, w = self.attack_params["trigger_size"]
-        print(
-            f"Worker {self.idx} Add Trigger at ({x}, {y}) with size ({h}, {w}) images.shape: {images.shape}"
-        )
-        for idx in backdoor_indices:
-            images[idx][:, x : x + h, y : y + w] = self.attack_params["trigger_value"]
-            labels[idx] = self.attack_params["target_label"]
-
-        return images, labels
-
-    def train(self, cur_round):
-        target_model_params = {}
-        for name, param in self.model.named_parameters():
-            if param.requires_grad:
-                target_model_params[name] = param.clone().detach().requires_grad_(False)
-
-        lr = self.lr_init * 0.1 ** ((cur_round - self.start_round) // 10)
[…]

### 2024-09-19 src/__init__.py

@@ -1,4 +1,0 @@
-from src.Aggregator import Aggregator
-from src.Worker import Worker
-from src.Plot  import *
-

### 2024-09-19 getResult/FL_Backdoor_CV/helper.py
refactor: 重整完成
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@ -1,206 +1,0 @@
-import math
-import random
-
-import numpy as np
-import torch
-
-from configs import args
-
-# ========= Fix the random seed (Start) =========
-torch.manual_seed(1)
-torch.cuda.manual_seed(1)
-random.seed(0)
-np.random.seed(0)
-
-
-# ========= Fix the random seed (End) =========
-
-
-class Helper:
-    def __init__(self, params):
-        self.target_model = None
-        self.local_model = None
-        self.training_data = None
-        self.benign_test_data = None
-        self.poisoned_data = None
-        self.poisoned_test_data = None
-        self.params = params
-        self.best_loss = math.inf
-
-    @staticmethod
-    def get_weight_difference(weight1, weight2):
-        difference = {}
-        res = []
-        if type(weight2) == dict:
-            for name, layer in weight1.items():
-                difference[name] = layer.data - weight2[name].data
-                res.append(difference[name].view(-1))
-        else:
-            for name, layer in weight2:
-                difference[name] = weight1[name].data - layer.data
-                res.append(difference[name].view(-1))
-        difference_flat = torch.cat(res)
-        return difference, difference_flat
-
-    @staticmethod
-    def get_l2_norm(weight1, weight2):
-        difference = {}
-        res = []
-        if type(weight2) == dict:
-            for name, layer in weight1.items():
-                difference[name] = layer.data - weight2[name].data
-                res.append(difference[name].view(-1))
-        else:
-            for name, layer in weight2:
-                difference[name] = weight1[name].data - layer.data
-                res.append(difference[name].view(-1))
-        difference_flat = torch.cat(res)
-        l2_norm = torch.norm(difference_flat.clone().detach().to(args.device))
-        l2_norm_np = np.linalg.norm(difference_flat.cpu().numpy())
-        return l2_norm, l2_norm_np
-
-    @staticmethod
-    def clip_grad(norm_bound, weight_difference, difference_flat):
-        l2_norm = torch.norm(difference_flat.clone().detach().to(args.device))
-        scale = max(1.0, float(torch.abs(l2_norm / norm_bound)))
-        for name in weight_difference.keys():
-            weight_difference[name].div_(scale)
-        return weight_difference, l2_norm
-
-    @staticmethod
-    def grad_mask_cv(helper, model, dataset_clearn, criterion, ratio=0.5):
-        """Generate a gradient mask based on the given dataset"""
-        model.train()
-        model.zero_grad()
-
[…]

### 2024-09-19 getResult/FL_Backdoor_CV/image_helper.py

@@ -1,740 +1,0 @@
-import copy
-import pickle
-import random
-from collections import defaultdict
-
-import numpy as np
-import torch
-from torch.utils.data import Dataset, DataLoader
-from torchvision import datasets, transforms
-from torchvision.datasets import EMNIST, FashionMNIST
-
-from FL_Backdoor_CV.helper import Helper
-from configs import args
-from transformers import CLIPProcessor, CLIPModel
-import os
-import platform
-from peft import LoraConfig, get_peft_model
-
-random.seed(0)
-np.random.seed(0)
-import matplotlib.pyplot as plt
-from torchvision.utils import make_grid
-
-
-def plot_image(images, lables, classes, batch_idx, adversarial_index=-1):
-    n_rows = (len(images) + 4) // 5
-    n_cols = 5
-    fig, axes = plt.subplots(n_rows, n_cols, figsize=(15, n_rows * 3))
-    for i in range(len(images)):
-        row = i // n_cols
-        col = i % n_cols
-        ax = axes[row, col] if n_rows > 1 else axes[col]
-        ax.set_title(f"Label: {classes[lables[i]]}", fontsize=8)
-        if args.dataset.lower() in ["emnist", "fmnist"]:
-            ax.imshow(images[i][0].reshape(28, 28), cmap="gray")
-            ax.axis("off")
-
-        elif args.dataset.lower() == "cifar10":
-            grid = make_grid(images[i])
-            # Add 0.5 after unnormalizing to [0, 255] to round to the nearest integer
-            ndarr = (
-                grid.mul(255)
-                .add_(0.5)
-                .clamp_(0, 255)
-                .permute(1, 2, 0)
-                .to("cpu", torch.uint8)
-                .numpy()
-            )
-            ax.imshow(ndarr)
-            ax.axis("off")
-
-    for j in range(len(images), n_rows * n_cols):
-        fig.delaxes(axes.flatten()[j])
-    plt.tight_layout()
-    if args.dataset.lower() == "emnist":
-        plt.savefig(
-            f"./emnist_{args.attack_mode.lower()}_{batch_idx}_{adversarial_index}.pdf",
-            bbox_inches="tight",
-        )
-    if args.dataset.lower() == "fmnist":
-        plt.savefig(
-            f"./fmnist_{args.attack_mode.lower()}_{batch_idx}_{adversarial_index}.pdf",
-            bbox_inches="tight",
-        )
[…]

### 2024-09-19 getResult/FL_Backdoor_CV/roles/aggregation_rules.py

@@ -1,366 +1,0 @@
-import math
-from collections import defaultdict
-from collections import Counter
-import numpy as np
-import sklearn.metrics.pairwise as smp
-import torch
-import torch.nn.functional as F
-import hdbscan
-from scipy.linalg import eigh as largest_eigh
-from sklearn.cluster import DBSCAN, KMeans
-
-from configs import args
-
-
-def avg(model_updates):
-    global_update = dict()
-    for name, data in model_updates.items():
-        global_update[name] = (
-            1
-            / args.participant_sample_size
-            * model_updates[name].sum(dim=0, keepdim=True)
-        )
-    return global_update
-
-
-from scipy.fftpack import dct
-
-
-def secfft(model_updates):
-    updates = torch.cat(list(model_updates.values()), dim=1)  # 整合模型更新
-
-    updates_dct = dct(
-        updates.cpu().numpy(), type=2, axis=1, norm="ortho"
-    )  # 离散余弦变换（DCT）
-    device = args.device
-    updates_dct = torch.tensor(updates_dct[:, :20000], device=device)  # 提取低频成分
-
-    # 计算特征值和特征向量
-    product_matrix = updates_dct @ updates_dct.T  # product_matrix为对称矩阵？
-    eigenvalues, eigenvectors = torch.linalg.eigh(product_matrix)
-    max_eigenvalue, max_eigenvector = eigenvalues[-1], eigenvectors[:, -1]
-
-    # 计算干净成分
-    max_eigenvalue = max_eigenvalue.real.item()  # 确保为实数
-    max_eigenvector = max_eigenvector.view(-1, 1)
-    clean_updates = updates_dct.T @ max_eigenvector / math.sqrt(max_eigenvalue)
-    clean_updates = clean_updates.reshape(1, -1)  # clean ingredient
-
-    # 计算KL散度
-    clean_updates = clean_updates.expand(updates_dct.shape[0], -1)
-    clean_updates_prob = F.softmax(clean_updates, dim=1)
-    updates_dct_log_prob = F.log_softmax(updates_dct, dim=1)
-    kl_div = F.kl_div(updates_dct_log_prob, clean_updates_prob, reduction="none")
-    kl_div_per_sample = kl_div.sum(dim=1).cpu().numpy()
-    clusterer = hdbscan.HDBSCAN(min_cluster_size=5, metric="euclidean")
-    clusters = clusterer.fit_predict(kl_div_per_sample.reshape(-1, 1))
[…]

### 2024-09-19 getResult/FL_Backdoor_CV/roles/client.py

@@ -1,374 +1,0 @@
-import copy
-import random
-import time
-
-import torch
-
-from FL_Backdoor_CV.roles.evaluation import test_poison_cv, test_cv
-from configs import args
-from FL_Backdoor_CV.image_helper import plot_image
-import torch.optim as optim
-
-
-class Client:
-    def __init__(self, client_id, local_data, local_data_size, malicious=False):
-        self.client_id = client_id
-        self.local_data = local_data
-        self.local_data_size = local_data_size
-        self.malicious = malicious
-        self.server = None
-        self.adversarial_index = None
-        self.range_no_id = None
-
-    def local_train(
-        self,
-        local_model,
-        helper,
-        epoch,
-        do_attack=False,
-        criterion=torch.nn.CrossEntropyLoss(),
-    ):
-        local_data = self.local_data
-        text_inputs = [f"This is a photo of a {label}" for label in helper.classes]
-        if self.malicious and do_attack:
-            # === clean part of malicious clients.
-            # === we need to remove indices corresponding to the target label when attackers conduct local training. ===
-            if self.range_no_id is None:
-                range_no_id = list(range(len(helper.train_dataset)))
-
-                if args.attack_mode.lower() in ["mr", "dba", "flip"]:
-                    for ind, x in enumerate(helper.train_dataset):
-                        imge, label = x
-                        if label == helper.params["poison_label_swap"]:
-                            range_no_id.remove(ind)  # 移除目标类别的图片
-
-                    if args.dataset == "cifar10":  # 移除指定的图片
-                        if args.attack_mode.lower() == "mr":
-                            for image in (
-                                helper.params["poison_images_test"]
-                                + helper.params["poison_images"]
-                            ):
-                                if image in range_no_id:
-                                    range_no_id.remove(image)
-
-                elif args.attack_mode.lower() == "combine":
-                    target_label = None
-                    if self.adversarial_index == 0:
-                        target_label = helper.params["poison_label_swaps"][0]
-                    elif self.adversarial_index == 1:
-                        target_label = helper.params["poison_label_swaps"][1]
-                    elif self.adversarial_index == 2:
-                        target_label = helper.params["poison_label_swaps"][2]
-                    elif self.adversarial_index == 3:
-                        target_label = helper.params["poison_label_swap"]
-                    for ind, x in enumerate(helper.train_dataset):
-                        imge, label = x
-                        if label == target_label:
-                            range_no_id.remove(ind)
-
-                    if args.dataset == "cifar10":
[…]

### 2024-09-19 getResult/FL_Backdoor_CV/roles/evaluation.py

@@ -1,87 +1,0 @@
-import torch
-import torch.nn.functional as F
-from configs import args
-
-
-def test_cv(data_source, model, classes, processor):
-    model.eval()
-    total_loss = 0
-    correct = 0
-    text_inputs = [f"This is a photo of a {label}" for label in classes]
-    data_iterator = data_source
-    num_data = 0.0
-    for batch_id, batch in enumerate(data_iterator):
-        data, targets = batch
-        clip_inputs = processor(
-            text=text_inputs,
-            images=data,
-            return_tensors="pt",
-            padding=True,
-            do_rescale=False,
-        ).to(args.device)
-        targets = targets.to(args.device)
-
-        outputs = model(**clip_inputs)
-        logits_per_image = outputs.logits_per_image
-        total_loss += F.cross_entropy(logits_per_image, targets, reduction="sum").item()
-        probs = logits_per_image.softmax(dim=-1)
-        pred = probs.argmax(dim=-1)
-        correct += pred.eq(targets.data.view_as(pred)).cpu().sum().item()
-        num_data += len(data)
-        # print(f"target: {targets}, pred: {pred}")
-
-    acc = float(correct) / float(num_data)
-    total_l = total_loss / float(num_data)
-
-    model.train()
-    return total_l, acc
-
-
-def test_poison_cv(
-    helper, data_source, model, classes, processor, adversarial_index=-1
-):
-    model.eval()
-    total_loss = 0.0
-    correct = 0.0
-    data_iterator = data_source
-    num_data = 0.0
-    text_inputs = [f"This is a photo of a {label}" for label in classes]
-
-    for batch_id, batch in enumerate(data_iterator):
-
-        if args.attack_mode.lower() in ["mr", "dba"]:
-            data, target = helper.get_poison_batch(batch, evaluation=True)
-        elif args.attack_mode.lower() == "combine":
-            data, target = helper.get_poison_batch(
-                batch, evaluation=True, adversarial_index=adversarial_index
-            )
-        else:
-            for pos in range(len(batch[0])):
-                batch[1][pos] = helper.params["poison_label_swap"]
-
-            data, target = batch
-
-        clip_inputs = processor(
-            text=text_inputs,
-            images=data,
-            return_tensors="pt",
-            padding=True,
-            do_rescale=False,
-        ).to(args.device)
-
-        target = target.to(args.device)
-
-        outputs = model(**clip_inputs)
[…]

### 2024-09-19 getResult/FL_Backdoor_CV/roles/server-init.py

@@ -1,924 +1,0 @@
-import copy
-
-import os
-import random
-import re
-from collections import defaultdict
-
-
-import numpy as np
-import sklearn.metrics.pairwise as smp
-import torch
-import torch.nn.functional as F
-from scipy.linalg import eigh as largest_eigh
-from scipy.stats import entropy
-from sklearn.cluster import DBSCAN, KMeans
-from sklearn.metrics import pairwise_distances
-from torch.nn.utils import parameters_to_vector, vector_to_parameters
-
-from FL_Backdoor_CV.models.create_model import create_model
-from FL_Backdoor_CV.roles.evaluation import test_cv, test_poison_cv
-from configs import args
-from FL_Backdoor_CV.roles.aggregation_rules import roseagg
-from FL_Backdoor_CV.roles.aggregation_rules import avg
-from FL_Backdoor_CV.roles.aggregation_rules import foolsgold
-from FL_Backdoor_CV.roles.aggregation_rules import flame
-from FL_Backdoor_CV.roles.aggregation_rules import fltrust
-from FL_Backdoor_CV.roles.aggregation_rules import robust_lr
-
-import pickle
-
-
-def softmax(x):
-    f_x = np.exp(x) / np.sum(np.exp(x))
-    return f_x
-
-
-class Server:
-    def __init__(self, helper, clients, adversary_list):
-        # === model ===
-        if args.resume:
-            self.model = torch.load(
-                os.path.join(
-                    "./FL_Backdoor_CV/saved_models/Revision_1", args.resumed_name
-                ),
-                map_location=args.device,
-            )
-        else:
-            self.model = create_model()
-
-        # === gradient correction ===
-        # self.previous_models = []
-        # if args.gradient_correction:
-        #     previous_model = copy.deepcopy(self.model)
-        #     previous_model.load_state_dict(self.model.state_dict())
-        #     self.previous_models.append(previous_model)
-
-        # === clients, participants, attackers, and benign clients ===
-        self.clients = clients
-        self.participants = None
-        self.adversary_list = adversary_list
-        self.benign_indices = list(
-            set(list(range(args.participant_population))) - set(self.adversary_list)
-        )
-
-        # === image helper ===
-        self.helper = helper
-
-        # === whether resume ===
-        self.current_round = 0
-        # === Inherent recognition accuracy on poisoned data sets
-        self.inheret_poison_acc = 0
-
-        if args.resume:
-            self.current_round = int(
[…]

### 2024-09-19 getResult/FL_Backdoor_CV/roles/server.py

@@ -1,952 +1,0 @@
-import copy
-
-import os
-import random
-import re
-from collections import defaultdict
-
-
-import numpy as np
-import sklearn.metrics.pairwise as smp
-import torch
-import torch.nn.functional as F
-from scipy.linalg import eigh as largest_eigh
-from scipy.stats import entropy
-from sklearn.cluster import DBSCAN, KMeans
-from sklearn.metrics import pairwise_distances
-from torch.nn.utils import parameters_to_vector, vector_to_parameters
-
-# from FL_Backdoor_CV.models.create_model import create_model
-from FL_Backdoor_CV.roles.evaluation import test_cv, test_poison_cv
-from configs import args
-from FL_Backdoor_CV.roles.aggregation_rules import roseagg
-from FL_Backdoor_CV.roles.aggregation_rules import avg
-from FL_Backdoor_CV.roles.aggregation_rules import foolsgold
-from FL_Backdoor_CV.roles.aggregation_rules import flame
-from FL_Backdoor_CV.roles.aggregation_rules import fltrust
-from FL_Backdoor_CV.roles.aggregation_rules import robust_lr
-from FL_Backdoor_CV.roles.aggregation_rules import secfft
-
-import pickle
-
-
-def softmax(x):
-    f_x = np.exp(x) / np.sum(np.exp(x))
-    return f_x
-
-
-class Server:
-    def __init__(self, helper, clients, adversary_list):
-        # === model ===
-        # if args.resume:
-        #     self.model = torch.load(
-        #         os.path.join(
-        #             "./FL_Backdoor_CV/saved_models/Revision_1", args.resumed_name
-        #         ),
-        #         map_location=args.device,
-        #     )
-        # else:
-        #     self.model = create_model()
-        self.model = helper.target_model
-
-        # === gradient correction ===
-        # self.previous_models = []
-        # if args.gradient_correction:
-        #     previous_model = copy.deepcopy(self.model)
-        #     previous_model.load_state_dict(self.model.state_dict())
-        #     self.previous_models.append(previous_model)
-
-        # === clients, participants, attackers, and benign clients ===
-        self.clients = clients
-        self.participants = None
-        self.adversary_list = adversary_list
-        self.benign_indices = list(
-            set(list(range(args.participant_population))) - set(self.adversary_list)
-        )
-
-        # === image helper ===
-        self.helper = helper
-
-        # === whether resume ===
-        self.current_round = 0
[…]

### 2024-09-19 getResult/configs.py

@@ -1,280 +1,0 @@
-import argparse
-
-parser = argparse.ArgumentParser(description="PPDL")
-
-parser.add_argument("--reduction_factor", type=int, default=1)
-
-# === dataset, data partitioning mode, device, model, and rounds
-parser.add_argument(
-    "--dataset",
-    default="fmnist",
-    choices=["cifar10", "emnist", "fmnist"],
-    help="dataset",
-)
-
-parser.add_argument("--params", default="utils/fmnist_params.yaml", dest="params")
-
-
-parser.add_argument(
-    "--emnist_style", default="digits", type=str, help="byclass digits letters"
-)
-
-
-parser.add_argument(
-    "--rounds", default=20, type=int, help="total rounds for convergence"
-)
-
-
-parser.add_argument(
-    "--participant_population", default=50, type=int, help="total clients"
-)
-
-
-parser.add_argument(
-    "--participant_sample_size", default=50, type=int, help="participants each round"
-)
-
-
-parser.add_argument("--is_poison", default=1, type=int, help="poison or not")
-
-
-parser.add_argument(
-    "--number_of_adversaries", default=20, type=int, help="the number of attackers"
-)
-
-
-parser.add_argument(
-    "--random_compromise", default=1, type=int, help="randomly compromise benign client"
-)
-
-parser.add_argument(
-    "--poison_rounds",
-    default="0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49",
-    type=str,
-    help="",
-)
-
-parser.add_argument(
-    "--retrain_rounds",
-    default=30,
-    type=int,
-    help="continue to train {retrain_rounds} rounds starting when resume is true",
-)  # end_rounds = curr_round + retrain_rounds + window 这个参数的意思是指明中毒攻击情况下训练的轮数
-
-parser.add_argument(
-    "--aggregation_rule",
-    default="avg",
-    type=str,
-    choices=[
-        "avg",
-        "rlr",
-        "flame",
-        "foolsgold",
-        "roseagg",
-        "fltrust",
-        "fedcie",
-        "secfft",
-    ],
-    help="aggregation method",
-)
-
-
-parser.add_argument(
-    "--class_imbalance",
-    type=int,
-    default=1,
[…]

### 2024-09-19 getResult/trainer.py

@@ -1,316 +1,0 @@
-import os
-
-os.environ["OMP_NUM_THREADS"] = "1"
-os.environ["HF_DATASETS_OFFLINE"] = "1"
-os.environ["HF_HUB_OFFLINE"] = "1"
-
-import random
-import time
-
-import numpy as np
-import torch.backends.cudnn
-import yaml
-
-from FL_Backdoor_CV.image_helper import ImageHelper
-from configs import args
-
-try:
-    from yaml import CLoader as Loader, CDumper as Dumper
-except ImportError:
-    from yaml import Loader, Dumper
-from FL_Backdoor_CV.roles.client import Client
-from FL_Backdoor_CV.roles.server import Server
-from PIL import Image
-from torchvision.utils import save_image, make_grid
-import matplotlib.pyplot as plt
-
-torch.manual_seed(1)
-torch.cuda.manual_seed(1)
-
-random.seed(0)
-np.random.seed(0)
-from datetime import datetime
-
-import csv
-from FL_Backdoor_CV.image_helper import plot_image
-
-from typing import Dict
-
-
-def save_results_to_csv(results: Dict[str, list], filename="results.csv"):
-    keys = list(results.keys())
-
-    max_length = max(len(v) for v in results.values())
-
-    for key in keys:
-        if len(results[key]) < max_length:
-            results[key].extend([""] * (max_length - len(results[key])))
-
-    rows = zip(*[results[key] for key in keys])
-
-    with open(filename, "w", newline="") as csvfile:
-        writer = csv.writer(csvfile)
-        writer.writerow(keys)
-        writer.writerows(rows)
-
-
-def check_params(params):
-    assert params["participant_sample_size"] <= params["participant_population"]
-    assert params["number_of_adversaries"] <= params["participant_sample_size"]
-
-
-class Trainer:
-    def __init__(self):
-        print(
-            f"We are conduct federated training using {args.aggregation_rule} on {args.dataset}... \n"
-        )
-
-        # === Load yaml file ===
-        with open(f"./FL_Backdoor_CV/{args.params}", "r", encoding="utf-8") as f:
-            params_loaded = yaml.load(f, Loader=Loader)
-
-        # === Add additional fields to the loaded params based on args ===
-        params_loaded.update(vars(args))
-        if (
-            params_loaded["dataset"] == "cifar10"
-            or params_loaded["dataset"] == "emnist"
-            or params_loaded["dataset"] == "fmnist"
[…]

### 2024-10-22 response.tex
tex: response1
half版本

Signed-off-by: LetMeFly666 <814114971@qq.com>

% !TeX encoding = UTF-8
\documentclass[a4paper,twoside,11pt,dvipsnames]{reviewresponse}
\usepackage{subcaption}
% 1. Load and set up proper language packages
\usepackage{amsbsy,amssymb,epsfig,bbm,mathrsfs,multirow,amsthm}
\usepackage{algorithm,algpseudocode}
\usepackage{amsmath}
\usepackage{graphicx}
% \usepackage[english]{babel}
\usepackage{mathtools,xparse}
\usepackage{array, multirow, graphicx}
\usepackage{graphicx}
\usepackage{graphics}
% \usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{natbib}
\setcitestyle{numbers,square}
\usepackage{bbm}
\usepackage{comment}
\usepackage{makecell}
\usepackage{xcolor}

\usepackage{listings}

% \usepackage{multirow}
% \usepackage{amsmath}

\usepackage{mathtools}

\usepackage{caption}
%\usepackage{vntex} 
%\usepackage[vietnamese]{babel}
%\usepackage[utf8]{vietnam}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}

\newcommand{\clU}{{\cal U}}
\newcommand{\clI}{{\mathbf I}}
\newcommand{\clD}{{\cal D}}
\newcommand{\bg}{\boldsymbol{g}}
\newcommand{\bo}{\boldsymbol{\omega}}
\newcommand{\bI}{\boldsymbol{I}}
\newcommand{\bx}{\boldsymbol{x}}
\newcommand{\by}{\boldsymbol{y}}
\newcommand{\bw}{\boldsymbol{w}}
\newcommand{\bz}{\mathbf{q}}
\newcommand{\rw}{\rm{w}}
\newcommand{\bh}{\mathbf{h}}
\newcommand{\bp}{\mathbf{p}_i}
\newcommand{\bn}{\mathbf{n}}
\newcommand{\bm}{\boldsymbol{m}}
\newcommand{\clS}{{\cal S}}
\newcommand{\ds}{\displaystyle}
\newcommand{\pik}{p_i^{(\kappa)}}
\newcommand{\pjk}{p_j^{(\kappa)}}
\newcommand{\rhok}{\rho^{(\kappa)}}
\newcommand{\bpk}{\mathbf{p}_i^{(\kappa)}}
\newtheorem{assumption}{Assumption}[section]

\newtheorem{Definition}{\hskip 0pt Definition}%[section]
\newtheorem{lemma}{Lemma}
\newtheorem{observation}{Observation}
\newtheorem{theorem}{\textbf{\textsc{Theorem}}}
\newtheorem{mypro}{Proposition}
\hyphenation{lists}

\graphicspath{ {./figures/} }

% 2. Complete the paper data
\newcommand{\myAuthors}{{Tran The Anh$^{\displaystyle 1}$, ~Nguyen Cong Luong$^{\displaystyle 2}$, } \\ {~Dusit Niyato$^{\displaystyle 2}$}}
\newcommand{\myAuthorsShort}{The Anh.~Tran et. al}
\newcommand{\myEmail}{theanh.tran@ntu.edu.sg}
\newcommand{\myTitle}{A Deep Reinforcement Learning Approach for Backscatter-Assisted Relay Communications}
\newcommand{\myShortTitle}{}
 \newcommand{\myJournal}{}
\newcommand{\myDept}{{$^{\displaystyle 1}$School of Computer Science and Engineering, Nanyang Technological University, Singapore. \\ \url{}}\\
{$^{\displaystyle 2}$School of Computer Science and Engineering, Nanyang Technological University. }\\}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[linktoc=all,bookmarks,bookmarksopen=true,bookmarksnumbered=true]{hyperref}

\hypersetup{
pdfauthor = {\myAuthorsShort},
pdftitle = {\myTitle},
pdfsubject = {\myJournal\xspace},
colorlinks = true,
linkcolor=black!70!green, 
citecolor=black!70!green,       
filecolor=magenta,      
urlcolor=black!70!black           
}

\begin{document}

\thispagestyle{plain}

 {\Large We would like to thank the editor for the time and effort to gather insightful reviews for our submission to IEEE Transactions on Network Science and Engineering (TNSESI-2023-01-0074: \textit{Combating ``Drug Resistance" of Intelligent Attack: Hierarchical Network Traffic Moving Target Defense with Endogenous Security Enhancement}). In response to the comments from the Editor and the reviewers, we have revised the paper extensively. We also would like to thank the Editor and the reviewers for the valuable and constructive comments that help us improve the quality of the paper significantly. The followings are the detailed answers to the comments. %It is also noted that, we add the letter ` `R'' (i.e., Response) before the reference number of references which are added in this response, e.g., ``[R1]'', and ``[R2]''. This is to distinguish references in this response letter and those in the revised paper.
 It is also noted that, as the whole manuscript has undergone substantial and comprehensive revisions, to facilitate clarity for the reviewers, we have marked the newly added or completely rewritten parts in {\color{blue}blue\color{black}} within the revised manuscript. The remaining sections, where only language and expression changes have been made, are still presented in black text.
 }

%\end{abstract}

\newpage

%=================================
%=================================
\section{Summary of changes}
Based on the valuable feedback from the reviewers, we have made significant improvements to the manuscript in the following areas:
\color{red}
\begin{itemize}

% 根据Reviewer 1's Comment 1，Comment 2以及Reviewer 2's Comment 1，我们修改了文章的部分公式以及重新构建了符号表，使文章的公式符号的意义更加清晰，优化阅读体验。
\item \textbf{[Writing and expression:]} Based on \textbf{Reviewer 1's Comment 1, Comment 2}, and \textbf{Reviewer 2's Comment 1}, we have revised some of the formulas in the article and reconstructed the symbol table to make the meanings of the formula symbols clearer and to enhance the overall reading experience.

% 根据Reviewer 1's Comment 3，我们对Threat models部分的基本假设做了进一步的假设，使得本文提出的概念更便于理解。
\item \textbf{[Threat Models:]} Based on \textbf{Reviewer 1's Comment 3}, we made further assumptions in the \textbf{Threat Models} section regarding the basic assumptions, making the concepts proposed in this paper easier to understand.

% 根据Reviewer 1's Comment 4，我们增加了额外的实验来说明了采样大小和模型准确率之间的关系。

% 根据Reviewer 1's Comment 5, 我们对DUPLEX PRIVACY AMPLIFICATION的auxiliary downlink privacy obfuscation部分做了修改，澄清了“社区导向框架”与"异质性情景下提高效率的意义“”之间联系。
\item \textbf{[Duplex privacy amplification:]} Based on \textbf{Reviewer 1's Comment 5}, we revised the \textbf{Auxiliary downlink privacy obfuscation} section of \textbf{Duplex privacy amplification}, clarifying the connection between the \textbf{community-oriented framework} and the \textbf{significance of improving efficiency in heterogeneous scenarios}.

% 根据Reviewer 2's Comment 2，
\item \textbf{[Credit-based active poisoning resistance:]} Based on \textbf{Reviewer 2's Comment 5}, we supplemented the consideration of resource consumption by adding an analysis of communication efficiency and computational time complexity.

% 根据Reviewer 2's Comment 3，我们对experimental Environment部分进行了相应的修改，解释了实验部分针对不同数据集选择对应模型结构和超参数的原因。根据Reviewer 2's Comment 4， 我们在实验结果描述部分添加了对CIFAR-100的实验结果以及相应的分析。
\item \textbf{[Performance evaluation:]} Based on \textbf{Reviewer 2's Comment 3}, we made corresponding revisions to the \textbf{Experimental environment} section of \textbf{Performance evaluation}, explaining the rationale behind selecting the appropriate model structures and hyperparameters for different datasets in the experiments. Additionally, in response to \textbf{Reviewer 2's Comment 4}, we added the experimental results for CIFAR-100, along with the corresponding analysis, to the experimental results description section. Furthermore, in response to \textbf{Reviewer 1's Comment 4}, We conducted additional experiments to illustrate the relationship between sample size and model accuracy.

\end{itemize}

\color{black}
The detailed responses to the comments are as follows. Thank you very much for your time again.

\newpage

%=================================
\section{Responses to the Comments from Reviewer 1}
%=================================
%=================================
%========================================================
\rcomment{
\color{red} The technical framework lacks sufficient explanatory detail. For example, the steps in Fig. 2 are explained too briefly, making them difficult to understand.
}
% 问题：技术框架解释性不足，比如Fig2步骤解释过于粗略，难以理解。
\textbf{Response:} 
We thanks the Reviewer for the comment.

%========================================================
\rcomment{
\color{red} There are several errors and linguistic issues throughout the paper. For instance, on page 5, at the end of the second paragraph, citation [36] is repeated consecutively. Please carefully review and correct these issues.
}
% 问题：文中存在部分错误和语病，如在P5页第二段末尾，引用[36]连续重复出现，请认真检查

\textbf{Response:} We thank the Reviewer for the constructive comment.

%========================================================
\rcomment{
\color{red} In Algorithm 1, there are unused variables in line 5.
}
% 问题：算法1第5行出现未使用变量。

\textbf{Response:} We thank the Reviewer for the constructive comment, and
% 非常抱歉，因为我们的疏忽，导致该算法出现让人无法理解的地方。根据您的建议，我们修改了该算法的相关部分，删除了未使用的变量。同时为了使整个算法过程更易理解，我们修改了另外一些跟原文不一致的地方，\ref{alg:malicious-node-detection}展示了修改后的结果。
we sincerely apologize for the confusion caused by the oversight in our algorithm.
Following your suggestion, we revised the relevant parts of the algorithm and removed unused variables.
Additionally, to make the entire algorithm process easier to understand, we adjusted some parts that were inconsistent with the original text, and algorithm \ref{alg:malicious-node-detection} shows the modified result.
% 最后，为了表现算法中某些变量会随训练轮次所变化，我们给一些变量添加时间$t$的上标，比如修改$C_{max},Chi_i^2,{C_1}', {C_2}'$至$C^t_{max},{Chi^t_i}^2,{C^t_1}', {C^t_2}'$
Finally, to represent that certain variables in the algorithm change with the training rounds, we added the superscript of round $t$ to some variables, such as modifying $C_{max}, Chi_i^2, {C'_1}, {C'_2}$ to $C^t_{max}, {Chi^t_i}^2, {C^t_1}', {C^t_2}'$.

\begin{algorithm}
\caption{Instantaneous Attack Behavior Perception}
\label{alg:malicious-node-detection}
\begin{algorithmic}[1]
\State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each update; $N$ is the number of nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from robot nodes during the $t$-th round; $m$ is the length of low-frequency components}
\State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
\State{\color{CadetBlue}/* \textbf{Frequency Domain Transformation */}} 
% \State Step 1: Frequency Domain Transformation
\For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
    \State \textcolor{blue}{$G_i^t \gets Trunc(DCT(Flatten(\triangledown \theta_i^t))), m)$}
\EndFor

% \State
\State{\color{CadetBlue}/* \textbf{Clean Ingredient Extraction */}} 
% \State Step 2: Clean Ingredient Extraction
\State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering\textcolor{blue}{ (G_0^t, G_1^t, \ldots, G_N^t)}$ \Comment{$\kappa$ denotes the number of clusters}
\State \textcolor{blue}{$ C^t_{max} \gets \underset{C^t_j}{\arg\max} \, |C^t_j|$ \Comment{$|C^t_j|$ denotes the number of nodes in cluster $C^t_j$, $j = 1, 2, \ldots, \kappa $}}
\State $H^t \gets (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C^t_{max}$.}

\State $\hat{H}^t \gets (H^t)^{T} H^t$
\State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
\State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}

% \State
\State{\color{CadetBlue}/* \textbf{Chi-square distance calculation */}} 
% \State Step 3: Chi-square distance calculation
% \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
\For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
    \State ${Chi_i^t}^2 \gets \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}$
\EndFor
\State \textcolor{blue}{$S^t \gets \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}$} \Comment{The Distance differences calculated by Chi-square distance.}

% \State
\State{\color{CadetBlue}/* \textbf{Single-round malicious behavior perception */}} 
% \State Step 4: Single-round malicious behavior perception
\State $\textcolor{blue}{\{C'_1, C'_2\}} \gets KMeans(S^t, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
\State \textcolor{blue}{$U_{nor} \gets C'_{\text{max}}$, $U_{mal} \gets \{C'_i \, | \, i \neq \text{max}\}$}

\end{algorithmic}
\end{algorithm}

%========================================================
\rcomment{
\color{red} Section 4 uses various metrics to demonstrate the improved defense performance of the proposed method against different types of attacks. However, there is insufficient explanation of the origin and calculation methods for these metrics, which makes it hard for readers to follow. It is recommended to add a brief explanation.
}
% 问题：实验数据大小的代表性引起了关注。应阐明所选值背后的基本原理，以加强实验结果的有效性和可靠性。（就是说实验设置为啥这样选，比如超参数啥的，需要说明道理，不然的话是不合理的）
% 回复：确实应该写一段话描述一下这些指标都是什么意思。
% 感谢你的建议，在实验四的部分，我们使用了ACC、Rec、FPR、FNR、AUC、MCC等指标作为我们方法的有效性验证依据。虽然这些指标是这些类似实验中常见的指标，但是为了论文的普适性以及为了方便更多读者的理解，还是应该简要介绍一下这些指标的含义。因此我们新增了一些描述，用来简要介绍这些指标的含义。 我们增加了如下的简单描述：

% 这些指标用于评估模型性能。“Acc”表示准确率，衡量预测正确的比例；“Rec”是召回率，表示模型正确识别正例的能力；“FPR”是假阳性率，指错误将负例预测为正例的比例；“FNR”是假阴性率，指错误将正例预测为负例的比例；“AUC”是曲线下面积，表示模型区分正负例的整体能力；“MCC”是马修斯相关系数，综合评估模型预测结果的平衡性。

\textbf{Response:} Thank you for your suggestion. In Section 4 of our experiments, we used metrics such as ACC, Rec, FPR, FNR, AUC, and MCC as the basis for validating the effectiveness of our method. Although these metrics are commonly used in similar experiments, for the sake of the paper's generality and to facilitate understanding for a broader audience, we believe it is necessary to briefly introduce the meaning of these metrics. Therefore, we have added some descriptions to provide a concise explanation of these metrics. The added description is as follows:

"Acc" refers to accuracy, which measures the proportion of correct predictions; "Rec" stands for recall, representing the model's ability to correctly identify positive instances; "FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; "FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; "AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and "MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.

%========================================================
% 表格2的内容太长，超出了双栏的空间了，建议重新进行调整规划
\rcomment{
\color{red} The content in Table 2 is too long and exceeds the space available for a two-column layout. Please revise and reformat accordingly.
}

% 我将每次给你一个审稿意见，请你对于该审稿意见写一个回复（回复要包括中文版本和英文版本）。回复要展现自己良好的态度，越详细越好。
你了解司法人工智能吗？请解

% 谢谢你的建议，表格2的宽度确实有些过长，已经超出了半栏的范围，甚至已经与右侧栏目的内容产生了融合。我们对这个表格进行了调整，适当缩小了表格的宽度，使得表格在不影响整体观感的同时，保证了表格格式符合要求，且不超过单栏范围。

Thank you for your suggestion. The width of Table 2 is indeed somewhat excessive, exceeding the single-column limit and even merging with the content in the adjacent column. We have made adjustments to the table, reducing its width appropriately to ensure that the table fits within the required format while maintaining the overall visual quality without exceeding the single-column range.

%========================================================
\rcomment{
\color{red} The paper may benefit from providing an explicit explanation of the relationship between the community-oriented framework and the significance of improving efficiency in heterogeneous scenarios. Clarifying this connection would contribute to a more comprehensive understanding of the proposed methodologies.
}

% 问题：需要详细阐释“社区导向框架”与"异质性情景下提高效率的意义“”之间的关系。澄清这种联系将有助于更全面地了解所提议的方法。
%========================================================

% 改法:暂时没想法，这个待定，先不用改。大家有想法了也可以跟我讨论

%感谢您的建议。为了更好地表达“Community-oriented framework”对提高异构场景下效果的关系，我们做出了如下修改：

%在异构场景下，在同一轮次更新中，异构的设备提交的梯度更新方向可能差异较大，设备间更新存在拮抗，导致全局模型无法达到最优解（引用CFL）。在本文第x章的公式xxx

%，第一个公式表示全局模型已经到达驻点，各个设备的更新累加后得到的全局更新为零。然而，第二个公式体现了对于单个设备，它的本地模型仍然有更新。因此，在这种异构的场景下，单个设备的最优解与全局最优解差别较大。社区化框架将更新方向相近的设备划分到同一个社区中，使得社区的全局最优解与社区内设备的最优解之间的差距限缩在一定范围内，提高模型在本地设备的表现。

%对于隐私框架，在差分隐私中，敏感度与所需添加的噪声量正相关:

%对于敏感度而言，不同设备集合对应的敏感度差异较大，如图所示

%经划分社区后，同一社区的设备梯度更新更加集中，敏感度较低，所需添加的差分隐私噪声方差就更小。对于社区划分的条件，由于社区划分时要求了单个设备的梯度更新范数的最大值，即xxx，因此，在CFL场景下的差分隐私噪声，其噪声量取决于划分社区时设置的超参数，因此所添加的差分隐私噪声可以根据CFL的设置控制在一定范围之内。

%为了使得文章更易懂，我们在正文中添加了如下内容：

\textbf{Response:} Thank you for your suggestions. The community-oriented framework can improve both convergence efficiency and privacy efficiency.

\textbf{In improving convergence efficiency:}In heterogeneous scenarios, during the same round of updates, the gradient update directions submitted by heterogeneous devices may differ significantly, leading to conflicts between device updates, which prevents the global model from reaching the optimal solution. We explained this conclusion in Section VI:

\color{blue}
\begin{equation}\label{eq:3conditions-og}
    \left\{
    \begin{array}{rcr}
    \frac{N}{K|D|} \sum_{P_i\in \mathcal{P}_t} |D_i| \cdot ||\Delta w^{i}_{t} || & <\beta,\\
    \max_{P_i\in \mathcal{P}_t}||\Delta w^{i}_t|| &>\theta,\\
    \alpha^{min}_{intra} - \alpha^{max}_{cross} & > 0
    %\underset{P_{h},P_{k}\in C_m \subseteq \mathcal{C}}{\min } \alpha^{h, k}_t-\underset{P_{i} \in C_{1}, P_{j} \in C_{2}}{ \max} \alpha^{{i}, {j}}_t & >0,
    \end{array}
    \right.
\end{equation}
where $\theta>\beta>0$ are predefined constant thresholds, $\alpha^{min}_{intra}$ and  $\alpha^{max}_{cross}$ are the minimum internal cosine similarity and the maximum cosine similarity cross communities respectively\color{black}.

The first formula indicates that the global model has reached a saddle point, where the aggregate updates from all devices approximate a global update close to zero. However, the second formula demonstrates that for individual devices, their local models still experience updates. Consequently, in this heterogeneous scenario, there is a significant disparity between the optimal solution of a single device and the global optimal solution. The community-based framework categorizes devices with similar update directions into the same community, thereby constraining the discrepancy between the community's global optimal solution and the optimal solutions of the devices within that community within a certain range, which enhances the model's performance on local devices.

\textbf{In improving privacy efficiency:} In differential privacy, the sensitivity is positively correlated to the amount of noise that needs to be added. To guarantee $(\epsilon_i,\delta_i)-DP$, the standard deviation of noises $\sigma_i$ from Gaussian mechanism should satisfy:

\begin{equation}
    \sigma_i = \frac{Sen\sqrt{2qTln(1/\delta_i)}}{\epsilon_i},
\end{equation}

where $Sen$ is the sensitivity of the local training process.

However, after community division, the gradient updates of devices within the same community are more concentrated, with lower sensitivity, resulting in smaller variance of the differential privacy noise that needs to be added. Regarding the conditions for community division, since the maximum norm of the gradient updates of individual devices is required during the division, i.e., $\theta$, therefore, in the CFL scenario, the amount of differential privacy noise depends on the hyperparameters set during community division. Thus, the differential privacy noise added can be controlled within a certain range according to the CFL settings.

In order to make the article more understandable, we have added the following content to the main text:

\color{blue}
It is evident that the hyperparameters $\theta$ and $\gamma$ in community division determine the maximum sensitivity within the community, which in turn determines the amount of differential privacy noise required to be added. 
\color{black}

\newpage
%=================================
%=================================
\section{Responses to the Comments from Reviewer 2}
%=================================
%========================================================

\rcomment{
\color{red} The variable f, n in line 52 on page 3 is missing a description. Similarly, multiple variables in this paper have not yet been described, so please check carefully.
}
% 问题：第3页第52行中的变量f, n缺少描述。同样，本文中有多个变量尚未描述，请仔细检查。

%改法 : 跟上一个审稿人第一个问题提的差不多，就是先道歉，然后好好描述下这几个变量啥意思，然后提供个参数表。

\textbf{Response:} We thank the Reviewer for the comment.

We apologize for overlooking the definition of some variables, which may have caused confusion for the readers. In response, we have supplemented the definitions of certain variables:

In Section II, we have supplemented the definitions of $f$ and $n$ as follows:

\color{blue} where $n$ is the number of clients and $f$ is the number of malicious clients\color{black}

In Section II, we have supplemented the definitions of $\alpha^{min}_{intra}$ and  $\alpha^{max}_{cross}$ as follows:

\color{blue}$\alpha^{min}_{intra}$ and  $\alpha^{max}_{cross}$ are the minimum internal cosine similarity and the maximum cosine similarity cross communities respectively.\color{black}

In Section VII, we have supplemented the definitions of $t$ as follows:

\color{blue}The real-time intimacy index in $t-th$ round  $\rho^{ij}_t$ between devices $P_i$ and $P_j$ is defined as:
\color{black}

In Section VII, we have supplemented the definitions of $\mu$ as follows:

\color{blue}$\mu> 0$ represents the impact of interaction time intervals on credibility.\color{black}

Additionally, to make the variables more easily searchable, we have added a parameter table on page four. We have provided this table in Reviewer 1's Comment 1.

%========================================================
\rcomment{
\color{red} Please specifically analyze the advantages of their privacy amplification mechanism. The authors' privacy amplification is achieved by limiting the sensitivity so that the epsilon is smaller at the same noise scale. Although this is not the same privacy mechanism I would expect, privacy enhancement is achieved. However, the authors seem to compare the effects of the different schemes only by comparing the accuracy of the experiments. Could the authors theoretically analyze the difference between their privacy amplification mechanism and other privacy enhancement schemes (such as DPFL as mentioned by the authors)?
% 请具体分析其隐私放大机制的优势。作者的隐私放大是通过限制灵敏度来实现的，使得在相同的噪声尺度下，噪声放大更小。虽然这不是我所期望的相同的隐私机制，但可以实现隐私增强。然而，作者似乎只是通过比较实验的准确性来比较不同方案的效果。作者能否从理论上分析他们的隐私放大机制与其他隐私增强方案（如作者提到的DPFL）的区别？
%改法：
}
% 非常感谢您的意见。

\textbf{Response:} Thanks for the reviewer's valuable comment.

%本文提出的隐私增强策略与Reviewer提出的联邦学习中的隐私策略不同，主要侧重于针对异构联邦学习场景下的差分隐私机制。在异构联邦学习场景，由于个体间本地模型更新的差异较大，而高斯差分隐私机制添加噪声的方差大小取决于敏感度的大小，因此，

\color{black}

% \textbf{Intension:}\\
% 1.Disrupting Neural Network Performance: The primary objective of the attacker is to impair the model's performance, causing it to produce incorrect outputs on certain inputs. This may pose a threat to the model's reliability and security, especially in critical domains such as intrusion detection.\\
% 2.Bypassing Security Measures: Adversarial attacks can also be used to circumvent security measures deployed with the model, such as CAPTCHA or malware detection systems. By targeting these security measures, attackers can gain access to restricted resources or carry out malicious activities.

% \textbf{Capabilities:}\\
% 1.Generating Adversarial Examples: Attackers can employ various techniques to create adversarial examples that closely resemble the original input but are capable of deceiving neural networks. These techniques include gradient-based attacks, Generative Adversarial Networks (GANs), and evolutionary algorithms, among others.\\
% 2.White-Box and Black-Box Attacks: Attackers can conduct white-box attacks (having full knowledge of the model's structure and parameters) or black-box attacks (only knowing the model's input and output but lacking detailed information about the model).\\
% 3.Transferability: An adversarial example may have the ability to generalize across different models, making it applicable to multiple models. This enables attackers to leverage the same adversarial examples in diverse environments.\\
% 4.Imperceptibility: Adversarial examples typically require being almost imperceptible to human observation. This necessitates careful crafting by attackers to ensure that they are indistinguishable from the original input in terms of visual or perceptual cues.

%========================================================
\newpage

\rcomment{
\color{red} What is the basis of the algorithm parameter setting, such as Table I and other parameters? % 架构
}
% 算法参数设置的依据是什么，如表I等参数？
% 本文所使用的基础模型架构及相应的超参数设置参考了如FL-WBC和SFAT等论文中的实验设置。针对不同数据集的特性，模型结构和超参数进行了调整，以适应特定任务需求。

% 对于MNIST和EMNIST数据集，这些数据集包含灰度手写数字图像，输入数据尺寸为28x28，且只有一个通道。为了有效提取图像的局部特征，模型使用了两层5x5的卷积层。第一层卷积层的输入通道为1（单通道灰度图像），输出通道设置为10，能捕捉图像的边缘和基本几何结构。第二层卷积层的输入为10个特征图，输出通道为20，进一步提取更高级的特征。每一层卷积之后，使用ReLU激活函数引入非线性，并通过2x2的最大池化层减少特征图的尺寸，从而降低计算复杂度并增强模型的泛化能力。此外，使用Dropout机制（在卷积层之后和全连接层之间）防止过拟合，特别是对于相对小规模的MNIST和EMNIST数据集，Dropout可以有效抑制模型在训练数据上表现过好而在测试数据上表现欠佳的问题。

% 针对CIFAR-10和CIFAR-100数据集，这些数据集由32x32的彩色图像组成，输入为RGB三通道。因此，模型的第一层卷积层设计为接受3个输入通道，并输出6个特征图，卷积核大小同样为5x5。通过这一层卷积，模型能够提取低级的颜色和边缘特征。第二层卷积层接收6个输入特征图，输出16个特征图，这一层进一步提取中级特征，如图像的纹理和形状。每一层卷积之后同样使用ReLU激活函数和2x2最大池化层，减少特征图尺寸并保留最重要的特征信息。

% 两种模型的不同之处在于，MNIST和EMNIST数据集为单通道灰度图像，结构相对简单，因此只需要10和20个特征通道即可有效提取图像信息。而对于CIFAR-10和CIFAR-100，由于其是彩色图像，且包含更多的复杂性（如多种颜色、形状和纹理），卷积层的通道数相对增加。此外，MNIST和EMNIST中的全连接层参数为320到50，再到最终的分类输出，而在CIFAR中，由于图像尺寸稍大，全连接层从1655（400个节点）开始，逐步减少至120，再到84，最后输出类别数。对于CIFAR-10和CIFAR-100，类别数分别为10和100，因此在最后的输出层中，分类节点数量根据数据集的不同进行了调整。

% 在所有数据集中，超参数如学习率、batch size、Dropout率等也根据实验调整，以确保在不同的数据集上都能获得最优性能，确保模型在有效学习数据特征的同时具备良好的泛化能力。

% FL-WBC: Enhancing Robustness against Model Poisoning Attacks in Federated Learning from a Client Perspective
% COMBATING EXACERBATED HETEROGENEITY FOR ROBUST MODELS IN FEDERATED LEARNING
%感谢您的提议。
\textbf{Response:} Thanks for the reviewer's valuable comment.

The basic model architecture and corresponding hyperparameter settings used in this paper were based on experimental setups from papers such as \cite{sun2021fl}, \cite{zhu2023combating}, \cite{liang2020think}, \cite{zhu2024isfl} and \cite{zhou2022adversarial}. The model structure and hyperparameters were adjusted to suit the characteristics of different datasets and meet the specific task requirements. To effectively capture the unique features of each dataset, we designed specific model architectures as detailed below.

\textbf{CNN architecture for MNIST and EMNIST}: For the MNIST and EMNIST datasets, which consist of grayscale handwritten digit images with an input size of 28x28 and a single channel, the model uses two 5x5 convolutional layers to effectively extract local features from the images. The first convolutional layer has 1 input channel (for the grayscale images) and 10 output channels, capturing edges and basic geometric structures. The second convolutional layer takes in 10 feature maps as input and outputs 20 channels, extracting more advanced features. After each convolutional layer, a ReLU activation function introduces nonlinearity, and a 2x2 max-pooling layer reduces the size of the feature maps, lowering computational complexity and enhancing the model’s generalization ability. Additionally, a Dropout mechanism (applied after the convolutional layers and between the fully connected layers) is used to prevent overfitting. This is particularly effective for relatively small-scale datasets like MNIST and EMNIST, where Dropout helps mitigate the issue of the model performing too well on training data but poorly on test data.

\textbf{CNN architecture for CIFAR-10}: For the CIFAR-10 datasets, which consist of 32x32 color images, the input is RGB with three channels. Thus, the first convolutional layer is designed to accept 3 input channels and outputs 6 feature maps, with the same 5x5 kernel size. This layer extracts low-level features like colors and edges. The second convolutional layer takes in 6 input feature maps and outputs 16, further extracting mid-level features such as textures and shapes. Each convolutional layer is followed by a ReLU activation function and a 2x2 max-pooling layer to reduce the size of the feature maps while retaining the most important information.

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/resnet_all.png}
    \caption{The architecture of ResNet-34}
    \label{fig:resnet34}
\end{figure}

\textbf{ResNet34 for CIFAR-100}: For the CIFAR-100 dataset, it contains 100 classes, and each image is a 32x32x3 image. A simple CNN structure is not suitable, so we used the ResNet34 model as the base model for our experiments. As Figure \ref{fig:resnet34} depicted, ResNet34 is a convolutional neural network with 34 layers, consisting of one convolutional layer (Conv1), one max-pooling layer (Maxpool), four residual blocks (Conv1\_x, Conv2\_x, Conv3\_x, Conv4\_x), one average pooling layer (Avgpool), and one fully connected layer (FC).

\textbf{Summary of differences between these models}: The key differences between the models lie in the input channels, model complexity, and number of output classes. For MNIST and EMNIST, the input consists of single-channel grayscale images, while for CIFAR-10 and CIFAR-100, the input consists of three-channel RGB images. Due to this, the first convolutional layer in the CNN models for MNIST and EMNIST has 1 input channel and outputs 10 feature maps, whereas for CIFAR-10, the first layer has 3 input channels and outputs 6 feature maps. Additionally, CIFAR-100 uses the more complex ResNet34 architecture, which is deeper and more capable of handling the greater complexity of color images and the larger number of output classes. The number of output classes also differs: MNIST, EMNIST, and CIFAR-10 each have 10 output classes, whereas CIFAR-100 has 100 output classes, necessitating a larger model and more complex feature extraction layers. Thus, the models are adjusted to capture the unique characteristics of the respective datasets, with simpler architectures for grayscale images and more complex architectures like ResNet34 for datasets with more classes and higher input complexity.

Across all datasets, hyperparameters such as learning rate, batch size, and Dropout rate were also adjusted based on experiments to ensure optimal performance. This allows the model to learn the data features effectively while maintaining good generalization ability.

% 为了在文章中准确表达模型选择的原因，我们进行了以下修改
To accurately explain the reasons for model selection in the article, we have made the following modifications:
\begin{table}[b]\scriptsize
\setlength{\abovecaptionskip}{0cm}
\setlength{\belowcaptionskip}{0.2cm}
\renewcommand{\arraystretch}{1.2}
    \caption{\centering{Neural network structures}}\label{table:NN-structure}
\centering
\begin{tabular}{l|l}
\hline
\makecell[l]{MNIST/EMNIST} & 
\makecell[l]{
$28^{2}\times1 \xrightarrow{Conv(f=5,s=1)} 24^{2}\times10 \xrightarrow{Pool(f=2)} $
$12^{2}\times10  \xrightarrow{Conv(f=5,s=1)} 8^{2}\times20\xrightarrow{Pool(f=2)} $\\
$4^{2}\times20 \xrightarrow{} 320 \xrightarrow{FC} 50 \xrightarrow{FC} 10\times1$
}\\ 
\hline

CIFAR-10 & 
\makecell[l]{
$ 32^{2}\times3 \xrightarrow{Conv(f=5,s=1)} 28^{2}\times6 \xrightarrow{Pool(f=2,s=2)} $
$14^{2}\times6 \xrightarrow{Conv(f=5,s=1)} 10^{2}\times16 \xrightarrow{Pool(f=2,s=2)}$\\
$5^{2}\times16 \xrightarrow{} 400 \xrightarrow{FC} 120 \xrightarrow{FC} 84 \xrightarrow{FC} 10\times1$
}\\ 
\hline

\textcolor{blue}{CIFAR-100}& 
\makecell[l]{ \color{blue}
$32^{2}\times3 \xrightarrow{Conv1(f=7,s=2)} 16^{2}\times64 \xrightarrow{Maxpool(f=3,s=2)} $
$8^{2}\times64 \xrightarrow{Conv2\_x} 8^{2}\times64 \xrightarrow{Conv3\_x}$\\ \color{blue}
$4^{2}\times128 \xrightarrow{Conv4\_x} 2^{2}\times256 \xrightarrow{Conv5\_x}$
$1^{2}\times512 \xrightarrow{Avgpool} 1^{2}\times512 \xrightarrow{} 512 \xrightarrow{FC} 100 \times 1$ \color{black}
}
\\ \hline
\end{tabular}
\end{table}

\color{blue}Based on existing researches such as \cite{sun2021fl}, \cite{zhu2023combating}, \cite{liang2020think}, \cite{zhu2024isfl} and \cite{zhou2022adversarial}, we construct different convolutional neural network (CNN) models to cater above image identification learning tasks. The key differences between the models are the input channels (single-channel grayscale for MNIST/EMNIST vs. three-channel RGB for CIFAR-10/CIFAR-100), model complexity (simpler CNNs for MNIST/EMNIST/CIFAR-10 vs. the deeper ResNet34 for CIFAR-100), and the number of output classes (10 for MNIST, EMNIST, and CIFAR-10 vs. 100 for CIFAR-100), with adjustments made to suit the specific characteristics and complexity of each dataset. \color{black}

\color{black}
%========================================================
\rcomment{
\color{red} The authors conducted experiments on three public data, MNIST, EMNIST, and CIFAR, and achieved good experimental results. However, the article does not specify whether CIFAR-10 or CIFAR-100 is used, although it can be known that the authors used CIFAR-10 by observing Table I, it is better to describe it clearly in the article. What will be the effect of CIFAR-100? Is it possible to simply test it?
}
% 作者在MNIST、EMNIST和CIFAR三个公共数据上进行了实验，取得了良好的实验结果。但文中并未明确使用的是CIFAR-10还是CIFAR-100，虽然通过观察表I可知作者使用的是CIFAR-10，但还是在文中描述清楚为好。CIFAR-100的效果如何？有没有可能简单地测试一下？
\textbf{Response:} Thanks for the reviewer's valuable comment.

%针对cifar-100数据集，为了验证cos-hfl在隐私增强上面的表现，我们额外增加了在正常、异构、不诚实用户三种场景下的实验，其具体实验结果如图1，图2，图3所示。同时为了验证cos-hfl在包含噪声和异构环境下的表现，我们也额外进行了相应的实验，具体实验结果如图3，图4所示。
To evaluate the privacy-amplification performance of Cos-HFL on the CIFAR-100 dataset, we additionally conducted experiments under three different scenarios: normal, heterogeneous, and dishonesty. The specific experimental results are shown in Figures \ref{result1:CIFAR100-normal-acc}, \ref{result1:CIFAR100-hetero-acc}, and \ref{result1:CIFAR100-dishonest-acc}. Additionally, to verify the performance of Cos-HFL in noisy \& heterogeneous environments, we also conducted corresponding experiments, with the specific results displayed in Figures \ref{result2:CIFAR100-hetero-norm} and \ref{result2:CIFAR100-hetero-acc}.

For CIFAR-100, the dataset size and the number of categories are much larger than those of CIFAR-10, MNIST, and EMNIST. Therefore, we used ResNet34 for our experiments. By observing the experimental results, we found that our method is less affected by noise in CIFAR-100. In particular, for dishonest users, it is evident that the accuracy of NbAFL and DPFL is significantly lower than that of CoS-HFL. Furthermore, for CFL, due to the noise affecting the clustering judgment, we observed that CFL falls into a local optimum, resulting in a lower final accuracy compared to the correctly clustered CoS-HFL.
% 对于CIFAR100来说，数据集大小与类型数量远大于CIFAR-10与MNIST、EMNIST，因此，我们采用了ResNet34进行实验。通过观察实验图发现，在CIFAR-100中，我们的方法受噪声影响较小。尤其是对于不诚实的用户，可以发现NbAFL与DPFL的Accuracy明显低于CoS-HFL。此外，对于CFL，由于噪声影响了分簇的判断，可以发现CFL陷入了局部最优解，导致收敛后的准确率低于分簇正确的CoS-HFL。

% 同时，我们在文章实验部分进行了以下修改，增加了对cifar-100数据集实验结果的描述：
At the same time, we made the following modifications in the experimental section of the article, adding a description of the experimental results on the CIFAR-100 dataset:

\color{blue}
Firstly, we demonstrate the accuracy in the normal situation without heterogeneous or dishonest participants in Figures 5, 8 and 11 (MNIST/CIFAR-10/CIFAR-100). Based on the results, we can see that private obfuscation causes a certain amount of accuracy decline in the beginning. Although, because CoS-HFL injects less noise than the other two peers, the purple line gradually outperforms green and red ones over time.

Secondly, Figures 6, 9 and 12 show the results under heterogeneous environments, where we replace 5 normal participants with 5 heterogeneous ones. We can tell that CoS-HFL still achieves better performance from the figures within merely 200 slots. With a greater heterogeneity degree and a much larger duration in real-world distributed learning scenarios, the amplification effect will be more significant.

Besides, we also consider the impact of dishonest devices. In like manner, we let 10 devices dishonestly exaggerate the data variances for additional privacy benefits, while the other 90 participants remain unchanged.  As shown in Figures 7, 10 and 13, the orange lines are almost unaffected, as FL injects no noise. Meanwhile, due to the unnecessarily overlarge sensitivity caused by exaggerated data variances, both DPFL and NbAFL suffer great performance degradation. 
By contrast, with the help of privacy amplification, CoS-HFL limits the noise scale to some extent and obtains better accuracy.

In HFL scenarios, dynamic and varied data characteristics or differentiated learning tasks present significant obstacles to model convergence and accuracy. 
Worse still, existing security designs such as data obfuscation and DP noise injection may further complicate the situation by introducing huge variance into weight updates of HFL model parameters. 
To verify the availability of CoS-HFL, we first deploy two different multitask scenarios, and assume that all devices can perturb local updates before uplink transmission, to simulate the heterogeneity and dynamic randomness, respectively. Then, we compare the model accuracy and max-norm/$Q$ of CoS-HFL with CFL and DPFL.

First, for EMNIST, as shown in Figure 1 (b), we rotate the images ($0^{\circ},90^{\circ},180^{\circ},270^{\circ}$) to create four classes of heterogeneous participants (25 devices per class). Based on Figure 14, our method can correctly partition the device set (blue vertical dashed lines) into different communities, and eventually outperform both CFL and DPFL after correct partition. Hence, as shown in Figure 15, CoS-HFL minimizes the $Q$ over time, while the other two methods' max norms remain high.

%\begin{comment}%13注释（6）-2
Then, for CIFAR-10 and CIFAR-100, as shown in Figure 1 (a), we create two classes of heterogeneous participants (50 devices per class) by extracting color features or profile features. 
Similar to Figures 14, 15 and 18, based on Figures 16, 17 and 19, CoS-HFL also divides participants to correct communities and converges to higher accuracy of the global model. Especially for CIFAR-100, since the ResNet34 model it uses has significantly more parameters compared to CNN, the impact of noise increases dramatically when noise is added. This can mislead the clustering of CFL, resulting in a noticeable decrease in the accuracy of CFL.

\color{black}
%\end{comment}%13注释（6）-2

\begin{figure}[tb]
	\captionsetup{font=tiny} % 调整图片字幕的大小
	\begin{minipage}[!t]{0.333\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{./figures/cifar100_acc_norm.pdf}
		\vspace{-0.5em}
		\caption{{\color{red}Accuracy vs normality on CIFAR-100}}
		\label{result1:CIFAR100-normal-acc}
	\end{minipage}%
	\begin{minipage}[!t]{0.333\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{./figures/cifar100_acc_heterog.pdf}
		\vspace{-0.5em}
		\caption{\textcolor{red}{Accuracy vs heterogeneity on CIFAR-100}}
		\label{result1:CIFAR100-hetero-acc}
	\end{minipage}
	\begin{minipage}[!t]{0.333\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{./figures/cifar100_acc_dishonest.pdf}
		\vspace{-0.5em}
		\caption{\textcolor{red}{Accuracy vs dishonesty on CIFAR-100}}
		\label{result1:CIFAR100-dishonest-acc}
	\end{minipage}
	\vspace{-0.3cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \begin{subfigure}[t]{0.45\textwidth} % 调整第一张图片的宽度
        \centering
        \includegraphics[width=\textwidth]{./figures/cifar100_acc_2.pdf}
        \caption{\textcolor{red}{Accuracy on CIFAR-100}} % 替换序号为(b)
        \label{result2:CIFAR100-hetero-norm}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.48\textwidth} % 调大第二张图片的宽度
        \centering
        \includegraphics[width=\textwidth]{./figures/cifar100_dw.pdf}
        \caption{\textcolor{red}{Max-norm/$Q$ on CIFAR-100}} % 替换序号为(a)
        \label{result2:CIFAR100-hetero-acc}
    \end{subfigure}
    \vspace{-0.3cm}
    \caption{Results of Accuracy(a) and Max-norm/$Q$(b) on CIFAR-100}
    \label{fig:cifar100-comparison}
\end{figure}

%========================================================
\rcomment{
\color{red} The authors do not seem to have considered the issue of communication overhead in federated learning, and I would ask the authors to think hard about whether this question needs to be answered.
}
% 作者似乎没有考虑到联邦学习中的通信开销问题，我想请作者认真思考这个问题是否需要回答。
% 感谢您的comment。根据您的提问，我们认真考虑了CoS-HFL的开销问题。在联邦学习中，客户端通常作为计算与通信能力较差的计算节点，主要有通信开销与计算开销。在通信层面，通常假设联邦学习的服务器拥有丰富的通信资源，故通常不考虑服务器的通信开销。因此，联邦学习的通信开销取决于模型的参数量、客户端与服务器通信轮次、额外的传递信息。对于CoS-HFL，假设深度学习模型为$\omega$,其参数量为$\|\omega\|$，对于单个通信轮次，其通信量相较于传统的联邦学习只增加了部分非超参数的传递，如$\mathbf{\lambda},\theta, \epsilon,\delta$等，这些参数相较于深度学习模型的大小可以忽略不记。因此，在单个轮次上，CoS-HFL的通信开销与传统的CFL并无明显差异。

%对于模型的收敛速率，通过观察实验数据，CoS-HFL的收敛速率与DPFL、FedAvg、CFL并无明显区别。同时，经过证明[]，FedAvg的收敛速率为$O(\frac{1}{\sqrt{TE})$，其中$T$为全局训练轮次，$E$为客户端本地的迭代次数。同时，CoS-HFL作为一种基于CFL的改进，收敛速度近似于$O(\frac{\sqrt{TME}})$，其中$M$为聚类个数。然而在实践中，聚类个数通常较低，可视作常数。因此，CFL与FedAvg收敛速度并无明显差异。

%综上所述，CoS-HFL与传统的FedAvg在通信开销上并无实质性差异，为

\textbf{Response:}Thank you for your comment! Based on your question, we have carefully considered the overhead of CoS-HFL in federated learning. In federated learning, clients typically serve as nodes with limited computational and communication capabilities, so the overhead mainly includes communication and computational costs.

\textbf{Communication overhead}: It is generally assumed that the server in federated learning has abundant communication resources, so the server's communication cost is not a primary concern. The communication overhead mainly depends on the following factors:

\textit{The number of model parameters:} The parameters that need to be transmitted in federated learning.

\textit{The number of communication rounds between clients and the server:} The frequency of communication determines the total communication burden.
Additional transmitted information: For example, extra parameters or auxiliary data in meta-learning.
For CoS-HFL, assuming the deep learning model is denoted as $\omega$, with parameter size $|\omega|$, in a single communication round, the communication load only slightly increases compared to traditional federated learning due to the transmission of non-hyperparameters like $\mathbf{\lambda}$, $\theta$, $\epsilon$, and $\delta$. Since the size of these parameters is negligible compared to the deep learning model, the communication overhead in a single round of CoS-HFL is not significantly different from that of traditional federated learning.

\begin{table}[t]\scriptsize
\setlength{\abovecaptionskip}{0cm}
\setlength{\belowcaptionskip}{0.2cm}
\renewcommand{\arraystretch}{1.2}
    \caption{\centering{Communication convergence of algorithms}}\label{table:Convergence}
\centering
\begin{tabular}{l|l}
\hline
\makecell[l]{FedAvg\cite{9377960}} & 
\makecell[l]{$\frac{1}{\sqrt{TE}}$
}\\ 
\hline

CFL\cite{CoRR} & 
\makecell[l]{$\frac{1}{\sqrt{TME}}$
}\\ 
\hline

PSASGD\cite{wang2021cooperative} & 
\makecell[l]{ $\frac{1}{\sqrt{TE}}$
}
\\ \hline
CoS-HFL & 
\makecell[l]{ $\frac{1}{\sqrt{TME}}$
}
\end{tabular}
\end{table}

Regarding the convergence rate of the models, through observing experimental data, we found that the convergence rate of CoS-HFL shows no significant difference compared to classic federated learning algorithms such as DPFL, FedAvg, and CFL. At the same time, research has proven [citation needed] that the convergence rate of FedAvg is $O(\frac{1}{\sqrt{TE}})$\cite{CoRR}, where $T$ represents the number of global training rounds, and $E$ is the number of local iterations on the client side. This suggests that FedAvg achieves a good balance between global and local computations, especially when an increase in local iterations can accelerate the model’s convergence.

\textbf{Computation overhead:}
As an improvement based on CFL, CoS-HFL’s convergence rate is approximately $O(\frac{1}{\sqrt{TME}})$\cite{9377960}, where $M$ is the number of clusters. Although this formula indicates that increasing $M$ could accelerate convergence, in practice, $M$ is usually small and can be treated as a constant. Therefore, in most cases, the convergence rates of CoS-HFL and CFL are similar, and there is no significant difference compared to FedAvg.

What's more, considering the computational cost, our method includes uplink privacy calculation, auxiliary downlink privacy calculation, community construction and credit calculation.
As the model's parameter size is $S$, clients number is $N$, the time complexity of each step is as follows:
\begin{itemize}
    \item Uplink privacy: $O(SN)$
    \item Auxiliary downlink privacy: $O(SN)$
    \item Community construction: $O(SN^2)$
    \item Credit calculation: $O(SN^2)$
\end{itemize}

For the whole workflow, the time complexity is $O(SN^2)$. Our method differs from traditional methods\cite{9377960} in terms of time complexity by only a constant factor.
In this article, we mainly focus on the privacy and security of federated learning, and for the next step, we will pay attention to the communication cost for the integration of our work. Our modifications are as follows:

\color{blue}
Let the number of model parameters be denoted as $S$. In a single round, our method shows no significant difference compared to traditional federated learning, both having a complexity of O($SK$). Furthermore, in terms of convergence rounds, as analyzed in \cite{CoRR} and \cite{9377960}, our method makes modifications to the clustering conditions compared to \cite{9377960}, yet only introduces a constant factor's change in communication efficiency. Additionally, the time complexity of the proposed method is the same as CFL, both being $O(SN^2)$, which provides security guarantees for federated learning without imposing an unacceptable computational burden.
\color{black}
% \begin{assumption}
% Local gradient $\Delta \mathcal{L}(w_t^i)$ is Lipschitz continuous with respect to $w$, i.e., $\|\Delta \mathcal{L}(w_t^i)-\Delta \mathcal{L}(w_{t+1}^i)\|\leq L\|w_{t}^i-w_{t+1}^i\|$, where $L$ is a positive constant.
% \end{assumption}
% \begin{assumption}
%     Local loss function $\mathcal{L}(w)$ is strongly convex with respect to $w$, i.e., $\mathcal{L}(w_t^i)\geq \mathcal{L}(w_{t+1}^i)+(w-w^{t+1})^T\Delta \mathcal{L}(w_t^i)+(\mu/2)\|w_t^i-w^{i}_{t+1}\|^2$,
% \end{assumption}
% \begin{assumption}
%     Training loss of cluster $s$ is defined as $\mathcal{L}(w_t^s)$ which is twice-continuously differentiable, i.e., $\mu I \leq \nabla^2\mathcal{L_t^s}$ satisfies $\zeta_1^2 \leq \|\nabla \mathcal{L}(w_t^s)\|^2\leq \zeta^2_2$ with $\zeta_1,\zeta_2>0$.
% \end{assumption}

%对于CoS_HFL,我们有如下约束：
% Due to weight clipping, we have:
% \begin{equation}
%     \begin{aligned}
% 		||\eta^i_{t}\nabla_{w}  \mathcal{L}_{i}(w, \zeta^{i,\prime}_{k})|| \leq \max||\Delta w^i_t||\color{black}= \xi_i. %\forall j,
% 		\end{aligned}
% \end{equation}

% So that 
% \begin{equation}
%     \| \nabla_{w}  \mathcal{L}_{i}(w, \zeta^{i,\prime}_{k})\| \leq \frac{\xi_i}{\eta_t^i}
% \end{equation}

% By L-smoothness of the loss function $\mathcal{L}$, we have
% \begin{equation}
% \begin{aligned}
%     \mathbb{E} [\mathcal{L}(w_{t+1}^i)-\mathcal{L}(w_t^i)]\\
%     \leq \mathbb{E}<\nabla\mathcal{L}(w_{t}^i),w_{t+1}^i-w_{t}^i >+\frac{L}{2}\mathbb{E}\|\|
% \end{aligned}
% \end{equation}

\newpage
% \begin{comment}

% \bibliographystyle{apalike}
% \bibliography{reference}

\textbf{\hspace{6.5cm}References:}
\bibliographystyle{IEEEtran}
\bibliography{reference}

% [R1] Achituve I, Shamsian A, Navon A, et al. Personalized federated learning with gaussian processes[J]. Advances in Neural Information Processing Systems, 2021, 34: 8392-8406.

% [R2] Wei K, Li J, Ding M, et al. User-level privacy-preserving federated learning: Analysis and performance optimization[J]. IEEE Transactions on Mobile Computing, 2021, 21(9): 3388-3401.

% [R3] Sun J, Li A, DiValentin L, et al. Fl-wbc: Enhancing robustness against model poisoning attacks in federated learning from a client perspective[J]. Advances in neural information processing systems, 2021, 34: 12613-12624.

% [R4] Zhu J, Yao J, Liu T, et al. Combating exacerbated heterogeneity for robust models in federated learning[J]. arXiv preprint arXiv:2303.00250, 2023.

% [R5] Zhang J, Hua Y, Wang H, et al. Fedala: Adaptive local aggregation for personalized federated learning[C]//Proceedings of the AAAI Conference on Artificial Intelligence. 2023, 37(9): 11237-11244.

% [R6] Han S, Buyukates B, Hu Z, et al. FedSecurity: A Benchmark for Attacks and Defenses in Federated Learning and Federated LLMs[C]//Proceedings of the 30th ACM SIGKDD Conference on Knowledge Discovery and Data Mining. 2024: 5070-5081.

% [R7] Liu Z, He W, Chang C H, et al. SPFL: A Self-purified Federated Learning Method Against Poisoning Attacks[J]. IEEE Transactions on Information Forensics and Security, 2024.

% [R8] Wei K, Li J, Ma C, et al. Personalized federated learning with differential privacy and convergence guarantee[J]. IEEE Transactions on Information Forensics and Security, 2023.

% [R9] Ilhan F, Su G, Liu L. Scalefl: Resource-adaptive federated learning with heterogeneous clients[C]//Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2023: 24532-24541.

% [R10] Wu X, Huang F, Hu Z, et al. Faster adaptive federated learning[C]//Proceedings of the AAAI conference on artificial intelligence. 2023, 37(9): 10379-10387.

% [R11] Ye R, Wang W, Chai J, et al. Openfedllm: Training large language models on decentralized private data via federated learning[C]//Proceedings of the 30th ACM SIGKDD Conference on Knowledge Discovery and Data Mining. 2024: 6137-6147.

% [R12] Nguyen T D, Rieger P, De Viti R, et al. {FLAME}: Taming backdoors in federated learning[C]//31st USENIX Security Symposium (USENIX Security 22). 2022: 1415-1432.

% [R13] Yang H, Xi W, Shen Y, et al. RoseAgg: Robust Defense Against Targeted Collusion Attacks in Federated Learning[J]. IEEE Transactions on Information Forensics and Security, 2024.

% \end{comment}

\end{document}

% FedSecurity: A Benchmark for Attacks and Defenses in Federated Learning and Federated LLMs
% SPFL: A Self-purified Federated Learning Method Against Poisoning Attacks
% Personalized Federated Learning With Differential Privacy and Convergence Guarantee
% ScaleFL: Resource-Adaptive Federated Learning with Heterogeneous Clients
% Faster Adaptive Federated Learning
% FedALA: Adaptive Local Aggregation for Personalized Federated Learning
% OpenFedLLM: Training Large Language Models on Decentralized Private Data via Federated Learning
% Every Parameter Matters: Ensuring the Convergence of Federated Learning with Dynamic Heterogeneous Models Reduction
% FLAME: Taming Backdoors in Federated Learning
% RoseAgg: Robust Defense Against Targeted Collusion Attacks in Federated Learning

### 2024-10-22 main-v2.tex
C:\Users\LetMeFly\Desktop\大语言模型\Codes\paper
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 %如图\ref{fig:scenario}所示，考虑在机器人物联网（IoRT）网络中对视觉大模型进行联邦微调的场景下，整个系统模型包括多个机器人节点和一个中心服务器。每轮，每个机器人节点在本地对视觉大模型进行微调并只上传微调部分的参数更新，随后中心服务器对所有更新进行聚合，然后下发聚合后的参数，开启新一轮的联邦微调。以下是系统模型的详细描述。
-As illustrated in Figure \ref{fig1:scene}, consider the federated learning scenario of fine-tuning of LVLMs in IoRT network.
-The system model consists of multiple robot nodes and a central server.
-In each round, every node calculates the fine-tuned model of LVLMs locally and uploads only the weights updates.
-The central server then aggregates all the updates and distributes the aggregated model to initiate the next round of the FFT process.
-Detailed description is provided below:
-
-%\textbf{参与者和数据集}：假设系统模型中存在 $N$ 个机器人节点，每个节点记作 $R_i$, 其中$i \in \{1, 2, \ldots, N\}$。 每个机器人节点 $R_i$ 拥有本地数据集 $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$，其中 $x_{i,j}$ 表示输入数据，$y_{i,j}$ 表示对应的标签数据，$|D_i|$ 为数据集的大小，所有节点本地数据集的并集$D = \bigcup_{i=1}^{N} D_i$构成整体数据集。
+As illustrated in Figure \ref{fig1:scene}, \textcolor{red}{consider the scenario of federated fine-tuning (FFT) for large vision language models (LVLMs) in an Internet of Robotic Things (IoRT) network.
+The entire system model consists of multiple robot nodes and a central server.
+In each round, each robot node locally fine-tunes the vision model and only uploads the updates of the fine-tuned part.
+The central server then aggregates all updates and distributes the aggregated parameters to initiate a new round of federated fine-tuning.
+Below is a detailed description of the system model.}
+
+%\textbf{参与者和数据集}：假设系统模型中存在 $N$ 个机器人节点，每个节点记作 $R_i$, 其中$i \in \{1, 2, \ldots, N\}$。 每个机器人节点 $R_i$ 拥有本地数据集 $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$，其中 $x_{i,j}$ 表示训练样本，$y_{i,j}$ 表示对应的标签数据，$|D_i|$ 为数据集的大小，所有节点本地数据集的并集$D = \bigcup_{i=1}^{N} D_i$构成整体数据集。
 \textbf{Participants and Datasets}:
-In the system model, there are $N$ robotic nodes, each denoted as $R_i$, where $i \in {1, 2, \ldots, N}$.
+\textcolor{red}{Assume there are $N$ robot nodes in the system model, with each node denoted as $R_i$, where $i \in {1, 2, \ldots, N}$.
+Each robot node $R_i$ possesses a local dataset $D_i = {x_{i,j}, y_{i,j}}{j=1}^{|D_i|}$, where $x{i,j}$ represents a training sample, $y_{i,j}$ represents the corresponding label, and $|D_i|$ denotes the size of the dataset.
+The union of all local datasets across the nodes, $D = \bigcup_{i=1}^{N} D_i$, constitutes the overall dataset.}
+
+% In this system model, there are $N$ robotic nodes, each denoted as $R_i$, where $i \in {1, 2, \ldots, N}$.
 Each robotic node $R_i$ has a local dataset $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$, where $x{i,j}$ represents the input data, $y_{i,j}$ represents the corresponding label, and $|D_i|$ is the size of the dataset.
@@
     %其中，$W_0$ 为模型的原始权重矩阵，$\Delta W$ 是低秩增量矩阵，$B$ 和 $A$ 是低秩分解矩阵，$r$ 为矩阵的秩。在对视觉大模型进行联邦微调的场景中，全局模型原始参数为$\Theta_p = \sum {W_0}$，而LoRA引入的增量参数为$\theta_p = \sum {W}$，因此全局模型的整个参数集为$\Theta = \Theta_p + \theta_g$。在整个联邦微调过程中，仅对全局模型的增量参数$\theta_g$ 进行微调训练，保持原始参数$\Theta_p$不变。
-    where $W_0$ is the original weight matrix of the model, and $\Delta W$ is the low-rank update matrix, with $B$ and $A$ being low-rank decomposition matrices and $r$ being the rank of the matrix.
-In the federated fine-tuning scenario of the large-scale vision model, the global model's original parameters are $\Theta_p = \sum {W_0}$, while the incremental parameters introduced by LoRA are $\theta_p = \sum {W}$.
+\textcolor{red}{where $W_0$ represents the original weight matrix of the model, $\Delta W$ denotes the low-rank increment matrix, $B$ and $A$ are the low-rank decomposition matrices, and $r$ is the rank of the matrix.
+In the scenario of FFT for LVLMs, the fixed parameters of the global model are given by $\Theta_p = \sum {W_0}$, and the incremental parameters introduced by LoRA are denoted as $\theta_g = \sum {W}$.
+Therefore, the entire parameter of the global model is $\Theta = \Theta_p + \theta_g$.
+Throughout the FFT process, only the parameters $\theta_g$ of the global model are fine-tuned, while the parameters $\Theta_p$ remain unchanged.}
+
+    % In the federated fine-tuning scenario of the large-scale vision model, the global model's original parameters are $\Theta_p = \sum {W_0}$, while the incremental parameters introduced by LoRA are $\theta_p = \sum {W}$.
 Therefore, the global model's full parameter set is $\Theta = \Theta_p + \theta_g$.
@@
 %在每轮联邦训练的开始时，中心服务器将全局模型的增量参数 $\theta_g^{t-1}$ 发送给每个机器人节点$R_i$。每个节点在获得增量参数$\theta_g^{t-1}$后，基于本地数据集 $D_i$ 进行微调训练。
-    At the beginning of each federated training round, the central server sends the global model's incremental parameters $\theta_g^{t-1}$ to each robotic node $R_i$.
-Upon receiving $\theta_g^{t-1}$, each node fine-tunes the model based on its local dataset $D_i$.
+At the beginning of each FFT round, the central server sends the global incremental parameters $\theta_g^{t-1}$ to each robot node $R_i$.
+Upon receiving $\theta_g^{t-1}$, each robot node fine-tunes the local incremental parameters based on its local dataset $D_i$.
 % 算法\ref{alg:local_update}展示了节点进行本地模型每轮训练的主要过程。
@@
 Assume the number of local training epochs is $E_l$, the batch size is $b$, and the learning rate is $\eta$.
-For each epoch, the node $R_i$ randomly samples a batch of data $D_i^b \sim Sample(D_i, b)$ from its local dataset and updates the incremental parameters using an optimization procedure as:
+For each epoch, the node $R_i$ randomly samples a batch of data $D_i^b \sim Sample(D_i, b)$ from $D_i$ and updates the $\theta_g^{t-1}$ using an optimization procedure as:
 \begin{equation}
@@
 %其中$(\theta_i^{t})^e$表示在第$e$轮微调后的参数，初始时$(\theta_i^{t})^0 = \theta_g^{t-1}$。
-    where $(\theta_i^{t})^e$ denotes the parameters after the $e$-th epoch, with the initial value $(\theta_i^{t})^0 = \theta_g^{t-1}$.
-
+where $(\theta_i^{t})^e$ denotes the local incremental parameters after $e$ training epoch, with the initial value $(\theta_i^{t})^0 = \theta_g^{t-1}$.
 %本地训练的目标是最小化损失函数 $f(D_i^b, (\theta_i^{t})^e)$： 
-    The local training objective to minimize the loss $f(D_i^b, (\theta_i^{t})^e)$ is:
+The local training objective to minimize the loss $f(D_i^b, (\theta_i^{t})^e)$:
 \begin{equation}
@@
 %其中$\Theta$是模型的原始参数， $\ell$表示损失函数（如交叉熵损失）。本地训练完成后，节点计算其增量参数更新 $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ 并上传至中心服务器。
-    where $\Theta_p$ represents the original parameters of the model, and $\ell$ denotes the loss function (e.g., cross-entropy loss).
-After local training is completed, the node computes the update to the incremental parameters $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ and uploads the result to the central server.
-
-    %\item \textbf{联邦聚合}：在每轮本地训练结束后，中心服务器从每个机器人节点 $R_i$ 收集本地更新$\triangledown \theta_i^t$，并利用相应的聚合算法进行聚合，以更新全局增量参数得到$\theta_g^t$，其计算公式为：
+where $\ell$ denotes the loss function (e.g., cross-entropy loss).
+After local training is completed, the robot node computes the update of the incremental parameters $\triangledown \theta_i^t = (\theta_i^t)^{E_l} - (\theta_i^t)^0$ and uploads it to the central server.
+
+%\item \textbf{联邦聚合}：当中心服务器接收到所有机器人节点的本地更新$\triangledown \theta_i^t$后，利用相应的聚合算法进行聚合得到新一轮的全局增量参数$\theta_g^t$：
 \textbf{Federated Aggregation}:
-    At the end of each round, the central server collects the local updates $\triangledown \theta_i^t$ from each robotic node $R_i$ and aggregates them using a specified aggregation algorithm to update the global model parameters $\theta_g^t$:
+\textcolor{red}{After the central server receives the updates $\triangledown \theta_i^t$ from all robot nodes, it applies the appropriate aggregation algorithm to generate the next round's global incremental parameters $\theta_g^t$:
+% The central server collects the local updates $\triangledown \theta_i^t$ from each robot node $R_i$ and aggregates them using a specified aggregation algorithm to update the global incremental parameters $\theta_g^t$:
 \begin{equation}
@@
 %其中，$Agg$表示中心服务器使用到的聚合算法，例如FedAvg、FLTrust\cite{cao2020fltrust}、RoseAgg\cite{yang2024roseagg}等，$\theta_g^t$ 是第 $t$ 轮更新的全局增量参数，更新后的全局增量参数 $\theta_g^t$ 将在下一轮训练前下发给所有机器人节点，用于进一步的本地微调。
-    where $Agg$ denotes the aggregation algorithm employed by the central server, such as FedAvg, FLTrust \cite{cao2020fltrust}, or RoseAgg \cite{yang2024roseagg}.
-The global incremental parameters $\theta_g^t$, updated in round $t$, are then distributed to all robotic nodes before the next round of training to facilitate further local fine-tuning.
+where $Agg$ denotes the aggregation algorithm employed by the central server, such as FedAvg, FLTrust \cite{cao2020fltrust}, or RoseAgg \cite{yang2024roseagg}.}
 
 \section{Threat Model}
-%Attacker's Goal：假设在对视觉语言模型进行联邦微调的场景中，存在一个或者多个由攻击者操纵的恶意节点。其目标是对全局模型$\Theta$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别，即$\Theta(x+\delta) = y'$，其中$x$代表正常输入，$y'$表示目标类别。同时尽可能保持对干净输入的分类准确性，即$\Theta(x) = y$，其中$y$为输出$x$的原始类别。
-\textbf{Attacker's Goal:} In the scenario of the FFT process of LVLMs, it is assumed that one or more malicious nodes are controlled by attackers.
-The goal is to implant a backdoor into the global model $\Theta$, such that the model classifies any test input with a predefined trigger $\delta$ as the target class, i.e., $\Theta(x + \delta) = y'$, where $x$ represents a normal input and $y'$ denotes the target class.
-Simultaneously, the attacker aims to preserve the classification accuracy on clean inputs, such that $\Theta(x) = y$, where $y$ is the original class corresponding to $x$.
-
-%Attacker's Ability: 在对视觉大模型进行联邦微调的场景中，假设攻击者对恶意节点的本地训练过程具有完全的控制权。这意味着攻击者可以任意操控本地数据、触发器模式、优化策略和本地更新过程。此外，攻击者可以采用“智能”攻击策略，这种策略的特点是攻击效果不会在单轮训练中显现，而是通过多轮训练的累积效应逐步将后门植入全局模型中。这种场景在实际中是可能存在的，因为中央服务器只能接收到客户端上传的训练后模型更新，而无法知晓每个客户端的具体训练过程。然而，攻击者无法对中央服务器的操作进行干扰，例如，无法更改全局模型的聚合规则或篡改其他良性客户端的模型更新。
-\textbf{Attacker's Ability:} In the FFT processes of LVLMs, it is assumed that the attacker has complete control over the local training process of malicious nodes.
+% 在对视觉语言模型进行联邦微调的场景中，我们假设存在一个或者多个由攻击者操纵的恶意节点，并且恶意节点的数量小于全部参与节点的一半。攻击者的目标是对全局模型$\Theta$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别，即$\Theta(x+\delta) = y'$，其中$x$代表正常输入，$y'$表示目标类别。同时尽可能保持对干净输入的分类准确性，即$\Theta(x) = y$，其中$y$为输出$x$的原始类别。
+\textcolor{red}{In the scenario of FFT for LVLMs, we assume the presence of one or more malicious nodes controlled by attackers, with the number of malicious nodes being less than half of all participating nodes.}
+
+\textbf{Attacker's Goal:} The attacker's goal is to implant a backdoor into the global model $\Theta$, such that the model classifies any input with a predefined trigger $\delta$ as the target class, i.e., $\Theta(x + \delta) = y'$, where $x$ represents a normal input and $y'$ denotes the target class.
+Simultaneously, the attacker seeks to maintain the classification accuracy for clean inputs, i.e., $\Theta(x) = y$, where $y$ is the original class corresponding to $x$.
+
+%Attacker's Ability: 攻击者对恶意节点的本地训练过程具有完全的控制权，意味着攻击者可以任意操控本地数据、触发器模式、优化策略和本地更新。此外，攻击者可以采用“智能”攻击策略，这种策略的特点是攻击效果不会在单轮训练中显现，而是通过多轮训练的累积效应逐步将后门植入全局模型中。这种场景在实际中是可能存在的，因为中央服务器只能接收到客户端上传的训练后模型更新，而无法知晓每个客户端的具体训练过程。然而，攻击者无法对中央服务器的操作进行干扰，例如，无法更改全局模型的聚合规则或篡改其他良性客户端的本地更新。
+\textbf{Attacker's Ability:} 
+\textcolor{red}{The attacker has complete control over the local training process of the malicious robot nodes, meaning they can manipulate local data, trigger patterns, optimization strategies, and local updates at will.
+Additionally, the attacker may adopt a stealthy attack strategy, where the backdoor is not implanted in a single training round but gradually embedded into the global model through the cumulative effect of multiple rounds of training.
+This scenario is plausible in practice, as the central server only receives the updates uploaded by robot nodes and has no insight into the specific training process of each node.
+However, the attacker cannot interfere with the aggregation process of the central server (i.e., altering the global model aggregation rules) or tamper with the local updates of benign nodes.}
+
+% In the FFT processes of LVLMs, it is assumed that the attacker has complete control over the local training process of malicious nodes.
 This means the attacker can manipulate the local dataset, trigger patterns, optimization strategies, and the local update procedure at will.
@@
 \end{figure}
-%^\textbf{Motivation:} 目前的防御策略主要集中于利用攻击的“浅层语义特征”来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向\cite{foolsgold}，范数\ref{sun2019can}以及几何中心\cite{pillutla2022robust}等几何或者统计特性。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。
-% Multi-metrics adaptively identifies backdoors in Federated learning
-%首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明\cite{huang2023multi}，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。但值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终在某种分布上具有偏移。
+%^\textbf{Motivation:} 目前的防御策略主要集中于利用攻击的“浅层语义特征”来进行恶意节点识别，所谓浅层语义是指模型上传更新的方向\cite{foolsgold}，范数\ref{sun2019can}以及几何中心\cite{pillutla2022robust}等几何或者统计特性。然而，这些基于浅层特征的防御方法在高维空间中存在显著的局限性。首先，这些防御方式只能在特定假设条件下对某些类型的攻击起作用。例如，余弦距离能够检测出具有较大方向偏差的恶意更新，而欧几里得距离则用于检测通过扩大$L_2$范数影响全局模型的恶意更新。同时最新的研究表明\cite{huang2023multi}，基于欧几里得距离等传统的距离度量方法在高维空间中无法有效区分恶意和良性更新，因为这些方法往往受到维度灾难的影响。此外攻击策略也在不停的演变，现在的攻击者已经能够通过精心调整，使恶意更新在方向、范数等浅层特征上与良性更新相似，从而巧妙地避开这些基于浅层语义特征的防御措施，最终在全局模型中植入后门。但尽管攻击者的攻击策略变得越来越复杂，值得注意的是，后门攻击的本质在于让模型建立起预定义触发器和目标之间的联系，因此无论攻击者如何调整自己的攻击方式或策略，其上传的模型更新相较于良性用户始终在某种分布上具有偏移。
 \textbf{Motivation:} 
-% Current defense strategies primarily focus on identifying malicious nodes using “shallow semantic features” of attacks, such as geometric or statistical characteristics like the direction\cite{foolsgold}, norm\cite{sun2019can}, and geometric center\cite{pillutla2022robust} of node updates.
-However, these shallow feature-based defenses exhibit significant limitations in high-dimensional spaces.
-For instance, these methods often only work under specific assumptions and for certain types of attacks.
-For example, cosine distance can detect malicious updates with significant directional deviation, while Euclidean distance is typically employed to identify malicious updates that inflate the $L_2$ norm and influence the global model.
-Recent studies have also demonstrated \cite{huang2023multi} that traditional distance metrics like Euclidean distance are inadequate in distinguishing between malicious and benign updates in high-dimensional spaces due to the curse of dimensionality.
-Furthermore, attack strategies continue to evolve, with attackers now able to fine-tune their updates to resemble benign ones in terms of direction, norm, and other shallow features, thus effectively bypassing these shallow semantic-based defenses while still implanting backdoors into the global model.
-It is important to note, however, that the core of a backdoor attack lies in creating an association between a predefined trigger and the target.
-Regardless of how the attacker adjusts their attack methods or strategies, the uploaded updates will always exhibit a distributional shift compared to benign nodes.
-Current defense strategies primarily focus on identifying malicious nodes using "shallow semantic features" of attacks, such as geometric or statistical characteristics like the direction\cite{foolsgold}, magnitude\cite{sun2019can}, and geometric center\cite{pillutla2022robust} of node updates.
+Current defense strategies primarily focus on identifying malicious nodes by leveraging shallow semantic features of the attack, such as the direction \cite{foolsgold}, magnitude \cite{sun2019can}, and geometric or statistical properties like geometric centers \cite{pillutla2022robust} of updates.
+However, these defense methods based on shallow semantic features face significant limitations in high-dimensional spaces.
+First, these methods are only effective against certain types of attacks under specific assumptions.
+For example, cosine distance can detect malicious updates with large directional deviations, while Euclidean distance is used to detect malicious updates that affect the global model by increasing the $L_2$ norm.
+Furthermore, recent studies \cite{huang2023multi} have shown that traditional distance metrics, such as Euclidean distance, cannot effectively distinguish between malicious and benign updates in high-dimensional spaces due to the curse of dimensionality.
+Additionally, attack strategies are constantly evolving, and attackers can now carefully adjust their malicious updates to resemble benign updates in terms of direction, magnitude, and other shallow features.
+This allows them to bypass defenses based on shallow semantic features and eventually implant backdoors into the global model.
+\textcolor{red}{Despite the increasingly sophisticated strategies employed by attackers, it is important to note that the essence of backdoor attacks lies in establishing a link between the predefined trigger and the target within the model.
+Thus, regardless of how attackers adjust their attack strategies, their updates will always exhibit some distributional shift compared to benign nodes.}
+
+% Current defense strategies primarily focus on identifying malicious nodes using "shallow semantic features" of attacks, such as geometric or statistical characteristics like the direction\cite{foolsgold}, magnitude\cite{sun2019can}, and geometric center\cite{pillutla2022robust} of node updates.
 However, these shallow feature-based defenses have significant limitations in high-dimensional spaces.
@@
 
-%\textbf{Overview:} 在深度神经网络模型中，每个权重代表两个神经元之间连接的强度。权重分布及其相关的能量在训练过程中会经历动态演变，以缩小模型预测结果与训练数据中的真实目标之间的差距。当后门攻击迫使神经网络模型学习一种在正常数据中不存在的关联模式时，根据后门触发器的设计和实现方式，这种模式可能是微妙的，也可能是相当明显的，但无论如何，它都代表了与模型从正常数据中学习到的模式的偏离。因此，为解决基于浅层语义特征的防御方法在高维空间中面临的局限性，我们从后门攻击的本质出发\cite{zeng2021rethinking}，提出了一种基于深层语义特征的防御策略，重点分析模型更新在频率分布上的差异。通过将本地模型更新转换到频域，我们能够更深入地捕捉恶意更新在低频成分上的异常表现，这些异常通常难以通过传统的浅层特征检测方法发现。通过对频率域上的特征进行分析，我们可以有效地区分出恶意节点与良性节点，从而增强联邦学习系统在面对复杂后门攻击时的鲁棒性和检测精度。
+%\textbf{Overview:} 在神经网络中，每个权重代表两个神经元之间连接的强度，权重分布及其相关的能量在训练过程中会经历动态演变，以缩小模型预测结果与真实目标类别之间的差距。当后门攻击迫使神经网络模型学习一种在正常数据中不存在的关联模式时，根据后门触发器的设计和实现方式，这种模式可能是微妙的，也可能是相当明显的，但无论如何，它都代表了与模型从正常数据中学习到的模式的偏离。因此，为解决基于浅层语义特征的防御方法在高维空间中面临的局限性，我们从后门攻击的本质出发\cite{zeng2021rethinking}，提出了一种基于深层语义特征的防御策略，重点分析模型更新在频域空间上的差异。通过将本地模型更新转换到频域，我们能够更准确地捕捉恶意更新在低频成分上的异常表现，这些异常通常难以被传统的浅层特征防御方法发现。通过对频域上的相应特征进行分析，我们可以有效地区分出恶意节点与良性节点，从而增强联邦学习系统在面对复杂后门攻击时的鲁棒性和检测精度。
 \textbf{Overview:} 
-% In deep neural networks, each weight represents the strength of the connection between two neurons.
-The distribution of these weights and their corresponding energy dynamically evolve during training to minimize the gap between the model's predictions and the ground truth in the training data.
-When a backdoor attack forces the neural network to learn an association pattern that does not exist in normal data, this pattern—depending on the design and implementation of the backdoor trigger—can be subtle or quite evident.
-Nonetheless, it always represents a deviation from the patterns learned from normal data.
-To address the limitations of shallow feature-based defenses in high-dimensional spaces, we propose a defense strategy rooted in the essence of backdoor attacks\cite{zeng2021rethinking}, focusing on deeper semantic features by analyzing differences in the frequency distribution of model updates.
-By transforming local model updates into the frequency domain, we can more effectively capture the anomalous behavior of malicious updates in low-frequency components, which are typically difficult to detect using traditional shallow-feature detection methods.
-Through frequency domain feature analysis, we can effectively distinguish malicious nodes from benign ones, thereby enhancing the robustness and detection precision of federated learning systems when facing sophisticated backdoor attacks.
-In deep neural networks, each weight signifies the strength of the connection between two neurons.
+In neural networks, each weight represents the strength of the connection between two neurons, and the distribution of these weights, along with their associated energy, undergoes dynamic evolution during training to reduce the gap between the model's predicted results and the true classes.
+nonetheless, When a backdoor attack forces the neural network to learn an association that does not exist in normal data, which may be subtle or quite obvious depending on the design and implementation of the backdoor trigger, it invariably represents a deviation from the association learned by the model from normal data.
+\textcolor{red}{To address the limitations faced by defense methods based on shallow semantic features in high-dimensional spaces, we propose a new defense strategy rooted in the essence of backdoor attacks \cite{zeng2021rethinking}, which leverages deep semantic features by focusing on the differences in model updates in the frequency domain.
+According to our experimental results, by transforming local model updates into the frequency domain, we can more accurately capture the abnormal behavior of malicious updates which is typically difficult to detect using traditional shallow feature-based defenses in low-frequency components.
+By analyzing the relevant features in the frequency domain, we can effectively distinguish between malicious and benign nodes, thereby enhancing the robustness and accuracy of federated learning in the face of sophisticated backdoor attacks.}
+
+% In deep neural networks, each weight signifies the strength of the connection between two neurons.
 The distribution of these weights and their corresponding energy dynamically evolves during training to minimize the gap between the model's predictions and the ground truth in the training data.
@@
 \subsubsection{Frequency domain transformation}
-%%%% 相比于目前基于浅层语义特征的防御方法，我们利用DCT进行频域转换，将模型的更新向量映射到频域空间，以探究其在频率域上的分布差异。其主要过程如算法\ref{alg:malicious-node-detection}的4-7行所示，假设每个本地模型的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，通过一维的DCT-II将其转换为对应的频率分布，并提取低频分量，得到频率向量\(G_i^t\)。这里的 $Trunc$ 操作表示仅保留前 $m$ 个低频分量，以捕捉频域中更具代表性的特征用于后续的恶意节点检测。
 %受高维空间中维度灾难的影响，传统的基于距离度量的方法已无法有效识别恶意节点。相反，将模型更新转换到频率域后，其差异将主要集中在低频成分上。因此，专注于低频成分的分析，在提升识别准确率的同时，将显著的降低计算开销。假设每个节点上传的更新为 \(\triangledown \theta_i^t \in \mathbb{R}^d\)，其中 \(i\) 表示机器人节点，\(t\) 表示通信轮次，\(d\) 为本地模型上传更新的维度。对于每个更新 \(\triangledown \theta_i^t\)，对其进行归一化，然后通过一维的DCT-II\cite{ahmed1974discrete}变化将其转换为对应的频率分布，并提取$m$个低频分量，例如5000，得到低频向量\(G_i^t\)。
-Due to the curse of dimensionality in high-dimensional spaces, traditional distance-based methods become ineffective in identifying malicious nodes.
-In contrast, by transforming model updates into the frequency domain, discrepancies primarily concentrate in the low-frequency components.
-Therefore, focusing on the analysis of low-frequency components not only enhances identification accuracy but also significantly reduces computational overhead.
-Suppose each node uploads an update \(\triangledown \theta_i^t \in \mathbb{R}^d\), where $i$ represents the robot node, $t$ denotes the communication round, and $d$ denotes the dimension of the local model update.
-For each update \(\triangledown \theta_i^t\), it is first normalized and then transformed into its corresponding frequency distribution using a one-dimensional DCT-II \cite{ahmed1974discrete}, from which $m$ low-frequency components\cite{fereidooni2023freqfed} (e.g.
-5000 )\cite{fereidooni2023freqfed} are extracted to form the low-frequency vector $G_i^t$.
+Due to the curse of dimensionality in high-dimensional spaces, traditional methods based on shallow semantic
+feature can no longer effectively identify malicious nodes.
+In contrast, once model updates are transformed into the frequency domain, their differences are primarily concentrated in the low-frequency components.
+Focusing on the analysis of these low-frequency components not only improves identification accuracy but also significantly reduces computational overhead.
+\textcolor{red}{For each update \(\triangledown \theta_i^t\), we apply one-dimensional DCT-II \cite{ahmed1974discrete} to obtain its corresponding frequency distribution.
+Then we extract $m$ low-frequency components\cite{fereidooni2023freqfed}, such as 5000, yielding the low-frequency vector $G_i^t$.}
 
@@
 \begin{equation}
-G_i^t = Trunc(DCT(Flatten(\frac{\triangledown \theta_i^t}{{\|\triangledown \theta_i^t\|}_2})), m)
+G_i^t = Trunc(DCT(Flatten(\triangledown \theta_i^t)), m)
 \label{eq:DCT}
@@
 % 在提取到节点更新对应的低频向量\(G_i^t\)后，我们使用流行的聚类算法例如HDBSCAN\cite{mcinnes2017hdbscan}对这些更新进行聚类，得到多个簇$C_0^t, C_1^t, \ldots, C_{\kappa}^t$，其中$\kappa$表示簇的数量。在大多数联邦学习场景中，良性节点的数量通常多于恶意节点的数量，且良性节点的更新通常更接近全局模型的方向并表现出更高的聚集性。基于这一观察，我们选择节点数量最多的簇$C_{max} = \{R_{i_0}, R_{i_1}, \ldots, R_{i_n}\}$作为主要分析对象。为了进一步提取该簇的主要特征或模式，我们对其中所有节点组成的矩阵进行奇异值分解\cite{wang2023scfl}。由于，SVD分解的左奇异向量$\tilde{G}^t$对应于数据的主要方向，因此，$\tilde{G}^t$可以作为良性节点在低频域内的主要特征。
-After extracting the corresponding low-frequency vectors \(G_i^t\) from node updates, we employ popular clustering algorithms such as HDBSCAN \cite{mcinnes2017hdbscan} to cluster these updates, resulting in multiple clusters \(C_0^t, C_1^t, \ldots, C_{\kappa}^t\), where \(\kappa\) denotes the number of clusters.
-In most federated learning scenarios, the number of benign nodes is generally greater than that of malicious nodes, and the updates from benign nodes are usually closer to the direction of the global model and exhibit greater cohesion.
-Based on this observation, we select the cluster with the largest number of nodes, \(C_{max} = \{R_{i_0}, R_{i_1}, \ldots, R_{i_n}\}\), as the primary focus for analysis.
-To further extract the main features or patterns of this cluster, we perform singular value decomposition (SVD)\cite{wang2023scfl} on the matrix formed by all nodes in this cluster.
-Since the left singular vectors of the SVD decomposition, \(\tilde{G}^t\), represent the main directions of the data, \(\tilde{G}^t\) can be considered the primary feature of benign nodes in the low-frequency domain.
+After extracting the corresponding low-frequency vectors \(G_i^t\) from updates, we employ popular clustering algorithms such as HDBSCAN \cite{mcinnes2017hdbscan} to cluster these vectors, resulting in multiple clusters \(C_0^t, C_1^t, \ldots, C_{\kappa}^t\), where \(\kappa\) denotes the number of clusters.
+In most federated learning scenarios, the number of benign nodes typically exceeds that of malicious nodes, which is consistent with the assumptions outlined in our threat model.
+Moreover, the updates from benign nodes are generally closer to the direction of the global model and exhibit a higher degree of aggregation.
+This behavior is also evident in the frequency domain, where it becomes even more pronounced.
+\textcolor{red}{Based on this observation, we select the largest cluster \(C_{max} = \{G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}\}\) as the primary subject for analysis.
+To further extract the main characteristics of this cluster, we perform singular value decomposition (SVD)\cite{wang2023scfl} on the matrix $H^t = (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n}$ formed by all nodes in this cluster.
+Since the left singular vectors of the SVD, denoted as \(\tilde{G}^t\), represent the principal directions of these vectors, \(\tilde{G}^t\) can be regarded as the principal component of benign nodes in the low-frequency domain.}
 
 \begin{equation}
-\tilde{G}^t = \frac{H^t \xi_{\text{max}^t}}{\sqrt{\lambda_{\text{max}^t}}}
+\tilde{G}^t = \frac{H^t \xi^t_{max}}{\sqrt{\lambda^t_{max}}}
 \label{eq:singular}
@@
 
-% 公式\ref{eq:singular}展示了计算左奇异向量$\tilde{G}^t$的主要过程，其中\(H^t = ({G_{i_0}^t}, {G_{i_1}^t}, \ldots, {G_{i_n}^t}) \in \mathbb{R}^{m \times n}\)为该簇节点的低频向量堆叠而成的矩阵，其中每一列代表一个节点的低频向量，$\lambda_{max}^t$与$xi_{max}^t$分别对应了矩阵$\hat{H}^t \gets (H^t)^{T} H^t$的最大特征值及其特征向量。通过这种方式，我们有效地提取了反映良性节点全局更新在频域上的主要特征，并将$\tilde{G}^t$作为“干净成分”，为后续恶意节点检测提供基准依据。
-Equation \ref{eq:singular} illustrates the main process of computing the left singular vector $\tilde{G}^t$, where \(H^t = ({G_{i_0}^t}, {G_{i_1}^t}, \ldots, {G_{i_n}^t}) \in \mathbb{R}^{m \times n}\) is a matrix formed by stacking the low-frequency vectors of nodes in the cluster, with each column representing a node's low-frequency vector.
-$\lambda_{max}^t$ and $\xi_{max}^t$ correspond to the largest eigenvalue and its eigenvector of the matrix $\hat{H}^t \gets (H^t)^{T} H^t$, respectively.
-In this way, we effectively extract the main features that reflect the global updates of benign nodes in the frequency domain, and $\tilde{G}^t$ is used as the clean ingredient for subsequent malicious node detection.
+Equation \ref{eq:singular} illustrates the main process of computing the left singular vector $\tilde{G}^t$.
+$\lambda^t_{max}$ and $\xi^t_{max}$ correspond to the largest eigenvalue and its eigenvector of the matrix $\hat{H}^t = (H^t)^{T} H^t$, respectively.
+In this way, we effectively extract the principal component that reflect the updates of benign nodes in the frequency domain, so $\tilde{G}^t$ can be used as the clean ingredient for subsequent malicious node detection.
 
 \subsubsection{Chi-square distance calculation}
-% 我们利用每个节点的低频向量与“干净成分”之间的差异度来作为衡量恶意节点和良性节点的依据。对于每个节点的低频向量 \(G_i^t\) 以及上一步中求得的“干净成分” \(\tilde{G}^t\)，通过卡方距离来计算两者之间的差异度，得到距离差异集合$S^t = Chi^t_i, Chi^t_2, \ldots, Chi^t_N$。卡方距离的计算公式为：
-We use the divergence between each node's low-frequency vector and the clean ingredient as a basis for distinguishing between malicious and benign nodes.
-For each node's low-frequency vector \(G_i^t\) and the clean ingredient \(\tilde{G}^t\) obtained in the previous step, we calculate their divergence using the Chi-square distance, resulting in a set of distance differences \(S^t = \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}\).
-The formula for the Chi-square distance is expressed as:
+% 我们利用每个节点的低频向量与“干净成分”之间的差异度来作为衡量恶意节点和良性节点的依据。对于每个节点的低频向量 \(G_i^t\) 以及上一步中求得的“干净成分” \(\tilde{G}^t\)，通过卡方距离来计算两者之间的差异度，得到距离差异集合$S^t = Chi^t_i, Chi^t_2, \ldots, Chi^t_N$。卡方距离的计算过程为：
+We use the divergence between each node's low-frequency vector and the clean ingredient as a measureto distinguish between malicious and benign nodes.
+For each  low-frequency vector \(G_i^t\) and the clean ingredient \(\tilde{G}^t\) we calculate their divergence using the Chi-square distance, yielding \(S^t = \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}\).
+The calculation process for the Chi-square distance is:
 
@@
 % 其中 \(m\) 是低频向量的维度，\(\epsilon\) 是一个小的常数，用于避免分母为零。相比于传统的欧氏距离，卡方距离根据两个向量对应分量的大小进行加权，使得特征值较大的部分对距离的影响更大，从而能够更准确地反映低频向量中重要特征之间的差异，同时忽略不重要的噪声成分。
-where \(m\) is the dimension of the low-frequency vector, and \(\epsilon\) is a small constant to avoid division by zero.
+where \(G_i^t[k]\) denotes the k-th element of vector \(G_i\) and \(\epsilon\) is a small constant to avoid division by zero.
 Compared to the traditional Euclidean distance, the Chi-square distance weights according to the magnitude of the corresponding components of the two vectors, making the influence of components with larger feature values more significant on the distance.
@@
 
+% 为什么要用卡方距离，不用欧式距离？实验论证？
+
 \subsubsection{Single-round malicious behavior perception}
-% 为了准确地识别恶意节点，我们利用良性节点的更新与干净成分的频率分布高度相似这一特性，对距离差异集合$S^t$进一步进行聚类分析。具体而言，我们采用流行的KMeans聚类算法\cite{wan2023four}对距离差异集合$S^t$进行聚类，并将类别数设置为2，因此聚类结果为两个簇\(C'_1, C'_2\)。基于在每轮训练中良性节点的数量通常多于恶意节点，以及良性节点与干净成分之间的距离差异通常更小，我们将 \(C'_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)。对于另一簇\(C'_k\)（\(k \neq {max}\)），则将其中所有节点标记为恶意节点，记作\(U_{mal}\)。
-To accurately identify malicious nodes, we leverage the fact that the updates of benign nodes exhibit a high degree of similarity in frequency distribution with the clean component.
-We conduct a further clustering analysis on the set of distance differences \(S^t\).
-Specifically, we employ the popular KMeans\cite{wan2023four} clustering algorithm to cluster the set \(S^t\), setting the number of clusters to 2.
-Consequently, the clustering algorithm produce two clusters, \(C'_1, C'_2\).
-Based on the observation that in each round of training, the number of benign nodes is typically greater than that of malicious nodes, and the distance differences between benign nodes and the clean component are generally smaller, we label all nodes in \(C'_{max}\) as benign nodes, denoted by \(U_{nor}\).
-For the other cluster \(C'_k\) (\(k \neq {max}\)), all nodes within it are labeled as malicious nodes, denoted by \(U_{mal}\).
+% 为了准确地识别恶意节点，我们利用良性节点的低频成分与干净成分之间的差异度相比于恶意节点与干净成分之间更为相似这一特性，对差异集合$S^t$进一步进行聚类分析。具体而言，我们采用流行的KMeans聚类算法\cite{wan2023four}对距离差异集合$S^t$进行聚类，并将类别数设置为2，得到聚类\(C'_1, C'_2\)，将用户数量较大的簇\(C'_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)，将另一簇\(C'_k\) \(k \neq {max}\)中的所有节点标记为恶意节点，记作\(U_{mal}\)。
+To accurately identify malicious nodes, we leverage the characteristic that the divergence between benign nodes' low-frequency components and the clean ingredient is more similar compared to that of malicious nodes.
+Based on this, we further perform cluster analysis on the divergence set \(S^t\).
+Specifically, we employ the popular clustering algorithm KMeans \cite{wan2023four} to \(S^t\), setting the number of clusters to 2, yielding two clusters \(C'_1, C'_2\).
+Based on the assumption before,  we label all nodes in the cluster with the larger number of nodes \(C'_{max}\) as benign nodes, denoted by \(U_{nor}\).
+while all nodes in the other cluster \(C'_k\) (\(k \neq {max}\)), are labeled as malicious nodes, denoted as \(U_{mal}\).
 
@@
 Algorithm \ref{alg:malicious-node-detection} outlines the overall process of Instantaneous Attack Behavior Perception. 
-% Lines 3-6 represent the computation process of frequency transformation, lines 7-12 represent the computation process of the clean component $\tilde{G}^t$, lines 13-16 represent the calculation of the Chi-square divergence between each user and the clean component, and finally, lines 17-18 represent the computation process of malicious user detection using the KMeans clustering algorithm.
-Lines 3-6 describe the computation process of frequency transformation, lines 7-12 detail the computation of the clean component $\tilde{G}^t$, lines 13-16 cover the calculation of the Chi-square divergence between each user and the clean component, and finally, lines 17-18 outline the computation process of malicious user detection using the KMeans clustering algorithm.
+Lines 3-6 describe the computation process of frequency domain transformation, lines 7-12 detail the extraction process of clean component, lines 13-16 cover the calculation of the Chi-square divergence between each update and the clean ingredient, and finally, lines 17-18 outline the process of single-round malicious behavior perception using KMeans.
 
@@
 \begin{algorithmic}[1]
-\State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each node update; $N$ is the number of the nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from nodes during the $t$-th round; $m$ is the length of low-frequency components}
+\State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each update; $N$ is the number of nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from robot nodes during the $t$-th round; $m$ is the length of low-frequency components}
 \State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
@@
 % \State Step 1: Frequency Domain Transformation
-\For {$R_i \in (R_1, \ldots, R_N)$}
-    \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
-    \State $G_i^t \gets Trunc(DCT(\frac{\triangledown \theta_i^t}{{\|\triangledown \theta_i^t\|}_2})), m)$ \Comment{Compute DCT and retain only the top $m$ low-frequency components}
+\For {$R_i \in \textcolor{red}{\{R_1, \ldots, R_N\}}$}
+    \State \textcolor{red}{$G_i^t \gets Trunc(DCT(Flatten(\triangledown \theta_i^t))), m)$}
 \EndFor
@@
 % \State Step 2: Clean Ingredient Extraction
-\State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering (\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t)$ \Comment{$\kappa$ denotes the number of clusters}
-\State $ C_{max} \gets \underset{C_i}{\arg\max} \, |C_i|, \quad i = 1, 2, \ldots, \kappa $ \Comment{$|C_i|$ denotes the number of nodes in cluster $C_i$}
-\State $H^t \gets (G_0^t, G_1^t, \ldots, G_{n}^t) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $\quad R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C_{max}$.}
+\State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering\textcolor{red}{ (G_0^t, G_1^t, \ldots, G_N^t)}$ \Comment{$\kappa$ denotes the number of clusters}
+\State \textcolor{red}{$ C^t_{max} \gets \underset{C^t_j}{\arg\max} \, |C^t_j|$ \Comment{$|C^t_j|$ denotes the number of nodes in cluster $C^t_j$, $j = 1, 2, \ldots, \kappa $}}
+\State $H^t \gets (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C^t_{max}$.}
 
 \State $\hat{H}^t \gets (H^t)^{T} H^t$
-\State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
+\State $\lambda_{max}^t, \xi_{max}^t \gets eig(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
 \State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
@@
 % \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
-\For {$R_i \in (R_1, \ldots, R_N)$}
-    \State ${Chi}_i^2 \gets \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}$
+\For {$R_i \in \textcolor{red}{\{R_1, \ldots, R_N\}}$}
+    \State ${Chi_i^t}^2 \gets \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}$
 \EndFor
-\State $S \gets \{Chi_1, Chi_2, \ldots, Chi_n\}$ \Comment{The Distance differences calculated by Chi-square distance.}
+\State \textcolor{red}{$S^t \gets \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}$} \Comment{The Distance differences calculated by Chi-square distance.}
 
@@
 % \State Step 4: Single-round malicious behavior perception
-\State $\{C_1, C_2\} \gets KMeans(S, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
-\State $U_{nor} \gets C_{\text{max}}$, $U_{mal} \gets \{C_i \, | \, i \neq \text{max}\}$
+\State $\textcolor{red}{\{{C^t_1}', {C^t_2}'\}} \gets KMeans(S^t, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
+\State \textcolor{red}{$U_{nor} \gets C'_{max}$, $U_{mal} \gets \{C'_i \, | \, i \neq max\}$}
 
@@
 Table \ref{tab:detect} provides a detailed quantitative analysis of the classification metrics for the four defense mechanisms against different strategies.
-It is clear that SecFFT not only consistently preserves its strong backdoor attack mitigation capability but also achieves the best detection accuracy, with significantly reduced false positive rates, ensuring reliable and robust performance.
+It is clear that SecFFT not only consistently preserves its strong backdoor attack mitigation capability but also achieves the best detection accuracy, with significantly reduced false positive rates, ensuring reliable and robust performance.\textcolor{red}{ "Acc" refers to accuracy, which measures the proportion of correct predictions; "Rec" stands for recall, representing the model's ability to correctly identify positive instances; "FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; "FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; "AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and "MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}
 

### 2024-10-24 response.tex
C:\Users\LetMeFly\Desktop\大语言模型\Codes\paper
Signed-off-by: LetMeFly666 <814114971@qq.com>
response: response until 2024.10.22 19:41

@@
 % 我将每次给你一个审稿意见，请你对于该审稿意见写一个回复（回复要包括中文版本和英文版本）。回复要展现自己良好的态度，越详细越好。
-你了解司法人工智能吗？请解
+% 你了解司法人工智能吗？请解释之。
 
@@
 
-%========================================================
-\rcomment{
-\color{red} The paper may benefit from providing an explicit explanation of the relationship between the community-oriented framework and the significance of improving efficiency in heterogeneous scenarios.
-Clarifying this connection would contribute to a more comprehensive understanding of the proposed methodologies.
-}
-
-% 问题：需要详细阐释“社区导向框架”与"异质性情景下提高效率的意义“”之间的关系。澄清这种联系将有助于更全面地了解所提议的方法。
-%========================================================
-
-% 改法:暂时没想法，这个待定，先不用改。大家有想法了也可以跟我讨论
-
-%感谢您的建议。为了更好地表达“Community-oriented framework”对提高异构场景下效果的关系，我们做出了如下修改：
-
-%在异构场景下，在同一轮次更新中，异构的设备提交的梯度更新方向可能差异较大，设备间更新存在拮抗，导致全局模型无法达到最优解（引用CFL）。在本文第x章的公式xxx
-
-%，第一个公式表示全局模型已经到达驻点，各个设备的更新累加后得到的全局更新为零。然而，第二个公式体现了对于单个设备，它的本地模型仍然有更新。因此，在这种异构的场景下，单个设备的最优解与全局最优解差别较大。社区化框架将更新方向相近的设备划分到同一个社区中，使得社区的全局最优解与社区内设备的最优解之间的差距限缩在一定范围内，提高模型在本地设备的表现。
-
-%对于隐私框架，在差分隐私中，敏感度与所需添加的噪声量正相关:
-
-%对于敏感度而言，不同设备集合对应的敏感度差异较大，如图所示
-
-%经划分社区后，同一社区的设备梯度更新更加集中，敏感度较低，所需添加的差分隐私噪声方差就更小。对于社区划分的条件，由于社区划分时要求了单个设备的梯度更新范数的最大值，即xxx，因此，在CFL场景下的差分隐私噪声，其噪声量取决于划分社区时设置的超参数，因此所添加的差分隐私噪声可以根据CFL的设置控制在一定范围之内。
-
-%为了使得文章更易懂，我们在正文中添加了如下内容：
-
-\textbf{Response:} Thank you for your suggestions. The community-oriented framework can improve both convergence efficiency and privacy efficiency.
-
-\textbf{In improving convergence efficiency:}In heterogeneous scenarios, during the same round of updates, the gradient update directions submitted by heterogeneous devices may differ significantly, leading to conflicts between device updates, which prevents the global model from reaching the optimal solution.
-We explained this conclusion in Section VI:
-
-\color{blue}
-\begin{equation}\label{eq:3conditions-og}
-    \left\{
-    \begin{array}{rcr}
-    \frac{N}{K|D|} \sum_{P_i\in \mathcal{P}_t} |D_i| \cdot ||\Delta w^{i}_{t} || & <\beta,\\
-    \max_{P_i\in \mathcal{P}_t}||\Delta w^{i}_t|| &>\theta,\\
-    \alpha^{min}_{intra} - \alpha^{max}_{cross} & > 0
-    %\underset{P_{h},P_{k}\in C_m \subseteq \mathcal{C}}{\min } \alpha^{h, k}_t-\underset{P_{i} \in C_{1}, P_{j} \in C_{2}}{ \max} \alpha^{{i}, {j}}_t & >0,
-    \end{array}
-    \right.
-\end{equation}
-where $\theta>\beta>0$ are predefined constant thresholds, $\alpha^{min}_{intra}$ and  $\alpha^{max}_{cross}$ are the minimum internal cosine similarity and the maximum cosine similarity cross communities respectively\color{black}.
-
-The first formula indicates that the global model has reached a saddle point, where the aggregate updates from all devices approximate a global update close to zero.
-However, the second formula demonstrates that for individual devices, their local models still experience updates.
-Consequently, in this heterogeneous scenario, there is a significant disparity between the optimal solution of a single device and the global optimal solution.
-The community-based framework categorizes devices with similar update directions into the same community, thereby constraining the discrepancy between the community's global optimal solution and the optimal solutions of the devices within that community within a certain range, which enhances the model's performance on local devices.
-
-\textbf{In improving privacy efficiency:} In differential privacy, the sensitivity is positively correlated to the amount of noise that needs to be added.
-To guarantee $(\epsilon_i,\delta_i)-DP$, the standard deviation of noises $\sigma_i$ from Gaussian mechanism should satisfy:
-
-\begin{equation}
-    \sigma_i = \frac{Sen\sqrt{2qTln(1/\delta_i)}}{\epsilon_i},
-\end{equation}
-
-where $Sen$ is the sensitivity of the local training process.
-
-However, after community division, the gradient updates of devices within the same community are more concentrated, with lower sensitivity, resulting in smaller variance of the differential privacy noise that needs to be added.
-Regarding the conditions for community division, since the maximum norm of the gradient updates of individual devices is required during the division, i.e., $\theta$, therefore, in the CFL scenario, the amount of differential privacy noise depends on the hyperparameters set during community division.
-Thus, the differential privacy noise added can be controlled within a certain range according to the CFL settings.
-
-In order to make the article more understandable, we have added the following content to the main text:
-
-\color{blue}
-It is evident that the hyperparameters $\theta$ and $\gamma$ in community division determine the maximum sensitivity within the community, which in turn determines the amount of differential privacy noise required to be added.
-\color{black}
-
 \newpage
@@
 %=================================
+% 我给你一些审稿意见，请你按照格式返回latex源码：
+
+% ```
+% \section{Responses to the Comments from Reviewer 2}
+
+% % comment6
+% \rcomment{
+% \color{red} 审稿意见6
+% }
+
+% Thank you for your suggestion.
+
+% % comment7
+% %...
+
+% \newpage
+% ```
 \section{Responses to the Comments from Reviewer 2}
-%=================================
-%========================================================
 
+% comment6
 \rcomment{
-\color{red} The variable f, n in line 52 on page 3 is missing a description. Similarly, multiple variables in this paper have not yet been described, so please check carefully.
+\color{red} The text in some experimental result figures is too small to be legible. Improving the clarity and resolution is recommended.
 }
-% 问题：第3页第52行中的变量f, n缺少描述。同样，本文中有多个变量尚未描述，请仔细检查。
 
-%改法 : 跟上一个审稿人第一个问题提的差不多，就是先道歉，然后好好描述下这几个变量啥意思，然后提供个参数表。
+Thank you for your suggestion.
 
-\textbf{Response:} We thank the Reviewer for the comment.
+% comment7
+\rcomment{
+\color{red} Figure 3 is not cited in the manuscript. It is suggested to reference and explain the figure in the relevant section, as its absence hinders understanding.
+}
 
-We apologize for overlooking the definition of some variables, which may have caused confusion for the readers. In response, we have supplemented the definitions of certain variables:
+% 感谢你指出这一点，我们的图3对应\ref{\section{Methodology}}部分的B部分的2)，我们只将图片放在了对应的文字介绍部分，但是并未对图片内容进行描述，甚至没有在文章中引用这段文字。现在，我们
+Thank you for pointing this out.
 
-In Section II, we have supplemented the definitions of $f$ and $n$ as follows:
+% comment8
+\rcomment{
+\color{red} The steps in the final paragraph of Section 5 do not align with Algorithm 2. Please revise for consistency.
+}
 
-\color{blue} where $n$ is the number of clients and $f$ is the number of malicious clients\color{black}
+Thank you for your suggestion.
 
-In Section II, we have supplemented the definitions of $\alpha^{min}_{intra}$ and  $\alpha^{max}_{cross}$ as follows:
+% comment9
+\rcomment{
+\color{red} Some conditions in Algorithm 2 are unclear, such as "for Client i do", "while Not Converged do", and "for Each point Oj $\neq$ Oi do". Clarification and revision are needed.
+}
 
-\color{blue}$\alpha^{min}_{intra}$ and  $\alpha^{max}_{cross}$ are the minimum internal cosine similarity and the maximum cosine similarity cross communities respectively.\color{black}
+Thank you for your suggestion.
 
-In Section VII, we have supplemented the definitions of $t$ as follows:
+% comment10
+\rcomment{
+\color{red} Section VI-C lacks quantitative analysis of the experimental results.
+The partitioning results in Fig.
+6 are hard to distinguish, and the font size is too small.
+Moreover, the four subplots lack necessary labels, and the same issues are present in Fig.
+7.
+}
 
-\color{blue}The real-time intimacy index in $t-th$ round  $\rho^{ij}_t$ between devices $P_i$ and $P_j$ is defined as:
-\color{black}
+Thank you for your suggestion.
 
-In Section VII, we have supplemented the definitions of $\mu$ as follows:
+% comment11
+\rcomment{
+\color{red} Some of the English expressions are difficult to understand. Improving the overall quality of writing is recommended.
+}
 
-\color{blue}$\mu> 0$ represents the impact of interaction time intervals on credibility.\color{black}
+Thank you for your suggestion.
 
-Additionally, to make the variables more easily searchable, we have added a parameter table on page four. We have provided this table in Reviewer 1's Comment 1.
-
-%========================================================
-\rcomment{
-\color{red} Please specifically analyze the advantages of their privacy amplification mechanism.
-The authors' privacy amplification is achieved by limiting the sensitivity so that the epsilon is smaller at the same noise scale.
-Although this is not the same privacy mechanism I would expect, privacy enhancement is achieved.
-However, the authors seem to compare the effects of the different schemes only by comparing the accuracy of the experiments.
-Could the authors theoretically analyze the difference between their privacy amplification mechanism and other privacy enhancement schemes (such as DPFL as mentioned by the authors)?
-% 请具体分析其隐私放大机制的优势。作者的隐私放大是通过限制灵敏度来实现的，使得在相同的噪声尺度下，噪声放大更小。虽然这不是我所期望的相同的隐私机制，但可以实现隐私增强。然而，作者似乎只是通过比较实验的准确性来比较不同方案的效果。作者能否从理论上分析他们的隐私放大机制与其他隐私增强方案（如作者提到的DPFL）的区别？
-%改法：
-}
-% 非常感谢您的意见。
-
-\textbf{Response:} Thanks for the reviewer's valuable comment.
-
-%本文提出的隐私增强策略与Reviewer提出的联邦学习中的隐私策略不同，主要侧重于针对异构联邦学习场景下的差分隐私机制。在异构联邦学习场景，由于个体间本地模型更新的差异较大，而高斯差分隐私机制添加噪声的方差大小取决于敏感度的大小，因此，
-
-\color{black}
-
-% \textbf{Intension:}\\
-% 1.Disrupting Neural Network Performance: The primary objective of the attacker is to impair the model's performance, causing it to produce incorrect outputs on certain inputs.
-This may pose a threat to the model's reliability and security, especially in critical domains such as intrusion detection.\\
-% 2.Bypassing Security Measures: Adversarial attacks can also be used to circumvent security measures deployed with the model, such as CAPTCHA or malware detection systems.
-By targeting these security measures, attackers can gain access to restricted resources or carry out malicious activities.
-
-% \textbf{Capabilities:}\\
-% 1.Generating Adversarial Examples: Attackers can employ various techniques to create adversarial examples that closely resemble the original input but are capable of deceiving neural networks.
-These techniques include gradient-based attacks, Generative Adversarial Networks (GANs), and evolutionary algorithms, among others.\\
-% 2.White-Box and Black-Box Attacks: Attackers can conduct white-box attacks (having full knowledge of the model's structure and parameters) or black-box attacks (only knowing the model's input and output but lacking detailed information about the model).\\
-% 3.Transferability: An adversarial example may have the ability to generalize across different models, making it applicable to multiple models.
-This enables attackers to leverage the same adversarial examples in diverse environments.\\
-% 4.Imperceptibility: Adversarial examples typically require being almost imperceptible to human observation.
-This necessitates careful crafting by attackers to ensure that they are indistinguishable from the original input in terms of visual or perceptual cues.
-
-%========================================================
 \newpage
 
+\section{Responses to the Comments from Reviewer 3}
+
+% comment12
 \rcomment{
-\color{red} What is the basis of the algorithm parameter setting, such as Table I and other parameters? % 架构
+\color{red} Why does the section on "Instantaneous Attack Behavior Perception" use the chi-square distribution to calculate outlier differences instead of cosine similarity?
+The manuscript lacks an explanation for this choice.
 }
-% 算法参数设置的依据是什么，如表I等参数？
-% 本文所使用的基础模型架构及相应的超参数设置参考了如FL-WBC和SFAT等论文中的实验设置。针对不同数据集的特性，模型结构和超参数进行了调整，以适应特定任务需求。
 
-% 对于MNIST和EMNIST数据集，这些数据集包含灰度手写数字图像，输入数据尺寸为28x28，且只有一个通道。为了有效提取图像的局部特征，模型使用了两层5x5的卷积层。第一层卷积层的输入通道为1（单通道灰度图像），输出通道设置为10，能捕捉图像的边缘和基本几何结构。第二层卷积层的输入为10个特征图，输出通道为20，进一步提取更高级的特征。每一层卷积之后，使用ReLU激活函数引入非线性，并通过2x2的最大池化层减少特征图的尺寸，从而降低计算复杂度并增强模型的泛化能力。此外，使用Dropout机制（在卷积层之后和全连接层之间）防止过拟合，特别是对于相对小规模的MNIST和EMNIST数据集，Dropout可以有效抑制模型在训练数据上表现过好而在测试数据上表现欠佳的问题。
+Thank you for your suggestion.
 
-% 针对CIFAR-10和CIFAR-100数据集，这些数据集由32x32的彩色图像组成，输入为RGB三通道。因此，模型的第一层卷积层设计为接受3个输入通道，并输出6个特征图，卷积核大小同样为5x5。通过这一层卷积，模型能够提取低级的颜色和边缘特征。第二层卷积层接收6个输入特征图，输出16个特征图，这一层进一步提取中级特征，如图像的纹理和形状。每一层卷积之后同样使用ReLU激活函数和2x2最大池化层，减少特征图尺寸并保留最重要的特征信息。
+% comment13
+\rcomment{
+\color{red} The manuscript uses inconsistent figure referencing styles (e.g., "Fig. 7" vs. "Figure 6"). Please standardize the citation format.
+}
 
-% 两种模型的不同之处在于，MNIST和EMNIST数据集为单通道灰度图像，结构相对简单，因此只需要10和20个特征通道即可有效提取图像信息。而对于CIFAR-10和CIFAR-100，由于其是彩色图像，且包含更多的复杂性（如多种颜色、形状和纹理），卷积层的通道数相对增加。此外，MNIST和EMNIST中的全连接层参数为320到50，再到最终的分类输出，而在CIFAR中，由于图像尺寸稍大，全连接层从1655（400个节点）开始，逐步减少至120，再到84，最后输出类别数。对于CIFAR-10和CIFAR-100，类别数分别为10和100，因此在最后的输出层中，分类节点数量根据数据集的不同进行了调整。
+Thank you for pointing this out.
 
-% 在所有数据集中，超参数如学习率、batch size、Dropout率等也根据实验调整，以确保在不同的数据集上都能获得最优性能，确保模型在有效学习数据特征的同时具备良好的泛化能力。
+% comment14
+\rcomment{
+\color{red} Several hyperparameters are used in the experiments, but their rationale and appropriateness are not explained. Please provide a justification for their settings.
+}
 
-% FL-WBC: Enhancing Robustness against Model Poisoning Attacks in Federated Learning from a Client Perspective
-% COMBATING EXACERBATED HETEROGENEITY FOR ROBUST MODELS IN FEDERATED LEARNING
-%感谢您的提议。
-\textbf{Response:} Thanks for the reviewer's valuable comment.
+Thank you for your suggestion.
 
-The basic model architecture and corresponding hyperparameter settings used in this paper were based on experimental setups from papers such as \cite{sun2021fl}, \cite{zhu2023combating}, \cite{liang2020think}, \cite{zhu2024isfl} and \cite{zhou2022adversarial}.
-The model structure and hyperparameters were adjusted to suit the characteristics of different datasets and meet the specific task requirements.
-To effectively capture the unique features of each dataset, we designed specific model architectures as detailed below.
+% comment15
+\rcomment{
+\color{red} Why is the condition $\zeta T$ set in the optimization problem in Section V.2? Clarification is needed.
+}
 
-\textbf{CNN architecture for MNIST and EMNIST}: For the MNIST and EMNIST datasets, which consist of grayscale handwritten digit images with an input size of 28x28 and a single channel, the model uses two 5x5 convolutional layers to effectively extract local features from the images.
-The first convolutional layer has 1 input channel (for the grayscale images) and 10 output channels, capturing edges and basic geometric structures.
-The second convolutional layer takes in 10 feature maps as input and outputs 20 channels, extracting more advanced features.
-After each convolutional layer, a ReLU activation function introduces nonlinearity, and a 2x2 max-pooling layer reduces the size of the feature maps, lowering computational complexity and enhancing the model’s generalization ability.
-Additionally, a Dropout mechanism (applied after the convolutional layers and between the fully connected layers) is used to prevent overfitting.
-This is particularly effective for relatively small-scale datasets like MNIST and EMNIST, where Dropout helps mitigate the issue of the model performing too well on training data but poorly on test data.
+Thank you for your suggestion.
 
-\textbf{CNN architecture for CIFAR-10}: For the CIFAR-10 datasets, which consist of 32x32 color images, the input is RGB with three channels.
-Thus, the first convolutional layer is designed to accept 3 input channels and outputs 6 feature maps, with the same 5x5 kernel size.
-This layer extracts low-level features like colors and edges.
-The second convolutional layer takes in 6 input feature maps and outputs 16, further extracting mid-level features such as textures and shapes.
-Each convolutional layer is followed by a ReLU activation function and a 2x2 max-pooling layer to reduce the size of the feature maps while retaining the most important information.
+% comment16
+\rcomment{
+\color{red} There are numerous instances of incorrect symbol usage throughout the manuscript. A thorough review and correction are necessary.
+}
 
-\begin{figure}[tb]
-    \centering
-    \includegraphics[width=0.9\linewidth]{figures/resnet_all.png}
-    \caption{The architecture of ResNet-34}
-    \label{fig:resnet34}
-\end{figure}
-
-\textbf{ResNet34 for CIFAR-100}: For the CIFAR-100 dataset, it contains 100 classes, and each image is a 32x32x3 image.
-A simple CNN structure is not suitable, so we used the ResNet34 model as the base model for our experiments.
-As Figure \ref{fig:resnet34} depicted, ResNet34 is a convolutional neural network with 34 layers, consisting of one convolutional layer (Conv1), one max-pooling layer (Maxpool), four residual blocks (Conv1\_x, Conv2\_x, Conv3\_x, Conv4\_x), one average pooling layer (Avgpool), and one fully connected layer (FC).
-
-\textbf{Summary of differences between these models}: The key differences between the models lie in the input channels, model complexity, and number of output classes.
-For MNIST and EMNIST, the input consists of single-channel grayscale images, while for CIFAR-10 and CIFAR-100, the input consists of three-channel RGB images.
-Due to this, the first convolutional layer in the CNN models for MNIST and EMNIST has 1 input channel and outputs 10 feature maps, whereas for CIFAR-10, the first layer has 3 input channels and outputs 6 feature maps.
-Additionally, CIFAR-100 uses the more complex ResNet34 architecture, which is deeper and more capable of handling the greater complexity of color images and the larger number of output classes.
-The number of output classes also differs: MNIST, EMNIST, and CIFAR-10 each have 10 output classes, whereas CIFAR-100 has 100 output classes, necessitating a larger model and more complex feature extraction layers.
-Thus, the models are adjusted to capture the unique characteristics of the respective datasets, with simpler architectures for grayscale images and more complex architectures like ResNet34 for datasets with more classes and higher input complexity.
-
-Across all datasets, hyperparameters such as learning rate, batch size, and Dropout rate were also adjusted based on experiments to ensure optimal performance.
-This allows the model to learn the data features effectively while maintaining good generalization ability.
-
-% 为了在文章中准确表达模型选择的原因，我们进行了以下修改
-To accurately explain the reasons for model selection in the article, we have made the following modifications:
-\begin{table}[b]\scriptsize
-\setlength{\abovecaptionskip}{0cm}
-\setlength{\belowcaptionskip}{0.2cm}
-\renewcommand{\arraystretch}{1.2}
-    \caption{\centering{Neural network structures}}\label{table:NN-structure}
-\centering
-\begin{tabular}{l|l}
-\hline
-\makecell[l]{MNIST/EMNIST} & 
-\makecell[l]{
-$28^{2}\times1 \xrightarrow{Conv(f=5,s=1)} 24^{2}\times10 \xrightarrow{Pool(f=2)} $
-$12^{2}\times10  \xrightarrow{Conv(f=5,s=1)} 8^{2}\times20\xrightarrow{Pool(f=2)} $\\
-$4^{2}\times20 \xrightarrow{} 320 \xrightarrow{FC} 50 \xrightarrow{FC} 10\times1$
-}\\ 
-\hline
-
-CIFAR-10 & 
-\makecell[l]{
-$ 32^{2}\times3 \xrightarrow{Conv(f=5,s=1)} 28^{2}\times6 \xrightarrow{Pool(f=2,s=2)} $
-$14^{2}\times6 \xrightarrow{Conv(f=5,s=1)} 10^{2}\times16 \xrightarrow{Pool(f=2,s=2)}$\\
-$5^{2}\times16 \xrightarrow{} 400 \xrightarrow{FC} 120 \xrightarrow{FC} 84 \xrightarrow{FC} 10\times1$
-}\\ 
-\hline
-
-\textcolor{blue}{CIFAR-100}& 
-\makecell[l]{ \color{blue}
-$32^{2}\times3 \xrightarrow{Conv1(f=7,s=2)} 16^{2}\times64 \xrightarrow{Maxpool(f=3,s=2)} $
-$8^{2}\times64 \xrightarrow{Conv2\_x} 8^{2}\times64 \xrightarrow{Conv3\_x}$\\ \color{blue}
-$4^{2}\times128 \xrightarrow{Conv4\_x} 2^{2}\times256 \xrightarrow{Conv5\_x}$
-$1^{2}\times512 \xrightarrow{Avgpool} 1^{2}\times512 \xrightarrow{} 512 \xrightarrow{FC} 100 \times 1$ \color{black}
-}
-\\ \hline
-\end{tabular}
-\end{table}
-
-\color{blue}Based on existing researches such as \cite{sun2021fl}, \cite{zhu2023combating}, \cite{liang2020think}, \cite{zhu2024isfl} and \cite{zhou2022adversarial}, we construct different convolutional neural network (CNN) models to cater above image identification learning tasks.
-The key differences between the models are the input channels (single-channel grayscale for MNIST/EMNIST vs.
-three-channel RGB for CIFAR-10/CIFAR-100), model complexity (simpler CNNs for MNIST/EMNIST/CIFAR-10 vs.
-the deeper ResNet34 for CIFAR-100), and the number of output classes (10 for MNIST, EMNIST, and CIFAR-10 vs.
-100 for CIFAR-100), with adjustments made to suit the specific characteristics and complexity of each dataset.
-\color{black}
-
-\color{black}
-%========================================================
-\rcomment{
-\color{red} The authors conducted experiments on three public data, MNIST, EMNIST, and CIFAR, and achieved good experimental results.
-However, the article does not specify whether CIFAR-10 or CIFAR-100 is used, although it can be known that the authors used CIFAR-10 by observing Table I, it is better to describe it clearly in the article.
-What will be the effect of CIFAR-100?
-Is it possible to simply test it?
-}
-% 作者在MNIST、EMNIST和CIFAR三个公共数据上进行了实验，取得了良好的实验结果。但文中并未明确使用的是CIFAR-10还是CIFAR-100，虽然通过观察表I可知作者使用的是CIFAR-10，但还是在文中描述清楚为好。CIFAR-100的效果如何？有没有可能简单地测试一下？
-\textbf{Response:} Thanks for the reviewer's valuable comment.
-
-%针对cifar-100数据集，为了验证cos-hfl在隐私增强上面的表现，我们额外增加了在正常、异构、不诚实用户三种场景下的实验，其具体实验结果如图1，图2，图3所示。同时为了验证cos-hfl在包含噪声和异构环境下的表现，我们也额外进行了相应的实验，具体实验结果如图3，图4所示。
-To evaluate the privacy-amplification performance of Cos-HFL on the CIFAR-100 dataset, we additionally conducted experiments under three different scenarios: normal, heterogeneous, and dishonesty.
-The specific experimental results are shown in Figures \ref{result1:CIFAR100-normal-acc}, \ref{result1:CIFAR100-hetero-acc}, and \ref{result1:CIFAR100-dishonest-acc}.
-Additionally, to verify the performance of Cos-HFL in noisy \& heterogeneous environments, we also conducted corresponding experiments, with the specific results displayed in Figures \ref{result2:CIFAR100-hetero-norm} and \ref{result2:CIFAR100-hetero-acc}.
-
-For CIFAR-100, the dataset size and the number of categories are much larger than those of CIFAR-10, MNIST, and EMNIST.
-Therefore, we used ResNet34 for our experiments.
-By observing the experimental results, we found that our method is less affected by noise in CIFAR-100.
-In particular, for dishonest users, it is evident that the accuracy of NbAFL and DPFL is significantly lower than that of CoS-HFL.
-Furthermore, for CFL, due to the noise affecting the clustering judgment, we observed that CFL falls into a local optimum, resulting in a lower final accuracy compared to the correctly clustered CoS-HFL.
-% 对于CIFAR100来说，数据集大小与类型数量远大于CIFAR-10与MNIST、EMNIST，因此，我们采用了ResNet34进行实验。通过观察实验图发现，在CIFAR-100中，我们的方法受噪声影响较小。尤其是对于不诚实的用户，可以发现NbAFL与DPFL的Accuracy明显低于CoS-HFL。此外，对于CFL，由于噪声影响了分簇的判断，可以发现CFL陷入了局部最优解，导致收敛后的准确率低于分簇正确的CoS-HFL。
-
-% 同时，我们在文章实验部分进行了以下修改，增加了对cifar-100数据集实验结果的描述：
-At the same time, we made the following modifications in the experimental section of the article, adding a description of the experimental results on the CIFAR-100 dataset:
-
-\color{blue}
-Firstly, we demonstrate the accuracy in the normal situation without heterogeneous or dishonest participants in Figures 5, 8 and 11 (MNIST/CIFAR-10/CIFAR-100).
-Based on the results, we can see that private obfuscation causes a certain amount of accuracy decline in the beginning.
-Although, because CoS-HFL injects less noise than the other two peers, the purple line gradually outperforms green and red ones over time.
-
-Secondly, Figures 6, 9 and 12 show the results under heterogeneous environments, where we replace 5 normal participants with 5 heterogeneous ones.
-We can tell that CoS-HFL still achieves better performance from the figures within merely 200 slots.
-With a greater heterogeneity degree and a much larger duration in real-world distributed learning scenarios, the amplification effect will be more significant.
-
-Besides, we also consider the impact of dishonest devices.
-In like manner, we let 10 devices dishonestly exaggerate the data variances for additional privacy benefits, while the other 90 participants remain unchanged.
-As shown in Figures 7, 10 and 13, the orange lines are almost unaffected, as FL injects no noise.
-Meanwhile, due to the unnecessarily overlarge sensitivity caused by exaggerated data variances, both DPFL and NbAFL suffer great performance degradation.
-By contrast, with the help of privacy amplification, CoS-HFL limits the noise scale to some extent and obtains better accuracy.
-
-In HFL scenarios, dynamic and varied data characteristics or differentiated learning tasks present significant obstacles to model convergence and accuracy. 
-Worse still, existing security designs such as data obfuscation and DP noise injection may further complicate the situation by introducing huge variance into weight updates of HFL model parameters. 
-To verify the availability of CoS-HFL, we first deploy two different multitask scenarios, and assume that all devices can perturb local updates before uplink transmission, to simulate the heterogeneity and dynamic randomness, respectively.
-Then, we compare the model accuracy and max-norm/$Q$ of CoS-HFL with CFL and DPFL.
-
-First, for EMNIST, as shown in Figure 1 (b), we rotate the images ($0^{\circ},90^{\circ},180^{\circ},270^{\circ}$) to create four classes of heterogeneous participants (25 devices per class).
-Based on Figure 14, our method can correctly partition the device set (blue vertical dashed lines) into different communities, and eventually outperform both CFL and DPFL after correct partition.
-Hence, as shown in Figure 15, CoS-HFL minimizes the $Q$ over time, while the other two methods' max norms remain high.
-
-%\begin{comment}%13注释（6）-2
-Then, for CIFAR-10 and CIFAR-100, as shown in Figure 1 (a), we create two classes of heterogeneous participants (50 devices per class) by extracting color features or profile features. 
-Similar to Figures 14, 15 and 18, based on Figures 16, 17 and 19, CoS-HFL also divides participants to correct communities and converges to higher accuracy of the global model.
-Especially for CIFAR-100, since the ResNet34 model it uses has significantly more parameters compared to CNN, the impact of noise increases dramatically when noise is added.
-This can mislead the clustering of CFL, resulting in a noticeable decrease in the accuracy of CFL.
-
-\color{black}
-%\end{comment}%13注释（6）-2
-
-\begin{figure}[tb]
-	\captionsetup{font=tiny} % 调整图片字幕的大小
-	\begin{minipage}[!t]{0.333\linewidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{./figures/cifar100_acc_norm.pdf}
-		\vspace{-0.5em}
-		\caption{{\color{red}Accuracy vs normality on CIFAR-100}}
-		\label{result1:CIFAR100-normal-acc}
-	\end{minipage}%
-	\begin{minipage}[!t]{0.333\linewidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{./figures/cifar100_acc_heterog.pdf}
-		\vspace{-0.5em}
-		\caption{\textcolor{red}{Accuracy vs heterogeneity on CIFAR-100}}
-		\label{result1:CIFAR100-hetero-acc}
-	\end{minipage}
-	\begin{minipage}[!t]{0.333\linewidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{./figures/cifar100_acc_dishonest.pdf}
-		\vspace{-0.5em}
-		\caption{\textcolor{red}{Accuracy vs dishonesty on CIFAR-100}}
-		\label{result1:CIFAR100-dishonest-acc}
-	\end{minipage}
-	\vspace{-0.3cm}
-\end{figure}
-
-\begin{figure}[tb]
-    \centering
-    \begin{subfigure}[t]{0.45\textwidth} % 调整第一张图片的宽度
-        \centering
-        \includegraphics[width=\textwidth]{./figures/cifar100_acc_2.pdf}
-        \caption{\textcolor{red}{Accuracy on CIFAR-100}} % 替换序号为(b)
-        \label{result2:CIFAR100-hetero-norm}
-    \end{subfigure}%
-    \hfill
-    \begin{subfigure}[t]{0.48\textwidth} % 调大第二张图片的宽度
-        \centering
-        \includegraphics[width=\textwidth]{./figures/cifar100_dw.pdf}
-        \caption{\textcolor{red}{Max-norm/$Q$ on CIFAR-100}} % 替换序号为(a)
-        \label{result2:CIFAR100-hetero-acc}
-    \end{subfigure}
-    \vspace{-0.3cm}
-    \caption{Results of Accuracy(a) and Max-norm/$Q$(b) on CIFAR-100}
-    \label{fig:cifar100-comparison}
-\end{figure}
-
-%========================================================
-\rcomment{
-\color{red} The authors do not seem to have considered the issue of communication overhead in federated learning, and I would ask the authors to think hard about whether this question needs to be answered.
-}
-% 作者似乎没有考虑到联邦学习中的通信开销问题，我想请作者认真思考这个问题是否需要回答。
-% 感谢您的comment。根据您的提问，我们认真考虑了CoS-HFL的开销问题。在联邦学习中，客户端通常作为计算与通信能力较差的计算节点，主要有通信开销与计算开销。在通信层面，通常假设联邦学习的服务器拥有丰富的通信资源，故通常不考虑服务器的通信开销。因此，联邦学习的通信开销取决于模型的参数量、客户端与服务器通信轮次、额外的传递信息。对于CoS-HFL，假设深度学习模型为$\omega$,其参数量为$\|\omega\|$，对于单个通信轮次，其通信量相较于传统的联邦学习只增加了部分非超参数的传递，如$\mathbf{\lambda},\theta, \epsilon,\delta$等，这些参数相较于深度学习模型的大小可以忽略不记。因此，在单个轮次上，CoS-HFL的通信开销与传统的CFL并无明显差异。
-
-%对于模型的收敛速率，通过观察实验数据，CoS-HFL的收敛速率与DPFL、FedAvg、CFL并无明显区别。同时，经过证明[]，FedAvg的收敛速率为$O(\frac{1}{\sqrt{TE})$，其中$T$为全局训练轮次，$E$为客户端本地的迭代次数。同时，CoS-HFL作为一种基于CFL的改进，收敛速度近似于$O(\frac{\sqrt{TME}})$，其中$M$为聚类个数。然而在实践中，聚类个数通常较低，可视作常数。因此，CFL与FedAvg收敛速度并无明显差异。
-
-%综上所述，CoS-HFL与传统的FedAvg在通信开销上并无实质性差异，为
-
-\textbf{Response:}Thank you for your comment!
-Based on your question, we have carefully considered the overhead of CoS-HFL in federated learning.
-In federated learning, clients typically serve as nodes with limited computational and communication capabilities, so the overhead mainly includes communication and computational costs.
-
-\textbf{Communication overhead}: It is generally assumed that the server in federated learning has abundant communication resources, so the server's communication cost is not a primary concern.
-The communication overhead mainly depends on the following factors:
-
-\textit{The number of model parameters:} The parameters that need to be transmitted in federated learning.
-
-\textit{The number of communication rounds between clients and the server:} The frequency of communication determines the total communication burden.
-Additional transmitted information: For example, extra parameters or auxiliary data in meta-learning.
-For CoS-HFL, assuming the deep learning model is denoted as $\omega$, with parameter size $|\omega|$, in a single communication round, the communication load only slightly increases compared to traditional federated learning due to the transmission of non-hyperparameters like $\mathbf{\lambda}$, $\theta$, $\epsilon$, and $\delta$.
-Since the size of these parameters is negligible compared to the deep learning model, the communication overhead in a single round of CoS-HFL is not significantly different from that of traditional federated learning.
-
-\begin{table}[t]\scriptsize
-\setlength{\abovecaptionskip}{0cm}
-\setlength{\belowcaptionskip}{0.2cm}
-\renewcommand{\arraystretch}{1.2}
-    \caption{\centering{Communication convergence of algorithms}}\label{table:Convergence}
-\centering
-\begin{tabular}{l|l}
-\hline
-\makecell[l]{FedAvg\cite{9377960}} & 
-\makecell[l]{$\frac{1}{\sqrt{TE}}$
-}\\ 
-\hline
-
-CFL\cite{CoRR} & 
-\makecell[l]{$\frac{1}{\sqrt{TME}}$
-}\\ 
-\hline
-
-PSASGD\cite{wang2021cooperative} & 
-\makecell[l]{ $\frac{1}{\sqrt{TE}}$
-}
-\\ \hline
-CoS-HFL & 
-\makecell[l]{ $\frac{1}{\sqrt{TME}}$
-}
-\end{tabular}
-\end{table}
-
-Regarding the convergence rate of the models, through observing experimental data, we found that the convergence rate of CoS-HFL shows no significant difference compared to classic federated learning algorithms such as DPFL, FedAvg, and CFL.
-At the same time, research has proven [citation needed] that the convergence rate of FedAvg is $O(\frac{1}{\sqrt{TE}})$\cite{CoRR}, where $T$ represents the number of global training rounds, and $E$ is the number of local iterations on the client side.
-This suggests that FedAvg achieves a good balance between global and local computations, especially when an increase in local iterations can accelerate the model’s convergence.
-
-\textbf{Computation overhead:}
-As an improvement based on CFL, CoS-HFL’s convergence rate is approximately $O(\frac{1}{\sqrt{TME}})$\cite{9377960}, where $M$ is the number of clusters.
-Although this formula indicates that increasing $M$ could accelerate convergence, in practice, $M$ is usually small and can be treated as a constant.
-Therefore, in most cases, the convergence rates of CoS-HFL and CFL are similar, and there is no significant difference compared to FedAvg.
-
-What's more, considering the computational cost, our method includes uplink privacy calculation, auxiliary downlink privacy calculation, community construction and credit calculation.
-As the model's parameter size is $S$, clients number is $N$, the time complexity of each step is as follows:
-\begin{itemize}
-    \item Uplink privacy: $O(SN)$
-    \item Auxiliary downlink privacy: $O(SN)$
-    \item Community construction: $O(SN^2)$
-    \item Credit calculation: $O(SN^2)$
-\end{itemize}
-
-For the whole workflow, the time complexity is $O(SN^2)$. Our method differs from traditional methods\cite{9377960} in terms of time complexity by only a constant factor.
-In this article, we mainly focus on the privacy and security of federated learning, and for the next step, we will pay attention to the communication cost for the integration of our work.
-Our modifications are as follows:
-
-\color{blue}
-Let the number of model parameters be denoted as $S$.
-In a single round, our method shows no significant difference compared to traditional federated learning, both having a complexity of O($SK$).
-Furthermore, in terms of convergence rounds, as analyzed in \cite{CoRR} and \cite{9377960}, our method makes modifications to the clustering conditions compared to \cite{9377960}, yet only introduces a constant factor's change in communication efficiency.
-Additionally, the time complexity of the proposed method is the same as CFL, both being $O(SN^2)$, which provides security guarantees for federated learning without imposing an unacceptable computational burden.
-\color{black}
-% \begin{assumption}
-% Local gradient $\Delta \mathcal{L}(w_t^i)$ is Lipschitz continuous with respect to $w$, i.e., $\|\Delta \mathcal{L}(w_t^i)-\Delta \mathcal{L}(w_{t+1}^i)\|\leq L\|w_{t}^i-w_{t+1}^i\|$, where $L$ is a positive constant.
-% \end{assumption}
-% \begin{assumption}
-%     Local loss function $\mathcal{L}(w)$ is strongly convex with respect to $w$, i.e., $\mathcal{L}(w_t^i)\geq \mathcal{L}(w_{t+1}^i)+(w-w^{t+1})^T\Delta \mathcal{L}(w_t^i)+(\mu/2)\|w_t^i-w^{i}_{t+1}\|^2$,
-% \end{assumption}
-% \begin{assumption}
-%     Training loss of cluster $s$ is defined as $\mathcal{L}(w_t^s)$ which is twice-continuously differentiable, i.e., $\mu I \leq \nabla^2\mathcal{L_t^s}$ satisfies $\zeta_1^2 \leq \|\nabla \mathcal{L}(w_t^s)\|^2\leq \zeta^2_2$ with $\zeta_1,\zeta_2>0$.
-% \end{assumption}
-
-%对于CoS_HFL,我们有如下约束：
-% Due to weight clipping, we have:
-% \begin{equation}
-%     \begin{aligned}
-% 		||\eta^i_{t}\nabla_{w}  \mathcal{L}_{i}(w, \zeta^{i,\prime}_{k})|| \leq \max||\Delta w^i_t||\color{black}= \xi_i. %\forall j,
-% 		\end{aligned}
-% \end{equation}
-
-% So that 
-% \begin{equation}
-%     \| \nabla_{w}  \mathcal{L}_{i}(w, \zeta^{i,\prime}_{k})\| \leq \frac{\xi_i}{\eta_t^i}
-% \end{equation}
-
-% By L-smoothness of the loss function $\mathcal{L}$, we have
-% \begin{equation}
-% \begin{aligned}
-%     \mathbb{E} [\mathcal{L}(w_{t+1}^i)-\mathcal{L}(w_t^i)]\\
-%     \leq \mathbb{E}<\nabla\mathcal{L}(w_{t}^i),w_{t+1}^i-w_{t}^i >+\frac{L}{2}\mathbb{E}\|\|
-% \end{aligned}
-% \end{equation}
+Thank you for your suggestion.
 
 \newpage
-% \begin{comment}
 
-% \bibliographystyle{apalike}
-% \bibliography{reference}
+\section{Responses to the Comments from Reviewer 4}
+
+% comment17
+\rcomment{
+\color{red} The concept of intent recognition is a key innovation in this manuscript’s.
+However, the definition and construction of attacker intent are vague and need further elaboration to help readers better understand the core idea.
+}
+
+Thank you for your suggestion.
+
+% comment18
+\rcomment{
+\color{red} The description of the experiments is unclear.
+The titles and text in the figures are too small, making them difficult to read.
+For example, in Fig.
+5, the data curves are hard to distinguish.
+It is recommended to enlarge key areas to better present the experimental results and analysis.
+Additionally, many figures lack sufficient explanation.
+}
+
+Thank you for your suggestion.
+
+% comment19
+\rcomment{
+\color{red} For the third paragraph of left column on page 9, several "steps" are mentioned but not explained in the text.
+}
+
+Thank you for your suggestion.
+
+% comment20
+\rcomment{
+\color{red} The manuscript’s language requires improvement, as there are multiple grammatical errors and unclear expressions. A thorough revision is suggested to enhance overall readability.
+}
+
+Thank you for your suggestion.
+
+\newpage
 

### 2024-10-30 response.tex
chore: mainly modified by wb
夹带了几行私货

Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 % 根据Reviewer 1's Comment 1，Comment 2以及Reviewer 2's Comment 1，我们修改了文章的部分公式以及重新构建了符号表，使文章的公式符号的意义更加清晰，优化阅读体验。
-\item \textbf{[Writing and expression:]} Based on \textbf{Reviewer 1's Comment 1, Comment 2}, and \textbf{Reviewer 2's Comment 1}, we have revised some of the formulas in the article and reconstructed the symbol table to make the meanings of the formula symbols clearer and to enhance the overall reading experience.
+\item \textbf{[Writing and expression:]} Based on \textbf{Reviewer 1's Comment 1, Comment 2}, and \textbf{Reviewer 2's Comment 1}, we have revised some of the formulas in the paper and reconstructed the symbol table to make the meanings of the formula symbols clearer and to enhance the overall reading experience.
 
@@
 %=================================
-\section{Responses to the Comments from Reviewer 1}
+\section{Responses to the Comments from Reviewer 3}
 %=================================
@@
 % 问题：文中存在部分错误和语病，如在P5页第二段末尾，引用[36]连续重复出现，请认真检查
+\textbf{Response:} Thank you for your valuable feedback on our paper. We greatly appreciate the time and effort you have taken to review our work.
 
-\textbf{Response:} We thank the Reviewer for the constructive comment.
+Regarding the issue of errors and linguistic problems throughout the paper, especially the repeated citation [36] at the end of the second paragraph on page 5, we have carefully reviewed the entire manuscript and made the necessary corrections.
+The repeated citation has been removed, and we have conducted a thorough proofreading process to address any other linguistic issues that may have affected the clarity and quality of the paper.
+% 对存在的这类问题，我们深表歉意。我们已经删除了该处存在的重复引用的问题，同时，我们也修改了本文其他地方存在的表述不清或者语法错误等问题。以下为详细的修改内容：
+
+The following are the detailed modifications:
+
+\textcolor{blue}{
+To address the limitations faced by defense methods based on shallow semantic features in high-dimensional spaces, we propose a new defense strategy rooted in the essence of backdoor attacks [34], which leverages deep semantic features by focusing on the differences in model updates in the frequency domain.
+According to our experimental results, by transforming local model updates into the frequency domain, we can more accurately capture the abnormal behavior of malicious updates which is typically difficult to detect using traditional shallow feature-based defenses in low-frequency components.
+By analyzing the relevant features in the frequency domain, we can effectively distinguish between malicious and benign nodes, thereby enhancing the robustness and accuracy of federated learning in the face of sophisticated backdoor attacks.
+}
+
+\textcolor{blue}{......}
+
+\textcolor{blue}{
+Due to the curse of dimensionality in high-dimensional spaces, traditional methods based on shallow semantic
+feature can no longer effectively identify malicious nodes.
+In contrast, once model updates are transformed into the frequency domain, their differences are primarily concentrated in the low-frequency components.
+Focusing on the analysis of these low-frequency components not only improves identification accuracy but also significantly reduces computational overhead.
+For each update \(\triangledown \theta_i^t\), we apply one-dimensional DCT-II[35] to obtain its corresponding frequency distribution.
+Then we extract $m$ low-frequency components[36], such as 5000, yielding the low-frequency vector $G_i^t$.
+}
 
@@
 Finally, to represent that certain variables in the algorithm change with the training rounds, we added the superscript of round $t$ to some variables, such as modifying $C_{max}, Chi_i^2, {C'_1}, {C'_2}$ to $C^t_{max}, {Chi^t_i}^2, {C^t_1}', {C^t_2}'$.
+
+% 图1展示了算法修改后的结果
+The Algorithm \ref{alg:malicious-node-detection} shows the result of the modified algorithm.
 
@@
 \State $\hat{H}^t \gets (H^t)^{T} H^t$
-\State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
+\State $\lambda_{max}^t, \xi_{max}^t \gets eig(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
 \State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
@@
 \For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
-    \State ${Chi_i^t}^2 \gets \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}$
+    \State $Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{{\tilde G}^t[k] + \epsilon}}$
 \EndFor
@@
 % \State Step 4: Single-round malicious behavior perception
-\State $\textcolor{blue}{\{C'_1, C'_2\}} \gets KMeans(S^t, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
-\State \textcolor{blue}{$U_{nor} \gets C'_{\text{max}}$, $U_{mal} \gets \{C'_i \, | \, i \neq \text{max}\}$}
+\State $\textcolor{blue}{\{{C^t_1}', {C^t_2}'\}} \gets KMeans(S^t, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
+\State \textcolor{blue}{$U_{nor} \gets C'_{max}$, $U_{mal} \gets \{C'_i \, | \, i \neq max\}$}
 
@@
 
+\textcolor{blue}{
 "Acc" refers to accuracy, which measures the proportion of correct predictions; "Rec" stands for recall, representing the model's ability to correctly identify positive instances; "FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; "FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; "AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and "MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.
-
+}
 %========================================================
@@
 % ```
-\section{Responses to the Comments from Reviewer 2}
+\section{Responses to the Comments from Reviewer 1}
 
@@
 Thank you for your suggestion.
+% 待定
 
@@
 % 感谢你指出这一点，我们的图3对应\ref{\section{Methodology}}部分的B部分的2)，我们只将图片放在了对应的文字介绍部分，但是并未对图片内容进行描述，甚至没有在文章中引用这段文字。现在，我们
+% 系统中断：先写合同去了
+% Log：昨天早上去答辩，在外面等待的时候背了会儿单词，B同学看我在看手机就说是不是在和兔米尼聊天，我说早上已经聊过了[害羞]，然后他“诶(撇嘴[撇嘴])”
+% 第二次是他说飞哥衣服好帅，然后我说对象送的[害羞]
 Thank you for pointing this out.
@@
 }
+Thank you for your feedback and suggestions for improving the clarity of our paper.
+We acknowledge that some English expressions may have been difficult to understand, and we appreciate your recommendation to enhance the overall quality of writing.To address this concern, we have revised the manuscript, focusing on improving the fluency and readability of the text.
+We have rephrased complex or unclear expressions to ensure that the language is more straightforward and easier to follow.
+Additionally, we have performed a detailed grammar and style check to improve the overall quality of writing.
 
-Thank you for your suggestion.
+The following are some of the modifications:
+
+\textcolor{blue}{The attacker has complete control over the local training process of the malicious robot nodes, meaning they can manipulate local data, trigger patterns, optimization strategies, and local updates at will.
+Additionally, the attacker may adopt a stealthy attack strategy, where the backdoor is not implanted in a single training round but gradually embedded into the global model through the cumulative effect of multiple rounds of training.
+This scenario is plausible in practice, as the central server only receives the updates uploaded by robot nodes and has no insight into the specific training process of each node.
+However, the attacker cannot interfere with the aggregation process of the central server (i.e., altering the global model aggregation rules) or tamper with the local updates of benign nodes.}
+
+\textcolor{blue}{......}
+
+\textcolor{blue}{Despite the increasingly sophisticated strategies employed by attackers, it is important to note that the essence of backdoor attacks lies in establishing a link between the predefined trigger and the target within the model.
+Thus, regardless of how attackers adjust their attack strategies, their updates will always exhibit some distributional shift compared to benign nodes.}
 
@@
 
-\section{Responses to the Comments from Reviewer 3}
+\section{Responses to the Comments from Reviewer 4}
 
@@
 
-Thank you for your suggestion.
+We appreciate the reviewer’s insightful feedback.
+The decision to use the chi-square distribution instead of cosine similarity is rooted in the nature of the feature distribution in the frequency domain.
+Cosine similarity, while useful for comparing the angle between two vectors, would not appropriately capture the frequency domain’s distributional features in our model, where the outlier differences are more pronounced in the low-frequency components rather than in directional changes.
+The chi-square distribution allows us to better distinguish between malicious updates, which tend to introduce subtle but consistent deviations in these low-frequency features, and benign updates.
+This approach enhances detection accuracy by weighting the significant deviations while minimizing the impact of noise in the higher-frequency components.
+
+To accurately explain the reasons for using the chi-square distribution in this paper, we have made the following modifications:
+
+% 卡方距离通常用来衡量某一种观测分布是不是符合某一类典型的理论分布，这一点与我们的方法非常契合，因为我们将计算出来的干净成分来作为衡量良性与恶意用户的标准。与传统的欧几里得距离相比，卡方距离根据干净分量分配权重，赋予较小分量更大的重要性。另一方面，余弦相似度测量两个向量之间的角度，通常用于评估它们的方向一致性，忽略数值差异。然而，在我们的方法中，我们关心的是每个用户的低频分量与干净分量的偏离程度，包括了数值差异，因此卡方距离比余弦相似度更适合捕捉隐蔽的恶意攻击。
+\textcolor{blue}{
+% Compared to traditional Euclidean distance, Chi-square distance assigns weights based on the magnitude of the corresponding components of two vectors, giving greater importance to components with larger feature values.
+This leads to a more accurate representation of differences in significant features within low-frequency vectors, while filtering out unimportant noise.
+On the other hand, Cosine similarity measures the angle between two vectors and is commonly used to evaluate their directional alignment in high-dimensional space.
+However, in our case, where the focus is on the magnitude and distribution of frequency-domain features, this method is less effective at capturing subtle variations in low-frequency components.
+These variations, which represent key differences between benign and malicious updates, are reflected more in the distribution and intensity of specific feature deviations than in directional alignment.
+As a result, Cosine similarity may overlook small but crucial frequency-based anomalies that can greatly affect the detection process.
+In contrast, the Chi-square distance emphasizes the magnitude of these differences, allowing for the detection of subtle yet meaningful shifts in data that signal covert attacks.
+Chi-square distribution is usually used to measure whether a certain observed distribution conforms to a typical theoretical distribution, which is very consistent with our method because we use the calculated clean ingredient as a criterion for measuring benign and malicious nodes.
+Compared with the traditional Euclidean distance, the chi-square distribution assigns weights according to the clean ingredient, giving greater importance to smaller components.
+On the other hand, cosine similarity measures the angle between two vectors and is usually used to evaluate their directional consistency, ignoring magnitude differences.
+However, in our method, we are concerned with the degree of deviation of each user's low-frequency vector $G_i^t$ from the clean ingredient $\tilde{G}^t$, including magnitude differences, so the chi-square distribution is more suitable for capturing hidden malicious attacks than cosine similarity.
+}
 
@@
 
-Thank you for pointing this out.
+Thank you for pointing out the inconsistency in figure referencing throughout the manuscript.
+We have carefully reviewed all figure references and standardized the citation format.
+Going forward, we have consistently used the term "Figure" when referencing figures, ensuring uniformity across the entire paper.
 
@@
 }
+`
+Thank you for your suggestion.
+% 1. 为啥只对visual-encoder部分进行lora微调
+% 我们的工作专注于联邦学习过程中的抗后门攻击，因此在CLIP模型微调这方面，我们采用了最基础的设置。参考CLIP-Adapter这篇文章，因为本文设定的场景是增加视觉大模型在zero-shot下对图像的识别能力，因此我们只对CLIP模型的visual-encoder部分进行lora微调，而对于text-encoder这部分，我们采用“a photo of a {CLASS}"作为文本方面的提示词模板。
+% 2. 为什么使用lora微调，而不用其他微调方式
+% 因为受限的计算资源导致对CLIP模型进行全量微调的时间成本非常之大，同时，我们的研究重点也不强调微调后的模型具有极高的性能，因此我们放弃了全量微调。目前也存在一些针对CLIP模型的微调方式，比如prompt engineering层面的CoOp、CoCoOp、MaPLe以及adapter层面的CLIP Adapter、TIP-Adapter，但这几个工作微调涉及到的参数量较小，与我们工作假设的高维场景不太契合。综上，我们选择了使用lora方式对CLIP模型进行微调，在微调成本和涉及到的参数量之间能够达到平衡。
+% 3. 使用lora对CLIP模型进行微调，相应超参数设置的理由
+% 我们所使用的超参数设置参考了CLIP-LORA这篇文章，
 
-Thank you for your suggestion.
-
+% lora微调设置
 % comment15
@@
 }
+Thank you for your valuable feedback regarding the incorrect symbol usage in the manuscript.
+We have conducted a thorough review and carefully corrected all instances of improper symbol usage to ensure accuracy and consistency throughout the paper.
 
-Thank you for your suggestion.
+The following are the detailed modifications:
+
+\textcolor{blue}{Assume there are $N$ robot nodes in the system model, with each node denoted as $R_i$, where $i \in {1, 2, \ldots, N}$.
+Each robot node $R_i$ possesses a local dataset $D_i = {x_{i,j}, y_{i,j}}{j=1}^{|D_i|}$, where $x{i,j}$ represents a training sample, $y_{i,j}$ represents the corresponding label, and $|D_i|$ denotes the size of the dataset.
+The union of all local datasets across the nodes, $D = \bigcup_{i=1}^{N} D_i$, constitutes the overall dataset.}
+
+\textcolor{blue}{......}
+
+\textcolor{blue}{Based on this observation, we select the largest cluster \(C^t_{max} = \{G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}\}\) as the primary subject for analysis.
+To further extract the main characteristics of this cluster, we perform singular value decomposition (SVD)[38] on the matrix $H^t = (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n}$ formed by all nodes in this cluster.
+Since the left singular vectors of the SVD, denoted as \(\tilde{G}^t\), represent the principal directions of these vectors, \(\tilde{G}^t\) can be regarded as the principal component of benign nodes in the low-frequency domain.}
 
@@
 
-\section{Responses to the Comments from Reviewer 4}
+\section{Responses to the Comments from Reviewer 2}
 
@@
 
-Thank you for your suggestion.
+Thank you for your valuable feedback. We appreciate your comments regarding the grammatical errors and unclear expressions in the manuscript.
+
+In response, we have undertaken a comprehensive revision of the paper, with particular attention to correcting grammatical mistakes and improving the clarity of the text.
+We have also simplified complex expressions and enhanced the overall readability to ensure the content is more accessible and coherent.
 

### 2024-10-30 main-v2.tex
response: response until 2024.10.22 19:41
chore: mainly modified by wb
夹带了几行私货

Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
     $\triangledown \theta_i^t$ & Local update of $R_i$ during round $t$. \\ \hline
-    $G_i^t $ & Frequency component of $R_i$'s update at round $t$. \\ \hline
-    $m$ & The length of the low-frequency components. \\ \hline
+    $G_i^t $ & Frequency vector of $R_i$'s update at round $t$. \\ \hline
+    $m$ & The length of the low-frequency vectors. \\ \hline
     $H^t$ & The matrix formed by stacking $G_i^t$. \\ \hline
@@
 This behavior is also evident in the frequency domain, where it becomes even more pronounced.
-\textcolor{red}{Based on this observation, we select the largest cluster \(C_{max} = \{G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}\}\) as the primary subject for analysis.
+\textcolor{red}{Based on this observation, we select the largest cluster \(C^t_{max} = \{G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}\}\) as the primary subject for analysis.
 To further extract the main characteristics of this cluster, we perform singular value decomposition (SVD)\cite{wang2023scfl} on the matrix $H^t = (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n}$ formed by all nodes in this cluster.
-Since the left singular vectors of the SVD, denoted as \(\tilde{G}^t\), represent the principal directions of these vectors, \(\tilde{G}^t\) can be regarded as the principal component of benign nodes in the low-frequency domain.}
+Since the left singular vectors of the SVD, denoted as \(\tilde{G}^t\), represent the principal directions of these vectors, \(\tilde{G}^t\) can be regarded as the principal ingredient of benign nodes in the low-frequency domain.}
 
@@
 $\lambda^t_{max}$ and $\xi^t_{max}$ correspond to the largest eigenvalue and its eigenvector of the matrix $\hat{H}^t = (H^t)^{T} H^t$, respectively.
-In this way, we effectively extract the principal component that reflect the updates of benign nodes in the frequency domain, so $\tilde{G}^t$ can be used as the clean ingredient for subsequent malicious node detection.
+In this way, we effectively extract the principal ingredient that reflect the updates of benign nodes in the frequency domain, so $\tilde{G}^t$ can be used as the clean ingredient for subsequent malicious node detection.
 
@@
 
+\textcolor{red}{
 \begin{equation}
-{Chi^t_i}^2 = \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}
+Chi^t_i = \sqrt{ \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{{|\tilde G}^t[k]| + \epsilon} }
 \label{equation:KL}
-\end{equation}
+\end{equation}}
 % 其中 \(m\) 是低频向量的维度，\(\epsilon\) 是一个小的常数，用于避免分母为零。相比于传统的欧氏距离，卡方距离根据两个向量对应分量的大小进行加权，使得特征值较大的部分对距离的影响更大，从而能够更准确地反映低频向量中重要特征之间的差异，同时忽略不重要的噪声成分。
 where \(G_i^t[k]\) denotes the k-th element of vector \(G_i\) and \(\epsilon\) is a small constant to avoid division by zero.
-Compared to the traditional Euclidean distance, the Chi-square distance weights according to the magnitude of the corresponding components of the two vectors, making the influence of components with larger feature values more significant on the distance.
-This allows for a more accurate reflection of the differences between important features in the low-frequency vectors, while ignoring unimportant noise components.
-
+
+\textcolor{red}{
+Chi-square distance is usually used to measure whether a certain observed distribution conforms to a typical theoretical distribution, which is very consistent with our method because we use the calculated clean ingredient as a criterion for measuring benign and malicious nodes.
+Compared with the traditional Euclidean distance, the chi-square distance assigns weights according to the clean ingredient, giving greater importance to smaller components.
+On the other hand, cosine similarity measures the angle between two vectors and is usually used to evaluate their directional consistency, ignoring magnitude differences.
+However, in our method, we are concerned with the degree of deviation of each user's low-frequency vector $G_i^t$ from the clean ingredient $\tilde{G}^t$, including magnitude differences, so the chi-square distance is more suitable for capturing hidden malicious attacks than cosine similarity.
+}
 % 为什么要用卡方距离，不用欧式距离？实验论证？
@@
 % 为了准确地识别恶意节点，我们利用良性节点的低频成分与干净成分之间的差异度相比于恶意节点与干净成分之间更为相似这一特性，对差异集合$S^t$进一步进行聚类分析。具体而言，我们采用流行的KMeans聚类算法\cite{wan2023four}对距离差异集合$S^t$进行聚类，并将类别数设置为2，得到聚类\(C'_1, C'_2\)，将用户数量较大的簇\(C'_{max}\)中的所有节点标记为良性节点， 记作为\(U_{nor}\)，将另一簇\(C'_k\) \(k \neq {max}\)中的所有节点标记为恶意节点，记作\(U_{mal}\)。
-To accurately identify malicious nodes, we leverage the characteristic that the divergence between benign nodes' low-frequency components and the clean ingredient is more similar compared to that of malicious nodes.
+To accurately identify malicious nodes, we leverage the characteristic that the divergence between benign nodes' low-frequency vectors and the clean ingredient is more similar compared to that of malicious nodes.
 Based on this, we further perform cluster analysis on the divergence set \(S^t\).
@@
 Algorithm \ref{alg:malicious-node-detection} outlines the overall process of Instantaneous Attack Behavior Perception. 
-Lines 3-6 describe the computation process of frequency domain transformation, lines 7-12 detail the extraction process of clean component, lines 13-16 cover the calculation of the Chi-square divergence between each update and the clean ingredient, and finally, lines 17-18 outline the process of single-round malicious behavior perception using KMeans.
+Lines 3-6 describe the computation process of frequency domain transformation, lines 7-12 detail the extraction process of clean ingredient, lines 13-16 cover the calculation of the Chi-square divergence between each low-frequency vector and the clean ingredient, and finally, lines 17-18 outline the process of single-round malicious behavior perception using KMeans.
 
@@
 \begin{algorithmic}[1]
-\State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each update; $N$ is the number of nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from robot nodes during the $t$-th round; $m$ is the length of low-frequency components}
+\State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each update; $N$ is the number of nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from robot nodes during the $t$-th round; $m$ is the length of low-frequency vector}
 \State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
@@
 \For {$R_i \in \textcolor{red}{\{R_1, \ldots, R_N\}}$}
-    \State ${Chi_i^t}^2 \gets \frac{1}{2} \sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|G_i^t[k]|+|{\tilde G}^t[k]| + \epsilon}$
+    \State $Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|{\tilde G}^t[k]| + \epsilon}}$
 \EndFor
@@
 To validate the capability of SecFFT in constructing attack intent and effectively defending against advanced covert backdoor attacks employing complex strategies, we added Size and Angle constraints to the NEUR attack over multiple rounds.
-As shown in Fig.
-\ref{fig:lab3}, by comparing with typical behavior-based defense mechanisms such as Foolsgold, FLTrust, and Flame, it is evident that the intent-based SecFFT significantly enhances attack detection capabilities.
+As shown in \textcolor{red}{Figure \ref{fig:lab3}}, by comparing with typical behavior-based defense mechanisms such as Foolsgold, FLTrust, and Flame, it is evident that the intent-based SecFFT significantly enhances attack detection capabilities.
 Even though certain defense methods like Flame can effectively identify some highly covert attack behaviors, their detection performance is quickly bypassed when more complex multi-round attack strategies are introduced.
@@
 \caption{Metrics results with different attack and defense methods.}
+\resizebox{\columnwidth}{!}{%
 \begin{tabular}{c|c|c|c|c|c|c|c}
@@
 \end{tabular}
+}
 \vspace{1em}

### 2024-11-01 response.tex
yesterday: we 2

@@
 \usepackage{makecell}
+\PassOptionsToPackage{dvipsnames, svgnames, x11names}{xcolor}
 \usepackage{xcolor}
+\usepackage{threeparttable}
 
@@
 \newpage
+%=================================
+%=================================
+% 我给你一些审稿意见，请你按照格式返回latex源码：
+
+% ```
+% \section{Responses to the Comments from Reviewer 2}
+
+% % comment6
+% \rcomment{
+% \color{red} 审稿意见6
+% }
+
+% Thank you for your suggestion.
+
+% % comment7
+% %...
+
+% \newpage
+% ```
+\section{Responses to the Comments from Reviewer 1}
+
+% comment6
+\rcomment{
+\color{red} The text in some experimental result figures is too small to be legible. Improving the clarity and resolution is recommended.
+}
+
+Thank you for your valuable feedback regarding the legibility of the experimental result figures.
+We have reviewed each figure in the manuscript and enhanced the resolution and clarity to ensure that all text and details are easily readable.
+Specifically, we have increased the font size within the figures and adjusted the image quality to provide a sharper, more distinct presentation of the experimental results.
+
+% comment7
+\rcomment{
+\color{red} Figure 3 is not cited in the manuscript. It is suggested to reference and explain the figure in the relevant section, as its absence hinders understanding.
+}
+
+% 系统中断：先写合同去了
+% 这是我回复的其中一个审稿意见，使用文章中的术语翻译这段话为英文
+% 感谢你指出这一点，我们的图3对应\ref{\section{Methodology}}部分的B部分的2)，我们只将图片放在了对应的文字介绍部分，但是并未对图片内容进行描述，甚至没有在文章中引用这段文字。现在，我们在文章中引用了该图片并对齐进行了一个简单的描述：
+% 图片3展示了Long-term Attack Intention Detection的前两步。这张图片总体上一共有3行，第一行展示了联邦学习的过程，很多机器人节点各自在下发的全局模型$G_{t-1}$的基础上训练并得到新的局部模型$\theta^t_{l_1}$，之后每个参与训练的客户端将自己的梯度变化上传到中央服务器的全局模型并聚合，从而形成新一轮的全局模型。第二行分为左右两个部分，左边部分展示了客户端多轮次中将更新的梯度展平后的结果，第一列代表某轮次的梯度更新，第二列代表$n$个客户端一轮次梯度更新展平后的结果，第三列则代表$n$个客户端$T$轮次梯度更新展平后的结果；右侧的图代表了每一轮次的全局模型。第三行则代表了如何根据多轮次的历史数据计算单个客户端的意图点，其中每条射线代表了模型更新展平后的结果，超球的球心则代表了当前客户端的意图点。
+
+Thank you for pointing this out.
+Our Figure 3 corresponds to Section B, 2) of the Methodology section.
+We placed the image alongside the related text but did not provide a description of the content, nor was the image referenced in the article.
+We have now cited this image in the text and provided a brief description:
+
+Figure 3 illustrates the first two steps of the Long-term Attack Intention Detection.
+The figure comprises three rows overall.
+The first row demonstrates the process of federated learning, where many robot nodes independently train their local models \( \theta^t_{l_1} \) based on the distributed global model \( G_{t-1} \).
+Each participating client then uploads its gradient updates to the central server's global model, which are aggregated to form the next global model iteration.
+The second row is divided into two sections: the left section shows the flattened gradients updated across multiple rounds for clients.
+The first column represents the gradient update of a specific round, the second column shows the flattened gradient updates from \( n \) clients in one round, and the third column displays the flattened updates across \( T \) rounds for \( n \) clients.
+The right section of the image represents the global model in each round.
+The third row depicts how a single client's intention point is calculated based on multi-round historical data, where each ray signifies the flattened results of the model updates, and the hypersphere's center represents the current client's intention point.
+
+% comment8
+\rcomment{
+\color{red} The steps in the final paragraph of Section 5 do not align with Algorithm 2. Please revise for consistency.
+}
+
+Thank you for your suggestion.
+
+% comment9
+\rcomment{
+\color{red} Some conditions in Algorithm 2 are unclear, such as "for Client i do", "while Not Converged do", and "for Each point Oj $\neq$ Oi do". Clarification and revision are needed.
+}
+
+\textbf{Response:}
+
+Thank you for your valuable feedback on Algorithm 2. We have reviewed the conditions and updated the descriptions to ensure they are clear and unambiguous. Specifically:
+
+\begin{itemize}
+    \item \textbf{"for Client $i$ do"}: We clarified this condition to indicate that the algorithm iterates over each client in the dataset, specifying how Client $i$ is selected and what actions are taken for each client.
+
+    \item \textbf{"while Not Converged do"}: We revised this condition to include the specific convergence criteria used in the algorithm.
+This provides a clear stopping condition, ensuring that readers understand when the loop will terminate.
+
+    \item \textbf{"for Each point $O_j \neq O_i$ do"}: We clarified that this loop iterates over all points in the dataset except for point $O_i$, and we specified the purpose of comparing each $O_j$ with $O_i$ in the context of the algorithm’s objective.
+\end{itemize}
+
+These modifications provide a more detailed and precise description of the algorithm’s flow.
+We appreciate your insights and believe these clarifications enhance the readability and understanding of Algorithm 2.
+
+% comment10
+\rcomment{
+\color{red} Section VI-C lacks quantitative analysis of the experimental results.
+The partitioning results in Fig.
+6 are hard to distinguish, and the font size is too small.
+Moreover, the four subplots lack necessary labels, and the same issues are present in Fig.
+7.
+}
+
+Thank you for your suggestion.
+
+% comment11
+\rcomment{
+\color{red} Some of the English expressions are difficult to understand. Improving the overall quality of writing is recommended.
+}
+Thank you for your feedback and suggestions for improving the clarity of our paper.
+We acknowledge that some English expressions may have been difficult to understand, and we appreciate your recommendation to enhance the overall quality of writing.To address this concern, we have revised the manuscript, focusing on improving the fluency and readability of the text.
+We have rephrased complex or unclear expressions to ensure that the language is more straightforward and easier to follow.
+Additionally, we have performed a detailed grammar and style check to improve the overall quality of writing.
+
+The following are some of the modifications:
+
+\textcolor{blue}{The attacker has complete control over the local training process of the malicious robot nodes, meaning they can manipulate local data, trigger patterns, optimization strategies, and local updates at will.
+Additionally, the attacker may adopt a stealthy attack strategy, where the backdoor is not implanted in a single training round but gradually embedded into the global model through the cumulative effect of multiple rounds of training.
+This scenario is plausible in practice, as the central server only receives the updates uploaded by robot nodes and has no insight into the specific training process of each node.
+However, the attacker cannot interfere with the aggregation process of the central server (i.e., altering the global model aggregation rules) or tamper with the local updates of benign nodes.}
+
+\textcolor{blue}{......}
+
+\textcolor{blue}{Despite the increasingly sophisticated strategies employed by attackers, it is important to note that the essence of backdoor attacks lies in establishing a link between the predefined trigger and the target within the model.
+Thus, regardless of how attackers adjust their attack strategies, their updates will always exhibit some distributional shift compared to benign nodes.}
+
+\newpage
+
+\section{Responses to the Comments from Reviewer 2}
+
+% comment17
+\rcomment{
+\color{red} The concept of intent recognition is a key innovation in this manuscript’s.
+However, the definition and construction of attacker intent are vague and need further elaboration to help readers better understand the core idea.
+}
+
+Thank you for your suggestion.
+
+% comment18
+\rcomment{
+\color{red} The description of the experiments is unclear.
+The titles and text in the figures are too small, making them difficult to read.
+For example, in Fig.
+5, the data curves are hard to distinguish.
+It is recommended to enlarge key areas to better present the experimental results and analysis.
+Additionally, many figures lack sufficient explanation.
+}
+
+% 对于第一个实验：Model integrity and poisoning resistance，我们重新整理了相应数据，并修改了图片的表现形式。修改包括对图例字体格式以及大小的修改，同时为图中折现重合的部分加上了子图，使其更容易辨别。同时，我们也修改了原文中对于该实验结果的描述，使其更符合实验数据，同时更易于阅读和理解。
+Thank you for your detailed feedback regarding the clarity of our experimental descriptions and figures. We have carefully revised the manuscript to address each of the issues you raised.
+
+Specifically, for the experiment \textbf{Model Integrity and Poisoning Resistance}, as dipicted in Figure \ref{fig:lab1}, we reorganized the relevant data and revised the presentation of the figures.
+These modifications include adjustments to the legend font style and size, as well as the addition of subplots for overlapping line segments, enhancing visual clarity.
+Furthermore, we refined the original description of the experimental results to align more closely with the experimental data, making it easier to read and understand.
+
+\begin{figure*}[!ht]
+    \centering
+    \includegraphics[width=1\linewidth]{figures/lab1-combined.pdf}
+    \caption{ASR and TSR of various defense mechanisms (FedAVG, FLTrust, Foolsgold, Flame, SecFFT) under three attacks (MR, NEUR, EDGE CASE).}
+    \label{fig:lab1}
+\end{figure*}
+
+The corresponding modifications in the article are as follows:
+
+As depicted in the figure, in all attack scenarios, SecFFT consistently achieves an attack success rate (ASR) close to zero, while the test success accuracy (TSR) remains high.
+\textcolor{blue}{This indicates that SecFFT effectively defends against attacks by accurately identifying and neutralizing malicious users, all while preserving the performance and accuracy of the global model.
+In contrast, other defense mechanisms perform less effectively.
+Although Flame also shows strong performance in reducing ASR and mitigating malicious attack, it introduces considerable noise in the identification process, leading to a decrease in TSR, especially under MR attacks, where the performance degradation is more pronounced.
+FLTrust fails to defend effectively, with ASR initially low in MR attacks but quickly rising after several iterations, ultimately proving ineffective; against NEUR and EDGE CASE attacks, ASR remains high from the outset, demonstrating inadequate defense.
+Foolsgold also shows poor performance in defending against all three types of attacks, maintaining a high ASR from the beginning.
+Overall, the comparison highlights that other defense mechanisms either fail to effectively resist attacks or compromise model performance during defense.
+This further underscores SecFFT's significant advantage in federated fine-tuning for backdoor attack resistance, making it the optimal defense choice.}
+
+% comment19
+\rcomment{
+\color{red} For the third paragraph of left column on page 9, several "steps" are mentioned but not explained in the text.
+}
+
+Thank you for your suggestion.
+
+% comment20
+\rcomment{
+\color{red} The manuscript’s language requires improvement, as there are multiple grammatical errors and unclear expressions. A thorough revision is suggested to enhance overall readability.
+}
+
+Thank you for your valuable feedback. We appreciate your comments regarding the grammatical errors and unclear expressions in the manuscript.
+
+In response, we have undertaken a comprehensive revision of the paper, with particular attention to correcting grammatical mistakes and improving the clarity of the text.
+We have also simplified complex expressions and enhanced the overall readability to ensure the content is more accessible and coherent.
+
+\newpage
 
@@
 \For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
-    \State $Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{{\tilde G}^t[k] + \epsilon}}$
+\State \textcolor{blue}{$Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{{|\tilde G}^t[k]| + \epsilon}}$}
 \EndFor
@@
 
-\newpage
-%=================================
-%=================================
-% 我给你一些审稿意见，请你按照格式返回latex源码：
+\begin{table}[h!]
+\small
+\centering
+\caption{\textcolor{blue}{Metrics results with different attack and defense methods.}}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{c|c|c|c|c|c|c|c}
+\hline
+\textcolor{blue}{Strategy} & \textcolor{blue}{Defense} & \textcolor{blue}{Acc.} & \textcolor{blue}{Rec.} & \textcolor{blue}{FPR} & \textcolor{blue}{FNR} & \textcolor{blue}{AUC} & \textcolor{blue}{MCC} \\ \hline
 
-% ```
-% \section{Responses to the Comments from Reviewer 2}
+\multirow{4}{*}{\textcolor{blue}{None}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.90} & \textcolor{blue}{0.67} & \textcolor{blue}{0.00} & \textcolor{blue}{0.33} & \textcolor{blue}{0.83} & \textcolor{blue}{0.76} \\
+                      & \textcolor{blue}{FLTrust}   & \textcolor{blue}{0.82} & \textcolor{blue}{0.40} & \textcolor{blue}{0.00} & \textcolor{blue}{0.60} & \textcolor{blue}{0.70} & \textcolor{blue}{0.56} \\
+                      & \textcolor{blue}{Flame}     & \textcolor{blue}{0.90} & \textcolor{blue}{0.67} & \textcolor{blue}{0.00} & \textcolor{blue}{0.33} & \textcolor{blue}{0.83} & \textcolor{blue}{0.76} \\
+                      & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} & \textcolor{blue}{0.00} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{1.00}} & \textbf{\textcolor{blue}{1.00}} \\ \hline
 
-% % comment6
-% \rcomment{
-% \color{red} 审稿意见6
-% }
+\multirow{4}{*}{\textcolor{blue}{Size}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.92} & \textcolor{blue}{0.80} & \textcolor{blue}{0.03} & \textcolor{blue}{0.20} & \textcolor{blue}{0.88} & \textcolor{blue}{0.72} \\
+                      & \textcolor{blue}{FLTrust}   & \textcolor{blue}{0.82} & \textcolor{blue}{0.53} & \textcolor{blue}{0.06} & \textcolor{blue}{0.47} & \textcolor{blue}{0.74} & \textcolor{blue}{0.61} \\
+                      & \textcolor{blue}{Flame}     & \textcolor{blue}{0.92} & \textcolor{blue}{0.73} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.27} & \textcolor{blue}{0.87} & \textcolor{blue}{0.78} \\
+                      & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{0.98}} & \textbf{\textcolor{blue}{0.93}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.07}} & \textbf{\textcolor{blue}{0.96}} & \textbf{\textcolor{blue}{0.91}} \\ \hline
 
-% Thank you for your suggestion.
-
-% % comment7
-% %...
-
-% \newpage
-% ```
-\section{Responses to the Comments from Reviewer 1}
-
-% comment6
-\rcomment{
-\color{red} The text in some experimental result figures is too small to be legible. Improving the clarity and resolution is recommended.
+\multirow{4}{*}{\textcolor{blue}{Angle}} & \textcolor{blue}{Foolsgold} & \textcolor{blue}{0.88} & \textcolor{blue}{0.73} & \textcolor{blue}{0.06} & \textcolor{blue}{0.27} & \textcolor{blue}{0.84} & \textcolor{blue}{0.68} \\
+                       & \textcolor{blue}{FLTrust}   & \textcolor{blue}{0.86} & \textcolor{blue}{0.60} & \textcolor{blue}{0.03} & \textcolor{blue}{0.40} & \textcolor{blue}{0.80} & \textcolor{blue}{0.65} \\
+                       & \textcolor{blue}{Flame}     & \textcolor{blue}{0.90} & \textcolor{blue}{0.67} & \textbf{\textcolor{blue}{0.00}} & \textcolor{blue}{0.33} & \textcolor{blue}{0.83} & \textcolor{blue}{0.76} \\
+                       & \textcolor{blue}{SecFFT}    & \textbf{\textcolor{blue}{0.96}} & \textbf{\textcolor{blue}{0.87}} & \textbf{\textcolor{blue}{0.00}} & \textbf{\textcolor{blue}{0.13}} & \textbf{\textcolor{blue}{0.94}} & \textbf{\textcolor{blue}{0.88}} \\ \hline
+\end{tabular}
 }
-
-Thank you for your suggestion.
-% 待定
-
-% comment7
-\rcomment{
-\color{red} Figure 3 is not cited in the manuscript. It is suggested to reference and explain the figure in the relevant section, as its absence hinders understanding.
-}
-
-% 感谢你指出这一点，我们的图3对应\ref{\section{Methodology}}部分的B部分的2)，我们只将图片放在了对应的文字介绍部分，但是并未对图片内容进行描述，甚至没有在文章中引用这段文字。现在，我们
-% 系统中断：先写合同去了
-% Log：昨天早上去答辩，在外面等待的时候背了会儿单词，B同学看我在看手机就说是不是在和兔米尼聊天，我说早上已经聊过了[害羞]，然后他“诶(撇嘴[撇嘴])”
-% 第二次是他说飞哥衣服好帅，然后我说对象送的[害羞]
-Thank you for pointing this out.
-
-% comment8
-\rcomment{
-\color{red} The steps in the final paragraph of Section 5 do not align with Algorithm 2. Please revise for consistency.
-}
-
-Thank you for your suggestion.
-
-% comment9
-\rcomment{
-\color{red} Some conditions in Algorithm 2 are unclear, such as "for Client i do", "while Not Converged do", and "for Each point Oj $\neq$ Oi do". Clarification and revision are needed.
-}
-
-Thank you for your suggestion.
-
-% comment10
-\rcomment{
-\color{red} Section VI-C lacks quantitative analysis of the experimental results.
-The partitioning results in Fig.
-6 are hard to distinguish, and the font size is too small.
-Moreover, the four subplots lack necessary labels, and the same issues are present in Fig.
-7.
-}
-
-Thank you for your suggestion.
-
-% comment11
-\rcomment{
-\color{red} Some of the English expressions are difficult to understand. Improving the overall quality of writing is recommended.
-}
-Thank you for your feedback and suggestions for improving the clarity of our paper.
-We acknowledge that some English expressions may have been difficult to understand, and we appreciate your recommendation to enhance the overall quality of writing.To address this concern, we have revised the manuscript, focusing on improving the fluency and readability of the text.
-We have rephrased complex or unclear expressions to ensure that the language is more straightforward and easier to follow.
-Additionally, we have performed a detailed grammar and style check to improve the overall quality of writing.
-
-The following are some of the modifications:
-
-\textcolor{blue}{The attacker has complete control over the local training process of the malicious robot nodes, meaning they can manipulate local data, trigger patterns, optimization strategies, and local updates at will.
-Additionally, the attacker may adopt a stealthy attack strategy, where the backdoor is not implanted in a single training round but gradually embedded into the global model through the cumulative effect of multiple rounds of training.
-This scenario is plausible in practice, as the central server only receives the updates uploaded by robot nodes and has no insight into the specific training process of each node.
-However, the attacker cannot interfere with the aggregation process of the central server (i.e., altering the global model aggregation rules) or tamper with the local updates of benign nodes.}
-
-\textcolor{blue}{......}
-
-\textcolor{blue}{Despite the increasingly sophisticated strategies employed by attackers, it is important to note that the essence of backdoor attacks lies in establishing a link between the predefined trigger and the target within the model.
-Thus, regardless of how attackers adjust their attack strategies, their updates will always exhibit some distributional shift compared to benign nodes.}
+\vspace{1em}
+\begin{tablenotes}
+\scriptsize
+\item ``Acc." stands for Accuracy, ``Rec." for Recall, ``FPR" for False Positive Rate, ``FNR" for False Negative Rate, ``AUC" for Area Under Curve, and ``MCC" for Matthews Correlation Coefficient.
+The strategies are abbreviated as ``None" (No strategy), ``Size" (Size-limited strategy), and ``Angle" (Angle-limited strategy).
+\end{tablenotes}
+\label{tab:detect}
+\end{table}
 
@@
 }
-`
-Thank you for your suggestion.
-% 1. 为啥只对visual-encoder部分进行lora微调
+% 1. 为什么使用lora微调，而不用其他微调方式
+% 因为受限的计算资源导致对CLIP模型进行全量微调的时间成本非常之大，同时，我们的研究重点也不强调微调后的模型具有极高的性能，因此我们放弃了全量微调。目前也存在一些针对CLIP模型的微调方式，比如prompt engineering层面的CoOp、CoCoOp、MaPLe以及adapter层面的CLIP Adapter、TIP-Adapter，但这几个工作微调涉及到的参数量较小，与我们工作假设的高维场景不太契合。综上，我们选择了使用lora方式对CLIP模型进行微调，在微调成本和涉及到的参数量之间能够达到平衡。
+% 2. 为啥只对visual-encoder部分进行lora微调
 % 我们的工作专注于联邦学习过程中的抗后门攻击，因此在CLIP模型微调这方面，我们采用了最基础的设置。参考CLIP-Adapter这篇文章，因为本文设定的场景是增加视觉大模型在zero-shot下对图像的识别能力，因此我们只对CLIP模型的visual-encoder部分进行lora微调，而对于text-encoder这部分，我们采用“a photo of a {CLASS}"作为文本方面的提示词模板。
-% 2. 为什么使用lora微调，而不用其他微调方式
-% 因为受限的计算资源导致对CLIP模型进行全量微调的时间成本非常之大，同时，我们的研究重点也不强调微调后的模型具有极高的性能，因此我们放弃了全量微调。目前也存在一些针对CLIP模型的微调方式，比如prompt engineering层面的CoOp、CoCoOp、MaPLe以及adapter层面的CLIP Adapter、TIP-Adapter，但这几个工作微调涉及到的参数量较小，与我们工作假设的高维场景不太契合。综上，我们选择了使用lora方式对CLIP模型进行微调，在微调成本和涉及到的参数量之间能够达到平衡。
 % 3. 使用lora对CLIP模型进行微调，相应超参数设置的理由
-% 我们所使用的超参数设置参考了CLIP-LORA这篇文章，
+% 在使用lora对CLIP模型进行微调时，我们所使用的超参数设置参考了CLIP-LORA这篇文章，相关的超参数例如learning rate, batch size等与该篇论文几乎相符合。而在lora参数秩的设置上，如果按照CLIP-LORA这篇文章进行设置则会导致最终微调涉及到的参数量较少，不符合本文设定的场景，因此我们进行了适当增大。
+% 4. 联邦训练过程相应的超参数设置理由
+% 对于联邦学习相关的超参数例如节点数量，我们的设置参考了\cite{wei2023personalized}, \cite{ilhan2023scalefl}, \cite{wu2023faster}, \cite{ye2024openfedllm}, \cite{zhou2024every}, \cite{nguyen2022flame}, and \cite{yang2024roseagg}等文章。这些工作所采用的节点数不尽相同，范围从20到200不等。因此，综合考虑时间成本，计算开销以及验证效果等方面，我们才采用相应的超参数设置。
+% Thank you for your valuable feedback.
+We appreciate your comments regarding the need for clarification and justification of the hyperparameter settings used in our experiments.
+Below, we provide a detailed response to address your concerns:
 
-% lora微调设置
+% \textbf{Rationale behind hyperparameter settings for LoRA fine-tuning of CLIP:}
+% We chose LoRA (Low-Rank Adaptation) for fine-tuning the CLIP model due to limited computational resources and the need to balance time cost and parameter efficiency.
+Full fine-tuning of the CLIP model is computationally expensive, and since our research does not prioritize pushing the fine-tuned model to peak performance, we selected LoRA to maintain computational efficiency while still allowing a sufficient degree of fine-tuning.
+LoRA enables us to adjust a smaller set of parameters, which is more practical for the high-dimensional data scenarios we explore in our work.
+% For the specific hyperparameters used in LoRA fine-tuning, we referred to the values suggested in the CLIP-LORA paper, such as learning rate and batch size.
+However, we found that the original rank setting of LoRA would have resulted in an insufficient number of parameters for our scenario.
+Thus, we adjusted the rank to increase the number of tunable parameters, ensuring that the model's capacity aligns with the complexity of the data used in our experiments.
+
+% Rationale behind the hyperparameter settings for federated training
+% For the federated training process, we carefully considered the hyperparameters, especially the number of participating nodes, which is a critical factor in federated learning.
+Informed by recent studies such as \cite{wei2023personalized}, \cite{ilhan2023scalefl}, and \cite{wu2023faster}, which tested node counts ranging from 20 to 200, we aimed to find a balance between computational cost, time efficiency, and model accuracy.
+After evaluating our available resources and validating our preliminary results, we settled on a configuration that fits the scope of our work while ensuring robust performance.
+
+Thank you for your insightful comments. We have carefully considered your concerns regarding the hyperparameter settings and provide a detailed explanation below:
+
+\textbf{LoRA was selected due to computational efficiency and alignment with our research goals:}
+Given the limited computational resources available, full-parameter fine-tuning of the CLIP model was impractical due to the substantial time and resource costs.
+Additionally, our research does not focus on achieving the highest possible performance but rather on efficiently conducting experiments.
+While other fine-tuning methods like CoOp\cite{zhou2022learning}, CoCoOp\cite{zhou2022conditional}, MaPLe, and adapter-based methods such as CLIP-Adapter\cite{gao2024clip} and TIP-Adapter\cite{zhang2021tip} are available, these involve fewer parameters and do not align well with the high-dimensional scenarios required in our study.
+LoRA offers a balanced solution, maintaining computational efficiency while optimizing parameter adjustment.
+
+\textbf{The visual encoder of the CLIP model was fine-tuned to meet the core focus of our research:}
+Our study primarily addresses backdoor attacks in federated learning, and thus we used a straightforward configuration for fine-tuning the CLIP model.
+In accordance with the approach from the CLIP-Adapter\cite{gao2024clip} paper, which enhances visual recognition capabilities, we applied LoRA exclusively to the visual encoder.
+For the text encoder, we retained the default prompt template (“a photo of a \{CLASS\}”) to guide text-based predictions, which met our research needs without introducing unnecessary complexity.
+
+\textbf{The hyperparameters for LoRA were adapted based on the demands of our experimental setup:}
+We adopted hyperparameters such as learning rate and batch size from the recommendations in the CLIP-LORA\cite{zanella2024low} paper.
+However, we determined that the default rank for LoRA parameters was insufficient to meet the high-dimensional requirements of our work.
+To better accommodate the parameter complexity in our experiments, we adjusted the rank to increase the number of tunable parameters, ensuring better fitting the requirements of our high-dimensional scenario.
+
+\textbf{Federated learning hyperparameters were informed by prior studies and practical considerations:}
+For the federated training aspect of our research, we relied on previous studies, including \cite{wei2023personalized}, \cite{ilhan2023scalefl}, and \cite{wu2023faster}, which suggested a participants range from 20 to 200.
+Considering the time cost, computational overhead, and  the effectiveness of experimental results, we selected the most suitable configuration for our experiments, optimizing both performance and resource use.
+
 % comment15
@@
 
-The following are the detailed modifications:
+The following are some of the detailed modifications:
 
@@
 Since the left singular vectors of the SVD, denoted as \(\tilde{G}^t\), represent the principal directions of these vectors, \(\tilde{G}^t\) can be regarded as the principal component of benign nodes in the low-frequency domain.}
-
-\newpage
-
-\section{Responses to the Comments from Reviewer 2}
-
-% comment17
-\rcomment{
-\color{red} The concept of intent recognition is a key innovation in this manuscript’s.
-However, the definition and construction of attacker intent are vague and need further elaboration to help readers better understand the core idea.
-}
-
-Thank you for your suggestion.
-
-% comment18
-\rcomment{
-\color{red} The description of the experiments is unclear.
-The titles and text in the figures are too small, making them difficult to read.
-For example, in Fig.
-5, the data curves are hard to distinguish.
-It is recommended to enlarge key areas to better present the experimental results and analysis.
-Additionally, many figures lack sufficient explanation.
-}
-
-Thank you for your suggestion.
-
-% comment19
-\rcomment{
-\color{red} For the third paragraph of left column on page 9, several "steps" are mentioned but not explained in the text.
-}
-
-Thank you for your suggestion.
-
-% comment20
-\rcomment{
-\color{red} The manuscript’s language requires improvement, as there are multiple grammatical errors and unclear expressions. A thorough revision is suggested to enhance overall readability.
-}
-
-Thank you for your valuable feedback. We appreciate your comments regarding the grammatical errors and unclear expressions in the manuscript.
-
-In response, we have undertaken a comprehensive revision of the paper, with particular attention to correcting grammatical mistakes and improving the clarity of the text.
-We have also simplified complex expressions and enhanced the overall readability to ensure the content is more accessible and coherent.
 

### 2024-11-01 main-v2.tex
yesterday: we 2

@@
 \For {$R_i \in \textcolor{red}{\{R_1, \ldots, R_N\}}$}
-    \State $Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|{\tilde G}^t[k]| + \epsilon}}$
+    \State \textcolor{red}{$Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|{\tilde G}^t[k]| + \epsilon}}$}
 \EndFor
@@
 When the difference between the updated radius \( r_{i,k+1} \) and the previous radius \( r_{i,k} \) is smaller than a predefined threshold \( \lambda \), or when the maximum number of iterations $k_{max}$ is reached, the iteration stops.
+
+\textcolor{red}{Figure \ref{fig3:longterm} illustrates the first two steps of the Long-term Attack Intention Detection.
+The figure comprises three rows overall.
+The first row demonstrates the process of federated learning, where many robot nodes independently train their local models \( \theta^t_{l_1} \) based on the distributed global model \( G_{t-1} \).
+Each participating client then uploads its gradient updates to the central server's global model, which are aggregated to form the next global model iteration.
+The second row is divided into two sections: the left section shows the flattened gradients updated across multiple rounds for clients.
+The first column represents the gradient update of a specific round, the second column shows the flattened gradient updates from \( n \) clients in one round, and the third column displays the flattened updates across \( T \) rounds for \( n \) clients.
+The right section of the image represents the global model in each round.
+The third row depicts how a single client's intention point is calculated based on multi-round historical data, where each ray signifies the flattened results of the model updates, and the hypersphere's center represents the current client's intention point.}
 
@@
 
-\For {Client $i$}
+% \For {Client $i$ \in 55}
 \State{\color{CadetBlue}/* \textbf{Construction of updates and model databases */}} 
@@
 
-%\textbf{数据集}：我们使用FMNIST\cite{minist}作为实验数据集。FMNIST数据集包含60,000张28x28像素的灰度时尚商品图像，共分为10个类别，其中50,000张为训练集，10,000张为测试集。
-
-\textbf{Dataset:} We used the FMNIST\cite{minist} dataset as the experimental dataset.
-The FMNIST dataset contains 60,000 grayscale images of fashion items with a resolution of 28x28 pixels, divided into 10 categories, with 50,000 images for training and 10,000 for testing.
-
- % \textbf{微调模型}：我们采用CLIP的CLIP-ViT-B/32\cite{huggingface_clip}模型作为微调所使用的预训练模型。CLIP是一种通过对比学习在文本和图像数据上进行预训练的模型，能将自然语言和视觉信息映射到同一特征空间中。CLIP-ViT-B/32基于ViT\cite{vit}架构，包含12层Transformer编码器，隐藏层维度为768，多头注意力头数为12，使用32x32的图像块作为输入。在微调过程中，我们使用LORA\cite{lora}方案仅在Vision Encoder模块插入低秩矩阵，保持Textual Encoder模块不变。我们设定低秩矩阵的秩为16，学习率为$10^{-4}$，以在有限计算资源下高效微调模型，使其更好地适应特定任务的数据分布。
+%\textbf{数据集}：我们使用FMNIST\cite{minist}作为实验数据集，该数据集在联邦学习场景中被广泛使用。FMNIST数据集包含60,000张28x28像素的灰度时尚商品图像，共分为10个类别，其中50,000张为训练集，10,000张为测试集。
+
+\textbf{Dataset:} We employ the FMNIST dataset \cite{minist} as our experimental data, which is widely utilized in federated learning research.
+The FMNIST dataset consists of 60,000 grayscale images of fashion items, each with a resolution of 28x28 pixels, categorized into 10 distinct classes.
+Of these, 50,000 images form the training set, while the remaining 10,000 images constitute the test set.
+
+ % \textbf{微调模型}：我们采用CLIP的CLIP-ViT-B/32\cite{huggingface_clip}模型作为微调所使用的预训练模型。CLIP是一种通过对比学习在文本和图像数据上进行预训练的模型，能将自然语言和视觉信息映射到同一特征空间中。CLIP-ViT-B/32基于ViT\cite{vit}架构，包含12层Transformer编码器，隐藏层维度为768，多头注意力头数为12，使用32x32的图像块作为输入。在微调过程中，我们使用LORA\cite{lora}方案仅在Vision Encoder模块插入低秩矩阵，保持Textual Encoder模块不变。我们设定低秩矩阵的秩为16，学习率为$10^{-4}$，以在有限计算资源下高效微调模型，同时符合我们设定的高维场景。
 \textbf{Models:} 
@@
 We set the rank of the low-rank matrices to 16 and the learning rate to \textbf{$10^{-4}$} to efficiently fine-tune the model under limited computational resources, allowing it to better adapt to the data distribution of specific tasks.
-We adopted the \textbf{CLIP-ViT-B/32}\cite{huggingface_clip} model from \cite{clip} as the pre-trained model for federated fine-tuning.
+We adopt the \textbf{CLIP-ViT-B/32}\cite{huggingface_clip} model from \cite{clip} as the base model for federated fine-tuning.
 CLIP is a vision-language model pre-trained on both text and image data through contrastive learning, capable of mapping natural language and visual information into a shared feature space.
 CLIP-ViT-B/32 is based on the ViT\cite{vit} architecture and consists of 12 layers of Transformer encoders, with a hidden dimension of 768 and 12 attention heads, processing 32x32 image patches as input.
-During fine-tuning, we employed the \textbf{LORA}\cite{lora} method to introduce low-rank matrices only into the Vision Encoder module, while keeping the Textual Encoder module unchanged.
-We set the rank of the low-rank matrices to 16 and the learning rate to \textbf{$10^{-4}$} to efficiently fine-tune the model under limited computational resources, enabling it to better adapt to the data distribution of specific tasks.
+Meanwhile, we employ the \textbf{LORA}\cite{lora} method to introduce low-rank matrices only into the Vision Encoder module, while keeping the Textual Encoder module unchanged during federated fine-tuning.
+We set the rank of the low-rank matrices to 16 and the learning rate to \textbf{$10^{-4}$} to efficiently fine-tune the model under limited computational resources, aligning with the high-dimensional setting defined in our experiment.
 
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{figures/lab1-combined.pdf}
-    \caption{ASR and TSR of various defense mechanisms (FedAVG, FLTrust, Foolsgold, Flame, SecFFT) under three attacks (MR, NEUR, Edge case).}
+    \includegraphics[width=1\linewidth]{figures/lab1-combined.pdf}
+    \caption{ASR and TSR of various defense mechanisms (FedAVG, FLTrust, Foolsgold, Flame, SecFFT) under three attacks (MR, NEUR, EDGE CASE).}
     \label{fig:lab1}
@@
 The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
-Similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
+\textcolor{red}{For single round recognition,} similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
 ASR denotes the probability that malicious nodes successfully manipulate the global model to predict a specified target.
@@
 The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR.
+\textcolor{red}{For multi round recognition, ``Acc" refers to accuracy, which measures the proportion of correct predictions;``Rec" stands for recall, representing the model's ability to correctly identify positive instances;``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive;``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative;``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/lab2-combined.pdf}
-    \caption{Visualization of node identification results under three different attack scenarios (MR, Edge Case, NEUR) for various defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE dimensionality reduction.
+    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
+    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE dimensionality reduction.
 The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign and benign nodes incorrectly identified as malicious.
@@
 % 为了验证我们所提方法“Instantaneous Attack Behavior Perception”的有效性，我们分别在MR、EDGE CASE、NEUR三种攻击下进行实验，并与FedAVG(Baseline)、Foolsgold、FLTrust、Flame进行对比，比较不同防御算法下相应的TSR以及ASR。图\ref{fig:lab1}分别展示了攻击相应的实验结果。
-To validate the effectiveness of our proposed method, we conducted experiments under three types of attacks: MR, Edge case, and NEUR.
+To validate the effectiveness of our proposed method SecFFT, we conducted experiments under three types of attack scenarios: MR, EDGE CASE, and NEUR.
 We compared our method with FedAVG (Baseline), FoolsGold, FLTrust, and Flame to evaluate the corresponding TSR and ASR under different defense mechanisms.
@@
 
-% 从图中可以看出，SecFFT在面对三种攻击场景（MR、NEUROTOXIN、EDGE_CASE）时展现了最强的鲁棒性和出色的模型性能。在所有场景下，SecFFT的攻击成功率（ASR）始终接近于零，测试准确率（TSR）依然维持在高位，这意味着该算法能够有效防御攻击，能够成功识别并防御恶意用户，同时保持全局模型的性能和准确性。相比之下，其他防御算法表现则较为逊色。虽然Flame在降低ASR方面同样表现优异，能有效识别出恶意用户，但其在识别过程中引入了较多噪声，导致全局模型的准确率（TSR）下降，特别是在MR攻击下，性能损失更为显著。FLTrust在应对MR攻击时几乎完全失效，ASR迅速上升，未能有效防御；尽管在NEUROTOXIN和EDGE_CASE场景下表现有所改善，但防御效果依然不够稳定。Foolsgold在MR和NEUROTOXIN攻击下的防御效果较差，ASR依旧很高，仅在EDGE case下表现出一些效果，但并不显著。总体而言，这些算法在抵御攻击时未能同时兼顾模型的性能，进一步突显了SecFFT在联邦学习攻击防御中的显著优势，成为最优的防御选择。
+% 从图中可以看出，SecFFT在面对三种攻击场景（MR、NEUROTOXIN、EDGE_CASE）时展现了最强的鲁棒性和出色的模型性能。在所有场景下，SecFFT的攻击成功率（ASR）始终接近于零，测试准确率（TSR）依然维持在高位，这意味着该算法能够有效防御攻击，能够成功识别并防御恶意用户，同时保持全局模型的性能和准确性。相比之下，其他防御算法表现则较为逊色。虽然Flame在降低ASR方面同样表现优异，能有效识别出恶意用户，但其在识别过程中引入了较多噪声，导致全局模型的准确率（TSR）下降，特别是在MR攻击下，性能损失更为显著。FLTrust在应对攻击时几乎完全失效，在面对MR攻击时，尽管刚开始ASR较低，但经过多轮迭代后，ASR迅速上升，未能有效防御，在面对NEUR和EDGE_CASE攻击时，ASR从开始就展现出较高值，也无法有效防御。Foolsgold在以上三种攻击时的防御效果均差，从开始就展现出较高的ASR。总体而言，对比的防御算法要么无法有效的抵抗攻击，要么在抵御攻击时未能同时兼顾模型的性能，进一步突显了SecFFT在联邦微调抗后门攻击中的显著优势，成为最优的防御选择。
 % As shown in the figure, SecFFT demonstrates the strongest robustness and excellent model performance when faced with three types of attack scenarios (MR, NEUR, EDGE CASE).
@@
 Overall, these mechanisms fail to balance model performance while defending against attacks, further highlighting SecFFT's significant advantage, making it the optimal choice for defense.
-As depicted in the figure, SecFFT exhibits the highest robustness and superior model performance when confronted with three types of attack scenarios (MR, NEUR, EDGE CASE).
-Across all scenarios, SecFFT's ASR remains near zero, whereas the TSR remains high, indicating that the algorithm effectively defends against attacks by accurately identifying and mitigating malicious nodes while preserving the performance and accuracy of the global model.
+As depicted in the figure, in all attack scenarios, SecFFT consistently achieves an attack success rate (ASR) close to zero, while the test success accuracy (TSR) remains high.
+\textcolor{red}{This indicates that SecFFT effectively defends against attacks by accurately identifying and neutralizing malicious users, all while preserving the performance and accuracy of the global model.
+In contrast, other defense mechanisms perform less effectively.
+Although Flame also shows strong performance in reducing ASR and mitigating malicious attack, it introduces considerable noise in the identification process, leading to a decrease in TSR, especially under MR attacks, where the performance degradation is more pronounced.
+FLTrust fails to defend effectively, with ASR initially low in MR attacks but quickly rising after several iterations, ultimately proving ineffective; against NEUR and EDGE CASE attacks, ASR remains high from the outset, demonstrating inadequate defense.
+Foolsgold also shows poor performance in defending against all three types of attacks, maintaining a high ASR from the beginning.
+Overall, the comparison highlights that other defense mechanisms either fail to effectively resist attacks or compromise model performance during defense.
+This further underscores SecFFT's significant advantage in federated fine-tuning for backdoor attack resistance, making it the optimal defense choice.}
+% SecFFT exhibits the highest robustness and superior model performance when confronted with three types of attack scenarios (MR, NEUR, EDGE CASE).
+Across all scenarios, SecFFT's ASR remains near zero, whereas the TSR remains highest, indicating that the algorithm effectively defends against attacks by accurately identifying and mitigating malicious nodes while preserving the performance and accuracy of the global model.
 Conversely, other defense algorithms perform less effectively.
@@
 \subsection{Performance of Attack Behavior Perception}
-% 为了验证我们所提方法在恶意用节点识别方面具有较高的准确度，我们总结了在三种攻击(MR, Edge case, NEUR)下所有轮次中SecFFT对恶意节点的识别情况，并与FoolsGold, FLTrust, and Flame三种防御算法进行了对比。具体对比结果如图\ref{fig:lab2}所示，我们利用t-sne算法将所有轮次中节点的更新降维到了二维平面，图中红色点表示被错误识别的节点，包括恶意节点被识别成良性节点以及良性节点被错误识别成恶意节点。对于无法直接获得节点识别情况的Foolsgold防御算法，我们通过利用KMeans聚合算法将该防御算法过程中分配给每个用户的聚合权重聚成两类，并取最大类作为良性节点其余作为恶意节点的结果作为统计标准。
-% To validate the high accuracy of our proposed method in identifying malicious nodes, we summarized the detection results of SecFFT under three types of attacks (MR, Edge Case, NEUR) across all rounds and compared them with three defense mechanisms: FoolsGold, FLTrust, and Flame.
+% 为了验证我们所提方法在恶意用节点识别方面具有较高的准确度，我们总结了在三种攻击(MR, EDGE CASE, NEUR)下所有轮次中SecFFT对恶意节点的识别情况，并与FoolsGold, FLTrust, and Flame三种防御算法进行了对比。具体对比结果如图\ref{fig:lab2}所示，我们利用t-sne算法将所有轮次中节点的更新降维到了二维平面，图中红色点表示被错误识别的节点，包括恶意节点被识别成良性节点以及良性节点被错误识别成恶意节点。对于无法直接获得节点识别情况的Foolsgold防御算法，我们通过利用KMeans聚合算法将该防御算法过程中分配给每个用户的聚合权重聚成两类，并取最大类作为良性节点其余作为恶意节点的结果作为统计标准。
+% To validate the high accuracy of our proposed method in identifying malicious nodes, we summarized the detection results of SecFFT under three types of attacks (MR, EDGE CASE, NEUR) across all rounds and compared them with three defense mechanisms: FoolsGold, FLTrust, and Flame.
 The specific comparison results are shown in Figure \ref{fig:lab2}.
@@
 Comparatively, SecFFT performs the best in dealing with various attack types, effectively reducing the misidentification rate and showing better generalization ability and accuracy.
-As illustrated in the figure, SecFFT achieves the lowest misidentification rate, at only 3\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes.
-Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 12\%, 19.5\%, and 37.5\%, respectively, with misidentified nodes more broadly distributed.
+As illustrated in the figure, comparatively, SecFFT outperforms other mechanisms in handling various attack.
+SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes.
+Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed.
 Notably, FoolsGold exhibits the highest misidentification rate, demonstrating suboptimal defense performance in managing complex attack scenarios.
-Comparatively, SecFFT outperforms other methods in handling various attack types, effectively reducing the misidentification rate and demonstrating superior generalization ability and accuracy.
 
@@
 Table \ref{tab:detect} provides a detailed quantitative analysis of the classification metrics for the four defense mechanisms against different strategies.
-It is clear that SecFFT not only consistently preserves its strong backdoor attack mitigation capability but also achieves the best detection accuracy, with significantly reduced false positive rates, ensuring reliable and robust performance.\textcolor{red}{ "Acc" refers to accuracy, which measures the proportion of correct predictions; "Rec" stands for recall, representing the model's ability to correctly identify positive instances; "FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; "FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; "AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and "MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}
+It is clear that SecFFT not only consistently preserves its strong backdoor attack mitigation capability but also achieves the best detection accuracy, with significantly reduced false positive rates, ensuring reliable and robust performance.
+
+% \begin{table}[h!]
+% \small
+% \centering
+% \caption{Metrics results with different attack and defense methods.}
+% \resizebox{\columnwidth}{!}{%
+% \begin{tabular}{c|c|c|c|c|c|c|c}
+% \hline
+% Strategy & Defense & Acc. & Rec. & FPR & FNR & AUC & MCC \\ \hline
+
+% \multirow{4}{*}{None} & Foolsgold & 0.90 & 0.67 & 0.00 & 0.33 & 0.83 & 0.76 \\
+%                       & FLTrust   & 0.82 & 0.40 & 0.00 & 0.60 & 0.70 & 0.56 \\
+%                       & Flame     & 0.90 & 0.67 & 0.00 & 0.33 & 0.83 & 0.76 \\
+%                       & SecFFT    & \textbf{1.00} & \textbf{1.00} & 0.00 & \textbf{0.00} & \textbf{1.00} & \textbf{1.00} \\ \hline
+
+% \multirow{4}{*}{Size} & Foolsgold & 0.92 & 0.80 & 0.03 & 0.20 & 0.88 & 0.72 \\ 
+%                       & FLTrust   & 0.82 & 0.53 & 0.06 & 0.47 & 0.74 & 0.61 \\ 
+%                       & Flame     & 0.92 & 0.73 & \textbf{0.00} & 0.27 & 0.87 & 0.78 \\ 
+%                       & SecFFT    & \textbf{0.98} & \textbf{0.93} & \textbf{0.00} & \textbf{0.07} & \textbf{0.96} & \textbf{0.91} \\ \hline
+
+% \multirow{4}{*}{Angle} & Foolsgold & 0.88 & 0.73 & 0.06 & 0.27 & 0.84 & 0.68 \\ 
+%                        & FLTrust   & 0.86 & 0.60 & 0.03 & 0.40 & 0.80 & 0.65 \\ 
+%                        & Flame     & 0.90 & 0.67 & \textbf{0.00} & 0.33 & 0.83 & 0.76 \\ 
+%                        & SecFFT    & \textbf{0.96} & \textbf{0.87} & \textbf{0.00} & \textbf{0.13} & \textbf{0.94} & \textbf{0.88} \\ \hline
+% \end{tabular}
+% }
+% \vspace{1em}
+% \begin{tablenotes}
+% \scriptsize
+% \item ``Acc." stands for Accuracy, ``Rec." for Recall, ``FPR" for False Positive Rate, ``FNR" for False Negative Rate, ``AUC" for Area Under Curve, and ``MCC" for Matthews Correlation Coefficient.
+The strategies are abbreviated as ``None" (No strategy), ``Size" (Size-limited strategy), and ``Angle" (Angle-limited strategy).
+% \end{tablenotes}
+% \label{tab:detect}
+% \end{table}
 
@@
 \centering
-\caption{Metrics results with different attack and defense methods.}
+\caption{\textcolor{red}{Metrics results with different attack and defense methods.}}
 \resizebox{\columnwidth}{!}{%
@@
 \hline
-Strategy & Defense & Acc. & Rec. & FPR & FNR & AUC & MCC \\ \hline
-
-\multirow{4}{*}{None} & Foolsgold & 0.90 & 0.67 & 0.00 & 0.33 & 0.83 & 0.76 \\
-                      & FLTrust   & 0.82 & 0.40 & 0.00 & 0.60 & 0.70 & 0.56 \\
-                      & Flame     & 0.90 & 0.67 & 0.00 & 0.33 & 0.83 & 0.76 \\
-                      & SecFFT    & \textbf{1.00} & \textbf{1.00} & 0.00 & \textbf{0.00} & \textbf{1.00} & \textbf{1.00} \\ \hline
-
-\multirow{4}{*}{Size} & Foolsgold & 0.92 & 0.80 & 0.03 & 0.20 & 0.88 & 0.72 \\ 
-                      & FLTrust   & 0.82 & 0.53 & 0.06 & 0.47 & 0.74 & 0.61 \\ 
-                      & Flame     & 0.92 & 0.73 & \textbf{0.00} & 0.27 & 0.87 & 0.78 \\ 
-                      & SecFFT    & \textbf{0.98} & \textbf{0.93} & \textbf{0.00} & \textbf{0.07} & \textbf{0.96} & \textbf{0.91} \\ \hline
-
-\multirow{4}{*}{Angle} & Foolsgold & 0.88 & 0.73 & 0.06 & 0.27 & 0.84 & 0.68 \\ 
-                       & FLTrust   & 0.86 & 0.60 & 0.03 & 0.40 & 0.80 & 0.65 \\ 
-                       & Flame     & 0.90 & 0.67 & \textbf{0.00} & 0.33 & 0.83 & 0.76 \\ 
-                       & SecFFT    & \textbf{0.96} & \textbf{0.87} & \textbf{0.00} & \textbf{0.13} & \textbf{0.94} & \textbf{0.88} \\ \hline
+\textcolor{red}{Strategy} & \textcolor{red}{Defense} & \textcolor{red}{Acc.} & \textcolor{red}{Rec.} & \textcolor{red}{FPR} & \textcolor{red}{FNR} & \textcolor{red}{AUC} & \textcolor{red}{MCC} \\ \hline
+
+\multirow{4}{*}{\textcolor{red}{None}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.90} & \textcolor{red}{0.67} & \textcolor{red}{0.00} & \textcolor{red}{0.33} & \textcolor{red}{0.83} & \textcolor{red}{0.76} \\
+                      & \textcolor{red}{FLTrust}   & \textcolor{red}{0.82} & \textcolor{red}{0.40} & \textcolor{red}{0.00} & \textcolor{red}{0.60} & \textcolor{red}{0.70} & \textcolor{red}{0.56} \\
+                      & \textcolor{red}{Flame}     & \textcolor{red}{0.90} & \textcolor{red}{0.67} & \textcolor{red}{0.00} & \textcolor{red}{0.33} & \textcolor{red}{0.83} & \textcolor{red}{0.76} \\
+                      & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textcolor{red}{0.00} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\ \hline
+
+\multirow{4}{*}{\textcolor{red}{Size}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.92} & \textcolor{red}{0.80} & \textcolor{red}{0.03} & \textcolor{red}{0.20} & \textcolor{red}{0.88} & \textcolor{red}{0.72} \\
+                      & \textcolor{red}{FLTrust}   & \textcolor{red}{0.82} & \textcolor{red}{0.53} & \textcolor{red}{0.06} & \textcolor{red}{0.47} & \textcolor{red}{0.74} & \textcolor{red}{0.61} \\ 
+                      & \textcolor{red}{Flame}     & \textcolor{red}{0.92} & \textcolor{red}{0.73} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.27} & \textcolor{red}{0.87} & \textcolor{red}{0.78} \\
+                      & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{0.98}} & \textbf{\textcolor{red}{0.93}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.07}} & \textbf{\textcolor{red}{0.96}} & \textbf{\textcolor{red}{0.91}} \\ \hline
+
+\multirow{4}{*}{\textcolor{red}{Angle}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.88} & \textcolor{red}{0.73} & \textcolor{red}{0.06} & \textcolor{red}{0.27} & \textcolor{red}{0.84} & \textcolor{red}{0.68} \\
+                       & \textcolor{red}{FLTrust}   & \textcolor{red}{0.86} & \textcolor{red}{0.60} & \textcolor{red}{0.03} & \textcolor{red}{0.40} & \textcolor{red}{0.80} & \textcolor{red}{0.65} \\ 
+                       & \textcolor{red}{Flame}     & \textcolor{red}{0.90} & \textcolor{red}{0.67} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.33} & \textcolor{red}{0.83} & \textcolor{red}{0.76} \\
+                       & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{0.96}} & \textbf{\textcolor{red}{0.87}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.13}} & \textbf{\textcolor{red}{0.94}} & \textbf{\textcolor{red}{0.88}} \\ \hline
 \end{tabular}
@@
 \end{tablenotes}
-
 \label{tab:detect}
 \end{table}
-
-% \begin{table}[h!]
-% \small
-% \centering
-% \begin{tabular}{c|c|c|c|c|c|c|c|c|c}
-% \hline
-% \makecell{Attack \\ strategy} & Defense & Accuracy & Precision & Recall & \makecell{Specificity} & FPR & FNR & AUC & MCC \\ \hline
-
-% \multirow{4}{*}{\makecell{No \\ strategy}} & Foolsgold & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\
-%                       & FLTrust   &  0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\
-%                       & Flame     &  0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\
-%                       & SecFFT    &  \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & \textbf{0.00} & \textbf{1.00} & \textbf{1.00} \\ \hline
-
-% \multirow{4}{*}{\makecell{Size-limited \\ strategy}} & Foolsgold &  0.92 & 0.92 & 0.80 & 0.97 & 0.03 & 0.20 & 0.88 & 0.72 \\ 
-%                       & FLTrust   & 0.82 & 0.80 & 0.53 & 0.94 & 0.06 & 0.47 & 0.74 & 0.61 \\ 
-%                       & Flame     & 0.92 &1.00 & 0.73 & 1.00 & 0.00 & 0.27 & 0.87 & 0.78 \\ 
-%                       & SecFFT    & \textbf{0.98} & 1.00 & \textbf{0.93} & 1.00 & 0.00 & \textbf{0.07} & \textbf{0.96} & \textbf{0.91} \\ \hline
-
-% \multirow{4}{*}{\makecell{Angle-limited \\ strategy}} & Foolsgold &  0.88 & 0.85 & 0.73 & 0.94 & 0.06 & 0.27 & 0.84 & 0.68 \\ 
-%                        & FLTrust   &  0.86 & 0.90 & 0.60 & 0.97 & 0.03 & 0.40 & 0.80 & 0.65 \\ 
-%                        & Flame     &  0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ 
-%                        & SecFFT    &  \textbf{0.96} & 1.00 & \textbf{0.87} & 1.00 & 0.00 & \textbf{0.13} & \textbf{0.94} & \textbf{0.88} \\ \hline
-% \end{tabular}
-% \vspace{1em}
-% \caption{Classification metrics results with different attack and defense methods}\label{tab:detect}
-% \end{table}
-
-% \begin{table*}[h!]
-% \small
-% \centering
-% \begin{tabular}{c|c|c|c|c|c|c|c|c|c|c|c|c|c}
-% \hline
-% \makecell{Attack \\ strategy} & Defense & TP & FP & TN & FN & Accuracy & Precision & Recall & \makecell{Specificity} & FPR & FNR & AUC & MCC \\ \hline
-
-% \multirow{4}{*}{\makecell{No \\ strategy}} & Foolsgold & 10 & 0 & 35 & 5 & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\
-%                       & FLTrust   & 6  & 0 & 35 & 9 & 0.82 & 1.00 & 0.40 & 1.00 & 0.00 & 0.60 & 0.70 & 0.56 \\
-%                       & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\
-%                       & SecFFT    & \textbf{15} & 0 & 35 & \textbf{0}  & \textbf{1.00} & 1.00 & \textbf{1.00} & 1.00 & 0.00 & \textbf{0.00} & \textbf{1.00} & \textbf{1.00} \\ \hline
-
-% \multirow{4}{*}{\makecell{Size-limited \\ strategy}} & Foolsgold & 12 & 1 & 34 & 3 & 0.92 & 0.92 & 0.80 & 0.97 & 0.03 & 0.20 & 0.88 & 0.72 \\ 
-%                       & FLTrust   & 8  & 2 & 33 & 7 & 0.82 & 0.80 & 0.53 & 0.94 & 0.06 & 0.47 & 0.74 & 0.61 \\ 
-%                       & Flame     & 11 & 0 & 35 & 4  & 0.92 &1.00 & 0.73 & 1.00 & 0.00 & 0.27 & 0.87 & 0.78 \\ 
-%                       & SecFFT    & \textbf{14} & 0 & 35 & \textbf{1}  & \textbf{0.98} & 1.00 & \textbf{0.93} & 1.00 & 0.00 & \textbf{0.07} & \textbf{0.96} & \textbf{0.91} \\ \hline
-
-% \multirow{4}{*}{\makecell{Angle-limited \\ strategy}} & Foolsgold & 11 & 2 & 33 & 4 & 0.88 & 0.85 & 0.73 & 0.94 & 0.06 & 0.27 & 0.84 & 0.68 \\ 
-%                        & FLTrust   & 9  & 1 & 34 & 6 & 0.86 & 0.90 & 0.60 & 0.97 & 0.03 & 0.40 & 0.80 & 0.65 \\ 
-%                        & Flame     & 10 & 0 & 35 & 5  & 0.90 & 1.00 & 0.67 & 1.00 & 0.00 & 0.33 & 0.83 & 0.76 \\ 
-%                        & SecFFT    & \textbf{13} & 0 & 35 & \textbf{2}  & \textbf{0.96} & 1.00 & \textbf{0.87} & 1.00 & 0.00 & \textbf{0.13} & \textbf{0.94} & \textbf{0.88} \\ \hline
-% \end{tabular}
-% \vspace{1em}
-% \caption{Classification metrics results with different attack and defense methods}\label{tab:detect}
-% \end{table*}
-
-% As a preeminent collaborative artificial intelligence paradigm, Federated Learning (FL) has garnered substantial research focus \cite{ETT2}. 
-% By effectively mobilizing a substantial number of participants with a discrete distribution, FL can concurrently enhance learning performance, resource utilization, and data security. 
-% Besides, as intelligent applications proliferate, concerns regarding fairness-aware federated learning (FFL) have also captured significant attention \cite{zhou2021towards-KDDtutorial-FFL}.
-Due to the agnostic of multiple data sources, models trained through FL may exhibit discriminatory tendencies toward specific features or demographic groups, such as gender, race, and occupation (e.g., COMPAS recidivism algorithm \cite{angwin2022machine} and facial recognition system \cite{raji2019actionable}).
-In response to this inherent deficiency, various FFL algorithms, such as FairFed \cite{ezzeldin2023fairfed}, Ditto \cite{li2021ditto}, and FairFL \cite{zhang2020fairfl}, have been proposed.
-
-% %安全问题很重要
-% \subsection{Mutual reliability problem of FFL}
-% Meanwhile, along with the continual emergence of novel attack techniques, such as gradient leakage and model poisoning \cite{fang2020local}, the \textit{``trust crisis''} \cite{zhou2022multi} has become a critical bottleneck in determining FFL deployment capabilities \cite{rodriguez2023survey}.
-Establishing a robust \textit{mutual reliability} relationship between the FL aggregator (parameter server) and local participants has proven challenging \cite{zhou2022multi}.
-To be specific, on the one hand, concerns about data sharing leading to privacy breaches (\textit{aggregator's reliability}) \cite{wang2021variational} raise apprehensions among owners of data and computational resources, significantly diminishing enthusiasm for collaborative learning participation and giving rise to the phenomena of ``isolated data islands''.
-On the other hand, PSs are troubled by the difficulty of promptly and accurately thwarting stealthy attackers hidden among a vast client base.
-This concern  (\textit{client nodes' reliability}) raises the specter of manipulation or even invalidation of the entire model, resulting in severe economic and intellectual property losses.
-
-% %列举几个特点，导致现有安全技术不能适用
-% %尽管多种最新的安全增强技术能够取得显著的防御效果，但攻击者并不能
-% \subsection{Characteristics and motivation of mutual reliable FFL in heterogeneous UAV networks}
-% With the advancement of integrated sensing, computation and communication (ISCC) \cite{he2023integrated}, and the space-air-ground integrated network (SAGIN) \cite{shen2023survey}, unmanned aerial vehicle (UAV) networks have played a crucial role in various domains such as post-disaster reconstruction, emergency temporary communication, and medical monitoring \cite{lu2023uav}.
-FLs based on UAV networks have also found widespread applications \cite{ETT1, ETT3, pandya2023federated}.
-However, despite the proposal of various secure FL technologies, the inherent characteristics of UAV networks continue to pose significant challenges in establishing mutual reliability for FFL in UAV environments.
-Specifically, these challenges encompass the following aspects:
-
-% %异构：大范围异构，小范围相似.因此
-% \textbf{1) Heterogeneity among UAV nodes:} As illustrated in Figure \ref{fig1:UAV-Network}, constrained by the mobility and patrol paths of UAVs, individual nodes are often limited to conducting data collection within a specific regional scope.
-Hence, even when employing identical equipment, the data distributions among UAV nodes across the entire network exhibit significant heterogeneity, while UAVs within the same area are similar.
-Therefore, various existing reliable FL technologies lacking adaptive considerations (such as Krum \cite{blanchard2017machine-krum}, Baffle \cite{andreina2021baffle}, and AGRamplifier \cite{gong2023agramplifier}) can lead to substantial accuracy losses.
-
-% %资源受限：因此高消耗的安全策略并不能适用  高计算消耗和带宽占用的安全技术（例如，加密）
-% \textbf{2) Resource limitation of UAV devices:} As UAV nodes function as mobile devices and bear substantial flight-related loads, their communication and energy resources are relatively constrained.
-The efficiency of FFL training is equally important.
-Consequently, solutions integrating cryptography, auxiliary training, multi-round detection, or other security mechanisms with high computational costs and bandwidth utilization (e.g., ShieldFL \cite{ma2022shieldfl}, AFA \cite{munoz2019byzantine-AFA}, and FLdetector \cite{zhang2022fldetector}) are not applicable for real-world deployment.
-
-% %我们的目标是实现（1）异构容忍的FFL框架（2）强隐私保护的个性化训练交互（3）抗污染的可信评估
-% The aforementioned characteristics distinguish the reliable FFL in heterogeneous UAV networks from existing secure FFL technologies, thereby motivating the establishment of the following new criteria for its enhancement:
-
-% \textbf{1) Heterogeneity-tolerant FFL framework:} Suitable nodes from the highly heterogeneous UAV networks can be organized promptly to efficiently fulfill arbitrary fairness-aware FL tasks, which also mitigates redundant computational energy consumption and accuracy loss induced by heterogeneity.
-
-% \textbf{2) Privacy-preserving personalized training:} Throughout the iteration training and interaction process, sample-level privacy protection must be implemented to prevent the leakage of sensitive information.
-Additionally, considering the resource constraints of UAV nodes, computational and bandwidth demands should be limited.
-
-% \textbf{3) Poisoning-resilient credit evaluation:} In addition to robust defense capabilities against various poisoning attacks, compatibility with heterogeneity and privacy requisites is also essential.
-In other words, without compromising the effectiveness of privacy guarantee, heterogeneous benign UAV nodes should be treated equally during the whole FFL workflow.%Achieving fairness among heterogeneous benign users without compromising the effectiveness of privacy protection is a crucial aspect.
-
-% \subsection{Our solution and contributions}
-% %解决方案
-% % Hence, in this paper, we propose mutually reliable FFL (MR-FFL), a stratified community-based framework to facilitate privacy protection (FFL aggregator's reliability) and poisoning elimination (client nodes' reliability) jointly for FFL in heterogeneous UAV networks.
-% % We first divide UAV nodes into both peer communities and colleague communities according to cross-participant similarity and task-oriented fitness, respectively. 
-% % Thus, the arbitrarily settled learning tasks following fair principles can be efficiently completed by fine-tuned colleague communities, even in the presence of a large degree of heterogeneity among peer communities.
-% Therefore, this paper proposes mutual reliable FFL (MR-FFL), a stratified community-based framework that collectively promotes privacy protection during data sharing (reliability of FFL aggregators) and poisoning elimination during model aggregation (reliability of client nodes) in heterogeneous UAV networks.
-The contributions of the proposed MR-FFL are three-fold:
-
-% %贡献
-
-% \begin{itemize}
-%     %\item In light of shuffling-based MTD \cite{zhou2022multi} strategies, we propose a credit to identify the malicious attackers without compromising of privacy guarantees, which is also one of the design inspirations of our framework.
-%     \item Initially, UAV nodes are partitioned into peer communities and colleague communities based on cross-participant similarity and task-oriented adaptability.
-Thus, adhering to fairness principles, any arbitrarily determined learning task can be effectively accomplished through carefully selected colleague communities, even in the presence of significant heterogeneity among UAV nodes, while peer communities provide an amplified privacy guarantee.
-%     %随后，我们提出了PSDP的隐私模糊化方式进行自适应训练，通过参数动态约束差分隐私敏感度，从而在同等隐私保护水平下大幅降低异构环境下的噪声损失。
-%     \item Subsequently, inspired by cross-silo privacy protection, we introduce the new privacy perturbation notion of peer community-specific differential privacy (PSDP) with changeable privacy budget.
-Through dynamically constraining the DP sensitivity within each peer community, PSDP significantly reduces noise loss in heterogeneous environments under equivalent privacy protection levels.
-%     %此外，我们提出了基于三值主观逻辑模型的信用评估，分别抽离投毒攻击的“操纵”（相似度）和“破坏”（准确度）行为进行群体参与的综合长效评价，从而有效抵御多种隐蔽的投毒攻击范式。
-%     \item Furthermore, we propose a new credit evaluation based on the ternary subjective logic model.
-This evaluation effectively integrates comprehensive and long-term assessments with the collective participation of heterogeneous UAV nodes, specifically extracting the ``manipulation'' (similarity) and ``disruption'' (accuracy) behaviors of poisoning attacks.
-This approach proves effective in defending against various covert poisoning attack paradigms.
-%     %\item Then, we integrate community-specific differential privacy into the MR-FFL process, to achieve privacy amplification as well as efficient and personal collaborative training at the same time.
-%     %\item More importantly, we proposed a community-based credit evaluation to resist poisoning attacks in heterogeneous environments.
-
-% \end{itemize}
-
-% %本文组织结构
-% The remainder of this paper is organized as follows: The related works are reviewed in Section \uppercase\expandafter{\romannumeral2}.
-The system model is presented in Section \uppercase\expandafter{\romannumeral3}.
-Then, stratified community construction, adaptive training, and credit evaluation modules are expounded upon in Section \uppercase\expandafter{\romannumeral4} to \uppercase\expandafter{\romannumeral6}, respectively, providing a detailed account of availability, privacy, and integrity for FFL in heterogeneous UAV networks.
-Section \uppercase\expandafter{\romannumeral7} presents experimental results.
-Finally, Section \uppercase\expandafter{\romannumeral8} concludes this paper.
-%and briefly explores future directions.
-
-% \section{Related work}
-
-% % \begin{tabular}{|p{0.4\textwidth}|p{0.5\textwidth}|}
-% % \hline
-% % \textbf{论文的期刊名、年份、引用} & \textbf{简介} \\
-% % \hline
-% % 期刊名1, 2024, 引用1 & 这篇论文讨论了...... \\
-% % \hline
-% % 期刊名2, 2023, 引用2 & 本研究着重于...... \\
-% % \hline
-% % 期刊名3, 2022, 引用3 & 本文提出了...... \\
-% % \hline
-% % \end{tabular}
-
-% According to the three basic tenets of information security \cite{zhou2021augmented-globecom}, in this section, we systematically review the most crucial hindrances of existing FFL solutions in UAV networks: \textit{availability}, \textit{confidentiality}, and \textit{in tegrity} problems, which we settled in following sections, respectively.
-% \subsection{FFL in heterogeneous environments (availability)}
-% To accomplish learning tasks and ensure the availability of FFL in heterogeneous environments, existing solutions can adopt debiasing on the client or server side.
-% \subsubsection{Server-side debiasing} %全局化
-% As the name indicated, server-side debiasing methods usually monitor the composition of training data and design new loss functions like Ratio loss \cite{wang2021addressing} to mitigate the impact of heterogeneity.
-% Besides, FairFed \cite{ezzeldin2023fairfed} adjusts the aggregation weights of heterogeneous participants based on equal opportunity difference (EOD).
-Hence, clients can conduct different debiasing processes.
-% Likewise, FedProto \cite{tan2022fedproto} regularizes the training of local models with the aid of abstract class prototypes from the server. 
-% To handle the performance degradation caused by heterogeneous and long-tailed data, CReFF\cite{shang2022federated} re-trains the biased classifier with federated features in a privacy-preserving manner.
-% Different from the above methods, several clustered FLs provide separate models for heterogeneous clients \cite{sattler2020clustered-CFL}, which can incur exponentially growing computation costs.
-% \subsubsection{Client-side debiasing} %个性化
-% Diverging from server-side debiasing, client-side debiasing methods primarily enhance accuracy by altering the local model \cite{tan2022towards}. 
-% For example, while retaining the standard FL mechanism as the inner optimizer, FairBatch \cite{roh2020fairbatch} further adds an outer optimizer to select minibatch sizes and improve model fairness adaptively.
-Similarly, Ditto \cite{li2021ditto} develops a regular term to optimize the local models without changing global aggregation rules.
-The robustness and fairness are jointly improved.
-% Moreover, Mohri \textit{et al.} \cite{mohri2019agnostic} propose agnostic federated learning (AFL) and prove its fairness using data-dependent Rademacher complexity guarantees.
-
-% %总结：现有FFL有两大问题，首先是效率不佳，往往需要多轮训练，不适合于能量受限的UAV network。其次是缺乏考虑对联邦学习可信技术的兼容。
-% To summarize, existing FFLs encounter two drawbacks.
-Firstly, they exhibit unsatisfactory efficiency, often necessitating multiple training rounds, rendering them unsuitable for energy-constrained UAV networks.
-Secondly, the consideration for compatibility with reliable technologies is insufficient.
-% \subsection{Reliability of information sharing (confidentiality)}%隐私安全
-% \subsubsection{Cryptography solutions} 
-% Homomorphic encryption (HE) and other cryptographic methods naturally serve as suitable privacy protection measures.
-For instance, ShieldFL \cite{ma2022shieldfl} employs secure cosine similarity to measure the distance between two encrypted gradients, utilizing dual-gate HE to resist model poisoning.
-BatchCrypt \cite{zhang2020batchcrypt} further enhances HE efficiency by incorporating batch gradient encoding and holistic encryption, effectively reducing training time and communication overhead.
-Additionally, FairFL \cite{zhang2020fairfl} adopts the principled deep multi-agent reinforcement learning framework and secure information aggregation protocol to simultaneously optimize the accuracy and the fairness of FFL while respecting the strict privacy constraints of the clients.
-% Besides, Lyu \textit{et al.} \cite{lyu2020towards} develop a local credibility mutual evaluation mechanism to guarantee fairness, and a three-layer onion-style encryption scheme to guarantee both accuracy and privacy.
-% \subsubsection{Obfuscation solutions}
-
-% In comparison to encryption, obfuscation approaches such as differential privacy (DP) do not introduce excessive overhead or extensive mechanism modifications, thus garnering significant attention \cite{padala2021federated}.
-For instance, Wei \textit{et al.} \cite{wei2021low} consider both general training performance and individual client privacy requirements to mitigate latency on wireless channels, addressing challenges posed by channel fading and interference in unknown network environments.
-Furthermore, considering potential model distortion from obfuscation techniques, privacy amplification as Shuffle \cite{girgis2021shuffled} can enhance the deployment capabilities of privacy protection.
-NbAFL \cite{wei2020federated-NbAFL} further diminishes the accuracy loss associated with DP by injecting secondary noise into the uplink and downlink channels.
-
-% %总结：密码学方法通信量和计算量过大，而DP方法缺乏对异构考量
-% Upon analysis, privacy-preserving information-sharing methods based on cryptography often incur excessive communication and computational overhead.
-On the other hand, methods relying on obfuscation like differential privacy lack adaptability to heterogeneous network environments, usually resulting in significant accuracy losses.
-% \subsection{Reliability of model aggregation (integrity)}%model安全
-% To resist the stealthy yet destructive poisoning attacks \cite{lyu2023poisoning}, multiple defense methods are proposed, which can be divided into the following types based on the realization concepts:
-% \subsubsection{Mitigation-oriented technologies} 
-% To ensure the integrity of the aggregated model, various robust FL methods, such as Byzantine-robustness, have been proposed.
-For instance, Krum \cite{blanchard2017machine-krum} selects partial neighboring nodes as references, enabling the algorithm to choose updates with the highest consensus for the next iteration.
-Diverging from Krum's approach of selecting only one update, FABA \cite{xia2019faba} employs gradient outlier computation to discard few gradients while retaining the majority of clients' training results, significantly enhancing learning speed.
-Building upon these methods, Gong \textit{et al.} devise AGRamplifier \cite{gong2023agramplifier}, which enhances the "morality" of local updates by identifying the most suppressive features in each gradient update.
-This augmentation further elevates model robustness, fidelity, and efficiency.
-
-% \subsubsection{Detection-oriented technologies} 
-% An alternative approach to fortify against poisoning is the direct detection of the learning model using a validation dataset or predefined rules.
-For instance, Zeno \cite{xie2019zeno} evaluates the stochastic descendant score for each gradient based on a validation dataset, selectively discarding gradients with low scores for the stochastic descendant.
-In contrast to relying on an auxiliary validation set, Baffle \cite{andreina2021baffle} capitalizes on the diverse datasets accessible across various clients by integrating a feedback loop into the FL process.
-Besides, Fldetector \cite{zhang2022fldetector} anticipates a client's model update during each iteration by leveraging historical model updates and flags a client as potentially malicious if the received model update contradicts the predicted update.
-% It is noteworthy that detection-centric solutions entail additional training costs and may not identify some zero-day attacks.
-
-% \subsubsection{Credit-oriented technologies} 
-% %鉴于联邦学习是协作式、多轮次的交互过程，通过维护信用评价机制同样可以很好地清除恶意用户。例如，Kang等人使用多权重主观逻辑模型设计基于声誉的可靠联邦学习用户选择方案，并利用区块链实现声誉管理。在不需要辅助验证数据集的情况下，Xu等人提出余弦梯度Shapley值来评估每个智能体上传的模型参数更新/梯度的期望边际贡献，以区别对待。Tan等人提出了一种基于声誉感知的随机整数规划的FL客户选择方法，可以最优地选择和补偿具有不同声誉档案的客户，从而对抗潜在的异常行为。
-% Considering that FL is a collaborative and iterative process, the credit evaluation mechanism proves effective in poisoning resistance.
-For instance, Kang \textit{et al.} \cite{credit1-kang2019IOT} design a reputation-based reliable scheme utilizing a multi-weight subjective logic model, and implement reputation management through blockchain.
-Xu \textit{et al.} \cite{xu2020reputation, xu2021gradient}, without the need for auxiliary verification datasets, introduced the cosine gradient Shapley value to assess the model parameter updates/gradients uploaded by each client.
-Tan \textit{et al.} \cite{tan2022reputation} propose a reputation-aware stochastic integer programming client selection method, selecting and compensating clients with varying reputation profiles to counter potential anomalous behavior.
-
-% %总结：现有方案缺乏对隐私的考量，计算量过大
-% In general, existing solutions often struggle to achieve a satisfactory balance between privacy and defensive performance, while also lacking adaptability to heterogeneous and dynamically changing environments.
-Furthermore, some methods exhibit relatively large computational overhead, imposing a non-negligible burden on UAV nodes.
-
-% \section{System model \& Preliminaries}
-% %%symbols 表格
-% \begin{table}[!t]
-% {
-% \renewcommand{\arraystretch}{1.2}
-% \caption{Summary of Main Notation}
-% \label{notations}
-% \vspace{0em}
-% \centering
-% \begin{tabular}{| c || l |}
-% \hline
-% \textbf{Symbol} & \multicolumn{1}{c |}{\textbf{Description}}\\
-%     \hline
-%     $U_i,\mathcal{D}_i$ & The $i$-th UAV devices and its dataset\\
-%     \hline
-%     $n^{s_{m}, i},\mathcal{P}^i$ & The size and normalized distribution of $\mathcal{D}_i$\\
-%     \hline
-%     $\mathcal{P}^{Tar}, w$ & Target distribution and model of learning task $Job$\\
-%     \hline
-%     $T$ & The maximum communication rounds of $Job$\\
-%     \hline
-%     $C,K$ & The set and number of all peer communities\\
-%     \hline
-%     $S,M$ & The set and number of all colleague communities\\
-%     \hline
-%     %$L$ & The number of clients in each super node\\
-%     %\hline
-%     $c_k$ & The $k$-th peer community\\
-%     \hline
-%     $s_m$ & The $m$-th colleague community\\ 
-%     \hline
-%     $\Delta \widetilde{\omega}_{t}^{s_{m},i}$ & The weight updates from $U_i \in s_m$ in round $t$\\
-%     \hline
-%     $p^{s_{m}, i}$ & The aggregation coefficient for $U_i$ within $s_m$\\
-%     \hline
-%     $\Delta\widetilde{\omega}_{t}^{s_{m}}$ & The weight updates from $s_m$ in round $t$\\
-%     \hline
-%     $p^{s_{m}}$ & The aggregation coefficient for $\Delta\widetilde{\omega}_{t}^{s_{m}}$ from $s_m$\\
-%     \hline
-%     $E_k$ & The clipping bound of peer community $c_k$\\
-%     \hline
-%     $Sen_k$ & The maximum sensitivity of $c_k$\\
-%     \hline
-%     $\varepsilon_k,\delta_k$& The parameters of differential privacy \\
-%     \hline
-%     $L$& The minimum size of colleague community\\
-%     \hline
-%     $\alpha^{a,b}_{t}$& The cosine similarity between $a$ and $b$\\
-%     \hline
-%     $PI^{c_k \rightarrow i}_{t}$ & The positive interaction between $c_k$ and $U_i$\\
-%     \hline
-%     $NI^{c_k \rightarrow i}_{t}$& The positive interaction between $c_k$ and $U_i$\\
-%     \hline
-%     $\Upsilon^{c_k \rightarrow i}_{t}$& The peer reputation opinion vector of $c_k$\\
-%     \hline
-%     $\Phi^{c_k \rightarrow i}_{t}$& $c_k$'s credit evaluation towards $U_i$ in round $t$\\
-%     \hline
-%     $\Upsilon^{s_m}_{t}$ & The colleague reputation opinion vector towards $s_m$\\
-%     \hline
-%     $\Phi^{s_m \rightarrow i}_{t}$& The colleague credit evaluation for $\forall U_i \in s_m$\\
-%     \hline
-%     $\Upsilon^{i}_{t},\Phi^{i}_{t}$& The comprehensive reputation and credit of $U_i$\\
-%     \hline
-%     $\psi^{i}_t$& The fairness-guaranteed selection probability\\
-%     \hline
-%     \end{tabular}
-%         }
-%      \vspace{-1.5em}
-%      \end{table}
-
-% \textbf{Heterogeneous UAV network scenario.} 
-% %\subsection{Network scenario}
-% %对于一个多无人机多任务联邦学习场景，有一个服务器与N个无人机，设无人机集合为$U=\{U_i\}$，$\vert\vert U\vert\vert=N$。所有无人机获取的数据集集合为$D=\{D_i\}$，第k个无人机的数据分布为$\mathcal{P}^k\in \mathbb{t}^F$，其中$F$为特征维度；任务场景集合为$T$，其中第k个任务场景中的数据分布为$\mathcal{P}^{tar_k}$。在同一现实场景中，无人机采集到的数据通常是类似的，即对于某个场景的分布$\phi$，所有属于该现实场景的设备集合$B'$均满足$\exists \epsilon\in \mathbb{t}^F,\forall k \in B', ||\phi-\mathcal{P}^k||_1 \leq \epsilon$。
-% As shown in Figure \ref{fig1:UAV-Network}, assume a multi-UAV multi-task federated learning scenario for the classification problems.
-There exists a parameter server (PS)/aggregator (normally equipped with ground base station) and $N$ UAV nodes (UN) $\mathbf{U}\triangleq\{U_1,...U_i,...U_N\}$.
-Each UN $U_i$ has local dataset $\mathcal{D}_i\triangleq\{(\xi_{i,1},y_{i,1}),...(\xi_{i,j},y_{i,j}),...(\xi_{i,n_i},y_{i,n_i})|y\in \mathbb{R}^F\}$ sampled following distribution $\varphi_q$.
-%with varied size $n_i$.
-% Here $x$ and $y$ are raw data and label, respectively.
-As the nodes with overlapped aerial areas or patrol routines may have similar data distributions, we have $\exists \epsilon\in \mathbb{R}^F,\forall U_i, U_j \sim \phi_q, ||\mathcal{P}^i-\mathcal{P}^j||_p \leq \epsilon^{\prime}$, where $\mathcal{P}^i$ is the normalized distribution of $\mathcal{D}_i$.
-For the highly heterogeneous networks, we also have $\exists U_i \sim \phi_{q^{\prime}}, U_j \sim \phi_q,||\mathcal{P}^i-\mathcal{P}^j||_p \gg \epsilon^{\prime}$ in the same time.
-
-% %\subsection{Threat model}
-% %值得一提的是，方便起见，我们此处仅以多分类问题中的数据类别作为公平性感知针对的对象，实际使用中可以通过特征extractor扩展到数据包含的任意抽象特征。此外，我们以范数差异度作为公平性衡量标准，实际应用中，也可以选取AIDD、DSF、SF等衡量方式并在特定方面取得更好的效果。
-% It is crucial to highlight that, for better understanding, our focus in this paper is solely on the data distribution of multi-classification problems as the target for fairness awareness.
-In practical scenarios, this concept can be easily extended to any abstract features derived from specific demographic groups through feature extractor as exemplified in \cite{shuai2022balancefl}.
-Furthermore, our chosen metric for fairness evaluation is the norm difference.
-However, other alternative fairness measures such as QCID \cite{yang2021federated}, ratio loss \cite{wang2021addressing}, and cross-entropy loss \cite{mohri2019agnostic} can be employed, depending on specific requirements, to attain more favorable results.
-
-% \textbf{Fairness-aware learning task.} Without loss of generality, the fairness-aware learning task can be denoted with the quadruple as $Job\triangleq(w,\mathcal{P}^{tar},t_0, T)$, which consists of the model $w$, target distribution $\mathcal{P}^{tar}$, arrival time $t_0$, and duration $T$.
-Different from existing solutions designed for certain $\mathcal{P}^{tar}$ \cite{li2022data,zeng2022heterogeneous,hiessl2022cohort}, our method can adaptively choose and schedule suitable UAV groups when a new learning task arrives.
-
-% \textbf{Optimization objective.} We start with vanilla FL algorithms like FedAvg \cite{li2019convergence-fedavg} without consideration of heterogeneity.
-The optimization objective can be expressed as:
-% %考虑一个联邦学习场景，有1个服务器和$N$个客户。具体来说，客户i的本地数据集为$D_{i}$，其类别分布被定义为$\mathcal{P}^{c_{k},i}$。不同客户的本地数据类别分布高度异构，与全局类别分布$\mathcal{P}^{real}$有巨大差距。为了最小化全局损失函数，得到普适的全局模型，我们有：
-% \begin{equation}
-%     w^{*}\triangleq \underset{w}{\arg \min } \sum_{i=1}^N p_i\mathcal{L}\left(w, \mathcal{D}_{i}\right) ,
-% \end{equation}
-% %其中，$\mathcal{L}_{i}(\cdot)$是客户i的由其本地经验风险得出的本地损失函数。然而，由于客户的数据间的高度异构性与客户数据分布与任务场景数据分布间的高度异构性，客户间的本地损失函数不尽相同，难以获得同时最小化各个模型经验风险的最优全局模型参数$w^{*}$并满足任务场景。因此，在上述场景中进行传统FL会导致全局模型无法正常收敛，无法得到满足任务场景的高性能全局模型。
-% where $\mathcal{L}(.)$ represents the loss function derived from the local empirical risk of $U_i$, $p_i$ is the aggregation weight.
-Due to the high heterogeneity among UAV nodes and the substantial mismatch between participants' data distributions and task requirements, obtaining the globally optimal model parameters $\omega^{*}$ that simultaneously minimize the empirical risks of each model and align with task requirements is challenging.
-%Thus, traditional Federated Learning (FL) in such scenarios leads to the global model failing to converge effectively, resulting in an inability to obtain a high-performance global model that satisfies task scenarios.
-
-% Hence, similar to the existing fair FL solutions in \cite{mohri2019agnostic,zhang2020fairfl,ezzeldin2023fairfed}, we define the optimization objective as follows:
-% \begin{equation}
-%     w^{*}\triangleq \underset{w}{\arg \min } \ \mathcal{L}_{FFL}(\omega)=\underset{(x, y) \sim \mathcal{P}^{Tar}}{\mathbb{E}}[\mathcal{L}{(\omega,(x, y))}]
-% \end{equation}
-% %（我这里想的是为了便于之后的凝聚聚类）此外，由于不同现实场景之间可能有较大的数据分布差异，与任务数据分布高度异构。为了最小化全局损失函数，得到适用于特定任务场景的全局模型，我们有：
-
-% \section{Stratified community construction in heterogeneous environment}\label{sec:community}
-% %为了实现高度异构的UAV节点集合与动态变化的学习任务之间的良好适配，我们提出了SCC。如图所示，该机制主要包含两个部分：PCC和CCC。其中PCC在网络初始化时运行一次，CCC则在每次收到新任务时运行一次。
-% To achieve a robust alignment between highly heterogeneous UAV nodes and dynamically evolving learning tasks, we propose the stratified community construction (SCC) mechanism.
-As illustrated in Figure \ref{fig2:framework}, SCC comprises two main components: peer community construction (PCC) and colleague community construction (CCC).
-PCC executes once during network initialization, while the CCC executes each time a new task is received.
-% \subsection{Peer community construction (PCC)}
-% Based on norm-based pair distance, we first cluster UAV nodes with similar data distributions into $K$ peer community $C=\{ c_{1}, \ldots, c_{K} \}$. The pair distance is calculated as:
-% \begin{equation}
-% d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}, \forall U_i,U_j\in \mathbf{U}.
-% \end{equation}
-
-% %基于客户的数据分布$\mathcal{P}^{i},i\in B$。我们用最大链接法对客户进行层次凝聚聚类。两个簇间的距离为它们中任意两个客户分布之间曼哈顿距离的最大值，当簇间距离大于合并阈值$\zeta$时停止合并，得到最终的聚类结果。由此可知同簇的任意客户分布之间的最大曼哈顿距离小于$\zeta$, 即$\forall i,j \in c, d_{i,j}<\zeta$。
-% Then, we employ the complete-linkage method to achieve agglomerative hierarchical clustering (AHC) among UAV nodes.
-The distance between two peer communities is defined as the maximum Euclidean distance between any two UNs' distributions.
-The clustering process ceases when the inter-community distance exceeds the merging threshold $\zeta$, resulting in the final outcome.
-Hence, the maximum distance between any pair of client distributions within the same PC is less than $\zeta$, i.e., $\forall U_i, U_j \in c_k, d_{i,j} < \zeta$, which is denoted as:
-% \begin{equation}\label{eq:peer-construct}
-%  C\triangleq \underset{c_{1} \cup c_{2} \cup \ldots c_{K}=C}{\arg \min} \left(\max _{\forall c_{k},c_{k'} \in C ,U_i \in c_{k}, U_j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .
-% \end{equation}
-
-% %根据上述公式，我们得到具有相似类别分布的$K$个簇$C=\{c_{1},\ldots,c_{K}\}$。可以计算每个簇的平均数据分布，簇$c$的平均数据分布$\mathcal{P}^{c}$计算为：
-% The average distribution of each peer community $c_k$ is:
-% \begin{equation}
-%     	 \mathcal{P}^{c_k}=\operatorname{norm}\left(\sum_{i \in c} n^{c,i} \mathcal{P}^{c,i} \right),
-% \end{equation}
-% %其中，$\mathcal{P}^{c,i}$是簇$c$中客户$i$的数据分布，$n^{c,i}$是簇$c$中客户$i$的数据量。为了保证隐私与数据安全，需要保证簇的个数，否则参与方将可能更容易推断出数据属于哪一簇。同时，当簇的数量较少时，每个簇代表的数据子集更大，这可能会导致更多的敏感信息聚集在同一簇中。如果某个恶意参与方能够成功识别并攻击一个簇，他们可能能够访问或推断出更多敏感信息，增加了数据泄露的风险。因此，需要添加约束：$K \geq \eta$，以确保隐私性。
-% where $\mathcal{P}^{k,i}$ represents the data distribution of $U_i$ within cluster $c_k$, and $n^{k,i}$ denotes the size of $\mathcal{D}_i$. 
-% To jointly ensure performance and security, it is imperative to control the number of peer communities.
-A large $K$ enhances the chance of attackers inferring the sensitive information.
-Conversely, a small $K$ may result in insufficient intra-community similarity, leading to a deterioration in learning performance.
-Therefore, the introduction of a constraint, $K \geq \kappa$, is essential.
-This constraint ensures a minimum size of peer community for privacy considerations.
-$\kappa$ can be adjusted by $\zeta$.
-
-% \subsection{Colleague community construction (CCC)}
-% After peer community construction, we further select suitable UAV nodes to form colleague communities $S\triangleq\{s_1, \ldots, s_{M}\}$ with desirable distribution $\mathcal{P}^{tar}$, which avoids the performance degradation caused by heterogeneity.
-
-% \subsubsection{Problem formulation}
-% As shown in Figure \ref{fig2:framework}, based on the requirements of task $job_i$, we first generate the ``\textit{template}'' $\mathbf{h}$ of the colleague community (i.e., required ratio of clients $h_k$ from each peer community $c_k$ in a colleague community $s_{m}$).
-$\mathbf{h}\triangleq\{h_{1}, \ldots, h_{K}\}$ is a vector to stipulate this composition.
-Then $M$ colleague communities are constructed accordingly by selecting UAV nodes from each $c_k$.
-Outlier $c_k$ with small sizes ($\vert\vert c_k\vert\vert< M$) are excluded to improve participation.
-
-% The optimization problem can be defined as:
-% \begin{equation}\label{eq:problem}
-% \begin{aligned}
-% \mathbf{h}^*\triangleq &\underset{\mathbf{h}}{\arg \min} \vert\vert \mathbf{h}\cdot\mathbf{P}-\mathcal{P}^{tar}\vert\vert_2 \\
-% \text{s.t. }& \forall c_k \in C, h_k\leq b_k, \\
-% &\sum_{i=1} ^K h_i\geq r,
-% \end{aligned}
-% \end{equation}
-% where $\mathbf{P}$ is a $K \times F$ matrix to denote the average feature values for all peer communities.
-Every row $\mathcal{P}^{c_k}\in \mathbb{R}^F$ denotes the average feature values of one peer community.
-$\mathbf{B}\triangleq \{ B_{1}, \ldots, B_{K}\}$ denotes the size of all peer communities.
-
-% \subsubsection{Problem transformation} As the above problem is an NP-C quadratic integer optimization problem \cite{murty1985some}, we want to further reduce it to a linear programming problem to meet the efficiency requirements of UAVs.
-% %即将$\mathcal{P}^{c_k}$拆成$l_k=\lceil \log_2(b_k+1) \rceil$行，拆成的新行中，第$i,1\leq i <l_k$行$d_i=2^{i-1}\mathcal{P}^{c_k},e_{k,i}=2^{i-1}$，第$l_k$行为$(b_k-2^i+1)\mathcal{P}^{c_k},e_{k,l_k}=(b_k-2^i+1)$。新矩阵有$R=\sum_{i=1}^k l_i$行，将原$\mathcal{P}$矩阵二进制拆分为一个$R\cdot F$的矩阵$\mathcal{Q}$，将整数规划问题转化成了一个0-1规划问题。
-% For each $c_k$, to remove the constraint $B_k$, we conduct binary split on $\mathcal{P}^{c_k}$ to get $l_k=\lceil \log_2(B_k+1) \rceil$ new rows.
-Hence, the new matrix has $R=\sum_{i=1}^k l_i$ rows.
-The problem becomes:
-
-% \begin{equation}
-% \begin{aligned}
-% \mathbf{x}^*\triangleq &\underset{\mathbf{x}}{\arg \min} \vert\vert \mathbf{x}\mathcal{Q}-\mathcal{P}^{tar}\vert\vert_2 \\
-% \text{s.t. } &\forall c_k \in C, x_i\in\{0,1\}, \\
-% &\sum_{i=1} ^K h_i\geq r,
-% \end{aligned}
-% \end{equation} 
-% where $\mathbf{x}$ can map to $\mathbf{h}$, i.e., $h_k = \sum _{i=1} ^{l_k} e_{k,i}x_{\sum_{j=1}^{k-1} l_j +i}$, and $e_{k,l_k}=(B_k-2^i+1)$.
-Hence, the above problem is equal to finding the minimum of $(\mathbf{x}\mathcal{Q}-\mathcal{P}^{tar})\cdot (\mathbf{x}\mathcal{Q}-\mathcal{P}^{tar})^T$ as:
-
-% \begin{equation}
-% \begin{aligned}
-% \mathbf{x}^*\triangleq\underset{\mathbf{x}}{\arg \min}\ \mathbf{x}\mathcal{Q} &\mathcal{Q}^T\mathbf{x}^T-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+\mathcal{P}^{tar}\mathcal{P}^{tar^T}\\
-% \text{s.t. }&\mathbf{x}\in\{0,1\}^R,\\
-% &\sum_{i=1} ^K h_i\geq r.
-% \end{aligned}
-% \end{equation}
-
-% We further introduce variable $z_{ij} \in \{0,1\}$ and have $z_{ij}\leq x_i$,$z_{ij}\leq x_j$,$z_{ij}\geq x_i+x_j-1$, to linearize the problem:
-
-% \begin{equation}%\label{eq:problem}
-% \begin{aligned}
-% \min\ &\mathcal{Q}\mathcal{Q}^T\mathbf{y}-2\mathcal{P}^{tar}Q^T\mathbf{x}^T+P^{tar}P^{tar^T}\\
-% \text{s.t. }& \mathbf{x}\in\{0,1\}^R,
-% \\
-% &x_{ij}\leq x_i, x_{ij}\leq x_j, x_{ij}\geq x_i+x_j-1,
-% \\&\sum_{i=1} ^K h_i\geq r.
-% \end{aligned}
-% \end{equation}
-
-% Thus, the problem can be efficiently solved by linear programming solvers\footnote{For example, https://coin-or.github.io/pulp/}.
-
-% % \begin{figure}[!t]
-% % \centering
-% % \includegraphics[width=\linewidth]{figures/fig2.PNG}
-% % \caption{Stratified community construction in a heterogeneous environment.}
-% % \label{fig2:framework}
-% % \end{figure}
-
-% \section{Adaptive FFL training with privacy amplification}
-% \subsection{Training workflow of MR-FFL}
-% % 初始化过程: task generation & community initiation
-% % Step 1: Local training
-% % Step 2: Noise obfuscation
-% % 中间过程: Upload gradient
-% % Step 3: Inner-community aggregation
-% % Step 4: Global aggregation
-% % Step 5: Personalisation
-% % 中间过程: Download model
-% % Step 6: Local update
-
-% As shown in Figure \ref{fig3:workflow}, the training workflow of MR-FFL mainly consists of the following steps in one round of iteration:
-
-% \begin{itemize}
-%     \item \textbf{Initialization:} Once the FFL task arrives, server conducts the CCC algorithm to quickly select $M$ colleague communities with similar average distributions near to $\mathcal{P}^{tar}$.
-%     \item \textbf{Step 1:} First, each node $U_i \in s_m$ trains the current model with personal data to generate the local model $\omega_t^{s_m, i}$.
-%     \item \textbf{Step 2:} Then, $U_i$ obfuscates the weights update $\widetilde{\omega}_{t}^{s_{m}, i}$ with differential private noise, and uploads it to the server.
-%     \item \textbf{Step 3:} Colleague community aggregates $\widetilde{\omega}_{t}^{s_{m}, i}, \forall U_i \in s_m$ to generate a colleague model $\omega_{t}^{s_{m}}$.
-%     \item \textbf{Step 4:} The server aggregates result $\omega^{s_k}$ from each colleague community $s_k \in S$ to get new global model.
-%     \item \textbf{Step 5:} Besides, UAV peer community can maintain a personalized peer model $\omega_{t}^{c_{k}}$ to further improve local performance. 
-%     \item \textbf{Step 6:} Finally, the global model is distributed to selected UAV nodes for the next round of training.
-% \end{itemize}
-
-% As Step 1, 2, and 6 aligns with existing secure FL training process \cite{wei2020federated-NbAFL,padala2021federated}, we focus on Step 3,4 and 5 subsequently.
-
-% \subsubsection{Colleague community aggregation} 
-% %为了尽可能地减小异构数据带来的模型方向的差异，以便更好地聚合普适的全局模型，在服务器聚合前，先在super node 内部聚合。也就是说，本地训练后，客户$i, i\in s_{m}$的加噪模型更新量$\Delta \widetilde{\omega}_{t}^{s_{m},i}$被上传到super node进行super node的内部同步。
-% To reduce the canceling phenomenon caused by heterogeneous data and improve training efficiency,  we first aggregate all $\Delta \widetilde{\omega}_{t}^{s_{m}, i}$ within $s_m$ to generate more homogeneous weight updates $\Delta\widetilde{\omega}_{t}^{s_{m}}$ of colleague model $s_m$ before the global aggregation: %In other words, following local training, the perturbed model update quantity, denoted as $\Delta \widetilde{\omega}{t}^{s{m},i}$ for client $i$ where $i\in s_{m}$, is uploaded to the super node for internal synchronization before server-level aggregation.
-% \begin{equation}
-%     \begin{gathered}
-%      \Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}
-%      = \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i},
-%      \end{gathered}
-% \end{equation}
-% where $p^{s_{m}, i}= {n^{s_{m}, i}}/{n^{s_{m}}}$ is aggregation coefficent, $n^{s_{m}}=\sum_{i \in s_{m}} n^{s_{m}, i}$.
-
-% \subsubsection{Global aggregation} 
-% Then, the server aggregates the learning results from all $s_m$ and updates the global model:
-% \begin{equation}
-% \widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}},
-% \end{equation}
-% where $p^{s_{m}}= \frac{n^{s_m}}{\sum_{s_{m} \in S} n^{s_m}}$, and $\widetilde{\omega}_{t}$ is the global model.
-The global aggregation iteratively executes $T$ rounds to complete the learning task $Job=(w,\mathcal{P}^{tar},t_0, T)$\footnote{The termination condition for the learning task can also be set based on accuracy $\epsilon^{\prime\prime}>0$ rather than a fixed number of rounds $T$, i.e., $\mathcal{L}_{FFL}(\omega_t)\leq \epsilon^{\prime\prime}$, by only modifying the quadruple to $(w,\mathcal{P}^{tar},t_0, \epsilon^{\prime\prime})$.}.
-
-% \subsubsection{Peer community personalization} Finally, to further improve the performance on local datasets, we personalize the local model for peer community by adding the proximal term:
-% \begin{equation}\label{eq:personal}
-% \omega_{t}^{k} = \omega_{t-1}^{k} - \eta\left(\sum_{i=1}^{\vert\vert c_{k}\vert\vert}p^{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega_{t-1} \right)\right)
-% \end{equation}
-%     where $p^{c_k}= \frac{n^{s_m}}{\sum_{c_k \in C} \vert\vert c_k\vert\vert}$, $\eta$ is the learning rate, $\lambda$ is the regularization coefficient.
-The smaller $\lambda$, the more the local models $\omega_t^{k}$ can deviate from the (corrupted) global model $\omega_t$, achieving robustness at the expense of generalization \cite{li2021ditto}.
-
-% In Algorithm \ref{algorithm1}, we present the pseudocode for the complete adaptive training process described above.
-It is evident from the algorithm that our approach only requires participants to provide distribution information, enabling significant improvements in efficiency, accuracy, and privacy in heterogeneous environments.
-Furthermore, our training method seamlessly integrates with the subsequently proposed credit evaluation mechanism.
-In cases where some attackers dishonestly report their information, the integrity of the model is still guaranteed.
-
-% % \begin{figure}[!t]
-% % \centering
-% % \includegraphics[width=\linewidth]{figures/fig3.PNG}
-% % \caption{The workflow of MR-FFL.}
-% % \label{fig3:workflow}
-% % \end{figure}
-
-% \subsection{Analysis of privacy amplification}
-
-% Different from existing central differential privacy (CDP) or local differential privacy (LDP) methods, which inevitably introduce excessive large noise and thus deteriorate the learning performance in heterogeneous environments, inspired by \cite{liu2022privacy}, we propose a novel DP notion: \textit{community-specific differential privacy} (CSDP) for heterogeneous federated learning.
-The anonymity is achieved within a peer community instead of the whole UAV network, which significantly reduces privacy loss under the same DP guarantee.
-Each peer community can be assigned with different $\varepsilon_k$ and $\delta_k$ based on personal needs.
-
-% \subsubsection{Noise calculation} We first calculate the noise scale needed for the MR-FFL workflow to achieve our $(\varepsilon_k,\delta_k)$-CSDP.
-Assume a pair of neighbor datasets $\mathcal{D}^{s_{m}, i}_{t}$ and $\mathcal{D}^{s_{m}, i'}_{t}$ sampled from same $s_m$ with size $n^{s_{m}, i}$, there is only one pair of nonidentical samples $\xi^{i}_{t}$ and $\xi^{i\prime}_{t}$ within the neighbor datasets.
-The $l_2$ norm-based sensitivity can be calculated as:
-
-% \begin{equation}
-%      \begin{aligned}
-%     \Delta F&=\max _{\xi^{i}_{t},\xi^{i\prime}_{t}}\left\|F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i}_{t}\right) -F^{s_m}\left(w_{t-1}, \mathcal{D}^{s_{m},i'}_{t}\right)\right\|\\
-%     &\leq \frac{n^{s_{m},i}}{n^{s_{m}} M}\left(  \max \left\| \Delta\omega_{r,t}^{s_{m},i}\right\|   + \max  \left\| \Delta\omega_{r,t}^{s_{m},i}\right\| \right)
-%      \end{aligned}
-% \end{equation}
-
-% The second inequality can be deduced through a similar analysis as in \cite{wei2020federated-NbAFL}. We omit the specific process for simplicity. 
-% After DP weights clipping \cite{abadi2016deep}, assuming an equal volume of data for clients and a minimum node count $L$ ($L\geq r$) within the colleague community, we have the best sensitivity as:
-% \begin{equation}
-%     Sen_k=\max _{i \in c_{k}}\left\{\Delta f\right\} \leq \frac{2 E_{k}}{L M},
-%     \end{equation}
-%  where $E_k$ is the clipping bound of $c_k$.
-% The standard deviation of the Gaussian noise to achieve $(\varepsilon_k,\delta_k)$-CSDP is:
-% \begin{equation}
-%     \sigma_{k}=\frac{\ell_{k} Sen_k }{\varepsilon_{k}}=\frac{2 \ell_{k} E_{k}}{L M\varepsilon_{k}},
-%     \end{equation}
-% where constant $\ell_{k} =\sqrt{2 \ln (1.25 / \delta_{k})}$ \cite{dwork2014algorithmic}.
-
-% \subsubsection{Privacy analysis}
-
-% %我们假设客户的类别分布$\mathcal{P}^{c_{k}}$符合高斯分布$\varphi_{c_{k}} $，即客户类别以方差$\sigma_{c_{k}}^{2}$正态分布在簇心$\mu_{c_{k}}$周围，即簇$c_{k}$的类别分布可以用$\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$的高斯分布表示。
-% We assume that the data distribution of the UAV clients, denoted as $\mathcal{P}^{c_{k}}$, follows a Gaussian distribution $\varphi_{c_{k}}$, where the data are normally distributed around the community center $\mu_{c_{k}}$ with a variance of $\sigma_{c_{k}}^{2}$.
-In other words, the data distribution of community $c_{k}$ can be represented by a distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_{k}}^{2}\right)$ \cite{wei2020federated-NbAFL}.
-% %对于某一簇$c_{i}$,整体类别分布符合高斯分布$\varphi_{c_{i}} \sim \mathcal{N}\left(\mu_{c_{i}}, \sigma_{c_i}^{2}\right)$，从中随机抽取任意客户$\forall i,i'\in c_{i}$，客户类别分布也符合$\varphi_{c_{i}}$。
-% For a specific peer community $c_{k}$, the overall data distribution follows distribution $\varphi_{c_{k}} \sim \mathcal{N}\left(\mu_{c_{k}}, \sigma_{c_i}^{2}\right)$.
-Hence, selecting any UAV client $\forall i,i'\in c_{k}$ from it, the client's distribution also follows $\varphi_{c_{k}}$ \cite{wei2021low}.
-
-% %由公式（9）可知，在本地训练中，客户最小化本地经验风险得到的梯度与客户的本地数据有关，且客户梯度间的最大距离与数据分布的分散程度正相关，可以得到簇$c_{i}$客户梯度间的最大距离：
-% As indicated by \cite{sattler2020clustered-CFL}, it is evident that in local training, the gradient obtained by a client, which minimizes the local empirical risk, is related to the client's local data.
-The maximum distance between client gradients is positively correlated with the dispersion of the distribution.
-Consequently, the maximum distance between gradients of nodes within peer community $c_{k}$ can be derived as $\max_{i,i'\in c_{k}} \left\| \Delta\omega_{t}^{c_{k},i}-\Delta\omega_{t}^{c_{k},i'}\right\| \simeq \sigma_{c_k}$.
-
-% %super node按照数量$n=[n_{1},\ldots,n_{k},\ldots,n_{K}],  n_{k} \in \mathbb{N}$从簇$\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中选择$L$个客户:$\sum^{K}_{k=1} n_{k}=L$。通过卷积求和上述簇分布，可以得到super node 的类别分布$\varphi_{s}$：
-% We choose UAV nodes from each peer communities $c_{k},\forall c_k \in C$ to constitute colleague communities according to composition vector $\textbf{h}=[h_{1},\ldots,h_{k},\ldots,h_{K}],  h_{k} \in \mathbb{N}$.
-Hence, by convolution summation among those peer distributions, we can obtain the distribution of colleague communities $\varphi_{s}$ as:
-
-% \begin{equation}    \varphi_{s}=h_{1}\varphi_{c_{1}}\oplus\ldots\oplus h_{k}\varphi_{c_{k}}\oplus\ldots\oplus h_{K}\varphi_{c_{K}}
-% \end{equation}
-
-% %因为簇分布$\varphi_{c_{k}} \forall c_{k} \in C$是相互独立的高斯分布，可以得到上述簇分布的卷积和。
-% As $\varphi_{c_{k}}, \forall c_{k} \in C$ are i.i.d.
-Gaussian distributions, we have $\varphi_{s} \sim \mathcal{N}\left(\mu_{s}, \sigma_{s}^{2}\right)$, where $\mu_{s}=\sum_{k}^{K} h_{k} \mu_{c_{k}}$, $\sigma_{s}^{2}=\sum_{k}^{K} h_{k}^{2} \sigma_{c_k}^{2}$.
-% Define the maximum distance between weight updates of two UAV nodes $U_i$ and $U_{i^{\prime}}$ from the same colleague community $s$ as $\max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\| \simeq \sigma_{s}$.
-As $\sigma_{s}=\sqrt{\sum_{k}^{K} h_{k}^{2} \sigma_{c_k}^{2}}$, easy to prove $\sigma_{s}\geq\sigma_{c_{k}}, \forall c_k \in C$.
-% Then, we have:
-% \begin{equation}
-%     \max_{i,i'\in c_{i}} \left\| \Delta\omega_{t}^{c_{i},i}-\Delta\omega_{t}^{c_{i},i'}\right\|\leq \max_{i,i'\in s} \left\| \Delta\omega_{t}^{s,i}-\Delta\omega_{t}^{s,i'}\right\|.
-% \end{equation}
-
-% %根据敏感度的定义，可知在super node 中计算supernode内的敏感度将远大于簇内的敏感度。
-% According to the definition of sensitivity, our peer community-specific $Sen_k$ and noise scale is much smaller than existing global-wide or colleague-wide DP methods.
-Hence, to achieve the same FFL performance, the clipping bound of our method is also much smaller, which requires less obfuscation.
-
-% \begin{comment}
-
-% \subsection{Analysis of personalization}
-% 在$K$个簇$C=\{c_{1},\ldots,c_{k},\ldots,c_{K}\}$中，每个簇$c_{k}$有相同的客户数$n$。$X^k \triangleq\left\{\omega^{k, i} \in\right.\mathbb{t}\}_{i \in[n]}$，且客户模型以方差$\upsilon^{2}$正态分布在簇心$\omega^{k}$周围，即$\omega^{k, i}=\omega^{k}+z^{k, i}$,其中$z^{k, i} \sim \mathcal{N}\left(0, \upsilon^{2}\right)$。具体来说，为了量化簇的异质性，我们假设簇心$\{\omega^{k}\}_{k \in \left[K\right]}$也以方差$\tau^{2}$正态分布在未知的固定元中心$\theta$周围,即$\omega^{k}=\theta+z^{k}$,其中$z^{k} \sim \mathcal{N}\left(0, \tau^{2}\right)$。其中，$\tau$表示簇心间的分散程度，$\tau$越大，簇越分散，整体分布的异构性越高。在此基础上，簇$c_{k}$为其中客户选择隐私预算$(\varepsilon_{k},\delta_{k})-DP$以最小化整体的泛化误差。每个簇$k$具有不同的裁剪边界$C_{k}$，并以$\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$的标准差在本地客户上传的模型加噪,在此基础上，簇$c_{k}$的优化目标可以表示为：
-% \begin{equation}
-% h_k(\omega)=\tilde{F}_k(\omega)+\frac{\lambda}{2}\|\omega-\omega^{g}\|_2^2
-% \end{equation}
-% 其中，$\tilde{F}_k(\omega) \triangleq \frac{1}{2}\left(\omega-\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i} \cdot \min \left(1, C_{k} /\left\|\omega^{k, i}\right\|_2\right)\right)\right)^2$是簇$c_{k}$的优化目标，簇$c_{k}$客户梯度加噪大小为$\xi^k \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$。由于数据是亚高斯的，我们可以选择裁剪的边界$C_{k}$避免引入削波误差。因此，簇$c_{k}$的最优本地优化结果为$\widehat{\omega}^k \triangleq \operatorname{argmin} \tilde{F}_k(w)=\frac{1}{n}\left(\xi^k+\sum_{i=1}^{n} \omega^{k, i}\right)$。由于服务器聚合全部参与客户的模型而客户分布在各簇中，因此可得$\omega^{g}=\frac{1}{Kn} \sum_{k=1}^{K}\left(\xi^k+\sum_{i=1}^{n}\omega^{k,i}\right)=\frac{1}{K}\sum_{k=1}^{K}\widehat{\omega}^{k}$。由此可得簇$c_{k}$外各簇的平均估计结果$\widehat{\omega}^{\backslash k}=\frac{1}{K-1}\sum_{j \neq k}\widehat{\omega}^{j}$。
-% \end{comment}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{algorithm}[!t]% !t top !b bottom !h right here !p float pages
-% \caption{Adaptive training with privacy amplification}
-% \label{algorithm1}
-% 	\begin{algorithmic} [1]
-%     \State \textit{\textbf{ Input: }Learning task $Job\triangleq(w^0,\mathcal{P}^{tar},t_0, T)$; Maximum
-% local training iterations $R$; all participant UAV nodes $\mathbf{U}$ and their local dataset $\mathcal{D}_i$.}
-%     \State \textit{\textbf{Output: }The global FFL model $\omega$ for task $Job$, personalized local models $\{ \omega^{k}\}_{k \in [K]}$} for peer communities.
-%             \State \textbf{Initialize:} $w^{0}_{i} \leftarrow\ w^{0}$%,$\mathcal{P}^{real}=\operatorname{norm}\left(\sum_{i \in B} N^{i} \mathcal{P}^{i} \right)$
-%             %\State {\color{CadetBlue}/* \textbf{Peer community construction */} } 
-%             %\State $d_{i,j}=\lVert \mathcal{P}^{i}-\mathcal{P}^{j} \rVert_{2}$
-%             %\State $C=\{ c_{1}, \ldots , c_{K} \} \leftarrow \arg \min _{c_{1} \cup c_{2} \cup \ldots c_{K}=C}\left(\max _{\forall c_{k},c_{k'} \in C ,i \in c_{k}, j \in c_{k'},d_{i, j}\geq\zeta} d_{i, j}\right) .$
-%             \State Construct $C=\{ c_{1}, \ldots , c_{K} \}$ with Eq. (\ref{eq:peer-construct});
-%              %\For { $r \in 1, \cdots, R$}
-%                 %\State{\color{CadetBlue} /* \textbf{Initialization} */} %$S \leftarrow Select-Clients()$}
-%             \State Calculate composition vector $\mathbf{h}$ by Eq. (\ref{eq:problem}) for $Job$;
-%             \State Construct colleague communities as $S^t=\{s_{1}, \ldots , s_{M}\}$ according to template $\mathbf{h}$;
-%                 \For {each colleague community $s_{m}$ in $S^{t}$ in parallel }
-%                     \For {each UAV node $U_i$ in $s_{m}$ in parallel}
-%                         \State {\color{CadetBlue}/*\textbf{Local Training*/}} 
-%                         %\State $\omega_{t}^{s_{m},i} \leftarrow \omega_{t-1}^{s_{m},i}-\frac{\eta}{NI^{s_{m},i}} \nabla_\omega \mathcal{L}_{s_{m},i}\left(\omega_{t-1}^{s_{m},i}, \mathcal{D}^{s_{m},i}_{t}\right)$
-%                         \State Update $\omega_{t}^{s_{m},i}$ with $\mathcal{D}_i$ for $R$ iterations;
-%                         \State $\Delta \omega_{t}^{s_{m},i}=\omega_{t-1}^{s_{m},i}-\omega_{t}^{s_{m},i}$;
-%                         \State{\color{CadetBlue}/* \textbf{Privacy obfuscation */}} 
-%                         %\State \textbf{DP:} client $i \in c_{k}$, guarantee ($\varepsilon_{k}$,$\delta_{k}$)-DP
-%                         \State Calculate noise $z^{k} \sim \mathcal{N}\left(0, \sigma_{k}^2\right)$, $\sigma_{k}=\frac{2 h_{k} C_{k}}{L M\varepsilon_{k}}$;
-%                         \State $\Delta \widetilde{\omega}_{t}^{s_{m},i}=\Delta \omega_{t}^{s_{m},i}+z^{k}$;
-%                     \EndFor
-%                     \State{\color{CadetBlue}/* \textbf{Colleague community aggregation */}} 
-%                     \State $\widetilde{\omega}_{t}^{s_{m}} \leftarrow \widetilde{\omega}_{t-1}^{s_{m}} -  \sum_{i \in s_{m}} p^{s_{m}, i}\Delta \widetilde{\omega}_{t}^{s_{m},i}$;
-%                     \State $\Delta\widetilde{\omega}_{t}^{s_{m}} =  \widetilde{\omega}_{t-1}^{s_{m}}-\widetilde{\omega}_{t}^{s_{m}}$;
-%                 \EndFor
-%                 \State {\color{CadetBlue}/* \textbf{Global aggregation */}}
-%                 \State $\widetilde{\omega}^g_{t} \leftarrow \widetilde{\omega}^g_{t-1} - p^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$;%$\widetilde{\omega}_{t} \leftarrow \widetilde{\omega}_{t-1} - PI^{s_{m}} \sum_{m=1}^{M} \Delta\widetilde{\omega}_{t}^{s_{m}}$
-%                 \State{\color{CadetBlue}/* \textbf{Peer community personalization */}}
-%                     \State Update the personalized model $\omega_{t}^{k}$ for each peer community $c_k$ with Eq.
-(\ref{eq:personal});%$\omega_{t}^{k} \leftarrow \omega_{t-1}^{k} - \eta_{c_{k}}\left(\sum_{i=1}^{n_{c_{k}}}p_{c_{k},i}  \Delta \widetilde{\omega}_{t}^{c_{k},i} + \lambda \left(\omega_{t-1}^{k}-\omega^{g}_{t-1} \right)\right)$
-%                     %\State Update $\omega_{t}^{k}$
-%             % \EndFor
-% \State \Return $w^g,\{w^k\}$
-% \end{algorithmic}
-% \end{algorithm}
-
-% \begin{algorithm}
-% \caption{Single}
-% \label{alg:malicious-node-detection-history}
-% \begin{algorithmic}[1]
-% \State \textit{\textbf{Input:} Global model $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical updates for each nodes $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$, threshold $\varepsilon$.}
-% \State \textit{\textbf{Output:} Sets of normal/malicious nodes $U_{nor}$ and $U_{mal}$.}
-
-% \State {\color{CadetBlue}/*\textbf{Step 1: historical database construction*/}}
-% \For {Client $i \in $}
-%     \State Record flattened gradients $\bar{\theta_i^t}$ and models $\theta_g^{t-1};$
-%     \State Establish a ray with Eq. () for each of the $t'$ most recent gradients, $t' = \max\{t-T+1, 1\}, \ldots, t$;
-% \EndFor
-
-% \State \textbf{Step 2: Obtain the Purpose Intention}
-% \For {Client $i$}
-%     \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
-%     \While {Not Converged}
-%         \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
-%     \EndWhile
-%     \State Calculate confidence $cre_i = \frac{1}{r_i + \rho}$
-% \EndFor
-
-% \State \textbf{Step 3: Abnormal Detection}
-% \For {Client $i$}
-%     \For {Each point $O_j \neq O_i$}
-%         \State Calculate distance $\|O_i - O_j\|$
-%     \EndFor
-%     \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
-%     \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
-%     \State Compute reachability distance $rea_{i,j} = \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$
-%     \State Calculate local reachability density $lrd_i = \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$
-% \EndFor
-% % \For {Client $i$}
-% %     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
-% %     \If {$lof_i > 1$}
-% %         \State Mark client $i$ as malicious, add to $U_{mal}$
-% %     \Else
-% %         \State Mark client $i$ as normal, add to $U_{nor}$
-% %     \EndIf
-% % \EndFor
-% \State Calculate $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$ for each client $i$
-% % \State $U_{mal} = \{i \,|\, lof_i > 1\}$
-% % \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
-% \State $U_{mal}, U_{nor} = \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$
-
-% \State \textbf{Step 4: Gradients Aggregation}
-% \For {Client $i\in U_{nor}$}
-%         \State Compute adjusted confidence $cre_i' = \tanh(cre_i)$
-%         \State Normalize weights $w_i = \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$
-% \EndFor
-
-% \State \textbf{Output:} Aggregated global model update $\theta_g^t = \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$
-% \end{algorithmic}
-% \end{algorithm}
-
-% \begin{algorithm}
-% \caption{Malicious Node Detection via DCT}
-% \label{alg:malicious-node-detection}
-% \begin{algorithmic}[1]
-% \State \textbf{Input:} $d$, $n$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$, $m$ \Comment{$d$ is the dimension of each node update; $n$ is the number of the nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_n^t) \in \mathbb{R}^{n \times d}$is the local updates from nodes during the $t$-th round; $m$ is the length of low-frequency components}
-% \State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
-
-% \State Step 1: Frequency Domain Transformation
-% \For {Node $R_i$}
-%     \State $\bar{\theta_i^t} \gets Flatten(\triangledown \theta_i^t)$
-%     \State $G_i^t = Trunc(DCT(\bar{\theta_i^t}), m)$ \Comment{Compute DCT and retain only the top $m$ low-frequency components}
-% \EndFor
-
-% \State
-
-% \State Step 2: Clean Ingredient Extraction
-% \State $H^t \gets (G_0^t, G_1^t, \ldots, G_{n}^t) \in \mathbb{R}^{d \times m}$ \Comment{Stacking to form Matrix $H^t$.}
-
-% \State $\hat{H}^t \gets (H^t)^{T} H^t$
-% \State $\lambda_{max}^t, \xi_{max}^t \gets \text{eig}(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
-% \State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
-
-% \State
-
-% \State Step 3: Kullback-Leibler Divergence Calculation
-% \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
-% \For {Node $R_i$}
-%     \State $Ki \gets \sum_{k=0}^{m-1} P_i^t[k] \log \left( \frac{P_i^t[k]}{Q^t[k]} \right)$
-% \EndFor
-% \State $S \gets \{KL_1, KL_2, \ldots, KL_n\}$ \Comment{The distribution differences calculated by KL divergence.}
-
-% \State
-
-% \State Step 4: Malicious Node Detection
-% \State $\{C_1, C_2, \ldots, C_K\} \gets \text{HDBSCAN}(S)$
-% \State $U_{nor} \gets C_{\text{max}}$, $U_{mal} \gets \{C_i \, | \, i \neq \text{max}\}$
-
-% \end{algorithmic}
-% \end{algorithm}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \section{Community-based credit evaluation of UAV nodes}
-% In this section, we design a community-based credit evaluation method with a modified three-valued subjective logic model (SLM) \cite{al2021subjective}, to eliminate malicious attackers hiding in heterogeneous UAV networks.
-By integrating credits from both similarity-dominated intra-community (peer) and performance-dominated inter-community (colleague), multiple poisoning paradigms can be efficiently thwarted.
-% \subsection{Similarity-dominated peer credit evaluation}
-% %首先，同一community内的用户在训练过程中上传的weights往往相似性较高。因此，通过社区内相似度比较，可以快速识别出离群的恶意用户。
-% UAV nodes' weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ within the same peer community $c_k$ often exhibit a high degree of similarity during the training process.
-Therefore, by leveraging community-based similarity, one can promptly identify malicious nodes that deviate significantly from the average norm.
-
-% \subsubsection{Basic setting}
-% For $\forall U_i \in c_k$, we first calculate the cosine similarity $\alpha_{c,i}^{t} \in [-1,1]$ between weight updates $\Delta\widetilde{\omega}^{c_k, i}_{t}$ from $U_i$ and average weight updates $\Delta\widetilde{\omega}^{c_k}_{t}$ from its peer community $c_k$:
-% \begin{equation}
-%     	  \alpha^{c_k,i}_{t} = \alpha( \Delta\widetilde{\omega}^{c_k}_{t-1}, \Delta\widetilde{\omega}^{i}_{t}) = \frac{\langle \Delta\widetilde{\omega}^{c_k}_{t-1},\Delta\widetilde{\omega}^{i}_{t}\rangle}{\Vert \Delta\widetilde{\omega}^{c_k}_{t-1}\Vert\cdot\Vert \Delta\widetilde{\omega}^{i}_{t}\Vert },\forall c_k \cap S.
-% \end{equation}
-
-% We further define the positive interaction $p^{c \rightarrow i}_{t} \in [0,2]$ as:
-% \begin{equation}
-%     	 PI^{c_k \rightarrow i}_{t} = \alpha^{c_k,i}_{t} -(-1),
-% \end{equation}
-% and the negative interaction $n^{c_k \rightarrow i}_{t} \in [0,2]$ as:
-% \begin{equation}
-%     	 NI^{c_k \rightarrow i}_{t} = 1-\alpha^{c_k,j}_{t}.
-% \end{equation}
-
-% %在FL的过程中，客户与簇的交互作用影响客户的信誉评估。诚实的交互行为将为客户的信誉评估带来正向的影响，具有攻击性的或不诚实的交互则会降低客户的信誉评分。我们分别用系数$b$和$c$表示内客户间正负交互作用对信任评价的影响比例，其中，$b>0,c>0$ 且 $b+c=1$。为了惩罚恶意客户，我们为客户间的负面交互设置更大的权重,即$b>c$。
-% During the FFL process, benign behaviors positively impact the reputation assessment, while aggressive or deceptive interactions diminish the client's reputation.
-We use coefficients $b$ and $c$ to quantify the impact of positive/negative interactions in credit evaluation, respectively.
-$b>0$ and $c>0$, $b+c=1$.
-To penalize malicious UAV nodes, we assign a greater weight $b>c$ to negative interactions among clients.
-% Hence, we obtain the temporary three-valued peer reputation opinion \cite{liu2019trust} vector $\Upsilon^{c_k \rightarrow i}_{t,temp}\triangleq \{b^{c_k \rightarrow i}_{t,temp}, d^{c_k \rightarrow i}_{t,temp}, u^{c_k \rightarrow i}_{t,temp}\}$ based on SLM as:
-% \begin{equation}
-% \Upsilon^{c_k \rightarrow i}_{t,temp}=
-% \left  \{
-%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-%         b^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{bPI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
-%         d^{c_k \rightarrow i}_{t,temp}=(1-u^{c_k \rightarrow i}_{t})\frac{cNI^{c_k \rightarrow i}_{t}}{ bPI^{c_k \rightarrow i}_{t}+cNI^{c_k \rightarrow i}_{t}},\\
-%         u^{c_k \rightarrow i}_{t,temp}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}},                
-%     \end{array}
-% \right.
-% \end{equation}
-% %$ \sigma_{c}$为簇c中满足$\varepsilon-DP$所加噪声的标准差，体现了根据客户上传加噪梯度计算可信度的不确定性，$ \sigma^{C}_{max}$和$\sigma^{C}_{min}$分别是所有簇$c\in C$中为满足$\varepsilon-DP$所添加的最大噪声和最小噪声。
-% where the standard deviation $ \sigma_{c_k}$ of peer community $c_k$ depicts the uncertainty in the credit calculation based on the noisy $\Delta\widetilde{\omega}^{c_k}_{t}$ to achieve DP guarantee.
-$ \sigma_{max}=\max_{c_k \in C}{\sigma_{c_k}}, \sigma_{min}=\min{c_k \in C}{\sigma_{c_k}}$.
-%Furthermore, $ \sigma^{C}{max}$ and $ \sigma^{C}{min}$ denote the maximum and minimum noise added, respectively, among all clusters $c\in C$ to satisfy $\varepsilon-DP$.
-% Besides, $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp}$ denote \textit{belief}, \textit{disbelief}, and \textit{uncertainty}, respectively.
-We have $b^{c_k \rightarrow i}_{t,temp}+d^{c_k \rightarrow i}_{t,temp}+u^{c_k \rightarrow i}_{t,temp}=1$ and $b^{c_k \rightarrow i}_{t,temp}$, $d^{c_k \rightarrow i}_{t,temp}$, $u^{c_k \rightarrow i}_{t,temp} \in [0,1]$.
-
-% Then $c_k$'s temporary credit evaluation towards UAV $U_i$ is:
-% \begin{equation}
-% \Phi^{c_k \rightarrow i}_{t}=b^{c_k \rightarrow i}_{t} + a u^{c_k \rightarrow i}_{t}, \forall c_k \cap S,
-% \end{equation}
-% %其中$a\in[0,1]$是信誉不确定影响程度的系数。基于上式，根据客户的信誉度可以更明显地区分出恶意客户，从而抑制客户间的负面交互。
-% where $a\in[0,1]$ is a coefficient regulating the importance of uncertainty. 
-% Based on the above equation, malicious clients can be distinctly distinguished via reputation scores, thereby mitigating negative interactions among clients.
-
-% \subsubsection{Long-term consideration}
-% %在r个同步轮次内，客户的信誉不总是一成不变的。由于客户的信誉随着时间的推移而变化，我们考虑客户间历史信誉的影响。定义信誉的时间衰减因子为：
-% During the iterative training, clients' reputations may not remain constant.
-Some sophisticated attackers even take advantage of this phenomenon and conduct more stealthy poisoning behaviors \cite{credit1-kang2019IOT}.
-Therefore, we take into account the influence of historical reputation.
-The time decay factor $v_{\tau}$ is defined as:
-% \begin{equation}
-% v_{\tau}=\frac{1}{e^{\iota(Y-\tau)}}=e^{-z(Y-\tau)},
-% \end{equation}
-% %其中$z>0$为冷却系数, $\tau \in [1,Y]$为历史交互时间的时隙,在内部通信中当前时隙$Y=r$。由于过于久远的信誉的时间衰减因子接近0，并且考虑到信誉交互中的内存与计算成本，我们只保留$\vert Y-\tau \vert \leq T$的历史信誉 ,即只记录并维护距离当前通信轮次的$T$轮历史信誉$\Phi^{c \rightarrow i}_{\tau}$。公式(7)表示，越接近当前同步轮次的信誉的时效性越高，即更相信近期交互的信誉度，而不是历史交互。
-% where $\iota>0$ is the cooling coefficient, $\tau \in [1,Y]$ represents the time slot of historical interaction, and $Y$ in the current time slot of internal communication.
-Since the time decay factor for too-old reputations approaches 0, and considering the memory and computational costs in reputation interactions, we set an expiration threshold and retain only $T$ historical reputations $\Phi^{c_ \rightarrow i}_{\tau}$, i.e., $\vert Y-\tau \vert \leq T$.
-%Formula (7) indicates that reputations closer to the current synchronization round are more timely, placing higher trust in recent interactions rather than historical ones.
-
-% \subsubsection{Stability consideration} 
-% %\item \textbf{更新：}在联合学习的迭代交互$r\in[1,R]$中，服务器选择参与本地训练的随机客户子集为$Set_{t}$,在第$r$轮迭代中，只有集合$Set_{t}$中的客户上传模型更新量并彼此交互评估信誉。然而，由于参与训练和客户数量远少于客户总数,即$\vert Set_{t}\vert \ll N$，当前轮次的评估结果不足以给出完整的评估结果。因此，我们使用每个客户端的最新信誉更新值来更新其当前信誉值。设$\left\{ \Phi^{c \rightarrow i}_{t} \right\}_{i}^N$表示在服务器上维护的每个客户的簇内直接信誉。在每一轮交互后，全部客户执行以下更新操作：
-% Moreover, as only chosen UAV nodes $U_i\in S$ participate in the FFL at round $t$, cross-slot reputation values can have erratic fluctuation or asynchronous obsolescence problems.
-Hence, inspired by \cite{jhunjhunwala2022fedvarp}, We introduce the momentum term to the reputation updating as:
-% \begin{equation}
-% \Upsilon^{c_k \rightarrow i}_{t}=
-% \left\{\begin{array}{ll}
-% \Upsilon^{c_k \rightarrow i}_{t} ,& \text { if } U_i \in S\\
-% \Upsilon^{c_k \rightarrow i}_{t-1},& \text { otherwise }
-% \end{array}\right.
-% \end{equation}
-
-% %在训练开始前，初始化所有客户$\forall i \in [N]$的信誉评价$\Upsilon^{c \rightarrow i}_{0}$可以表示为：
-% %可以看出我们提供较高的初始信誉并保证非参与客户历史信誉的连续性。
-% Then, in the initialization phase $t=0$, we have:
-% \begin{equation}
-% \Upsilon^{c_k \rightarrow i}_{0}=
-% \left  \{
-%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-%         b^{c_k \rightarrow i}_{0}=1-u^{c_k \rightarrow i}_{0},\\
-%         d^{c_k \rightarrow i}_{0}=0,\\
-%         u^{c_k \rightarrow i}_{0}=\frac{\sigma_{c_k}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}
-%       \end{array}
-% \right.
-% \forall U_i\in c_k.
-% \end{equation}
-
-% %上式确保了客户簇内直接信誉的实时性，即维护了包括参与和非参与交互客户在内的全部客户的当前信誉均为其最近的信誉更新值。
-% The above design ensures the stability of credit evaluation for both participating and non-participating UAV nodes in the current round.
-
-% By integrating both stability and long-term consideration, we obtain the final peer reputation opinion: 
-% \begin{equation}
-% \Upsilon^{c_k \rightarrow i}_{t}=
-% \left  \{
-%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-%         b^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} b^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
-%         d^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} d^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}},\\
-%         u^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} u^{c_k \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}  ,              
-%     \end{array}
-% \right.
-% \forall U_i\in c_k,
-% \end{equation}
-% %第r轮同步，簇$c$中客户i的信誉评价为：
-% and $c_k$'s credit evaluation towards UAV node $U_i$ at round $t$:
-% \begin{equation}
-% \Phi^{c_k \rightarrow i}_{t}=\frac{\sum_{\tau=r-T}^{t}{v_{\tau} \Phi^{c \rightarrow i}_{\tau}}}{\sum_{\tau=r-T}^{t}{v_{\tau}}}, \forall U_i\in c_k.             
-% \end{equation}
-
-% \subsection{Performance-dominated colleague credit evaluation}
-% Performance-dominated colleague credit evaluation generates the general judgment $\Phi^{s_m}_{t}, \forall s_m\in S$ from other colleague communities. 
-% As colleague communities are regrouped after every iteration, different from peer credit, colleague credit pays more attention to comprehensive consideration of both performance and similarity between $s_m$ and $s_{m^{\prime}}, \forall s_{m^{\prime}} \in S_{\neg s_m}$.
-
-% Hence, we first calculate the similarity between $s_m$ and $s_{m^{\prime}}$:
-% \begin{equation}
-%     	  \alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega}^{s_{m}}_{t},  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}) = \frac{\langle  \Delta\widetilde{\omega}^{s_{m}}_{t}, \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\rangle}{\Vert  \Delta\widetilde{\omega}^{s_{m}}_{t}\Vert\cdot\Vert  \Delta\widetilde{\omega}^{s_{m^{\prime}}}_{t}\Vert }.
-% \end{equation}
-
-% The positive and negative interactions are $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$ and $NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$, respectively.
-$PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} + NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 2$.
-
-% Thereafter, the \textit{belief} $b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$b^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u_t^{s_{m} \rightarrow s_{m^{\prime}}})\frac{bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$
-% \textit{disbelief} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=(1-u^{s_{m} \rightarrow s_{m^{\prime}}}_{t})\frac{cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}}{ bPI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}+cNI^{s_{m} \rightarrow s_{m^{\prime}}}_{t}},$$ and \textit{uncertainty} $u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}$ is $$u^{s_{m} \rightarrow s_{m^{\prime}}}_{t}=\Vert PI^{s_{m}}-PI^{s_{m^{\prime}}}\Vert/2.$$
-
-% For round $t$, the reputation opinion vector can be defined as follows:
-
-% \begin{equation}
-% \Upsilon^{s_m}_{t}=
-% \left  \{
-%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-%         b^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  b^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
-%         d^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  d^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},\\
-%         u^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}  u^{s_{m^{\prime}} \rightarrow s_m}_{t}}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},
-%     \end{array}
-% \right.
-% \end{equation}
-% where $\rho^{s_m}_{t}=acc^{s_m}_{t}$ is the accuracy of colleague community $s_m$.
-From the perspective of model security, we assign lower weights to attackers who dishonestly report data distributions based on the model accuracy $acc^{s_m}_{t}$ of $s_m$.
-Therefore, as the model accuracy $acc^{s_m}_{t}$ increases, the weight assigned to $s_m$ also increases, making the reputation opinion from $s_m$ more reliable.
-
-% The final colleague credit evaluation for $\forall U_i \in s_m$ can be calculated as:
-% \begin{equation}
-% \Phi^{s_m \rightarrow i}_{t}=\Phi^{s_m}_{t}=\frac{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{(\rho^{s_{m^{\prime}}}_{t} b^{s_{m^{\prime}} \rightarrow s_{m}}_{t}+ a u^{s_{m^{\prime}} \rightarrow s_{m}}_{t})}}{\sum_{s_{m^{\prime}}\in S_{\neg s_m}}{\rho^{s_{m^{\prime}}}_{t}}},
-% \end{equation}
-
-% \subsection{UAV nodes selection with comprehensive
-% community-based credit}
-% \subsubsection{Comprehensive community-based credit} 
-% Finally, by merging peer credit and colleague credit evaluation results, we can obtain comprehensive evaluations of participant UAV nodes based on similarity and performance jointly. 
-% The comprehensive reputation opinion $\Upsilon^{i}_{t}$ can be calculated by conducting consensus mechanism between $\Upsilon^{c_k\rightarrow i}_{t}$ and $\Upsilon^{s_m\rightarrow i}_{t}$ as:
-% \begin{equation}
-% \Upsilon^{i}_{t}=
-% \left  \{
-%       \begin{array}{ll}%ll按顺序是公式左对齐和条件左对齐
-%         b^{i}_{t}=\frac{b^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+b^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
-%         {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
-%         d^{i}_{t}=\frac{d^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}+d^{s_m \rightarrow i}_{t}u^{c_k \rightarrow i}_{t}}
-%         {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}},\\
-%         u^{i}_{t}=\frac{u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}
-%         {u^{c_k \rightarrow i}_{t}+u^{s_m \rightarrow i}_{t}-u^{c_k \rightarrow i}_{t}u^{s_m \rightarrow i}_{t}}         
-%     \end{array}
-% \right.
-% \end{equation}
-
-% %因此，可得客户 $j$ 的综合信任度为：
-% The comprehensive community-based credit of $U_i$ is: 
-% \begin{equation}
-% \Phi^{i}_{t}=b^{i}_{t}+a u^{i}_{t}
-% \end{equation}
-
-% %通过上述信誉评估过程，服务器可以从簇和super node两个维度综合选择具有高性能和可靠数据的高信誉候选客户作为联邦学习任务中的参与者。该方法能够与FEDGS框架紧密结合，在FEDGS内部同步和外部同步的过程中分别从簇内和super node间评估客户信誉，将信誉评估细化到每轮迭代中，能够及时发现并排除攻击者，尽可能地减少其对联合学习的干扰。
-
-% Similar to peer credit evaluation, the updating rule of $\Phi^{i}_{t}$ is also designed with stability consideration as follows:
-% %\textbf{更新：}第$r$轮迭代，被选中参与联合学习的客户集合为$Set_{t}$。设$\left\{ \Phi^{i}_{t} \right\}_{i=1}^N$表示维护的第$r$轮每个客户的综合信誉。在迭代学习的过程中，对于未被选中构建supernode并参与训练的客户，保持其最近轮次的信用评分，并根据最近的综合信任度计算其下一轮次的选择概率：
-% \begin{equation}
-% \Phi^{i}_{t}=
-% \left\{\begin{array}{ll}
-% \Phi^{i}_{t} & \text { if } i \in Set_{t} \\
-% \Phi^{i}_{t-1}& \text { otherwise }
-% \end{array}, \text { for all } i\in[N]\right.
-% \end{equation}
-
-% \textbf{Resistance ability against collusion attack:} 
-% %当攻击者拥有多个compromised节点时，多个节点可以进行共谋攻击。MR-FFL可以通过简单的设置实现对共谋攻击的阻断。具体来说，在MR-FFL中，攻击者可以采取“集中合谋”或者“分散合谋”策略：（1）分散合谋的攻击者上报不同的数据分布，从而隐藏进不同的异构Peer社区中。显然，这一策略面对传统防御方法或许能够实现绕过，面对MR-FFL时则会被社区内其他用户发现；（2）顾名思义，集中合谋下的攻击者攻击者通过汇报相同的分布而集中在同一个peer社区中。显然，由于我们的综合信用评价同时综合相似度和性能的影响，因此攻击者仍会因为性能不佳而降低评价。我们可以设定一个参与FFL的最低信用值，拥有过多恶意用户的peer社区也会被排除出后续训练。
-% When attackers possess multiple compromised UAV nodes, these nodes can conspire to launch collusion attacks.
-MR-FFL can effectively thwart collusion attacks through simple configurations.
-Specifically, within MR-FFL, attackers may adopt either a "distributed collusion" or a "centralized collusion" strategy: (a) Attackers engaged in distributed collusion report distinct data distributions, thereby concealing themselves within different heterogeneous peer communities.
-While this strategy might potentially evade traditional defense methods, when facing MR-FFL, it becomes detectable by other users within the community; (b) As the name implies, attackers engaging in centralized collusion report identical distributions and concentrate within the same peer community.
-However, due to our comprehensive credit evaluation, which considers both similarity and performance impacts, attackers are still subject to diminished evaluations due to poor performance.
-A minimum credit threshold for participation in FFL can be set, and peer communities with an excess of malicious users can be excluded from subsequent training.
-
-% \subsubsection{UAV nodes selection}
-% %在每轮外部同步结束，我们重新选择客户构建下一轮参与联合学习的super node。
-% %为了尽可能地消除攻击者的干扰，我们设计簇内客户选择机制，客户被选中参与联合学习的概率由其上一轮次的综合信用评价决定。在簇$c$中，用sigmoid函数量化客户$i$被选中的概率：
-% After each round of FFL training, we reconstruct colleague communities as participants for the next round.
-To mitigate the impact of potential attacks, we introduce a client selection mechanism within the peer community.
-The probability of a client being chosen to participate in FFL is determined by its current comprehensive credit evaluation.
-Drawing inspiration from \cite{zhou2022defta}, we employ a Sigmoid-like function to quantify this probability of UAV $U_i$:
-% \begin{equation}
-% \psi^{i}_t=\frac{1}{1+e^{-k (\Phi^{i}_{t}-\gamma)}},\forall U_i \in \mathbf{U}, \forall t
-% \end{equation}
-% %其中$k$为控制sigmoid斜率的参数。由于$\Phi^{i}_{t}\in [0,1]$,我们规定选择概率函数的定义域在[0,1]区间内。可以看出选择概率函数在定义域内的值域$[\frac{1}{1+e^{0.5k}},\frac{1}{1+e^{-0.5k}}]$取决于参数$k$。在实际应用中，为了使选择概率在定义域内尽可能接近0和1，一般选择较大的斜率$k$。
-% where $k$ controls the slope of the Sigmoid function.
-As $\Phi^{i}_{t}\in [0,1]$, we stipulate that the domain of the probability function $\psi^{i}_t$ lies within $[0,1]$.
-It can be observed that the range of $\psi^{i}_t$ is $[\frac{1}{1+e^{\gamma k}},\frac{1}{1+e^{-\gamma k}}]$, depending on $k$.
-In practical applications, to ensure that the selection probability function closely approaches 0 (malicious clients) and 1 (benign yet heterogeneous clients) within its domain, a larger slope parameter $k$ is usually chosen.
-
-% \textbf{Positive assumption for fairness among benign UAVs:} It is worth mentioning that, different from existing methods' negative assumption, we initiate the selection with positive assumption, i.e., $\Phi^{i}_{0}=1 ,\forall U_i\in \mathbf{U}$, which provides high selective probability for inexperienced new participants.
-Therefore, this approach can achieve more fair selection results among benign UAV nodes and maximize client participation.
-Besides, we obtain a more comprehensive evaluation of credit, drastically mitigating the potential impact of adversarial behavior.
-
-% %服务器基于本轮综合信用评分选择客户参与下一轮次的训练，为了尽可能地提高客户的参与率，得到更全面、完整的客户信誉评估结果，将综合信誉作为客户属性进行持久化存储，服务器将赋予客户乐观的初始综合信誉并在每轮交互中更新客户的最新综合信誉。
-% %The server selects clients for the next training round based on the current comprehensive credit score.
-In order to maximize client participation, achieve a more comprehensive and complete client credit assessment, and persistently store the comprehensive credit as a client attribute, the server endows clients with an optimistic initial comprehensive credit.
-% %乐观的初始信誉和时间延迟的信誉更新增加了参与训练次数较少的客户被选中的概率，能够更全面、完善地评估所有客户的信誉，避免潜在攻击的影响。
-% %This initial credit, along with delayed credit updates over time, increases the probability of selecting clients with fewer training participations.
-This approach aims to provide a more comprehensive and thorough evaluation of all clients' reputations, mitigating the potential impact of adversarial behavior.
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % \begin{algorithm}[t]
-% % \caption{algorithm credit} %算法的名字
-% % \begin{algorithmic}[1]
-% %  \State \textbf{\bf Input:Model Variation of Client i $\Delta\widetilde{\omega^{i}_{t}}$, Model Variation of Cluster c $\Delta\widetilde{\omega^{c}_{t-1}}$}
-% % \State\textbf{Output:Comprehensive Credit of Client $\Phi^{i}_{t}$,Peputation Opinion Vector $\Upsilon^{i}_{t}$} 
-% % \State \textbf{Initialize:$u^{c \rightarrow i}_{0}=\frac{\sigma_{c}-\sigma_{min}}{\sigma_{max}-\sigma_{min}}$,$b^{c \rightarrow i}_{0}=1-u^{c \rightarrow i}_{0}$,$d^{c \rightarrow i}_{0}=0$}
-% % \For{$r \in 1,\cdots,R$}
-% %     \State {\color{CadetBlue}/*\textbf{Credit in cluster $c$ */}}
-% %         \For{each client $i \in c$ }
-% %             \If{client $i \in C \cap S$ }
-% %                 \State $ \alpha^{c,i}_{t} = \alpha( \Delta\widetilde{\omega^{c}_{t-1}}, \Delta\widetilde{\omega^{i}_{t}}) = \frac{\langle \Delta\widetilde{\omega^{c}_{t-1}},\Delta\widetilde{\omega^{i}_{t}}\rangle}{\Vert \Delta\widetilde{\omega^{c}_{t-1}}\Vert\cdot\Vert \Delta\widetilde{\omega^{i}_{t}}\Vert }$,
-% %                 \State$p^{c \rightarrow i}_{t} = \alpha^{c,i}_{t} -(-1)$,$n^{c \rightarrow i}_{t} = 1-\alpha^{i,j}_{t}$,
-% %                 \State \textbf{update  $\Upsilon^{c \rightarrow i}_{t},\Phi^{c \rightarrow i}_{r,time}$ with equation}
-% %                 \State $\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{r,time}$
-% %             \Else
-% %                 \State$\Phi^{c \rightarrow j}_{t}=\Phi^{c \rightarrow i}_{t-1}$
-% %             \EndIf
-% %          \EndFor
-% %     \State {\color{CadetBlue}/*\textbf{Credit in supernode $s$ */}}
-% %     \For{each supernode $s_{m} \in S-s_{m}$}
-% %         \State $\alpha^{s_{m},s_{m^{\prime}}}_{t}= \alpha( \Delta \widetilde{\omega^{s_{m}}_{t}},  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}) = \frac{\langle  \Delta\widetilde{\omega^{s_{m}}_{t}}, \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\rangle}{\Vert  \Delta\widetilde{\omega^{s_{m}}_{t}}\Vert\cdot\Vert  \Delta\widetilde{\omega^{s_{m^{\prime}}}_{t}}\Vert }$,
-% %         \State $PI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = \alpha^{s_{m},s_{m^{\prime}}} -(-1)$,$ NI^{s_{m} \rightarrow s_{m^{\prime}}}_{t} = 1-\alpha^{s_{m},s_{m^{\prime}}}_{t}$
-% %         \State \textbf{update $\UpsiloNI^{s_{m} \rightarrow s}_{t},\Phi^{s}_{t}$ with equation}
-% %     \EndFor
-% %     \For{each client $i \in S$}
-% %         \State $\Phi^{s \rightarrow i}_{t}=\Phi^{s}_{t} $
-% %     \EndFor
-% %     \State {\color{CadetBlue} /*\textbf{Comprehensive credit */}}
-% %     \For{each client $i \in Clients$}
-% %         \If{client $i \in C\cap S$ }
-% %         \State \textbf{update $\Upsilon^{i}_{t},\Phi^{i}_{t}$ with equation}
-% %         \Else 
-% %         \State $\Phi^{i}_{t} = \Phi^{i}_{t-1}$
-% %         \EndIf
-% %     \EndFor
-% % \EndFor
-% % \end{algorithmic}
-% % \end{algorithm}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}[tb]
-% 	\begin{minipage}[!t]{0.49\linewidth}
-% 		\centering
-% 		\includegraphics[width=\linewidth]{results/SCC_diff.pdf}
-% 		%\vspace{-2em}
-% 		\caption{$L_2$-divergence}
-% 		\label{results:1-diff}
-% 	\end{minipage}
-%         \begin{minipage}[!t]{0.49\linewidth}
-% 		\centering
-% 		\includegraphics[width=\linewidth]{results/SCC_time.pdf}
-% 		%\vspace{-2em}
-% 		\caption{Running time}
-% 		\label{results:1-time}
-% 	\end{minipage}
-% \end{figure}
-
-% \begin{figure}[!t]
-% \centering
-% \includegraphics[width=\linewidth]{results/SCC_acc.pdf}
-% \caption{The accuracy comparison between MR-FFL with existing heterogeneity-robust methods.}
-% \label{results:1-acc}
-% \end{figure}
-
-% \section{Experimental results}
-% \subsection{Experimental settings}
-% Experiments were conducted using the PyTorch deep learning framework, employing two widely adopted benchmark datasets (EMNIST and CIFAR).
-To demonstrate the defense performance of the proposed MR-FFL scheme, we conduct both explicit (Flipping attack) and implicit (Backdoor attack) attack paradigms.
-%The EMNIST dataset encompasses 10 categories for digits and 52 categories for uppercase and lowercase English letters, totaling 62 categories.
-All images have dimensions of 28x28 pixels.
-% In line with the methodologies of previous studies \cite{mohri2019agnostic,tan2022fedproto, zeng2022heterogeneous}, our experiments were conducted under a non-iid setting, implementing non-uniform sampling within the dataset.
-% To create an equitable but dissimilar distribution among clients, we extracted 12,0000 training samples and 30,000 testing samples, allocating them in an 8:2 ratio between the training set and the validation set.
-This ensured that each client possessed an equal number of samples in the training dataset, albeit with distinct data distributions.
-%Two neural network architectures, a simple CNN and an MLP, were employed to undertake the Federated Learning (FL) task on the EMNIST dataset.
-The detailed configurations of the local network models are delineated in Tables 2 and 3.
-% Throughout our experiments, we configured $200\sim 500$ UAV nodes.
-A total of 200 communication rounds were executed, where the local training epoch for each $U_i$ is 5, the batch size is 128, the learning rate $\eta$ is 0.1, and the momentum is 0.9.
-
-% \subsection{The effectiveness of MR-FFL in heterogeneous UAV network}
-
-% To verify the effectiveness of our stratified community construction mechanism, we compare it with existing heterogeneity-robust methods in terms of divergence reduction, running time, and learning performance.
-We choose three benchmark methods (\textbf{Random}, \textbf{Bayesian}, \textbf{Generic algorithms}) and two latest methods (\textbf{Cohort} \cite{hiessl2022cohort} and \textbf{GBP-CS} \cite{li2022data}).
-% In terms of divergence reduction, as shown in Figure \ref{results:1-diff}, our method significantly reduces both the average maximum divergences and deviation among clients, which indicates better robustness.
-% Regarding execution time, SCC requires only one operation to generate a sampling template.
-Subsequently, it performs random sampling based on the template, resulting in a short execution time.
-This advantage becomes more pronounced with increasing rounds.
-As shown in Figure \ref{results:1-time}, our method is more time-saving than other alternative methods.%On the other hand, Bayesian sampling and Genetic Algorithm have excessively long execution times, which are not acceptable.
-The Cohort algorithm has a relatively short runtime, but it suffers from a large deviation from the target distribution.
-GBP-CS algorithm needs sampling before each iteration, and its runtime is not as efficient as the QIP algorithm.
-
-% In terms of learning performance, we also compared three representative algorithms (\textbf{FedAvg} \cite{li2019convergence-fedavg}, \textbf{FedNova} \cite{wang2020tackling-fednova}, \textbf{FedProx} \cite{yuan2022convergence-fedprox}) with MR-FFL.
-As illustrated in Figure \ref{results:1-acc}, vanilla FL algorithms exhibit slow convergence rates and poor performance with large fluctuations in heterogeneous environments.
-In comparison to heterogeneous FL algorithms like FedNova and FedProx, MR-FFL continues to achieve better convergence speed, stability, and accuracy.
-
-% \subsection{The performance of MR-FFL against poisoning attacks}
-% \begin{figure*}[!t]
-% \centering
-% \subfloat[EMNIST (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_MINIST_acc.pdf}%
-% \label{result0:acc-EMNIST-FLIP}}
-% \hfil
-% \subfloat[CIFAR (Flipping)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/Flip_Cifar_acc.pdf}%
-% \label{result0:acc-CIFAR-FLIP}}
-% \hfil
-% \subfloat[EMNIST (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_MINIST_att_acc.pdf}%
-% \label{result0:acc-EMNIST-Backdoor}}
-% \hfil
-% \subfloat[CIFAR (Backdoor)]{\includegraphics[width=0.25\linewidth]{results-new/accuracy/BACKDOOR_Cifar_att_acc.pdf}%
-% \label{result0:acc-CIFAR-Backdoor}}
-% \caption{The defense performance comparison between MR-FFL with existing poisoning-resistant methods against Flipping and Backdoor attacks.}
-% \label{results:0-acc}
-% \end{figure*}
-
-% % %%%%%%%%%%%%EMNIST+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % \begin{figure}[!t]
-% % \centering
-% % \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_MINIST_cr_1.pdf}%
-% % \label{result1:credit-AAD}}
-% % \hfil
-% % \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_MINIST_pr_1.pdf}%
-% % \label{result1:prob-AAD}}
-% % \hfil
-% % \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_MINIST_cr_1.pdf}%
-% % \label{result1:credit-FLtrust}}
-% % \hfil
-% % \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_MINIST_pr_1.pdf}%
-% % \label{result1:prob-FLtrust}}
-% % \hfil
-% % \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_MINIST_cr_1.pdf}%
-% % \label{result1:credit-MRFFL}}
-% % \hfil
-% % \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_Flip_MINIST_pr_1.pdf}%
-% % \label{result1:prob-MRFFL}}
-% % \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on EMNIST.}
-% % \label{results_EMNIST_flip}
-% % \end{figure}
-
-% % %%%%%%%%%%%EMNIST+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
-% % \begin{figure}[!t]
-% % \centering
-% % \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_MINIST_cr_1.pdf}%
-% % \label{result2:credit-AAD}}
-% % \hfil
-% % \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_MINIST_pr_1.pdf}%
-% % \label{result2:prob-AAD}}
-% % \hfil
-% % \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_MINIST_cr_1.pdf}%
-% % \label{result2:credit-FLtrust}}
-% % \hfil
-% % \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_MINIST_pr_1.pdf}%
-% % \label{result2:prob-FLtrust}}
-% % \hfil
-% % \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_MINIST_cr_1.pdf}%
-% % \label{result2:credit-MRFFL}}
-% % \hfil
-% % \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFLL_BACKDOOR_MINIST_pr_1.pdf}%
-% % \label{result2:prob-MRFFL}}
-% % \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on EMNIST.}
-% % \label{results_EMNIST_Backdoor}
-% % \end{figure}
-% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % %%%%%%%%%%%%CIFAR+Flip%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % \begin{figure}[!t]
-% % \centering
-% % \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_Flip_Cifar_cr_1.pdf}%
-% % \label{result3:credit-AAD}}
-% % \hfil
-% % \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_Flip_Cifar_pr_1.pdf}%
-% % \label{result3:prob-AAD}}
-% % \hfil
-% % \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_Flip_Cifar_cr_1.pdf}%
-% % \label{result3:credit-FLtrust}}
-% % \hfil
-% % \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_Flip_Cifar_pr_1.pdf}%
-% % \label{result3:prob-FLtrust}}
-% % \hfil
-% % \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_Flip_Cifar_cr_1.pdf}%
-% % \label{result3:credit-MRFFL}}
-% % \hfil
-% % \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_Flip_Cifar_pr_1.pdf}%
-% % \label{result3:prob-MRFFL}}
-% % \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Flipping on CIFAR.}
-% % \label{results_Cifar_flip}
-% % \end{figure}
-% % %%%%%%%%%%%CIFAR+Backdoor%%%%%%%%%%%%%%%%%%%%%%%
-% % \begin{figure}[!t]
-% % \centering
-% % \subfloat[Credit (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/AAD_BACKDOOR_Cifar_cr_1.pdf}%
-% % \label{result4:credit-AAD}}
-% % \hfil
-% % \subfloat[PR (AAD)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/AAD_BACKDOOR_Cifar_pr_1.pdf}%
-% % \label{result4:prob-AAD}}
-% % \hfil
-% % \subfloat[Credit (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/FL_BACKDOOR_Cifar_cr_1.pdf}%
-% % \label{result4:credit-FLtrust}}
-% % \hfil
-% % \subfloat[PR (FLTrust)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/FL_BACKDOOR_Cifar_pr_1.pdf}%
-% % \label{result4:prob-FLtrust}}
-% % \hfil
-% % \subfloat[Credit (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Credit/MRFLL_BACKDOOR_Cifar_cr_1.pdf}%
-% % \label{result4:credit-MRFFL}}
-% % \hfil
-% % \subfloat[PR (MR-FFL)]{\includegraphics[width=0.5\linewidth]{results-new/Prob/MRFFL_BACKDOOR_Cifar_pr_1.pdf}%
-% % \label{result4:prob-MRFFL}}
-% % \caption{The credit scores (after 200 rounds) and selection probabilities of different methods (AAD, FLTrust, MR-FFL) against Backdoor on CIFAR.}
-% % \label{results_Cifar_Backdoor}
-% % \end{figure}
-% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Subsequently, to further demonstrate the advantages of the MR-FFL method in ensuring model integrity, we compare our approach with existing representative reliable FL algorithms, including \textit{mitigation-oriented} \cite{blanchard2017machine-krum,yin2018byzantine-trimmedmean}, \textit{detection-oriented} \cite{andreina2021baffle}, and \textit{credit-oriented} \cite{li2019abnormal,cao2020fltrust}.
-The total number of UAV ndoes is set to 200.
-As shown in Figure \ref{results:0-acc}, we conduct explicit attacks (flipping) and compare the training accuracy in Figure \ref{result0:acc-EMNIST-FLIP} and \ref{result0:acc-CIFAR-FLIP}.
-Higher accuracy means better defense effect.
-Meanwhile, the backdoor task accuracy (implicit attack) on EMNIST and CIFAR is demonstrated in Figure \ref{result0:acc-EMNIST-Backdoor} and \ref{result0:acc-CIFAR-Backdoor}, respectively.
-Lower backdoor accuracy indicates better defense performance.
-% Based on the results, it is evident that mitigation-oriented schemes such as \textbf{Trimmed-mean} \cite{yin2018byzantine-trimmedmean} exhibit significant deviations from the global objectives in heterogeneous environments, resulting in lower accuracy.
-\textbf{BaFFLe} \cite{andreina2021baffle}, as a detection-oriented method, struggles to converge rapidly and requires additional validation rounds, incurring substantial communication and time overhead.
-For credit-oriented methods \textbf{AAD} \cite{li2019abnormal} and \textbf{FLTrust} \cite{cao2020fltrust}, although AAD can permanently ban attackers, the gap between heterogeneous gradients and attacker gradients relative to the pre-trained global model leads to erroneous elimination, resulting in an overall performance decline.
-Similarly, in FLTrust, heterogeneous UAVs with gradients opposite to the direction of server-side model updates face challenges participating in the global model aggregation, causing a decline in model performance.
-
-% Furthermore, in Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, through a comparative analysis of credit assessment values and selection probabilities with existing methods such as AAD (based on autoencoder) and FLTrust (based on bootstrapping), we validate the effectiveness of the credit evaluation mechanism in the MR-FFL scheme.
-This validation is crucial for guiding subsequent hyperparameter tuning and adaptive configurations.
-As illustrated in the first rows of those figures, the AAD method lacks adaptation to highly heterogeneous environments, leading to the misclassification of numerous legitimate UAV nodes.
-Under FLTrust, as shown in the second rows of above figures, both the credit of normal UAV participants and their selection probabilities exhibit significant fluctuations, with a lack of robustness in detecting certain covert attacks.
-In contrast, MR-FFL evaluates the integrity of UAV nodes in terms of both community-wide similarity and performance.
-As shown in the third rows of Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, our method can accurately identify the stealthy malicious attackers from benign nodes.
-
-% \subsection{The fairness of MR-FFL under adversarial environments}
-% One of the important drawbacks of existing security technologies is unfairness.
-As shown in the second columns of Figure \ref{results_EMNIST_flip} to \ref{results_Cifar_Backdoor}, except for the low accuracy, AAD and FLTrust also assign vastly different selection probabilities to benign UAV nodes.
-Different from existing methods, MR-FFL employs a Sigmoid function to optimize the selection strategy, resulting in a clearer distinction between attackers and normal users (e.g., Figure \ref{result3:credit-MRFFL} and \ref{result4:credit-MRFFL}).
-Hence, the probabilities of legitimate clients being selected are approximate (e.g., Figure \ref{result1:prob-MRFFL} and \ref{result2:prob-MRFFL}), ensuring fairness among benign UAV nodes.
 

### 2024-11-02 response.tex
yesterday: archive - mainly me
先协助学弟把OWA迁移过去

@@
 
+% 修改后的结果如图\ref{fig:lab2}所示，同时我们也修改了文章中相应的分析部分，使其更易符合实验结果并且更易理解。
+\begin{figure*}[!h]
+    \centering
+    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
+    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE.
+The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa.
+}
+    \label{fig:lab2}
+\end{figure*}
+
+Figure \ref{fig:lab2} shows the image after modification.
+We also updated the corresponding analysis section in the article to better align with the experimental findings and enhance readability.
+The revised analysis is shown below:
+
+\textcolor{blue}{SecFFT outperforms other mechanisms in handling various attack.
+SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes.
+Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed.
+Among them, FoolsGold exhibits the highest misidentification rate.
+It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}
+
 % comment7
@@
 
-Thank you for pointing this out.
+\textbf{Response:} Thank you for pointing this out.
 Our Figure 3 corresponds to Section B, 2) of the Methodology section.
@@
 
-Thank you for your suggestion.
+% 感谢您指出文本中描述行数与算法不一致的问题。我们已根据算法的最新修改，仔细检查并修正了第五节最后一段中的行数描述，确保其与算法2的步骤完全对齐。具体来说，我们逐条对照了算法中的每个步骤，确保每个操作、条件和循环都在文本中得到了准确反映。
+
+% 此外，我们在修订过程中还增强了描述的清晰度，以便读者能够更容易理解算法的执行流程。我们还添加了必要的背景信息和解释，以帮助读者在上下文中更好地理解每一步的意义和目的。
+
+% 这些修改不仅提高了文本的准确性，也增强了整篇论文的逻辑连贯性。我们非常感谢您对此问题的关注，这使我们能够提升稿件的整体质量和可读性。
+
+Thank you for pointing out the inconsistency between the line numbers described in the text and those in Algorithm 2.
+We have carefully reviewed and revised the final paragraph of Section 5 to ensure that it aligns perfectly with the updated steps in the algorithm.
+Specifically, we compared each step in the algorithm with the corresponding actions, conditions, and loops described in the text to ensure accurate representation.
+
+In addition to correcting the line numbers, we enhanced the clarity of the descriptions during the revision process.
+This makes it easier for readers to understand the execution flow of the algorithm.
+We also added necessary background information and explanations to help readers grasp the significance and purpose of each step within the context.
+
+These modifications not only improve the accuracy of the text but also enhance the logical coherence of the entire paper.
+We greatly appreciate your attention to this issue, which has allowed us to elevate the overall quality and readability of the manuscript.
+
+\textcolor{blue}{We summarize the algorithm in the form of pseudocode, as shown in Algorithm \ref{alg:malicious-node-detection-history}.
+Lines 4 to 6 correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds.
+Lines 7 to 12 correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level.
+Lines 13 to 22 correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm.
+Finally, lines 23 to 25 correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.
+}
 
@@
 
-\textbf{Response:}
-
-Thank you for your valuable feedback on Algorithm 2. We have reviewed the conditions and updated the descriptions to ensure they are clear and unambiguous. Specifically:
+\textbf{Response:} Thank you for your valuable feedback on Algorithm 2. We have reviewed the conditions and updated the descriptions to ensure they are clear and unambiguous. Specifically:
 
@@
     \item \textbf{"while Not Converged do"}: We revised this condition to include the specific convergence criteria used in the algorithm.
-This provides a clear stopping condition, ensuring that readers understand when the loop will terminate.
+This provides a clear stopping condition of $\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$, ensuring that readers understand when the loop will terminate.
 
@@
 
+% 除此之外，我们还发现了一个小细节，即原本的注释中注释符号和注释内容左右空格数量不一致，我们顺便修复了这个错误。
+
+In addition, we also discovered a small detail that the number of spaces left and right in the original comments was inconsistent between the comment symbols and the comment content.
+We also fixed this error.
+
 These modifications provide a more detailed and precise description of the algorithm’s flow.
 We appreciate your insights and believe these clarifications enhance the readability and understanding of Algorithm 2.
+
+% 现在的算法2伪代码如下所示：
+
+% TODO: 现在有一个问题就是，文章中的算法2在Response中出现更早，因此编号变成了Algorithm 1
+The pseudocode for Algorithm 2 is as follows:
+
+\begin{algorithm}
+\caption{Attack intention detection and secure aggregation}
+\label{alg:malicious-node-detection-history}
+\begin{algorithmic}[1]
+\State \textbf{Input:} Global model history $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$
+\State \textbf{Output:} Sets of normal clients $U_{nor}$ and malicious clients $U_{mal}$
+
+\For {Client \textcolor{blue}{$i\in \{1\ldots N\}$}}
+
+\State{\color{CadetBlue}/* \textbf{Construction of updates and model databases */}} 
+    \State Record flattened gradients $\bar{\theta_i^t}$ and models $\theta_g^{t-1}$
+    % \State $\widetilde{\theta_{i}^{t'-1}}  \gets Flatten(\theta_g^{t'-1})$, ${v}_{i}^{t'}  \gets \overline{\triangledown\theta_{i}^{t'}}$ for $t'  \gets \max\{t-T+1, 1\}, \ldots, t$ \Comment{Construct rays}
+    \State Construct rays for each $'$, $\max\{t-T+1, 1\}\leq t' \leq t$
+
+\State{\color{CadetBlue}/* \textbf{Construction of attack intention */}}
+
+    \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
+    \While {\textcolor{blue}{$\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$}}
+        \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
+    \EndWhile
+    \State  $cre_i  \gets \frac{1}{r_i + \rho}$ \Comment{Calculate confidence}
+
+\State{\color{CadetBlue}/* \textbf{LOF-driven malicious intention detection */}}
+
+    \For {Each point $O_j \neq O_i$\textcolor{blue}{, $j\in\{1\ldots N\}$}}
+        \State Calculate distance $\|O_i - O_j\|$
+    \EndFor
+    \State Determine $q$-distance $\widetilde{dis_i^q}$ for $O_i$
+    \State Find neighbors $Nei_i$ within $\widetilde{dis_i^q}$
+    \State $rea_{i,j}  \gets \max\{\widetilde{dis_i^q}, \|O_i - O_j\|\}$ for $O_j \in Nei_i$  \Comment{Compute reachability distance}
+    \State  $lrd_i  \gets \frac{|Nei_i|}{\sum_{j \in Nei_i} rea_{i,j}}$ \Comment{Calculate reachability density}
+    \State $lof_i  \gets \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
+
+% \For {Client $i$}
+%     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
+%     \If {$lof_i > 1$}
+%         \State Mark client $i$ as malicious, add to $U_{mal}$
+%     \Else
+%         \State Mark client $i$ as normal, add to $U_{nor}$
+%     \EndIf
+% \EndFor
+% \State $U_{mal} = \{i \,|\, lof_i > 1\}$
+% \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
+\State $U_{mal}, U_{nor}  \gets \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$
+
+\State{\color{CadetBlue}/* \textbf{Secure aggregation of global FFT model */}} 
+        \State $cre_i'  \gets \tanh(cre_i)$\Comment{Compute adjusted confidence}
+        \State $w_i  \gets \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$\Comment{Normalize weights}
+\EndFor
+
+\State \textbf{Output:} $\theta_g^t \gets \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$\Comment{Aggregate global model}
+\end{algorithmic}
+\end{algorithm}
 
@@
 }
+\textbf{Response:} 
+Thank you for your valuable comments and suggestions, which have greatly helped us to improve our paper. We have carefully addressed each of the issues you raised and made the following modifications:
 
-Thank you for your suggestion.
+First, we recognized the need for a more in-depth quantitative analysis in this section.
+We have now included additional statistical data to provide a comprehensive analysis of the experimental results, including metrics that better quantify the effectiveness of our partitioning method.
+This has been added to enhance the clarity and significance of our findings.
+The following are the corresponding modifications in the article:
+
+\textcolor{blue}{This indicates that SecFFT effectively defends against attacks by accurately identifying and neutralizing malicious users, all while preserving the performance and accuracy of the global model.
+In contrast, other defense mechanisms perform less effectively.
+Although Flame also shows strong performance in reducing ASR and mitigating malicious attack, it introduces considerable noise in the identification process, leading to a decrease in TSR, especially under MR attacks, where the performance degradation is more pronounced.
+FLTrust fails to defend effectively, with ASR initially low in MR attacks but quickly rising after several iterations, ultimately proving ineffective; against NEUR and EDGE CASE attacks, ASR remains high from the outset, demonstrating inadequate defense.
+Foolsgold also shows poor performance in defending against all three types of attacks, maintaining a high ASR from the beginning.
+Overall, the comparison highlights that other defense mechanisms either fail to effectively resist attacks or compromise model performance during defense.
+This further underscores SecFFT's significant advantage in federated fine-tuning for backdoor attack resistance, making it the optimal defense choice.}
+
+\textcolor{blue}{......}
+
+\textcolor{blue}{SecFFT outperforms other mechanisms in handling various attack.
+SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes.
+Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed.
+Among them, FoolsGold exhibits the highest misidentification rate.
+It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}
+
+Second, to improve the visibility and distinguish-ability of the partitioning results in Figure 6, we have added a supplementary sub-image that provides a clearer presentation of the partitioned sections.
+We also increased the font size to enhance readability, ensuring that key features are visible and easy to interpret.
+For details, please refer to Figure \ref{fig:lab1} and responses to the comment 2 from Reviewer 2.
+
+Third, we re-adjusted the layout of Figure 7 to address the issues you pointed out.
+Specifically, we improved the font sizes, added necessary labels, and modified the legend for better comprehension.
+These adjustments were made to ensure that the experimental data in Figure 7 are both readable and visually clear.
+For details, please refer to Figure \ref{fig:lab2} and responses to the comment 1 from Reviewer 1.
 
@@
 }
+\textbf{Response:} 
 Thank you for your feedback and suggestions for improving the clarity of our paper.
@@
 }
-
+\textbf{Response:} 
 % 对于第一个实验：Model integrity and poisoning resistance，我们重新整理了相应数据，并修改了图片的表现形式。修改包括对图例字体格式以及大小的修改，同时为图中折现重合的部分加上了子图，使其更容易辨别。同时，我们也修改了原文中对于该实验结果的描述，使其更符合实验数据，同时更易于阅读和理解。
@@
 }
-
+\textbf{Response:} 
 Thank you for your valuable feedback. We appreciate your comments regarding the grammatical errors and unclear expressions in the manuscript.
@@
 }
-% 问题：技术框架解释性不足，比如Fig2步骤解释过于粗略，难以理解。
+
 \textbf{Response:} 
-We thanks the Reviewer for the comment.
+Thank you for your valuable feedback. We appreciate your insights, especially regarding the need for further detail in the technical framework explanation and the steps illustrated in Figure 2.
+
+In response, we have carefully considered your suggestions and revised the framework diagram to enhance clarity and detail.
+The new version of Figure 2 (which depicted as Figure \ref{fig2:instant}) has been redrawn to illustrate each step in the algorithm more thoroughly, ensuring that readers can understand the entire process without ambiguity.
+We have added comprehensive explanations for each step, including intermediate processes and transitions, to provide a clearer and more accessible description of the framework.
+These changes are intended to ensure that the entire flow of the framework is presented in a more intuitive and informative manner.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\linewidth]{figures/secfft-1.pdf}
+    \caption{SecFFT's instantaneous attack behavior perception module with frequency-domain deep outlier feature semantics extraction}
+    \label{fig2:instant}
+\end{figure}
 
@@
 
+% \begin{algorithm}
+% \caption{Instantaneous Attack Behavior Perception}
+% \label{alg:malicious-node-detection}
+% \begin{algorithmic}[1]
+% \State \textbf{Input:} $d$, $N$, $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$, $m$ \Comment{$d$ is the dimension of each update; $N$ is the number of nodes participating during each round; $(\triangledown \theta_0^t, \triangledown \theta_1^t, \ldots, \triangledown \theta_N^t) \in \mathbb{R}^{N \times d}$ is the local updates from robot nodes during the $t$-th round; $m$ is the length of low-frequency components}
+% \State \textbf{Output:} $U_{nor}$, $U_{mal}$ \Comment{benign nodes, malicious nodes}
+% \State{\color{CadetBlue}/* \textbf{Frequency Domain Transformation */}} 
+% % \State Step 1: Frequency Domain Transformation
+% \For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
+%     \State \textcolor{blue}{$G_i^t \gets Trunc(DCT(Flatten(\triangledown \theta_i^t))), m)$}
+% \EndFor
+
+% % \State
+% \State{\color{CadetBlue}/* \textbf{Clean Ingredient Extraction */}} 
+% % \State Step 2: Clean Ingredient Extraction
+% \State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering\textcolor{blue}{ (G_0^t, G_1^t, \ldots, G_N^t)}$ \Comment{$\kappa$ denotes the number of clusters}
+% \State \textcolor{blue}{$ C^t_{max} \gets \underset{C^t_j}{\arg\max} \, |C^t_j|$ \Comment{$|C^t_j|$ denotes the number of nodes in cluster $C^t_j$, $j = 1, 2, \ldots, \kappa $}}
+% \State $H^t \gets (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C^t_{max}$.}
+
+% \State $\hat{H}^t \gets (H^t)^{T} H^t$
+% \State $\lambda_{max}^t, \xi_{max}^t \gets eig(\hat{H}^t)$ \Comment{Calculating the maximum singular value and its corresponding eigenvector}
+% \State $\tilde{G}^t \gets \frac{H^t \xi_{max}^t}{\sqrt{\lambda_{max}^t}}$ \Comment{The clean ingredient}
+
+% % \State
+% \State{\color{CadetBlue}/* \textbf{Chi-square distance calculation */}} 
+% % \State Step 3: Chi-square distance calculation
+% % \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
+% \For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
+% \State \textcolor{blue}{$Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{{|\tilde G}^t[k]| + \epsilon}}$}
+% \EndFor
+% \State \textcolor{blue}{$S^t \gets \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}$} \Comment{The Distance differences calculated by Chi-square distance.}
+
+% % \State
+% \State{\color{CadetBlue}/* \textbf{Single-round malicious behavior perception */}} 
+% % \State Step 4: Single-round malicious behavior perception
+% \State $\textcolor{blue}{\{{C^t_1}', {C^t_2}'\}} \gets KMeans(S^t, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
+% \State \textcolor{blue}{$U_{nor} \gets C'_{max}$, $U_{mal} \gets \{C'_i \, | \, i \neq max\}$}
+
+% \end{algorithmic}
+% \end{algorithm}
+
 \begin{algorithm}
@@
 \For {$R_i \in \textcolor{blue}{\{R_1, \ldots, R_N\}}$}
-\State \textcolor{blue}{$Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{{|\tilde G}^t[k]| + \epsilon}}$}
+    \State \textcolor{blue}{$Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|{\tilde G}^t[k]| + \epsilon}}$}
 \EndFor
@@
 % 谢谢你的建议，表格2的宽度确实有些过长，已经超出了半栏的范围，甚至已经与右侧栏目的内容产生了融合。我们对这个表格进行了调整，适当缩小了表格的宽度，使得表格在不影响整体观感的同时，保证了表格格式符合要求，且不超过单栏范围。
-
+\textbf{Response:} 
 Thank you for your suggestion.
@@
 }
-
+\textbf{Response:} 
 We appreciate the reviewer’s insightful feedback.
@@
 }
-
+\textbf{Response:} 
 Thank you for pointing out the inconsistency in figure referencing throughout the manuscript.
@@
 After evaluating our available resources and validating our preliminary results, we settled on a configuration that fits the scope of our work while ensuring robust performance.
-
+\textbf{Response:} 
 Thank you for your insightful comments. We have carefully considered your concerns regarding the hyperparameter settings and provide a detailed explanation below:
@@
 }
+\textbf{Response:} 
 Thank you for your valuable feedback regarding the incorrect symbol usage in the manuscript.

### 2024-11-02 main-v2.tex
yesterday: archive - mainly me
先协助学弟把OWA迁移过去

@@
     \centering
-    \includegraphics[width=\linewidth]{figures/fig2.png}
+    \includegraphics[width=1\linewidth]{figures/secfft-1.pdf}
     \caption{SecFFT's instantaneous attack behavior perception module with frequency-domain deep outlier feature semantics extraction}
@@
 We summarize the algorithm in the form of pseudocode, as shown in Algorithm \ref{alg:malicious-node-detection-history}.
-Lines 3 to 7 correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds.
-Lines 8 to 15 correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level.
-Lines 16 to 27 correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm.
-Finally, lines 28 to 32 correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.
+Lines \textcolor{red}{4 to 6} correspond to Step 1, which outlines the method for retaining historical records for \(T\) rounds.
+Lines \textcolor{red}{7 to 12} correspond to Step 2, which describes the use of the minimum enclosing hypersphere algorithm to determine each robot node's intent point and confidence level.
+Lines \textcolor{red}{13 to 22} correspond to Step 3, which explains how to identify normal and abnormal nodes using the LOF algorithm.
+Finally, lines \textcolor{red}{23 to 25} correspond to Step 4, which illustrates the method for performing weighted aggregation based on each robot node's confidence level.
 
@@
 
-% \For {Client $i$ \in 55}
+\For {Client \textcolor{red}{$i\in \{1\ldots N\}$}}
+
 \State{\color{CadetBlue}/* \textbf{Construction of updates and model databases */}} 
@@
     \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
-    \While {Not Converged}
+    \While {\textcolor{red}{$\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$}}
         \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
@@
 
-\State{\color{CadetBlue}/* \textbf{LOF-driven malicious intention detection*/}}
-
-    \For {Each point $O_j \neq O_i$}
+\State{\color{CadetBlue}/* \textbf{LOF-driven malicious intention detection */}}
+
+    \For {Each point $O_j \neq O_i$\textcolor{red}{, $j\in\{1\ldots N\}$}}
         \State Calculate distance $\|O_i - O_j\|$
@@
 
-\State{\color{CadetBlue}/* \textbf{Secure aggregation of global FFT model*/}} 
+\State{\color{CadetBlue}/* \textbf{Secure aggregation of global FFT model */}} 
         \State $cre_i'  \gets \tanh(cre_i)$\Comment{Compute adjusted confidence}
@@
 The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
-\textcolor{red}{For single round recognition,} similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
+\textcolor{red}{For instantaneous attack behavior perception,} similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
 ASR denotes the probability that malicious nodes successfully manipulate the global model to predict a specified target.
@@
 The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR.
-\textcolor{red}{For multi round recognition, ``Acc" refers to accuracy, which measures the proportion of correct predictions;``Rec" stands for recall, representing the model's ability to correctly identify positive instances;``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive;``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative;``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}
+\textcolor{red}{For long-term attack intention detection, ``Acc" refers to accuracy, which measures the proportion of correct predictions;``Rec" stands for recall, representing the model's ability to correctly identify positive instances;``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive;``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative;``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}
 
@@
     \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
-    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE dimensionality reduction.
-The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign and benign nodes incorrectly identified as malicious.
+    \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE.
+The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa.
 }
@@
 The specific comparison results are illustrated in Figure \ref{fig:lab2}.
-We employed the t-SNE algorithm to reduce the dimensionality of the nodes' updates across all rounds to a two-dimensional plane.
-In the figure, red dots represent misidentified nodes, which include malicious nodes mistakenly identified as benign and benign nodes mistakenly identified as malicious.
+We employed the t-SNE to reduce the dimensionality of the nodes' updates across all rounds to a two-dimensional plane.
+In the figure, red dots represent misidentified nodes, which include malicious nodes mistakenly identified as benign , or vice versa.
 For the FoolsGold defense algorithm, which does not directly provide node identification results, we employed the KMeans clustering algorithm to classify the aggregation weights assigned to each user during the defense process into two clusters, considering the larger cluster as benign nodes and the remaining as malicious nodes for evaluation purposes.
@@
 Comparatively, SecFFT performs the best in dealing with various attack types, effectively reducing the misidentification rate and showing better generalization ability and accuracy.
-As illustrated in the figure, comparatively, SecFFT outperforms other mechanisms in handling various attack.
+As illustrated in the Figure \ref{fig:lab2}, comparatively, \textcolor{red}{SecFFT outperforms other mechanisms in handling various attack.
 SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes.
 Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed.
-Notably, FoolsGold exhibits the highest misidentification rate, demonstrating suboptimal defense performance in managing complex attack scenarios.
+Among them, FoolsGold exhibits the highest misidentification rate.
+It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}
 

### 2024-11-04 main-v2.tex
archive: responsed all

@@
     $H^t$ & The matrix formed by stacking $G_i^t$. \\ \hline
-    $\tilde{G}^t $ & The extracted global clean ingredient at round $t$. \\ \hline
+    $\tilde{G}^t $ & The extracted clean ingredient at round $t$. \\ \hline
     $\lambda_{max}^t$ & The largest singular value of matrix $H^t$ at round $t$. \\ \hline
@@
 The optimization goal of the problem is to find a minimum hypersphere that covers at least a $\zeta$ proportion of the rays.
+\textcolor{red}{Among them, $\ zeta $is to avoid interference from excessively outlier rays}.
 % 我们使用符号$O_i$代表客户端$i$在高维空间中超球的球心，使用符号$r_i$代表这个超球的半径。假设当前轮次为$t$，$t'$是最近$T$轮次中的其中一轮，使用符号$\tilde O_i^{t'}$代表球心到第$t'$对应射线的最近点。则可以定义优化问题：
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/fig3.png}
+    \includegraphics[width=\linewidth]{figures/fig3-history.pdf}
     \caption{Long-term attack intention detection module and secure aggregation}
@@
 When the difference between the updated radius \( r_{i,k+1} \) and the previous radius \( r_{i,k} \) is smaller than a predefined threshold \( \lambda \), or when the maximum number of iterations $k_{max}$ is reached, the iteration stops.
+
+\textcolor{red}{In our proposed framework, the concept of the "intention point" serves as a pivotal element in recognizing the underlying motives of malicious nodes during the federated fine-tuning process.
+The intention point is defined as the central position within a high-dimensional space, representing the aggregated gradient updates of a client across multiple training rounds.
+This point encapsulates the client's intended direction for influencing the global model.
+To construct the intention point, we utilize a Minimum Enclosing Hypersphere approach, which encompasses a proportion of the client’s gradient updates.
+The radius of this hypersphere reflects the reliability of the intention point, effectively quantifying the client's consistency in updating the model.
+By analyzing these intention points, our method can discern the behaviors of malicious clients from benign ones, enhancing the overall security and robustness of the federated learning system.}
 
@@
 \textbf{Attack paradigms:} we employed three state-of-the-art attacks targeting federated learning scenarios, namely \textbf{MR}\cite{MR}, \textbf{EDGE CASE}\cite{EDGE_CASE}, and \textbf{NEUR}\cite{zhang2022neurotoxin}.
-The MR attack generates a malicious dataset by combining poisoned images with normal ones and employing the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack employs rare "edge-case" samples to inject backdoors into the federated learning model through data or model poisoning; the NEUR attack seeks to identify parameters that are seldom updated during normal node training and uses these parameters to insert backdoors, thereby enhancing the persistence of the backdoor.
+The MR attack generates a malicious dataset by combining poisoned images with normal ones and employing the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack employs rare "edge-case" samples to inject backdoors into the federated learning model through data or model poisoning; the NEUR attack seeks to identify parameters that are seldom updated during normal node training and uses these parameters to insert backdoors, thereby enhancing the persistence of the backdoor\color{red}{\cite{yao2022blockchain}}\color{black}{.}
 
@@
 FLTrust employs a clean dataset and aggregates only those updates from nodes that exhibit high cosine similarity with the updates derived from the clean dataset.
-Flame estimates and injects an appropriate amount of noise via model clustering and weight clipping to mitigate backdoor attacks in federated learning effectively.
+Flame estimates and injects an appropriate amount of noise via model clustering and weight clipping to mitigate backdoor attacks in federated learning effectively\color{red}{\cite{yao2024leoedge}}\color{black}{.}
 

### 2024-11-12 main-v2.tex
archive: 2024.11.5 22:04
《ignore the》

Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR.
-\textcolor{red}{For long-term attack intention detection, ``Acc" refers to accuracy, which measures the proportion of correct predictions;``Rec" stands for recall, representing the model's ability to correctly identify positive instances;``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive;``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative;``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}
+\textcolor{red}{For long-term attack intention detection, ``Acc" refers to accuracy, which measures the proportion of correct predictions; ``Rec" stands for recall, representing the model's ability to identify positive instances correctly; ``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; ``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; ``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}
 
@@
     \centering
-    \includegraphics[width=1\linewidth]{figures/lab2-combined.pdf}
+    \includegraphics[width=0.9\linewidth]{figures/lab2-combined.pdf}
     \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE.

### 2024-11-12 main-v2.tex
response: whom do I really response for?
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
     \centering
-    \includegraphics[width=\linewidth]{figures/fig4.jpg}
+    \includegraphics[width=\linewidth]{figures/fig4.pdf}
     \caption{Benign and Malicious Nodes Before Aggregation}
@@
     \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE.
-The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa.
+The F represent mis-identification, including both malicious nodes incorrectly identified as benign, or vice versa.
 }
@@
     \includegraphics[width=\linewidth]{figures/lab3-combined.pdf}
-    \caption{Detection performance of different defense technologies against intelligent attackers with sophisticated multi-round strategies}
+    % \caption{攻击防御实验结果图。第一列到第四列分别代表防御方式Foolsgold、FLTrust、Flame和SecFFT，第一行到第三行分别代表攻击方式EdgeCase、限制大小的EdgeCase、限制大小和角度的EdgeCase。每个实验中有50个客户端，其中0-19号是恶意客户端，每个子图中颜色越红代表识别结果越相似，越蓝代表识别结果越不相似。第一列绘图依据是Foolsgold防御算法中基于余弦相似度计算出来的wv值，第二列绘图依据是FLTrust防御算法中依据余弦相似度和relu激活函数计算出来的聚合权重，第三列绘图依据是Flame算法聚类时所采用的HDBSCAN算法的评分，第四列绘图依据是我们提出的SecFFT算法依据意图点进行相似度计算得到的评分。虽然Flame算法看起来相同种类客户端之间分数较为类似，但实际上其聚类时有明显的聚类错误。}
+    \caption{\textcolor{red}{The experimental results of attack defense are illustrated in the figures.
+The first to fourth columns represent the defense methods \cite{foolsgold}, FLTrust\cite{FLTrust}, Flame\cite{FLAME}, and SecFFT, respectively, while the first to third rows represent the attack methods EdgeCase\cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle.
+Each experiment involves 50 clients, among which clients numbered 0–19 are malicious.
+In each subplot, the redder the color, the more similar the identification results, and the bluer the color, the less similar they are.
+The first column visualizes the results based on the wv values calculated using cosine similarity in the Foolsgold defense algorithm.
+The second column is based on the aggregation weights computed by the FLTrust defense algorithm using cosine similarity and the ReLU activation function.
+The third column visualizes scores obtained from the HDBSCAN algorithm used for clustering in the Flame defense method.
+The fourth column shows scores derived from the similarity calculation based on intent points in the proposed SecFFT algorithm.
+Although the Flame algorithm appears to produce more similar scores among the same type of clients, it exhibits evident clustering errors during its clustering process.}}
     \label{fig:lab3}
@@
 In contrast, our method, even when facing the most sophisticated "size+angle" strategy, maintains a notable difference, enabling the continued distinction between the attacker's intent and that of benign nodes, despite a decrease in absolute values.
+
+% 由图\ref{fig:lab3}可以明显看出，FoolsGold防御算法对EdgeCase攻击的防御效果较为一般，但是基本上能看出良性机器人节点之间的行为较为类似。限制大小对余弦相似度的计算结果不会产生影响，但是限制大小和角度后可以发现Foolsgold算法已经无法成功防御。对于FLTrust防御算法，其在EdgeCase攻击下的防御效果较FoolsGold略好，但恶意机器人节点和良性机器人节点之间仍有一定程度的相似性。限制大小对FLTrust的防御效果没有影响，但是限制大小和角度后，FLTrust算法的防御效果明显下降，已经无法做到准确识别。对于Flame防御算法，其识别依据是HDBSCAN的聚类方式。在聚类时，Flame算法对于相同类别的客户端所赋的分数十分接近（甚至相同），因此导致绘制出来的热力图效果看起来较为均匀明了。但实际上，Flame的聚类结果直接是错误的，例如图中的客户端25、46、47能够看到有不同颜色的条纹。虽然这些条纹颜色较浅，但实际上这些都是识别错误的机器人节点。对于SecFFT防御算法，其识别依据是基于意图点的相似度计算。在EdgeCase攻击下，SecFFT算法能够准确识别出恶意机器人节点，而良性机器人节点之间的相似性较低。限制大小对SecFFT的防御效果几乎没有影响，并且限制大小和角度后SecFFT算法仍然能够保持一个不错的相似度分类效果以及完美的正确率。
+
+\textcolor{red}{As shown in Figure \ref{fig:lab3}, the Foolsgold defense algorithm exhibits moderate performance against EdgeCase attacks.
+While it can generally identify similar behaviors among benign bot nodes, its effectiveness is limited.
+The size constraint does not affect the cosine similarity calculations, but with both size and angle constraints applied, Foolsgold fails to defend effectively.
+For the FLTrust defense algorithm, its performance against EdgeCase attacks slightly surpasses that of Foolsgold; however, a certain degree of similarity remains between malicious and benign bot nodes.
+The size constraint has no impact on FLTrust's defense, but the combined constraints of size and angle significantly weaken its effectiveness, rendering it unable to correctly identify malicious nodes.
+The Flame defense algorithm relies on the HDBSCAN clustering method for identification.
+During clustering, Flame assigns nearly identical (or even identical) scores to clients of the same category, resulting in heatmaps that appear uniform and visually clear.
+However, the clustering results are fundamentally flawed.
+For instance, in the figure, clients 25, 46, and 47 display streaks of different colors, which, although faint, indicate incorrectly classified bot nodes.
+In contrast, the SecFFT defense algorithm leverages similarity calculations based on intent points.
+Under EdgeCase attacks, SecFFT can accurately identify malicious bot nodes, while the similarity among benign bot nodes remains low.
+The size constraint has minimal impact on SecFFT's performance, and even with size and angle constraints applied, the algorithm maintains robust similarity classification and achieves perfect accuracy.}
 

### 2024-11-13 main-v2.tex
archive: 实验三第三列三张图更换指标前

@@
     % \caption{攻击防御实验结果图。第一列到第四列分别代表防御方式Foolsgold、FLTrust、Flame和SecFFT，第一行到第三行分别代表攻击方式EdgeCase、限制大小的EdgeCase、限制大小和角度的EdgeCase。每个实验中有50个客户端，其中0-19号是恶意客户端，每个子图中颜色越红代表识别结果越相似，越蓝代表识别结果越不相似。第一列绘图依据是Foolsgold防御算法中基于余弦相似度计算出来的wv值，第二列绘图依据是FLTrust防御算法中依据余弦相似度和relu激活函数计算出来的聚合权重，第三列绘图依据是Flame算法聚类时所采用的HDBSCAN算法的评分，第四列绘图依据是我们提出的SecFFT算法依据意图点进行相似度计算得到的评分。虽然Flame算法看起来相同种类客户端之间分数较为类似，但实际上其聚类时有明显的聚类错误。}
-    \caption{\textcolor{red}{The experimental results of attack defense are illustrated in the figures.
+    % \caption{\textcolor{red}{The experimental results of attack defense are illustrated in the figures.
 The first to fourth columns represent the defense methods \cite{foolsgold}, FLTrust\cite{FLTrust}, Flame\cite{FLAME}, and SecFFT, respectively, while the first to third rows represent the attack methods EdgeCase\cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle.
@@
 Although the Flame algorithm appears to produce more similar scores among the same type of clients, it exhibits evident clustering errors during its clustering process.}}
+    % \caption{图中展示了四种防御方法（Foolsgold \cite{foolsgold}、FLTrust \cite{FLTrust}、Flame \cite{FLAME}、SecFFT）对三种攻击（EdgeCase \cite{EDGE_CASE}、大小限制的EdgeCase、同时限制大小和角度的EdgeCase）的防御效果。每个实验使用50个客户端（0-19为恶意客户端）。第一到三行分别代表EdgeCase攻击、限制大小的EdgeCase攻击和同时限制大小和角度的EdgeCase攻击。各列分别展示了基于余弦相似度（Foolsgold）、聚合权重（FLTrust）、HDBSCAN得分（Flame）和意图点相似度（SecFFT）的结果。}
+    \caption{\textcolor{red}{The figure illustrates the defense performance of four methods—Foolsgold \cite{foolsgold}, FLTrust \cite{FLTrust}, Flame \cite{FLAME}, and SecFFT—against three attack types: EdgeCase \cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle.
+Each experiment involves 50 clients, with clients 0-19 being malicious.
+The first to third rows represent EdgeCase attacks, size-constrained EdgeCase attacks, and EdgeCase attacks constrained by both size and angle, respectively.
+The columns show results based on cosine similarity (Foolsgold algorithm 1 line 7), aggregation weights (FLTrust algorithm 2 line 15), HDBSCAN scores (Flame Chapter 2.4), and intent-point similarity (SecFFT).}}
     \label{fig:lab3}
@@
 
-% 由图\ref{fig:lab3}可以明显看出，FoolsGold防御算法对EdgeCase攻击的防御效果较为一般，但是基本上能看出良性机器人节点之间的行为较为类似。限制大小对余弦相似度的计算结果不会产生影响，但是限制大小和角度后可以发现Foolsgold算法已经无法成功防御。对于FLTrust防御算法，其在EdgeCase攻击下的防御效果较FoolsGold略好，但恶意机器人节点和良性机器人节点之间仍有一定程度的相似性。限制大小对FLTrust的防御效果没有影响，但是限制大小和角度后，FLTrust算法的防御效果明显下降，已经无法做到准确识别。对于Flame防御算法，其识别依据是HDBSCAN的聚类方式。在聚类时，Flame算法对于相同类别的客户端所赋的分数十分接近（甚至相同），因此导致绘制出来的热力图效果看起来较为均匀明了。但实际上，Flame的聚类结果直接是错误的，例如图中的客户端25、46、47能够看到有不同颜色的条纹。虽然这些条纹颜色较浅，但实际上这些都是识别错误的机器人节点。对于SecFFT防御算法，其识别依据是基于意图点的相似度计算。在EdgeCase攻击下，SecFFT算法能够准确识别出恶意机器人节点，而良性机器人节点之间的相似性较低。限制大小对SecFFT的防御效果几乎没有影响，并且限制大小和角度后SecFFT算法仍然能够保持一个不错的相似度分类效果以及完美的正确率。
+% 由图\ref{fig:lab3}可以明显看出，FoolsGold防御算法对EdgeCase攻击的防御效果较为一般，但是基本上能看出良性机器人节点之间的行为较为类似。限制大小对余弦相似度的计算结果不会产生影响，但是限制大小和角度后可以发现Foolsgold算法已经无法成功防御。对于FLTrust防御算法，其在EdgeCase攻击下的防御效果较FoolsGold略好，但恶意机器人节点和良性机器人节点之间仍有一定程度的相似性。限制大小对FLTrust的防御效果没有影响，但是限制大小和角度后，FLTrust算法的防御效果明显下降，已经无法做到准确识别。对于Flame防御算法，其识别依据是HDBSCAN的聚类方式。在聚类时，Flame算法对于相同类别的机器人节点所赋的分数十分接近（甚至相同），因此导致绘制出来的热力图效果看起来较为均匀明了。但实际上，Flame的聚类结果直接是错误的，例如图中的机器人节点25、46、47能够看到有不同颜色的条纹。虽然这些条纹颜色较浅，但实际上这些都是识别错误的机器人节点。这是由于乘此密度聚类算法(HDBSCAN)会以最佳的方式创建最稳定聚类的聚类级别，该聚类会尽可能多的合并聚类点而不是加入噪点，因此对于评分和良性机器人节点相差并不是很大的25、46、47等机器人节点，其仍然会被识别为噪点，从而不被认为是良性机器人节点。对于SecFFT防御算法，其识别依据是基于意图点的相似度计算。在EdgeCase攻击下，SecFFT算法能够准确识别出恶意机器人节点，而良性机器人节点之间的相似性较低。限制大小对SecFFT的防御效果几乎没有影响，并且限制大小和角度后SecFFT算法仍然能够保持一个不错的相似度分类效果以及完美的正确率。
 

### 2024-11-15 main-v2.tex
R1: 实验全部跑完
Signed-off-by: LetMeFly666 <814114971@qq.com>

--- 2024-11-12 main-v2.tex
@@
 \textbf{Backdoor Detection} primarily aims to identify existing backdoor attackers.
-In this category, FoolsGold\cite{foolsgold} proposes a method to identify attackers by detecting the similarity of updates from each client.
+In this category, FoolsGold\cite{foolsgold} proposes a method to identify attackers by detecting the similarity of updates from each node.
 This method adaptively adjusts the learning rate of each nodes based on the observation that the updates from attackers are usually more similar.
@@
 \textbf{Motivation}: To evade anomaly detection systems, many backdoor attacks employ multi-round composite strategies that are difficult to detect in a single round.
-These attacks can be broadly classified into three types: (1) \textbf{Size-Limited Attacks} (e.g., \cite{geisler2024attacking, chen2024optimal}), which constrain the magnitude of each attack to make it subtle and less conspicuous, thereby reducing its detectability; (2) \textbf{Angle-Limited Attacks} (e.g., \cite{you2023three, sagliano2024powered, dong2023adaptive}), which restrict the direction of each attack so that it appears similar to legitimate updates, making them harder to recognize; and (3) \textbf{Sign-Limited Attacks} (e.g., \cite{wan2023average, zhu2023boosting}), which use techniques such as gradient scaling or gradient composition to ensure that the signs of the malicious gradients align with those of legitimate clients, thereby increasing the difficulty of detection.
-This section presents an approach that leverages each client's historical records to identify malicious nodes by analyzing their ultimate intent to manipulate the global model.
+These attacks can be broadly classified into three types: (1) \textbf{Size-Limited Attacks} (e.g., \cite{geisler2024attacking, chen2024optimal}), which constrain the magnitude of each attack to make it subtle and less conspicuous, thereby reducing its detectability; (2) \textbf{Angle-Limited Attacks} (e.g., \cite{you2023three, sagliano2024powered, dong2023adaptive}), which restrict the direction of each attack so that it appears similar to legitimate updates, making them harder to recognize; and (3) \textbf{Sign-Limited Attacks} (e.g., \cite{wan2023average, zhu2023boosting}), which use techniques such as gradient scaling or gradient composition to ensure that the signs of the malicious gradients align with those of legitimate nodes, thereby increasing the difficulty of detection.
+This section presents an approach that leverages each node's historical records to identify malicious nodes by analyzing their ultimate intent to manipulate the global model.
 
@@
 
-\textbf{Overview}: The previous defense algorithms have effectively identified single-round attacks; this section focuses on leveraging clients' historical records for effective identification.
-We maintain the global models $\theta_g^{t'}$ from the past $T$ rounds, where $\max\{t-T+1, 1\}\leq t'\leq t$, and consider their flattened versions as points in a high-dimensional space.
-Simultaneously, we keep track of each client's historical updates, viewing them as vectors in the high-dimensional space and extending them as rays.
-For each client, we use the Minimum Enclosing Ball algorithm to compute a minimal hypersphere that covers a $\zeta$ proportion of the ray.
+\textbf{Overview}: The ``Instantaneous Attack Behavior Perception" mechanism is effective in identifying single-round attacks, however, it performs poorly when addressing stealthy multi-round composite attacks.
+Consequently, this section focuses on utilizing the historical updates to effectively identify malicious nodes.
+We maintain the global models $\theta_g^{t'}$ from the past $T$ rounds, where $\max\{t-T+1, 1\}\leq t'\leq t$, and consider flattened global model as a point in a high-dimensional space.
+Simultaneously, the historical updates of each node are recorded and represented as vectors in the same high-dimensional space, which are then extended into rays.
+% Simultaneously, we keep track of each client's historical updates, viewing them as vectors in the high-dimensional space and extending them as rays. 
+% For each client, we use the Minimum Enclosing Ball algorithm to compute a minimal hypersphere that covers a $\zeta$ proportion of the ray.
 The final position of the hypersphere's center can be regarded as the intended steering point of the global model for the corresponding node, and the radius of the hypersphere can be regarded as the reliability level.
+For each node, the ``Minimum Enclosing Hypersphere Ball (MEHB)" is applied to compute the smallest hypersphere that covers a 
+$\zeta$-proportion of the rays.
+The center of the hypersphere can be interpreted as the intended guiding point of the node for the global model, while the radius of the hypersphere reflects the confidence level of the corresponding node.
 
@@
 % 像正常的联邦学习过程一样，中央服务器每次下发一个全局模型，每个客户端得到全局模型后使用本地数据进行训练，并将更新变化上传到中央服务器中。我们将第$t$轮次的全局模型记为$\theta_t$，将客户端$i$第$t$轮次训练后的模型记为$\theta^t_i$。客户端$i$将训练后的模型$\theta^t_{i}$减去训练前中央服务器下发的全局模型$\theta^t$，就得到了$t$轮次的更新变化$\triangledown \theta^t_{i}=\theta^t_{i}-\theta^t$。客户端将更新变化$\triangledown \theta^t_{i}$上传到中央服务器，中央服务器在聚合的同时，记录下每个客户端当前轮次的更新$\triangledown \theta^t_{i}$展平后的结果$\bar{\theta_i^t}$，同时存下中央服务器上轮次下发的全局模型$\theta^{t-1}$。中央服务器最多保留$T$轮次的模型和更新历史记录。“Keep T-rounds History”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的3-13行所示。
-As in a typical federated learning process, the central server distributes a global model in each round.
+Similar to the standard federated learning process, the central server distributes a global model in each round.
+After receiving the global model, each node trains it using local data and uploads the updates to the central server.
+Let the global model in round $t$ be denoted as $\theta^{t-1}_g$, and the model trained by node $i$ in round $t$ be denoted as $\theta^t_i$.
+The update from node $i$ in round $t$ is calculated as $\triangledown \theta^t_{i} = \theta^t_{i} - \theta^{t-1}_g$.
+While aggregating the updates, the central server records the flattened update $\bar{\theta_i^t}$ of each node and stores the global model $\overline{\theta_g^{t-1}}$.
+The central server maintains the history of models and updates for up to $T$ rounds.
+Therefore, let \( \overline{\theta_g^{t-T}}, \overline{\theta_g^{t-T+1}}, \dots, \overline{\theta_g^{t-1}} \) denote the flattened global models and \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) denote the flattened update uploaded by node \(i\) from the past \(T\) rounds.
+
+% As in a typical federated learning process, the central server distributes a global model in each round.
 Upon receiving the global model, each client trains on its local data and uploads the updates to the central server.
-Let the global model in the $t$-th round be denoted as $\theta_t$, and the model of client $i$ after training in the $t$-th round be denoted as $\theta^t_i$.
+Let the global model in the $t$-th round be denoted as $\theta_g^t$, and the model of client $i$ after training in the $t$-th round be denoted as $\theta^t_i$.
 Client $i$ computes its update in the $t$-th round as the difference between the trained model $\theta^t_{i}$ and the global model received before training $\theta^t$, i.e., $\triangledown \theta^t_{i} = \theta^t_{i} - \theta_g^t$.
@@
 % 这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。
-This problem can be abstracted as rays in a high-dimensional space with specific starting points.
+% This problem can be abstracted as rays in a high-dimensional space with specific starting points.
 The starting point of a ray represents the global model from the previous round, and the direction of the ray represents the flattened update in the current round.
@@
 % 我们使用符号$O_i$代表客户端$i$在高维空间中超球的球心，使用符号$r_i$代表这个超球的半径。假设当前轮次为$t$，$t'$是最近$T$轮次中的其中一轮，使用符号$\tilde O_i^{t'}$代表球心到第$t'$对应射线的最近点。则可以定义优化问题：
-We use the symbol $O_i$ to represent the center of the hypersphere for client $i$ in the high-dimensional space and $r_i$ to represent the radius of this hypersphere.
+% We use the symbol $O_i$ to represent the center of the hypersphere for client $i$ in the high-dimensional space and $r_i$ to represent the radius of this hypersphere.
 Suppose the current round is $t$, and $t'$ is one of the recent $T$ rounds.
@@
 
-\begin{equation}
-    \min_{O_i, r_i} \quad r_i
-\end{equation}
-
-\begin{equation} 
-\text{s.t.} \quad \left| \left\{ t' \mid \| O_i - \tilde{O}_{i}^{t'} \| \leq r_i \right\} \right| \geq \zeta T,
-\end{equation}
-\begin{equation} 
-    \quad\quad\max\{t-T+1, 1\}\leq  t'\leq t.
-\end{equation}
+This problem can be abstracted as finding a smallest hypersphere that covers at least $\zeta$-proportion of a set of rays in a high-dimensional space, each with a defined starting point.
+The starting point of a ray is the flattened global model in the round $t'-1$, and the direction of the ray corresponds to the flattened update from node $R_i$ in the round $t'$, where $\max\{t-T+1, 1\}\leq t'\leq t$.
+Equation \ref{eq:ray} is the corresponding ray equation, where $\alpha\in [0, +\infty)$ is the parameter of the ray.
+We use the symbol $O_i$ to denote the center of the hypersphere for node $i$ in the high-dimensional space, the symbol $r_i$ to denote the radius of this hypersphere and the symbol $\tilde{O}_i^{t'}$ to denote the nearest point from the hypersphere center to the ray corresponding to round $t'$.
+Thus, the optimization problem can then be defined as Equation \ref{eq:optimization}.
+
+\begin{equation}
+l_i^{t'}=Flatten(\theta_g^{t'-1}) + \alpha \overline{\triangledown\theta_{i}^{t'}},
+\label{eq:ray}
+\end{equation}
+
+\begin{equation}
+\min_{O_i, r_i} \quad r_i, \quad
+\text{s.t.} 
+\begin{cases}
+    \left| \left\{ t' \mid \| O_i - \tilde{O}_{i}^{t'} \| \leq r_i \right\} \right| \geq \zeta T, \\
+    \max\{t-T+1, 1\} \leq t' \leq t.
+\end{cases}
+\label{eq:optimization}
+\end{equation}
+
+% \begin{equation}
+%     \min_{O_i, r_i} \quad r_i
+% \end{equation}
+
+% \begin{equation} 
+% \text{s.t.} \quad \left| \left\{ t' \mid \| O_i - \tilde{O}_{i}^{t'} \| \leq r_i \right\} \right| \geq \zeta T,
+% \end{equation}
+% \begin{equation} 
+%     \quad\quad\max\{t-T+1, 1\}\leq  t'\leq t.
+% \end{equation}
+
 % “Obtain the Purpose Intention”的主要算法过程如算法\ref{alg:malicious-node-detection-history}的14-18行所示。此部分又可以分为“Construct Ray Model”和“Minimum Enclosing Hypersphere Calculation”两部分。
@@
 %The main process of "Construct Ray Model" is as follows. 
-For each client \(R_i\), the central server retains the global model history and the update history for the most recent \(T\) rounds.
+% For each client \(R_i\), the central server retains the global model history and the update history for the most recent \(T\) rounds.
 Let \( \theta_g^{t-T}, \theta_g^{t-T+1}, \dots, \theta_g^{t-1} \) represent the global models of the most recent \(T\) rounds, which have been "flattened" to a point in a high-dimensional space.
 Similarly, let \( \overline{\triangledown\theta_{i}^{t-T}}, \overline{\triangledown\theta_{i}^{t-T+1}}, \dots, \overline{\triangledown\theta_{i}^{t-1}} \) represent the flattened gradient update vectors uploaded by client \(i\) in the most recent \(T\) rounds.
+
 % 对于每一轮 \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \))，我们将每个射线的起点表示为展平后的全局模型 \( \theta_g^{t'} \)，并将每个射线的方向向量表示为展平后的梯度变化 \( \overline{\triangledown\theta_{i}^{t'}} \)。因此，射线模型可以构建如下：
-For each round \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \)), the starting point of each ray is represented by the flattened global model \( \theta_g^{t'} \), and the direction vector of each ray is represented by the flattened gradient update \( \overline{\triangledown\theta_{i}^{t'}} \).
+% For each round \( t' \) (\( \max\{t-T+1, 1\}\leq  t'\leq t \)), the starting point of each ray is represented by the flattened global model \( \theta_g^{t'} \), and the direction vector of each ray is represented by the flattened gradient update \( \overline{\triangledown\theta_{i}^{t'}} \).
 Thus, the ray model can be constructed as follows:
 
-\begin{equation}
-    \left\{\begin{matrix}
-    \widetilde{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1})\\
-    {v}_{i}^{t'} = \overline{\triangledown\theta_{i}^{t'}}
-    \end{matrix}\right.,
-\end{equation}
+% For each round \(t'\) (\( \max\{t-T+1, 1\} \leq t' \leq t \)), the starting point of each ray is represented by the flattened global model \( \theta_g^{t'} \), and the directional vector of each ray is represented by the flattened gradient update \( \overline{\triangledown\theta_{i}^{t'}} \).
+Therefore, the ray model can be constructed as follows:
+
+% \begin{equation}
+%     \left\{\begin{matrix}
+%     \widetilde{\theta_{i}^{t'-1}} = Flatten(\theta_g^{t'-1})\\
+%     {v}_{i}^{t'} = \overline{\triangledown\theta_{i}^{t'}}
+%     \end{matrix}\right.,
+% \end{equation}
+
 % 其中，\( \widetilde{\theta_{i}^{t'-1}} \) 是射线的起点，\( {v}_{i}^{t'} \) 是射线的方向向量。则射线方程为：
-where \( \widetilde{\theta_{i}^{t'-1}} \) is the starting point of the ray, and \( {v}_{i}^{t'} \) is the direction vector of the ray. The ray equation is then given by:
-
-\begin{equation}
-l_i^{t'}=\widetilde{\theta_{i}^{t'-1}}+\alpha {v}_{i}^{t'},
-\end{equation}
+% where \( \widetilde{\theta_{i}^{t'-1}} \) is the starting point of the ray, and \( {v}_{i}^{t'} \) is the directional vector of the ray. The ray equation is then given by:
+
 % 其中，$\alpha\in [0, +\infty)$为射线的自变量参数。
-where $\alpha\in [0, +\infty)$ is the parameter of the ray.
+
 % “Minimum Enclosing Hypersphere Calculation”的主要过程如下。基于构建的射线模型，使用最小覆盖球算法找到一个能够覆盖至少 \( \zeta \) 比例的射线的最小超球。首先，设定初始球心 \( O_{i,0} \) 为所有射线起点的几何中心，计算公式如下：
-Therefore, we approximate the attack intention hiddden behind the series of behaviors based on Minimum Enclosing Hypersphere Ball (MEHB) construction as follows.
-Based on the constructed ray model, the MEHB model is adopted to find the smallest hypersphere that can cover at least a \( \zeta \) proportion of the rays, which denotes the intention of the current node.
+
+To solve this problem, we approximate the attack intention hiddden behind the series of behaviors based on ``Minimum Enclosing Hypersphere Ball (MEHB)".
+Based on the constructed ray model, the MEHB model is adopted to find the smallest hypersphere that can cover at least \( \zeta \)-proportion of the rays, which denotes the intention of the current node.
+
 First, the initial center of the hypersphere \( O_{i,0} \) is set to the geometric center of all ray starting points, calculated as follows:
@@
 \textcolor{red}{In our proposed framework, the concept of the "intention point" serves as a pivotal element in recognizing the underlying motives of malicious nodes during the federated fine-tuning process.
-The intention point is defined as the central position within a high-dimensional space, representing the aggregated gradient updates of a client across multiple training rounds.
-This point encapsulates the client's intended direction for influencing the global model.
-To construct the intention point, we utilize a Minimum Enclosing Hypersphere approach, which encompasses a proportion of the client’s gradient updates.
-The radius of this hypersphere reflects the reliability of the intention point, effectively quantifying the client's consistency in updating the model.
-By analyzing these intention points, our method can discern the behaviors of malicious clients from benign ones, enhancing the overall security and robustness of the federated learning system.}
+The intention point is defined as the central position within a high-dimensional space, representing the aggregated gradient updates of a node across multiple training rounds.
+This point encapsulates the node's intended direction for influencing the global model.
+To construct the intention point, we utilize a Minimum Enclosing Hypersphere approach, which encompasses a proportion of the node’s gradient updates.
+The radius of this hypersphere reflects the reliability of the intention point, effectively quantifying the node's consistency in updating the model.
+By analyzing these intention points, our method can discern the behaviors of malicious nodes from benign ones, enhancing the overall security and robustness of the federated learning system.}
 
@@
 The first row demonstrates the process of federated learning, where many robot nodes independently train their local models \( \theta^t_{l_1} \) based on the distributed global model \( G_{t-1} \).
-Each participating client then uploads its gradient updates to the central server's global model, which are aggregated to form the next global model iteration.
-The second row is divided into two sections: the left section shows the flattened gradients updated across multiple rounds for clients.
-The first column represents the gradient update of a specific round, the second column shows the flattened gradient updates from \( n \) clients in one round, and the third column displays the flattened updates across \( T \) rounds for \( n \) clients.
+Each participating node then uploads its gradient updates to the central server's global model, which are aggregated to form the next global model iteration.
+The second row is divided into two sections: the left section shows the flattened gradients updated across multiple rounds for nodes.
+The first column represents the gradient update of a specific round, the second column shows the flattened gradient updates from \( n \) nodes in one round, and the third column displays the flattened updates across \( T \) rounds for \( n \) nodes.
 The right section of the image represents the global model in each round.
-The third row depicts how a single client's intention point is calculated based on multi-round historical data, where each ray signifies the flattened results of the model updates, and the hypersphere's center represents the current client's intention point.}
+The third row depicts how a single node's intention point is calculated based on multi-round historical data, where each ray signifies the flattened results of the model updates, and the hypersphere's center represents the current node's intention point.}
 
@@
 Density is primarily calculated based on the distance between points: the greater the distance between points, the lower the density; the closer the distance, the higher the density.
-After calculating the local outlier factor $lof_i$ for each node $i$, clients with $lof_i$ greater than $1$ are regarded as abnormal clients, and their gradients are discarded.
+After calculating the local outlier factor $lof_i$ for each node $i$, nodes with $lof_i$ greater than $1$ are regarded as abnormal nodes, and their gradients are discarded.
 % “Abnormal Detection”的主要过程如算法\ref{alg:malicious-node-detection-history}的19-30行所示。
@@
 where $\rho$ is a small positive number to prevent the denominator from being zero. 
-
-As shown in Figure \ref{fig:before-agg}, the LOF algorithm can identify and remove potential malicious clients, but among the normal nodes, there are still some nodes with very low confidence.
+As shown in Figure \ref{fig:before-agg}, the LOF algorithm can identify and remove potential malicious nodes, but among the normal nodes, there are still some nodes with very low confidence.
 The minimum enclosing hypersphere of these nodes may even overlap with the abnormal nodes.
@@
 %     \centering
-%     \includegraphics[width=\linewidth]{results/prob-history-Visualization of Client Intentions and Anomalies.png}
+%     \includegraphics[width=\linewidth]{results/prob-history-Visualization of node Intentions and Anomalies.png}
 %     \centering \caption{Results obtained using simulated data}
@@
 \begin{algorithmic}[1]
-\State \textbf{Input:} Global model history $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$
-\State \textbf{Output:} Sets of normal clients $U_{nor}$ and malicious clients $U_{mal}$
+\State \textbf{Input:} Global model history $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical gradient updates for each node $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$
+\State \textbf{Output:} Sets of normal nodes $U_{nor}$ and malicious nodes $U_{mal}$
 
@@
 FedAVG conducts weighted aggregation of updates uploaded by each node based on the size of its dataset.
-FoolsGold differentiates between benign and malicious clients by evaluating pairwise similarity among model updates and subsequently down-weighting anomalous updates on the FL server.
+FoolsGold differentiates between benign and malicious nodes by evaluating pairwise similarity among model updates and subsequently down-weighting anomalous updates on the FL server.
 FLTrust employs a clean dataset and aggregates only those updates from nodes that exhibit high cosine similarity with the updates derived from the clean dataset.
@@
     \caption{Visualization of node identification results under three attack scenarios (MR, EDGE CASE, NEUR) for four defense mechanisms (SecFFT, Flame, FLTrust, FoolsGold) using t-SNE.
-The red dots represent misidentified nodes, including both malicious nodes incorrectly identified as benign, or vice versa.
+The F represents misidentification, including both malicious nodes incorrectly identified as benign, or vice versa.
 }
@@
     \includegraphics[width=\linewidth]{figures/lab3-combined.pdf}
-    \caption{Detection performance of different defense technologies against intelligent attackers with sophisticated multi-round strategies}
+    % \caption{攻击防御实验结果图。第一列到第四列分别代表防御方式Foolsgold、FLTrust、Flame和SecFFT，第一行到第三行分别代表攻击方式EdgeCase、限制大小的EdgeCase、限制大小和角度的EdgeCase。每个实验中有50个客户端，其中0-19号是恶意客户端，每个子图中颜色越红代表识别结果越相似，越蓝代表识别结果越不相似。第一列绘图依据是Foolsgold防御算法中基于余弦相似度计算出来的wv值，第二列绘图依据是FLTrust防御算法中依据余弦相似度和relu激活函数计算出来的聚合权重，第三列绘图依据是Flame算法聚类时所采用的HDBSCAN算法的评分，第四列绘图依据是我们提出的SecFFT算法依据意图点进行相似度计算得到的评分。虽然Flame算法看起来相同种类客户端之间分数较为类似，但实际上其聚类时有明显的聚类错误。}
+    % \caption{\textcolor{red}{The experimental results of attack defense are illustrated in the figures.
+The first to fourth columns represent the defense methods \cite{foolsgold}, FLTrust\cite{FLTrust}, Flame\cite{FLAME}, and SecFFT, respectively, while the first to third rows represent the attack methods EdgeCase\cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle.
+Each experiment involves 50 clients, among which clients numbered 0–19 are malicious.
+In each subplot, the redder the color, the more similar the identification results, and the bluer the color, the less similar they are.
+The first column visualizes the results based on the wv values calculated using cosine similarity in the Foolsgold defense algorithm.
+The second column is based on the aggregation weights computed by the FLTrust defense algorithm using cosine similarity and the ReLU activation function.
+The third column visualizes scores obtained from the HDBSCAN algorithm used for clustering in the Flame defense method.
+The fourth column shows scores derived from the similarity calculation based on intent points in the proposed SecFFT algorithm.
+Although the Flame algorithm appears to produce more similar scores among the same type of clients, it exhibits evident clustering errors during its clustering process.}}
+    % \caption{图中展示了四种防御方法（Foolsgold \cite{foolsgold}、FLTrust \cite{FLTrust}、Flame \cite{FLAME}、SecFFT）对三种攻击（EdgeCase \cite{EDGE_CASE}、大小限制的EdgeCase、同时限制大小和角度的EdgeCase）的防御效果。每个实验使用50个客户端（0-19为恶意客户端）。第一到三行分别代表EdgeCase攻击、限制大小的EdgeCase攻击和同时限制大小和角度的EdgeCase攻击。各列分别展示了基于余弦相似度（Foolsgold）、聚合权重（FLTrust）、HDBSCAN概率得分（Flame）和意图点相似度（SecFFT）的结果。}
+    \caption{\textcolor{red}{The figure illustrates the defense performance of four methods—Foolsgold \cite{foolsgold}, FLTrust \cite{FLTrust}, Flame \cite{FLAME}, and SecFFT—against three attack types: EdgeCase \cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle.
+Each experiment involves 50 nodes, with nodes 0-19 being malicious.
+The first to third rows represent EdgeCase attacks, size-constrained EdgeCase attacks, and EdgeCase attacks constrained by both size and angle, respectively.
+The columns show results based on cosine similarity (Foolsgold algorithm 1 line 7), aggregation weights (FLTrust algorithm 2 line 15), HDBSCAN probability scores (Flame Chapter 2.4), and intent-point similarity (SecFFT).}}
     \label{fig:lab3}
@@
 
-Table \ref{tab:detect} provides a detailed quantitative analysis of the classification metrics for the four defense mechanisms against different strategies.
+% 由图\ref{fig:lab3}可以明显看出，FoolsGold防御算法对EdgeCase攻击的防御效果较为一般，但是基本上能看出良性机器人节点之间的行为较为类似。限制大小对余弦相似度的计算结果不会产生影响，但是限制大小和角度后可以发现Foolsgold算法已经无法成功防御。其中FoolsGold防御算法的绘图指标是原文中算法1的第7行，即作者公布的开源代码中的$wv$值。对于FLTrust防御算法，其在EdgeCase攻击下的防御效果较FoolsGold略好，但恶意机器人节点和良性机器人节点之间仍有一定程度的相似性。限制大小对FLTrust的防御效果没有影响，但是限制大小和角度后，FLTrust算法的防御效果明显下降，已经无法做到准确识别。其中FLTrust防御算法的绘图指标是原文中算法2的第15行，对应作者公布的开源代码中，两两机器人节点梯度变化的余弦相似度经过ReLU激活函数后的结果$weights$。对于Flame防御算法，其识别依据是HDBSCAN的聚类方式，绘图依据是作者公布的开源代码中调用库函数HDBSCAN后得到的返回值$cluster$中的聚类概率(Prob)。在聚类时，Flame算法对于相同类别的机器人节点所赋的分数十分接近（甚至相同），因此导致绘制出来的热力图效果看起来较为均匀明了。但实际上，Flame的聚类结果直接是错误的，例如图中的机器人节点25、31、32、34会被是被为噪声点从而不是核心点也不是边界点。这是由于层次密度聚类算法(HDBSCAN)会以最佳的方式创建最稳定聚类的聚类级别，该聚类会尽可能多的合并聚类点而不是加入噪点，因此对于异常值(Outlier)评分和良性机器人节点相差并不是很大的25、31、32、34等机器人节点，其仍然会被识别为噪点，从而不被认为是良性机器人节点。对于SecFFT防御算法，其识别依据是基于意图点的相似度计算。在EdgeCase攻击下，SecFFT算法能够准确识别出恶意机器人节点，而良性机器人节点之间的相似性较低。限制大小对SecFFT的防御效果几乎没有影响，并且限制大小和角度后SecFFT算法仍然能够保持一个不错的相似度分类效果以及完美的正确率。
+
+\textcolor{red}{As shown in Figure \ref{fig:lab3}, the Foolsgold defense algorithm shows moderate performance against EdgeCase attacks, but it can generally identify similar behaviors among benign bot nodes.
+The size constraint does not affect the cosine similarity results, but once both size and angle are constrained, Foolsgold fails to defend effectively.
+The metric used for Foolsgold in the plots is the $wv$ value from line 7 of Algorithm 1 in the original paper, which corresponds to the value in the author's open-source code.}
+
+\textcolor{red}{For FLTrust, its defense against EdgeCase attacks is slightly better than Foolsgold, but there is still some similarity between malicious and benign nodes.
+The size constraint has no impact on FLTrust's performance, but when both size and angle are constrained, its defense effectiveness declines significantly, making it unable to accurately identify malicious nodes.
+The metric for FLTrust is the $weights$ value from line 15 of Algorithm 2 in the original paper, corresponding to the result of applying the ReLU activation function to the cosine similarity of gradient changes between pairs of bot nodes in the author's open-source code.}
+
+\textcolor{red}{Flame uses HDBSCAN clustering for identification.
+The metric is the cluster probability ($Prob$) obtained after calling the HDBSCAN library function in the author's open-source code.
+While Flame assigns similar (or identical) scores to bot nodes of the same category, the clustering results are fundamentally flawed.
+For instance, bot nodes 25, 31, 32, and 34 are incorrectly identified as noise points rather than core or border points.
+This is due to HDBSCAN's hierarchical density clustering, which prioritizes the creation of stable clusters and merges points, classifying outliers with scores similar to benign bot nodes (e.g., 25, 31, 32, and 34) as noise.}
+
+\textcolor{red}{For SecFFT, the defense is based on intent-point similarity.
+Under EdgeCase attacks, SecFFT accurately identifies malicious bot nodes while showing low similarity among benign nodes.
+The size constraint has minimal impact on SecFFT's performance, and even with both size and angle constraints, SecFFT maintains strong similarity classification with perfect accuracy.}
+
+Table \ref{tab:detect} provides a detailed quantitative analysis of the classification metrics for the four defense mechanisms against different strategies \textcolor{red}{of EdgeCase}.
 It is clear that SecFFT not only consistently preserves its strong backdoor attack mitigation capability but also achieves the best detection accuracy, with significantly reduced false positive rates, ensuring reliable and robust performance.
@@
 \hline
+
 \textcolor{red}{Strategy} & \textcolor{red}{Defense} & \textcolor{red}{Acc.} & \textcolor{red}{Rec.} & \textcolor{red}{FPR} & \textcolor{red}{FNR} & \textcolor{red}{AUC} & \textcolor{red}{MCC} \\ \hline
 
-\multirow{4}{*}{\textcolor{red}{None}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.90} & \textcolor{red}{0.67} & \textcolor{red}{0.00} & \textcolor{red}{0.33} & \textcolor{red}{0.83} & \textcolor{red}{0.76} \\
-                      & \textcolor{red}{FLTrust}   & \textcolor{red}{0.82} & \textcolor{red}{0.40} & \textcolor{red}{0.00} & \textcolor{red}{0.60} & \textcolor{red}{0.70} & \textcolor{red}{0.56} \\
-                      & \textcolor{red}{Flame}     & \textcolor{red}{0.90} & \textcolor{red}{0.67} & \textcolor{red}{0.00} & \textcolor{red}{0.33} & \textcolor{red}{0.83} & \textcolor{red}{0.76} \\
-                      & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textcolor{red}{0.00} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\ \hline
-
-\multirow{4}{*}{\textcolor{red}{Size}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.92} & \textcolor{red}{0.80} & \textcolor{red}{0.03} & \textcolor{red}{0.20} & \textcolor{red}{0.88} & \textcolor{red}{0.72} \\
-                      & \textcolor{red}{FLTrust}   & \textcolor{red}{0.82} & \textcolor{red}{0.53} & \textcolor{red}{0.06} & \textcolor{red}{0.47} & \textcolor{red}{0.74} & \textcolor{red}{0.61} \\ 
-                      & \textcolor{red}{Flame}     & \textcolor{red}{0.92} & \textcolor{red}{0.73} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.27} & \textcolor{red}{0.87} & \textcolor{red}{0.78} \\
-                      & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{0.98}} & \textbf{\textcolor{red}{0.93}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.07}} & \textbf{\textcolor{red}{0.96}} & \textbf{\textcolor{red}{0.91}} \\ \hline
-
-\multirow{4}{*}{\textcolor{red}{Angle}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.88} & \textcolor{red}{0.73} & \textcolor{red}{0.06} & \textcolor{red}{0.27} & \textcolor{red}{0.84} & \textcolor{red}{0.68} \\
-                       & \textcolor{red}{FLTrust}   & \textcolor{red}{0.86} & \textcolor{red}{0.60} & \textcolor{red}{0.03} & \textcolor{red}{0.40} & \textcolor{red}{0.80} & \textcolor{red}{0.65} \\ 
-                       & \textcolor{red}{Flame}     & \textcolor{red}{0.90} & \textcolor{red}{0.67} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.33} & \textcolor{red}{0.83} & \textcolor{red}{0.76} \\
-                       & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{0.96}} & \textbf{\textcolor{red}{0.87}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.13}} & \textbf{\textcolor{red}{0.94}} & \textbf{\textcolor{red}{0.88}} \\ \hline
+\multirow{4}{*}{\textcolor{red}{None}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.96} & \textcolor{red}{0.90} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.10} & \textcolor{red}{0.95} & \textcolor{red}{0.92} \\
+                        & \textcolor{red}{FLTrust}   & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\
+                        & \textcolor{red}{Flame}     & \textcolor{red}{0.92} & \textbf{\textcolor{red}{1.00}} & \textcolor{red}{0.13} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.93} & \textcolor{red}{0.85} \\
+                        & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\ \hline
+
+\multirow{4}{*}{\textcolor{red}{Size}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.96} & \textcolor{red}{0.90} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.10} & \textcolor{red}{0.95} & \textcolor{red}{0.92} \\
+                        & \textcolor{red}{FLTrust}   & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\
+                        & \textcolor{red}{Flame}     & \textcolor{red}{0.92} & \textbf{\textcolor{red}{1.00}} & \textcolor{red}{0.13} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.93} & \textcolor{red}{0.85} \\
+                        & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\ \hline
+
+\multirow{4}{*}{\textcolor{red}{Angle}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.96} & \textcolor{red}{0.90} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.10} & \textcolor{red}{0.95} & \textcolor{red}{0.92} \\
+                        & \textcolor{red}{FLTrust}   & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\
+                        & \textcolor{red}{Flame}     & \textcolor{red}{0.92} & \textbf{\textcolor{red}{1.00}} & \textcolor{red}{0.13} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.93} & \textcolor{red}{0.85} \\
+                        & \textcolor{red}{SecFFT}    & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\ \hline
+
 \end{tabular}
@@
 \item ``Acc." stands for Accuracy, ``Rec." for Recall, ``FPR" for False Positive Rate, ``FNR" for False Negative Rate, ``AUC" for Area Under Curve, and ``MCC" for Matthews Correlation Coefficient.
-The strategies are abbreviated as ``None" (No strategy), ``Size" (Size-limited strategy), and ``Angle" (Angle-limited strategy).
+The strategies are abbreviated as ``None" (EdgeCase without other strategies), ``Size" (Size-limited strategy), and ``Angle" (Angle-limited strategy).
 \end{tablenotes}
@@
 \section*{Acknowledgments}
-This work is partially supported by China Postdoctoral Science Foundation (grant No.
+% This work is partially supported by China Postdoctoral Science Foundation (grant No.
 2024M750259), Beijing Natural Science Foundation (grant No.
@@
 62401075, 62394322).
+
+This work is partially supported by the China Postdoctoral Science Foundation (grant No.
+2024M750259), Beijing Natural Science Foundation (grant No.
+4244084), National Natural Science Foundation of China (grants No.
+62401075, 62394322, 61932016, 62132011, 62132009, U22B2031, 62221003 and 92167204), the Beijing National Research Center for Information Science and Technology under (grant No.
+BNR2023TD03006) and the National Key Research and Development Program of China (grant No.
+2023YFB2904200).
 

### 2024-11-18 main-v2.tex
fix: GPT表格填写错误
Signed-off-by: LetMeFly666 <814114971@qq.com>

@@
 \hline
-
+% 0.96, 0.9, 0.0, 0.1, 0.95, 0.9185586535436917
+% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
+% 0.92, 1.0, 0.13333333333333333, 0.0, 0.9333333333333333, 0.8498365855987975
+% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
+% ----------------
+% 0.96, 0.9, 0.0, 0.1, 0.95, 0.9185586535436917
+% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
+% 0.92, 1.0, 0.13333333333333333, 0.0, 0.9333333333333333, 0.8498365855987975
+% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
+% ----------------
+% 0.96, 0.9, 0.0, 0.1, 0.95, 0.9185586535436917
+% 0.94, 0.85, 0.0, 0.15, 0.925, 0.8790490729915326
+% 0.92, 1.0, 0.13333333333333333, 0.0, 0.9333333333333333, 0.8498365855987975
+% 1.0, 1.0, 0.0, 0.0, 1.0, 1.0
 \textcolor{red}{Strategy} & \textcolor{red}{Defense} & \textcolor{red}{Acc.} & \textcolor{red}{Rec.} & \textcolor{red}{FPR} & \textcolor{red}{FNR} & \textcolor{red}{AUC} & \textcolor{red}{MCC} \\ \hline
@@
 \multirow{4}{*}{\textcolor{red}{Angle}} & \textcolor{red}{Foolsgold} & \textcolor{red}{0.96} & \textcolor{red}{0.90} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.10} & \textcolor{red}{0.95} & \textcolor{red}{0.92} \\
-                        & \textcolor{red}{FLTrust}   & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{0.00}} & \textbf{\textcolor{red}{1.00}} & \textbf{\textcolor{red}{1.00}} \\
+                        & \textcolor{red}{FLTrust}   & \textcolor{red}{0.94} & \textcolor{red}{0.85} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.15} & \textcolor{red}{0.93} & \textcolor{red}{0.88} \\
                         & \textcolor{red}{Flame}     & \textcolor{red}{0.92} & \textbf{\textcolor{red}{1.00}} & \textcolor{red}{0.13} & \textbf{\textcolor{red}{0.00}} & \textcolor{red}{0.93} & \textcolor{red}{0.85} \\

### 2024-11-29 main-v3(final).tex
before.final: modified by zz
Signed-off-by: LetMeFly666 <814114971@qq.com>

--- 2024-11-18 main-v2.tex
@@
 %如图\ref{fig:scenario}所示，考虑在机器人物联网（IoRT）网络中对视觉大模型进行联邦微调的场景下，整个系统模型包括多个机器人节点和一个中心服务器。每轮，每个机器人节点在本地对视觉大模型进行微调并只上传微调部分的参数更新，随后中心服务器对所有更新进行聚合，然后下发聚合后的参数，开启新一轮的联邦微调。以下是系统模型的详细描述。
-As illustrated in Figure \ref{fig1:scene}, \textcolor{red}{consider the scenario of federated fine-tuning (FFT) for large vision language models (LVLMs) in an Internet of Robotic Things (IoRT) network.
+As illustrated in Figure \ref{fig1:scene}, consider the scenario of federated fine-tuning (FFT) for large vision language models (LVLMs) in an Internet of Robotic Things (IoRT) network.
 The entire system model consists of multiple robot nodes and a central server.
@@
 The central server then aggregates all updates and distributes the aggregated parameters to initiate a new round of federated fine-tuning.
-Below is a detailed description of the system model.}
+Below is a detailed description of the system model.
 
 %\textbf{参与者和数据集}：假设系统模型中存在 $N$ 个机器人节点，每个节点记作 $R_i$, 其中$i \in \{1, 2, \ldots, N\}$。 每个机器人节点 $R_i$ 拥有本地数据集 $D_i = \{x_{i,j}, y_{i,j}\}_{j=1}^{|D_i|}$，其中 $x_{i,j}$ 表示训练样本，$y_{i,j}$ 表示对应的标签数据，$|D_i|$ 为数据集的大小，所有节点本地数据集的并集$D = \bigcup_{i=1}^{N} D_i$构成整体数据集。
-\textbf{Participants and Datasets}:
-\textcolor{red}{Assume there are $N$ robot nodes in the system model, with each node denoted as $R_i$, where $i \in {1, 2, \ldots, N}$.
+\textbf{Participants and Datasets}: Assume there are $N$ robot nodes in the system model, with each node denoted as $R_i$, where $i \in {1, 2, \ldots, N}$.
 Each robot node $R_i$ possesses a local dataset $D_i = {x_{i,j}, y_{i,j}}{j=1}^{|D_i|}$, where $x{i,j}$ represents a training sample, $y_{i,j}$ represents the corresponding label, and $|D_i|$ denotes the size of the dataset.
-The union of all local datasets across the nodes, $D = \bigcup_{i=1}^{N} D_i$, constitutes the overall dataset.}
+The union of all local datasets across the nodes, $D = \bigcup_{i=1}^{N} D_i$, constitutes the overall dataset.
 
@@
     %其中，$W_0$ 为模型的原始权重矩阵，$\Delta W$ 是低秩增量矩阵，$B$ 和 $A$ 是低秩分解矩阵，$r$ 为矩阵的秩。在对视觉大模型进行联邦微调的场景中，全局模型原始参数为$\Theta_p = \sum {W_0}$，而LoRA引入的增量参数为$\theta_p = \sum {W}$，因此全局模型的整个参数集为$\Theta = \Theta_p + \theta_g$。在整个联邦微调过程中，仅对全局模型的增量参数$\theta_g$ 进行微调训练，保持原始参数$\Theta_p$不变。
-\textcolor{red}{where $W_0$ represents the original weight matrix of the model, $\Delta W$ denotes the low-rank increment matrix, $B$ and $A$ are the low-rank decomposition matrices, and $r$ is the rank of the matrix.
+where $W_0$ represents the original weight matrix of the model, $\Delta W$ denotes the low-rank increment matrix, $B$ and $A$ are the low-rank decomposition matrices, and $r$ is the rank of the matrix.
 In the scenario of FFT for LVLMs, the fixed parameters of the global model are given by $\Theta_p = \sum {W_0}$, and the incremental parameters introduced by LoRA are denoted as $\theta_g = \sum {W}$.
 Therefore, the entire parameter of the global model is $\Theta = \Theta_p + \theta_g$.
-Throughout the FFT process, only the parameters $\theta_g$ of the global model are fine-tuned, while the parameters $\Theta_p$ remain unchanged.}
+Throughout the FFT process, only the parameters $\theta_g$ of the global model are fine-tuned, while the parameters $\Theta_p$ remain unchanged.
 
@@
 %\item \textbf{联邦聚合}：当中心服务器接收到所有机器人节点的本地更新$\triangledown \theta_i^t$后，利用相应的聚合算法进行聚合得到新一轮的全局增量参数$\theta_g^t$：
-\textbf{Federated Aggregation}:
-\textcolor{red}{After the central server receives the updates $\triangledown \theta_i^t$ from all robot nodes, it applies the appropriate aggregation algorithm to generate the next round's global incremental parameters $\theta_g^t$:
+\textbf{Federated Aggregation}: After the central server receives the updates $\triangledown \theta_i^t$ from all robot nodes, it applies the appropriate aggregation algorithm to generate the next round's global incremental parameters $\theta_g^t$:
 % The central server collects the local updates $\triangledown \theta_i^t$ from each robot node $R_i$ and aggregates them using a specified aggregation algorithm to update the global incremental parameters $\theta_g^t$:
@@
 %其中，$Agg$表示中心服务器使用到的聚合算法，例如FedAvg、FLTrust\cite{cao2020fltrust}、RoseAgg\cite{yang2024roseagg}等，$\theta_g^t$ 是第 $t$ 轮更新的全局增量参数，更新后的全局增量参数 $\theta_g^t$ 将在下一轮训练前下发给所有机器人节点，用于进一步的本地微调。
-where $Agg$ denotes the aggregation algorithm employed by the central server, such as FedAvg, FLTrust \cite{cao2020fltrust}, or RoseAgg \cite{yang2024roseagg}.}
+where $Agg$ denotes the aggregation algorithm employed by the central server, such as FedAvg, FLTrust \cite{cao2020fltrust}, or RoseAgg \cite{yang2024roseagg}.
 
@@
 % 在对视觉语言模型进行联邦微调的场景中，我们假设存在一个或者多个由攻击者操纵的恶意节点，并且恶意节点的数量小于全部参与节点的一半。攻击者的目标是对全局模型$\Theta$ 进行后门植入，使得模型能够将任何带有预定义触发器 $\delta$ 的测试输入分类为目标类别，即$\Theta(x+\delta) = y'$，其中$x$代表正常输入，$y'$表示目标类别。同时尽可能保持对干净输入的分类准确性，即$\Theta(x) = y$，其中$y$为输出$x$的原始类别。
-\textcolor{red}{In the scenario of FFT for LVLMs, we assume the presence of one or more malicious nodes controlled by attackers, with the number of malicious nodes being less than half of all participating nodes.}
+In the scenario of FFT for LVLMs, we assume the presence of one or more malicious nodes controlled by attackers, with the number of malicious nodes being less than half of all participating nodes.
 
@@
 %Attacker's Ability: 攻击者对恶意节点的本地训练过程具有完全的控制权，意味着攻击者可以任意操控本地数据、触发器模式、优化策略和本地更新。此外，攻击者可以采用“智能”攻击策略，这种策略的特点是攻击效果不会在单轮训练中显现，而是通过多轮训练的累积效应逐步将后门植入全局模型中。这种场景在实际中是可能存在的，因为中央服务器只能接收到客户端上传的训练后模型更新，而无法知晓每个客户端的具体训练过程。然而，攻击者无法对中央服务器的操作进行干扰，例如，无法更改全局模型的聚合规则或篡改其他良性客户端的本地更新。
-\textbf{Attacker's Ability:} 
-\textcolor{red}{The attacker has complete control over the local training process of the malicious robot nodes, meaning they can manipulate local data, trigger patterns, optimization strategies, and local updates at will.
+\textbf{Attacker's Ability:} The attacker has complete control over the local training process of the malicious robot nodes, meaning they can manipulate local data, trigger patterns, optimization strategies, and local updates at will.
 Additionally, the attacker may adopt a stealthy attack strategy, where the backdoor is not implanted in a single training round but gradually embedded into the global model through the cumulative effect of multiple rounds of training.
 This scenario is plausible in practice, as the central server only receives the updates uploaded by robot nodes and has no insight into the specific training process of each node.
-However, the attacker cannot interfere with the aggregation process of the central server (i.e., altering the global model aggregation rules) or tamper with the local updates of benign nodes.}
+However, the attacker cannot interfere with the aggregation process of the central server (i.e., altering the global model aggregation rules) or tamper with the local updates of benign nodes.
 
@@
 This allows them to bypass defenses based on shallow semantic features and eventually implant backdoors into the global model.
-\textcolor{red}{Despite the increasingly sophisticated strategies employed by attackers, it is important to note that the essence of backdoor attacks lies in establishing a link between the predefined trigger and the target within the model.
-Thus, regardless of how attackers adjust their attack strategies, their updates will always exhibit some distributional shift compared to benign nodes.}
+Despite the increasingly sophisticated strategies employed by attackers, it is important to note that the essence of backdoor attacks lies in establishing a link between the predefined trigger and the target within the model.
+Thus, regardless of how attackers adjust their attack strategies, their updates will always exhibit some distributional shift compared to benign nodes.
 
@@
 nonetheless, When a backdoor attack forces the neural network to learn an association that does not exist in normal data, which may be subtle or quite obvious depending on the design and implementation of the backdoor trigger, it invariably represents a deviation from the association learned by the model from normal data.
-\textcolor{red}{To address the limitations faced by defense methods based on shallow semantic features in high-dimensional spaces, we propose a new defense strategy rooted in the essence of backdoor attacks \cite{zeng2021rethinking}, which leverages deep semantic features by focusing on the differences in model updates in the frequency domain.
+To address the limitations faced by defense methods based on shallow semantic features in high-dimensional spaces, we propose a new defense strategy rooted in the essence of backdoor attacks \cite{zeng2021rethinking}, which leverages deep semantic features by focusing on the differences in model updates in the frequency domain.
 According to our experimental results, by transforming local model updates into the frequency domain, we can more accurately capture the abnormal behavior of malicious updates which is typically difficult to detect using traditional shallow feature-based defenses in low-frequency components.
-By analyzing the relevant features in the frequency domain, we can effectively distinguish between malicious and benign nodes, thereby enhancing the robustness and accuracy of federated learning in the face of sophisticated backdoor attacks.}
+By analyzing the relevant features in the frequency domain, we can effectively distinguish between malicious and benign nodes, thereby enhancing the robustness and accuracy of federated learning in the face of sophisticated backdoor attacks.
 
@@
 Focusing on the analysis of these low-frequency components not only improves identification accuracy but also significantly reduces computational overhead.
-\textcolor{red}{For each update \(\triangledown \theta_i^t\), we apply one-dimensional DCT-II \cite{ahmed1974discrete} to obtain its corresponding frequency distribution.
-Then we extract $m$ low-frequency components\cite{fereidooni2023freqfed}, such as 5000, yielding the low-frequency vector $G_i^t$.}
+For each update \(\triangledown \theta_i^t\), we apply one-dimensional DCT-II \cite{ahmed1974discrete} to obtain its corresponding frequency distribution.
+Then we extract $m$ low-frequency components\cite{fereidooni2023freqfed}, such as 5000, yielding the low-frequency vector $G_i^t$.
 
@@
 This behavior is also evident in the frequency domain, where it becomes even more pronounced.
-\textcolor{red}{Based on this observation, we select the largest cluster \(C^t_{max} = \{G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}\}\) as the primary subject for analysis.
+Based on this observation, we select the largest cluster \(C^t_{max} = \{G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}\}\) as the primary subject for analysis.
 To further extract the main characteristics of this cluster, we perform singular value decomposition (SVD)\cite{wang2023scfl} on the matrix $H^t = (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n}$ formed by all nodes in this cluster.
-Since the left singular vectors of the SVD, denoted as \(\tilde{G}^t\), represent the principal directions of these vectors, \(\tilde{G}^t\) can be regarded as the principal ingredient of benign nodes in the low-frequency domain.}
+Since the left singular vectors of the SVD, denoted as \(\tilde{G}^t\), represent the principal directions of these vectors, \(\tilde{G}^t\) can be regarded as the principal ingredient of benign nodes in the low-frequency domain.
 
@@
 
-\textcolor{red}{
 \begin{equation}
@@
 \label{equation:KL}
-\end{equation}}
+\end{equation}
 % 其中 \(m\) 是低频向量的维度，\(\epsilon\) 是一个小的常数，用于避免分母为零。相比于传统的欧氏距离，卡方距离根据两个向量对应分量的大小进行加权，使得特征值较大的部分对距离的影响更大，从而能够更准确地反映低频向量中重要特征之间的差异，同时忽略不重要的噪声成分。
@@
 
-\textcolor{red}{
 Chi-square distance is usually used to measure whether a certain observed distribution conforms to a typical theoretical distribution, which is very consistent with our method because we use the calculated clean ingredient as a criterion for measuring benign and malicious nodes.
@@
 However, in our method, we are concerned with the degree of deviation of each user's low-frequency vector $G_i^t$ from the clean ingredient $\tilde{G}^t$, including magnitude differences, so the chi-square distance is more suitable for capturing hidden malicious attacks than cosine similarity.
-}
+
 % 为什么要用卡方距离，不用欧式距离？实验论证？
@@
 % \State Step 1: Frequency Domain Transformation
-\For {$R_i \in \textcolor{red}{\{R_1, \ldots, R_N\}}$}
-    \State \textcolor{red}{$G_i^t \gets Trunc(DCT(Flatten(\triangledown \theta_i^t))), m)$}
+\For {$R_i \in \{R_1, \ldots, R_N\}$}
+    \State $G_i^t \gets Trunc(DCT(Flatten(\triangledown \theta_i^t))), m)$
 \EndFor
@@
 % \State Step 2: Clean Ingredient Extraction
-\State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering\textcolor{red}{ (G_0^t, G_1^t, \ldots, G_N^t)}$ \Comment{$\kappa$ denotes the number of clusters}
-\State \textcolor{red}{$ C^t_{max} \gets \underset{C^t_j}{\arg\max} \, |C^t_j|$ \Comment{$|C^t_j|$ denotes the number of nodes in cluster $C^t_j$, $j = 1, 2, \ldots, \kappa $}}
+\State $(C_0^t, C_1^t, \ldots, C_{\kappa}^t) \gets Clustering (G_0^t, G_1^t, \ldots, G_N^t)$ \Comment{$\kappa$ denotes the number of clusters}
+\State $ C^t_{max} \gets \underset{C^t_j}{\arg\max} \, |C^t_j|$ \Comment{$|C^t_j|$ denotes the number of nodes in cluster $C^t_j$, $j = 1, 2, \ldots, \kappa $}
 \State $H^t \gets (G^t_{i_0}, G^t_{i_1}, \ldots, G^t_{i_n}) \in \mathbb{R}^{m \times n} $ \Comment{Stacking to form Matrix $H^t$, where $R_{i_0}, R_{i_1}, \ldots, R_{i_n} \in C^t_{max}$.}
@@
 % \State $P_i^t \gets Softmax(G_i^t), \, Q^t \gets Softmax(\tilde{G}^t)$
-\For {$R_i \in \textcolor{red}{\{R_1, \ldots, R_N\}}$}
-    \State \textcolor{red}{$Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|{\tilde G}^t[k]| + \epsilon}}$}
+\For {$R_i \in \{R_1, \ldots, R_N\}$}
+    \State $Chi^t_i \gets \sqrt{\sum_{k=0}^{m-1}\frac{(G_i^t[k] - {\tilde G}^t[k])^2}{|{\tilde G}^t[k]| + \epsilon}}$
 \EndFor
-\State \textcolor{red}{$S^t \gets \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}$} \Comment{The Distance differences calculated by Chi-square distance.}
+\State $S^t \gets \{Chi^t_1, Chi^t_2, \ldots, Chi^t_N\}$ \Comment{The Distance differences calculated by Chi-square distance.}
 
@@
 % \State Step 4: Single-round malicious behavior perception
-\State $\textcolor{red}{\{{C^t_1}', {C^t_2}'\}} \gets KMeans(S^t, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
-\State \textcolor{red}{$U_{nor} \gets C'_{max}$, $U_{mal} \gets \{C'_i \, | \, i \neq max\}$}
+\State $\{{C^t_1}', {C^t_2}'\} \gets KMeans(S^t, 2)$ \Comment{Cluster $S$ into 2 clusters using KMeans.}
+\State $U_{nor} \gets C'_{max}$, $U_{mal} \gets \{C'_i \, | \, i \neq max\}$
 
@@
 
-\textcolor{red}{In our proposed framework, the concept of the "intention point" serves as a pivotal element in recognizing the underlying motives of malicious nodes during the federated fine-tuning process.
+In our proposed framework, the concept of the "intention point" serves as a pivotal element in recognizing the underlying motives of malicious nodes during the federated fine-tuning process.
 The intention point is defined as the central position within a high-dimensional space, representing the aggregated gradient updates of a node across multiple training rounds.
@@
 The radius of this hypersphere reflects the reliability of the intention point, effectively quantifying the node's consistency in updating the model.
-By analyzing these intention points, our method can discern the behaviors of malicious nodes from benign ones, enhancing the overall security and robustness of the federated learning system.}
-
-\textcolor{red}{Figure \ref{fig3:longterm} illustrates the first two steps of the Long-term Attack Intention Detection.
+By analyzing these intention points, our method can discern the behaviors of malicious nodes from benign ones, enhancing the overall security and robustness of the federated learning system.
+
+Figure \ref{fig3:longterm} illustrates the first two steps of the Long-term Attack Intention Detection.
 The figure comprises three rows overall.
@@
 The right section of the image represents the global model in each round.
-The third row depicts how a single node's intention point is calculated based on multi-round historical data, where each ray signifies the flattened results of the model updates, and the hypersphere's center represents the current node's intention point.}
+The third row depicts how a single node's intention point is calculated based on multi-round historical data, where each ray signifies the flattened results of the model updates, and the hypersphere's center represents the current node's intention point.
 
@@
 
-\For {Client \textcolor{red}{$i\in \{1\ldots N\}$}}
+\For {Client $i\in \{1\ldots N\}$}
 
@@
     \State Initialize center $O_{i,0}$ and radius $r_{i,0}$
-    \While {\textcolor{red}{$\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$}}
+    \While {$\|O_{i,k}-O_{i,k+1}\|\geq \lambda$ and $k\leq k_{max}$}
         \State Update center $O_{i,k+1}$ and radius $r_{i,k+1}$
@@
 
-    \For {Each point $O_j \neq O_i$\textcolor{red}{, $j\in\{1\ldots N\}$}}
+    \For {Each point $O_j \neq O_i$, $j\in\{1\ldots N\}$}
         \State Calculate distance $\|O_i - O_j\|$
@@
 \textbf{Attack paradigms:} we employed three state-of-the-art attacks targeting federated learning scenarios, namely \textbf{MR}\cite{MR}, \textbf{EDGE CASE}\cite{EDGE_CASE}, and \textbf{NEUR}\cite{zhang2022neurotoxin}.
-The MR attack generates a malicious dataset by combining poisoned images with normal ones and employing the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack employs rare "edge-case" samples to inject backdoors into the federated learning model through data or model poisoning; the NEUR attack seeks to identify parameters that are seldom updated during normal node training and uses these parameters to insert backdoors, thereby enhancing the persistence of the backdoor\color{red}{\cite{yao2022blockchain}}\color{black}{.}
+The MR attack generates a malicious dataset by combining poisoned images with normal ones and employing the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack employs rare "edge-case" samples to inject backdoors into the federated learning model through data or model poisoning; the NEUR attack seeks to identify parameters that are seldom updated during normal node training and uses these parameters to insert backdoors, thereby enhancing the persistence of the backdoor \cite{yao2022blockchain}\color{black}{.}
 
@@
 FLTrust employs a clean dataset and aggregates only those updates from nodes that exhibit high cosine similarity with the updates derived from the clean dataset.
-Flame estimates and injects an appropriate amount of noise via model clustering and weight clipping to mitigate backdoor attacks in federated learning effectively\color{red}{\cite{yao2024leoedge}}\color{black}{.}
+Flame estimates and injects an appropriate amount of noise via model clustering and weight clipping to mitigate backdoor attacks in federated learning effectively \cite{yao2024leoedge}\color{black}{.}
 
@@
 The attacker's goal is to maintain the TSR of the model as unchanged as possible to avoid easy detection, while effective defense measures should not significantly reduce the TSR.
-\textcolor{red}{For instantaneous attack behavior perception,} similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
+For instantaneous attack behavior perception, similar to the evaluation metrics employed in other studies\cite{tang2023port, jin2024learning, rong2023special}, we utilize two key metrics to assess the effectiveness of poisoning attacks and defense mechanisms: \textbf{ASR} (Attack Success Rate) and \textbf{TSR} (Test Success Rate).
 ASR denotes the probability that malicious nodes successfully manipulate the global model to predict a specified target.
@@
 The attacker aims to keep the TSR of the model as stable as possible to avoid easy detection, whereas effective defense mechanisms should not significantly degrade the TSR.
-\textcolor{red}{For long-term attack intention detection, ``Acc" refers to accuracy, which measures the proportion of correct predictions; ``Rec" stands for recall, representing the model's ability to identify positive instances correctly; ``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; ``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; ``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.}
+For long-term attack intention detection, ``Acc" refers to accuracy, which measures the proportion of correct predictions; ``Rec" stands for recall, representing the model's ability to identify positive instances correctly; ``FPR" denotes the false positive rate, indicating the proportion of negative instances incorrectly predicted as positive; ``FNR" refers to the false negative rate, which represents the proportion of positive instances incorrectly predicted as negative; ``AUC" stands for the area under the curve, reflecting the model's overall ability to distinguish between positive and negative instances; and``MCC" represents the Matthews correlation coefficient, which provides a balanced evaluation of the model's predictions.
 
@@
 As depicted in the figure, in all attack scenarios, SecFFT consistently achieves an attack success rate (ASR) close to zero, while the test success accuracy (TSR) remains high.
-\textcolor{red}{This indicates that SecFFT effectively defends against attacks by accurately identifying and neutralizing malicious users, all while preserving the performance and accuracy of the global model.
+This indicates that SecFFT effectively defends against attacks by accurately identifying and neutralizing malicious users, all while preserving the performance and accuracy of the global model.
 In contrast, other defense mechanisms perform less effectively.
@@
 Overall, the comparison highlights that other defense mechanisms either fail to effectively resist attacks or compromise model performance during defense.
-This further underscores SecFFT's significant advantage in federated fine-tuning for backdoor attack resistance, making it the optimal defense choice.}
+This further underscores SecFFT's significant advantage in federated fine-tuning for backdoor attack resistance, making it the optimal defense choice.
 % SecFFT exhibits the highest robustness and superior model performance when confronted with three types of attack scenarios (MR, NEUR, EDGE CASE).
@@
 Comparatively, SecFFT performs the best in dealing with various attack types, effectively reducing the misidentification rate and showing better generalization ability and accuracy.
-As illustrated in the Figure \ref{fig:lab2}, comparatively, \textcolor{red}{SecFFT outperforms other mechanisms in handling various attack.
+As illustrated in the Figure \ref{fig:lab2}, comparatively, SecFFT outperforms other mechanisms in handling various attack.
 SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes.
@@
 Among them, FoolsGold exhibits the highest misidentification rate.
-It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}
+It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.
 
@@
     % \caption{图中展示了四种防御方法（Foolsgold \cite{foolsgold}、FLTrust \cite{FLTrust}、Flame \cite{FLAME}、SecFFT）对三种攻击（EdgeCase \cite{EDGE_CASE}、大小限制的EdgeCase、同时限制大小和角度的EdgeCase）的防御效果。每个实验使用50个客户端（0-19为恶意客户端）。第一到三行分别代表EdgeCase攻击、限制大小的EdgeCase攻击和同时限制大小和角度的EdgeCase攻击。各列分别展示了基于余弦相似度（Foolsgold）、聚合权重（FLTrust）、HDBSCAN概率得分（Flame）和意图点相似度（SecFFT）的结果。}
-    \caption{\textcolor{red}{The figure illustrates the defense performance of four methods—Foolsgold \cite{foolsgold}, FLTrust \cite{FLTrust}, Flame \cite{FLAME}, and SecFFT—against three attack types: EdgeCase \cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle.
+    \caption{The figure illustrates the defense performance of four methods—Foolsgold \cite{foolsgold}, FLTrust \cite{FLTrust}, Flame \cite{FLAME}, and SecFFT—against three attack types: EdgeCase \cite{EDGE_CASE}, size-constrained EdgeCase, and EdgeCase constrained by both size and angle.
 Each experiment involves 50 nodes, with nodes 0-19 being malicious.
 The first to third rows represent EdgeCase attacks, size-constrained EdgeCase attacks, and EdgeCase attacks constrained by both size and angle, respectively.
-The columns show results based on cosine similarity (Foolsgold algorithm 1 line 7), aggregation weights (FLTrust algorithm 2 line 15), HDBSCAN probability scores (Flame Chapter 2.4), and intent-point similarity (SecFFT).}}
+The columns show results based on cosine similarity (Foolsgold algorithm 1 line 7), aggregation weights (FLTrust algorithm 2 line 15), HDBSCAN probability scores (Flame Chapter 2.4), and intent-point similarity (SecFFT).}
     \label{fig:lab3}
@@
 To validate the capability of SecFFT in constructing attack intent and effectively defending against advanced covert backdoor attacks employing complex strategies, we added Size and Angle constraints to the NEUR attack over multiple rounds.
-As shown in \textcolor{red}{Figure \ref{fig:lab3}}, by comparing with typical behavior-based defense mechanisms such as Foolsgold, FLTrust, and Flame, it is evident that the intent-based SecFFT significantly enhances attack detection capabilities.
+As shown in Figure \ref{fig:lab3}, by comparing with typical behavior-based defense mechanisms such as Foolsgold, FLTrust, and Flame, it is evident that the intent-based SecFFT significantly enhances attack detection capabilities.
 Even though certain defense methods like Flame can effectively identify some highly covert attack behaviors, their detection performance is quickly bypassed when more complex multi-round attack strategies are introduced.
@@
 
-\textcolor{red}{As shown in Figure \ref{fig:lab3}, the Foolsgold defense algorithm shows moderate performance against EdgeCase attacks, but it can generally identify similar behaviors among benign bot nodes.
+As shown in Figure \ref{fig:lab3}, the Foolsgold defense algorithm shows moderate performance against EdgeCase attacks, but it can generally identify similar behaviors among benign bot nodes.
 The size constraint does not affect the cosine similarity results, but once both size and angle are constrained, Foolsgold fails to defend effectively.
-The metric used for Foolsgold in the plots is the $wv$ value from line 7 of Algorithm 1 in the original paper, which corresponds to the value in the author's open-source code.}
-
-\textcolor{red}{For FLTrust, its defense against EdgeCase attacks is slightly better than Foolsgold, but there is still some similarity between malicious and benign nodes.
+The metric used for Foolsgold in the plots is the $wv$ value from line 7 of Algorithm 1 in the original paper, which corresponds to the value in the author's open-source code.
+
+For FLTrust, its defense against EdgeCase attacks is slightly better than Foolsgold, but there is still some similarity between malicious and benign nodes.
 The size constraint has no impact on FLTrust's performance, but when both size and angle are constrained, its defense effectiveness declines significantly, making it unable to accurately identify malicious nodes.
-The metric for FLTrust is the $weights$ value from line 15 of Algorithm 2 in the original paper, corresponding to the result of applying the ReLU activation function to the cosine similarity of gradient changes between pairs of bot nodes in the author's open-source code.}
-
-\textcolor{red}{Flame uses HDBSCAN clustering for identification.
+The metric for FLTrust is the $weights$ value from line 15 of Algorithm 2 in the original paper, corresponding to the result of applying the ReLU activation function to the cosine similarity of gradient changes between pairs of bot nodes in the author's open-source code.
+
+Flame uses HDBSCAN clustering for identification.
 The metric is the cluster probability ($Prob$) obtained after calling the HDBSCAN library function in the author's open-source code.
@@
 For instance, bot nodes 25, 31, 32, and 34 are incorrectly identified as noise points rather than core or border points.
-This is due to HDBSCAN's hierarchical density clustering, which prioritizes the creation of stable clusters and merges points, classifying outliers with scores similar to benign bot nodes (e.g., 25, 31, 32, and 34) as noise.}
-
-\textcolor{red}{For SecFFT, the defense is based on intent-point similarity.
+This is due to HDBSCAN's hierarchical density clustering, which prioritizes the creation of stable clusters and merges points, classifying outliers with scores similar to benign bot nodes (e.g., 25, 31, 32, and 34) as noise.
+
+For SecFFT, the defense is based on intent-point similarity.
 Under EdgeCase attacks, SecFFT accurately identifies malicious bot nodes while showing low similarity among benign nodes.
-The size constraint has minimal impact on SecFFT's performance, and even with both size and angle constraints, SecFFT maintains strong similarity classification with perfect accuracy.}
-
-Table \ref{tab:detect} provides a detailed quantitative analysis of the classification metrics for the four defense mechanisms against different strategies \textcolor{red}{of EdgeCase}.
+The size constraint has minimal impact on SecFFT's performance, and even with both size and angle constraints, SecFFT maintains strong similarity classification with perfect accuracy.
+
+Table \ref{tab:detect} provides a detailed quantitative analysis of the classification metrics for the four defense mechanisms against different strategies of EdgeCase.
 It is clear that SecFFT not only consistently preserves its strong backdoor attack mitigation capability but also achieves the best detection accuracy, with significantly reduced false positive rates, ensuring reliable and robust performance.
